### 2020-10-11 material/stimuli/R/analysis/ioi.Rmd
add analsysi script TBC
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Tempo Analysis: The Sound of Teaching Music 1'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a summary of all analyses for a tempo.

- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`

# Overview
## IOIs

## Articulation

## Dynamics

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}

# ggplots
theme_set(theme_classic())
theme_update(text = element_text(size = 20, family = "Helvetica Neue LT Std 57 Condensed"), legend.position = "bottom")
```

```{r file, include = FALSE}
# create a list of data file names
lf_a_t <- list.files("../filtered/art_teaching", pattern = "txt")
lf_a_p <- list.files("../filtered/art_performing", pattern = "txt")
lf_d_t <- list.files("../filtered/dyn_teaching", pattern = "txt")
lf_d_p <- list.files("../filtered/dyn_performing", pattern = "txt")

# merge all data files into one
data <- data.table()
for (i in 1:length(lf_a_t)){
  data_i <- fread(file.path("../filtered/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_a_p)){
  data_i <- fread(file.path("../filtered/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_d_t)){
  data_i <- fread(file.path("../filtered/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_d_p)){
  data_i <- fread(file.path("../filtered/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}

# define subcomponents
# For intervals
ls_legato <- list(c(1:7), c(17:23), c(42:48), c(58:64))
ls_staccato <- list(c(9:15), c(25:31), c(34:40), c(50:56))
ls_forte <- list(c(1:7), c(17:23), c(42:48), c(58:64))
ls_piano <- list(c(9:15), c(25:31), c(34:40), c(50:56))

# For each note (velocity only)
ls_legato_2 <- list(c(1:8), c(17:24), c(42:49), c(58:65))
ls_staccato_2 <- list(c(9:16), c(25:32), c(34:41), c(50:57))
ls_forte_2 <- list(c(1:8), c(17:24), c(42:49), c(58:65))
ls_piano_2 <- list(c(9:16), c(25:32), c(34:41), c(50:57))

# Define Skill Change (LtoS, FtoP)
change_1 <- c(8, 24, 49)
# Define Skill Change (StoL, PtoF)
change_2 <- c(16, 41, 57)
```

# IOIs
```{r ioi, include = FALSE}
data_onset <- data[Key_OnOff == 1]
data_offset <- data[Key_OnOff == 0]

data_onset$IOI <- diff(c(0, data_onset$TimeStamp))
dt_ioi <- data_onset[NoteNr != 17]
dt_ioi$Interval <- rep(1:66, nrow(dt_ioi)/66)

# assign Subcomponents
dt_ioi$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato)){
  for (note in 1:length(ls_legato[[phrase]])){
    dt_ioi[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
  }
}
# Staccato
for (phrase in 1:length(ls_staccato)){
  for (note in 1:length(ls_staccato[[phrase]])){
    dt_ioi[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
  }
}

# Forte
for (phrase in 1:length(ls_forte)){
  for (note in 1:length(ls_forte[[phrase]])){
    dt_ioi[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
  }
}
# Piano
for (phrase in 1:length(ls_piano)){
  for (note in 1:length(ls_piano[[phrase]])){
    dt_ioi[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
  }
}

# assign Subcomponent Change
for (number in change_1){
  dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
  dt_ioi[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
}
for (number in change_2){
  dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
  dt_ioi[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
}

ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(Instance, Condition, Skill)]
ioi_all <- ioi[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill)]
```

```{r ioi_plot, echo = FALSE}
p_ioi <- ggplot(ioi, aes(x = Instance, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  geom_hline(yintercept = 188, linetype = "dashed") +
  facet_grid(Skill ~ .) +
  labs(y = "IOI (ms)", subtitle = "IOI: Each instance")
p_ioi

p_ioi_all <- ggplot(ioi_all, aes(x = Skill, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  geom_hline(yintercept = 188, linetype = "dashed") +
  labs(y = "IOI (ms)", subtitle = "IOI: Each instance")
p_ioi_all
```

### 2020-10-11 script/psychopy/experiment.py
fix typo
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -90,7 +90,7 @@ def trial(expMode, imageFile, midFile, resultsList):
 os.system("open " + "./midiplayer.maxpat") # open max file
 port = mido.open_output("to Max 1")
 
-# participants’s info
+# participants's info
 expInfo = {"Number": "", "Today": data.getDateStr(), "Expression": ["Articulation", "Dynamics"]}
 dlg = gui.DlgFromDict(expInfo, fixed = ["Today"], title = "Music Perception 2020")
 if dlg.OK == False:

### 2020-10-11 material/stimuli/R/analysis/ioi.Rmd
correct comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ---
-title: 'Tempo Analysis: The Sound of Teaching Music 1'
+title: 'Music Perception 2020: Stimuli profiles'
 output:
@@
 ---
-
-Description: This is a summary of all analyses for a tempo.
 

### 2020-10-12 material/stimuli/R/analysis/random.Rmd
update analysis for stimuli
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Music Perception 2020: Stimuli profiles (random)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`

I chose stimuli randomly.  
Note: SubNr16 was excluded because of a deviated tempo (see analysis for [teaching-v1.0](https://github.com/atsukotominaga/teaching-v1.0))

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}

# ggplots
theme_set(theme_classic())
theme_update(text = element_text(size = 20, family = "Helvetica Neue LT Std 57 Condensed"), legend.position = "bottom")
```

```{r file, include = FALSE}
# create a list of data file names
lf_a_t <- list.files("../filtered/art_teaching", pattern = "txt")
lf_a_p <- list.files("../filtered/art_performing", pattern = "txt")
lf_d_t <- list.files("../filtered/dyn_teaching", pattern = "txt")
lf_d_p <- list.files("../filtered/dyn_performing", pattern = "txt")

# merge all data files into one
data <- data.table()
for (i in 1:length(lf_a_t)){
  data_i <- fread(file.path("../filtered/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_a_p)){
  data_i <- fread(file.path("../filtered/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_d_t)){
  data_i <- fread(file.path("../filtered/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_d_p)){
  data_i <- fread(file.path("../filtered/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}

# define subcomponents
# For intervals
ls_legato <- list(c(1:7), c(17:23), c(42:48), c(58:64))
ls_staccato <- list(c(9:15), c(25:31), c(34:40), c(50:56))
ls_forte <- list(c(1:7), c(17:23), c(42:48), c(58:64))
ls_piano <- list(c(9:15), c(25:31), c(34:40), c(50:56))

# For each note (velocity only)
ls_legato_2 <- list(c(1:8), c(17:24), c(42:49), c(58:65))
ls_staccato_2 <- list(c(9:16), c(25:32), c(34:41), c(50:57))
ls_forte_2 <- list(c(1:8), c(17:24), c(42:49), c(58:65))
ls_piano_2 <- list(c(9:16), c(25:32), c(34:41), c(50:57))

# Define Skill Change (LtoS, FtoP)
change_1 <- c(8, 24, 49)
# Define Skill Change (StoL, PtoF)
change_2 <- c(16, 41, 57)
```

# IOIs
```{r ioi, include = FALSE}
data_onset <- data[Key_OnOff == 1]
data_offset <- data[Key_OnOff == 0]

data_onset$IOI <- diff(c(0, data_onset$TimeStamp))
dt_ioi <- data_onset[NoteNr != 17]
dt_ioi$Interval <- rep(1:66, nrow(dt_ioi)/66)

# assign Subcomponents
dt_ioi$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato)){
  for (note in 1:length(ls_legato[[phrase]])){
    dt_ioi[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
  }
}
# Staccato
for (phrase in 1:length(ls_staccato)){
  for (note in 1:length(ls_staccato[[phrase]])){
    dt_ioi[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
  }
}

# Forte
for (phrase in 1:length(ls_forte)){
  for (note in 1:length(ls_forte[[phrase]])){
    dt_ioi[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
  }
}
# Piano
for (phrase in 1:length(ls_piano)){
  for (note in 1:length(ls_piano[[phrase]])){
    dt_ioi[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
  }
}

# assign Subcomponent Change
for (number in change_1){
  dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
  dt_ioi[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
}
for (number in change_2){
  dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
  dt_ioi[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
}

ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(Instance, Condition, Skill)]
ioi_all <- ioi[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill)]
```

## Each instance
```{r ioi_stats_ind, echo = FALSE}
ioi
```

## Averaged
```{r ioi_stats_all, echo = FALSE}
ioi_all
```

## Plots
```{r ioi_plot, echo = FALSE}
p_ioi <- ggplot(ioi, aes(x = Instance, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  geom_hline(yintercept = 188, linetype = "dashed") +
  facet_grid(Skill ~ .) +
  labs(y = "IOI (ms)", subtitle = "IOI: Each instance (All)")
p_ioi

p_ioi_all <- ggplot(ioi_all, aes(x = Skill, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  geom_hline(yintercept = 188, linetype = "dashed") +
  labs(y = "IOI (ms)", subtitle = "IOI: Averaged (All)")
p_ioi_all
```

# KOT
```{r kot, include = FALSE}
data_onset$KOT <- NA
for (row in 1:nrow(data_onset)){
  if (row < nrow(data_onset)){
    data_onset$KOT[row+1] <- data_offset$TimeStamp[row] - data_onset$TimeStamp[row+1] # offset(n) - onset(n+1)
  }
}

dt_kot <- data_onset[NoteNr != 17]
dt_kot$Interval <- rep(1:66, nrow(dt_kot)/66)

# assign Subcomponents
dt_kot$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato)){
  for (note in 1:length(ls_legato[[phrase]])){
    dt_kot[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
  }
}
# Staccato
for (phrase in 1:length(ls_staccato)){
  for (note in 1:length(ls_staccato[[phrase]])){
    dt_kot[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
  }
}

# Forte
for (phrase in 1:length(ls_forte)){
  for (note in 1:length(ls_forte[[phrase]])){
    dt_kot[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
  }
}
# Piano
for (phrase in 1:length(ls_piano)){
  for (note in 1:length(ls_piano[[phrase]])){
    dt_kot[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
  }
}

# assign Subcomponent Change
for (number in change_1){
  dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
  dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
}
for (number in change_2){
  dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
  dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
}

kot <- dt_kot[Subcomponent == "Legato" | Subcomponent == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(Instance, Condition, Skill, Subcomponent)]
kot_all <- kot[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Subcomponent)]
```

## Plots
```{r kot_plot, echo = FALSE}
p_kot <- ggplot(kot, aes(x = Instance, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "KOT (ms)", subtitle = "KOT: Each instance (Articulation)")
p_kot

p_kot_all <- ggplot(kot_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  labs(y = "KOT (ms)", subtitle = "KOT: Averaged (Articulation)")
p_kot_all
```

## Each instance
```{r kot_stats_ind, echo = FALSE}
kot
```

## Averaged
```{r kot_stats_all, echo = FALSE}
kot_all
```

# KV
```{r kv, include = FALSE}
dt_vel <- data_onset
dt_vel$Note <- rep(1:67, nrow(dt_vel)/67)

# assign Subcomponents
# for each note
dt_vel$Subcomponent <- NA
# Legato
for (phrase in 1:length(ls_legato_2)){
  for (note in 1:length(ls_legato_2[[phrase]])){
    dt_vel$Subcomponent[dt_vel$Skill == "articulation" & dt_vel$Note == ls_legato_2[[phrase]][note]] <- "Legato"
  }
}
# Staccato
for (phrase in 1:length(ls_staccato_2)){
  for (note in 1:length(ls_staccato_2[[phrase]])){
    dt_vel$Subcomponent[dt_vel$Skill == "articulation" & dt_vel$Note == ls_staccato_2[[phrase]][note]] <- "Staccato"
  }
}

# Forte
for (phrase in 1:length(ls_forte_2)){
  for (note in 1:length(ls_forte_2[[phrase]])){
    dt_vel$Subcomponent[dt_vel$Skill == "dynamics" & dt_vel$Note == ls_forte_2[[phrase]][note]] <- "Forte"
  }
}

# Piano
for (phrase in 1:length(ls_piano_2)){
  for (note in 1:length(ls_piano_2[[phrase]])){
    dt_vel$Subcomponent[dt_vel$Skill == "dynamics" & dt_vel$Note == ls_piano_2[[phrase]][note]] <- "Piano"
  }
}

vel <- dt_vel[Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(Instance, Condition, Skill, Subcomponent)]
vel_all <- vel[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Subcomponent)]
```

## Each instance
```{r vel_stats_ind, echo = FALSE}
vel
```

## Averaged
```{r vel_stats_all, echo = FALSE}
vel_all
```

## Plots
```{r vel_plot, echo = FALSE}
p_vel <- ggplot(vel, aes(x = Instance, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "Key Velocity", subtitle = "KV: Each instance (Dynamics)")
p_vel

p_vel_all <- ggplot(vel_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  labs(y = "Key Velocity", subtitle = "KV: Averaged (Dynamics)")
p_vel_all
```

# KV-Diff
```{r vel_diff, include = FALSE}
# calculate differences and remove the first note
dt_vel$Diff <- diff(c(0, dt_vel$Velocity))
dt_vel_diff <- dt_vel[Note != 1]
dt_vel$Diff <- NULL # remove Diff from dt_vel

# assign Interval
dt_vel_diff$Interval <- rep(1:66, nrow(dt_vel_diff)/66)

# assign Subcomponents
# for intervals
dt_vel_diff$Subcomponent <- NA
# Legato
for (phrase in 1:length(ls_legato)){
  for (note in 1:length(ls_legato[[phrase]])){
    dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == ls_legato[[phrase]][note]] <- "Legato"
  }
}
# Staccato
for (phrase in 1:length(ls_staccato)){
  for (note in 1:length(ls_staccato[[phrase]])){
    dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == ls_staccato[[phrase]][note]] <- "Staccato"
  }
}

# Forte
for (phrase in 1:length(ls_forte)){
  for (note in 1:length(ls_forte[[phrase]])){
    dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == ls_forte[[phrase]][note]] <- "Forte"
  }
}
# Piano
for (phrase in 1:length(ls_piano)){
  for (note in 1:length(ls_piano[[phrase]])){
    dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == ls_piano[[phrase]][note]] <- "Piano"
  }
}

# Assign Skill Change
for (i in change_1){
  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "LtoS"
  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "FtoP"
}
for (i in change_2){
  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "StoL"
  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "PtoF"
}

vel_diff <- dt_vel_diff[Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(Instance, Condition, Skill, Subcomponent)]
vel_diff_all <- vel_diff[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Subcomponent)]
```

## Each instance
```{r vel__diff_stats_ind, echo = FALSE}
vel_diff
```

## Averaged
```{r vel_diff_stats_all, echo = FALSE}
vel_diff_all
```

## Plots
```{r vel_diff_plot, echo = FALSE}
p_vel_diff <- ggplot(vel_diff, aes(x = Instance, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "KV difference", subtitle = "KV-Diff: Each instance (Dynamics)")
p_vel_diff

p_vel_diff_all <- ggplot(vel_diff_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  labs(y = "KV difference", subtitle = "KV-Diff: Averaged (Dynamics)")
p_vel_diff_all
```

### 2020-10-12 material/stimuli/R/analysis/random.Rmd
random filtering
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 # create a list of data file names
-lf_a_t <- list.files("../filtered/art_teaching", pattern = "txt")
-lf_a_p <- list.files("../filtered/art_performing", pattern = "txt")
-lf_d_t <- list.files("../filtered/dyn_teaching", pattern = "txt")
-lf_d_p <- list.files("../filtered/dyn_performing", pattern = "txt")
+lf_a_t <- list.files("../random/art_teaching", pattern = "txt")
+lf_a_p <- list.files("../random/art_performing", pattern = "txt")
+lf_d_t <- list.files("../random/dyn_teaching", pattern = "txt")
+lf_d_p <- list.files("../random/dyn_performing", pattern = "txt")
 

### 2020-10-12 material/stimuli/R/filtering_random.R

@@ -5,28 +5,28 @@
 #  Documentation
 ####################################
 # Created: 06/10/2020
-# This script organises raw data and select performances which do not contain any pitch errors.
+# This script organises raw data and randomly select performances which do not contain any pitch errors.
 # GitHub repo (private): https://github.com/atsukotominaga/perception-v1.0/tree/master/material/stimuli
 
 # create folders if not exists
-if (!file.exists("filtered/")){
-  dir.create("filtered")
+if (!file.exists("random/")){
+  dir.create("random")
 }
 
-if (!file.exists("filtered/art_teaching")){
-  dir.create("filtered/art_teaching")
+if (!file.exists("random/art_teaching")){
+  dir.create("random/art_teaching")
 }
 
-if (!file.exists("filtered/dyn_teaching")){
-  dir.create("filtered/dyn_teaching")
+if (!file.exists("random/dyn_teaching")){
+  dir.create("random/dyn_teaching")
 }
 
-if (!file.exists("filtered/art_performing")){
-  dir.create("filtered/art_performing")
+if (!file.exists("random/art_performing")){
+  dir.create("random/art_performing")
 }
 
-if (!file.exists("filtered/dyn_performing")){
-  dir.create("filtered/dyn_performing")
+if (!file.exists("random/dyn_performing")){
+  dir.create("random/dyn_performing")
 }
 
 # read functions

### 2020-10-12 material/stimuli/R/filtering_random.R
filtered >> random
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -111,13 +111,13 @@ for (i in 1:128){ # 32 stimuli for each category
   current$TimeStamp <- current$TimeStamp - firstTimestamp # start with time 0
   
   if (cond == "teaching" & skill == "articulation"){
-    filename = paste("./filtered/art_teaching/", subject, block, trial, ".txt", sep = "")
+    filename = paste("./random/art_teaching/", subject, block, trial, ".txt", sep = "")
   } else if (cond == "teaching" & skill == "dynamics"){
-    filename = paste("./filtered/dyn_teaching/", subject, block, trial, ".txt", sep = "")
+    filename = paste("./random/dyn_teaching/", subject, block, trial, ".txt", sep = "")
   } else if (cond == "performing" & skill == "articulation"){
-    filename = paste("./filtered/art_performing/", subject, block, trial, ".txt", sep = "")
+    filename = paste("./random/art_performing/", subject, block, trial, ".txt", sep = "")
   } else if (cond == "performing" & skill == "dynamics"){
-    filename = paste("./filtered/dyn_performing/", subject, block, trial, ".txt", sep = "")
+    filename = paste("./random/dyn_performing/", subject, block, trial, ".txt", sep = "")
   }
   fwrite(current, file = filename)
 }

### 2020-10-12 material/stimuli/R/filtering_3sd.R
add filtering with ioi within 3sd
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -1,0 +1,145 @@
+#!/usr/local/bin/R
+#rm(list=ls(all=T)) # clear all
+
+####################################
+#  Documentation
+####################################
+# Created: 06/10/2020
+# This script organises raw data and randomly select performances which do not contain any pitch errors.
+# GitHub repo (private): https://github.com/atsukotominaga/perception-v1.0/tree/master/material/stimuli
+
+# create folders if not exists
+if (!file.exists("3sd/")){
+  dir.create("3sd")
+}
+
+if (!file.exists("3sd/art_teaching")){
+  dir.create("3sd/art_teaching")
+}
+
+if (!file.exists("3sd/dyn_teaching")){
+  dir.create("3sd/dyn_teaching")
+}
+
+if (!file.exists("3sd/art_performing")){
+  dir.create("3sd/art_performing")
+}
+
+if (!file.exists("3sd/dyn_performing")){
+  dir.create("3sd/dyn_performing")
+}
+
+# read functions
+source("./function.R")
+
+# read a text file for ideal performance
+dt_ideal <- read.table("./ideal.txt")
+colnames(dt_ideal) <- "Pitch"
+dt_ideal$RowNr <- 1:nrow(dt_ideal)
+setcolorder(dt_ideal, c(2, 1))
+
+# create a list of data file names
+lf <- list.files("./raw_data", pattern = "txt")
+
+# create raw_data - merge all data files into one
+raw_data <- data.table()
+for (i in 1:length(lf)){
+  data_i <- fread(file.path("./raw_data", lf[i]), header = F, sep = " ", dec = ".")
+  raw_data <- rbind(raw_data, data_i)
+}
+
+# add column namesls
+colnames(raw_data) <- c("NoteNr", "TimeStamp", "Pitch", "Velocity", "Key_OnOff", "Device", "SubNr", "BlockNr", "TrialNr", "Skill", "Condition", "Image")
+
+# clean raw_data
+raw_data$NoteNr <- as.numeric(gsub(",", "", raw_data$NoteNr))
+raw_data$Image <- gsub(";", "", raw_data$Image)
+
+# sort by SubNr, BlockNr, TrialNr
+raw_data <- raw_data[order(raw_data$SubNr, raw_data$BlockNr, raw_data$TrialNr),]
+
+# raw_data without metronome
+dt_all <- raw_data[Pitch != 31 & Pitch != 34]
+
+# onset and offset
[…]

### 2020-10-12 material/stimuli/R/analysis/random.Rmd
filtered >> random
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 for (i in 1:length(lf_a_t)){
-  data_i <- fread(file.path("../filtered/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
+  data_i <- fread(file.path("../random/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
   data_i$Instance <- i
@@
 for (i in 1:length(lf_a_p)){
-  data_i <- fread(file.path("../filtered/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
+  data_i <- fread(file.path("../random/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
   data_i$Instance <- i
@@
 for (i in 1:length(lf_d_t)){
-  data_i <- fread(file.path("../filtered/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
+  data_i <- fread(file.path("../random/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
   data_i$Instance <- i
@@
 for (i in 1:length(lf_d_p)){
-  data_i <- fread(file.path("../filtered/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
+  data_i <- fread(file.path("../random/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
   data_i$Instance <- i

### 2020-10-12 material/stimuli/R/analysis/3sd.Rmd
analysis for 3sd data
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2020-10-12 material/stimuli/R/analysis/random.Rmd
@@
 ---
-title: 'Music Perception 2020: Stimuli profiles (random)'
+title: 'Music Perception 2020: Stimuli profiles (3sd)'
 output:
@@
 
-I chose stimuli randomly.  
+I chose stimuli with the IOIs within 3SD randomly.  
 Note: SubNr16 was excluded because of a deviated tempo (see analysis for [teaching-v1.0](https://github.com/atsukotominaga/teaching-v1.0))
@@
 # create a list of data file names
-lf_a_t <- list.files("../random/art_teaching", pattern = "txt")
-lf_a_p <- list.files("../random/art_performing", pattern = "txt")
-lf_d_t <- list.files("../random/dyn_teaching", pattern = "txt")
-lf_d_p <- list.files("../random/dyn_performing", pattern = "txt")
+lf_a_t <- list.files("../3sd/art_teaching", pattern = "txt")
+lf_a_p <- list.files("../3sd/art_performing", pattern = "txt")
+lf_d_t <- list.files("../3sd/dyn_teaching", pattern = "txt")
+lf_d_p <- list.files("../3sd/dyn_performing", pattern = "txt")
 
@@
 for (i in 1:length(lf_a_t)){
-  data_i <- fread(file.path("../random/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
+  data_i <- fread(file.path("../3sd/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
   data_i$Instance <- i
@@
 for (i in 1:length(lf_a_p)){
-  data_i <- fread(file.path("../random/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
+  data_i <- fread(file.path("../3sd/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
   data_i$Instance <- i
@@
 for (i in 1:length(lf_d_t)){
-  data_i <- fread(file.path("../random/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
+  data_i <- fread(file.path("../3sd/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
   data_i$Instance <- i
@@
 for (i in 1:length(lf_d_p)){
-  data_i <- fread(file.path("../random/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
+  data_i <- fread(file.path("../3sd/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
   data_i$Instance <- i

### 2020-10-13 material/stimuli/R/filtering_3sd.R
add comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -4,8 +4,8 @@
 ####################################
 #  Documentation
 ####################################
-# Created: 06/10/2020
-# This script organises raw data and randomly select performances which do not contain any pitch errors.
+# Created: 12/10/2020
+# This script organises raw data and randomly select performances which do not contain any pitch errors (IOIs within 3SD).
 # GitHub repo (private): https://github.com/atsukotominaga/perception-v1.0/tree/master/material/stimuli
 
 # create folders if not exists

### 2020-10-13 material/stimuli/R/analysis/3sd.Rmd
add x ticks
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
   geom_hline(yintercept = 188, linetype = "dashed") +
-  facet_grid(Skill ~ .) +
+  facet_grid(Skill ~ .) + scale_x_continuous(breaks = seq(1:32)) +
   labs(y = "IOI (ms)", subtitle = "IOI: Each instance (All)")
@@
 
+## Each instance
+```{r kot_stats_ind, echo = FALSE}
+kot
+```
+
+## Averaged
+```{r kot_stats_all, echo = FALSE}
+kot_all
+```
+
 ## Plots
@@
                 width = .2, position = position_dodge(.9)) +
-  facet_grid(Subcomponent ~ .) +
+  facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:32)) +
   labs(y = "KOT (ms)", subtitle = "KOT: Each instance (Articulation)")
@@
 p_kot_all
-```
-
-## Each instance
-```{r kot_stats_ind, echo = FALSE}
-kot
-```
-
-## Averaged
-```{r kot_stats_all, echo = FALSE}
-kot_all
 ```
@@
                 width = .2, position = position_dodge(.9)) +
-  facet_grid(Subcomponent ~ .) +
+  facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:32)) +
   labs(y = "Key Velocity", subtitle = "KV: Each instance (Dynamics)")
@@
                 width = .2, position = position_dodge(.9)) +
-  facet_grid(Subcomponent ~ .) +
+  facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:32)) +
   labs(y = "KV difference", subtitle = "KV-Diff: Each instance (Dynamics)")

### 2020-10-13 script/psychopy/experiment.py
ignore return keys (accept) without selection
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -18,7 +18,7 @@ def next():
                 break
             elif resp == "escape": # force quit
                 for item in resultsList: # save data so far
-                    dataFile.write('{0}, {1}, {2}, {3}, {4}, {5}, {6}, {7}, {8}\n'.format(*item))
+                    dataFile.write('{0}, {1}, {2}, {3}, {4}, {5}, {6}, {7}, {8}, {9}\n'.format(*item))
                 dataFile.close()
                 core.quit()
     return
@@ -41,15 +41,19 @@ def trial(expMode, imageFile, midFile, resultsList):
         playing = False
     
     # get response (yes/no answer)
-    ratingScale = visual.RatingScale(win, choices = ["Yes", "No"], markerStart = 0.5, markerColor = "Orange", textFont = "Avenir", size = 1.5, noMouse = True, acceptKeys = "return", showAccept = False, skipKeys = None)
-    question = visual.TextStim(win, pos=[0, 0], font = "Avenir", height = 60, wrapWidth = 1400,
-    text = "Teaching?")
+    ratingScale = visual.RatingScale(win, pos = (0.0, -0.4), choices = ["Yes", "No"], markerStart = 0.5, markerColor = "Orange", textFont = "Avenir", size = 1.5, noMouse = True, acceptKeys = "return", showAccept = True, acceptPreText =  "Select your response", acceptSize = 1.8, skipKeys = None)
+    question = visual.TextStim(win, pos=[0, 200], font = "Avenir", height = 60, wrapWidth = 1400,
+    text = "Teaching\nYes: <Left>    No: <Right>?\n\nPress <Return> to confirm")
     trialClock = core.Clock()
     while ratingScale.noResponse:
         question.draw()
         ratingScale.draw()
         win.flip()
-    
+        if len(ratingScale.getHistory()) == 2: # if accidentally hit return, ignore
+            ratingScale.noResponse = True
+        elif len(ratingScale.getHistory()) > 2 and ratingScale.getHistory()[-1] == ratingScale.getHistory()[-2]: # if there is no response (i.e., keep on pressing return, ignore)
+            ratingScale.noResponse = True
+
     # store responses1
     resultsList.append([
         expMode, # practice/experiment
@@ -58,6 +62,7 @@ def trial(expMode, imageFile, midFile, resultsList):
         ratingScale.getRating(), # final answer
[…]

### 2020-10-13 material/stimuli/python/mid_export.py
change folder name
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -11,10 +11,10 @@ if not os.path.exists("mid"):
     os.mkdir("mid")
 
 #%% folder names
-folder_a_t = "../R/filtered/art_teaching/"
-folder_d_t = "../R/filtered/dyn_teaching/"
-folder_a_p = "../R/filtered/art_performing/"
-folder_d_p = "../R/filtered/dyn_performing/"
+folder_a_t = "../R/3sd/art_teaching/"
+folder_d_t = "../R/3sd/dyn_teaching/"
+folder_a_p = "../R/3sd/art_performing/"
+folder_d_p = "../R/3sd/dyn_performing/"
 folders = [folder_a_t, folder_d_t, folder_a_p, folder_d_p]
 
 #%% mid export
@@ -29,13 +29,13 @@ for folder in folders:
             mid.tracks.append(track)
             track.append(mido.Message('program_change', program=0, time=0)) # program 0 = Acoustic Grand Piano
             # name for mid file
-            if folder == "../R/filtered/art_teaching/":
+            if folder == "../R/3sd/art_teaching/":
                 midname = "./mid/a_t_" + str(instance+1) + ".mid"
-            elif folder == "../R/filtered/dyn_teaching/":
+            elif folder == "../R/3sd/dyn_teaching/":
                 midname = "./mid/d_t_" + str(instance+1) + ".mid"
-            elif folder == "../R/filtered/art_performing/":
+            elif folder == "../R/3sd/art_performing/":
                 midname = "./mid/a_p_" + str(instance+1) + ".mid"
-            elif folder == "../R/filtered/dyn_performing/":
+            elif folder == "../R/3sd/dyn_performing/":
                 midname = "./mid/d_p_" + str(instance+1) + ".mid"
             # read current track data (txt file)   
             current = csv.reader(csvfile, delimiter = ",")

### 2020-10-13 script/psychopy/experiment.py
adjust rating layout
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -41,9 +41,9 @@ def trial(expMode, imageFile, midFile, resultsList):
         playing = False
     
     # get response (yes/no answer)
-    ratingScale = visual.RatingScale(win, pos = (0.0, -0.4), choices = ["Yes", "No"], markerStart = 0.5, markerColor = "Orange", textFont = "Avenir", size = 1.5, noMouse = True, acceptKeys = "return", showAccept = True, acceptPreText =  "Select your response", acceptSize = 1.8, skipKeys = None)
-    question = visual.TextStim(win, pos=[0, 200], font = "Avenir", height = 60, wrapWidth = 1400,
-    text = "Teaching\nYes: <Left>    No: <Right>?\n\nPress <Return> to confirm")
+    ratingScale = visual.RatingScale(win, pos = (0, -200), choices = ["Yes", "No"], markerStart = 0.5, markerColor = "Orange", textFont = "Avenir", size = 1.5, noMouse = True, acceptKeys = "return", showAccept = True, acceptPreText =  "Select your response", acceptSize = 1.8, skipKeys = None)
+    question = visual.TextStim(win, pos=[0, 0], font = "Avenir", height = 60, wrapWidth = 1400,
+    text = "Teaching?\nYes: <Left>    No: <Right>\n\nPress <Return> to confirm\n\n\n\n")
     trialClock = core.Clock()
     while ratingScale.noResponse:
         question.draw()
@@ -51,7 +51,7 @@ def trial(expMode, imageFile, midFile, resultsList):
         win.flip()
         if len(ratingScale.getHistory()) == 2: # if accidentally hit return, ignore
             ratingScale.noResponse = True
-        elif len(ratingScale.getHistory()) > 2 and ratingScale.getHistory()[-1] == ratingScale.getHistory()[-2]: # if there is no response (i.e., keep on pressing return, ignore)
+        elif len(ratingScale.getHistory()) > 2 and ratingScale.getHistory()[-1] == ratingScale.getHistory()[-2]: # if there is no response, ignore (i.e., keep on pressing return)
             ratingScale.noResponse = True
 
     # store responses1
@@ -207,7 +207,7 @@ while practice:
                 practice = True
 
 inst8 = visual.TextStim(win, pos = [0, 0], font = "Avenir", height = 60, wrapWidth = 1400, alignText = "left",
[…]

### 2020-10-13 material/stimuli/R/filtering_3sd.R
correct labelling mistakes... and generate new stimuli
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -58,8 +58,22 @@ raw_data$Image <- gsub(";", "", raw_data$Image)
 # sort by SubNr, BlockNr, TrialNr
 raw_data <- raw_data[order(raw_data$SubNr, raw_data$BlockNr, raw_data$TrialNr),]
 
+# correct labelling (due to a labelling error of the original study)
+# articulation
+dt_a <- raw_data[grepl("stim_a", Image)]
+# correct wrong labelling
+dt_a$Skill <- "articulation"
+
+# dynamics
+dt_d <- raw_data[grepl("stim_d", Image)]
+# correct wrong labelling
+dt_d$Skill <- "dynamics"
+
+# bind data frames for articulation and dynamics
+dt_all <- rbind(dt_a, dt_d)
+
 # raw_data without metronome
-dt_all <- raw_data[Pitch != 31 & Pitch != 34]
+dt_all <- dt_all[Pitch != 31 & Pitch != 34]
 
 # onset and offset
 dt_onset <- dt_all[Key_OnOff == 1]

### 2020-10-14 script/psychopy/experiment.py
edit instructionss and implement practice trials
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -41,7 +41,7 @@ def trial(expMode, imageFile, midFile, resultsList):
         playing = False
     
     # get response (yes/no answer)
-    ratingScale = visual.RatingScale(win, pos = (0, -200), choices = ["Yes", "No"], markerStart = 0.5, markerColor = "Orange", textFont = "Avenir", size = 1.5, noMouse = True, acceptKeys = "return", showAccept = True, acceptPreText =  "Select your response", acceptSize = 1.8, skipKeys = None)
+    ratingScale = visual.RatingScale(win, pos = (0, -200), choices = ["Yes", "No"], markerStart = 0.5, markerColor = "Orange", textFont = "Avenir", size = 1.5, noMouse = True, acceptKeys = "return", showAccept = False, acceptPreText =  "Select your response", acceptSize = 1.8, skipKeys = None)
     question = visual.TextStim(win, pos=[0, 0], font = "Avenir", height = 60, wrapWidth = 1400,
     text = "Teaching?\nYes: <Left>    No: <Right>\n\nPress <Return> to confirm\n\n\n\n")
     trialClock = core.Clock()
@@ -135,7 +135,7 @@ globalClock = core.Clock()
 ### Instruction ###
 # display instructions and wait
 inst1 = visual.TextStim(win, pos = [0, 0], font = "Avenir", height = 60, wrapWidth = 1400, alignText = "left",
-    text = "Thank you very much for participating in our study!\n\nIn this experiment, you are going to listen to a number of piano performances and will be asked to judge whether each performance was produced in order to teach a musical technique or not.\n\nPress <Space> to continue")
+    text = "Thank you very much for participating in our study!\n\nIn this experiment, you are going to listen to a number of piano performances and be asked to judge whether each performance was produced in order to teach a musical technique or not.\n\nPress <Space> to continue")
 inst1.draw()
 win.flip()
 next() # proceed/force quit
@@ -150,7 +150,7 @@ win.flip()
 next() # proceed/force quit
 
 ## instruction 3
-inst3 = visual.TextStim(win, pos = [-50, 0], font = "Avenir", height = 60, wrapWidth = 1400, text = text_3)
+inst3 = visual.TextStim(win, pos = [0, 0], font = "Avenir", height = 60, wrapWidth = 1400, text = text_3)
 imageSheet.draw()
 inst3.draw()
 win.flip()
@@ -158,14 +158,14 @@ next() # proceed/force quit
 
 ## instruction 4
[…]

### 2020-10-14 script/psychopy/experiment.py
different stimuli for practice trials
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -107,12 +107,14 @@ if expInfo["Expression"] == "Articulation":
     # sheet music
     imageFile = "./image/stim_a.png"
     text_3 = "Musical Technique: [ Articulation ]\nthe smoothness of sound\nslurs: legato, dots: staccato\n\n\n\n\n\n\nPress <Space> to continue"
+    pFileList = [f for f in os.listdir("practice/") if f.startswith("a_")]
     eFileList = [f for f in os.listdir("mid/") if f.startswith("a_")]
     
 elif expInfo["Expression"] == "Dynamics":
     # sheet music
     imageFile = "./image/stim_d.png"
-    text_3 = "Musical Technique: [ Dynamics ]\nthe smoothness of sound\nf: forte, p: piano\n\n\n\n\n\n\nPress <Space> to continue"
+    text_3 = "Musical Technique: [ Dynamics ]\nthe loudness of sound\nf: forte, p: piano\n\n\n\n\n\n\nPress <Space> to continue"
+    pFileList = [f for f in os.listdir("practice/") if f.startswith("d_")]
     eFileList = [f for f in os.listdir("mid/") if f.startswith("d_")]
 
 # create csv to save data

### 2020-10-14 material/stimuli/R/filtering_3sd.R
delete stimuli
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -1,159 +1,0 @@
-#!/usr/local/bin/R
-#rm(list=ls(all=T)) # clear all
-
-####################################
-#  Documentation
-####################################
-# Created: 12/10/2020
-# This script organises raw data and randomly select performances which do not contain any pitch errors (IOIs within 3SD).
-# GitHub repo (private): https://github.com/atsukotominaga/perception-v1.0/tree/master/material/stimuli
-
-# create folders if not exists
-if (!file.exists("3sd/")){
-  dir.create("3sd")
-}
-
-if (!file.exists("3sd/art_teaching")){
-  dir.create("3sd/art_teaching")
-}
-
-if (!file.exists("3sd/dyn_teaching")){
-  dir.create("3sd/dyn_teaching")
-}
-
-if (!file.exists("3sd/art_performing")){
-  dir.create("3sd/art_performing")
-}
-
-if (!file.exists("3sd/dyn_performing")){
-  dir.create("3sd/dyn_performing")
-}
-
-# read functions
-source("./function.R")
-
-# read a text file for ideal performance
-dt_ideal <- read.table("./ideal.txt")
-colnames(dt_ideal) <- "Pitch"
-dt_ideal$RowNr <- 1:nrow(dt_ideal)
-setcolorder(dt_ideal, c(2, 1))
-
-# create a list of data file names
-lf <- list.files("./raw_data", pattern = "txt")
-
-# create raw_data - merge all data files into one
-raw_data <- data.table()
-for (i in 1:length(lf)){
-  data_i <- fread(file.path("./raw_data", lf[i]), header = F, sep = " ", dec = ".")
-  raw_data <- rbind(raw_data, data_i)
-}
-
-# add column namesls
-colnames(raw_data) <- c("NoteNr", "TimeStamp", "Pitch", "Velocity", "Key_OnOff", "Device", "SubNr", "BlockNr", "TrialNr", "Skill", "Condition", "Image")
-
-# clean raw_data
-raw_data$NoteNr <- as.numeric(gsub(",", "", raw_data$NoteNr))
-raw_data$Image <- gsub(";", "", raw_data$Image)
-
-# sort by SubNr, BlockNr, TrialNr
-raw_data <- raw_data[order(raw_data$SubNr, raw_data$BlockNr, raw_data$TrialNr),]
-
-# correct labelling (due to a labelling error of the original study)
-# articulation
[…]

### 2020-10-14 script/psychopy/experiment.py
adjust ratingScale layout / correct practice stimuli path
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -41,7 +41,7 @@ def trial(expMode, imageFile, midFile, resultsList):
         playing = False
     
     # get response (yes/no answer)
-    ratingScale = visual.RatingScale(win, pos = (0, -200), choices = ["Yes", "No"], markerStart = 0.5, markerColor = "Orange", textFont = "Avenir", size = 1.5, noMouse = True, acceptKeys = "return", showAccept = False, acceptPreText =  "Select your response", acceptSize = 1.8, skipKeys = None)
+    ratingScale = visual.RatingScale(win, pos = (0, -300), choices = ["Yes", "No"], lineColor = (-.7, -.7, -.7), tickHeight = 0.0, markerStart = 0.5, markerColor = "Orange", textFont = "Avenir", size = 1.5, noMouse = True, acceptKeys = "return", showAccept = False, acceptPreText =  "Select your response", acceptSize = 1.8, skipKeys = None)
     question = visual.TextStim(win, pos=[0, 0], font = "Avenir", height = 60, wrapWidth = 1400,
     text = "Teaching?\nYes: <Left>    No: <Right>\n\nPress <Return> to confirm\n\n\n\n")
     trialClock = core.Clock()
@@ -181,7 +181,6 @@ next() # proceed/force quit
 
 ### Practice ###
 expMode = "practice"
-pFileList = os.listdir("practice")
 random.shuffle(pFileList) # stimuli randomisation
 practice = True
 while practice:

### 2020-10-14 material/stimuli/python/mid_export.py
mid export for practice stimuli
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -9,12 +9,14 @@ import os, csv, mido
 #%% create mid folder if not existed
 if not os.path.exists("mid"):
     os.mkdir("mid")
+if not os.path.exists("practice"):
+    os.mkdir("practice")
 
 #%% folder names
-folder_a_t = "../R/3sd/art_teaching/"
-folder_d_t = "../R/3sd/dyn_teaching/"
-folder_a_p = "../R/3sd/art_performing/"
-folder_d_p = "../R/3sd/dyn_performing/"
+folder_a_t = "../R/2sd/art_teaching/"
+folder_d_t = "../R/2sd/dyn_teaching/"
+folder_a_p = "../R/2sd/art_performing/"
+folder_d_p = "../R/2sd/dyn_performing/"
 folders = [folder_a_t, folder_d_t, folder_a_p, folder_d_p]
 
 #%% mid export
@@ -29,13 +31,13 @@ for folder in folders:
             mid.tracks.append(track)
             track.append(mido.Message('program_change', program=0, time=0)) # program 0 = Acoustic Grand Piano
             # name for mid file
-            if folder == "../R/3sd/art_teaching/":
+            if folder == "../R/2sd/art_teaching/":
                 midname = "./mid/a_t_" + str(instance+1) + ".mid"
-            elif folder == "../R/3sd/dyn_teaching/":
+            elif folder == "../R/2sd/dyn_teaching/":
                 midname = "./mid/d_t_" + str(instance+1) + ".mid"
-            elif folder == "../R/3sd/art_performing/":
+            elif folder == "../R/2sd/art_performing/":
                 midname = "./mid/a_p_" + str(instance+1) + ".mid"
-            elif folder == "../R/3sd/dyn_performing/":
+            elif folder == "../R/2sd/dyn_performing/":
                 midname = "./mid/d_p_" + str(instance+1) + ".mid"
             # read current track data (txt file)   
             current = csv.reader(csvfile, delimiter = ",")
@@ -58,5 +60,54 @@ for folder in folders:
                     track.append(mido.Message('note_off', note=currentPitch, velocity=currentVelocity, time=currentTime-previousTime))
             mid.save(midname) # save track
 
-print("Done :D")
-# %%
+print("Experimental stimuli - Done :D")
+
+#%%
+folder_a_t_p = "../R/2sd/practice/art_teaching/"
[…]

### 2020-10-14 material/stimuli/R/filtering_2sd.R
.gitignore fix
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -1,189 +1,0 @@
-#!/usr/local/bin/R
-#rm(list=ls(all=T)) # clear all
-
-####################################
-#  Documentation
-####################################
-# Created: 12/10/2020
-# This script organises raw data and randomly select performances which do not contain any pitch errors (IOIs within 3SD).
-# GitHub repo (private): https://github.com/atsukotominaga/perception-v1.0/tree/master/material/stimuli
-
-# create folders if not exists
-if (!file.exists("2sd/")){
-  dir.create("2sd")
-  dir.create("2sd/practice/")
-}
-
-if (!file.exists("2sd/art_teaching")){
-  dir.create("2sd/art_teaching")
-  dir.create("2sd/practice/art_teaching")
-}
-
-if (!file.exists("2sd/dyn_teaching")){
-  dir.create("2sd/dyn_teaching")
-  dir.create("2sd/practice/dyn_teaching")
-}
-
-if (!file.exists("2sd/art_performing")){
-  dir.create("2sd/art_performing")
-  dir.create("2sd/practice/art_performing")
-}
-
-if (!file.exists("2sd/dyn_performing")){
-  dir.create("2sd/dyn_performing")
-  dir.create("2sd/practice/dyn_performing")
-}
-
-# read functions
-source("./function.R")
-
-# read a text file for ideal performance
-dt_ideal <- read.table("./ideal.txt")
-colnames(dt_ideal) <- "Pitch"
-dt_ideal$RowNr <- 1:nrow(dt_ideal)
-setcolorder(dt_ideal, c(2, 1))
-
-# create a list of data file names
-lf <- list.files("./raw_data", pattern = "txt")
-
-# create raw_data - merge all data files into one
-raw_data <- data.table()
-for (i in 1:length(lf)){
-  data_i <- fread(file.path("./raw_data", lf[i]), header = F, sep = " ", dec = ".")
-  raw_data <- rbind(raw_data, data_i)
-}
-
-# add column namesls
-colnames(raw_data) <- c("NoteNr", "TimeStamp", "Pitch", "Velocity", "Key_OnOff", "Device", "SubNr", "BlockNr", "TrialNr", "Skill", "Condition", "Image")
-
-# clean raw_data
-raw_data$NoteNr <- as.numeric(gsub(",", "", raw_data$NoteNr))
-raw_data$Image <- gsub(";", "", raw_data$Image)
-
-# sort by SubNr, BlockNr, TrialNr
[…]

### 2020-10-14 material/stimuli/R/function.R

@@ -1,39 +1,0 @@
-# install and load required packages
-if (!require("data.table")) {install.packages("data.table"); require("data.table")}
-if (!require("tibble")) {install.packages("tibble"); require("tibble")}
-if (!require("editData")) {install.packages("editData"); require("editData")}
-if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
-
-### check whether a trial contains pitch errors
-# data: data of the current trial
-# ideal: dt_ideal
-checker <- function(data, ideal){
-  dt_errors <- data.table() # return data of erroneous trials - SubNr/BlockNr/TrialNr/Reason
-  for (subject in unique(data$SubNr)){
-    for(block in c(1:4)){
-      for (trial in c(1:8)){
-        current <- data[SubNr == subject & BlockNr == block & TrialNr == trial]
-        if (nrow(current) != 0){ # current data not empty
-          if (nrow(current) != nrow(ideal)){ # extra/missing note
-            if (nrow(current) > nrow(ideal)){
-              dt_errors <- rbind(dt_errors, data.table(subject, block, trial, "Extra Notes")) 
-            } else if (nrow(current) < nrow(ideal)){
-              dt_errors <- rbind(dt_errors, data.table(subject, block, trial, "Missing Notes")) 
-            }
-          } else if (nrow(current) == nrow(ideal)){ # substituted note
-            for (note in 1:nrow(ideal)){
-              if (current$Pitch[note] != ideal$Pitch[note]){
-                dt_errors <- rbind(dt_errors, data.table(subject, block, trial, paste("Substituted Notes - RowNr ", as.character(note), sep = "")))
-                break
-              }
-            }
-          }
-        } else if (nrow(current) == 0){ # current data empty
-          dt_errors <- rbind(dt_errors, data.table(subject, block, trial, paste("Missing Trial")))
-        }
-      }
-    }
-  }
-  colnames(dt_errors) <- c("SubNr", "BlockNr", "TrialNr", "Reason")
-  return(dt_errors)
-}

### 2020-10-14 material/stimuli/python/mid_export.py

@@ -1,113 +1,0 @@
-#!/usr/local/bin/python
-####################
-# Created: 20/04/2020
-# This script converts txt files to mid files.
-
-#%% import packages
-import os, csv, mido
-
-#%% create mid folder if not existed
-if not os.path.exists("mid"):
-    os.mkdir("mid")
-if not os.path.exists("practice"):
-    os.mkdir("practice")
-
-#%% folder names
-folder_a_t = "../R/2sd/art_teaching/"
-folder_d_t = "../R/2sd/dyn_teaching/"
-folder_a_p = "../R/2sd/art_performing/"
-folder_d_p = "../R/2sd/dyn_performing/"
-folders = [folder_a_t, folder_d_t, folder_a_p, folder_d_p]
-
-#%% mid export
-for folder in folders:
-    files = [f for f in os.listdir(folder) if os.path.isfile(os.path.join(folder, f))]
-    for instance in range(0, len(files)):
-        filename = folder + files[instance]
-        with open(filename) as csvfile:
-            # create mid file
-            mid = mido.MidiFile()
-            track = mido.MidiTrack()
-            mid.tracks.append(track)
-            track.append(mido.Message('program_change', program=0, time=0)) # program 0 = Acoustic Grand Piano
-            # name for mid file
-            if folder == "../R/2sd/art_teaching/":
-                midname = "./mid/a_t_" + str(instance+1) + ".mid"
-            elif folder == "../R/2sd/dyn_teaching/":
-                midname = "./mid/d_t_" + str(instance+1) + ".mid"
-            elif folder == "../R/2sd/art_performing/":
-                midname = "./mid/a_p_" + str(instance+1) + ".mid"
-            elif folder == "../R/2sd/dyn_performing/":
-                midname = "./mid/d_p_" + str(instance+1) + ".mid"
-            # read current track data (txt file)   
-            current = csv.reader(csvfile, delimiter = ",")
-            next(current) # skip first row
-            counter = 0
-            for row in current:
-                if counter == 0:
-                    previousTime = 0
-                    counter += 1
-                else:
-                    previousTime = currentTime
-                currentTime = int(mido.second2tick(int(row[1])*0.001+3, 480, 500000))
-                currentPitch = int(row[2])
-                currentVelocity = int(row[3])
-                currentOnOff = int(row[4])
-                # assign midi values
-                if currentOnOff == 1:
[…]

### 2020-10-14 script/psychopy/experiment.py

@@ -1,239 +1,0 @@
-#!usr/bin/env python
-
-"""
-This is an experimental programme for Music Perception 2020
-"""
-
-# import libraries
-from psychopy import core, visual, gui, data, event
-import os, random, mido
-
-### function ###
-def next():
-    resp = None
-    while resp == None:
-        allKeys = event.getKeys(keyList = ["space", "escape"])
-        for resp in allKeys:
-            if resp == "space": # proceed
-                break
-            elif resp == "escape": # force quit
-                for item in resultsList: # save data so far
-                    dataFile.write('{0}, {1}, {2}, {3}, {4}, {5}, {6}, {7}, {8}, {9}\n'.format(*item))
-                dataFile.close()
-                core.quit()
-    return
-
-def trial(expMode, imageFile, midFile, resultsList):
-    # stimuli presentation
-    ## 1. sheet music
-    stimuli = visual.ImageStim(win, image = imageFile, size = [1500, 300])
-    stimuli.draw()
-
-    ## 2. midi play
-    playing = True
-    while playing:
-        win.flip() # sheet music
-        mid = mido.MidiFile(midFile)
-        for msg in mid.play():
-            port.send(msg)
-        event.clearEvents() # clear if any keypress
-        core.wait(1)
-        playing = False
-    
-    # get response (yes/no answer)
-    ratingScale = visual.RatingScale(win, pos = (0, -300), choices = ["Yes", "No"], lineColor = (-.7, -.7, -.7), tickHeight = 0.0, markerStart = 0.5, markerColor = "Orange", textFont = "Avenir", size = 1.5, noMouse = True, acceptKeys = "return", showAccept = False, acceptPreText =  "Select your response", acceptSize = 1.8, skipKeys = None)
-    question = visual.TextStim(win, pos=[0, 0], font = "Avenir", height = 60, wrapWidth = 1400,
-    text = "Teaching?\nYes: <Left>    No: <Right>\n\nPress <Return> to confirm\n\n\n\n")
-    trialClock = core.Clock()
-    while ratingScale.noResponse:
-        question.draw()
-        ratingScale.draw()
-        win.flip()
-        if len(ratingScale.getHistory()) == 2: # if accidentally hit return, ignore
-            ratingScale.noResponse = True
[…]

### 2020-10-14 material/stimuli/R/filtering_2sd.R
.gitignore fix
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -1,0 +1,189 @@
+#!/usr/local/bin/R
+#rm(list=ls(all=T)) # clear all
+
+####################################
+#  Documentation
+####################################
+# Created: 12/10/2020
+# This script organises raw data and randomly select performances which do not contain any pitch errors (IOIs within 3SD).
+# GitHub repo (private): https://github.com/atsukotominaga/perception-v1.0/tree/master/material/stimuli
+
+# create folders if not exists
+if (!file.exists("2sd/")){
+  dir.create("2sd")
+  dir.create("2sd/practice/")
+}
+
+if (!file.exists("2sd/art_teaching")){
+  dir.create("2sd/art_teaching")
+  dir.create("2sd/practice/art_teaching")
+}
+
+if (!file.exists("2sd/dyn_teaching")){
+  dir.create("2sd/dyn_teaching")
+  dir.create("2sd/practice/dyn_teaching")
+}
+
+if (!file.exists("2sd/art_performing")){
+  dir.create("2sd/art_performing")
+  dir.create("2sd/practice/art_performing")
+}
+
+if (!file.exists("2sd/dyn_performing")){
+  dir.create("2sd/dyn_performing")
+  dir.create("2sd/practice/dyn_performing")
+}
+
+# read functions
+source("./function.R")
+
+# read a text file for ideal performance
+dt_ideal <- read.table("./ideal.txt")
+colnames(dt_ideal) <- "Pitch"
+dt_ideal$RowNr <- 1:nrow(dt_ideal)
+setcolorder(dt_ideal, c(2, 1))
+
+# create a list of data file names
+lf <- list.files("./raw_data", pattern = "txt")
+
+# create raw_data - merge all data files into one
+raw_data <- data.table()
+for (i in 1:length(lf)){
+  data_i <- fread(file.path("./raw_data", lf[i]), header = F, sep = " ", dec = ".")
+  raw_data <- rbind(raw_data, data_i)
+}
+
+# add column namesls
+colnames(raw_data) <- c("NoteNr", "TimeStamp", "Pitch", "Velocity", "Key_OnOff", "Device", "SubNr", "BlockNr", "TrialNr", "Skill", "Condition", "Image")
+
+# clean raw_data
+raw_data$NoteNr <- as.numeric(gsub(",", "", raw_data$NoteNr))
+raw_data$Image <- gsub(";", "", raw_data$Image)
+
+# sort by SubNr, BlockNr, TrialNr
[…]

### 2020-10-14 material/stimuli/R/filtering_random.R

@@ -1,0 +1,139 @@
+#!/usr/local/bin/R
+#rm(list=ls(all=T)) # clear all
+
+####################################
+#  Documentation
+####################################
+# Created: 06/10/2020
+# This script organises raw data and randomly select performances which do not contain any pitch errors.
+# GitHub repo (private): https://github.com/atsukotominaga/perception-v1.0/tree/master/material/stimuli
+
+# create folders if not exists
+if (!file.exists("random/")){
+  dir.create("random")
+}
+
+if (!file.exists("random/art_teaching")){
+  dir.create("random/art_teaching")
+}
+
+if (!file.exists("random/dyn_teaching")){
+  dir.create("random/dyn_teaching")
+}
+
+if (!file.exists("random/art_performing")){
+  dir.create("random/art_performing")
+}
+
+if (!file.exists("random/dyn_performing")){
+  dir.create("random/dyn_performing")
+}
+
+# read functions
+source("./function.R")
+
+# read a text file for ideal performance
+dt_ideal <- read.table("./ideal.txt")
+colnames(dt_ideal) <- "Pitch"
+dt_ideal$RowNr <- 1:nrow(dt_ideal)
+setcolorder(dt_ideal, c(2, 1))
+
+# create a list of data file names
+lf <- list.files("./raw_data", pattern = "txt")
+
+# create raw_data - merge all data files into one
+raw_data <- data.table()
+for (i in 1:length(lf)){
+  data_i <- fread(file.path("./raw_data", lf[i]), header = F, sep = " ", dec = ".")
+  raw_data <- rbind(raw_data, data_i)
+}
+
+# add column namesls
+colnames(raw_data) <- c("NoteNr", "TimeStamp", "Pitch", "Velocity", "Key_OnOff", "Device", "SubNr", "BlockNr", "TrialNr", "Skill", "Condition", "Image")
+
+# clean raw_data
+raw_data$NoteNr <- as.numeric(gsub(",", "", raw_data$NoteNr))
+raw_data$Image <- gsub(";", "", raw_data$Image)
+
+# sort by SubNr, BlockNr, TrialNr
+raw_data <- raw_data[order(raw_data$SubNr, raw_data$BlockNr, raw_data$TrialNr),]
+
+# correct labelling (due to a labelling error of the original study)
+# articulation
+dt_a <- raw_data[grepl("stim_a", Image)]
+# correct wrong labelling
+dt_a$Skill <- "articulation"
+
[…]

### 2020-10-14 material/stimuli/R/function.R

@@ -1,0 +1,39 @@
+# install and load required packages
+if (!require("data.table")) {install.packages("data.table"); require("data.table")}
+if (!require("tibble")) {install.packages("tibble"); require("tibble")}
+if (!require("editData")) {install.packages("editData"); require("editData")}
+if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
+
+### check whether a trial contains pitch errors
+# data: data of the current trial
+# ideal: dt_ideal
+checker <- function(data, ideal){
+  dt_errors <- data.table() # return data of erroneous trials - SubNr/BlockNr/TrialNr/Reason
+  for (subject in unique(data$SubNr)){
+    for(block in c(1:4)){
+      for (trial in c(1:8)){
+        current <- data[SubNr == subject & BlockNr == block & TrialNr == trial]
+        if (nrow(current) != 0){ # current data not empty
+          if (nrow(current) != nrow(ideal)){ # extra/missing note
+            if (nrow(current) > nrow(ideal)){
+              dt_errors <- rbind(dt_errors, data.table(subject, block, trial, "Extra Notes")) 
+            } else if (nrow(current) < nrow(ideal)){
+              dt_errors <- rbind(dt_errors, data.table(subject, block, trial, "Missing Notes")) 
+            }
+          } else if (nrow(current) == nrow(ideal)){ # substituted note
+            for (note in 1:nrow(ideal)){
+              if (current$Pitch[note] != ideal$Pitch[note]){
+                dt_errors <- rbind(dt_errors, data.table(subject, block, trial, paste("Substituted Notes - RowNr ", as.character(note), sep = "")))
+                break
+              }
+            }
+          }
+        } else if (nrow(current) == 0){ # current data empty
+          dt_errors <- rbind(dt_errors, data.table(subject, block, trial, paste("Missing Trial")))
+        }
+      }
+    }
+  }
+  colnames(dt_errors) <- c("SubNr", "BlockNr", "TrialNr", "Reason")
+  return(dt_errors)
+}

### 2020-10-14 material/stimuli/python/mid_export.py

@@ -1,0 +1,113 @@
+#!/usr/local/bin/python
+####################
+# Created: 20/04/2020
+# This script converts txt files to mid files.
+
+#%% import packages
+import os, csv, mido
+
+#%% create mid folder if not existed
+if not os.path.exists("mid"):
+    os.mkdir("mid")
+if not os.path.exists("practice"):
+    os.mkdir("practice")
+
+#%% folder names
+folder_a_t = "../R/2sd/art_teaching/"
+folder_d_t = "../R/2sd/dyn_teaching/"
+folder_a_p = "../R/2sd/art_performing/"
+folder_d_p = "../R/2sd/dyn_performing/"
+folders = [folder_a_t, folder_d_t, folder_a_p, folder_d_p]
+
+#%% mid export
+for folder in folders:
+    files = [f for f in os.listdir(folder) if os.path.isfile(os.path.join(folder, f))]
+    for instance in range(0, len(files)):
+        filename = folder + files[instance]
+        with open(filename) as csvfile:
+            # create mid file
+            mid = mido.MidiFile()
+            track = mido.MidiTrack()
+            mid.tracks.append(track)
+            track.append(mido.Message('program_change', program=0, time=0)) # program 0 = Acoustic Grand Piano
+            # name for mid file
+            if folder == "../R/2sd/art_teaching/":
+                midname = "./mid/a_t_" + str(instance+1) + ".mid"
+            elif folder == "../R/2sd/dyn_teaching/":
+                midname = "./mid/d_t_" + str(instance+1) + ".mid"
+            elif folder == "../R/2sd/art_performing/":
+                midname = "./mid/a_p_" + str(instance+1) + ".mid"
+            elif folder == "../R/2sd/dyn_performing/":
+                midname = "./mid/d_p_" + str(instance+1) + ".mid"
+            # read current track data (txt file)   
+            current = csv.reader(csvfile, delimiter = ",")
+            next(current) # skip first row
+            counter = 0
+            for row in current:
+                if counter == 0:
+                    previousTime = 0
+                    counter += 1
+                else:
+                    previousTime = currentTime
+                currentTime = int(mido.second2tick(int(row[1])*0.001+3, 480, 500000))
+                currentPitch = int(row[2])
+                currentVelocity = int(row[3])
+                currentOnOff = int(row[4])
+                # assign midi values
+                if currentOnOff == 1:
[…]

### 2020-10-14 script/psychopy/experiment.py

@@ -1,0 +1,239 @@
+#!usr/bin/env python
+
+"""
+This is an experimental programme for Music Perception 2020
+"""
+
+# import libraries
+from psychopy import core, visual, gui, data, event
+import os, random, mido
+
+### function ###
+def next():
+    resp = None
+    while resp == None:
+        allKeys = event.getKeys(keyList = ["space", "escape"])
+        for resp in allKeys:
+            if resp == "space": # proceed
+                break
+            elif resp == "escape": # force quit
+                for item in resultsList: # save data so far
+                    dataFile.write('{0}, {1}, {2}, {3}, {4}, {5}, {6}, {7}, {8}, {9}\n'.format(*item))
+                dataFile.close()
+                core.quit()
+    return
+
+def trial(expMode, imageFile, midFile, resultsList):
+    # stimuli presentation
+    ## 1. sheet music
+    stimuli = visual.ImageStim(win, image = imageFile, size = [1500, 300])
+    stimuli.draw()
+
+    ## 2. midi play
+    playing = True
+    while playing:
+        win.flip() # sheet music
+        mid = mido.MidiFile(midFile)
+        for msg in mid.play():
+            port.send(msg)
+        event.clearEvents() # clear if any keypress
+        core.wait(1)
+        playing = False
+    
+    # get response (yes/no answer)
+    ratingScale = visual.RatingScale(win, pos = (0, -300), choices = ["Yes", "No"], lineColor = (-.7, -.7, -.7), tickHeight = 0.0, markerStart = 0.5, markerColor = "Orange", textFont = "Avenir", size = 1.5, noMouse = True, acceptKeys = "return", showAccept = False, acceptPreText =  "Select your response", acceptSize = 1.8, skipKeys = None)
+    question = visual.TextStim(win, pos=[0, 0], font = "Avenir", height = 60, wrapWidth = 1400,
+    text = "Teaching?\nYes: <Left>    No: <Right>\n\nPress <Return> to confirm\n\n\n\n")
+    trialClock = core.Clock()
+    while ratingScale.noResponse:
+        question.draw()
+        ratingScale.draw()
+        win.flip()
+        if len(ratingScale.getHistory()) == 2: # if accidentally hit return, ignore
+            ratingScale.noResponse = True
[…]

### 2020-11-09 script/RNotebook/test.Rmd
short script for checking data format
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: "Checking data format"
author: "Atsuko Tominaga"
output: html_notebook
---

- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`

This notebook is to check whether data format of the current experiment is okay.

```{r packages, include = FALSE}
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
```

```{r read, include = FALSE}
# read files and combine them
data_ls <- list.files("data")
combined <- lapply(data_ls, function(f){
  fread(paste("data/", f, sep = ""), sep = ",")
})
data <- do.call(rbind.data.frame, combined)
summary(data[expMode == "experiment"])
```

## Summary Stats for my data
```{r summary, echo = FALSE}
# name conditions
data$condition <- "NA"
data$technique <- "NA"
data[grepl("_t_", midFile)]$condition <- "teaching"
data[grepl("_p_", midFile)]$condition <- "performing"
data[grepl("a_", midFile)]$technique <- "articulation"
data[grepl("d_", midFile)]$technique <- "dynamics"
# check correct or incorrect
data$correct <- 0
data[condition == "teaching" & rating == "Yes"]$correct <- 1
data[condition == "performing" & rating == "No"]$correct <- 1

# summary
sum_stats <- data[expMode == "experiment", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/24)*100), by = .(condition, technique, subjectNumber)]
sum_stats
```

## Plots
### 1. Teaching vs. Performing regardless of techniques
```{r plot1, echo = FALSE}
subset1 <- sum_stats[, .(N = .N, Sum = sum(Sum), SD_Sum = sd(Sum), Percent = sum(Sum)/(48*2)*100, SD_Percent = sd(Sum)/(48*2)*100), by = .(condition)]
subset1

plot1 <- ggplot(subset1, aes(x = condition, y = Percent, fill = condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Percent - SD_Percent, ymax = Percent + SD_Percent), width = .2, position = position_dodge(.9)) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  labs(y = "Correct responses (%)")
plot1
```

### 2. Teaching vs. Performing for each technique
```{r plot2, echo = FALSE}
subset2 <- sum_stats[, .(N = .N, Sum = sum(Sum), SD_Sum = sd(Sum), Percent = sum(Sum)/(24*2)*100, SD_Percent = sd(Sum)/(24*2)*100), by = .(condition, technique)]
subset2

plot2 <- ggplot(subset2, aes(x = technique, y = Percent, fill = condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Percent - SD_Percent, ymax = Percent + SD_Percent), width = .2, position = position_dodge(.9)) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  labs(y = "Correct responses (%)")
plot2
```

### 2021-01-11 material/expstimuli/selection/analysis(2sd).Rmd
organised files and updated readme
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2020-10-12 material/stimuli/R/analysis/3sd.Rmd
@@
 ---
-title: 'Music Perception 2020: Stimuli profiles (3sd)'
-output:
-  html_notebook: default
-editor_options: 
-  chunk_output_type: inline
+title: "Music Perception: Stimuli profiles (2sd)"
+output: html_notebook
 ---
@@
 
-I chose stimuli with the IOIs within 3SD randomly.  
-Note: SubNr16 was excluded because of a deviated tempo (see analysis for [teaching-v1.0](https://github.com/atsukotominaga/teaching-v1.0))
+I chose stimuli with the IOIs within 2sd randomly.
+
+Note: SubNr 8 was excluded due to an experimental error, SubNr 16 was excluded due to a deviated tempo (see analysis for [teaching-v1.0](https://github.com/atsukotominaga/teaching-v1.0))
 
 ```{r setup, include = FALSE}
-# packages
-# data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
-# plot
 if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
-
-# ggplots
-theme_set(theme_classic())
-theme_update(text = element_text(size = 20, family = "Helvetica Neue LT Std 57 Condensed"), legend.position = "bottom")
 ```
@@
 # create a list of data file names
-lf_a_t <- list.files("../3sd/art_teaching", pattern = "txt")
-lf_a_p <- list.files("../3sd/art_performing", pattern = "txt")
-lf_d_t <- list.files("../3sd/dyn_teaching", pattern = "txt")
-lf_d_p <- list.files("../3sd/dyn_performing", pattern = "txt")
+lf_a_t <- list.files("./2sd/art_teaching", pattern = "txt")
+lf_a_p <- list.files("./2sd/art_performing", pattern = "txt")
+lf_d_t <- list.files("./2sd/dyn_teaching", pattern = "txt")
+lf_d_p <- list.files("./2sd/dyn_performing", pattern = "txt")
 
@@
 for (i in 1:length(lf_a_t)){
-  data_i <- fread(file.path("../3sd/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
+ data_i <- fread(file.path("./2sd/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
@@
 for (i in 1:length(lf_a_p)){
-  data_i <- fread(file.path("../3sd/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
+ data_i <- fread(file.path("./2sd/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
@@
 for (i in 1:length(lf_d_t)){
-  data_i <- fread(file.path("../3sd/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
+ data_i <- fread(file.path("./2sd/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
@@
 for (i in 1:length(lf_d_p)){
-  data_i <- fread(file.path("../3sd/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
+ data_i <- fread(file.path("./2sd/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
@@
 ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(Instance, Condition, Skill)]
-ioi_all <- ioi[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill)]
+ioi_art <- ioi[Skill == "articulation", .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill)]
+ioi_dyn <- ioi[Skill == "dynamics", .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill)]
 ```
 
-## Each instance
+## Summary Stats
+### Individual
 ```{r ioi_stats_ind, echo = FALSE}
@@
 
-## Averaged
+### Averaged
 ```{r ioi_stats_all, echo = FALSE}
-ioi_all
+ioi_art
+ioi_dyn
 ```
@@
 ## Plots
-```{r ioi_plot, echo = FALSE}
-p_ioi <- ggplot(ioi, aes(x = Instance, y = Mean, fill = Condition)) +
+### Articulation
+```{r ioi_art_plot, echo = FALSE}
+p_ioi_art <- ggplot(ioi[Skill == "articulation"], aes(x = Instance, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
@@
  geom_hline(yintercept = 188, linetype = "dashed") +
-  facet_grid(Skill ~ .) +
-  labs(y = "IOI (ms)", subtitle = "IOI: Each instance (All)")
-p_ioi
+ scale_x_continuous(breaks = seq(1:24)) +
+ labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Articulation)")
+p_ioi_art
 
-p_ioi_all <- ggplot(ioi_all, aes(x = Skill, y = Mean, fill = Condition)) +
+p_ioi_art_all <- ggplot(ioi_art, aes(x = Skill, y = Mean, fill = Condition)) +
    geom_bar(stat = "identity", position = position_dodge()) +
@@
    geom_hline(yintercept = 188, linetype = "dashed") +
-  labs(y = "IOI (ms)", subtitle = "IOI: Averaged (All)")
-p_ioi_all
+   labs(y = "IOI (ms)", subtitle = "IOI: Averaged (Articulation)")
+p_ioi_art_all
+```
+### Dynamics
+```{r ioi_dyn_plot, echo = FALSE}
+p_ioi_dyn <- ggplot(ioi[Skill == "dynamics"], aes(x = Instance, y = Mean, fill = Condition)) +
+ geom_bar(stat = "identity", position = position_dodge()) +
+ geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+               width = .2, position = position_dodge(.9)) +
+ geom_hline(yintercept = 188, linetype = "dashed") +
+ scale_x_continuous(breaks = seq(1:24)) +
+ labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Dynamics)")
+p_ioi_dyn
+
+p_ioi_dyn_all <- ggplot(ioi_dyn, aes(x = Skill, y = Mean, fill = Condition)) +
+   geom_bar(stat = "identity", position = position_dodge()) +
+   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+                 width = .2, position = position_dodge(.9)) +
+   geom_hline(yintercept = 188, linetype = "dashed") +
+   labs(y = "IOI (ms)", subtitle = "IOI: Averaged (Dynamics)")
+p_ioi_dyn_all
 ```
@@
                  width = .2, position = position_dodge(.9)) +
-  facet_grid(Subcomponent ~ .) +
+   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
    labs(y = "KOT (ms)", subtitle = "KOT: Each instance (Articulation)")
@@
                  width = .2, position = position_dodge(.9)) +
-  facet_grid(Subcomponent ~ .) +
+   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
    labs(y = "Key Velocity", subtitle = "KV: Each instance (Dynamics)")
@@
               width = .2, position = position_dodge(.9)) +
-  facet_grid(Subcomponent ~ .) +
+facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
 labs(y = "KV difference", subtitle = "KV-Diff: Each instance (Dynamics)")

### 2021-01-11 material/expstimuli/selection/analysis(3sd).Rmd
organised files and updated readme
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-01-11 material/expstimuli/selection/analysis(2sd).Rmd
@@
 ---
-title: "Music Perception: Stimuli profiles (2sd)"
+title: "Music Perception: Stimuli profiles (3sd)"
 output: html_notebook
@@
 
-I chose stimuli with the IOIs within 2sd randomly.
+I chose stimuli with the IOIs within 3sd randomly.
 
@@
 # create a list of data file names
-lf_a_t <- list.files("./2sd/art_teaching", pattern = "txt")
-lf_a_p <- list.files("./2sd/art_performing", pattern = "txt")
-lf_d_t <- list.files("./2sd/dyn_teaching", pattern = "txt")
-lf_d_p <- list.files("./2sd/dyn_performing", pattern = "txt")
+lf_a_t <- list.files("./3sd/art_teaching", pattern = "txt")
+lf_a_p <- list.files("./3sd/art_performing", pattern = "txt")
+lf_d_t <- list.files("./3sd/dyn_teaching", pattern = "txt")
+lf_d_p <- list.files("./3sd/dyn_performing", pattern = "txt")
 
@@
 for (i in 1:length(lf_a_t)){
- data_i <- fread(file.path("./2sd/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
+ data_i <- fread(file.path("./3sd/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
@@
 for (i in 1:length(lf_a_p)){
- data_i <- fread(file.path("./2sd/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
+ data_i <- fread(file.path("./3sd/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
@@
 for (i in 1:length(lf_d_t)){
- data_i <- fread(file.path("./2sd/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
+ data_i <- fread(file.path("./3sd/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
@@
 for (i in 1:length(lf_d_p)){
- data_i <- fread(file.path("./2sd/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
+ data_i <- fread(file.path("./3sd/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
@@
               width = .2, position = position_dodge(.9)) +
-   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
+facet_grid(Subcomponent ~ .) +
 labs(y = "KOT (ms)", subtitle = "KOT: Each instance (Articulation)")
@@
               width = .2, position = position_dodge(.9)) +
-   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
+facet_grid(Subcomponent ~ .) +
 labs(y = "Key Velocity", subtitle = "KV: Each instance (Dynamics)")
@@
               width = .2, position = position_dodge(.9)) +
-facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
+facet_grid(Subcomponent ~ .) +
 labs(y = "KV difference", subtitle = "KV-Diff: Each instance (Dynamics)")

### 2021-01-20 analysis/analysis.Rmd
add pilot analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: "Pilot Analysis (music perception study)"
author: "Atsuko Tominaga"
output: html_notebook
---

- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`

- 10 participants (experimental error = 1)

```{r packages, include = FALSE}
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
```

```{r read, include = FALSE}
# read files and combine them
data_ls <- list.files("data")
combined <- lapply(data_ls, function(f){
  fread(paste("data/", f, sep = ""), sep = ",")
})
data <- do.call(rbind.data.frame, combined)
```

## Individual data
```{r summary, echo = FALSE}
# remove irrelevant strings
data$midFile <- gsub("./practice/", "", data$midFile)
data$midFile <- gsub("./mid/", "", data$midFile)
data$midFile <- gsub(".mid", "", data$midFile)

# name conditions
data$condition <- "NA"
data$technique <- "NA"
data[grepl("_t_", midFile)]$condition <- "teaching"
data[grepl("_p_", midFile)]$condition <- "performing"
data[grepl("a_", midFile)]$technique <- "articulation"
data[grepl("d_", midFile)]$technique <- "dynamics"
# check correct or incorrect
data$correct <- 0
data[condition == "teaching" & rating == "Yes"]$correct <- 1
data[condition == "performing" & rating == "No"]$correct <- 1

all <- data[expMode == "experiment", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique)]
all[order(subjectNumber, condition, technique)]
```

## Accuracy
### All
```{r acc, echo = FALSE}
# individual
ind_data <- data[expMode == "experiment" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber)]
ind_data <- ind_data[order(subjectNumber)]

# all
subset <- ind_data[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/96)*100, SD_Percent = (sd(Sum)/96)*100)]
subset
```
### articulation
```{r acc-a, echo = FALSE}
# individual
ind_data_a <- data[expMode == "experiment" & technique == "articulation" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber)]
ind_data_a <- ind_data_a[order(subjectNumber)]

# all
subset_a <- ind_data_a[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100)]
subset_a
```

### dynamics
```{r acc-d, echo = FALSE}
# individual
ind_data_d <- data[expMode == "experiment" & technique == "dynamics" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber)]
ind_data_d <- ind_data_d[order(subjectNumber)]

# all
subset_d <- ind_data_d[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100)]
subset_d
```

```{r plot, echo = FALSE}
ind_data_t <- data[expMode == "experiment" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, technique)]
ind_data_t <- ind_data_t[order(subjectNumber, technique)]

subset_t <- ind_data_t[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100), by = .(technique)]
subset_t

data_box <- data.table(subjectNumber = ind_data_t$subjectNumber, articulation = ind_data_t[technique == "articulation"]$Percent, dynamics = ind_data_t[technique == "dynamics"]$Percent)
box <- ggpaired(data_box, cond1 = "articulation", cond2 = "dynamics", line.color = "gray", line.size = 0.4, ylab = "Correct %")
box
```

## 1. teaching vs. performing (altogether)
```{r plot1, echo = FALSE}
# individual
ind_data1 <- data[expMode == "experiment" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition)]
ind_data1 <- ind_data1[order(subjectNumber, condition)]

# all
subset1 <- ind_data1[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100), by = .(condition)]
subset1

data_box1 <- data.table(subjectNumber = ind_data1$subjectNumber, teaching = ind_data1[condition == "teaching"]$Percent, performing = ind_data1[condition == "performing"]$Percent)
box1 <- ggpaired(data_box1, cond1 = "teaching", cond2 = "performing", line.color = "gray", line.size = 0.4, ylab = "Correct %")
box1
```

## 2. teaching vs. performing (each technique)
```{r plot2, echo = FALSE}
# individual
ind_data2 <- data[expMode == "experiment" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique)]
ind_data2 <- ind_data2[order(subjectNumber, condition, technique)]

# all
subset2 <- ind_data2[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/24)*100, SD_Percent = (sd(Sum)/24)*100), by = .(condition, technique)]
subset2

data_box2 <- data.table(subjectNumber = ind_data2$subjectNumber, teaching = ind_data2[condition == "teaching"]$Percent, performing = ind_data2[condition == "performing"]$Percent, technique = ind_data2$technique)
box2 <- ggpaired(data_box2, cond1 = "teaching", cond2 = "performing", facet.by = "technique", line.color = "gray", line.size = 0.4, ylab = "Correct %")
box2
```

## 3. teaching (each item)
```{r item1, echo = FALSE}
# individual
ind_data3 <- data[expMode == "experiment" & subjectNumber != 9 & condition == "teaching", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique, midFile)]
ind_data3 <- ind_data3[order(subjectNumber, condition, technique, midFile)]

# all
subset3 <- ind_data3[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(condition, technique, midFile)]
subset3[order(-Mean_Percent)]

bar <- ggplot(subset3, aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
bar
```

### articulation
```{r item1-a, echo = FALSE}
subset3_a <- subset3[technique == "articulation"]
subset3_a[order(-Mean_Percent)]

bar_a <- ggplot(subset3[technique == "articulation"], aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
bar_a
```

### dynamics
```{r item1-d, echo = FALSE}
subset3_b <- subset3[order(-Mean_Percent) & technique == "dynamics"]
subset3_b[order(-Mean_Percent)]

bar_d <- ggplot(subset3[technique == "dynamics"], aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
bar_d
```

## 3. performing (each item)
```{r item2, echo = FALSE}
# individual
ind_data4 <- data[expMode == "experiment" & subjectNumber != 9 & condition == "performing", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique, midFile)]
ind_data4 <- ind_data4[order(subjectNumber, condition, technique, midFile)]

# all
subset4 <- ind_data4[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(condition, technique, midFile)]
subset4[order(-Mean_Percent)]

bar2 <- ggplot(subset4, aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
bar2
```

### articulation
```{r item2-a, echo = FALSE}
subset4_a <- subset4[technique == "articulation"]
subset4_a[order(-Mean_Percent)]

bar2_a <- ggplot(subset4[technique == "articulation"], aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
bar2_a
```

### dynamics
```{r item2-d, echo = FALSE}
subset4_d <- subset4[technique == "dynamics"]
subset4_d[order(-Mean_Percent)]

bar2_d <- ggplot(subset4[technique == "dynamics"], aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
bar2_d
```

### 2021-01-21 analysis/analysis.Rmd
update pilot analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
+# Accuracy
 ## Individual data
@@
 data[grepl("d_", midFile)]$technique <- "dynamics"
+data$item <- gsub("a_t_", "", data$midFile)
+data$item <- gsub("d_t_", "", data$item)
+data$item <- gsub("a_p_", "", data$item)
+data$item <- gsub("d_p_", "", data$item)
+
 # check correct or incorrect
@@
 
-## Accuracy
-### All
+## Summary
+### all
 ```{r acc, echo = FALSE}
@@
 ```
-### articulation
-```{r acc-a, echo = FALSE}
-# individual
-ind_data_a <- data[expMode == "experiment" & technique == "articulation" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber)]
-ind_data_a <- ind_data_a[order(subjectNumber)]
-
-# all
-subset_a <- ind_data_a[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100)]
-subset_a
-```
-
-### dynamics
-```{r acc-d, echo = FALSE}
-# individual
-ind_data_d <- data[expMode == "experiment" & technique == "dynamics" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber)]
-ind_data_d <- ind_data_d[order(subjectNumber)]
-
-# all
-subset_d <- ind_data_d[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100)]
-subset_d
-```
+### articulation vs. dynamics
 
@@
 # individual
-ind_data3 <- data[expMode == "experiment" & subjectNumber != 9 & condition == "teaching", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique, midFile)]
-ind_data3 <- ind_data3[order(subjectNumber, condition, technique, midFile)]
+ind_data3 <- data[expMode == "experiment" & subjectNumber != 9 & condition == "teaching", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique, item)]
+ind_data3 <- ind_data3[order(subjectNumber, condition, technique, item)]
 
 # all
-subset3 <- ind_data3[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(condition, technique, midFile)]
+subset3 <- ind_data3[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(condition, technique, item)]
 subset3[order(-Mean_Percent)]
-
-bar <- ggplot(subset3, aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
-bar
 ```
@@
 
-bar_a <- ggplot(subset3[technique == "articulation"], aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
+bar_a <- ggplot(subset3[technique == "articulation"], aes(x = reorder(item, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
 bar_a
@@
 ```{r item1-d, echo = FALSE}
-subset3_b <- subset3[order(-Mean_Percent) & technique == "dynamics"]
-subset3_b[order(-Mean_Percent)]
+subset3_d <- subset3[order(-Mean_Percent) & technique == "dynamics"]
+subset3_d[order(-Mean_Percent)]
 
-bar_d <- ggplot(subset3[technique == "dynamics"], aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
+bar_d <- ggplot(subset3[technique == "dynamics"], aes(x = reorder(item, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
 bar_d
@@
 # individual
-ind_data4 <- data[expMode == "experiment" & subjectNumber != 9 & condition == "performing", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique, midFile)]
-ind_data4 <- ind_data4[order(subjectNumber, condition, technique, midFile)]
+ind_data4 <- data[expMode == "experiment" & subjectNumber != 9 & condition == "performing", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique, item)]
+ind_data4 <- ind_data4[order(subjectNumber, condition, technique, item)]
 
 # all
-subset4 <- ind_data4[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(condition, technique, midFile)]
+subset4 <- ind_data4[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(condition, technique, item)]
 subset4[order(-Mean_Percent)]
-
-bar2 <- ggplot(subset4, aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
-bar2
 ```
@@
 
-bar2_a <- ggplot(subset4[technique == "articulation"], aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
+bar2_a <- ggplot(subset4[technique == "articulation"], aes(x = reorder(item, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
 bar2_a
@@
 
-bar2_d <- ggplot(subset4[technique == "dynamics"], aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
+bar2_d <- ggplot(subset4[technique == "dynamics"], aes(x = reorder(item, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
 bar2_d
 ```
+
+```{r export, include = FALSE}
+order_data <- rbind(
+  data.table(subset3_a$condition, subset3_a$technique, subset3_a$item, subset3_a$Mean_Percent),
+  data.table(subset3_d$condition, subset3_d$technique, subset3_d$item, subset3_d$Mean_Percent),
+  data.table(subset4_a$condition, subset4_a$technique, subset4_a$item, subset4_a$Mean_Percent),
+  data.table(subset4_d$condition, subset4_d$technique, subset4_d$item, subset4_d$Mean_Percent))
+
+colnames(order_data) <- c("condition", "technique", "item", "mean_percent")
+
+# export
+fwrite(order_data, file = "order_data.txt")
+```

### 2021-01-21 material/expstimuli/selection/analysis(2sd).Rmd
add analysis 2sd
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-Note: SubNr 8 was excluded due to an experimental error, SubNr 16 was excluded due to a deviated tempo (see analysis for [teaching-v1.0](https://github.com/atsukotominaga/teaching-v1.0))
+Note: SubNr 8 was excluded due to an experimental error, SubNr 16 was excluded due to a deviated tempo (see analysis for [music-teaching: experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1))
 
@@
 ```{r ioi_art_plot, echo = FALSE}
-p_ioi_art <- ggplot(ioi[Skill == "articulation"], aes(x = Instance, y = Mean, fill = Condition)) +
+p_ioi_art_t <- ggplot(ioi[Skill == "articulation" & Condition == "teaching"], aes(x = Instance, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
@@
  scale_x_continuous(breaks = seq(1:24)) +
- labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Articulation)")
-p_ioi_art
+ labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Articulation-Teaching)")
+p_ioi_art_t
+
+p_ioi_art_p <- ggplot(ioi[Skill == "articulation" & Condition == "performing"], aes(x = Instance, y = Mean)) +
+ geom_bar(stat = "identity", position = position_dodge()) +
+ geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+               width = .2, position = position_dodge(.9)) +
+ geom_hline(yintercept = 188, linetype = "dashed") +
+ scale_x_continuous(breaks = seq(1:24)) +
+ labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Articulation-Performing)")
+p_ioi_art_p
 
@@
 ```{r ioi_dyn_plot, echo = FALSE}
-p_ioi_dyn <- ggplot(ioi[Skill == "dynamics"], aes(x = Instance, y = Mean, fill = Condition)) +
+p_ioi_dyn_t <- ggplot(ioi[Skill == "dynamics" & Condition == "teaching"], aes(x = Instance, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
@@
  labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Dynamics)")
-p_ioi_dyn
+p_ioi_dyn_t
+
+p_ioi_dyn_p <- ggplot(ioi[Skill == "dynamics" & Condition == "performing"], aes(x = Instance, y = Mean)) +
+ geom_bar(stat = "identity", position = position_dodge()) +
+ geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+               width = .2, position = position_dodge(.9)) +
+ geom_hline(yintercept = 188, linetype = "dashed") +
+ scale_x_continuous(breaks = seq(1:24)) +
+ labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Dynamics)")
+p_ioi_dyn_p
 
@@
 
-## Plots
-```{r kot_plot, echo = FALSE}
-p_kot <- ggplot(kot, aes(x = Instance, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
-   labs(y = "KOT (ms)", subtitle = "KOT: Each instance (Articulation)")
-p_kot
-
-p_kot_all <- ggplot(kot_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   labs(y = "KOT (ms)", subtitle = "KOT: Averaged (Articulation)")
-p_kot_all
-```
-
 ## Each instance
@@
 kot_all
+```
+
+## Plots
+```{r kot_plot, echo = FALSE}
+p_kot_a <- ggplot(kot[Condition == "teaching"], aes(x = Instance, y = Mean)) +
+   geom_bar(stat = "identity", position = position_dodge()) +
+   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+                 width = .2, position = position_dodge(.9)) +
+   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
+   labs(y = "KOT (ms)", subtitle = "KOT: Each instance (Articulation-Teaching)")
+p_kot_a
+
+p_kot_d <- ggplot(kot[Condition == "performing"], aes(x = Instance, y = Mean)) +
+   geom_bar(stat = "identity", position = position_dodge()) +
+   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+                 width = .2, position = position_dodge(.9)) +
+   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
+   labs(y = "KOT (ms)", subtitle = "KOT: Each instance (Articulation-Performing)")
+p_kot_d
+
+p_kot_all <- ggplot(kot_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
+   geom_bar(stat = "identity", position = position_dodge()) +
+   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+                 width = .2, position = position_dodge(.9)) +
+   labs(y = "KOT (ms)", subtitle = "KOT: Averaged (Articulation)")
+p_kot_all
 ```
@@
 ```{r vel_plot, echo = FALSE}
-p_vel <- ggplot(vel, aes(x = Instance, y = Mean, fill = Condition)) +
+p_vel_t <- ggplot(vel[Condition == "teaching"], aes(x = Instance, y = Mean)) +
    geom_bar(stat = "identity", position = position_dodge()) +
@@
    facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
-   labs(y = "Key Velocity", subtitle = "KV: Each instance (Dynamics)")
-p_vel
+   labs(y = "Key Velocity", subtitle = "KV: Each instance (Dynamics-Teaching)")
+p_vel_t
+
+p_vel_p <- ggplot(vel[Condition == "performing"], aes(x = Instance, y = Mean)) +
+   geom_bar(stat = "identity", position = position_dodge()) +
+   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+                 width = .2, position = position_dodge(.9)) +
+   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
+   labs(y = "Key Velocity", subtitle = "KV: Each instance (Dynamics-Performing)")
+p_vel_p
 
@@
 ```{r vel_diff_plot, echo = FALSE}
-p_vel_diff <- ggplot(vel_diff, aes(x = Instance, y = Mean, fill = Condition)) +
+p_vel_diff_t <- ggplot(vel_diff[Condition == "teaching"], aes(x = Instance, y = Mean)) +
 geom_bar(stat = "identity", position = position_dodge()) +
@@
 labs(y = "KV difference", subtitle = "KV-Diff: Each instance (Dynamics)")
-p_vel_diff
+p_vel_diff_t
+
+p_vel_diff_p <- ggplot(vel_diff[Condition == "performing"], aes(x = Instance, y = Mean)) +
+geom_bar(stat = "identity", position = position_dodge()) +
+geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+              width = .2, position = position_dodge(.9)) +
+facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
+labs(y = "KV difference", subtitle = "KV-Diff: Each instance (Dynamics)")
+p_vel_diff_p
 
@@
 ```
+
+# Pilot data (with 9 participants)
+```{r read-2, include = FALSE}
+order_data <- fread("../../../analysis/order_data.txt")
+```
+
+order stimuli by participants' performance (left: low accuracy - high: high accuracy)
+
+## Legato
+```{r kot-legato, echo = FALSE}
+# kot-legato
+kot_legato <- kot[Subcomponent == "Legato"]
+order_art <- order_data[technique == "articulation"]
+order_art <- order_art[order(condition, item)]
+
+kot_legato$Correct <- 0
+kot_legato[Condition == "teaching"]$Correct <- order_art[condition == "teaching"]$mean_percent
+kot_legato[Condition == "performing"]$Correct <- order_art[condition == "performing"]$mean_percent
+
+ggplot(kot_legato[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Teaching-Legato (Correct Answer = YES)")
+
+ggplot(kot_legato[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Performing-Legato (Correct Answer = NO)")
+```
+
+## Staccato
+```{r kot-staccato, echo = FALSE}
+# kot-staccato
+kot_staccato <- kot[Subcomponent == "Staccato"]
+
+kot_staccato$Correct <- 0
+kot_staccato[Condition == "teaching"]$Correct <- order_art[condition == "teaching"]$mean_percent
+kot_staccato[Condition == "performing"]$Correct <- order_art[condition == "performing"]$mean_percent
+
+ggplot(kot_staccato[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Teaching-Staccato (Correct Answer = YES)")
+
+ggplot(kot_staccato[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Performing-Staccato (Correct Answer = NO)")
+```
+
+## Legato vs. Staccato
+```{r leg-sta, echo = FALSE}
+leg_sta <- rbind(kot_legato, kot_staccato)
+
+ggplot(leg_sta[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Teaching (Correct Answer = YES)")
+
+ggplot(leg_sta[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Performing (Correct Answer = NO)")
+```
+
+## Forte
+```{r vel-forte, echo = FALSE}
+# vel-forte
+vel_forte <- vel[Subcomponent == "Forte"]
+order_dyn <- order_data[technique == "dynamics"]
+order_dyn <- order_dyn[order(condition, item)]
+
+vel_forte$Correct <- 0
+vel_forte[Condition == "teaching"]$Correct <- order_dyn[condition == "teaching"]$mean_percent
+vel_forte[Condition == "performing"]$Correct <- order_dyn[condition == "performing"]$mean_percent
+
+ggplot(vel_forte[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching-Forte (Correct Answer = YES)")
+
+ggplot(vel_forte[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing-Forte (Correct Answer = NO)")
+```
+
+## Piano
+```{r vel-piano, echo = FALSE}
+# vel-piano
+vel_piano <- vel[Subcomponent == "Piano"]
+
+vel_piano$Correct <- 0
+vel_piano[Condition == "teaching"]$Correct <- order_dyn[condition == "teaching"]$mean_percent
+vel_piano[Condition == "performing"]$Correct <- order_dyn[condition == "performing"]$mean_percent
+
+ggplot(vel_piano[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching-Piano (Correct Answer = YES)")
+
+ggplot(vel_piano[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing-Piano (Correct Answer = NO)")
+```
+
+## Forte vs. Piano
+```{r for-pia, echo = FALSE}
+for_pia <- rbind(vel_forte, vel_piano)
+
+ggplot(for_pia[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching (Correct Answer = YES)")
+
+ggplot(for_pia[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing (Correct Answer = NO)")
+```
+
+## Forte to Piano
+```{r vel-diff-ftop, echo = FALSE}
+# vel_diff-ftop
+vel_diff_ftop <- vel_diff[Subcomponent == "FtoP"]
+
+vel_diff_ftop$Correct <- 0
+vel_diff_ftop[Condition == "teaching"]$Correct <- order_dyn[condition == "teaching"]$mean_percent
+vel_diff_ftop[Condition == "performing"]$Correct <- order_dyn[condition == "performing"]$mean_percent
+
+ggplot(vel_diff_ftop[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching-FtoP (Correct Answer = YES)")
+
+ggplot(vel_diff_ftop[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing-FtoP (Correct Answer = NO)")
+```
+
+## Piano to Forte
+```{r vel-diff-ptof, echo = FALSE}
+# vel_diff-ptof
+vel_diff_ptof <- vel_diff[Subcomponent == "PtoF"]
+
+vel_diff_ptof$Correct <- 0
+vel_diff_ptof[Condition == "teaching"]$Correct <- order_dyn[condition == "teaching"]$mean_percent
+vel_diff_ptof[Condition == "performing"]$Correct <- order_dyn[condition == "performing"]$mean_percent
+
+ggplot(vel_diff_ptof[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching-PtoF (Correct Answer = YES)")
+
+ggplot(vel_diff_ptof[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing-PtoF (Correct Answer = NO)")
+```
+
+## FtoP vs. PtoF
+```{r ftop-ptof, echo = FALSE}
+ftop_ptof <- rbind(vel_diff_ftop, vel_diff_ptof)
+
+ggplot(ftop_ptof[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching (Correct Answer = YES)")
+
+ggplot(ftop_ptof[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing (Correct Answer = NO)")
+```

### 2021-01-22 analysis/analysis.Rmd
add stats
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ---
-title: "Pilot Analysis (music perception study)"
+title: "Music Perception: Pilot Analysis"
 author: "Atsuko Tominaga"
@@
 
-- 10 participants (experimental error = 1)
+- 10 participants (experimental error = 1) >> 9 participants were included for analysis.
+
+# Experiment
+
+## Stimuli
+- Stimuli were selected from the previous study ([the sound of teaching music/experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1)).
+- 48 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 96 stimuli).
+The half of them were selected from the teaching condition and the other half were from the performing condition.
+  + 24 for teaching-articulation performances
+  + 24 for performing-articulation performances
+  + 24 for teaching-dynamics performances
+  + 24 for performing-dynamics performances
+
+## Design
+
+- 2 blocks (articulation / dynamics): participants were asked to do the same task for two expressions separately. The order of the blocks was counterbalanced across participants.
+- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomised across participants.
+
+## Procedure
+1. Musicians (> 6yo experience) were asked to listen to a number of recordings and judge whether each performance was produced for teaching purposes or not.
+
+Actual instruction:
+```
+Each performance was produced in order to either1) teach the musical expressive technique (as a teacher) 2) perform their best (as a performer).
+
+You will be asked to judge whether each performer had the intention to teach or not by pressing the 'Yes' <Left> or 'No' <Right> key.
+```
+
+2. Participants pressed "YES" if they think the recording was produced for teaching (as a teacher) whereas they pressed "NO" if they thought the recording was produced for performing (as a performer).
+
+3. Correct answers would be 1) participants pressed "YES" when they listened to teaching performances or 2) participants pressed "NO" when they listened to performing performances.
+
+I hope these make sense...
 
@@
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
+if (!require("afex")) {install.packages("afex"); require("afex")}
 ```
@@
 
-# Accuracy
+# Results
 ## Individual data
@@
 
-## Summary
+## 1. Summary
 ### all
@@
 ```
+
+```{r plot, echo = FALSE}
+ggboxplot(ind_data, x = "N", y = "Percent", add = "dotplot", xlab = FALSE) + ylab("Correct %") + theme(axis.text.x = element_blank())
+```
+
+### One-sample *t*-test
+```{r t-test, echo = FALSE}
+# normality check
+shapiro.test(ind_data$Percent)
+
+t.test(ind_data$Percent, mu = 50, alternative = "two.sided")
+```
+
+- Surprisingly, it showed a trend ( p = .06) but the 95% confidence interval overlaps with 50 %.
+
 ### articulation vs. dynamics
 
-```{r plot, echo = FALSE}
-ind_data_t <- data[expMode == "experiment" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, technique)]
-ind_data_t <- ind_data_t[order(subjectNumber, technique)]
+```{r plot2, echo = FALSE}
+ind_data_ad <- data[expMode == "experiment" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, technique)]
+ind_data_ad <- ind_data_ad[order(subjectNumber, technique)]
 
-subset_t <- ind_data_t[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100), by = .(technique)]
-subset_t
+subset_ad <- ind_data_ad[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100), by = .(technique)]
+subset_ad
 
-data_box <- data.table(subjectNumber = ind_data_t$subjectNumber, articulation = ind_data_t[technique == "articulation"]$Percent, dynamics = ind_data_t[technique == "dynamics"]$Percent)
+data_box <- data.table(subjectNumber = ind_data_ad$subjectNumber, articulation = ind_data_ad[technique == "articulation"]$Percent, dynamics = ind_data_ad[technique == "dynamics"]$Percent)
 box <- ggpaired(data_box, cond1 = "articulation", cond2 = "dynamics", line.color = "gray", line.size = 0.4, ylab = "Correct %")
@@
 
-## 1. teaching vs. performing (altogether)
-```{r plot1, echo = FALSE}
-# individual
-ind_data1 <- data[expMode == "experiment" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition)]
-ind_data1 <- ind_data1[order(subjectNumber, condition)]
+## One-sample *t*-test
+### articulation
+```{r t-test-a, echo = FALSE}
+# normality check
+shapiro.test(ind_data_ad[technique == "articulation"]$Percent)
 
-# all
-subset1 <- ind_data1[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100), by = .(condition)]
-subset1
+t.test(ind_data_ad[technique == "articulation"]$Percent, mu = 50, alternative = "two.sided")
+```
+- Not significantly different from chance (p > .2).
 
-data_box1 <- data.table(subjectNumber = ind_data1$subjectNumber, teaching = ind_data1[condition == "teaching"]$Percent, performing = ind_data1[condition == "performing"]$Percent)
-box1 <- ggpaired(data_box1, cond1 = "teaching", cond2 = "performing", line.color = "gray", line.size = 0.4, ylab = "Correct %")
-box1
+### dynamics
+```{r t-test-d, echo = FALSE}
+# normality check
+shapiro.test(ind_data_ad[technique == "dynamics"]$Percent)
+
+t.test(ind_data_ad[technique == "dynamics"]$Percent, mu = 50, alternative = "two.sided")
 ```
 
-## 2. teaching vs. performing (each technique)
-```{r plot2, echo = FALSE}
-# individual
-ind_data2 <- data[expMode == "experiment" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique)]
-ind_data2 <- ind_data2[order(subjectNumber, condition, technique)]
+- The performance was significantly better than chance (p < .01).
 
-# all
-subset2 <- ind_data2[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/24)*100, SD_Percent = (sd(Sum)/24)*100), by = .(condition, technique)]
-subset2
+## Paired *t*-test between articulation and dynamics
+```{r p-t-test, echo = FALSE}
+# normality check
+shapiro.test(ind_data_ad[technique == "dynamics"]$Percent-ind_data_ad[technique == "articulation"]$Percent)
 
-data_box2 <- data.table(subjectNumber = ind_data2$subjectNumber, teaching = ind_data2[condition == "teaching"]$Percent, performing = ind_data2[condition == "performing"]$Percent, technique = ind_data2$technique)
-box2 <- ggpaired(data_box2, cond1 = "teaching", cond2 = "performing", facet.by = "technique", line.color = "gray", line.size = 0.4, ylab = "Correct %")
-box2
+t.test(ind_data_ad[technique == "articulation"]$Percent, ind_data_ad[technique == "dynamics"]$Percent, paired = TRUE)
 ```
 
-## 3. teaching (each item)
+- There was a difference between articulation and dynamics in terms of accuracy.
+
+## 2. teaching (each item)
+### all
 ```{r item1, echo = FALSE}
@@
 ## 3. performing (each item)
+### all
 ```{r item2, echo = FALSE}

### 2021-01-24 material/expstimuli/selection/filtering_3sd.R
move a file to 3sd folder
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -1,189 +1,0 @@
-#!/usr/local/bin/R
-#rm(list=ls(all=T)) # clear all
-
-####################################
-#  Documentation
-####################################
-# Created: 12/10/2020
-# This script organises raw data and randomly select performances which do not contain any pitch errors (IOIs within 3SD).
-# GitHub repo (private): https://github.com/atsukotominaga/perception-v1.0/tree/master/material/stimuli
-
-# create folders if not exists
-if (!file.exists("3sd/")){
-  dir.create("3sd")
-  dir.create("3sd/practice/")
-}
-
-if (!file.exists("3sd/art_teaching")){
-  dir.create("3sd/art_teaching")
-  dir.create("3sd/practice/art_teaching")
-}
-
-if (!file.exists("3sd/dyn_teaching")){
-  dir.create("3sd/dyn_teaching")
-  dir.create("3sd/practice/dyn_teaching")
-}
-
-if (!file.exists("3sd/art_performing")){
-  dir.create("3sd/art_performing")
-  dir.create("3sd/practice/art_performing")
-}
-
-if (!file.exists("3sd/dyn_performing")){
-  dir.create("3sd/dyn_performing")
-  dir.create("3sd/practice/dyn_performing")
-}
-
-# read functions
-source("./function.R")
-
-# read a text file for ideal performance
-dt_ideal <- read.table("./ideal.txt")
-colnames(dt_ideal) <- "Pitch"
-dt_ideal$RowNr <- 1:nrow(dt_ideal)
-setcolorder(dt_ideal, c(2, 1))
-
-# create a list of data file names
-lf <- list.files("./raw_data", pattern = "txt")
-
-# create raw_data - merge all data files into one
-raw_data <- data.table()
-for (i in 1:length(lf)){
-  data_i <- fread(file.path("./raw_data", lf[i]), header = F, sep = " ", dec = ".")
-  raw_data <- rbind(raw_data, data_i)
-}
-
-# add column namesls
-colnames(raw_data) <- c("NoteNr", "TimeStamp", "Pitch", "Velocity", "Key_OnOff", "Device", "SubNr", "BlockNr", "TrialNr", "Skill", "Condition", "Image")
-
-# clean raw_data
-raw_data$NoteNr <- as.numeric(gsub(",", "", raw_data$NoteNr))
-raw_data$Image <- gsub(";", "", raw_data$Image)
-
-# sort by SubNr, BlockNr, TrialNr
[…]

### 2021-01-24 material/expstimuli/selection/stimuli.Rmd
rename filename analysis(2sd) >> stimuli
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-01-21 material/expstimuli/selection/analysis(2sd).Rmd
@@
 
-I chose stimuli with the IOIs within 2sd randomly.
+I chose stimuli with the IOIs within 2sd randomly from each condition (teaching, performing), each technique (articulation, dynamics).
 
 Note: SubNr 8 was excluded due to an experimental error, SubNr 16 was excluded due to a deviated tempo (see analysis for [music-teaching: experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1))
+
+# DVs
+- IOIs (average tempo)
+- Transition points
+- CV (tempo variability)
+- KOT (articulation)
+- KV (dynamics)
+- KV-diff (dynamics)
 
@@
 
-## Summary Stats
-### Individual
+## 1. All
+## Each instance
 ```{r ioi_stats_ind, echo = FALSE}
@@
 
-### Averaged
+## Averaged
 ```{r ioi_stats_all, echo = FALSE}
@@
 
-# KOT
+## 2. Transition points
+## Each instance
+```{r transition, echo = FALSE}
+ioi_tra <- dt_ioi[Subcomponent == "LtoS" | Subcomponent == "StoL" | Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(Instance, Condition, Skill)]
+ioi_tra
+
+ioi_tra_art <- ioi_tra[Skill == "articulation", .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill)]
+ioi_tra_dyn <- ioi_tra[Skill == "dynamics", .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill)]
+```
+
+## Averaged
+```{r transition-tats_all, echo = FALSE}
+
+ioi_tra_art
+ioi_tra_dyn
+```
+
+## Plots
+### Articulation
+```{r ioi_tra_art_plot, echo = FALSE}
+p_ioi_tra_art_t <- ggplot(ioi_tra[Skill == "articulation" & Condition == "teaching"], aes(x = Instance, y = Mean)) +
+ geom_bar(stat = "identity", position = position_dodge()) +
+ geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+               width = .2, position = position_dodge(.9)) +
+ geom_hline(yintercept = 188, linetype = "dashed") +
+ scale_x_continuous(breaks = seq(1:24)) +
+ labs(y = "IOI (ms)", subtitle = "IOI-Transition: Each instance (Articulation-Teaching)")
+p_ioi_tra_art_t
+
+p_ioi_tra_art_p <- ggplot(ioi_tra[Skill == "articulation" & Condition == "performing"], aes(x = Instance, y = Mean)) +
+ geom_bar(stat = "identity", position = position_dodge()) +
+ geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+               width = .2, position = position_dodge(.9)) +
+ geom_hline(yintercept = 188, linetype = "dashed") +
+ scale_x_continuous(breaks = seq(1:24)) +
+ labs(y = "IOI (ms)", subtitle = "IOI-Transition: Each instance (Articulation-Performing)")
+p_ioi_tra_art_p
+
+p_ioi_tra_art_all <- ggplot(ioi_tra_art, aes(x = Skill, y = Mean, fill = Condition)) +
+   geom_bar(stat = "identity", position = position_dodge()) +
+   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+                 width = .2, position = position_dodge(.9)) +
+   geom_hline(yintercept = 188, linetype = "dashed") +
+   labs(y = "IOI (ms)", subtitle = "IOI-Transition: Averaged (Articulation)")
+p_ioi_tra_art_all
+```
+
+### Dynamics
+```{r ioi_tra_dyn_plot, echo = FALSE}
+p_ioi_tra_dyn_t <- ggplot(ioi_tra[Skill == "dynamics" & Condition == "teaching"], aes(x = Instance, y = Mean)) +
+ geom_bar(stat = "identity", position = position_dodge()) +
+ geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+               width = .2, position = position_dodge(.9)) +
+ geom_hline(yintercept = 188, linetype = "dashed") +
+ scale_x_continuous(breaks = seq(1:24)) +
+ labs(y = "IOI (ms)", subtitle = "IOI-Transition: Each instance (Dynamics)")
+p_ioi_tra_dyn_t
+
+p_ioi_tra_dyn_p <- ggplot(ioi_tra[Skill == "dynamics" & Condition == "performing"], aes(x = Instance, y = Mean)) +
+ geom_bar(stat = "identity", position = position_dodge()) +
+ geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+               width = .2, position = position_dodge(.9)) +
+ geom_hline(yintercept = 188, linetype = "dashed") +
+ scale_x_continuous(breaks = seq(1:24)) +
+ labs(y = "IOI (ms)", subtitle = "IOI-Transition: Each instance (Dynamics)")
+p_ioi_tra_dyn_p
+
+p_ioi_tra_dyn_all <- ggplot(ioi_tra_dyn, aes(x = Skill, y = Mean, fill = Condition)) +
+   geom_bar(stat = "identity", position = position_dodge()) +
+   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+                 width = .2, position = position_dodge(.9)) +
+   geom_hline(yintercept = 188, linetype = "dashed") +
+   labs(y = "IOI (ms)", subtitle = "IOI-Transition: Averaged (Dynamics)")
+p_ioi_tra_dyn_all
+```
+
+## 3. CV
+## Each instance
+```{r cv, echo = FALSE}
+ioi_cv <- ioi
+ioi_cv$CV <- 0
+for (cond in unique(dt_ioi$Condition)){
+   for (tech in unique(dt_ioi$Skill)){
+      for (i in 1:24){
+         current <- dt_ioi[Condition == cond & Skill == tech & Instance == i]
+         current_cv <- sd(current$IOI)/ioi[Condition == cond & Skill == tech & Instance == i]$Mean
+         ioi_cv[Condition == cond & Skill == tech & Instance == i]$CV <- current_cv
+      }
+   }
+}
+ioi_cv
+ioi_cv_art <- ioi_cv[Skill == "articulation", .(N = .N, Mean = mean(CV), SD = sd(CV)), by = .(Condition, Skill)]
+ioi_cv_dyn <- ioi_cv[Skill == "dynamics", .(N = .N, Mean = mean(CV), SD = sd(CV)), by = .(Condition, Skill)]
+```
+
+## Averaged
+```{r ioi_cv_stats_all, echo = FALSE}
+ioi_cv_art
+ioi_cv_dyn
+```
+
+## Plots
+### Articulation
+```{r ioi_cv_art_plot, echo = FALSE}
+p_ioi_cv_art_t <- ggplot(ioi_cv[Skill == "articulation" & Condition == "teaching"], aes(x = Instance, y = CV)) +
+ geom_bar(stat = "identity", position = position_dodge()) +
+ scale_x_continuous(breaks = seq(1:24)) +
+ labs(y = "CV", subtitle = "IOI-CV: Each instance (Articulation-Teaching)")
+p_ioi_cv_art_t
+
+p_ioi_cv_art_p <- ggplot(ioi_cv[Skill == "articulation" & Condition == "performing"], aes(x = Instance, y = CV)) +
+ geom_bar(stat = "identity", position = position_dodge()) +
+ scale_x_continuous(breaks = seq(1:24)) +
+ labs(y = "CV", subtitle = "IOI-CV: Each instance (Articulation-Performing)")
+p_ioi_cv_art_p
+
+p_ioi_cv_art_all <- ggplot(ioi_cv_art, aes(x = Skill, y = Mean, fill = Condition)) +
+   geom_bar(stat = "identity", position = position_dodge()) +
+   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+                 width = .2, position = position_dodge(.9)) +
+   labs(y = "CV", subtitle = "IOI-CV: Averaged (Articulation)")
+p_ioi_cv_art_all
+```
+
+### Dynamics
+```{r ioi_cv_dyn_plot, echo = FALSE}
+p_ioi_cv_dyn_t <- ggplot(ioi_cv[Skill == "dynamics" & Condition == "teaching"], aes(x = Instance, y = CV)) +
+ geom_bar(stat = "identity", position = position_dodge()) +
+ scale_x_continuous(breaks = seq(1:24)) +
+ labs(y = "CV", subtitle = "IOI-CV: Each instance (Dynamics)")
+p_ioi_cv_dyn_t
+
+p_ioi_cv_dyn_p <- ggplot(ioi_cv[Skill == "dynamics" & Condition == "performing"], aes(x = Instance, y = CV)) +
+ geom_bar(stat = "identity", position = position_dodge()) +
+ scale_x_continuous(breaks = seq(1:24)) +
+ labs(y = "CV", subtitle = "IOI-CV: Each instance (Dynamics)")
+p_ioi_cv_dyn_p
+
+p_ioi_cv_dyn_all <- ggplot(ioi_cv_dyn, aes(x = Skill, y = Mean, fill = Condition)) +
+   geom_bar(stat = "identity", position = position_dodge()) +
+   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
+                 width = .2, position = position_dodge(.9)) +
+   labs(y = "CV", subtitle = "IOI-CV: Averaged (Dynamics)")
+p_ioi_cv_dyn_all
+```
+
+# KOT (only for articulation stimuli)
 ```{r kot, include = FALSE}
@@
 
-# KV
+# KV (only for dynamics stimuli)
 ```{r kv, include = FALSE}
@@
 
-# KV-Diff
+# KV-Diff (only for dynamics stimuli)
 ```{r vel_diff, include = FALSE}
@@
 
-order stimuli by participants' performance (left: low accuracy - high: high accuracy)
+I order stimuli above by participants' performance (left: low accuracy - high: high accuracy).
 
-## Legato
+- dashed lines indicate a target tempo
+
+## 1. Tempo
+### All IOIs (articulation)
+```{r ioi-articulation, echo = FALSE}
+# ioi-articulation
+ioi_articulation <- ioi[Skill == "articulation"]
+order_art <- order_data[technique == "articulation"]
+order_art <- order_art[order(condition, item)]
+
+ioi_articulation$Correct <- 0
+ioi_articulation[Condition == "teaching"]$Correct <- order_art[condition == "teaching"]$mean_percent
+ioi_articulation[Condition == "performing"]$Correct <- order_art[condition == "performing"]$mean_percent
+
+ggplot(ioi_articulation[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(0, 250) +
+ geom_hline(yintercept = 188, linetype = "dashed") + labs(x = "Stimuli", y = "IOI (ms)", subtitle = "Teaching-Articulation (Correct Answer = YES)")
+
+ggplot(ioi_articulation[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(0, 250) +
+ geom_hline(yintercept = 188, linetype = "dashed") + labs(x = "Stimuli", y = "IOI (ms)", subtitle = "Performing-Articulation (Correct Answer = NO)")
+```
+
+### All IOIs (dynamics)
+```{r ioi-dynamics, echo = FALSE}
+# ioi-dynamics
+ioi_dynamics <- ioi[Skill == "dynamics"]
+order_dyn <- order_data[technique == "dynamics"]
+order_dyn <- order_dyn[order(condition, item)]
+
+ioi_dynamics$Correct <- 0
+ioi_dynamics[Condition == "teaching"]$Correct <- order_art[condition == "teaching"]$mean_percent
+ioi_dynamics[Condition == "performing"]$Correct <- order_art[condition == "performing"]$mean_percent
+
+ggplot(ioi_dynamics[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(0, 300) +
+ geom_hline(yintercept = 188, linetype = "dashed") + labs(x = "Stimuli", y = "IOI (ms)", subtitle = "Teaching-Dynamics (Correct Answer = YES)")
+
+ggplot(ioi_dynamics[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(0, 300) +
+ geom_hline(yintercept = 188, linetype = "dashed") + labs(x = "Stimuli", y = "IOI (ms)", subtitle = "Performing-Dynamics (Correct Answer = NO)")
+```
+
+### Transition (articulation)
+```{r ioi-tra-articulation, echo = FALSE}
+# ioi-tra-articulation
+ioi_tra_articulation <- ioi_tra[Skill == "articulation"]
+
+ioi_tra_articulation$Correct <- 0
+ioi_tra_articulation[Condition == "teaching"]$Correct <- order_art[condition == "teaching"]$mean_percent
+ioi_tra_articulation[Condition == "performing"]$Correct <- order_art[condition == "performing"]$mean_percent
+
+ggplot(ioi_tra_articulation[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(0, 300) +
+ geom_hline(yintercept = 188, linetype = "dashed") + labs(x = "Stimuli", y = "IOI (ms)", subtitle = "Teaching-Articulation (Correct Answer = YES)")
+
+ggplot(ioi_tra_articulation[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(0, 300) +
+ geom_hline(yintercept = 188, linetype = "dashed") + labs(x = "Stimuli", y = "IOI (ms)", subtitle = "Performing-Articulation (Correct Answer = NO)")
+```
+
+### Transition (dynamics)
+```{r ioi-tra-dynamics, echo = FALSE}
+# ioi-tra-dynamics
+ioi_tra_dynamics <- ioi_tra[Skill == "dynamics"]
+
+ioi_tra_dynamics$Correct <- 0
+ioi_tra_dynamics[Condition == "teaching"]$Correct <- order_art[condition == "teaching"]$mean_percent
+ioi_tra_dynamics[Condition == "performing"]$Correct <- order_art[condition == "performing"]$mean_percent
+
+ggplot(ioi_tra_dynamics[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(0, 350) +
+ geom_hline(yintercept = 188, linetype = "dashed") + labs(x = "Stimuli", y = "IOI (ms)", subtitle = "Teaching-Articulation (Correct Answer = YES)")
+
+ggplot(ioi_tra_dynamics[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(0, 350) +
+ geom_hline(yintercept = 188, linetype = "dashed") + labs(x = "Stimuli", y = "IOI (ms)", subtitle = "Performing-Articulation (Correct Answer = NO)")
+```
+
+### CV(articulation)
+```{r ioi-cv-articulation, echo = FALSE}
+# ioi-tra-articulation
+ioi_cv_articulation <- ioi_cv[Skill == "articulation"]
+
+ioi_cv_articulation$Correct <- 0
+ioi_cv_articulation[Condition == "teaching"]$Correct <- order_art[condition == "teaching"]$mean_percent
+ioi_cv_articulation[Condition == "performing"]$Correct <- order_art[condition == "performing"]$mean_percent
+
+ggplot(ioi_cv_articulation[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = CV, fill = Correct)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "CV", subtitle = "Teaching-Articulation (Correct Answer = YES)")
+
+ggplot(ioi_cv_articulation[Condition == "performing"], aes(x = reorder(Instance, Correct), y = CV, fill = Correct)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "CV", subtitle = "Performing-Articulation (Correct Answer = NO)")
+```
+### CV (dynamics)
+```{r ioi-cv-dynamics, echo = FALSE}
+# ioi-tra-dynamics
+ioi_cv_dynamics <- ioi_cv[Skill == "dynamics"]
+
+ioi_cv_dynamics$Correct <- 0
+ioi_cv_dynamics[Condition == "teaching"]$Correct <- order_art[condition == "teaching"]$mean_percent
+ioi_cv_dynamics[Condition == "performing"]$Correct <- order_art[condition == "performing"]$mean_percent
+
+ggplot(ioi_cv_dynamics[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = CV, fill = Correct)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "CV", subtitle = "Teaching-Dynamics (Correct Answer = YES)")
+
+ggplot(ioi_cv_dynamics[Condition == "performing"], aes(x = reorder(Instance, Correct), y = CV, fill = Correct)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "CV", subtitle = "Performing-Dynamics (Correct Answer = NO)")
+```
+
+## 2. Articulation
+### Legato
 ```{r kot-legato, echo = FALSE}
@@
 kot_legato <- kot[Subcomponent == "Legato"]
-order_art <- order_data[technique == "articulation"]
-order_art <- order_art[order(condition, item)]
 
@@
 
-ggplot(kot_legato[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Teaching-Legato (Correct Answer = YES)")
+ggplot(kot_legato[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(-100, 100) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Teaching-Legato (Correct Answer = YES)")
 
-ggplot(kot_legato[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Performing-Legato (Correct Answer = NO)")
+ggplot(kot_legato[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(-100, 100) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Performing-Legato (Correct Answer = NO)")
 ```
 
-## Staccato
+### Staccato
 ```{r kot-staccato, echo = FALSE}
@@
 
-ggplot(kot_staccato[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Teaching-Staccato (Correct Answer = YES)")
+ggplot(kot_staccato[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(-200, 0) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Teaching-Staccato (Correct Answer = YES)")
 
-ggplot(kot_staccato[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Performing-Staccato (Correct Answer = NO)")
+ggplot(kot_staccato[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(-200, 0) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Performing-Staccato (Correct Answer = NO)")
 ```
 
-## Legato vs. Staccato
+### Legato vs. Staccato
 ```{r leg-sta, echo = FALSE}
@@
 
-ggplot(leg_sta[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Teaching (Correct Answer = YES)")
+ggplot(leg_sta[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(-200, 100) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Teaching (Correct Answer = YES)")
 
-ggplot(leg_sta[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Performing (Correct Answer = NO)")
+ggplot(leg_sta[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(-200, 100) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Performing (Correct Answer = NO)")
 ```
 
-## Forte
+## 3. Dynamics
+### Forte
 ```{r vel-forte, echo = FALSE}
@@
 vel_forte <- vel[Subcomponent == "Forte"]
-order_dyn <- order_data[technique == "dynamics"]
-order_dyn <- order_dyn[order(condition, item)]
 
@@
 
-## Piano
+### Piano
 ```{r vel-piano, echo = FALSE}
@@
 
-ggplot(vel_piano[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching-Piano (Correct Answer = YES)")
+ggplot(vel_piano[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(0, 90) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching-Piano (Correct Answer = YES)")
 
-ggplot(vel_piano[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing-Piano (Correct Answer = NO)")
+ggplot(vel_piano[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(0, 90) + labs(x = "Stimuli", y = "KV", subtitle = "Performing-Piano (Correct Answer = NO)")
 ```
 
-## Forte vs. Piano
+### Forte vs. Piano
 ```{r for-pia, echo = FALSE}
@@
 
-## Forte to Piano
+### Forte to Piano
 ```{r vel-diff-ftop, echo = FALSE}
@@
 
-ggplot(vel_diff_ftop[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching-FtoP (Correct Answer = YES)")
+ggplot(vel_diff_ftop[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(-50, 10) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching-FtoP (Correct Answer = YES)")
 
-ggplot(vel_diff_ftop[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing-FtoP (Correct Answer = NO)")
+ggplot(vel_diff_ftop[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(-50, 10) + labs(x = "Stimuli", y = "KV", subtitle = "Performing-FtoP (Correct Answer = NO)")
 ```
 
-## Piano to Forte
+### Piano to Forte
 ```{r vel-diff-ptof, echo = FALSE}
@@
 
-ggplot(vel_diff_ptof[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching-PtoF (Correct Answer = YES)")
+ggplot(vel_diff_ptof[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(0, 60) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching-PtoF (Correct Answer = YES)")
 
-ggplot(vel_diff_ptof[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing-PtoF (Correct Answer = NO)")
+ggplot(vel_diff_ptof[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(0, 60) + labs(x = "Stimuli", y = "KV", subtitle = "Performing-PtoF (Correct Answer = NO)")
 ```
 
-## FtoP vs. PtoF
+### FtoP vs. PtoF
 ```{r ftop-ptof, echo = FALSE}
@@
 
-ggplot(ftop_ptof[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching (Correct Answer = YES)")
+ggplot(ftop_ptof[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(-40, 45) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching (Correct Answer = YES)")
 
-ggplot(ftop_ptof[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing (Correct Answer = NO)")
+ggplot(ftop_ptof[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + ylim(-40, 45) + labs(x = "Stimuli", y = "KV", subtitle = "Performing (Correct Answer = NO)")
 ```

### 2021-01-25 material/expstimuli/export/mid_export.py
change to correct paths
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -13,10 +13,10 @@ if not os.path.exists("practice"):
     os.mkdir("practice")
 
 #%% folder names
-folder_a_t = "../R/2sd/art_teaching/"
-folder_d_t = "../R/2sd/dyn_teaching/"
-folder_a_p = "../R/2sd/art_performing/"
-folder_d_p = "../R/2sd/dyn_performing/"
+folder_a_t = "../selection/2sd/art_teaching/"
+folder_d_t = "../selection/2sd/dyn_teaching/"
+folder_a_p = "../selection/2sd/art_performing/"
+folder_d_p = "../selection/2sd/dyn_performing/"
 folders = [folder_a_t, folder_d_t, folder_a_p, folder_d_p]
 
 #%% mid export
@@ -31,13 +31,13 @@ for folder in folders:
             mid.tracks.append(track)
             track.append(mido.Message('program_change', program=0, time=0)) # program 0 = Acoustic Grand Piano
             # name for mid file
-            if folder == "../R/2sd/art_teaching/":
+            if folder == "../selection/2sd/art_teaching/":
                 midname = "./mid/a_t_" + str(instance+1) + ".mid"
-            elif folder == "../R/2sd/dyn_teaching/":
+            elif folder == "../selection/2sd/dyn_teaching/":
                 midname = "./mid/d_t_" + str(instance+1) + ".mid"
-            elif folder == "../R/2sd/art_performing/":
+            elif folder == "../selection/2sd/art_performing/":
                 midname = "./mid/a_p_" + str(instance+1) + ".mid"
-            elif folder == "../R/2sd/dyn_performing/":
+            elif folder == "../selection/2sd/dyn_performing/":
                 midname = "./mid/d_p_" + str(instance+1) + ".mid"
             # read current track data (txt file)   
             current = csv.reader(csvfile, delimiter = ",")
@@ -63,10 +63,10 @@ for folder in folders:
 print("Experimental stimuli - Done :D")
 
 #%%
-folder_a_t_p = "../R/2sd/practice/art_teaching/"
-folder_d_t_p = "../R/2sd/practice/dyn_teaching/"
-folder_a_p_p = "../R/2sd/practice/art_performing/"
-folder_d_p_p = "../R/2sd/practice/dyn_performing/"
+folder_a_t_p = "../selection/2sd/practice/art_teaching/"
+folder_d_t_p = "../selection/2sd/practice/dyn_teaching/"
[…]

### 2021-01-25 analysis/stimuli/stimuli_analysis.Rmd
stimuli analysis from actual midfiles
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-01-11 material/expstimuli/selection/analysis(2sd).Rmd
@@
 ---
-title: "Music Perception: Stimuli profiles (2sd)"
+title: "Music Perception: Stimuli Analysis)"
 output: html_notebook
@@
 
-I chose stimuli with the IOIs within 2sd randomly.
+I chose stimuli with the IOIs within 2sd randomly from each condition (teaching, performing), each technique (articulation, dynamics).
 
-Note: SubNr 8 was excluded due to an experimental error, SubNr 16 was excluded due to a deviated tempo (see analysis for [teaching-v1.0](https://github.com/atsukotominaga/teaching-v1.0))
+Note: SubNr 8 was excluded due to an experimental error, SubNr 16 was excluded due to a deviated tempo (see analysis for [music-teaching: experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1))
+
+# DVs
+- IOIs (average tempo)
+- Transition points
+- CV (tempo variability)
+- KOT (articulation)
+- KV (dynamics)
+- KV-diff (dynamics)
 
@@
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
+if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
 if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
@@
 # create a list of data file names
-lf_a_t <- list.files("./2sd/art_teaching", pattern = "txt")
-lf_a_p <- list.files("./2sd/art_performing", pattern = "txt")
-lf_d_t <- list.files("./2sd/dyn_teaching", pattern = "txt")
-lf_d_p <- list.files("./2sd/dyn_performing", pattern = "txt")
+lf <- list.files("../../experiment/mid/", pattern = "mid")
 
-# merge all data files into one
-data <- data.table()
-for (i in 1:length(lf_a_t)){
- data_i <- fread(file.path("./2sd/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
- data_i$Instance <- i
- data <- rbind(data, data_i)
+# combine data
+all_data <- data.table()
+for (file in lf){
+   current <- readMidi(paste("../../experiment/mid/", file, sep = ""))
+   current$midfile <- file
+   all_data <- rbind(all_data, current)
 }
-for (i in 1:length(lf_a_p)){
- data_i <- fread(file.path("./2sd/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
- data_i$Instance <- i
- data <- rbind(data, data_i)
-}
-for (i in 1:length(lf_d_t)){
- data_i <- fread(file.path("./2sd/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
- data_i$Instance <- i
- data <- rbind(data, data_i)
-}
-for (i in 1:length(lf_d_p)){
- data_i <- fread(file.path("./2sd/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
- data_i$Instance <- i
- data <- rbind(data, data_i)
+
+data <- all_data[event == "Note On" | event == "Note Off"]
+data$NoteNr <- rep(1:134, nrow(data)/134)
+data$channel <- NULL
+data$parameterMetaSystem <- NULL
+data$track <- NULL
+data$type <- NULL
+
+# labelling
+colnames(data)[c(3,4)] <- c("Pitch", "Velocity")
+data$Condition <- "NA"
+data$Skill <- "NA"
+data[midfile %like% "_t_"]$Condition <- "teaching"
+data[midfile %like% "_p_"]$Condition <- "performing"
+data[startsWith(midfile, "a_")]$Skill <- "articulation"
+data[startsWith(midfile, "d_")]$Skill <- "dynamics"
+
+# numbering
+instance = 1
+data$Instance <- 0
+for (file in unique(data$midfile)){
+   data[midfile == file]$Instance <- instance
+   instance = instance + 1
 }
@@
 ```{r ioi, include = FALSE}
-data_onset <- data[Key_OnOff == 1]
-data_offset <- data[Key_OnOff == 0]
+data_onset <- data[event == "Note On"]
+data_offset <- data[event == "Note Off"]
 
-data_onset$IOI <- diff(c(0, data_onset$TimeStamp))
-dt_ioi <- data_onset[NoteNr != 17]
+data_onset$IOI <- diff(c(0, data_onset$time))
+dt_ioi <- data_onset[NoteNr != 1]
 dt_ioi$Interval <- rep(1:66, nrow(dt_ioi)/66)
@@
 }
-
-ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(Instance, Condition, Skill)]
-ioi_art <- ioi[Skill == "articulation", .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill)]
-ioi_dyn <- ioi[Skill == "dynamics", .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill)]
 ```
 
-## Summary Stats
-### Individual
-```{r ioi_stats_ind, echo = FALSE}
-ioi
+# All
+## Articulation
+```{r ioi-all-art, echo = FALSE}
+ioi_art <- dt_ioi[Skill == "articulation"]
+
 ```
 
-### Averaged
-```{r ioi_stats_all, echo = FALSE}
-ioi_art
-ioi_dyn
+## Dynamics
+```{r ioi-all-dyn, echo = FALSE}
+ioi_dyn <- dt_ioi[Skill == "dynamics"]
+
 ```
-
-## Plots
-### Articulation
-```{r ioi_art_plot, echo = FALSE}
-p_ioi_art <- ggplot(ioi[Skill == "articulation"], aes(x = Instance, y = Mean, fill = Condition)) +
- geom_bar(stat = "identity", position = position_dodge()) +
- geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-               width = .2, position = position_dodge(.9)) +
- geom_hline(yintercept = 188, linetype = "dashed") +
- scale_x_continuous(breaks = seq(1:24)) +
- labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Articulation)")
-p_ioi_art
-
-p_ioi_art_all <- ggplot(ioi_art, aes(x = Skill, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   geom_hline(yintercept = 188, linetype = "dashed") +
-   labs(y = "IOI (ms)", subtitle = "IOI: Averaged (Articulation)")
-p_ioi_art_all
-```
-### Dynamics
-```{r ioi_dyn_plot, echo = FALSE}
-p_ioi_dyn <- ggplot(ioi[Skill == "dynamics"], aes(x = Instance, y = Mean, fill = Condition)) +
- geom_bar(stat = "identity", position = position_dodge()) +
- geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-               width = .2, position = position_dodge(.9)) +
- geom_hline(yintercept = 188, linetype = "dashed") +
- scale_x_continuous(breaks = seq(1:24)) +
- labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Dynamics)")
-p_ioi_dyn
-
-p_ioi_dyn_all <- ggplot(ioi_dyn, aes(x = Skill, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   geom_hline(yintercept = 188, linetype = "dashed") +
-   labs(y = "IOI (ms)", subtitle = "IOI: Averaged (Dynamics)")
-p_ioi_dyn_all
-```
-
-# KOT
-```{r kot, include = FALSE}
-data_onset$KOT <- NA
-for (row in 1:nrow(data_onset)){
-   if (row < nrow(data_onset)){
-      data_onset$KOT[row+1] <- data_offset$TimeStamp[row] - data_onset$TimeStamp[row+1] # offset(n) - onset(n+1)
-   }
-}
-
-dt_kot <- data_onset[NoteNr != 17]
-dt_kot$Interval <- rep(1:66, nrow(dt_kot)/66)
-
-# assign Subcomponents
-dt_kot$Subcomponent <- "NA"
-# Legato
-for (phrase in 1:length(ls_legato)){
-   for (note in 1:length(ls_legato[[phrase]])){
-     dt_kot[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
-   }
-}
-# Staccato
-for (phrase in 1:length(ls_staccato)){
-   for (note in 1:length(ls_staccato[[phrase]])){
-     dt_kot[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
-   }
-}
-
-# Forte
-for (phrase in 1:length(ls_forte)){
-   for (note in 1:length(ls_forte[[phrase]])){
-     dt_kot[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
-   }
-}
-# Piano
-for (phrase in 1:length(ls_piano)){
-   for (note in 1:length(ls_piano[[phrase]])){
-     dt_kot[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
-   }
-}
-
-# assign Subcomponent Change
-for (number in change_1){
-   dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
-   dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
-}
-for (number in change_2){
-   dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
-   dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
-}
-
-kot <- dt_kot[Subcomponent == "Legato" | Subcomponent == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(Instance, Condition, Skill, Subcomponent)]
-kot_all <- kot[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Subcomponent)]
-```
-
-## Plots
-```{r kot_plot, echo = FALSE}
-p_kot <- ggplot(kot, aes(x = Instance, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
-   labs(y = "KOT (ms)", subtitle = "KOT: Each instance (Articulation)")
-p_kot
-
-p_kot_all <- ggplot(kot_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   labs(y = "KOT (ms)", subtitle = "KOT: Averaged (Articulation)")
-p_kot_all
-```
-
-## Each instance
-```{r kot_stats_ind, echo = FALSE}
-kot
-```
-
-## Averaged
-```{r kot_stats_all, echo = FALSE}
-kot_all
-```
-
-# KV
-```{r kv, include = FALSE}
-dt_vel <- data_onset
-dt_vel$Note <- rep(1:67, nrow(dt_vel)/67)
-
-# assign Subcomponents
-# for each note
-dt_vel$Subcomponent <- NA
-# Legato
-for (phrase in 1:length(ls_legato_2)){
-   for (note in 1:length(ls_legato_2[[phrase]])){
-     dt_vel$Subcomponent[dt_vel$Skill == "articulation" & dt_vel$Note == ls_legato_2[[phrase]][note]] <- "Legato"
-   }
-}
-# Staccato
-for (phrase in 1:length(ls_staccato_2)){
-   for (note in 1:length(ls_staccato_2[[phrase]])){
-     dt_vel$Subcomponent[dt_vel$Skill == "articulation" & dt_vel$Note == ls_staccato_2[[phrase]][note]] <- "Staccato"
-   }
-}
-
-# Forte
-for (phrase in 1:length(ls_forte_2)){
-   for (note in 1:length(ls_forte_2[[phrase]])){
-     dt_vel$Subcomponent[dt_vel$Skill == "dynamics" & dt_vel$Note == ls_forte_2[[phrase]][note]] <- "Forte"
-   }
-}
-
-# Piano
-for (phrase in 1:length(ls_piano_2)){
-   for (note in 1:length(ls_piano_2[[phrase]])){
-     dt_vel$Subcomponent[dt_vel$Skill == "dynamics" & dt_vel$Note == ls_piano_2[[phrase]][note]] <- "Piano"
-   }
-}
-
-vel <- dt_vel[Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(Instance, Condition, Skill, Subcomponent)]
-vel_all <- vel[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Subcomponent)]
-```
-
-## Each instance
-```{r vel_stats_ind, echo = FALSE}
-vel
-```
-
-## Averaged
-```{r vel_stats_all, echo = FALSE}
-vel_all
-```
-
-## Plots
-```{r vel_plot, echo = FALSE}
-p_vel <- ggplot(vel, aes(x = Instance, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
-   labs(y = "Key Velocity", subtitle = "KV: Each instance (Dynamics)")
-p_vel
-
-p_vel_all <- ggplot(vel_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   labs(y = "Key Velocity", subtitle = "KV: Averaged (Dynamics)")
-p_vel_all
-```
-
-# KV-Diff
-```{r vel_diff, include = FALSE}
-# calculate differences and remove the first note
-dt_vel$Diff <- diff(c(0, dt_vel$Velocity))
-dt_vel_diff <- dt_vel[Note != 1]
-dt_vel$Diff <- NULL # remove Diff from dt_vel
-
-# assign Interval
-dt_vel_diff$Interval <- rep(1:66, nrow(dt_vel_diff)/66)
-
-# assign Subcomponents
-# for intervals
-dt_vel_diff$Subcomponent <- NA
-# Legato
-for (phrase in 1:length(ls_legato)){
-for (note in 1:length(ls_legato[[phrase]])){
-  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == ls_legato[[phrase]][note]] <- "Legato"
-}
-}
-# Staccato
-for (phrase in 1:length(ls_staccato)){
-for (note in 1:length(ls_staccato[[phrase]])){
-  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == ls_staccato[[phrase]][note]] <- "Staccato"
-}
-}
-
-# Forte
-for (phrase in 1:length(ls_forte)){
-for (note in 1:length(ls_forte[[phrase]])){
-  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == ls_forte[[phrase]][note]] <- "Forte"
-}
-}
-# Piano
-for (phrase in 1:length(ls_piano)){
-for (note in 1:length(ls_piano[[phrase]])){
-  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == ls_piano[[phrase]][note]] <- "Piano"
-}
-}
-
-# Assign Skill Change
-for (i in change_1){
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "LtoS"
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "FtoP"
-}
-for (i in change_2){
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "StoL"
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "PtoF"
-}
-
-vel_diff <- dt_vel_diff[Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(Instance, Condition, Skill, Subcomponent)]
-vel_diff_all <- vel_diff[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Subcomponent)]
-```
-
-## Each instance
-```{r vel__diff_stats_ind, echo = FALSE}
-vel_diff
-```
-
-## Averaged
-```{r vel_diff_stats_all, echo = FALSE}
-vel_diff_all
-```
-
-## Plots
-```{r vel_diff_plot, echo = FALSE}
-p_vel_diff <- ggplot(vel_diff, aes(x = Instance, y = Mean, fill = Condition)) +
-geom_bar(stat = "identity", position = position_dodge()) +
-geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-              width = .2, position = position_dodge(.9)) +
-facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
-labs(y = "KV difference", subtitle = "KV-Diff: Each instance (Dynamics)")
-p_vel_diff
-
-p_vel_diff_all <- ggplot(vel_diff_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
-geom_bar(stat = "identity", position = position_dodge()) +
-geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-              width = .2, position = position_dodge(.9)) +
-labs(y = "KV difference", subtitle = "KV-Diff: Averaged (Dynamics)")
-p_vel_diff_all
-```

### 2021-01-25 analysis/analysis.Rmd
update analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ---
-title: "Music Perception: Pilot Analysis"
+title: "Music Perception: Pilot Accuracy Analysis"
 author: "Atsuko Tominaga"
@@
 
-I hope these make sense...
-
 ```{r packages, include = FALSE}
@@
 })
-data <- do.call(rbind.data.frame, combined)
+all_data <- do.call(rbind.data.frame, combined)
 ```
@@
 # remove irrelevant strings
-data$midFile <- gsub("./practice/", "", data$midFile)
-data$midFile <- gsub("./mid/", "", data$midFile)
-data$midFile <- gsub(".mid", "", data$midFile)
+data <- all_data[expMode == "experiment"]
+data$MidFile <- gsub("./mid/", "", data$midFile)
+data$MidFile <- gsub(".mid", "", data$MidFile)
 
 # name conditions
-data$condition <- "NA"
-data$technique <- "NA"
-data[grepl("_t_", midFile)]$condition <- "teaching"
-data[grepl("_p_", midFile)]$condition <- "performing"
-data[grepl("a_", midFile)]$technique <- "articulation"
-data[grepl("d_", midFile)]$technique <- "dynamics"
-data$item <- gsub("a_t_", "", data$midFile)
-data$item <- gsub("d_t_", "", data$item)
-data$item <- gsub("a_p_", "", data$item)
-data$item <- gsub("d_p_", "", data$item)
+data$Condition <- "NA"
+data$Skill <- "NA"
+data[grepl("_t_", midFile)]$Condition <- "teaching"
+data[grepl("_p_", midFile)]$Condition <- "performing"
+data[grepl("a_", midFile)]$Skill <- "articulation"
+data[grepl("d_", midFile)]$Skill <- "dynamics"
 
 # check correct or incorrect
-data$correct <- 0
-data[condition == "teaching" & rating == "Yes"]$correct <- 1
-data[condition == "performing" & rating == "No"]$correct <- 1
+data$Correct <- 0
+data[Condition == "teaching" & rating == "Yes"]$Correct <- 1
+data[Condition == "performing" & rating == "No"]$Correct <- 1
 
-all <- data[expMode == "experiment", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique)]
-all[order(subjectNumber, condition, technique)]
+all <- data[expMode == "experiment", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill)]
+all[order(subjectNumber, Condition, Skill)]
 ```
@@
 ## 1. Summary
-### all
+### All
 ```{r acc, echo = FALSE}
 # individual
-ind_data <- data[expMode == "experiment" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber)]
+ind_data <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber)]
 ind_data <- ind_data[order(subjectNumber)]
@@
 
-- Surprisingly, it showed a trend ( p = .06) but the 95% confidence interval overlaps with 50 %.
-
-### articulation vs. dynamics
+### Articulation vs. Dynamics
 
 ```{r plot2, echo = FALSE}
-ind_data_ad <- data[expMode == "experiment" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, technique)]
-ind_data_ad <- ind_data_ad[order(subjectNumber, technique)]
+ind_data_ad <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Skill)]
+ind_data_ad <- ind_data_ad[order(subjectNumber, Skill)]
 
-subset_ad <- ind_data_ad[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100), by = .(technique)]
+subset_ad <- ind_data_ad[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100), by = .(Skill)]
 subset_ad
 
-data_box <- data.table(subjectNumber = ind_data_ad$subjectNumber, articulation = ind_data_ad[technique == "articulation"]$Percent, dynamics = ind_data_ad[technique == "dynamics"]$Percent)
+data_box <- data.table(subjectNumber = ind_data_ad$subjectNumber, articulation = ind_data_ad[Skill == "articulation"]$Percent, dynamics = ind_data_ad[Skill == "dynamics"]$Percent)
 box <- ggpaired(data_box, cond1 = "articulation", cond2 = "dynamics", line.color = "gray", line.size = 0.4, ylab = "Correct %")
@@
 ## One-sample *t*-test
-### articulation
+### Articulation
 ```{r t-test-a, echo = FALSE}
 # normality check
-shapiro.test(ind_data_ad[technique == "articulation"]$Percent)
+shapiro.test(ind_data_ad[Skill == "articulation"]$Percent)
 
-t.test(ind_data_ad[technique == "articulation"]$Percent, mu = 50, alternative = "two.sided")
+t.test(ind_data_ad[Skill == "articulation"]$Percent, mu = 50, alternative = "two.sided")
 ```
@@
 
-### dynamics
+### Dynamics
 ```{r t-test-d, echo = FALSE}
 # normality check
-shapiro.test(ind_data_ad[technique == "dynamics"]$Percent)
+shapiro.test(ind_data_ad[Skill == "dynamics"]$Percent)
 
-t.test(ind_data_ad[technique == "dynamics"]$Percent, mu = 50, alternative = "two.sided")
+t.test(ind_data_ad[Skill == "dynamics"]$Percent, mu = 50, alternative = "two.sided")
 ```
-
-- The performance was significantly better than chance (p < .01).
 
@@
 # normality check
-shapiro.test(ind_data_ad[technique == "dynamics"]$Percent-ind_data_ad[technique == "articulation"]$Percent)
+shapiro.test(ind_data_ad[Skill == "dynamics"]$Percent-ind_data_ad[Skill == "articulation"]$Percent)
 
-t.test(ind_data_ad[technique == "articulation"]$Percent, ind_data_ad[technique == "dynamics"]$Percent, paired = TRUE)
+t.test(ind_data_ad[Skill == "articulation"]$Percent, ind_data_ad[Skill == "dynamics"]$Percent, paired = TRUE)
 ```
 
-- There was a difference between articulation and dynamics in terms of accuracy.
-
-## 2. teaching (each item)
-### all
+## 2. Teaching stimuli
+### All
 ```{r item1, echo = FALSE}
 # individual
-ind_data3 <- data[expMode == "experiment" & subjectNumber != 9 & condition == "teaching", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique, item)]
-ind_data3 <- ind_data3[order(subjectNumber, condition, technique, item)]
+ind_data2 <- data[subjectNumber != 9 & Condition == "teaching", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill, MidFile)]
+ind_data2 <- ind_data3[order(subjectNumber, Condition, Skill, MidFile)]
 
 # all
-subset3 <- ind_data3[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(condition, technique, item)]
-subset3[order(-Mean_Percent)]
+subset2 <- ind_data2[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
+subset2[order(-Mean_Percent)]
 ```
@@
 ```{r item1-a, echo = FALSE}
-subset3_a <- subset3[technique == "articulation"]
-subset3_a[order(-Mean_Percent)]
+subset2_a <- subset2[Skill == "articulation"]
+subset2_a$MidFile <- gsub("a_t_", "", subset2_a$MidFile)
+subset2_a[order(-Mean_Percent)]
 
-bar_a <- ggplot(subset3[technique == "articulation"], aes(x = reorder(item, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
+bar_a <- ggplot(subset2_a, aes(x = reorder(MidFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
 bar_a
@@
 ```{r item1-d, echo = FALSE}
-subset3_d <- subset3[order(-Mean_Percent) & technique == "dynamics"]
-subset3_d[order(-Mean_Percent)]
+subset2_d <- subset2[Skill == "dynamics"]
+subset2_d$MidFile <- gsub("d_t_", "", subset2_d$MidFile)
+subset2_d[order(-Mean_Percent)]
 
-bar_d <- ggplot(subset3[technique == "dynamics"], aes(x = reorder(item, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
+bar_d <- ggplot(subset2_d, aes(x = reorder(MidFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
 bar_d
@@
 # individual
-ind_data4 <- data[expMode == "experiment" & subjectNumber != 9 & condition == "performing", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique, item)]
-ind_data4 <- ind_data4[order(subjectNumber, condition, technique, item)]
+ind_data3 <- data[subjectNumber != 9 & Condition == "performing", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill, MidFile)]
+ind_data3 <- ind_data3[order(subjectNumber, Condition, Skill, MidFile)]
 
 # all
-subset4 <- ind_data4[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(condition, technique, item)]
-subset4[order(-Mean_Percent)]
+subset3 <- ind_data3[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
+subset3[order(-Mean_Percent)]
 ```
@@
 ```{r item2-a, echo = FALSE}
-subset4_a <- subset4[technique == "articulation"]
-subset4_a[order(-Mean_Percent)]
+subset3_a <- subset3[Skill == "articulation"]
+subset3_a$MidFile <- gsub("a_p_", "", subset3_a$MidFile)
+subset3_a[order(-Mean_Percent)]
 
-bar2_a <- ggplot(subset4[technique == "articulation"], aes(x = reorder(item, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
+bar2_a <- ggplot(subset3_a, aes(x = reorder(MidFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
 bar2_a
@@
 ```{r item2-d, echo = FALSE}
-subset4_d <- subset4[technique == "dynamics"]
-subset4_d[order(-Mean_Percent)]
+subset3_d <- subset3[Skill == "dynamics"]
+subset3_d$MidFile <- gsub("d_p_", "", subset3_d$MidFile)
+subset3_d[order(-Mean_Percent)]
 
-bar2_d <- ggplot(subset4[technique == "dynamics"], aes(x = reorder(item, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
+bar2_d <- ggplot(subset3_d, aes(x = reorder(MidFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
 bar2_d
@@
 ```{r export, include = FALSE}
-order_data <- rbind(
-  data.table(subset3_a$condition, subset3_a$technique, subset3_a$item, subset3_a$Mean_Percent),
-  data.table(subset3_d$condition, subset3_d$technique, subset3_d$item, subset3_d$Mean_Percent),
-  data.table(subset4_a$condition, subset4_a$technique, subset4_a$item, subset4_a$Mean_Percent),
-  data.table(subset4_d$condition, subset4_d$technique, subset4_d$item, subset4_d$Mean_Percent))
-
-colnames(order_data) <- c("condition", "technique", "item", "mean_percent")
+order_data <- rbind(subset2, subset3)
 

### 2021-01-25 analysis/analysis.Rmd
correct outlines
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ind_data2 <- data[subjectNumber != 9 & Condition == "teaching", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill, MidFile)]
-ind_data2 <- ind_data3[order(subjectNumber, Condition, Skill, MidFile)]
+ind_data2 <- ind_data2[order(subjectNumber, Condition, Skill, MidFile)]
 
@@
 
-### articulation
+### Articulation
 ```{r item1-a, echo = FALSE}
@@
 
-### dynamics
+### Dynamics
 ```{r item1-d, echo = FALSE}
@@
 
-## 3. performing (each item)
-### all
+## 3. Performing stimuli
+### All
 ```{r item2, echo = FALSE}
@@
 
-### articulation
+### Articulation
 ```{r item2-a, echo = FALSE}
@@
 
-### dynamics
+### Dynamics
 ```{r item2-d, echo = FALSE}

### 2021-01-25 analysis/analysis.Rmd
export judgements for teaching
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-## 1. Summary
+## 1. Statistics
 ### All
@@
 ## 2. Teaching stimuli
-### All
 ```{r item1, echo = FALSE}
@@
 subset2 <- ind_data2[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
-subset2[order(-Mean_Percent)]
 ```
@@
 ## 3. Performing stimuli
-### All
 ```{r item2, echo = FALSE}
@@
 subset3 <- ind_data3[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
-subset3[order(-Mean_Percent)]
 ```
@@
 
-```{r export, include = FALSE}
-order_data <- rbind(subset2, subset3)
+# Accuracy for each stimulus
+```{r export, echo = FALSE}
+accuracy_data <- rbind(subset2, subset3)
+accuracy_data <- accuracy_data[order(MidFile)]
+accuracy_data
 
 # export
-fwrite(order_data, file = "order_data.txt")
+fwrite(accuracy_data, file = "accuracy_data.txt")
 ```
+
+# Judged as "teaching" for each stimulus
+```{r teaching, echo = FALSE}
+data$Teaching <- 0
+data[rating == "Yes"]$Teaching <- 1
+
+# individual
+ind_data4 <- data[subjectNumber != 9, .(N = .N, Sum = sum(Teaching)), by = .(subjectNumber, Condition, Skill, MidFile)]
+ind_data4 <- ind_data4[order(subjectNumber)]
+
+# all
+subset4 <- ind_data4[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
+subset4 <- subset4[order(MidFile)]
+subset4
+
+# export
+fwrite(subset4, file = "teaching_data.txt")
+```

### 2021-01-25 analysis/stimuli/stimuli_analysis.Rmd
plot relations between each parameter and teaching judgment
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ---
-title: "Music Perception: Stimuli Analysis)"
+title: "Music Perception: Pilot Stimuli Analysis"
 output: html_notebook
@@
 
-I chose stimuli with the IOIs within 2sd randomly from each condition (teaching, performing), each technique (articulation, dynamics).
+# Experiment
 
-Note: SubNr 8 was excluded due to an experimental error, SubNr 16 was excluded due to a deviated tempo (see analysis for [music-teaching: experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1))
+## Stimuli
+- Stimuli were selected from the previous study ([the sound of teaching music/experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1)).
+- 48 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 96 stimuli).
+The half of them were selected from the teaching condition and the other half were from the performing condition.
+  + 24 for teaching-articulation performances
+  + 24 for performing-articulation performances
+  + 24 for teaching-dynamics performances
+  + 24 for performing-dynamics performances
+
+*Note: SubNr 8 was excluded due to an experimental error, SubNr 16 was excluded due to a deviated tempo (see analysis for [music-teaching: experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1))*
 
@@
 
+# Results
+- 1. [Accuracy](https://github.com/atsukotominaga/perception-v1.0/blob/master/analysis/analysis.Rmd)
+- 2. Exploratory analysis
+
+In order to see which stimulus was recognised as teaching performances, we decided to run exploratory analysis. We plotted correlations between each DV and the percentage of judgement as "teaching".
+
 ```{r setup, include = FALSE}
@@
 if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
-if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
+if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
 ```
@@
    current <- readMidi(paste("../../experiment/mid/", file, sep = ""))
-   current$midfile <- file
+   current$MidFile <- gsub(".mid", "", file)
    all_data <- rbind(all_data, current)
@@
 # labelling
-colnames(data)[c(3,4)] <- c("Pitch", "Velocity")
+colnames(data)[c(3,4)] <- c("Pitch", "Velocity") # time event also change
 data$Condition <- "NA"
 data$Skill <- "NA"
-data[midfile %like% "_t_"]$Condition <- "teaching"
-data[midfile %like% "_p_"]$Condition <- "performing"
-data[startsWith(midfile, "a_")]$Skill <- "articulation"
-data[startsWith(midfile, "d_")]$Skill <- "dynamics"
-
-# numbering
-instance = 1
-data$Instance <- 0
-for (file in unique(data$midfile)){
-   data[midfile == file]$Instance <- instance
-   instance = instance + 1
-}
+data[grepl("_t_", MidFile)]$Condition <- "teaching"
+data[grepl("_p_", MidFile)]$Condition <- "performing"
+data[grepl("a_", MidFile)]$Skill <- "articulation"
+data[grepl("d_", MidFile)]$Skill <- "dynamics"
 
@@
 
-# IOIs
+# IOIs (average tempo)
 ```{r ioi, include = FALSE}
@@
 
-# All
+```{r rating, include = FALSE}
+# rating as teaching
+rating <- fread("../teaching_data.txt")
+rating <- rating[order(MidFile)]
+```
+
+## All
+```{r ioi-all, echo = FALSE}
+ioi <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile)]
+
+# sorted
+ioi <- ioi[order(MidFile)]
+
+# plot
+ioi$Teaching <- rating$Mean_Percent
+ioi$TeachingSD <- rating$SD_Percent
+
+ggscatter(ioi, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+```
+
 ## Articulation
 ```{r ioi-all-art, echo = FALSE}
-ioi_art <- dt_ioi[Skill == "articulation"]
+ioi_art <- dt_ioi[Skill == "articulation", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile)]
 
+# sorted
+ioi_art <- ioi_art[order(MidFile)]
+
+# plot
+ioi_art$Teaching <- rating[Skill == "articulation"]$Mean_Percent
+ioi_art$TeachingSD <- rating[Skill == "articulation"]$SD_Percent
+
+ggscatter(ioi_art, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
 ```
@@
 ```{r ioi-all-dyn, echo = FALSE}
-ioi_dyn <- dt_ioi[Skill == "dynamics"]
+ioi_dyn <- dt_ioi[Skill == "dynamics", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile)]
 
+# sorted
+ioi_dyn <- ioi_dyn[order(MidFile)]
+
+# plot
+ioi_dyn$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
+ioi_dyn$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
+
+ggscatter(ioi_dyn, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
 ```
+
+# Transition points
+## All
+```{r ioi-tra-all, echo = FALSE}
+ioi_tra <- dt_ioi[Subcomponent == "LtoS" | Subcomponent == "StoL" | Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile)]
+
+# sorted
+ioi_tra <- ioi_tra[order(MidFile)]
+
+# plot
+ioi_tra$Teaching <- rating$Mean_Percent
+ioi_tra$TeachingSD <- rating$SD_Percent
+
+ggscatter(ioi_tra, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+```
+
+## Articulation
+```{r ioi-tra-art, echo = FALSE}
+ioi_tra_art <- dt_ioi[Subcomponent == "LtoS" | Subcomponent == "StoL", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile)]
+
+# sorted
+ioi_tra_art <- ioi_tra_art[order(MidFile)]
+
+# plot
+ioi_tra_art$Teaching <- rating[Skill == "articulation"]$Mean_Percent
+ioi_tra_art$TeachingSD <- rating[Skill == "articulation"]$SD_Percent
+
+ggscatter(ioi_tra_art, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+```
+
+## Dynamics
+```{r ioi-tra-dyn, echo = FALSE}
+ioi_tra_dyn <- dt_ioi[Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile)]
+
+# sorted
+ioi_tra_dyn <- ioi_tra_dyn[order(MidFile)]
+
+# plot
+ioi_tra_dyn$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
+ioi_tra_dyn$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
+
+ggscatter(ioi_tra_dyn, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+```
+
+# CV (tempo variability)
+## All
+```{r cv, echo = FALSE}
+cv <- dt_ioi[, .(N = .N, CV = sd(IOI)/mean(IOI)), by = .(MidFile)]
+
+# sorted
+cv <- cv[order(MidFile)]
+
+# plot
+cv$Teaching <- rating$Mean_Percent
+cv$TeachingSD <- rating$SD_Percent
+
+ggscatter(cv, x = "CV", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+```
+## Articulation
+```{r cv-art, echo = FALSE}
+cv_art <- dt_ioi[Skill == "articulation", .(N = .N, CV = sd(IOI)/mean(IOI)), by = .(MidFile)]
+
+# sorted
+cv_art <- cv_art[order(MidFile)]
+
+# plot
+cv_art$Teaching <- rating[Skill == "articulation"]$Mean_Percent
+cv_art$TeachingSD <- rating[Skill == "articulation"]$SD_Percent
+
+ggscatter(cv_art, x = "CV", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+```
+
+## Dynamics
+```{r cv-dyn, echo = FALSE}
+cv_dyn <- dt_ioi[Skill == "dynamics", .(N = .N, CV = sd(IOI)/mean(IOI)), by = .(MidFile)]
+
+# sorted
+cv_dyn <- cv_dyn[order(MidFile)]
+
+# plot
+cv_dyn$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
+cv_dyn$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
+
+ggscatter(cv_dyn, x = "CV", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+```
+
+# KOT (only articulation stimuli)
+```{r kot, include = FALSE}
+data_onset$KOT <- NA
+for (row in 1:nrow(data_onset)){
+   if (row < nrow(data_onset)){
+      data_onset$KOT[row+1] <- data_offset$time[row] - data_onset$time[row+1] # offset(n) - onset(n+1)
+   }
+}
+
+dt_kot <- data_onset[NoteNr != 17]
+dt_kot$Interval <- rep(1:66, nrow(dt_kot)/66)
+
+# assign Subcomponents
+dt_kot$Subcomponent <- "NA"
+# Legato
+for (phrase in 1:length(ls_legato)){
+   for (note in 1:length(ls_legato[[phrase]])){
+     dt_kot[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
+   }
+}
+# Staccato
+for (phrase in 1:length(ls_staccato)){
+   for (note in 1:length(ls_staccato[[phrase]])){
+     dt_kot[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
+   }
+}
+# Forte
+for (phrase in 1:length(ls_forte)){
+   for (note in 1:length(ls_forte[[phrase]])){
+     dt_kot[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
+   }
+}
+# Piano
+for (phrase in 1:length(ls_piano)){
+   for (note in 1:length(ls_piano[[phrase]])){
+     dt_kot[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
+   }
+}
+# assign Subcomponent Change
+for (number in change_1){
+   dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
+   dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
+}
+for (number in change_2){
+   dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
+   dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
+}
+```
+
+## Legato
+```{r kot-legato, echo = FALSE}
+kot_legato <- dt_kot[Subcomponent == "Legato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile)]
+
+# sorted
+kot_legato <- kot_legato[order(MidFile)]
+
+# plot
+kot_legato$Teaching <- rating[Skill == "articulation"]$Mean_Percent
+kot_legato$TeachingSD <- rating[Skill == "articulation"]$SD_Percent
+
+ggscatter(kot_legato, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+```
+## Staccato
+```{r kot-legato, echo = FALSE}
+kot_staccato <- dt_kot[Subcomponent == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile)]
+
+# sorted
+kot_staccato <- kot_staccato[order(MidFile)]
+
+# plot
+kot_staccato$Teaching <- rating[Skill == "articulation"]$Mean_Percent
+kot_staccato$TeachingSD <- rating[Skill == "articulation"]$SD_Percent
+
+ggscatter(kot_staccato, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+```
+# KV (only dynamics stimuli)
+## Forte
+```{r vel-forte, echo = FALSE}
+dt_vel <- data_onset
+# assign Subcomponents
+# for each note
+dt_vel$Subcomponent <- NA
+# Legato
+for (phrase in 1:length(ls_legato_2)){
+   for (note in 1:length(ls_legato_2[[phrase]])){
+     dt_vel$Subcomponent[dt_vel$Skill == "articulation" & dt_vel$Note == ls_legato_2[[phrase]][note]] <- "Legato"
+   }
+}
+# Staccato
+for (phrase in 1:length(ls_staccato_2)){
+   for (note in 1:length(ls_staccato_2[[phrase]])){
+     dt_vel$Subcomponent[dt_vel$Skill == "articulation" & dt_vel$Note == ls_staccato_2[[phrase]][note]] <- "Staccato"
+   }
+}
+# Forte
+for (phrase in 1:length(ls_forte_2)){
+   for (note in 1:length(ls_forte_2[[phrase]])){
+     dt_vel$Subcomponent[dt_vel$Skill == "dynamics" & dt_vel$Note == ls_forte_2[[phrase]][note]] <- "Forte"
+   }
+}
+# Piano
+for (phrase in 1:length(ls_piano_2)){
+   for (note in 1:length(ls_piano_2[[phrase]])){
+     dt_vel$Subcomponent[dt_vel$Skill == "dynamics" & dt_vel$Note == ls_piano_2[[phrase]][note]] <- "Piano"
+   }
+}
+
+vel_forte <- dt_vel[Subcomponent == "Forte", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(MidFile)]
+
+# sorted
+vel_forte <- vel_forte[order(MidFile)]
+
+# plot
+vel_forte$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
+vel_forte$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
+
+ggscatter(vel_forte, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+```
+
+## Piano
+```{r vel-piano, echo = FALSE}
+vel_piano <- dt_vel[Subcomponent == "Piano", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(MidFile)]
+
+# sorted
+vel_piano <- vel_piano[order(MidFile)]
+
+# plot
+vel_piano$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
+vel_piano$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
+
+ggscatter(vel_piano, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+```
+
+# KV-diff (dynamics)
+## Forte to Piano
+```{r vel-diff-forte, echo = FALSE}
+data_onset$Diff <- diff(c(0, data_onset$Velocity))
+dt_vel_diff <- data_onset[NoteNr != 1]
+# assign Interval
+dt_vel_diff$Interval <- rep(1:66, nrow(dt_vel_diff)/66)
+
+# for intervals
+dt_vel_diff$Subcomponent <- NA
+# Legato
+for (phrase in 1:length(ls_legato)){
+for (note in 1:length(ls_legato[[phrase]])){
+  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == ls_legato[[phrase]][note]] <- "Legato"
+}
+}
+# Staccato
+for (phrase in 1:length(ls_staccato)){
+for (note in 1:length(ls_staccato[[phrase]])){
+  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == ls_staccato[[phrase]][note]] <- "Staccato"
+}
+}
+# Forte
+for (phrase in 1:length(ls_forte)){
+for (note in 1:length(ls_forte[[phrase]])){
+  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == ls_forte[[phrase]][note]] <- "Forte"
+}
+}
+# Piano
+for (phrase in 1:length(ls_piano)){
+for (note in 1:length(ls_piano[[phrase]])){
+  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == ls_piano[[phrase]][note]] <- "Piano"
+}
+}
+# Assign Skill Change
+for (i in change_1){
+dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "LtoS"
+dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "FtoP"
+}
+for (i in change_2){
+dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "StoL"
+dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "PtoF"
+}
+
+vel_diff_ftop <- dt_vel_diff[Subcomponent == "FtoP", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(MidFile)]
+
+# sorted
+vel_diff_ftop <- vel_diff_ftop[order(MidFile)]
+
+# plot
+vel_diff_ftop$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
+vel_diff_ftop$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
+
+ggscatter(vel_diff_ftop, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+```
+
+## Piano to Forte
+```{r vel-diff-ptof, echo = FALSE}
+vel_diff_ptof <- dt_vel_diff[Subcomponent == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(MidFile)]
+
+# sorted
+vel_diff_ptof <- vel_diff_ptof[order(MidFile)]
+
+# plot
+vel_diff_ptof$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
+vel_diff_ptof$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
+
+ggscatter(vel_diff_ptof, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+```

### 2021-01-25 analysis/stimuli/stimuli_analysis.Rmd
plot relations between each parameter and teaching judgment
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-dt_kot <- data_onset[NoteNr != 17]
+dt_kot <- data_onset[NoteNr != 1]
 dt_kot$Interval <- rep(1:66, nrow(dt_kot)/66)
@@
 ## Staccato
-```{r kot-legato, echo = FALSE}
+```{r kot-staccato, echo = FALSE}
 kot_staccato <- dt_kot[Subcomponent == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile)]

### 2021-01-25 analysis/stimuli/stimuli_analysis.Rmd
add notes and fix ylim
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-# DVs
+## DVs
 - IOIs (average tempo)
@@
 
-# Results
+## Results
 - 1. [Accuracy](https://github.com/atsukotominaga/perception-v1.0/blob/master/analysis/analysis.Rmd)
+
+The accuracy results showed that it was not clear whether participants could detect teaching performances because the stimuli selection was not appropriate.
+
 - 2. Exploratory analysis
 
-In order to see which stimulus was recognised as teaching performances, we decided to run exploratory analysis. We plotted correlations between each DV and the percentage of judgement as "teaching".
+In order to see which stimulus was recognised as teaching performances, we decided to run exploratory analysis.
+We plotted correlations between each DV and the percentage of judgement as "teaching" regardless of their original conditions (i.e., teaching vs.
+performing).
 
@@
 
-# IOIs (average tempo)
+# IOIs
+- average tempo and teaching judgement
+
 ```{r ioi, include = FALSE}
@@
 ggscatter(ioi, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 ggscatter(ioi_art, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 ggscatter(ioi_dyn, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 # Transition points
+- tempo at transition points (e.g., legato to staccato / forte to piano) and teaching judgement
+
 ## All
@@
 ggscatter(ioi_tra, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 ggscatter(ioi_tra_art, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 ggscatter(ioi_tra_dyn, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 # CV (tempo variability)
+- tempo variability and teaching judgement
+
 ## All
@@
 ggscatter(cv, x = "CV", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 ggscatter(cv_art, x = "CV", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 ggscatter(cv_dyn, x = "CV", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 # KOT (only articulation stimuli)
+- articulation and teaching judgement
+
 ```{r kot, include = FALSE}
@@
 ggscatter(kot_legato, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 ggscatter(kot_staccato, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
 # KV (only dynamics stimuli)
+- dynamics and teaching judgement
+
 ## Forte
@@
 ggscatter(vel_forte, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 ggscatter(vel_piano, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 # KV-diff (dynamics)
+- dynamics changes at transition points (between forte and piano) and teaching judgement
+
 ## Forte to Piano
@@
 ggscatter(vel_diff_ftop, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "Velocity Difference (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 ggscatter(vel_diff_ptof, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE)
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "Velocity Difference (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```

### 2021-01-25 analysis/stimuli/stimuli_analysis.Rmd
add models
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
+if (!require("performance")) {install.packages("performance"); require("performance")}
 ```
@@
 - average tempo and teaching judgement
+- linear regression line (black) and 95% confidence interval (gray)
 
@@
 
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ Mean, data = ioi)
+check_normality(model)
+summary(model)
+r2(model)
+```
+
 ## Articulation
@@
 
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ Mean, data = ioi_art)
+check_normality(model)
+summary(model)
+r2(model)
+```
 ## Dynamics
@@
 
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ Mean, data = ioi_dyn)
+check_normality(model)
+summary(model)
+r2(model)
+```
+
 # Transition points
 - tempo at transition points (e.g., legato to staccato / forte to piano) and teaching judgement
+- linear regression line (black) and 95% confidence interval (gray)
 
@@
           xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```
+
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ Mean, data = ioi_tra)
+check_normality(model)
+summary(model)
+r2(model)
 ```
@@
 
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ Mean, data = ioi_tra_art)
+check_normality(model)
+summary(model)
+r2(model)
+```
 ## Dynamics
@@
 
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ Mean, data = ioi_tra_dyn)
+check_normality(model)
+summary(model)
+r2(model)
+```
+
 # CV (tempo variability)
 - tempo variability and teaching judgement
+- linear regression line (black) and 95% confidence interval (gray)
 
@@
 ```
+
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ CV, data = cv)
+check_normality(model)
+summary(model)
+r2(model)
+```
+
 ## Articulation
@@
           xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```
+
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ CV, data = cv_art)
+check_normality(model)
+summary(model)
+r2(model)
 ```
@@
 
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ CV, data = cv_dyn)
+check_normality(model)
+summary(model)
+r2(model)
+```
+
 # KOT (only articulation stimuli)
 - articulation and teaching judgement
+- linear regression line (black) and 95% confidence interval (gray)
 
@@
 ```
+
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ Mean, data = kot_legato)
+check_normality(model)
+summary(model)
+r2(model)
+```
+
 ## Staccato
@@
 ```
+
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ Mean, data = kot_staccato)
+check_normality(model)
+summary(model)
+r2(model)
+```
+
 # KV (only dynamics stimuli)
 - dynamics and teaching judgement
+- linear regression line (black) and 95% confidence interval (gray)
 
@@
 
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ Mean, data = vel_forte)
+check_normality(model)
+summary(model)
+r2(model)
+```
+
 ## Piano
@@
 
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ Mean, data = vel_piano)
+check_normality(model)
+summary(model)
+r2(model)
+```
+
 # KV-diff (dynamics)
 - dynamics changes at transition points (between forte and piano) and teaching judgement
+- linear regression line (black) and 95% confidence interval (gray)
 
@@
 
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ Mean, data = vel_diff_ftop)
+check_normality(model)
+summary(model)
+r2(model)
+```
+
 ## Piano to Forte
@@
 ```
+
+### Model
+```{r, echo = FALSE}
+model <- lm(Teaching ~ Mean, data = vel_diff_ptof)
+check_normality(model)
+summary(model)
+r2(model)
+```

### 2021-01-25 analysis/stimuli/stimuli_analysis.Rmd
correct xlab
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
-          xlab = "Velocity Difference (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```

### 2021-01-27 analysis/analysis.Rmd
update analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 - 48 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 96 stimuli).
-The half of them were selected from the teaching condition and the other half were from the performing condition.
+The half of them was selected from the teaching condition and the other half was from the performing condition.
   + 24 for teaching-articulation performances
@@
 
-- 2 blocks (articulation / dynamics): participants were asked to do the same task for two expressions separately. The order of the blocks was counterbalanced across participants.
-- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomised across participants.
+- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques (expressions) separately. The order of the blocks was counterbalanced across participants.
+- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented across participants.
 
@@
 ```
-Each performance was produced in order to either1) teach the musical expressive technique (as a teacher) 2) perform their best (as a performer).
+Each performance was produced in order to either 1) teach the musical expressive technique (as a teacher) or 2) perform their best (as a performer).
 
@@
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
-if (!require("afex")) {install.packages("afex"); require("afex")}
 ```
@@
 ```
-- Not significantly different from chance (p > .2).
 
@@
 
-# Accuracy for each stimulus
+# Accuracy (%) for each stimulus
 ```{r export, echo = FALSE}
@@
 
-# Judged as "teaching" for each stimulus
+# Judged as "teaching" (%) for each stimulus
 ```{r teaching, echo = FALSE}

### 2021-01-27 analysis/stimuli/stimuli_analysis.Rmd
update analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ## Results
-- 1. [Accuracy](https://github.com/atsukotominaga/perception-v1.0/blob/master/analysis/analysis.Rmd)
+- 1. [Accuracy (private repo)](https://github.com/atsukotominaga/perception-v1.0/blob/master/analysis/analysis.Rmd)
 
@@
 In order to see which stimulus was recognised as teaching performances, we decided to run exploratory analysis.
-We plotted correlations between each DV and the percentage of judgement as "teaching" regardless of their original conditions (i.e., teaching vs.
-performing).
+We plotted relationships between each DV and the percentage of judgement as "teaching" for each stimulus regardless of their original conditions (i.e., whether each stimulus was coming from the teaching or performing condition).
 

### 2021-02-07 material/expstimuli/selection/filtering_2sd.R
implement here()
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -8,6 +8,10 @@
 # This script organises raw data and randomly select performances which do not contain any pitch errors (IOIs within 2SD).
 # GitHub repo (private): https://github.com/atsukotominaga/perception-v1.0/tree/master/material/stimuli
 
+# set working directory
+if (!require("here")) {install.packages("here"); require("here")}
+here::i_am("filtering_2sd.R")
+
 # create folders if not exists
 if (!file.exists("2sd/")){
   dir.create("2sd")

### 2021-02-08 analysis/analysis.Rmd
move previous analysis to pilot folder
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-01-25 analysis/analysis.Rmd
@@
 ---
-title: "Music Perception: Pilot Accuracy Analysis"
-author: "Atsuko Tominaga"
+title: "Music Perception: Analysis"
 output: html_notebook
 ---
-
-- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`
-
-- 10 participants (experimental error = 1) >> 9 participants were included for analysis.
-
-# Experiment
-
-## Stimuli
-- Stimuli were selected from the previous study ([the sound of teaching music/experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1)).
-- 48 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 96 stimuli).
-The half of them were selected from the teaching condition and the other half were from the performing condition.
-  + 24 for teaching-articulation performances
-  + 24 for performing-articulation performances
-  + 24 for teaching-dynamics performances
-  + 24 for performing-dynamics performances
-
-## Design
-
-- 2 blocks (articulation / dynamics): participants were asked to do the same task for two expressions separately. The order of the blocks was counterbalanced across participants.
-- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomised across participants.
-
-## Procedure
-1. Musicians (> 6yo experience) were asked to listen to a number of recordings and judge whether each performance was produced for teaching purposes or not.
-
-Actual instruction:
-```
-Each performance was produced in order to either1) teach the musical expressive technique (as a teacher) 2) perform their best (as a performer).
-
-You will be asked to judge whether each performer had the intention to teach or not by pressing the 'Yes' <Left> or 'No' <Right> key.
-```
-
-2. Participants pressed "YES" if they think the recording was produced for teaching (as a teacher) whereas they pressed "NO" if they thought the recording was produced for performing (as a performer).
-
-3. Correct answers would be 1) participants pressed "YES" when they listened to teaching performances or 2) participants pressed "NO" when they listened to performing performances.
-
-```{r packages, include = FALSE}
-if (!require("data.table")) {install.packages("data.table"); require("data.table")}
-if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
-if (!require("afex")) {install.packages("afex"); require("afex")}
-```
-
-```{r read, include = FALSE}
-# read files and combine them
-data_ls <- list.files("data")
-combined <- lapply(data_ls, function(f){
-  fread(paste("data/", f, sep = ""), sep = ",")
-})
-all_data <- do.call(rbind.data.frame, combined)
-```
-
-# Results
-## Individual data
-```{r summary, echo = FALSE}
-# remove irrelevant strings
-data <- all_data[expMode == "experiment"]
-data$MidFile <- gsub("./mid/", "", data$midFile)
-data$MidFile <- gsub(".mid", "", data$MidFile)
-
-# name conditions
-data$Condition <- "NA"
-data$Skill <- "NA"
-data[grepl("_t_", midFile)]$Condition <- "teaching"
-data[grepl("_p_", midFile)]$Condition <- "performing"
-data[grepl("a_", midFile)]$Skill <- "articulation"
-data[grepl("d_", midFile)]$Skill <- "dynamics"
-
-# check correct or incorrect
-data$Correct <- 0
-data[Condition == "teaching" & rating == "Yes"]$Correct <- 1
-data[Condition == "performing" & rating == "No"]$Correct <- 1
-
-all <- data[expMode == "experiment", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill)]
-all[order(subjectNumber, Condition, Skill)]
-```
-
-## 1. Summary
-### All
-```{r acc, echo = FALSE}
-# individual
-ind_data <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber)]
-ind_data <- ind_data[order(subjectNumber)]
-
-# all
-subset <- ind_data[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/96)*100, SD_Percent = (sd(Sum)/96)*100)]
-subset
-```
-
-```{r plot, echo = FALSE}
-ggboxplot(ind_data, x = "N", y = "Percent", add = "dotplot", xlab = FALSE) + ylab("Correct %") + theme(axis.text.x = element_blank())
-```
-
-### One-sample *t*-test
-```{r t-test, echo = FALSE}
-# normality check
-shapiro.test(ind_data$Percent)
-
-t.test(ind_data$Percent, mu = 50, alternative = "two.sided")
-```
-
-### Articulation vs. Dynamics
-
-```{r plot2, echo = FALSE}
-ind_data_ad <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Skill)]
-ind_data_ad <- ind_data_ad[order(subjectNumber, Skill)]
-
-subset_ad <- ind_data_ad[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100), by = .(Skill)]
-subset_ad
-
-data_box <- data.table(subjectNumber = ind_data_ad$subjectNumber, articulation = ind_data_ad[Skill == "articulation"]$Percent, dynamics = ind_data_ad[Skill == "dynamics"]$Percent)
-box <- ggpaired(data_box, cond1 = "articulation", cond2 = "dynamics", line.color = "gray", line.size = 0.4, ylab = "Correct %")
-box
-```
-
-## One-sample *t*-test
-### Articulation
-```{r t-test-a, echo = FALSE}
-# normality check
-shapiro.test(ind_data_ad[Skill == "articulation"]$Percent)
-
-t.test(ind_data_ad[Skill == "articulation"]$Percent, mu = 50, alternative = "two.sided")
-```
-- Not significantly different from chance (p > .2).
-
-### Dynamics
-```{r t-test-d, echo = FALSE}
-# normality check
-shapiro.test(ind_data_ad[Skill == "dynamics"]$Percent)
-
-t.test(ind_data_ad[Skill == "dynamics"]$Percent, mu = 50, alternative = "two.sided")
-```
-
-## Paired *t*-test between articulation and dynamics
-```{r p-t-test, echo = FALSE}
-# normality check
-shapiro.test(ind_data_ad[Skill == "dynamics"]$Percent-ind_data_ad[Skill == "articulation"]$Percent)
-
-t.test(ind_data_ad[Skill == "articulation"]$Percent, ind_data_ad[Skill == "dynamics"]$Percent, paired = TRUE)
-```
-
-## 2. Teaching stimuli
-### All
-```{r item1, echo = FALSE}
-# individual
-ind_data2 <- data[subjectNumber != 9 & Condition == "teaching", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill, MidFile)]
-ind_data2 <- ind_data2[order(subjectNumber, Condition, Skill, MidFile)]
-
-# all
-subset2 <- ind_data2[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
-subset2[order(-Mean_Percent)]
-```
-
-### Articulation
-```{r item1-a, echo = FALSE}
-subset2_a <- subset2[Skill == "articulation"]
-subset2_a$MidFile <- gsub("a_t_", "", subset2_a$MidFile)
-subset2_a[order(-Mean_Percent)]
-
-bar_a <- ggplot(subset2_a, aes(x = reorder(MidFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
-bar_a
-```
-
-### Dynamics
-```{r item1-d, echo = FALSE}
-subset2_d <- subset2[Skill == "dynamics"]
-subset2_d$MidFile <- gsub("d_t_", "", subset2_d$MidFile)
-subset2_d[order(-Mean_Percent)]
-
-bar_d <- ggplot(subset2_d, aes(x = reorder(MidFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
-bar_d
-```
-
-## 3. Performing stimuli
-### All
-```{r item2, echo = FALSE}
-# individual
-ind_data3 <- data[subjectNumber != 9 & Condition == "performing", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill, MidFile)]
-ind_data3 <- ind_data3[order(subjectNumber, Condition, Skill, MidFile)]
-
-# all
-subset3 <- ind_data3[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
-subset3[order(-Mean_Percent)]
-```
-
-### Articulation
-```{r item2-a, echo = FALSE}
-subset3_a <- subset3[Skill == "articulation"]
-subset3_a$MidFile <- gsub("a_p_", "", subset3_a$MidFile)
-subset3_a[order(-Mean_Percent)]
-
-bar2_a <- ggplot(subset3_a, aes(x = reorder(MidFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
-bar2_a
-```
-
-### Dynamics
-```{r item2-d, echo = FALSE}
-subset3_d <- subset3[Skill == "dynamics"]
-subset3_d$MidFile <- gsub("d_p_", "", subset3_d$MidFile)
-subset3_d[order(-Mean_Percent)]
-
-bar2_d <- ggplot(subset3_d, aes(x = reorder(MidFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
-bar2_d
-```
-
-```{r export, include = FALSE}
-order_data <- rbind(subset2, subset3)
-
-# export
-fwrite(order_data, file = "order_data.txt")
-```

### 2021-02-08 analysis/analysis.Rmd
add color to scatterplots
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ---
+
+- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`
+
+- 21 participants (experimental error = 1) >> 20 participants were included for analysis.
+
+# Experiment
+
+## Stimuli
+- Stimuli were selected from the previous study ([the sound of teaching music/experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1)).
+- 48 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 96 stimuli).
+The half of them was selected from the teaching condition and the other half was from the performing condition.
+  + 24 for teaching-articulation performances
+  + 24 for performing-articulation performances
+  + 24 for teaching-dynamics performances
+  + 24 for performing-dynamics performances
+
+## Design
+
+- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques (expressions) separately. The order of the blocks was counterbalanced across participants.
+- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented across participants.
+
+## Procedure
+1. Musicians (> 6yo experience) were asked to listen to a number of recordings and judge whether each performance was produced for teaching purposes or not.
+
+Actual instruction:
+```
+Each performance was produced in order to either 1) teach the musical expressive technique (as a teacher) or 2) perform their best (as a performer).
+
+You will be asked to judge whether each performer had the intention to teach or not by pressing the 'Yes' <Left> or 'No' <Right> key.
+```
+
+2. Participants pressed "YES" if they think the recording was produced for teaching (as a teacher) whereas they pressed "NO" if they thought the recording was produced for performing (as a performer).
+
+3. Correct answers would be 1) participants pressed "YES" when they listened to teaching performances or 2) participants pressed "NO" when they listened to performing performances.
+
+## DVs
+- IOIs (tempo)
+- IOIs at transition points (tempo)
+- CV (tempo)
+- KOT (articulation)
+- KV (dynamics)
+- KV-Diff (dynamics)
+
+```{r packages, include = FALSE}
+# data manipulation
+if (!require("data.table")) {install.packages("data.table"); require("data.table")}
+# midi
+if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
+# plot
+if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
+# stats
+if (!require("performance")) {install.packages("performance"); require("performance")}
+```
+
+```{r read, include = FALSE}
+# read files and combine them
+data_ls <- list.files("data")
+combined <- lapply(data_ls, function(f){
+  fread(paste("data/", f, sep = ""), sep = ",")
+})
+all_data <- do.call(rbind.data.frame, combined)
+
+# remove irrelevant strings
+data <- all_data[expMode == "experiment"]
+data$MidFile <- gsub("./mid/", "", data$midFile)
+data$MidFile <- gsub(".mid", "", data$MidFile)
+
+# name conditions
+data$Condition <- "NA"
+data$Skill <- "NA"
+data[grepl("_t_", midFile)]$Condition <- "teaching"
+data[grepl("_p_", midFile)]$Condition <- "performing"
+data[grepl("a_", midFile)]$Skill <- "articulation"
+data[grepl("d_", midFile)]$Skill <- "dynamics"
+```
+
+# Judged as "teaching" (%) for each stimulus
+```{r teaching, echo = FALSE}
+data$Teaching <- 0
+data[rating == "Yes"]$Teaching <- 1
+
+# individual
+individual <- data[subjectNumber != 9, .(N = .N, Sum = sum(Teaching)), by = .(subjectNumber, Condition, Skill, MidFile)]
+individual<- individual[order(subjectNumber)]
+
+# all
+all <- individual[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
+all <- all[order(MidFile)]
+all
+```
+
+```{r midi, include = FALSE}
+# create a list of data file names
+lf <- list.files("../experiment/mid/", pattern = "mid")
+
+# combine data
+all_data <- data.table()
+for (file in lf){
+   current <- readMidi(paste("../experiment/mid/", file, sep = ""))
+   current$MidFile <- gsub(".mid", "", file)
+   all_data <- rbind(all_data, current)
+}
+
+data <- all_data[event == "Note On" | event == "Note Off"]
+data$NoteNr <- rep(1:134, nrow(data)/134)
+data$channel <- NULL
+data$parameterMetaSystem <- NULL
+data$track <- NULL
+data$type <- NULL
+
+# labelling
+colnames(data)[c(3,4)] <- c("Pitch", "Velocity") # time event also change
+data$Condition <- "NA"
+data$Skill <- "NA"
+data[grepl("_t_", MidFile)]$Condition <- "teaching"
+data[grepl("_p_", MidFile)]$Condition <- "performing"
+data[grepl("a_", MidFile)]$Skill <- "articulation"
+data[grepl("d_", MidFile)]$Skill <- "dynamics"
+
+# define subcomponents
+# For intervals
+ls_legato <- list(c(1:7), c(17:23), c(42:48), c(58:64))
+ls_staccato <- list(c(9:15), c(25:31), c(34:40), c(50:56))
+ls_forte <- list(c(1:7), c(17:23), c(42:48), c(58:64))
+ls_piano <- list(c(9:15), c(25:31), c(34:40), c(50:56))
+
+# For each note (velocity only)
+ls_legato_2 <- list(c(1:8), c(17:24), c(42:49), c(58:65))
+ls_staccato_2 <- list(c(9:16), c(25:32), c(34:41), c(50:57))
+ls_forte_2 <- list(c(1:8), c(17:24), c(42:49), c(58:65))
+ls_piano_2 <- list(c(9:16), c(25:32), c(34:41), c(50:57))
+
+# Define Skill Change (LtoS, FtoP)
+change_1 <- c(8, 24, 49)
+# Define Skill Change (StoL, PtoF)
+change_2 <- c(16, 41, 57)
+```
+
+# IOIs
+- average tempo and teaching judgement
+- linear regression line (black) and 95% confidence interval (gray)
+
+```{r ioi, include = FALSE}
+data_onset <- data[event == "Note On"]
+data_offset <- data[event == "Note Off"]
+
+data_onset$IOI <- diff(c(0, data_onset$time))
+dt_ioi <- data_onset[NoteNr != 1]
+dt_ioi$Interval <- rep(1:66, nrow(dt_ioi)/66)
+
+# assign Subcomponents
+dt_ioi$Subcomponent <- "NA"
+# Legato
+for (phrase in 1:length(ls_legato)){
+ for (note in 1:length(ls_legato[[phrase]])){
+   dt_ioi[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
+ }
+}
+# Staccato
+for (phrase in 1:length(ls_staccato)){
+ for (note in 1:length(ls_staccato[[phrase]])){
+   dt_ioi[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
+ }
+}
+
+# Forte
+for (phrase in 1:length(ls_forte)){
+ for (note in 1:length(ls_forte[[phrase]])){
+   dt_ioi[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
+ }
+}
+# Piano
+for (phrase in 1:length(ls_piano)){
+ for (note in 1:length(ls_piano[[phrase]])){
+   dt_ioi[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
+ }
+}
+
+# assign Subcomponent Change
+for (number in change_1){
+ dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
+ dt_ioi[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
+}
+for (number in change_2){
+ dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
+ dt_ioi[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
+}
+```
+
+## All
+```{r ioi-all, echo = FALSE}
+rating <- all # rating data
+
+ioi <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill)]
+
+# sorted
+ioi <- ioi[order(MidFile)]
+
+# plot
+ioi$Teaching <- rating$Mean_Percent
+ioi$TeachingSD <- rating$SD_Percent
+
+ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```
+
+# Tempo at transition points
+- tempo at transition points (e.g., legato to staccato / forte to piano) and teaching judgement
+- linear regression line (black) and 95% confidence interval (gray)
+
+## All
+```{r ioi-tra-all, echo = FALSE}
+ioi_tra <- dt_ioi[Subcomponent == "LtoS" | Subcomponent == "StoL" | Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill)]
+
+# sorted
+ioi_tra <- ioi_tra[order(MidFile)]
+
+# plot
+ioi_tra$Teaching <- rating$Mean_Percent
+ioi_tra$TeachingSD <- rating$SD_Percent
+
+ggscatter(ioi_tra, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```
+
+# CV (tempo variability)
+- tempo variability and teaching judgement
+- linear regression line (black) and 95% confidence interval (gray)
+
+## All
+```{r cv, echo = FALSE}
+cv <- dt_ioi[, .(N = .N, CV = sd(IOI)/mean(IOI)), by = .(MidFile, Skill)]
+
+# sorted
+cv <- cv[order(MidFile)]
+
+# plot
+cv$Teaching <- rating$Mean_Percent
+cv$TeachingSD <- rating$SD_Percent
+
+ggscatter(cv, x = "CV", y = "Teaching", color = "Skill", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```
+
+# KOT
+- articulation and teaching judgement
+- linear regression line (black) and 95% confidence interval (gray)
+
+```{r kot, include = FALSE}
+data_onset$KOT <- NA
+for (row in 1:nrow(data_onset)){
+   if (row < nrow(data_onset)){
+      data_onset$KOT[row+1] <- data_offset$time[row] - data_onset$time[row+1] # offset(n) - onset(n+1)
+   }
+}
+
+dt_kot <- data_onset[NoteNr != 1]
+dt_kot$Interval <- rep(1:66, nrow(dt_kot)/66)
+
+# assign Subcomponents
+dt_kot$Subcomponent <- "NA"
+# Legato
+for (phrase in 1:length(ls_legato)){
+   for (note in 1:length(ls_legato[[phrase]])){
+     dt_kot[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
+   }
+}
+# Staccato
+for (phrase in 1:length(ls_staccato)){
+   for (note in 1:length(ls_staccato[[phrase]])){
+     dt_kot[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
+   }
+}
+# Forte
+for (phrase in 1:length(ls_forte)){
+   for (note in 1:length(ls_forte[[phrase]])){
+     dt_kot[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
+   }
+}
+# Piano
+for (phrase in 1:length(ls_piano)){
+   for (note in 1:length(ls_piano[[phrase]])){
+     dt_kot[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
+   }
+}
+# assign Subcomponent Change
+for (number in change_1){
+   dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
+   dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
+}
+for (number in change_2){
+   dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
+   dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
+}
+```
+
+## All
+```{r kot-all, echo = FALSE}
+kot_all <- dt_kot[Subcomponent == "Legato" | Subcomponent == "Staccato" | Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile, Subcomponent)]
+
+# sorted
+kot_all <- kot_all[order(MidFile)]
+
+# plot
+kot_all$Teaching <- rep(rating$Mean_Percent, each = 2)
+kot_all$TeachingSD <- rep(rating$SD_Percent, each = 2)
+
+ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```
+
+## Legato
+```{r kot-legato, echo = FALSE}
+kot_legato <- dt_kot[Subcomponent == "Legato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile)]
+
+# sorted
+kot_legato <- kot_legato[order(MidFile)]
+
+# plot
+kot_legato$Teaching <- rating[Skill == "articulation"]$Mean_Percent
+kot_legato$TeachingSD <- rating[Skill == "articulation"]$SD_Percent
+
+ggscatter(kot_legato, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```
+
+## Staccato
+```{r kot-staccato, echo = FALSE}
+kot_staccato <- dt_kot[Subcomponent == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile)]
+
+# sorted
+kot_staccato <- kot_staccato[order(MidFile)]
+
+# plot
+kot_staccato$Teaching <- rating[Skill == "articulation"]$Mean_Percent
+kot_staccato$TeachingSD <- rating[Skill == "articulation"]$SD_Percent
+
+ggscatter(kot_staccato, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```
+
+# KV
+- dynamics and teaching judgement
+- linear regression line (black) and 95% confidence interval (gray)
+
+```{r vel, include = FALSE}
+dt_vel <- data_onset
+# assign Subcomponents
+# for each note
+dt_vel$Subcomponent <- NA
+# Legato
+for (phrase in 1:length(ls_legato_2)){
+   for (note in 1:length(ls_legato_2[[phrase]])){
+     dt_vel$Subcomponent[dt_vel$Skill == "articulation" & dt_vel$Note == ls_legato_2[[phrase]][note]] <- "Legato"
+   }
+}
+# Staccato
+for (phrase in 1:length(ls_staccato_2)){
+   for (note in 1:length(ls_staccato_2[[phrase]])){
+     dt_vel$Subcomponent[dt_vel$Skill == "articulation" & dt_vel$Note == ls_staccato_2[[phrase]][note]] <- "Staccato"
+   }
+}
+# Forte
+for (phrase in 1:length(ls_forte_2)){
+   for (note in 1:length(ls_forte_2[[phrase]])){
+     dt_vel$Subcomponent[dt_vel$Skill == "dynamics" & dt_vel$Note == ls_forte_2[[phrase]][note]] <- "Forte"
+   }
+}
+# Piano
+for (phrase in 1:length(ls_piano_2)){
+   for (note in 1:length(ls_piano_2[[phrase]])){
+     dt_vel$Subcomponent[dt_vel$Skill == "dynamics" & dt_vel$Note == ls_piano_2[[phrase]][note]] <- "Piano"
+   }
+}
+```
+
+## All
+```{r vel-all, echo = FALSE}
+vel_all <- dt_vel[Subcomponent == "Legato" | Subcomponent == "Staccato" | Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(MidFile, Subcomponent)]
+
+# sorted
+vel_all <- vel_all[order(MidFile)]
+
+# plot
+vel_all$Teaching <- rep(rating$Mean_Percent, each = 2)
+vel_all$TeachingSD <- rep(rating$SD_Percent, each = 2)
+
+ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```
+
+## Forte
+```{r vel-forte, echo = FALSE}
+vel_forte <- dt_vel[Subcomponent == "Forte", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(MidFile)]
+
+# sorted
+vel_forte <- vel_forte[order(MidFile)]
+
+# plot
+vel_forte$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
+vel_forte$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
+
+ggscatter(vel_forte, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```
+
+## Piano
+```{r vel-piano, echo = FALSE}
+vel_piano <- dt_vel[Subcomponent == "Piano", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(MidFile)]
+
+# sorted
+vel_piano <- vel_piano[order(MidFile)]
+
+# plot
+vel_piano$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
+vel_piano$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
+
+ggscatter(vel_piano, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```
+
+# KV-diff
+- dynamics changes at transition points (between forte and piano) and teaching judgement
+- linear regression line (black) and 95% confidence interval (gray)
+
+```{r vel-diff, include = FALSE}
+data_onset$Diff <- diff(c(0, data_onset$Velocity))
+dt_vel_diff <- data_onset[NoteNr != 1]
+# assign Interval
+dt_vel_diff$Interval <- rep(1:66, nrow(dt_vel_diff)/66)
+
+# for intervals
+dt_vel_diff$Subcomponent <- NA
+# Legato
+for (phrase in 1:length(ls_legato)){
+for (note in 1:length(ls_legato[[phrase]])){
+  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == ls_legato[[phrase]][note]] <- "Legato"
+}
+}
+# Staccato
+for (phrase in 1:length(ls_staccato)){
+for (note in 1:length(ls_staccato[[phrase]])){
+  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == ls_staccato[[phrase]][note]] <- "Staccato"
+}
+}
+# Forte
+for (phrase in 1:length(ls_forte)){
+for (note in 1:length(ls_forte[[phrase]])){
+  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == ls_forte[[phrase]][note]] <- "Forte"
+}
+}
+# Piano
+for (phrase in 1:length(ls_piano)){
+for (note in 1:length(ls_piano[[phrase]])){
+  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == ls_piano[[phrase]][note]] <- "Piano"
+}
+}
+# Assign Skill Change
+for (i in change_1){
+dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "LtoS"
+dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "FtoP"
+}
+for (i in change_2){
+dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "StoL"
+dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "PtoF"
+}
+```
+
+## All
+```{r vel-diff-all, echo = FALSE}
+vel_diff_all <- dt_vel_diff[Subcomponent == "FtoP" | Subcomponent == "PtoF" | Subcomponent == "LtoS" | Subcomponent == "StoL", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(MidFile, Subcomponent)]
+
+# sorted
+vel_diff_all <- vel_diff_all[order(MidFile)]
+
+# plot
+vel_diff_all$Teaching <- rep(rating$Mean_Percent, each = 2)
+vel_diff_all$TeachingSD <- rep(rating$SD_Percent, each = 2)
+
+ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
+          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```
+
+## Forte to Piano
+```{r vel-diff-forte, echo = FALSE}
+vel_diff_ftop <- dt_vel_diff[Subcomponent == "FtoP", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(MidFile)]
+
+# sorted
+vel_diff_ftop <- vel_diff_ftop[order(MidFile)]
+
+# plot
+vel_diff_ftop$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
+vel_diff_ftop$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
+
+ggscatter(vel_diff_ftop, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```
+
+## Piano to Forte
+```{r vel-diff-ptof, echo = FALSE}
+vel_diff_ptof <- dt_vel_diff[Subcomponent == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(MidFile)]
+
+# sorted
+vel_diff_ptof <- vel_diff_ptof[order(MidFile)]
+
+# plot
+vel_diff_ptof$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
+vel_diff_ptof$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
+
+ggscatter(vel_diff_ptof, x = "Mean", y = "Teaching", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```

### 2021-02-10 analysis/analysis.Rmd
add partial correlations/multiple regressions
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-## DVs
+## Variables
 - IOIs (tempo)
@@
 # stats
+if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
 if (!require("performance")) {install.packages("performance"); require("performance")}
@@
 
+# Results
+- significance levels: `***: 0.001, **: 0.01, *: 0.05`
+
+# 1. Correlations
+- Summaries of pure correlations between each parameter and the teaching judgement (**without controlling for potential third variables**)
+
 # IOIs
 - average tempo and teaching judgement
-- linear regression line (black) and 95% confidence interval (gray)
+- linear regression lines and 95% confidence interval (gray)
 
@@
 
-## All
+## All (***)
 ```{r ioi-all, echo = FALSE}
@@
 ```
+## Articulation (***)
+```{r, echo = FALSE}
+cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
+```
+
+## Dynamics (**)
+```{r, echo = FALSE}
+cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
+```
 
@@
 
-## All
+## All (***)
 ```{r ioi-tra-all, echo = FALSE}
@@
 
+## Articulation (***)
+```{r, echo = FALSE}
+cor.test(ioi_tra[Skill == "articulation"]$Teaching, ioi_tra[Skill == "articulation"]$Mean)
+```
+
+## Dynamics (**)
+```{r, echo = FALSE}
+cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean)
+```
+
 # CV (tempo variability)
 - tempo variability and teaching judgement
-- linear regression line (black) and 95% confidence interval (gray)
+- linear regression lines and 95% confidence interval (gray)
 
-## All
+## All (**)
 ```{r cv, echo = FALSE}
@@
 ```
+## Articulation (***)
+```{r, echo = FALSE}
+cor.test(cv[Skill == "articulation"]$Teaching, cv[Skill == "articulation"]$CV)
+```
+## Dynamics (n.s.)
+```{r, echo = FALSE}
+cor.test(cv[Skill == "dynamics"]$Teaching, cv[Skill == "dynamics"]$CV)
+```
 
@@
 - articulation and teaching judgement
-- linear regression line (black) and 95% confidence interval (gray)
+- linear regression lines and 95% confidence interval (gray)
 
@@
 ```{r kot-all, echo = FALSE}
-kot_all <- dt_kot[Subcomponent == "Legato" | Subcomponent == "Staccato" | Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile, Subcomponent)]
+kot_all <- dt_kot[Subcomponent == "Legato" | Subcomponent == "Staccato" | Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile, Skill, Subcomponent)]
 
@@
 
-ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line",
+ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
@@
 ```
-
-## Legato
-```{r kot-legato, echo = FALSE}
-kot_legato <- dt_kot[Subcomponent == "Legato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile)]
-
-# sorted
-kot_legato <- kot_legato[order(MidFile)]
-
-# plot
-kot_legato$Teaching <- rating[Skill == "articulation"]$Mean_Percent
-kot_legato$TeachingSD <- rating[Skill == "articulation"]$SD_Percent
-
-ggscatter(kot_legato, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+## Legato (**)
+```{r, echo = FALSE}
+cor.test(kot_all[Subcomponent == "Legato"]$Teaching, kot_all[Subcomponent == "Legato"]$Mean)
 ```
 
-## Staccato
-```{r kot-staccato, echo = FALSE}
-kot_staccato <- dt_kot[Subcomponent == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile)]
+## Staccato (***)
+```{r, echo = FALSE}
+cor.test(kot_all[Subcomponent == "Staccato"]$Teaching, kot_all[Subcomponent == "Staccato"]$Mean)
+```
 
-# sorted
-kot_staccato <- kot_staccato[order(MidFile)]
+## Forte (n.s.)
+```{r, echo = FALSE}
+cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean)
+```
 
-# plot
-kot_staccato$Teaching <- rating[Skill == "articulation"]$Mean_Percent
-kot_staccato$TeachingSD <- rating[Skill == "articulation"]$SD_Percent
-
-ggscatter(kot_staccato, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+## Piano (n.s.)
+```{r, echo = FALSE}
+cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean)
 ```
@@
 - dynamics and teaching judgement
-- linear regression line (black) and 95% confidence interval (gray)
+- linear regression lines and 95% confidence interval (gray)
 
@@
 ```{r vel-all, echo = FALSE}
-vel_all <- dt_vel[Subcomponent == "Legato" | Subcomponent == "Staccato" | Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(MidFile, Subcomponent)]
+vel_all <- dt_vel[Subcomponent == "Legato" | Subcomponent == "Staccato" | Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(MidFile, Skill, Subcomponent)]
 
@@
 
-ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line",
+ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
@@
 
-## Forte
-```{r vel-forte, echo = FALSE}
-vel_forte <- dt_vel[Subcomponent == "Forte", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(MidFile)]
-
-# sorted
-vel_forte <- vel_forte[order(MidFile)]
-
-# plot
-vel_forte$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
-vel_forte$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
-
-ggscatter(vel_forte, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
-          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+## Forte (n.s.)
+```{r, echo = FALSE}
+cor.test(vel_all[Subcomponent == "Forte"]$Teaching, vel_all[Subcomponent == "Forte"]$Mean)
 ```
 
-## Piano
-```{r vel-piano, echo = FALSE}
-vel_piano <- dt_vel[Subcomponent == "Piano", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(MidFile)]
-
-# sorted
-vel_piano <- vel_piano[order(MidFile)]
-
-# plot
-vel_piano$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
-vel_piano$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
-
-ggscatter(vel_piano, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
-          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+## Piano (n.s.)
+```{r, echo = FALSE}
+cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean)
+```
+## Legat (n.s.)
+```{r, echo = FALSE}
+cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean)
 ```
 
-# KV-diff
+## Staccato (n.s.)
+```{r, echo = FALSE}
+cor.test(vel_all[Subcomponent == "Staccato"]$Teaching, vel_all[Subcomponent == "Staccato"]$Mean)
+```
+
+# KV-Diff
 - dynamics changes at transition points (between forte and piano) and teaching judgement
-- linear regression line (black) and 95% confidence interval (gray)
+- linear regression lines and 95% confidence interval (gray)
 
@@
 ```{r vel-diff-all, echo = FALSE}
-vel_diff_all <- dt_vel_diff[Subcomponent == "FtoP" | Subcomponent == "PtoF" | Subcomponent == "LtoS" | Subcomponent == "StoL", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(MidFile, Subcomponent)]
+vel_diff_all <- dt_vel_diff[Subcomponent == "FtoP" | Subcomponent == "PtoF" | Subcomponent == "LtoS" | Subcomponent == "StoL", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(MidFile, Skill, Subcomponent)]
 
@@
 
-ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line",
+ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") +ylim(0, 100)
 ```
 
-## Forte to Piano
-```{r vel-diff-forte, echo = FALSE}
-vel_diff_ftop <- dt_vel_diff[Subcomponent == "FtoP", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(MidFile)]
-
-# sorted
-vel_diff_ftop <- vel_diff_ftop[order(MidFile)]
-
-# plot
-vel_diff_ftop$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
-vel_diff_ftop$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
-
-ggscatter(vel_diff_ftop, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
-          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+## Forte to Piano (***)
+```{r, echo = FALSE}
+cor.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching, vel_diff_all[Subcomponent == "FtoP"]$Mean)
 ```
 
-## Piano to Forte
-```{r vel-diff-ptof, echo = FALSE}
-vel_diff_ptof <- dt_vel_diff[Subcomponent == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(MidFile)]
+## Piano to Forte (***)
+```{r, echo = FALSE}
+cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean)
+```
+## Legato to Staccato (n.s.)
+```{r, echo = FALSE}
+cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean)
+```
 
-# sorted
-vel_diff_ptof <- vel_diff_ptof[order(MidFile)]
+## Staccato to Legato (n.s.)
+```{r, echo = FALSE}
+cor.test(vel_diff_all[Subcomponent == "StoL"]$Teaching, vel_diff_all[Subcomponent == "StoL"]$Mean)
+```
 
-# plot
-vel_diff_ptof$Teaching <- rating[Skill == "dynamics"]$Mean_Percent
-vel_diff_ptof$TeachingSD <- rating[Skill == "dynamics"]$SD_Percent
+# 2. Partical correlations (only for KOT, KV, KV-Diff)
+- Control for third variables
+- When investigating the effect of KOT, we control for IOIs and dynamics (KV, KV-Diff)
+- When investigating the effect of KV or KV-Diff, we control for IOIs and articulation (KOT)
 
-ggscatter(vel_diff_ptof, x = "Mean", y = "Teaching", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
-          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```{r partial, include = FALSE}
+partial <- dt_ioi[Subcomponent != "NA", .(N = .N, IOI = mean(IOI), IOISD = sd(IOI)), by = .(MidFile, Skill)]
+partial <- rbind(partial, partial)
+partial <- partial[order(MidFile)]
+
+partial$Subcomponent <- kot_all$Subcomponent
+partial$KOT <- kot_all$Mean
+partial$KOTSD <- kot_all$SD
+partial$KV <- vel_all$Mean
+partial$KVSD <- vel_all$SD
+partial$Subcomponent2 <- vel_diff_all$Subcomponent
+partial$KVDiff <- vel_diff_all$Mean
+partial$KVDiffSD <- vel_diff_all$SD
+
+partial$Teaching <- rep(rating$Mean_Percent, each = 2)
+partial$TeachingSD <- rep(rating$SD_Percent, each = 2)
 ```
+
+# KOT
+## Legato (**)
+```{r kot-partial-leg, echo = TRUE}
+pcor.test(partial[Subcomponent == "Legato"]$KOT, partial[Subcomponent == "Legato"]$Teaching, partial[Subcomponent == "Legato", c("IOI", "KV", "KVDiff")])
+```
+
+## Staccato (*)
+```{r kot-partial-sta, echo = TRUE}
+pcor.test(partial[Subcomponent == "Staccato"]$KOT, partial[Subcomponent == "Staccato"]$Teaching, partial[Subcomponent == "Staccato", c("IOI", "KV", "KVDiff")])
+```
+
+# KV
+## Forte (n.s.)
+```{r vel-partial-for, echo = TRUE}
+pcor.test(partial[Subcomponent == "Forte"]$KV, partial[Subcomponent == "Forte"]$Teaching, partial[Subcomponent == "Forte", c("IOI", "KOT", "KVDiff")])
+```
+
+## Piano (n.s.)
+```{r vel-partial-pia, echo = TRUE}
+pcor.test(partial[Subcomponent == "Piano"]$KV, partial[Subcomponent == "Piano"]$Teaching, partial[Subcomponent == "Piano", c("IOI", "KOT", "KVDiff")])
+```
+
+# KV-Diff
+## Forte to Piano (**)
+```{r vel-diff-partial-ftop, echo = TRUE}
+pcor.test(partial[Subcomponent2 == "FtoP"]$KVDiff, partial[Subcomponent2 == "FtoP"]$Teaching, partial[Subcomponent2 == "FtoP", c("IOI", "KOT", "KV")])
+```
+
+## Piano to Forte (***)
+```{r vel-diff-partial-ptof, echo = TRUE}
+pcor.test(partial[Subcomponent2 == "PtoF"]$KVDiff, partial[Subcomponent2 == "PtoF"]$Teaching, partial[Subcomponent2 == "PtoF", c("IOI", "KOT", "KV")])
+```
+
+# Multiple regressions
+Note: additive - **no interaction considered**
+
+## Legato
+```{r, echo = TRUE}
+m1 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Legato"])
+summary(m1)
+check_model(m1)
+```
+
+## Staccato
+```{r, echo = TRUE}
+m2 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Staccato"])
+summary(m2)
+check_model(m2)
+```
+
+## Forte
+```{r, echo = TRUE}
+m3 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Forte"])
+summary(m3)
+check_model(m3)
+```
+
+## Piano
+```{r, echo = TRUE}
+m4 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Piano"])
+summary(m4)
+check_model(m4)
+```

### 2021-02-17 analysis/analysis.Rmd
correct data table
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
+## Each subcomponent
+```{r ioi-sub, echo = FALSE}
+ioi_sub <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill, Subcomponent)]
+
+# sorted
+ioi <- ioi[order(MidFile)]
+
+# plot
+ioi$Teaching <- rating$Mean_Percent
+ioi$TeachingSD <- rating$SD_Percent
+
+ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+```
+
 # Tempo at transition points
@@
 dt_vel <- data_onset
+dt_vel$Note <- rep(1:67, nrow(dt_vel)/67)
 # assign Subcomponents
 # for each note
-dt_vel$Subcomponent <- NA
+dt_vel$Subcomponent <- "NA"
 # Legato
@@
    for (note in 1:length(ls_legato_2[[phrase]])){
-     dt_vel$Subcomponent[dt_vel$Skill == "articulation" & dt_vel$Note == ls_legato_2[[phrase]][note]] <- "Legato"
+     dt_vel[Skill == "articulation" & Note == ls_legato_2[[phrase]][note]]$Subcomponent <- "Legato"
    }
@@
    for (note in 1:length(ls_staccato_2[[phrase]])){
-     dt_vel$Subcomponent[dt_vel$Skill == "articulation" & dt_vel$Note == ls_staccato_2[[phrase]][note]] <- "Staccato"
+     dt_vel[Skill == "articulation" & Note == ls_staccato_2[[phrase]][note]]$Subcomponent <- "Staccato"
    }
@@
    for (note in 1:length(ls_forte_2[[phrase]])){
-     dt_vel$Subcomponent[dt_vel$Skill == "dynamics" & dt_vel$Note == ls_forte_2[[phrase]][note]] <- "Forte"
+     dt_vel[Skill == "dynamics" & Note == ls_forte_2[[phrase]][note]]$Subcomponent <- "Forte"
    }
@@
    for (note in 1:length(ls_piano_2[[phrase]])){
-     dt_vel$Subcomponent[dt_vel$Skill == "dynamics" & dt_vel$Note == ls_piano_2[[phrase]][note]] <- "Piano"
+     dt_vel[Skill == "dynamics" & Note == ls_piano_2[[phrase]][note]]$Subcomponent <- "Piano"
    }
@@
 
-## Forte (n.s.)
+## Forte (***)
 ```{r, echo = FALSE}
@@
 ```
-## Legat (n.s.)
+## Legato (n.s.)
 ```{r, echo = FALSE}
@@
 # for intervals
-dt_vel_diff$Subcomponent <- NA
+dt_vel_diff$Subcomponent <- "NA"
 # Legato
@@
 for (note in 1:length(ls_legato[[phrase]])){
-  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == ls_legato[[phrase]][note]] <- "Legato"
+  dt_vel_diff[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
 }
@@
 for (note in 1:length(ls_staccato[[phrase]])){
-  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == ls_staccato[[phrase]][note]] <- "Staccato"
+  dt_vel_diff[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
 }
@@
 for (note in 1:length(ls_piano[[phrase]])){
-  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == ls_piano[[phrase]][note]] <- "Piano"
+  dt_vel_diff[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
 }
@@
 for (i in change_1){
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "LtoS"
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "FtoP"
+dt_vel_diff[Skill == "articulation" & Interval == i]$Subcomponent <- "LtoS"
+dt_vel_diff[Skill == "dynamics" & Interval == i]$Subcomponent <- "FtoP"
 }
 for (i in change_2){
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "StoL"
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "PtoF"
+dt_vel_diff[Skill == "articulation" & Interval == i]$Subcomponent <- "StoL"
+dt_vel_diff[Skill == "dynamics" & Interval == i]$Subcomponent <- "PtoF"
 }
@@
 
-# 2. Partical correlations (only for KOT, KV, KV-Diff)
+# 2. Partical correlation (only for KOT, KV, KV-Diff)
 - Control for third variables
@@
 # KV
-## Forte (n.s.)
+## Forte (*)
 ```{r vel-partial-for, echo = TRUE}
@@
 # KV-Diff
-## Forte to Piano (**)
+## Forte to Piano (n.s.)
 ```{r vel-diff-partial-ftop, echo = TRUE}
@@
 
-# Multiple regressions
+# Multiple regression
 Note: additive - **no interaction considered**

### 2021-02-21 material/expstimuli/stimuli.Rmd
add stimli selection and info
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: "Music Perception: Stimuli profiles"
output: html_notebook
---

- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`

I chose stimuli with the IOIs within 2sd randomly from each condition (teaching, performing), each technique (articulation, dynamics).

Note: SubNr 3 was excluded due to insufficient motor skills (see analysis for [music-teaching: experiment-2](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2))

# DVs
- IOIs (average tempo)
- Transition points
- CV (tempo variability)
- KOR (articulation)
- KV (dynamics)
- KV-diff (dynamics)

```{r filtering, include = FALSE}
foldername = paste(format(Sys.time(), "%s-%d%m%y"), "/", sep = "") # current time

# create folders if not exists
if (!file.exists(foldername)){
  dir.create(foldername)
  dir.create(paste(foldername, "practice", sep = ""))
}

if (!file.exists(paste(foldername, "art_teaching", sep = ""))){
  dir.create(paste(foldername, "art_teaching", sep = ""))
  dir.create(paste(foldername, "practice/art_teaching", sep = ""))
}

if (!file.exists(paste(foldername, "dyn_teaching", sep = ""))){
  dir.create(paste(foldername, "dyn_teaching", sep = ""))
  dir.create(paste(foldername, "practice/dyn_teaching", sep = ""))
}

if (!file.exists(paste(foldername, "art_performing"))){
  dir.create(paste(foldername, "art_performing", sep = ""))
  dir.create(paste(foldername, "practice/art_performing", sep = ""))
}

if (!file.exists(paste(foldername, "dyn_performing"))){
  dir.create(paste(foldername, "dyn_performing", sep = ""))
  dir.create(paste(foldername, "practice/dyn_performing", sep = ""))
}

# read functions
source("./function.R")

# read a text file for ideal performance
dt_ideal <- read.table("./ideal.txt")
colnames(dt_ideal) <- "Pitch"
dt_ideal$RowNr <- 1:nrow(dt_ideal)
setcolorder(dt_ideal, c(2, 1))

# create a list of data file names
lf <- list.files("./raw_data", pattern = "txt")

# create raw_data - merge all data files into one
raw_data <- data.table()
for (i in 1:length(lf)){
  data_i <- fread(file.path("./raw_data", lf[i]), header = F, sep = " ", dec = ".")
  raw_data <- rbind(raw_data, data_i)
}

# add column namesls
colnames(raw_data) <- c("NoteNr", "TimeStamp", "Pitch", "Velocity", "Key_OnOff", "Device", "Tempo", "SubNr", "BlockNr", "TrialNr", "Skill", "Condition", "Image")

# clean raw_data
raw_data$NoteNr <- as.numeric(gsub(",", "", raw_data$NoteNr))
raw_data$Image <- gsub(";", "", raw_data$Image)

# sort by SubNr, BlockNr, TrialNr
raw_data <- raw_data[order(raw_data$SubNr, raw_data$BlockNr, raw_data$TrialNr),]

# correct labelling (due to a labelling error of the original study)
# articulation
dt_a <- raw_data[grepl("stim_a", Image)]
# correct wrong labelling
dt_a$Skill <- "articulation"

# dynamics
dt_d <- raw_data[grepl("stim_d", Image)]
# correct wrong labelling
dt_d$Skill <- "dynamics"

# bind data frames for articulation and dynamics
dt_all <- rbind(dt_a, dt_d)

# raw_data without metronome
dt_all <- dt_all[Pitch != 31 & Pitch != 34]

# onset and offset
dt_onset <- dt_all[Key_OnOff == 1]
dt_offset <- dt_all[Key_OnOff == 0]

# 1. Detect error trials
dt_error_onset <- checker(dt_onset, dt_ideal)
dt_error_offset <- checker(dt_offset, dt_ideal)

# combine onset/offset
dt_error <- rbind(dt_error_onset, dt_error_offset)
dt_error$Duplicate <- duplicated(dt_error)

# exclude error performances
dt_exclude <- dt_error[Duplicate == FALSE]

# mark imperfect performances
dt_all$Error <- 0
for (error in 1:nrow(dt_exclude)){
  dt_all[SubNr == dt_exclude$SubNr[error] & BlockNr == dt_exclude$BlockNr[error] & TrialNr == dt_exclude$TrialNr[error]]$Error <- 1
}
dt_include <- dt_all[Error == 0]

# exclude IOIs +/- 3SD
dt_ioi <- dt_include[Key_OnOff == 1]
dt_ioi$IOI <- diff(c(0, dt_ioi$TimeStamp))
dt_ioi <- dt_ioi[NoteNr != 17] # remove irrelevant notes
dt_ioi$Interval <- rep(1:71, nrow(dt_ioi)/71)

# convert bpm to ms
dt_ioi[Tempo == 120]$Tempo <- 250
dt_ioi[Tempo == 110]$Tempo <- 273
dt_ioi[Tempo == 100]$Tempo <- 300

# normalise IOIs
dt_ioi$normIOI <- dt_ioi$IOI/dt_ioi$Tempo

ioi <- dt_ioi[Interval != 25 & Interval != 26 & Interval != 27 & Interval != 28 & Interval != 32 & Interval != 33 & Interval != 34 & Interval != 35 & Interval != 51 & Interval != 52 & Interval != 56 & Interval != 57 & Interval != 65 & Interval != 66 & Interval != 67 & Interval != 68 & Interval != 69 & Interval != 70 & Interval != 71, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, BlockNr, TrialNr)]
mean_ioi <- mean(ioi$Mean)
sd_ioi <- sd(ioi$Mean)
ioi_include <- ioi[Mean < mean_ioi+2*sd_ioi & Mean > mean_ioi-2*sd_ioi]

dt_include_updated <- data.table()
for (row in 1:nrow(ioi_include)){
  subnr = ioi_include$SubNr[row]
  block = ioi_include$BlockNr[row]
  trial = ioi_include$TrialNr[row]

  current <- dt_include[SubNr == subnr & BlockNr == block & TrialNr == trial]
  dt_include_updated <- rbind(dt_include_updated, current)
}
```

```{r selection, include = FALSE}
# create a list for included performances
list_include <- dt_include_updated[, .N, by = .(SubNr, BlockNr, TrialNr, Condition, Skill)]
list_overall <- list_include[, .N, by = .(Condition, Skill)]

# assign random numbers for performances in each category
list_include$RandNr <- 0
for (cond in c("teaching", "performing")){
  for (skill in c("articulation", "dynamics")){
    list_include[Condition == cond & Skill == skill]$RandNr <- sample(nrow(list_include[Condition == cond & Skill == skill]), replace = FALSE)
  }
}
list_include <- list_include[order(RandNr),]
# stimuli for experimental trials
for (i in 1:96){ # 24 stimuli for each category
  subject = list_include$SubNr[i]
  block = list_include$BlockNr[i]
  trial = list_include$TrialNr[i]
  cond = list_include$Condition[i]
  skill = list_include$Skill[i]
  current <- dt_include[SubNr == subject & BlockNr == block & TrialNr == trial]
  firstTimestamp = current$TimeStamp[1]
  current$TimeStamp <- current$TimeStamp - firstTimestamp # start with time 0

  if (cond == "teaching" & skill == "articulation"){
    filename = paste(foldername, "art_teaching/", subject, block, trial, ".txt", sep = "")
  } else if (cond == "teaching" & skill == "dynamics"){
    filename = paste(foldername, "dyn_teaching/", subject, block, trial, ".txt", sep = "")
  } else if (cond == "performing" & skill == "articulation"){
    filename = paste(foldername, "art_performing/", subject, block, trial, ".txt", sep = "")
  } else if (cond == "performing" & skill == "dynamics"){
    filename = paste(foldername, "dyn_performing/", subject, block, trial, ".txt", sep = "")
  }
  fwrite(current, file = filename)
}

print("Experimental stimuli - Done! :)")

# stimuli for practice trials
for (i in 97:104){ # 4 stimuli for each category
  subject = list_include$SubNr[i]
  block = list_include$BlockNr[i]
  trial = list_include$TrialNr[i]
  cond = list_include$Condition[i]
  skill = list_include$Skill[i]
  current <- dt_include[SubNr == subject & BlockNr == block & TrialNr == trial]
  firstTimestamp = current$TimeStamp[1]
  current$TimeStamp <- current$TimeStamp - firstTimestamp # start with time 0

  if (cond == "teaching" & skill == "articulation"){
    filename = paste(foldername, "practice/art_teaching/", subject, block, trial, ".txt", sep = "")
  } else if (cond == "teaching" & skill == "dynamics"){
    filename = paste(foldername, "practice/dyn_teaching/", subject, block, trial, ".txt", sep = "")
  } else if (cond == "performing" & skill == "articulation"){
    filename = paste(foldername, "practice/art_performing/", subject, block, trial, ".txt", sep = "")
  } else if (cond == "performing" & skill == "dynamics"){
    filename = paste(foldername, "practice/dyn_performing/", subject, block, trial, ".txt", sep = "")
  }
  fwrite(current, file = filename)
}

print("Practice stimuli - Done! :)")
```

```{r stimuli, include = FALSE}
rm(list = ls()) # clear all

# packages
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}

# create a list of data file names
lf_a_t <- list.files("./1613936591-210221/art_teaching", pattern = "txt")
lf_a_p <- list.files("./1613936591-210221/art_performing", pattern = "txt")
lf_d_t <- list.files("./1613936591-210221/dyn_teaching", pattern = "txt")
lf_d_p <- list.files("./1613936591-210221/dyn_performing", pattern = "txt")

# merge all data files into one
data <- data.table()
for (i in 1:length(lf_a_t)){
 data_i <- fread(file.path("./1613936591-210221/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
 data_i$Instance <- i
 data <- rbind(data, data_i)
}
for (i in 1:length(lf_a_p)){
 data_i <- fread(file.path("./1613936591-210221/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
 data_i$Instance <- i
 data <- rbind(data, data_i)
}
for (i in 1:length(lf_d_t)){
 data_i <- fread(file.path("./1613936591-210221/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
 data_i$Instance <- i
 data <- rbind(data, data_i)
}
for (i in 1:length(lf_d_p)){
 data_i <- fread(file.path("./1613936591-210221/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
 data_i$Instance <- i
 data <- rbind(data, data_i)
}

# define subcomponents
# for intervals
ls_legato <- list(c(1:4), c(9:16), c(21:24), c(40:46))
ls_staccato <- list(c(6:7), c(18:19), c(29:31), c(36:38), c(48:50), c(53:55), c(58:64))
ls_forte <- list(c(1:4), c(9:16), c(21:24), c(40:46))
ls_piano <- list(c(6:7), c(18:19), c(29:31), c(36:38), c(48:50), c(53:55), c(58:64))

# for each note (velocity)
ls_legato2 <- list(c(1:5), c(9:17), c(21:26), c(40:47))
ls_staccato2 <- list(c(6:8), c(18:20), c(29:32), c(36:39), c(48:51), c(53:56), c(58:65))
ls_forte2 <- list(c(1:5), c(9:17), c(21:26), c(40:47))
ls_piano2 <- list(c(6:8), c(18:20), c(29:32), c(36:39), c(48:51), c(53:56), c(58:65))

# define Component Change (LtoS, FtoP)
change_1 <- c(5, 17, 47)
# define Component Change (StoL, PtoF)
change_2 <- c(8, 20, 39)
```

# IOIs
```{r ioi, include = FALSE}
data_onset <- data[Key_OnOff == 1]
data_offset <- data[Key_OnOff == 0]

data_onset$IOI <- diff(c(0, data_onset$TimeStamp))
dt_ioi <- data_onset[NoteNr != 17]
dt_ioi$Interval <- rep(1:71, nrow(dt_ioi)/71)

# convert bpm to ms
dt_ioi[Tempo == 120]$Tempo <- 250
dt_ioi[Tempo == 110]$Tempo <- 273
dt_ioi[Tempo == 100]$Tempo <- 300

# normalise IOIs
dt_ioi$normIOI <- dt_ioi$IOI/dt_ioi$Tempo

# assign Subcomponents
dt_ioi$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato)){
 for (note in 1:length(ls_legato[[phrase]])){
   dt_ioi[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
 }
}
# Staccato
for (phrase in 1:length(ls_staccato)){
 for (note in 1:length(ls_staccato[[phrase]])){
   dt_ioi[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
 }
}

# Forte
for (phrase in 1:length(ls_forte)){
 for (note in 1:length(ls_forte[[phrase]])){
   dt_ioi[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
 }
}
# Piano
for (phrase in 1:length(ls_piano)){
 for (note in 1:length(ls_piano[[phrase]])){
   dt_ioi[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
 }
}

# assign Subcomponent Change
for (number in change_1){
 dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
 dt_ioi[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
}
for (number in change_2){
 dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
 dt_ioi[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
}

ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(Instance, Condition, Skill)]
```

## Each instance
```{r ioi-each, echo = FALSE}
ioi
```

## Averaged
```{r ioi-averaged, echo = FALSE}
ioi[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), .(Condition, Skill)]
```

## Plot
```{r plot-ioi, echo = FALSE}
ggboxplot(ioi, x = "Condition", y = "Mean", color = "Condition", facet.by = "Skill", add = "jitter")
```

# KOR
```{r kor, include = FALSE}
data_onset$KOT <- NA
for (row in 1:nrow(data_onset)){
   if (row < nrow(data_onset)){
      data_onset$KOT[row+1] <- data_offset$TimeStamp[row] - data_onset$TimeStamp[row+1] # offset(n) - onset(n+1)
   }
}

ioi_forKOT <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(Instance, Condition, Skill)]

data_onset$KOR <- 0
for (cond in c("teaching", "performing")){
  for (skill in c("articulation", "dynamics")){
    for (i in c(1:24)){
      data_onset[Condition == cond & Skill == skill & Instance == i]$KOR <- data_onset[Condition == cond & Skill == skill & Instance == i]$KOT/ioi_forKOT[Condition == cond & Skill == skill & Instance == i]$Mean
    }
  }
}

dt_kor <- data_onset[NoteNr != 17]
dt_kor$Interval <- rep(1:71, nrow(dt_kor)/71)

# assign Subcomponents
dt_kor$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato)){
   for (note in 1:length(ls_legato[[phrase]])){
     dt_kor[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
   }
}
# Staccato
for (phrase in 1:length(ls_staccato)){
   for (note in 1:length(ls_staccato[[phrase]])){
     dt_kor[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
   }
}

# Forte
for (phrase in 1:length(ls_forte)){
   for (note in 1:length(ls_forte[[phrase]])){
     dt_kor[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
   }
}
# Piano
for (phrase in 1:length(ls_piano)){
   for (note in 1:length(ls_piano[[phrase]])){
     dt_kor[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
   }
}

# assign Subcomponent Change
for (number in change_1){
   dt_kor[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
   dt_kor[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
}
for (number in change_2){
   dt_kor[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
   dt_kor[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
}

kor <- dt_kor[Subcomponent != "NA" & Subcomponent != "LtoS" & Subcomponent != "StoL" & Subcomponent != "FtoP" & Subcomponent != "PtoF", .(N = .N, Mean = mean(KOR), SD = sd(KOR)), by = .(Instance, Condition, Skill, Subcomponent)]
```

## Each instance
```{r kor-each, echo = FALSE}
kor
```

## Averaged
```{r kor-averaged, echo = FALSE}
kor[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), .(Condition, Skill, Subcomponent)]
```

## Plot
### Articulation
```{r plot-kor-art, echo = FALSE}
ggboxplot(kor[Skill == "articulation"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
```

### Dynamics
```{r plot-kor-dyn, echo = FALSE}
ggboxplot(kor[Skill == "dynamics"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
```

# KV

```{r vel, include = FALSE}
dt_vel <- data_onset
dt_vel$Note <- rep(1:72, nrow(dt_vel)/72)

# assign Subcomponents
# for each note
dt_vel$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato2)){
   for (note in 1:length(ls_legato2[[phrase]])){
     dt_vel[Skill == "articulation" & Note == ls_legato2[[phrase]][note]]$Subcomponent <- "Legato"
   }
}
# Staccato
for (phrase in 1:length(ls_staccato2)){
   for (note in 1:length(ls_staccato2[[phrase]])){
     dt_vel[Skill == "articulation" & Note == ls_staccato2[[phrase]][note]]$Subcomponent <- "Staccato"
   }
}

# Forte
for (phrase in 1:length(ls_forte2)){
   for (note in 1:length(ls_forte2[[phrase]])){
     dt_vel[Skill == "dynamics" & Note == ls_forte2[[phrase]][note]]$Subcomponent <- "Forte"
   }
}

# Piano
for (phrase in 1:length(ls_piano2)){
   for (note in 1:length(ls_piano2[[phrase]])){
     dt_vel[Skill == "dynamics" & Note == ls_piano2[[phrase]][note]]$Subcomponent <- "Piano"
   }
}

vel <- dt_vel[Subcomponent != "NA", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(Instance, Condition, Skill, Subcomponent)]
```

## Each instance
```{r vel-each, echo = FALSE}
vel
```

## Averaged
```{r vel-averaged, echo = FALSE}
vel[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), .(Condition, Skill, Subcomponent)]
```

## Plot
### Dynamics
```{r plot-vel-dyn, echo = FALSE}
ggboxplot(vel[Skill == "dynamics"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
```

### Articulation
```{r plot-vel-art, echo = FALSE}
ggboxplot(vel[Skill == "articulation"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
```

# KV-Diff
```{r vel-diff, include = FALSE}
# calculate differences and remove the first note
dt_vel$Diff <- diff(c(0, dt_vel$Velocity))
dt_vel_diff <- dt_vel[Note != 1]
dt_vel$Diff <- NULL # remove Diff from dt_vel

# assign Interval
dt_vel_diff$Interval <- rep(1:71, nrow(dt_vel_diff)/71)

# assign Subcomponents
# for intervals
dt_vel_diff$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato)){
for (note in 1:length(ls_legato[[phrase]])){
  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == ls_legato[[phrase]][note]] <- "Legato"
}
}
# Staccato
for (phrase in 1:length(ls_staccato)){
for (note in 1:length(ls_staccato[[phrase]])){
  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == ls_staccato[[phrase]][note]] <- "Staccato"
}
}

# Forte
for (phrase in 1:length(ls_forte)){
for (note in 1:length(ls_forte[[phrase]])){
  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == ls_forte[[phrase]][note]] <- "Forte"
}
}
# Piano
for (phrase in 1:length(ls_piano)){
for (note in 1:length(ls_piano[[phrase]])){
  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == ls_piano[[phrase]][note]] <- "Piano"
}
}

# Assign Skill Change
for (i in change_1){
dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "LtoS"
dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "FtoP"
}
for (i in change_2){
dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "StoL"
dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "PtoF"
}

vel_diff <- dt_vel_diff[Subcomponent == "LtoS" | Subcomponent == "StoL" | Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(Instance, Condition, Skill, Subcomponent)]
```

## Each instance
```{r vel-diff-each, echo = FALSE}
vel_diff
```

## Averaged
```{r vel-diff-averaged, echo = FALSE}
vel_diff[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), .(Condition, Skill, Subcomponent)]
```

## Plot
### Dynamics
```{r plot-vel-diff-dyn, echo = FALSE}
ggboxplot(vel_diff[Skill == "dynamics"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
```

### Articulation
```{r plot-vel-diff-art, echo = FALSE}
ggboxplot(vel_diff[Skill == "articulation"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
```

### 2021-02-21 material/expstimuli/stimuli.Rmd
remove irrelevant variable names
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 # packages
+if (!require("data.table")) {install.packages("data.table"); require("data.table")}
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
@@
 # KV
-
 ```{r vel, include = FALSE}
@@
 # assign Subcomponents
-# for each note
 dt_vel$Subcomponent <- "NA"
@@
 # assign Subcomponents
-# for intervals
 dt_vel_diff$Subcomponent <- "NA"
@@
 for (note in 1:length(ls_forte[[phrase]])){
-  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == ls_forte[[phrase]][note]] <- "Forte"
+  dt_vel_diff[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
 }
@@
 
-# Assign Skill Change
+# assign Subcomponent Change
 for (i in change_1){
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "LtoS"
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "FtoP"
+dt_vel_diff[Skill == "articulation" & Interval == i]$Subcomponent <- "LtoS"
+dt_vel_diff[Skill == "dynamics" & Interval == i]$Subcomponent <- "FtoP"
 }
 for (i in change_2){
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "StoL"
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "PtoF"
+dt_vel_diff[Skill == "articulation" & Interval == i]$Subcomponent <- "StoL"
+dt_vel_diff[Skill == "dynamics" & Interval == i]$Subcomponent <- "PtoF"
 }

### 2021-02-21 material/expstimuli/selection/filtering_2sd.R
correct comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -96,7 +96,7 @@ dt_error_offset <- checker(dt_offset, dt_ideal)
 dt_error <- rbind(dt_error_onset, dt_error_offset)
 dt_error$Duplicate <- duplicated(dt_error)
 
-# exclude these performances
+# exclude error performances
 dt_exclude <- dt_error[Duplicate == FALSE]
 
 # mark imperfect performances
@@ -133,7 +133,7 @@ for (row in 1:nrow(ioi_include)){
 list_include <- dt_include_updated[, .N, by = .(SubNr, BlockNr, TrialNr, Condition, Skill)]
 list_overall <- list_include[, .N, by = .(Condition, Skill)]
 
-# assign random nubmers for performances in each category
+# assign random numbers for performances in each category
 list_include$RandNr <- 0
 for (cond in c("teaching", "performing")){
   for (skill in c("articulation", "dynamics")){

### 2021-02-21 material/expstimuli/selection/profile.Rmd
update stimuli profile
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-01-11 material/expstimuli/selection/analysis(2sd).Rmd
@@
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
-if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
+if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
 ```
@@
 # IOIs
-```{r ioi, include = FALSE}
+## Each instance
+```{r ioi, echo = FALSE}
 data_onset <- data[Key_OnOff == 1]
@@
 ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(Instance, Condition, Skill)]
-ioi_art <- ioi[Skill == "articulation", .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill)]
-ioi_dyn <- ioi[Skill == "dynamics", .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill)]
-```
-
-## Summary Stats
-### Individual
-```{r ioi_stats_ind, echo = FALSE}
 ioi
@@
 
-### Averaged
-```{r ioi_stats_all, echo = FALSE}
-ioi_art
-ioi_dyn
+## Averaged
+```{r ioi-averaged, echo = FALSE}
+ioi[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), .(Condition, Skill)]
 ```
@@
 ### Articulation
-```{r ioi_art_plot, echo = FALSE}
-p_ioi_art <- ggplot(ioi[Skill == "articulation"], aes(x = Instance, y = Mean, fill = Condition)) +
- geom_bar(stat = "identity", position = position_dodge()) +
- geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-               width = .2, position = position_dodge(.9)) +
- geom_hline(yintercept = 188, linetype = "dashed") +
- scale_x_continuous(breaks = seq(1:24)) +
- labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Articulation)")
-p_ioi_art
-
-p_ioi_art_all <- ggplot(ioi_art, aes(x = Skill, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   geom_hline(yintercept = 188, linetype = "dashed") +
-   labs(y = "IOI (ms)", subtitle = "IOI: Averaged (Articulation)")
-p_ioi_art_all
-```
-### Dynamics
-```{r ioi_dyn_plot, echo = FALSE}
-p_ioi_dyn <- ggplot(ioi[Skill == "dynamics"], aes(x = Instance, y = Mean, fill = Condition)) +
- geom_bar(stat = "identity", position = position_dodge()) +
- geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-               width = .2, position = position_dodge(.9)) +
- geom_hline(yintercept = 188, linetype = "dashed") +
- scale_x_continuous(breaks = seq(1:24)) +
- labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Dynamics)")
-p_ioi_dyn
-
-p_ioi_dyn_all <- ggplot(ioi_dyn, aes(x = Skill, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   geom_hline(yintercept = 188, linetype = "dashed") +
-   labs(y = "IOI (ms)", subtitle = "IOI: Averaged (Dynamics)")
-p_ioi_dyn_all
+```{r plot-ioi, echo = FALSE}
+ggboxplot(ioi, x = "Condition", y = "Mean", color = "Condition", facet.by = "Skill", add = "jitter")
 ```
 
-# KOT
+#Transition points
+## Each instance
+```{r transition, echo = FALSE}
+ioi_tra <- dt_ioi[Subcomponent == "LtoS" | Subcomponent == "StoL" | Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(Instance, Condition, Skill)]
+ioi_tra
+```
+
+## Averaged
+```{r transition-tats_all, echo = FALSE}
+ioi_tra[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), .(Condition, Skill)]
+```
+
+## Plots
+```{r plot-ioi-tra, echo = FALSE}
+ggboxplot(ioi_tra, x = "Condition", y = "Mean", color = "Condition", facet.by = "Skill", add = "jitter")
+```
+
+# CV
+## Each instance
+```{r cv, echo = FALSE}
+ioi_cv <- ioi
+ioi_cv$CV <- 0
+for (cond in c("teaching", "performing")){
+   for (skill in c("articulation", "dynamics")){
+      for (i in 1:24){
+         current <- dt_ioi[Condition == cond & Skill == skill & Instance == i]
+         ioi_cv[Condition == cond & Skill == skill & Instance == i]$CV <- sd(current$IOI)/ioi[Condition == cond & Skill == skill & Instance == i]$Mean
+      }
+   }
+}
+ioi_cv
+```
+
+## Averaged
+```{r ioi-cv, echo = FALSE}
+ioi_cv[, .(N = .N, Mean = mean(CV), SD = sd(CV)), .(Condition, Skill)]
+```
+
+## Plots
+```{r plot-ioi-cv, echo = FALSE}
+ggboxplot(ioi_cv, x = "Condition", y = "CV", color = "Condition", facet.by = "Skill", add = "jitter")
+```
+
+# KOT (only for articulation stimuli)
+## Each instance
 ```{r kot, include = FALSE}
@@
 
-kot <- dt_kot[Subcomponent == "Legato" | Subcomponent == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(Instance, Condition, Skill, Subcomponent)]
-kot_all <- kot[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Subcomponent)]
-```
-
-## Plots
-```{r kot_plot, echo = FALSE}
-p_kot <- ggplot(kot, aes(x = Instance, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
-   labs(y = "KOT (ms)", subtitle = "KOT: Each instance (Articulation)")
-p_kot
-
-p_kot_all <- ggplot(kot_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   labs(y = "KOT (ms)", subtitle = "KOT: Averaged (Articulation)")
-p_kot_all
-```
-
-## Each instance
-```{r kot_stats_ind, echo = FALSE}
+kot <- dt_kot[Subcomponent != "NA" & Subcomponent != "LtoS" & Subcomponent != "StoL" & Subcomponent != "FtoP" & Subcomponent != "PtoF", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(Instance, Condition, Skill, Subcomponent)]
 kot
@@
 ## Averaged
-```{r kot_stats_all, echo = FALSE}
-kot_all
+```{r kot-averaged, echo = FALSE}
+kot[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Subcomponent)]
 ```
 
-# KV
-```{r kv, include = FALSE}
+## Plots
+### Articulation
+```{r plot-kot-art, echo = FALSE}
+ggboxplot(kot[Skill == "articulation"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
+```
+
+### Dynamics
+```{r plot-kot-dyn, echo = FALSE}
+ggboxplot(kot[Skill == "dynamics"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
+```
+
+# KV (only for dynamics stimuli)
+## Each instance
+```{r vel, include = FALSE}
 dt_vel <- data_onset
@@
 # for each note
-dt_vel$Subcomponent <- NA
+dt_vel$Subcomponent <- "NA"
 # Legato
@@
 
-vel <- dt_vel[Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(Instance, Condition, Skill, Subcomponent)]
-vel_all <- vel[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Subcomponent)]
-```
-
-## Each instance
-```{r vel_stats_ind, echo = FALSE}
+vel <- dt_vel[Subcomponent != "NA", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(Instance, Condition, Skill, Subcomponent)]
 vel
@@
 ## Averaged
-```{r vel_stats_all, echo = FALSE}
-vel_all
+```{r vel-averaged, echo = FALSE}
+vel[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), .(Condition, Skill, Subcomponent)]
 ```
 
-## Plots
-```{r vel_plot, echo = FALSE}
-p_vel <- ggplot(vel, aes(x = Instance, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
-   labs(y = "Key Velocity", subtitle = "KV: Each instance (Dynamics)")
-p_vel
-
-p_vel_all <- ggplot(vel_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   labs(y = "Key Velocity", subtitle = "KV: Averaged (Dynamics)")
-p_vel_all
+## Plot
+### Dynamics
+```{r plot-vel-dyn, echo = FALSE}
+ggboxplot(vel[Skill == "dynamics"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
 ```
 
-# KV-Diff
-```{r vel_diff, include = FALSE}
+### Articulation
+```{r plot-vel-art, echo = FALSE}
+ggboxplot(vel[Skill == "articulation"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
+```
+
+# KV-Diff (only for dynamics stimuli)
+## Each instance
+```{r vel-diff, include = FALSE}
 # calculate differences and remove the first note
@@
 for (i in change_1){
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "LtoS"
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "FtoP"
+dt_vel_diff[Skill == "articulation" & Interval == i]$Subcomponent <- "LtoS"
+dt_vel_diff[Skill == "dynamics" & Interval == i]$Subcomponent <- "FtoP"
 }
 for (i in change_2){
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "StoL"
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "PtoF"
+dt_vel_diff[Skill == "articulation" & Interval == i]$Subcomponent <- "StoL"
+dt_vel_diff[Skill == "dynamics" & Interval == i]$Subcomponent <- "PtoF"
 }
 
-vel_diff <- dt_vel_diff[Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(Instance, Condition, Skill, Subcomponent)]
-vel_diff_all <- vel_diff[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Subcomponent)]
-```
-
-## Each instance
-```{r vel__diff_stats_ind, echo = FALSE}
+vel_diff <- dt_vel_diff[Subcomponent == "LtoS" | Subcomponent == "StoL" | Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(Instance, Condition, Skill, Subcomponent)]
 vel_diff
@@
 ## Averaged
-```{r vel_diff_stats_all, echo = FALSE}
-vel_diff_all
+```{r vel-diff-averaged, echo = FALSE}
+vel_diff[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Subcomponent)]
 ```
@@
 ## Plots
-```{r vel_diff_plot, echo = FALSE}
-p_vel_diff <- ggplot(vel_diff, aes(x = Instance, y = Mean, fill = Condition)) +
-geom_bar(stat = "identity", position = position_dodge()) +
-geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-              width = .2, position = position_dodge(.9)) +
-facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
-labs(y = "KV difference", subtitle = "KV-Diff: Each instance (Dynamics)")
-p_vel_diff
+### Dynamics
+```{r plot-vel-diff-dyn, echo = FALSE}
+ggboxplot(vel_diff[Skill == "dynamics"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
+```
 
-p_vel_diff_all <- ggplot(vel_diff_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
-geom_bar(stat = "identity", position = position_dodge()) +
-geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-              width = .2, position = position_dodge(.9)) +
-labs(y = "KV difference", subtitle = "KV-Diff: Averaged (Dynamics)")
-p_vel_diff_all
+### Articulation
+```{r plot-vel-diff-art, echo = FALSE}
+ggboxplot(vel_diff[Skill == "articulation"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
 ```

### 2021-02-21 material/expstimuli/mid_export.py
add mid export
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -1,0 +1,113 @@
+#!/usr/local/bin/python
+####################
+# Created: 20/04/2020
+# This script converts txt files to mid files.
+
+#%% import packages
+import os, csv, mido
+
+#%% create mid folder if not existed
+if not os.path.exists("mid"):
+    os.mkdir("mid")
+if not os.path.exists("practice"):
+    os.mkdir("practice")
+
+#%% folder names
+folder_a_t = "./1613936591-210221/art_teaching/"
+folder_d_t = "./1613936591-210221/dyn_teaching/"
+folder_a_p = "./1613936591-210221/art_performing/"
+folder_d_p = "./1613936591-210221/dyn_performing/"
+folders = [folder_a_t, folder_d_t, folder_a_p, folder_d_p]
+
+#%% mid export
+for folder in folders:
+    files = [f for f in os.listdir(folder) if os.path.isfile(os.path.join(folder, f))]
+    for instance in range(0, len(files)):
+        filename = folder + files[instance]
+        with open(filename) as csvfile:
+            # create mid file
+            mid = mido.MidiFile()
+            track = mido.MidiTrack()
+            mid.tracks.append(track)
+            track.append(mido.Message('program_change', program=0, time=0)) # program 0 = Acoustic Grand Piano
+            # name for mid file
+            if folder == "./1613936591-210221/art_teaching/":
+                midname = "./mid/a_t_" + str(instance+1) + ".mid"
+            elif folder == "./1613936591-210221/dyn_teaching/":
+                midname = "./mid/d_t_" + str(instance+1) + ".mid"
+            elif folder == "./1613936591-210221/art_performing/":
+                midname = "./mid/a_p_" + str(instance+1) + ".mid"
+            elif folder == "./1613936591-210221/dyn_performing/":
+                midname = "./mid/d_p_" + str(instance+1) + ".mid"
+            # read current track data (txt file)   
+            current = csv.reader(csvfile, delimiter = ",")
+            next(current) # skip first row
+            counter = 0
+            for row in current:
+                if counter == 0:
+                    previousTime = 0
+                    counter += 1
+                else:
+                    previousTime = currentTime
+                currentTime = int(mido.second2tick(int(row[1])*0.001+3, 480, 500000))
+                currentPitch = int(row[2])
+                currentVelocity = int(row[3])
+                currentOnOff = int(row[4])
+                # assign midi values
+                if currentOnOff == 1:
[…]

### 2021-02-23 material/expstimuli/stimuli.Rmd
add mid export
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
update stimuli profile
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
+  + 18 stimuli for teaching-articulation
+  + 18 stimuli for teaching-dynamics
+  + 18 stimuli for performing-articulation
+  + 18 stimuli for performing-dynamics
+
 Note: SubNr 3 was excluded due to insufficient motor skills (see analysis for [music-teaching: experiment-2](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2))
@@
 - IOIs (average tempo)
-- Transition points
-- CV (tempo variability)
-- KOR (articulation)
+- KOT (articulation)
 - KV (dynamics)
@@
 
+```{r setup, include = FALSE}
+# packages
+# data manipulation
+if (!require("data.table")) {install.packages("data.table"); require("data.table")}
+# plot
+if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
+# midi
+if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
+```
+
+# Filtering
 ```{r filtering, include = FALSE}
-foldername = paste(format(Sys.time(), "%s-%d%m%y"), "/", sep = "") # current time
-
-# create folders if not exists
-if (!file.exists(foldername)){
-  dir.create(foldername)
-  dir.create(paste(foldername, "practice", sep = ""))
-}
-
-if (!file.exists(paste(foldername, "art_teaching", sep = ""))){
-  dir.create(paste(foldername, "art_teaching", sep = ""))
-  dir.create(paste(foldername, "practice/art_teaching", sep = ""))
-}
-
-if (!file.exists(paste(foldername, "dyn_teaching", sep = ""))){
-  dir.create(paste(foldername, "dyn_teaching", sep = ""))
-  dir.create(paste(foldername, "practice/dyn_teaching", sep = ""))
-}
-
-if (!file.exists(paste(foldername, "art_performing"))){
-  dir.create(paste(foldername, "art_performing", sep = ""))
-  dir.create(paste(foldername, "practice/art_performing", sep = ""))
-}
-
-if (!file.exists(paste(foldername, "dyn_performing"))){
-  dir.create(paste(foldername, "dyn_performing", sep = ""))
-  dir.create(paste(foldername, "practice/dyn_performing", sep = ""))
-}
-
 # read functions
@@
 
-# add column namesls
+# add column names
 colnames(raw_data) <- c("NoteNr", "TimeStamp", "Pitch", "Velocity", "Key_OnOff", "Device", "Tempo", "SubNr", "BlockNr", "TrialNr", "Skill", "Condition", "Image")
@@
 
-# correct labelling (due to a labelling error of the original study)
-# articulation
-dt_a <- raw_data[grepl("stim_a", Image)]
-# correct wrong labelling
-dt_a$Skill <- "articulation"
-
-# dynamics
-dt_d <- raw_data[grepl("stim_d", Image)]
-# correct wrong labelling
-dt_d$Skill <- "dynamics"
-
-# bind data frames for articulation and dynamics
-dt_all <- rbind(dt_a, dt_d)
-
 # raw_data without metronome
-dt_all <- dt_all[Pitch != 31 & Pitch != 34]
+dt_all <- raw_data[Pitch != 31 & Pitch != 34]
 
@@
 
-# convert bpm to ms
-dt_ioi[Tempo == 120]$Tempo <- 250
-dt_ioi[Tempo == 110]$Tempo <- 273
-dt_ioi[Tempo == 100]$Tempo <- 300
-
-# normalise IOIs
-dt_ioi$normIOI <- dt_ioi$IOI/dt_ioi$Tempo
-
-ioi <- dt_ioi[Interval != 25 & Interval != 26 & Interval != 27 & Interval != 28 & Interval != 32 & Interval != 33 & Interval != 34 & Interval != 35 & Interval != 51 & Interval != 52 & Interval != 56 & Interval != 57 & Interval != 65 & Interval != 66 & Interval != 67 & Interval != 68 & Interval != 69 & Interval != 70 & Interval != 71, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, BlockNr, TrialNr)]
+ioi <- dt_ioi[Interval != 25 & Interval != 26 & Interval != 27 & Interval != 28 & Interval != 32 & Interval != 33 & Interval != 34 & Interval != 35 & Interval != 51 & Interval != 52 & Interval != 56 & Interval != 57 & Interval != 65 & Interval != 66 & Interval != 67 & Interval != 68 & Interval != 69 & Interval != 70 & Interval != 71, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, BlockNr, TrialNr, Tempo)]
 mean_ioi <- mean(ioi$Mean)
@@
 
-```{r selection, include = FALSE}
+## Histogram
+- Exclude performances outside 2sd
+- Gray vertical lines indicate ideal tempi (300ms for 100bpm, 273ms for 110bpm, 250ms for 120bpm)
+
+1. Before exclusion
+```{r plot-hist, echo = FALSE}
+ioi$Tempo <- factor(ioi$Tempo)
+gghistogram(ioi, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
+gghistogram(ioi, x = "Mean", fill = "Tempo", color = "Tempo", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
+```
+
+2. After exclusion
+```{r plot-hist2, echo = FALSE}
+ioi_include$Tempo <- factor(ioi_include$Tempo)
+gghistogram(ioi_include, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
+gghistogram(ioi_include, x = "Mean", fill = "Tempo", color = "Tempo", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
+```
+
+```{r selection, eval = FALSE, include = FALSE}
+foldername = paste(format(Sys.time(), "%s-%d%m%y"), "/", sep = "") # current time
+
+# create folders if not exists
+if (!file.exists(foldername)){
+  dir.create(foldername)
+  dir.create(paste(foldername, "practice", sep = ""))
+}
+
+if (!file.exists(paste(foldername, "art_teaching", sep = ""))){
+  dir.create(paste(foldername, "art_teaching", sep = ""))
+  dir.create(paste(foldername, "practice/art_teaching", sep = ""))
+}
+
+if (!file.exists(paste(foldername, "dyn_teaching", sep = ""))){
+  dir.create(paste(foldername, "dyn_teaching", sep = ""))
+  dir.create(paste(foldername, "practice/dyn_teaching", sep = ""))
+}
+
+if (!file.exists(paste(foldername, "art_performing"))){
+  dir.create(paste(foldername, "art_performing", sep = ""))
+  dir.create(paste(foldername, "practice/art_performing", sep = ""))
+}
+
+if (!file.exists(paste(foldername, "dyn_performing"))){
+  dir.create(paste(foldername, "dyn_performing", sep = ""))
+  dir.create(paste(foldername, "practice/dyn_performing", sep = ""))
+}
+
 # create a list for included performances
@@
 list_include <- list_include[order(RandNr),]
+
 # stimuli for experimental trials
-for (i in 1:96){ # 24 stimuli for each category
+for (i in 1:72){ # 18 stimuli for each category
   subject = list_include$SubNr[i]
@@
 
+# Export as midi files
+```{bash, echo = TRUE}
+# python
+source /Users/atsukotominaga/Pyenv/bin/activate
+python mid_export.py
+```
+
 ```{r stimuli, include = FALSE}
@@
 
-# packages
-if (!require("data.table")) {install.packages("data.table"); require("data.table")}
-if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
+# read midi data with tuneR
+# create a list of data file names
+lf <- list.files("./mid/", pattern = "mid")
 
-# create a list of data file names
-lf_a_t <- list.files("./1613936591-210221/art_teaching", pattern = "txt")
-lf_a_p <- list.files("./1613936591-210221/art_performing", pattern = "txt")
-lf_d_t <- list.files("./1613936591-210221/dyn_teaching", pattern = "txt")
-lf_d_p <- list.files("./1613936591-210221/dyn_performing", pattern = "txt")
+# combine data
+all_data <- data.table()
+for (file in lf){
+   current <- readMidi(paste("./mid/", file, sep = ""))
+   current$MidFile <- gsub(".mid", "", file)
+   all_data <- rbind(all_data, current)
+}
 
-# merge all data files into one
-data <- data.table()
-for (i in 1:length(lf_a_t)){
- data_i <- fread(file.path("./1613936591-210221/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
- data_i$Instance <- i
- data <- rbind(data, data_i)
-}
-for (i in 1:length(lf_a_p)){
- data_i <- fread(file.path("./1613936591-210221/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
- data_i$Instance <- i
- data <- rbind(data, data_i)
-}
-for (i in 1:length(lf_d_t)){
- data_i <- fread(file.path("./1613936591-210221/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
- data_i$Instance <- i
- data <- rbind(data, data_i)
-}
-for (i in 1:length(lf_d_p)){
- data_i <- fread(file.path("./1613936591-210221/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
- data_i$Instance <- i
- data <- rbind(data, data_i)
-}
+data <- all_data[event == "Note On" | event == "Note Off"]
+data$NoteNr <- rep(1:144, nrow(data)/144)
+data$channel <- NULL
+data$parameterMetaSystem <- NULL
+data$track <- NULL
+data$type <- NULL
+data$time2 <- (data$time/960)*1000 # deltatime to time (ms)
+
+# labelling
+colnames(data)[c(3,4)] <- c("Pitch", "Velocity") # time event also change
+data$Condition <- "NA"
+data$Skill <- "NA"
+data[grepl("_t_", MidFile)]$Condition <- "teaching"
+data[grepl("_p_", MidFile)]$Condition <- "performing"
+data[grepl("a_", MidFile)]$Skill <- "articulation"
+data[grepl("d_", MidFile)]$Skill <- "dynamics"
 
@@
 ```{r ioi, include = FALSE}
-data_onset <- data[Key_OnOff == 1]
-data_offset <- data[Key_OnOff == 0]
+data_onset <- data[event == "Note On"]
+data_offset <- data[event == "Note Off"]
 
-data_onset$IOI <- diff(c(0, data_onset$TimeStamp))
-dt_ioi <- data_onset[NoteNr != 17]
+data_onset$IOI <- diff(c(0, data_onset$time2))
+dt_ioi <- data_onset[NoteNr != 1]
 dt_ioi$Interval <- rep(1:71, nrow(dt_ioi)/71)
-
-# convert bpm to ms
-dt_ioi[Tempo == 120]$Tempo <- 250
-dt_ioi[Tempo == 110]$Tempo <- 273
-dt_ioi[Tempo == 100]$Tempo <- 300
-
-# normalise IOIs
-dt_ioi$normIOI <- dt_ioi$IOI/dt_ioi$Tempo
 
@@
 
-ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(Instance, Condition, Skill)]
+ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Condition, Skill)]
 ```
@@
 
-# KOR
-```{r kor, include = FALSE}
+# KOT
+```{r kot, include = FALSE}
 data_onset$KOT <- NA
@@
    if (row < nrow(data_onset)){
-      data_onset$KOT[row+1] <- data_offset$TimeStamp[row] - data_onset$TimeStamp[row+1] # offset(n) - onset(n+1)
+      data_onset$KOT[row+1] <- data_offset$time2[row] - data_onset$time2[row+1] # offset(n) - onset(n+1)
    }
@@
 
-ioi_forKOT <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(Instance, Condition, Skill)]
-
-data_onset$KOR <- 0
-for (cond in c("teaching", "performing")){
-  for (skill in c("articulation", "dynamics")){
-    for (i in c(1:24)){
-      data_onset[Condition == cond & Skill == skill & Instance == i]$KOR <- data_onset[Condition == cond & Skill == skill & Instance == i]$KOT/ioi_forKOT[Condition == cond & Skill == skill & Instance == i]$Mean
-    }
-  }
-}
-
-dt_kor <- data_onset[NoteNr != 17]
-dt_kor$Interval <- rep(1:71, nrow(dt_kor)/71)
+dt_kot <- data_onset[NoteNr != 1]
+dt_kot$Interval <- rep(1:71, nrow(dt_kot)/71)
 
 # assign Subcomponents
-dt_kor$Subcomponent <- "NA"
+dt_kot$Subcomponent <- "NA"
 # Legato
@@
    for (note in 1:length(ls_legato[[phrase]])){
-     dt_kor[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
+     dt_kot[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
    }
@@
    for (note in 1:length(ls_staccato[[phrase]])){
-     dt_kor[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
+     dt_kot[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
    }
@@
    for (note in 1:length(ls_forte[[phrase]])){
-     dt_kor[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
+     dt_kot[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
    }
@@
    for (note in 1:length(ls_piano[[phrase]])){
-     dt_kor[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
+     dt_kot[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
    }
@@
 for (number in change_1){
-   dt_kor[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
-   dt_kor[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
+   dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
+   dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
 }
 for (number in change_2){
-   dt_kor[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
-   dt_kor[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
+   dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
+   dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
 }
 
-kor <- dt_kor[Subcomponent != "NA" & Subcomponent != "LtoS" & Subcomponent != "StoL" & Subcomponent != "FtoP" & Subcomponent != "PtoF", .(N = .N, Mean = mean(KOR), SD = sd(KOR)), by = .(Instance, Condition, Skill, Subcomponent)]
+kot <- dt_kot[Subcomponent != "NA" & Subcomponent != "LtoS" & Subcomponent != "StoL" & Subcomponent != "FtoP" & Subcomponent != "PtoF", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile, Condition, Skill, Subcomponent)]
 ```
@@
 ## Each instance
-```{r kor-each, echo = FALSE}
-kor
+```{r kot-each, echo = FALSE}
+kot
 ```
@@
 ```{r kor-averaged, echo = FALSE}
-kor[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), .(Condition, Skill, Subcomponent)]
+kot[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), .(Condition, Skill, Subcomponent)]
 ```
@@
 ### Articulation
-```{r plot-kor-art, echo = FALSE}
-ggboxplot(kor[Skill == "articulation"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
+```{r plot-kot-art, echo = FALSE}
+ggboxplot(kot[Skill == "articulation"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
 ```
@@
 ```{r plot-kor-dyn, echo = FALSE}
-ggboxplot(kor[Skill == "dynamics"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
+ggboxplot(kot[Skill == "dynamics"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
 ```
@@
 
-vel <- dt_vel[Subcomponent != "NA", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(Instance, Condition, Skill, Subcomponent)]
+vel <- dt_vel[Subcomponent != "NA", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(MidFile, Condition, Skill, Subcomponent)]
 ```
@@
 
-vel_diff <- dt_vel_diff[Subcomponent == "LtoS" | Subcomponent == "StoL" | Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(Instance, Condition, Skill, Subcomponent)]
+vel_diff <- dt_vel_diff[Subcomponent == "LtoS" | Subcomponent == "StoL" | Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(MidFile, Condition, Skill, Subcomponent)]
 ```

### 2021-02-23 material/expstimuli/mid_export.py

@@ -1,6 +1,6 @@
 #!/usr/local/bin/python
 ####################
-# Created: 20/04/2020
+# Created: 23/02/2020
 # This script converts txt files to mid files.
 
 #%% import packages
@@ -13,10 +13,10 @@ if not os.path.exists("practice"):
     os.mkdir("practice")
 
 #%% folder names
-folder_a_t = "./1613936591-210221/art_teaching/"
-folder_d_t = "./1613936591-210221/dyn_teaching/"
-folder_a_p = "./1613936591-210221/art_performing/"
-folder_d_p = "./1613936591-210221/dyn_performing/"
+folder_a_t = "./1614096852-230221/art_teaching/"
+folder_d_t = "./1614096852-230221/dyn_teaching/"
+folder_a_p = "./1614096852-230221/art_performing/"
+folder_d_p = "./1614096852-230221/dyn_performing/"
 folders = [folder_a_t, folder_d_t, folder_a_p, folder_d_p]
 
 #%% mid export
@@ -31,13 +31,13 @@ for folder in folders:
             mid.tracks.append(track)
             track.append(mido.Message('program_change', program=0, time=0)) # program 0 = Acoustic Grand Piano
             # name for mid file
-            if folder == "./1613936591-210221/art_teaching/":
+            if folder == "./1614096852-230221/art_teaching/":
                 midname = "./mid/a_t_" + str(instance+1) + ".mid"
-            elif folder == "./1613936591-210221/dyn_teaching/":
+            elif folder == "./1614096852-230221/dyn_teaching/":
                 midname = "./mid/d_t_" + str(instance+1) + ".mid"
-            elif folder == "./1613936591-210221/art_performing/":
+            elif folder == "./1614096852-230221/art_performing/":
                 midname = "./mid/a_p_" + str(instance+1) + ".mid"
-            elif folder == "./1613936591-210221/dyn_performing/":
+            elif folder == "./1614096852-230221/dyn_performing/":
                 midname = "./mid/d_p_" + str(instance+1) + ".mid"
             # read current track data (txt file)   
             current = csv.reader(csvfile, delimiter = ",")
@@ -49,7 +49,12 @@ for folder in folders:
                     counter += 1
                 else:
                     previousTime = currentTime
-                currentTime = int(mido.second2tick(int(row[1])*0.001+3, 480, 500000))
+                if int(row[6]) == 100:
[…]

### 2021-02-23 experiment/experiment.py
add experimenta programme
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -1,0 +1,239 @@
+#!usr/bin/env python
+
+"""
+This is an experimental programme for Music Perception 2021
+"""
+
+# import libraries
+from psychopy import core, visual, gui, data, event
+import os, random, mido
+
+### function ###
+def next():
+    resp = None
+    while resp == None:
+        allKeys = event.getKeys(keyList = ["space", "escape"])
+        for resp in allKeys:
+            if resp == "space": # proceed
+                break
+            elif resp == "escape": # force quit
+                for item in resultsList: # save data so far
+                    dataFile.write('{0}, {1}, {2}, {3}, {4}, {5}, {6}, {7}, {8}\n'.format(*item))
+                dataFile.close()
+                core.quit()
+    return
+
+def trial(expMode, imageFile, midFile, resultsList):
+    # stimuli presentation
+    ## 1. sheet music
+    stimuli = visual.ImageStim(win, image = imageFile, size = [1500, 500])
+    stimuli.draw()
+
+    ## 2. midi play
+    playing = True
+    while playing:
+        win.flip() # sheet music
+        mid = mido.MidiFile(midFile)
+        for msg in mid.play():
+            port.send(msg)
+        event.clearEvents() # clear if any keypress
+        core.wait(1)
+        playing = False
+    
+    # get response (yes/no answer)
+    ratingScale = visual.RatingScale(win, pos = (0, -300), choices = ["Yes", "No"], lineColor = (-.7, -.7, -.7), tickHeight = 0.0, markerStart = 0.5, markerColor = "Orange", textFont = "Avenir", size = 1.5, noMouse = True, acceptKeys = "return", showAccept = False, acceptPreText =  "Select your response", acceptSize = 1.8, skipKeys = None)
+    question = visual.TextStim(win, pos=[0, 0], font = "Avenir", height = 60, wrapWidth = 1400,
+    text = "Teaching?\nYes: <Left>    No: <Right>\n\nPress <Return> to confirm\n\n\n\n")
+    trialClock = core.Clock()
+    while ratingScale.noResponse:
+        question.draw()
+        ratingScale.draw()
+        win.flip()
+        if len(ratingScale.getHistory()) == 2: # if accidentally hit return, ignore
+            ratingScale.noResponse = True
[…]

### 2021-02-24 analysis/analysis.Rmd
update analysis / add NA for ioi analysis / deltatime to ms / add lines for an ideal tempo
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 data$type <- NULL
+data$time2 <- (data$time/960)*1000 # deltatime to time (ms)
 
@@
 - linear regression lines and 95% confidence interval (gray)
+- dotted lines indicate an ideal tempo (80bpm for 16th notes - 188ms interval)
 
@@
 
-data_onset$IOI <- diff(c(0, data_onset$time))
+data_onset$IOI <- diff(c(0, data_onset$time2))
 dt_ioi <- data_onset[NoteNr != 1]
@@
 
-ioi <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill)]
+ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill)]
 
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
 ```
@@
 ```{r ioi-sub, echo = FALSE}
-ioi_sub <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill, Subcomponent)]
+ioi_sub <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill, Subcomponent)]
 
@@
 
-## All (**)
+## All (n.s.)
 ```{r cv, echo = FALSE}
-cv <- dt_ioi[, .(N = .N, CV = sd(IOI)/mean(IOI)), by = .(MidFile, Skill)]
+cv <- dt_ioi[Subcomponent != "NA", .(N = .N, CV = sd(IOI)/mean(IOI)), by = .(MidFile, Skill)]
 
@@
 ```
-## Articulation (***)
+## Articulation (n.s.)
 ```{r, echo = FALSE}
@@
 ```{r kot, include = FALSE}
-data_onset$KOT <- NA
+data_onset$KOT <- 0
 for (row in 1:nrow(data_onset)){
    if (row < nrow(data_onset)){
-      data_onset$KOT[row+1] <- data_offset$time[row] - data_onset$time[row+1] # offset(n) - onset(n+1)
+      data_onset$KOT[row+1] <- data_offset$time2[row] - data_onset$time2[row+1] # offset(n) - onset(n+1)
    }

### 2021-02-25 material/expstimuli/stimuli.Rmd
change loop number
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 # stimuli for practice trials
-for (i in 97:104){ # 4 stimuli for each category
+for (i in 73:80){ # 4 stimuli for each category
   subject = list_include$SubNr[i]

### 2021-03-04 material/expstimuli/selection/stimuli.Rmd
update stimuli profile
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-01-11 material/expstimuli/selection/analysis(2sd).Rmd
@@
 ---
-title: "Music Perception: Stimuli profiles (2sd)"
+title: "Music Perception: Stimuli profiles"
 output: html_notebook
@@
 
-I chose stimuli with the IOIs within 2sd randomly.
+I chose stimuli with the IOIs within 2sd randomly from each condition (teaching, performing), each technique (articulation, dynamics).
 
-Note: SubNr 8 was excluded due to an experimental error, SubNr 16 was excluded due to a deviated tempo (see analysis for [teaching-v1.0](https://github.com/atsukotominaga/teaching-v1.0))
+  + 24 stimuli for teaching-articulation
+  + 24 stimuli for teaching-dynamics
+  + 24 stimuli for performing-articulation
+  + 24 stimuli for performing-dynamics
+
+Note: SubNr 8 & 16 was excluded due to insufficient motor skills (see analysis for [music-teaching: experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1))
+
+# DVs
+- IOIs (average tempo)
+- KOT (articulation)
+- KV (dynamics)
+- KV-diff (dynamics)
 
 ```{r setup, include = FALSE}
+# packages
+# data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
-if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
+# plot
+if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
+# midi
+if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
 ```
 
-```{r file, include = FALSE}
+# Filtering
+```{r filtering, eval = FALSE, include = FALSE}
+# read functions
+source("./function.R")
+
+# read a text file for ideal performance
+dt_ideal <- read.table("./ideal.txt")
+colnames(dt_ideal) <- "Pitch"
+dt_ideal$RowNr <- 1:nrow(dt_ideal)
+setcolorder(dt_ideal, c(2, 1))
+
 # create a list of data file names
-lf_a_t <- list.files("./2sd/art_teaching", pattern = "txt")
-lf_a_p <- list.files("./2sd/art_performing", pattern = "txt")
-lf_d_t <- list.files("./2sd/dyn_teaching", pattern = "txt")
-lf_d_p <- list.files("./2sd/dyn_performing", pattern = "txt")
+lf <- list.files("./raw_data", pattern = "txt")
 
-# merge all data files into one
-data <- data.table()
-for (i in 1:length(lf_a_t)){
- data_i <- fread(file.path("./2sd/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
- data_i$Instance <- i
- data <- rbind(data, data_i)
+# create raw_data - merge all data files into one
+raw_data <- data.table()
+for (i in 1:length(lf)){
+  data_i <- fread(file.path("./raw_data", lf[i]), header = F, sep = " ", dec = ".")
+  raw_data <- rbind(raw_data, data_i)
 }
-for (i in 1:length(lf_a_p)){
- data_i <- fread(file.path("./2sd/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
- data_i$Instance <- i
- data <- rbind(data, data_i)
+
+# add column namesls
+colnames(raw_data) <- c("NoteNr", "TimeStamp", "Pitch", "Velocity", "Key_OnOff", "Device", "SubNr", "BlockNr", "TrialNr", "Skill", "Condition", "Image")
+
+# clean raw_data
+raw_data$NoteNr <- as.numeric(gsub(",", "", raw_data$NoteNr))
+raw_data$Image <- gsub(";", "", raw_data$Image)
+
+# sort by SubNr, BlockNr, TrialNr
+raw_data <- raw_data[order(raw_data$SubNr, raw_data$BlockNr, raw_data$TrialNr),]
+
+# correct labelling (due to a labelling error of the original study)
+# articulation
+dt_a <- raw_data[grepl("stim_a", Image)]
+# correct wrong labelling
+dt_a$Skill <- "articulation"
+
+# dynamics
+dt_d <- raw_data[grepl("stim_d", Image)]
+# correct wrong labelling
+dt_d$Skill <- "dynamics"
+
+# bind data frames for articulation and dynamics
+dt_all <- rbind(dt_a, dt_d)
+
+# raw_data without metronome
+dt_all <- dt_all[Pitch != 31 & Pitch != 34]
+
+# onset and offset
+dt_onset <- dt_all[Key_OnOff == 1]
+dt_offset <- dt_all[Key_OnOff == 0]
+
+# 1. Detect error trials
+dt_error_onset <- checker(dt_onset, dt_ideal)
+dt_error_offset <- checker(dt_offset, dt_ideal)
+
+# combine onset/offset
+dt_error <- rbind(dt_error_onset, dt_error_offset)
+dt_error$Duplicate <- duplicated(dt_error)
+
+# exclude error performances
+dt_exclude <- dt_error[Duplicate == FALSE]
+
+# mark imperfect performances
+dt_all$Error <- 0
+for (error in 1:nrow(dt_exclude)){
+  dt_all[SubNr == dt_exclude$SubNr[error] & BlockNr == dt_exclude$BlockNr[error] & TrialNr == dt_exclude$TrialNr[error]]$Error <- 1
 }
-for (i in 1:length(lf_d_t)){
- data_i <- fread(file.path("./2sd/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
- data_i$Instance <- i
- data <- rbind(data, data_i)
+dt_include <- dt_all[Error == 0]
+
+# exclude SubNr 16 due to a deviated tempo
+dt_include <- dt_include[SubNr != 16]
+
+# exclude IOIs +/- 3SD
+dt_ioi <- dt_include[Key_OnOff == 1]
+dt_ioi$IOI <- diff(c(0, dt_ioi$TimeStamp))
+dt_ioi <- dt_ioi[NoteNr != 17] # remove irrelevant notes
+dt_ioi$Interval <- rep(1:66, nrow(dt_ioi)/66)
+ioi <- dt_ioi[Interval != 32 & Interval != 33 & Interval != 65 & Interval != 66, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, BlockNr, TrialNr)]
+mean_ioi <- mean(ioi$Mean)
+sd_ioi <- sd(ioi$Mean)
+ioi_include <- ioi[Mean < mean_ioi+2*sd_ioi & Mean > mean_ioi-2*sd_ioi]
+
+dt_include_updated <- data.table()
+for (row in 1:nrow(ioi_include)){
+  subnr = ioi_include$SubNr[row]
+  block = ioi_include$BlockNr[row]
+  trial = ioi_include$TrialNr[row]
+
+  current <- dt_include[SubNr == subnr & BlockNr == block & TrialNr == trial]
+  dt_include_updated <- rbind(dt_include_updated, current)
 }
-for (i in 1:length(lf_d_p)){
- data_i <- fread(file.path("./2sd/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
- data_i$Instance <- i
- data <- rbind(data, data_i)
+```
+
+## Histogram
+- Gray vertical lines indicate ideal tempi (300ms for 100bpm, 273ms for 110bpm, 250ms for 120bpm)
+
+1. Before exclusion
+```{r plot-hist, echo = FALSE}
+gghistogram(ioi, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 188, color = "gray", size = 1)
+```
+
+2. After exclusion
+```{r plot-hist2, echo = FALSE}
+gghistogram(ioi_include, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 188, color = "gray", size = 1)
+```
+
+```{r selection, eval = FALSE, include = FALSE}
+foldername = paste(format(Sys.time(), "%s-%d%m%y"), "/", sep = "") # current time
+
+# create folders if not exists
+if (!file.exists(foldername)){
+  dir.create(foldername)
+  dir.create(paste(foldername, "practice", sep = ""))
 }
+
+if (!file.exists(paste(foldername, "art_teaching", sep = ""))){
+  dir.create(paste(foldername, "art_teaching", sep = ""))
+  dir.create(paste(foldername, "practice/art_teaching", sep = ""))
+}
+
+if (!file.exists(paste(foldername, "dyn_teaching", sep = ""))){
+  dir.create(paste(foldername, "dyn_teaching", sep = ""))
+  dir.create(paste(foldername, "practice/dyn_teaching", sep = ""))
+}
+
+if (!file.exists(paste(foldername, "art_performing"))){
+  dir.create(paste(foldername, "art_performing", sep = ""))
+  dir.create(paste(foldername, "practice/art_performing", sep = ""))
+}
+
+if (!file.exists(paste(foldername, "dyn_performing"))){
+  dir.create(paste(foldername, "dyn_performing", sep = ""))
+  dir.create(paste(foldername, "practice/dyn_performing", sep = ""))
+}
+
+# create a list for included performances
+list_include <- dt_include_updated[, .N, by = .(SubNr, BlockNr, TrialNr, Condition, Skill)]
+list_overall <- list_include[, .N, by = .(Condition, Skill)]
+
+# assign random numbers for performances in each category
+list_include$RandNr <- 0
+for (cond in c("teaching", "performing")){
+  for (skill in c("articulation", "dynamics")){
+    list_include[Condition == cond & Skill == skill]$RandNr <- sample(nrow(list_include[Condition == cond & Skill == skill]), replace = FALSE)
+  }
+}
+list_include <- list_include[order(RandNr),]
+
+# stimuli for experimental trials
+for (i in 1:96){ # 18 stimuli for each category
+  subject = list_include$SubNr[i]
+  block = list_include$BlockNr[i]
+  trial = list_include$TrialNr[i]
+  cond = list_include$Condition[i]
+  skill = list_include$Skill[i]
+  current <- dt_include[SubNr == subject & BlockNr == block & TrialNr == trial]
+  firstTimestamp = current$TimeStamp[1]
+  current$TimeStamp <- current$TimeStamp - firstTimestamp # start with time 0
+
+  if (cond == "teaching" & skill == "articulation"){
+    filename = paste(foldername, "art_teaching/", subject, block, trial, ".txt", sep = "")
+  } else if (cond == "teaching" & skill == "dynamics"){
+    filename = paste(foldername, "dyn_teaching/", subject, block, trial, ".txt", sep = "")
+  } else if (cond == "performing" & skill == "articulation"){
+    filename = paste(foldername, "art_performing/", subject, block, trial, ".txt", sep = "")
+  } else if (cond == "performing" & skill == "dynamics"){
+    filename = paste(foldername, "dyn_performing/", subject, block, trial, ".txt", sep = "")
+  }
+  fwrite(current, file = filename)
+}
+
+print("Experimental stimuli - Done! :)")
+
+# stimuli for practice trials
+for (i in 97:104){ # 2 stimuli for each category
+  subject = list_include$SubNr[i]
+  block = list_include$BlockNr[i]
+  trial = list_include$TrialNr[i]
+  cond = list_include$Condition[i]
+  skill = list_include$Skill[i]
+  current <- dt_include[SubNr == subject & BlockNr == block & TrialNr == trial]
+  firstTimestamp = current$TimeStamp[1]
+  current$TimeStamp <- current$TimeStamp - firstTimestamp # start with time 0
+
+  if (cond == "teaching" & skill == "articulation"){
+    filename = paste(foldername, "practice/art_teaching/", subject, block, trial, ".txt", sep = "")
+  } else if (cond == "teaching" & skill == "dynamics"){
+    filename = paste(foldername, "practice/dyn_teaching/", subject, block, trial, ".txt", sep = "")
+  } else if (cond == "performing" & skill == "articulation"){
+    filename = paste(foldername, "practice/art_performing/", subject, block, trial, ".txt", sep = "")
+  } else if (cond == "performing" & skill == "dynamics"){
+    filename = paste(foldername, "practice/dyn_performing/", subject, block, trial, ".txt", sep = "")
+  }
+  fwrite(current, file = filename)
+}
+
+print("Practice stimuli - Done! :)")
+```
+
+```{r stimuli, include = FALSE}
+rm(list = ls()) # clear all
+
+# read midi data with tuneR
+# create a list of data file names
+lf <- list.files("../export/mid/", pattern = "mid")
+
+# combine data
+all_data <- data.table()
+for (file in lf){
+   current <- readMidi(paste("../export/mid/", file, sep = ""))
+   current$MidFile <- gsub(".mid", "", file)
+   all_data <- rbind(all_data, current)
+}
+
+data <- all_data[event == "Note On" | event == "Note Off"]
+data$NoteNr <- rep(1:134, nrow(data)/134)
+data$channel <- NULL
+data$parameterMetaSystem <- NULL
+data$track <- NULL
+data$type <- NULL
+data$time2 <- round((data$time/960)*1000) # deltatime to time (ms)
+
+# labelling
+colnames(data)[c(3,4)] <- c("Pitch", "Velocity") # time event also change
+data$Condition <- "NA"
+data$Skill <- "NA"
+data[grepl("_t_", MidFile)]$Condition <- "teaching"
+data[grepl("_p_", MidFile)]$Condition <- "performing"
+data[grepl("a_", MidFile)]$Skill <- "articulation"
+data[grepl("d_", MidFile)]$Skill <- "dynamics"
 
@@
 ```{r ioi, include = FALSE}
-data_onset <- data[Key_OnOff == 1]
-data_offset <- data[Key_OnOff == 0]
+data_onset <- data[event == "Note On"]
+data_offset <- data[event == "Note Off"]
 
-data_onset$IOI <- diff(c(0, data_onset$TimeStamp))
-dt_ioi <- data_onset[NoteNr != 17]
+data_onset$IOI <- diff(c(0, data_onset$time2))
+dt_ioi <- data_onset[NoteNr != 1]
 dt_ioi$Interval <- rep(1:66, nrow(dt_ioi)/66)
@@
 
-ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(Instance, Condition, Skill)]
-ioi_art <- ioi[Skill == "articulation", .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill)]
-ioi_dyn <- ioi[Skill == "dynamics", .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill)]
+ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Condition, Skill)]
 ```
 
-## Summary Stats
-### Individual
-```{r ioi_stats_ind, echo = FALSE}
+## Each instance
+```{r ioi-each, echo = FALSE}
 ioi
@@
 
-### Averaged
-```{r ioi_stats_all, echo = FALSE}
-ioi_art
-ioi_dyn
+## Averaged
+```{r ioi-averaged, echo = FALSE}
+ioi[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), .(Condition, Skill)]
 ```
 
-## Plots
-### Articulation
-```{r ioi_art_plot, echo = FALSE}
-p_ioi_art <- ggplot(ioi[Skill == "articulation"], aes(x = Instance, y = Mean, fill = Condition)) +
- geom_bar(stat = "identity", position = position_dodge()) +
- geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-               width = .2, position = position_dodge(.9)) +
- geom_hline(yintercept = 188, linetype = "dashed") +
- scale_x_continuous(breaks = seq(1:24)) +
- labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Articulation)")
-p_ioi_art
-
-p_ioi_art_all <- ggplot(ioi_art, aes(x = Skill, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   geom_hline(yintercept = 188, linetype = "dashed") +
-   labs(y = "IOI (ms)", subtitle = "IOI: Averaged (Articulation)")
-p_ioi_art_all
-```
-### Dynamics
-```{r ioi_dyn_plot, echo = FALSE}
-p_ioi_dyn <- ggplot(ioi[Skill == "dynamics"], aes(x = Instance, y = Mean, fill = Condition)) +
- geom_bar(stat = "identity", position = position_dodge()) +
- geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-               width = .2, position = position_dodge(.9)) +
- geom_hline(yintercept = 188, linetype = "dashed") +
- scale_x_continuous(breaks = seq(1:24)) +
- labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Dynamics)")
-p_ioi_dyn
-
-p_ioi_dyn_all <- ggplot(ioi_dyn, aes(x = Skill, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   geom_hline(yintercept = 188, linetype = "dashed") +
-   labs(y = "IOI (ms)", subtitle = "IOI: Averaged (Dynamics)")
-p_ioi_dyn_all
+## Plot
+```{r plot-ioi, echo = FALSE}
+ggboxplot(ioi, x = "Condition", y = "Mean", color = "Condition", facet.by = "Skill", add = "jitter")
 ```
@@
 
-kot <- dt_kot[Subcomponent == "Legato" | Subcomponent == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(Instance, Condition, Skill, Subcomponent)]
-kot_all <- kot[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Subcomponent)]
-```
-
-## Plots
-```{r kot_plot, echo = FALSE}
-p_kot <- ggplot(kot, aes(x = Instance, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
-   labs(y = "KOT (ms)", subtitle = "KOT: Each instance (Articulation)")
-p_kot
-
-p_kot_all <- ggplot(kot_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   labs(y = "KOT (ms)", subtitle = "KOT: Averaged (Articulation)")
-p_kot_all
+kot <- dt_kot[Subcomponent != "NA" & Subcomponent != "LtoS" & Subcomponent != "StoL" & Subcomponent != "FtoP" & Subcomponent != "PtoF", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile, Condition, Skill, Subcomponent)]
 ```
@@
 ## Each instance
-```{r kot_stats_ind, echo = FALSE}
+```{r kot-each, echo = FALSE}
 kot
@@
 ## Averaged
-```{r kot_stats_all, echo = FALSE}
-kot_all
+```{r kor-averaged, echo = FALSE}
+kot[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), .(Condition, Skill, Subcomponent)]
+```
+
+## Plot
+### Articulation
+```{r plot-kot-art, echo = FALSE}
+ggboxplot(kot[Skill == "articulation"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
+```
+
+### Dynamics
+```{r plot-kor-dyn, echo = FALSE}
+ggboxplot(kot[Skill == "dynamics"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
 ```
@@
 # KV
-```{r kv, include = FALSE}
+```{r vel, include = FALSE}
 dt_vel <- data_onset
@@
 # assign Subcomponents
-# for each note
-dt_vel$Subcomponent <- NA
+dt_vel$Subcomponent <- "NA"
 # Legato
@@
 
-vel <- dt_vel[Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(Instance, Condition, Skill, Subcomponent)]
-vel_all <- vel[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Subcomponent)]
+vel <- dt_vel[Subcomponent != "NA", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(MidFile, Condition, Skill, Subcomponent)]
 ```
@@
 ## Each instance
-```{r vel_stats_ind, echo = FALSE}
+```{r vel-each, echo = FALSE}
 vel
@@
 ## Averaged
-```{r vel_stats_all, echo = FALSE}
-vel_all
+```{r vel-averaged, echo = FALSE}
+vel[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), .(Condition, Skill, Subcomponent)]
 ```
 
-## Plots
-```{r vel_plot, echo = FALSE}
-p_vel <- ggplot(vel, aes(x = Instance, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
-   labs(y = "Key Velocity", subtitle = "KV: Each instance (Dynamics)")
-p_vel
+## Plot
+### Dynamics
+```{r plot-vel-dyn, echo = FALSE}
+ggboxplot(vel[Skill == "dynamics"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
+```
 
-p_vel_all <- ggplot(vel_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
-   geom_bar(stat = "identity", position = position_dodge()) +
-   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-                 width = .2, position = position_dodge(.9)) +
-   labs(y = "Key Velocity", subtitle = "KV: Averaged (Dynamics)")
-p_vel_all
+### Articulation
+```{r plot-vel-art, echo = FALSE}
+ggboxplot(vel[Skill == "articulation"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
 ```
@@
 # KV-Diff
-```{r vel_diff, include = FALSE}
+```{r vel-diff, include = FALSE}
 # calculate differences and remove the first note
@@
 # assign Subcomponents
-# for intervals
-dt_vel_diff$Subcomponent <- NA
+dt_vel_diff$Subcomponent <- "NA"
 # Legato
@@
 
-# Assign Skill Change
+# assign Subcomponent Change
 for (i in change_1){
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "LtoS"
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "FtoP"
+dt_vel_diff[Skill == "articulation" & Interval == i]$Subcomponent <- "LtoS"
+dt_vel_diff[Skill == "dynamics" & Interval == i]$Subcomponent <- "FtoP"
 }
 for (i in change_2){
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "StoL"
-dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "PtoF"
+dt_vel_diff[Skill == "articulation" & Interval == i]$Subcomponent <- "StoL"
+dt_vel_diff[Skill == "dynamics" & Interval == i]$Subcomponent <- "PtoF"
 }
 
-vel_diff <- dt_vel_diff[Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(Instance, Condition, Skill, Subcomponent)]
-vel_diff_all <- vel_diff[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(Condition, Skill, Subcomponent)]
+vel_diff <- dt_vel_diff[Subcomponent == "LtoS" | Subcomponent == "StoL" | Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(MidFile, Condition, Skill, Subcomponent)]
 ```
@@
 ## Each instance
-```{r vel__diff_stats_ind, echo = FALSE}
+```{r vel-diff-each, echo = FALSE}
 vel_diff
@@
 ## Averaged
-```{r vel_diff_stats_all, echo = FALSE}
-vel_diff_all
+```{r vel-diff-averaged, echo = FALSE}
+vel_diff[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), .(Condition, Skill, Subcomponent)]
 ```
 
-## Plots
-```{r vel_diff_plot, echo = FALSE}
-p_vel_diff <- ggplot(vel_diff, aes(x = Instance, y = Mean, fill = Condition)) +
-geom_bar(stat = "identity", position = position_dodge()) +
-geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-              width = .2, position = position_dodge(.9)) +
-facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
-labs(y = "KV difference", subtitle = "KV-Diff: Each instance (Dynamics)")
-p_vel_diff
+## Plot
+### Dynamics
+```{r plot-vel-diff-dyn, echo = FALSE}
+ggboxplot(vel_diff[Skill == "dynamics"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
+```
 
-p_vel_diff_all <- ggplot(vel_diff_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
-geom_bar(stat = "identity", position = position_dodge()) +
-geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
-              width = .2, position = position_dodge(.9)) +
-labs(y = "KV difference", subtitle = "KV-Diff: Averaged (Dynamics)")
-p_vel_diff_all
+### Articulation
+```{r plot-vel-diff-art, echo = FALSE}
+ggboxplot(vel_diff[Skill == "articulation"], x = "Condition", y = "Mean", color = "Condition", facet.by = "Subcomponent", add = "jitter")
 ```

### 2021-03-04 material/expstimuli/stimuli.Rmd
round time2
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 # stimuli for practice trials
-for (i in 73:80){ # 4 stimuli for each category
+for (i in 73:80){ # 2 stimuli for each category
   subject = list_include$SubNr[i]
@@
 data$type <- NULL
-data$time2 <- (data$time/960)*1000 # deltatime to time (ms)
+data$time2 <- round((data$time/960)*1000) # deltatime to time (ms)
 

### 2021-05-10 analysis/analysis.Rmd
upload analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-02-17 analysis/analysis.Rmd
@@
 ---
-title: "Music Perception: Analysis"
+title: "Music Perception 2: Analysis"
 output: html_notebook
@@
 
-- 21 participants (experimental error = 1) >> 20 participants were included for analysis.
+- 15 participants were included for analysis.
 
@@
 ## Stimuli
-- Stimuli were selected from the previous study ([the sound of teaching music/experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1)).
-- 48 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 96 stimuli).
+- Stimuli were selected from the previous study ([the sound of teaching music/experiment-2](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2)).
+- 36 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 72 stimuli).
 The half of them was selected from the teaching condition and the other half was from the performing condition.
-  + 24 for teaching-articulation performances
-  + 24 for performing-articulation performances
-  + 24 for teaching-dynamics performances
-  + 24 for performing-dynamics performances
+  + 18 for teaching-articulation performances
+  + 18 for performing-articulation performances
+  + 18 for teaching-dynamics performances
+  + 18 for performing-dynamics performances
 
@@
 - 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques (expressions) separately. The order of the blocks was counterbalanced across participants.
-- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented across participants.
+- 36 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented across participants.
 
@@
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
+if (!require("qqplotr")) {install.packages("qqplotr"); require("qqplotr")}
 # stats
@@
 # individual
-individual <- data[subjectNumber != 9, .(N = .N, Sum = sum(Teaching)), by = .(subjectNumber, Condition, Skill, MidFile)]
+individual <- data[subjectNumber != 4, .(N = .N, Sum = sum(Teaching)), by = .(subjectNumber, Condition, Skill, MidFile)]
 individual<- individual[order(subjectNumber)]
@@
 data <- all_data[event == "Note On" | event == "Note Off"]
-data$NoteNr <- rep(1:134, nrow(data)/134)
+data$NoteNr <- rep(1:144, nrow(data)/144)
 data$channel <- NULL
@@
 # define subcomponents
-# For intervals
-ls_legato <- list(c(1:7), c(17:23), c(42:48), c(58:64))
-ls_staccato <- list(c(9:15), c(25:31), c(34:40), c(50:56))
-ls_forte <- list(c(1:7), c(17:23), c(42:48), c(58:64))
-ls_piano <- list(c(9:15), c(25:31), c(34:40), c(50:56))
+# for intervals
+ls_legato <- list(c(1:4), c(9:16), c(21:24), c(40:46))
+ls_staccato <- list(c(6:7), c(18:19), c(29:31), c(36:38), c(48:50), c(53:55), c(58:64))
+ls_forte <- list(c(1:4), c(9:16), c(21:24), c(40:46))
+ls_piano <- list(c(6:7), c(18:19), c(29:31), c(36:38), c(48:50), c(53:55), c(58:64))
 
-# For each note (velocity only)
-ls_legato_2 <- list(c(1:8), c(17:24), c(42:49), c(58:65))
-ls_staccato_2 <- list(c(9:16), c(25:32), c(34:41), c(50:57))
-ls_forte_2 <- list(c(1:8), c(17:24), c(42:49), c(58:65))
-ls_piano_2 <- list(c(9:16), c(25:32), c(34:41), c(50:57))
+# for each note (velocity)
+ls_legato_2 <- list(c(1:5), c(9:17), c(21:26), c(40:47))
+ls_staccato_2 <- list(c(6:8), c(18:20), c(29:32), c(36:39), c(48:51), c(53:56), c(58:65))
+ls_forte_2 <- list(c(1:5), c(9:17), c(21:26), c(40:47))
+ls_piano_2 <- list(c(6:8), c(18:20), c(29:32), c(36:39), c(48:51), c(53:56), c(58:65))
 
-# Define Skill Change (LtoS, FtoP)
-change_1 <- c(8, 24, 49)
-# Define Skill Change (StoL, PtoF)
-change_2 <- c(16, 41, 57)
+# define Component Change (LtoS, FtoP)
+change_1 <- c(5, 17, 47)
+# define Component Change (StoL, PtoF)
+change_2 <- c(8, 20, 39)
 ```
@@
 
-data_onset$IOI <- diff(c(0, data_onset$time))
+data_onset$IOI <- diff(c(0, data_onset$time2))
 dt_ioi <- data_onset[NoteNr != 1]
-dt_ioi$Interval <- rep(1:66, nrow(dt_ioi)/66)
+dt_ioi$Interval <- rep(1:71, nrow(dt_ioi)/71)
 
@@
 
-## All (***)
+## All (n.s.)
 ```{r ioi-all, echo = FALSE}
@@
 
-## Dynamics (**)
+## Dynamics (n.s.)
 ```{r, echo = FALSE}
 cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
-```
-
-## Each subcomponent
-```{r ioi-sub, echo = FALSE}
-ioi_sub <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill, Subcomponent)]
-
-# sorted
-ioi <- ioi[order(MidFile)]
-
-# plot
-ioi$Teaching <- rating$Mean_Percent
-ioi$TeachingSD <- rating$SD_Percent
-
-ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 
-## All (***)
+## All (n.s.)
 ```{r ioi-tra-all, echo = FALSE}
@@
 
-## Articulation (***)
+## Articulation (n.s.)
 ```{r, echo = FALSE}
@@
 
-## Dynamics (**)
+## Dynamics (n.s.)
 ```{r, echo = FALSE}
@@
 ```
+
 ## Dynamics (n.s.)
@@
 dt_kot <- data_onset[NoteNr != 1]
-dt_kot$Interval <- rep(1:66, nrow(dt_kot)/66)
+dt_kot$Interval <- rep(1:71, nrow(dt_kot)/71)
 
@@
 ```
-## Legato (**)
+## Legato (n.s.)
 ```{r, echo = FALSE}
@@
 
-## Staccato (***)
+## Staccato (n.s.)
 ```{r, echo = FALSE}
@@
 dt_vel <- data_onset
-dt_vel$Note <- rep(1:67, nrow(dt_vel)/67)
+dt_vel$Note <- rep(1:72, nrow(dt_vel)/72)
 # assign Subcomponents
@@
 
-## Forte (***)
+## Forte (*)
 ```{r, echo = FALSE}
@@
 
-## Piano (n.s.)
+## Piano (*)
 ```{r, echo = FALSE}
@@
 # assign Interval
-dt_vel_diff$Interval <- rep(1:66, nrow(dt_vel_diff)/66)
+dt_vel_diff$Interval <- rep(1:71, nrow(dt_vel_diff)/71)
 
@@
 ```
-## Legato to Staccato (n.s.)
+## Legato to Staccato (*)
 ```{r, echo = FALSE}
@@
 # KOT
-## Legato (**)
+## Legato (n.s.)
 ```{r kot-partial-leg, echo = TRUE}
@@
 
-## Staccato (*)
+## Staccato (n.s.)
 ```{r kot-partial-sta, echo = TRUE}
@@
 # KV
-## Forte (*)
+## Forte (n.s.)
 ```{r vel-partial-for, echo = TRUE}
@@
 # KV-Diff
-## Forte to Piano (n.s.)
+## Forte to Piano (***)
 ```{r vel-diff-partial-ftop, echo = TRUE}

### 2021-05-10 analysis/questionnaire.Rmd
upload quesionnaire summary
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: "Music Perception: Questionnaire"
output: html_notebook
---

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
```

# Questionnaire

```{r read, echo = FALSE}
dt <- fread("questionnaire.csv", header = T, sep = ",", dec = ".", na.string = "NA")

# change some colnames
colnames(dt)[2] <- "SubNr"
colnames(dt)[3] <- "Age"
colnames(dt)[4] <- "Gender"
colnames(dt)[7] <- "Handedness"

# extract the total number of years of training for the longest instrument (input manually based on the original csv file)
dt$Training <- c(7, 7, 10, 6, 7, 6, 6, 20, 12, 7, 7, 11, 9, 16, 20, 15, 19, 14, 24, 12, 14)

# exclude participants
dt_included <- dt[SubNr != 9]

print(dt_included)
```

## Descriptive stats for included participants
- Number of included participants: `r nrow(dt_included)` (mean age: `r round(mean(dt_included$Age), 2)`, sd: `r round(sd(dt_included$Age), 2)`)
- Male: `r nrow(dt_included[Gender == "Male"])` (mean age: `r round(mean(dt_included[Gender == "Male"]$Age), 2)`, sd: `r round(sd(dt_included[Gender == "Male"]$Age), 2)`)
- Female: `r nrow(dt_included[Gender == "Female"])` (mean age: `r round(mean(dt_included[Gender == "Female"]$Age), 2)`, sd: `r round(sd(dt_included[Gender == "Female"]$Age), 2)`)
- Average training years: `r round(mean(dt_included$Training), 2)` years (*SD* = `r round(sd(dt_included$Training), 2)`)
- Handedness: Right (`r nrow(dt_included[Handedness == "Right"])`), Left (`r nrow(dt_included[Handedness == "Left"])`), Both (`r nrow(dt_included[Handedness == "Both"])`)

## Some descriptive questions
1. Did you try to perform differently when you are asked to play as a teacher during the experiment? If so, please describe how you changed your performance?

```{r 1, echo = FALSE}
data.table("Answer" = dt_included$`Have you noticed anything special regarding the tasks in the experiment? If any, please describe below.`)
```

### 2021-05-10 analysis/analysis.Rmd
update comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
remove significant levels
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-- 15 participants were included for analysis.
+- 16 participants (experimental error = 1) >> 15 participants were included for analysis.
 
@@
 
-## All (n.s.)
+## All ()
 ```{r ioi-all, echo = FALSE}
@@
 ```
-## Articulation (n.s.)
+## Articulation ()
 ```{r, echo = FALSE}
@@
 
-## Dynamics (n.s.)
+## Dynamics ()
 ```{r, echo = FALSE}
@@
 
-## All (n.s.)
+## All ()
 ```{r ioi-tra-all, echo = FALSE}
@@
 
-## Articulation (n.s.)
+## Articulation ()
 ```{r, echo = FALSE}
@@
 
-## All (n.s.)
+## All ()
 ```{r cv, echo = FALSE}
@@
 ```
-## Legato (n.s.)
+## Legato ()
 ```{r, echo = FALSE}
@@
 
-## Staccato (n.s.)
+## Staccato ()
 ```{r, echo = FALSE}
@@
 
-## Forte (n.s.)
+## Forte ()
 ```{r, echo = FALSE}
@@
 
-## Piano (n.s.)
+## Piano ()
 ```{r, echo = FALSE}
@@
 
-## Forte (*)
+## Forte ()
 ```{r, echo = FALSE}
@@
 
-## Piano (*)
+## Piano ()
 ```{r, echo = FALSE}
@@
 
-## Forte to Piano (***)
+## Forte to Piano ()
 ```{r, echo = FALSE}
@@
 
-## Piano to Forte (***)
+## Piano to Forte ()
 ```{r, echo = FALSE}
@@
 ```
-## Legato to Staccato (*)
+## Legato to Staccato ()
 ```{r, echo = FALSE}
@@
 
-## Staccato to Legato (n.s.)
+## Staccato to Legato ()
 ```{r, echo = FALSE}
@@
 # KOT
-## Legato (n.s.)
+## Legato ()
 ```{r kot-partial-leg, echo = TRUE}
@@
 
-## Staccato (n.s.)
+## Staccato ()
 ```{r kot-partial-sta, echo = TRUE}
@@
 # KV
-## Forte (n.s.)
+## Forte ()
 ```{r vel-partial-for, echo = TRUE}
@@
 
-## Piano (n.s.)
+## Piano ()
 ```{r vel-partial-pia, echo = TRUE}
@@
 # KV-Diff
-## Forte to Piano (***)
+## Forte to Piano ()
 ```{r vel-diff-partial-ftop, echo = TRUE}
@@
 
-## Piano to Forte (***)
+## Piano to Forte ()
 ```{r vel-diff-partial-ptof, echo = TRUE}

### 2021-05-10 analysis/questionnaire.Rmd
upload questionnaire summary (up to 14)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ---
-title: "Music Perception: Questionnaire"
+title: "Music Perception 2: Questionnaire"
 output: html_notebook
@@
 # extract the total number of years of training for the longest instrument (input manually based on the original csv file)
-dt$Training <- c(7, 7, 10, 6, 7, 6, 6, 20, 12, 7, 7, 11, 9, 16, 20, 15, 19, 14, 24, 12, 14)
+dt$Training <- c(14, 13, 7, 18, 23, 12, 17, 20, 12, 7, 12, 7, 7, 13, 20)
 
 # exclude participants
-dt_included <- dt[SubNr != 9]
+dt_included <- dt[SubNr != 4]
 

### 2021-05-31 material/expstimuli/selection/stimuli.Rmd
correct comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
count the number of original performances
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 # Filtering
-```{r filtering, eval = FALSE, include = FALSE}
+```{r filtering, include = FALSE}
 # read functions
@@
 dt_ioi$Interval <- rep(1:66, nrow(dt_ioi)/66)
-ioi <- dt_ioi[Interval != 32 & Interval != 33 & Interval != 65 & Interval != 66, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, BlockNr, TrialNr)]
-mean_ioi <- mean(ioi$Mean)
-sd_ioi <- sd(ioi$Mean)
-ioi_include <- ioi[Mean < mean_ioi+2*sd_ioi & Mean > mean_ioi-2*sd_ioi]
+ioi_original <- dt_ioi[Interval != 32 & Interval != 33 & Interval != 65 & Interval != 66, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, BlockNr, TrialNr, Condition)]
+mean_ioi <- mean(ioi_original$Mean)
+sd_ioi <- sd(ioi_original$Mean)
+ioi_include <- ioi_original[Mean < mean_ioi+2*sd_ioi & Mean > mean_ioi-2*sd_ioi]
 
@@
 
-## Histogram
-- Gray vertical lines indicate ideal tempi (300ms for 100bpm, 273ms for 110bpm, 250ms for 120bpm)
+## IOIs Histogram
+- Gray vertical lines indicate the ideal tempo (188ms for 80 bpm).
 
@@
 ```{r plot-hist, echo = FALSE}
-gghistogram(ioi, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 188, color = "gray", size = 1)
+gghistogram(ioi_original, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 188, color = "gray", size = 1)
 ```
+- the number of performances in the teaching condition: `r nrow(ioi_original[Condition == "teaching"])`
+- the number of performances in the performing condition: `r nrow(ioi_original[Condition == "performing"])`
 
@@
 ```
+- the number of performances in the teaching condition: `r nrow(ioi_include[Condition == "teaching"])`
+- the number of performances in the performing condition: `r nrow(ioi_include[Condition == "performing"])`
 
@@
 ```{r stimuli, include = FALSE}
-rm(list = ls()) # clear all
+#rm(list = ls()) # clear all
 

### 2021-06-03 analysis/analysis.R
removed some stats from plots / rerun analysis after removing empty files
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -1,50 +1,4 @@
----
-title: "Music Perception 1: Analysis"
-output: html_notebook
----
-
-- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`
-
-- 21 participants (experimental error = 1) >> 20 participants were included for analysis.
-
-# Experiment
-
-## Stimuli
-- Stimuli were selected from the previous study ([the sound of teaching music/experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1)).
-- 48 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 96 stimuli). The half of them was selected from the teaching condition and the other half was from the performing condition.
-  + 24 for teaching-articulation performances
-  + 24 for performing-articulation performances
-  + 24 for teaching-dynamics performances
-  + 24 for performing-dynamics performances
-
-## Design
-
-- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques (expressions) separately. The order of the blocks was counterbalanced across participants.
-- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented across participants.
-
-## Procedure
-1. Musicians (> 6yo experience) were asked to listen to a number of recordings and judge whether each performance was produced for teaching purposes or not.
-
-Actual instruction:
-```
-Each performance was produced in order to either 1) teach the musical expressive technique (as a teacher) or 2) perform their best (as a performer).
-
-You will be asked to judge whether each performer had the intention to teach or not by pressing the 'Yes' <Left> or 'No' <Right> key.
-```
-
-2. Participants pressed "YES" if they think the recording was produced for teaching (as a teacher) whereas they pressed "NO" if they thought the recording was produced for performing (as a performer).
-
[…]

### 2021-06-03 analysis/questionnaire.R
export R code / change the title
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -1,0 +1,33 @@
+## ----setup, include = FALSE----------------------------------
+# packages
+# data manipulation
+if (!require("data.table")) {install.packages("data.table"); require("data.table")}
+# plot
+if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
+
+
+## ----read, echo = FALSE--------------------------------------
+dt <- fread("questionnaire.csv", header = T, sep = ",", dec = ".", na.string = "NA")
+
+# change some colnames
+colnames(dt)[2] <- "SubNr"
+colnames(dt)[3] <- "Age"
+colnames(dt)[4] <- "Gender"
+colnames(dt)[7] <- "Handedness"
+
+# extract the total number of years of training for the longest instrument (input manually based on the original csv file)
+dt$Training <- c(7, 7, 10, 6, 7, 6, 6, 20, 12, 7, 7, 11, 9, 16, 20, 15, 19, 14, 24, 12, 14)
+
+# exclude participants
+dt_included <- dt[SubNr != 9]
+
+print(dt_included)
+
+
+## ----1, echo = FALSE-----------------------------------------
+data.table("Answer" = dt_included$`Have you noticed anything special regarding the tasks in the experiment? If any, please describe below.`)
+
+
+## ----export, include = FALSE---------------------------------
+knitr::purl("questionnaire.Rmd")
+

### 2021-06-07 analysis/analysis.R
export R code
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -1,50 +1,4 @@
----
-title: "Music Perception 2: Analysis"
-output: html_notebook
----
-
-- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`
-
-- 15 participants (experimental error = 1) >> 14 participants were included for analysis.
-
-# Experiment
-
-## Stimuli
-- Stimuli were selected from the previous study ([the sound of teaching music/experiment-2](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2)).
-- 36 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 72 stimuli). The half of them was selected from the teaching condition and the other half was from the performing condition.
-  + 18 for teaching-articulation performances
-  + 18 for performing-articulation performances
-  + 18 for teaching-dynamics performances
-  + 18 for performing-dynamics performances
-
-## Design
-
-- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques (expressions) separately. The order of the blocks was counterbalanced across participants.
-- 36 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented across participants.
-
-## Procedure
-1. Musicians (> 6yo experience) were asked to listen to a number of recordings and judge whether each performance was produced for teaching purposes or not.
-
-Actual instruction:
-```
-Each performance was produced in order to either 1) teach the musical expressive technique (as a teacher) or 2) perform their best (as a performer).
-
-You will be asked to judge whether each performer had the intention to teach or not by pressing the 'Yes' <Left> or 'No' <Right> key.
-```
-
-2. Participants pressed "YES" if they think the recording was produced for teaching (as a teacher) whereas they pressed "NO" if they thought the recording was produced for performing (as a performer).
-
[…]

### 2021-06-07 analysis/questionnaire.R

@@ -1,0 +1,33 @@
+## ----setup, include = FALSE----------------------------------
+# packages
+# data manipulation
+if (!require("data.table")) {install.packages("data.table"); require("data.table")}
+# plot
+if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
+
+
+## ----read, echo = FALSE--------------------------------------
+dt <- fread("questionnaire.csv", header = T, sep = ",", dec = ".", na.string = "NA")
+
+# change some colnames
+colnames(dt)[2] <- "SubNr"
+colnames(dt)[3] <- "Age"
+colnames(dt)[4] <- "Gender"
+colnames(dt)[7] <- "Handedness"
+
+# extract the total number of years of training for the longest instrument (input manually based on the original csv file)
+dt$Training <- c(14, 13, 7, 18, 23, 12, 17, 20, 12, 7, 12, 7, 7, 13, 20)
+
+# exclude participants
+dt_included <- dt[SubNr != 4]
+
+print(dt_included)
+
+
+## ----1, echo = FALSE-----------------------------------------
+data.table("Answer" = dt_included$`Have you noticed anything special regarding the tasks in the experiment? If any, please describe below.`)
+
+
+## ----export, include = FALSE---------------------------------
+knitr::purl("questionnaire.Rmd")
+

### 2021-06-07 material/expstimuli/stimuli.Rmd
correct comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
calculate total number of performances
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-ioi <- dt_ioi[Interval != 25 & Interval != 26 & Interval != 27 & Interval != 28 & Interval != 32 & Interval != 33 & Interval != 34 & Interval != 35 & Interval != 51 & Interval != 52 & Interval != 56 & Interval != 57 & Interval != 65 & Interval != 66 & Interval != 67 & Interval != 68 & Interval != 69 & Interval != 70 & Interval != 71, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, BlockNr, TrialNr, Tempo)]
-mean_ioi <- mean(ioi$Mean)
-sd_ioi <- sd(ioi$Mean)
-ioi_include <- ioi[Mean < mean_ioi+2*sd_ioi & Mean > mean_ioi-2*sd_ioi]
+ioi_original <- dt_ioi[Interval != 25 & Interval != 26 & Interval != 27 & Interval != 28 & Interval != 32 & Interval != 33 & Interval != 34 & Interval != 35 & Interval != 51 & Interval != 52 & Interval != 56 & Interval != 57 & Interval != 65 & Interval != 66 & Interval != 67 & Interval != 68 & Interval != 69 & Interval != 70 & Interval != 71, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, BlockNr, TrialNr, Tempo, Condition)]
+mean_ioi <- mean(ioi_original$Mean)
+sd_ioi <- sd(ioi_original$Mean)
+ioi_include <- ioi_original[Mean < mean_ioi+2*sd_ioi & Mean > mean_ioi-2*sd_ioi]
 
@@
 
-## Histogram
+## IOIs Histogram
 - Exclude performances outside 2sd
@@
 ```{r plot-hist, echo = FALSE}
-ioi$Tempo <- factor(ioi$Tempo)
-gghistogram(ioi, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
-gghistogram(ioi, x = "Mean", fill = "Tempo", color = "Tempo", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
+ioi_original$Tempo <- factor(ioi_original$Tempo)
+gghistogram(ioi_original, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
+gghistogram(ioi_original, x = "Mean", fill = "Tempo", color = "Tempo", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
 ```
+- the number of performances in the teaching condition: `r nrow(ioi_original[Condition == "teaching"])`
+- the number of performances in the performing condition: `r nrow(ioi_original[Condition == "performing"])`
 

### 2021-06-10 analysis/prereg_analysis/prereg_analysis.Rmd
upload preregistered analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: "Music Perception 1: Preregistered Analysis"
output: html_notebook
---

- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`

- 21 participants (experimental error = 1) >> 20 participants were included for analysis.

# Experiment
## Preregistered Analysis
We originally had a analysis plan to look at the accuracy of participants' judgements whether participants would be able to judge stimuli from the teaching condition as "teaching". For more detailed explanations, please see [the OSF preregistration](https://osf.io/z3j69).

## Stimuli
- Stimuli were selected from the previous study ([the sound of teaching music/experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1)).
- 48 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 96 stimuli). The half of them was selected from the teaching condition and the other half was from the performing condition.
  + 24 for teaching-articulation performances
  + 24 for performing-articulation performances
  + 24 for teaching-dynamics performances
  + 24 for performing-dynamics performances

## Design

- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques (expressions) separately. The order of the blocks was counterbalanced across participants.
- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented across participants.

## Procedure
1. Musicians (> 6yo experience) were asked to listen to a number of recordings and judge whether each performance was produced for teaching purposes or not.

Actual instruction:
```
Each performance was produced in order to either 1) teach the musical expressive technique (as a teacher) or 2) perform their best (as a performer).

You will be asked to judge whether each performer had the intention to teach or not by pressing the 'Yes' <Left> or 'No' <Right> key.
```

2. Participants pressed "YES" if they think the recording was produced for teaching (as a teacher) whereas they pressed "NO" if they thought the recording was produced for performing (as a performer).

3. Correct answers would be 1) participants pressed "YES" when they listened to teaching performances or 2) participants pressed "NO" when they listened to performing performances.

## Dependent variables
- Accuracy (Correct %)
   + "YES" to teaching stimuli: correct
   + "NO" to performing stimuli: correct
   + "NO" to teaching stimuli: incorrect
   + "YES" to performing stimuli: incorrect

```{r packages, include = FALSE}
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# midi
if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
# stats
if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
if (!require("performance")) {install.packages("performance"); require("performance")}
```

```{r read, include = FALSE}
# read files and combine them
data_ls <- list.files("../data", pattern = "csv")
combined <- lapply(data_ls, function(f){
  fread(paste("../data/", f, sep = ""), sep = ",")
})
all_data <- do.call(rbind.data.frame, combined)

# remove irrelevant strings
data <- all_data[expMode == "experiment"]
data$MidFile <- gsub("./mid/", "", data$midFile)
data$MidFile <- gsub(".mid", "", data$MidFile)

# name conditions
data$Condition <- "NA"
data$Skill <- "NA"
data[grepl("_t_", midFile)]$Condition <- "teaching"
data[grepl("_p_", midFile)]$Condition <- "performing"
data[grepl("a_", midFile)]$Skill <- "articulation"
data[grepl("d_", midFile)]$Skill <- "dynamics"

# check correct or incorrect
data$Correct <- 0
data[Condition == "teaching" & rating == "Yes"]$Correct <- 1
data[Condition == "performing" & rating == "No"]$Correct <- 1

all <- data[expMode == "experiment", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill)]
all[order(subjectNumber, Condition, Skill)]
```

# Results
- significance levels: `***: 0.001, **: 0.01, *: 0.05`

## 1. Statistics
### All
```{r acc, echo = FALSE}
# individual
ind_data <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber)]
ind_data <- ind_data[order(subjectNumber)]

# all
subset <- ind_data[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/96)*100, SD_Percent = (sd(Sum)/96)*100)]
subset
```

```{r plot, echo = FALSE}
ggboxplot(ind_data, x = "N", y = "Percent", add = "dotplot", xlab = FALSE) + ylab("Correct %") + theme(axis.text.x = element_blank())
```

### One-sample *t*-test
```{r t-test, echo = FALSE}
# normality check
shapiro.test(ind_data$Percent)

t.test(ind_data$Percent, mu = 50, alternative = "two.sided")
```

### Articulation vs. Dynamics

```{r plot2, echo = FALSE}
ind_data_ad <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Skill)]
ind_data_ad <- ind_data_ad[order(subjectNumber, Skill)]

subset_ad <- ind_data_ad[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100), by = .(Skill)]
subset_ad

data_box <- data.table(subjectNumber = ind_data_ad$subjectNumber, articulation = ind_data_ad[Skill == "articulation"]$Percent, dynamics = ind_data_ad[Skill == "dynamics"]$Percent)
box <- ggpaired(data_box, cond1 = "articulation", cond2 = "dynamics", line.color = "gray", line.size = 0.4, ylab = "Correct %")
box
```

## One-sample *t*-test
### Articulation
```{r t-test-a, echo = FALSE}
# normality check
shapiro.test(ind_data_ad[Skill == "articulation"]$Percent)

t.test(ind_data_ad[Skill == "articulation"]$Percent, mu = 50, alternative = "two.sided")
```

### Dynamics
```{r t-test-d, echo = FALSE}
# normality check
shapiro.test(ind_data_ad[Skill == "dynamics"]$Percent)

t.test(ind_data_ad[Skill == "dynamics"]$Percent, mu = 50, alternative = "two.sided")
```

## Paired *t*-test between articulation and dynamics
```{r p-t-test, echo = FALSE}
# normality check
shapiro.test(ind_data_ad[Skill == "dynamics"]$Percent-ind_data_ad[Skill == "articulation"]$Percent)

t.test(ind_data_ad[Skill == "articulation"]$Percent, ind_data_ad[Skill == "dynamics"]$Percent, paired = TRUE)
```

```{r export, include = FALSE}
knitr::purl("prereg_analysis.Rmd")
```

### 2021-06-10 analysis/prereg_analysis/prereg_analysis.R

@@ -1,0 +1,99 @@
+## ----packages, include = FALSE------------------------------
+# data manipulation
+if (!require("data.table")) {install.packages("data.table"); require("data.table")}
+# midi
+if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
+# plot
+if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
+# stats
+if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
+if (!require("performance")) {install.packages("performance"); require("performance")}
+
+
+## ----read, include = FALSE----------------------------------
+# read files and combine them
+data_ls <- list.files("../data", pattern = "csv")
+combined <- lapply(data_ls, function(f){
+  fread(paste("../data/", f, sep = ""), sep = ",")
+})
+all_data <- do.call(rbind.data.frame, combined)
+
+# remove irrelevant strings
+data <- all_data[expMode == "experiment"]
+data$MidFile <- gsub("./mid/", "", data$midFile)
+data$MidFile <- gsub(".mid", "", data$MidFile)
+
+# name conditions
+data$Condition <- "NA"
+data$Skill <- "NA"
+data[grepl("_t_", midFile)]$Condition <- "teaching"
+data[grepl("_p_", midFile)]$Condition <- "performing"
+data[grepl("a_", midFile)]$Skill <- "articulation"
+data[grepl("d_", midFile)]$Skill <- "dynamics"
+
+# check correct or incorrect
+data$Correct <- 0
+data[Condition == "teaching" & rating == "Yes"]$Correct <- 1
+data[Condition == "performing" & rating == "No"]$Correct <- 1
+
+all <- data[expMode == "experiment", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill)]
+all[order(subjectNumber, Condition, Skill)]
+
+
+## ----acc, echo = FALSE--------------------------------------
+# individual
+ind_data <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber)]
+ind_data <- ind_data[order(subjectNumber)]
+
+# all
[…]

### 2021-06-11 analysis/analysis.Rmd
add shapiro.test
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-02-24 analysis/analysis.Rmd
@@
 ---
-title: "Music Perception: Analysis"
+title: "Music Perception 1: Analysis"
 output: html_notebook
@@
 # read files and combine them
-data_ls <- list.files("data")
+data_ls <- list.files("data", pattern = "csv")
 combined <- lapply(data_ls, function(f){
@@
 ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          add.params = list(fill = "lightgray"), conf.int = TRUE,
           xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
@@
 ```{r, echo = FALSE}
-cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
+# normality check
+shapiro.test(ioi[Skill == "articulation"]$Teaching)
+shapiro.test(ioi[Skill == "articulation"]$Mean)
+
+cor_ioi_art <- cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
+cor_ioi_art
 ```
@@
 ```{r, echo = FALSE}
-cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
-```
+# normality check
+shapiro.test(ioi[Skill == "dynamics"]$Teaching)
+shapiro.test(ioi[Skill == "dynamics"]$Mean)
 
-## Each subcomponent
-```{r ioi-sub, echo = FALSE}
-ioi_sub <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill, Subcomponent)]
+cor_ioi_dyn <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
+cor_ioi_dyn
 
-# sorted
-ioi <- ioi[order(MidFile)]
-
-# plot
-ioi$Teaching <- rating$Mean_Percent
-ioi$TeachingSD <- rating$SD_Percent
-
-ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
+cor_ioi_dyn_spearman <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean, method = "spearman")
+cor_ioi_dyn_spearman
 ```
@@
 ggscatter(ioi_tra, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          add.params = list(fill = "lightgray"), conf.int = TRUE,
           xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
+shapiro.test(ioi_tra[Skill == "articulation"]$Mean)
+
 cor.test(ioi_tra[Skill == "articulation"]$Teaching, ioi_tra[Skill == "articulation"]$Mean)
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
+shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)
+
 cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean)
@@
 ggscatter(cv, x = "CV", y = "Teaching", color = "Skill", add = "reg.line",
-          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
+          add.params = list(fill = "lightgray"), conf.int = TRUE,
           xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(cv[Skill == "articulation"]$Teaching)
+shapiro.test(cv[Skill == "articulation"]$CV)
+
 cor.test(cv[Skill == "articulation"]$Teaching, cv[Skill == "articulation"]$CV)
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(cv[Skill == "dynamics"]$Teaching)
+shapiro.test(cv[Skill == "dynamics"]$CV)
+
 cor.test(cv[Skill == "dynamics"]$Teaching, cv[Skill == "dynamics"]$CV)
@@
 ```{r, echo = FALSE}
-cor.test(kot_all[Subcomponent == "Legato"]$Teaching, kot_all[Subcomponent == "Legato"]$Mean)
+# normality check
+shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
+shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)
+
+cor_kot_leg <- cor.test(kot_all[Subcomponent == "Legato"]$Teaching, kot_all[Subcomponent == "Legato"]$Mean)
+cor_kot_leg
 ```
@@
 ```{r, echo = FALSE}
-cor.test(kot_all[Subcomponent == "Staccato"]$Teaching, kot_all[Subcomponent == "Staccato"]$Mean)
+# normality check
+shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
+shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)
+
+cor_kot_sta <- cor.test(kot_all[Subcomponent == "Staccato"]$Teaching, kot_all[Subcomponent == "Staccato"]$Mean)
+cor_kot_sta
 ```
@@
 ```{r, echo = FALSE}
-cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean)
+# normality check
+shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
+shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)
+
+cor_kot_for <- cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean)
+cor_kot_for
+
+cor_kot_for_spearman <- cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean, method = "spearman")
+cor_kot_for_spearman
 ```
@@
 ```{r, echo = FALSE}
-cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean)
+# normality check
+shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
+shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)
+
+cor_kot_pia <- cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean)
+cor_kot_pia
+
+cor_kot_pia_spearman <- cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean, method = "spearman")
+cor_kot_pia_spearman
 ```
@@
 ```{r, echo = FALSE}
-cor.test(vel_all[Subcomponent == "Forte"]$Teaching, vel_all[Subcomponent == "Forte"]$Mean)
+# normality check
+shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
+shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)
+
+cor_vel_for <- cor.test(vel_all[Subcomponent == "Forte"]$Teaching, vel_all[Subcomponent == "Forte"]$Mean)
+cor_vel_for
 ```
@@
 ```{r, echo = FALSE}
-cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean)
+# normality check
+shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
+shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)
+
+cor_vel_pia <- cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean)
+cor_vel_pia
 ```
@@
 ```{r, echo = FALSE}
-cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean)
+# normality check
+shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
+shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)
+
+cor_vel_leg <- cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean)
+cor_vel_leg
+
+cor_vel_leg_spearman <- cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean, method = "spearman")
+cor_vel_leg_spearman
 ```
@@
 ```{r, echo = FALSE}
-cor.test(vel_all[Subcomponent == "Staccato"]$Teaching, vel_all[Subcomponent == "Staccato"]$Mean)
+# normality check
+shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
+shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)
+
+cor_vel_sta <- cor.test(vel_all[Subcomponent == "Staccato"]$Teaching, vel_all[Subcomponent == "Staccato"]$Mean)
+cor_vel_sta
 ```
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") +ylim(0, 100)
+          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
@@
 ```{r, echo = FALSE}
-cor.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching, vel_diff_all[Subcomponent == "FtoP"]$Mean)
+# normality check
+shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
+shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)
+
+cor_vel_diff_ftop <- cor.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching, vel_diff_all[Subcomponent == "FtoP"]$Mean)
+cor_vel_diff_ftop
 ```
@@
 ```{r, echo = FALSE}
-cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean)
+# normality check
+shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
+shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)
+
+cor_vel_diff_ptof <- cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean)
+cor_vel_diff_ptof
 ```
@@
 ```{r, echo = FALSE}
-cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean)
+# normality check
+shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
+shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)
+
+cor_vel_diff_ltos <- cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean)
+cor_vel_diff_ltos
+
+cor_vel_diff_ltos_spearman <- cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean, method = "spearman")
+cor_vel_diff_ltos_spearman
 ```
@@
 ```{r, echo = FALSE}
-cor.test(vel_diff_all[Subcomponent == "StoL"]$Teaching, vel_diff_all[Subcomponent == "StoL"]$Mean)
+# normality check
+shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Teaching)
+shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Mean)
+
+cor_vel_diff_stol <- cor.test(vel_diff_all[Subcomponent == "StoL"]$Teaching, vel_diff_all[Subcomponent == "StoL"]$Mean)
+cor_vel_diff_stol
 ```
@@
 ```
+```{r export, include = FALSE}
+knitr::purl("analysis.Rmd")
+```

### 2021-06-11 analysis/analysis.R

@@ -159,13 +159,24 @@ ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
 
 
 ## ---- echo = FALSE------------------------------------------
+# normality check
+shapiro.test(ioi[Skill == "articulation"]$Teaching)
+shapiro.test(ioi[Skill == "articulation"]$Mean)
+
 cor_ioi_art <- cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
 cor_ioi_art
 
 
 ## ---- echo = FALSE------------------------------------------
+# normality check
+shapiro.test(ioi[Skill == "dynamics"]$Teaching)
+shapiro.test(ioi[Skill == "dynamics"]$Mean)
+
 cor_ioi_dyn <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
 cor_ioi_dyn
+
+cor_ioi_dyn_spearman <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean, method = "spearman")
+cor_ioi_dyn_spearman
 
 
 ## ----ioi-tra-all, echo = FALSE------------------------------
@@ -184,10 +195,18 @@ ggscatter(ioi_tra, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line"
 
 
 ## ---- echo = FALSE------------------------------------------
+# normality check
+shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
+shapiro.test(ioi_tra[Skill == "articulation"]$Mean)
+
 cor.test(ioi_tra[Skill == "articulation"]$Teaching, ioi_tra[Skill == "articulation"]$Mean)
 
 
 ## ---- echo = FALSE------------------------------------------
+# normality check
+shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
+shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)
+
 cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean)
 
 
@@ -207,10 +226,18 @@ ggscatter(cv, x = "CV", y = "Teaching", color = "Skill", add = "reg.line",
 
 
 ## ---- echo = FALSE------------------------------------------
+# normality check
[…]

### 2021-06-22 analysis/analysis.Rmd
add exact = FALSE to spearman's tests
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-cor_ioi_dyn_spearman <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean, method = "spearman")
+cor_ioi_dyn_spearman <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
 cor_ioi_dyn_spearman
@@
 cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean)
+
+cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
 ```
@@
 
-cor_kot_for_spearman <- cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean, method = "spearman")
+cor_kot_for_spearman <- cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean, method = "spearman", exact = FALSE)
 cor_kot_for_spearman
@@
 
-cor_kot_pia_spearman <- cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean, method = "spearman")
+cor_kot_pia_spearman <- cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
 cor_kot_pia_spearman
@@
 
-cor_vel_leg_spearman <- cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean, method = "spearman")
+cor_vel_leg_spearman <- cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean, method = "spearman", exact = FALSE)
 cor_vel_leg_spearman
@@
 
-cor_vel_diff_ltos_spearman <- cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean, method = "spearman")
+cor_vel_diff_ltos_spearman <- cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean, method = "spearman", exact = FALSE)
 cor_vel_diff_ltos_spearman

### 2021-06-22 analysis/analysis.R

@@ -175,7 +175,7 @@ shapiro.test(ioi[Skill == "dynamics"]$Mean)
 cor_ioi_dyn <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
 cor_ioi_dyn
 
-cor_ioi_dyn_spearman <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean, method = "spearman")
+cor_ioi_dyn_spearman <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
 cor_ioi_dyn_spearman
 
 
@@ -330,7 +330,7 @@ shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)
 cor_kot_for <- cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean)
 cor_kot_for
 
-cor_kot_for_spearman <- cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean, method = "spearman")
+cor_kot_for_spearman <- cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean, method = "spearman", exact = FALSE)
 cor_kot_for_spearman
 
 
@@ -342,7 +342,7 @@ shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)
 cor_kot_pia <- cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean)
 cor_kot_pia
 
-cor_kot_pia_spearman <- cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean, method = "spearman")
+cor_kot_pia_spearman <- cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
 cor_kot_pia_spearman
 
 
@@ -419,7 +419,7 @@ shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)
[…]

### 2021-06-24 analysis/variability.Rmd
add variability analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: "Music Perception 1: Variability Analysis"
output: html_notebook
---

- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`

- 21 participants (experimental error = 1) >> 20 participants were included for analysis.

# Data analysis
- Pearson's correlation (if normality is violated, Spearman's rank correlation instead) between variability measurements and participants' judgments as "teaching"

## Variables
- CV for IOIs (tempo)
- SD for KOT (articulation)
- CV for KOT (articulation)
- CV for KV (dynamics)

```{r packages, include = FALSE}
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# midi
if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
```

```{r read, include = FALSE}
# read files and combine them
data_ls <- list.files("data", pattern = "csv")
combined <- lapply(data_ls, function(f){
  fread(paste("data/", f, sep = ""), sep = ",")
})
all_data <- do.call(rbind.data.frame, combined)

# remove irrelevant strings
data <- all_data[expMode == "experiment"]
data$MidFile <- gsub("./mid/", "", data$midFile)
data$MidFile <- gsub(".mid", "", data$MidFile)

# name conditions
data$Condition <- "NA"
data$Skill <- "NA"
data[grepl("_t_", midFile)]$Condition <- "teaching"
data[grepl("_p_", midFile)]$Condition <- "performing"
data[grepl("a_", midFile)]$Skill <- "articulation"
data[grepl("d_", midFile)]$Skill <- "dynamics"
```

# Judged as "teaching" (%) for each stimulus
```{r teaching, echo = FALSE}
data$Teaching <- 0
data[rating == "Yes"]$Teaching <- 1

# individual
individual <- data[subjectNumber != 9, .(N = .N, Sum = sum(Teaching)), by = .(subjectNumber, Condition, Skill, MidFile)]
individual<- individual[order(subjectNumber)]

# all
all <- individual[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
all <- all[order(MidFile)]
all
```

```{r midi, include = FALSE}
# create a list of data file names
lf <- list.files("../experiment/mid/", pattern = "mid")

# combine data
all_data <- data.table()
for (file in lf){
   current <- readMidi(paste("../experiment/mid/", file, sep = ""))
   current$MidFile <- gsub(".mid", "", file)
   all_data <- rbind(all_data, current)
}

data <- all_data[event == "Note On" | event == "Note Off"]
data$NoteNr <- rep(1:134, nrow(data)/134)
data$channel <- NULL
data$parameterMetaSystem <- NULL
data$track <- NULL
data$type <- NULL
data$time2 <- data$time
#data$time2 <- (data$time/960)*1000 # deltatime to time (ms)

# labelling
colnames(data)[c(3,4)] <- c("Pitch", "Velocity") # time event also change
data$Condition <- "NA"
data$Skill <- "NA"
data[grepl("_t_", MidFile)]$Condition <- "teaching"
data[grepl("_p_", MidFile)]$Condition <- "performing"
data[grepl("a_", MidFile)]$Skill <- "articulation"
data[grepl("d_", MidFile)]$Skill <- "dynamics"

# define subcomponents
# For intervals
ls_legato <- list(c(1:7), c(17:23), c(42:48), c(58:64))
ls_staccato <- list(c(9:15), c(25:31), c(34:40), c(50:56))
ls_forte <- list(c(1:7), c(17:23), c(42:48), c(58:64))
ls_piano <- list(c(9:15), c(25:31), c(34:40), c(50:56))

# For each note (velocity only)
ls_legato_2 <- list(c(1:8), c(17:24), c(42:49), c(58:65))
ls_staccato_2 <- list(c(9:16), c(25:32), c(34:41), c(50:57))
ls_forte_2 <- list(c(1:8), c(17:24), c(42:49), c(58:65))
ls_piano_2 <- list(c(9:16), c(25:32), c(34:41), c(50:57))

# Define Skill Change (LtoS, FtoP)
change_1 <- c(8, 24, 49)
# Define Skill Change (StoL, PtoF)
change_2 <- c(16, 41, 57)
```

# Results
- significance levels: `***: 0.001, **: 0.01, *: 0.05`
- scatter plots with linear regression lines and 95% confidence intervals (gray)
- SD: Standard deviation
- CV: Coefficient of variation (SD/mean)

# IOIs: CV (tempo variability)
```{r ioi, include = FALSE}
data_onset <- data[event == "Note On"]
data_offset <- data[event == "Note Off"]

data_onset$IOI <- diff(c(0, data_onset$time2))
dt_ioi <- data_onset[NoteNr != 1]
dt_ioi$Interval <- rep(1:66, nrow(dt_ioi)/66)

# assign Subcomponents
dt_ioi$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato)){
 for (note in 1:length(ls_legato[[phrase]])){
   dt_ioi[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
 }
}
# Staccato
for (phrase in 1:length(ls_staccato)){
 for (note in 1:length(ls_staccato[[phrase]])){
   dt_ioi[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
 }
}

# Forte
for (phrase in 1:length(ls_forte)){
 for (note in 1:length(ls_forte[[phrase]])){
   dt_ioi[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
 }
}
# Piano
for (phrase in 1:length(ls_piano)){
 for (note in 1:length(ls_piano[[phrase]])){
   dt_ioi[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
 }
}

# assign Subcomponent Change
for (number in change_1){
 dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
 dt_ioi[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
}
for (number in change_2){
 dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
 dt_ioi[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
}
```

## Whole excerpt
```{r cv-ioi, echo = FALSE}
rating <- all # rating data

cv <- dt_ioi[Subcomponent != "NA", .(N = .N, CV = sd(IOI)/mean(IOI)), by = .(MidFile, Skill)]
cv

# sorted
cv <- cv[order(MidFile)]

# plot
cv$Teaching <- rating$Mean_Percent
cv$TeachingSD <- rating$SD_Percent

ggscatter(cv, x = "CV", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

### Articulation (n.s.)
```{r, echo = FALSE}
# normality check
shapiro.test(cv[Skill == "articulation"]$Teaching)
shapiro.test(cv[Skill == "articulation"]$CV)

cor.test(cv[Skill == "articulation"]$Teaching, cv[Skill == "articulation"]$CV)

cor.test(cv[Skill == "articulation"]$Teaching, cv[Skill == "articulation"]$CV, method = "spearman", exact = FALSE)
```

### Dynamics (n.s.)
```{r, echo = FALSE}
# normality check
shapiro.test(cv[Skill == "dynamics"]$Teaching)
shapiro.test(cv[Skill == "dynamics"]$CV)

cor.test(cv[Skill == "dynamics"]$Teaching, cv[Skill == "dynamics"]$CV)

cor.test(cv[Skill == "dynamics"]$Teaching, cv[Skill == "dynamics"]$CV, method = "spearman", exact = FALSE)
```

## Except transition points
Generally pianists were likely to play slowly around transition points where one subcomponent of a technique moves to the other (e.g., from legat to staccato, from forte to piano). Therefore, we excluded these points to look at tempo variability.

```{r cv-ioi-2, echo = FALSE}
cv_2 <- dt_ioi[Subcomponent == "Legato" | Subcomponent == "Staccato" | Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, CV = sd(IOI)/mean(IOI)), by = .(MidFile, Skill)]
cv_2

# sorted
cv_2 <- cv_2[order(MidFile)]

# plot
cv_2$Teaching <- rating$Mean_Percent
cv_2$TeachingSD <- rating$SD_Percent

ggscatter(cv_2, x = "CV", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

### Articulation (n.s.)
```{r, echo = FALSE}
# normality check
shapiro.test(cv_2[Skill == "articulation"]$Teaching)
shapiro.test(cv_2[Skill == "articulation"]$CV)

cor.test(cv_2[Skill == "articulation"]$Teaching, cv_2[Skill == "articulation"]$CV)

cor.test(cv_2[Skill == "articulation"]$Teaching, cv_2[Skill == "articulation"]$CV, method = "spearman", exact = FALSE)
```

### Dynamics (*)
```{r, echo = FALSE}
# normality check
shapiro.test(cv_2[Skill == "dynamics"]$Teaching)
shapiro.test(cv_2[Skill == "dynamics"]$CV)

cor.test(cv_2[Skill == "dynamics"]$Teaching, cv_2[Skill == "dynamics"]$CV)

cor.test(cv_2[Skill == "dynamics"]$Teaching, cv_2[Skill == "dynamics"]$CV, method = "spearman", exact = FALSE)
```
# KOT: SD (articulation variability)
Because some recordings have a negative mean of KOT even for legato parts, SD, instead of CV, would be suitble to see articulation variation.

```{r kot, include = FALSE}
data_onset$KOT <- 0
for (row in 1:nrow(data_onset)){
   if (row < nrow(data_onset)){
      data_onset$KOT[row+1] <- data_offset$time2[row] - data_onset$time2[row+1] # offset(n) - onset(n+1)
   }
}

dt_kot <- data_onset[NoteNr != 1]
dt_kot$Interval <- rep(1:66, nrow(dt_kot)/66)

# assign Subcomponents
dt_kot$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato)){
   for (note in 1:length(ls_legato[[phrase]])){
     dt_kot[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
   }
}
# Staccato
for (phrase in 1:length(ls_staccato)){
   for (note in 1:length(ls_staccato[[phrase]])){
     dt_kot[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
   }
}
# Forte
for (phrase in 1:length(ls_forte)){
   for (note in 1:length(ls_forte[[phrase]])){
     dt_kot[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
   }
}
# Piano
for (phrase in 1:length(ls_piano)){
   for (note in 1:length(ls_piano[[phrase]])){
     dt_kot[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
   }
}
# assign Subcomponent Change
for (number in change_1){
   dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
   dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
}
for (number in change_2){
   dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
   dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
}
```

## Articulation
```{r sd-kot-art, echo = FALSE}
sd_kot_art <- dt_kot[Subcomponent == "Legato" | Subcomponent == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile, Subcomponent)]
sd_kot_art

# sorted
sd_kot_art <- sd_kot_art[order(MidFile)]

# plot
sd_kot_art$Teaching <- rep(rating[Skill == "articulation"]$Mean_Percent, each = 2)
sd_kot_art$TeachingSD <- rep(rating[Skill == "articulation"]$SD_Percent, each = 2)

ggscatter(sd_kot_art, x = "SD", y = "Teaching", color = "Subcomponent", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "SD (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

### Legato (n.s.)
```{r, echo = FALSE}
# normality check
shapiro.test(sd_kot_art[Subcomponent == "Legato"]$Teaching)
shapiro.test(sd_kot_art[Subcomponent == "Legato"]$SD)

cor.test(sd_kot_art[Subcomponent == "Legato"]$Teaching, sd_kot_art[Subcomponent == "Legato"]$SD)
```

### Staccato (n.s.)
```{r, echo = FALSE}
# normality check
shapiro.test(sd_kot_art[Subcomponent == "Staccato"]$Teaching)
shapiro.test(sd_kot_art[Subcomponent == "Staccato"]$SD)

cor.test(sd_kot_art[Subcomponent == "Staccato"]$Teaching, sd_kot_art[Subcomponent == "Staccato"]$SD)

cor.test(sd_kot_art[Subcomponent == "Staccato"]$Teaching, sd_kot_art[Subcomponent == "Staccato"]$SD, method = "spearman", exact = FALSE)
```

## Dynamics
```{r sd-kot-dyn, echo = FALSE}
sd_kot_dyn <- dt_kot[Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile, Subcomponent)]
sd_kot_dyn

# sorted
sd_kot_dyn <- sd_kot_dyn[order(MidFile)]

# plot
sd_kot_dyn$Teaching <- rep(rating[Skill == "dynamics"]$Mean_Percent, each = 2)
sd_kot_dyn$TeachingSD <- rep(rating[Skill == "dynamics"]$SD_Percent, each = 2)

ggscatter(sd_kot_dyn, x = "SD", y = "Teaching", color = "Subcomponent", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "SD (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

### Forte (n.s.)
```{r, echo = FALSE}
# normality check
shapiro.test(sd_kot_dyn[Subcomponent == "Forte"]$Teaching)
shapiro.test(sd_kot_dyn[Subcomponent == "Forte"]$SD)

cor.test(sd_kot_dyn[Subcomponent == "Forte"]$Teaching, sd_kot_dyn[Subcomponent == "Forte"]$SD)

cor.test(sd_kot_dyn[Subcomponent == "Forte"]$Teaching, sd_kot_dyn[Subcomponent == "Forte"]$SD, method = "spearman", exact = FALSE)
```

### Piano (n.s.)
```{r, echo = FALSE}
# normality check
shapiro.test(sd_kot_dyn[Subcomponent == "Piano"]$Teaching)
shapiro.test(sd_kot_dyn[Subcomponent == "Piano"]$SD)

cor.test(sd_kot_dyn[Subcomponent == "Piano"]$Teaching, sd_kot_dyn[Subcomponent == "Piano"]$SD)

cor.test(sd_kot_dyn[Subcomponent == "Piano"]$Teaching, sd_kot_dyn[Subcomponent == "Piano"]$SD, method = "spearman", exact = FALSE)
```

# KOT: CV (articulation variability)
Because some recordings have the negative mean value or KOT even for Legato parts (i.e., relatively short legato), this measurement might not be useful.

## Articulation
### Legato
```{r cv-kot-leg, echo = FALSE}
cv_kot_leg <- dt_kot[Subcomponent == "Legato", .(N = .N, CV = sd(KOT)/mean(KOT)), by = .(MidFile)]
cv_kot_leg

# sorted
cv_kot_leg <- cv_kot_leg[order(MidFile)]

# plot
cv_kot_leg$Teaching <- rep(rating[Skill == "articulation"]$Mean_Percent, each = 1)
cv_kot_leg$TeachingSD <- rep(rating[Skill == "articulation"]$SD_Percent, each = 1)

ggscatter(cv_kot_leg, x = "CV", y = "Teaching", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

### Staccato
```{r cv-kot-sta, echo = FALSE}
cv_kot_sta <- dt_kot[Subcomponent == "Staccato", .(N = .N, CV = sd(KOT)/mean(KOT)), by = .(MidFile)]
cv_kot_sta

# sorted
cv_kot_sta <- cv_kot_sta[order(MidFile)]

# plot
cv_kot_sta$Teaching <- rep(rating[Skill == "articulation"]$Mean_Percent, each = 1)
cv_kot_sta$TeachingSD <- rep(rating[Skill == "articulation"]$SD_Percent, each = 1)

ggscatter(cv_kot_sta, x = "CV", y = "Teaching", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

## Dynamics
### Forte
```{r cv-kot-for, echo = FALSE}
cv_kot_for <- dt_kot[Subcomponent == "Forte", .(N = .N, CV = sd(KOT)/mean(KOT)), by = .(MidFile)]
cv_kot_for

# sorted
cv_kot_for <- cv_kot_for[order(MidFile)]

# plot
cv_kot_for$Teaching <- rep(rating[Skill == "articulation"]$Mean_Percent, each = 1)
cv_kot_for$TeachingSD <- rep(rating[Skill == "articulation"]$SD_Percent, each = 1)

ggscatter(cv_kot_for, x = "CV", y = "Teaching", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

### Piano
```{r cv-kot-pia, echo = FALSE}
cv_kot_pia <- dt_kot[Subcomponent == "Piano", .(N = .N, CV = sd(KOT)/mean(KOT)), by = .(MidFile)]
cv_kot_pia

# sorted
cv_kot_pia <- cv_kot_pia[order(MidFile)]

# plot
cv_kot_pia$Teaching <- rep(rating[Skill == "articulation"]$Mean_Percent, each = 1)
cv_kot_pia$TeachingSD <- rep(rating[Skill == "articulation"]$SD_Percent, each = 1)

ggscatter(cv_kot_pia, x = "CV", y = "Teaching", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

# KV: CV (dynamics variability)
```{r vel, include = FALSE}
dt_vel <- data_onset
dt_vel$Note <- rep(1:67, nrow(dt_vel)/67)
# assign Subcomponents
# for each note
dt_vel$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato_2)){
   for (note in 1:length(ls_legato_2[[phrase]])){
     dt_vel[Skill == "articulation" & Note == ls_legato_2[[phrase]][note]]$Subcomponent <- "Legato"
   }
}
# Staccato
for (phrase in 1:length(ls_staccato_2)){
   for (note in 1:length(ls_staccato_2[[phrase]])){
     dt_vel[Skill == "articulation" & Note == ls_staccato_2[[phrase]][note]]$Subcomponent <- "Staccato"
   }
}
# Forte
for (phrase in 1:length(ls_forte_2)){
   for (note in 1:length(ls_forte_2[[phrase]])){
     dt_vel[Skill == "dynamics" & Note == ls_forte_2[[phrase]][note]]$Subcomponent <- "Forte"
   }
}
# Piano
for (phrase in 1:length(ls_piano_2)){
   for (note in 1:length(ls_piano_2[[phrase]])){
     dt_vel[Skill == "dynamics" & Note == ls_piano_2[[phrase]][note]]$Subcomponent <- "Piano"
   }
}
```

## Dynamics
```{r cv-vel-dyn, echo = FALSE}
cv_vel_dyn <- dt_vel[Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, CV = sd(Velocity)/mean(Velocity)), by = .(MidFile, Subcomponent)]
cv_vel_dyn

# sorted
cv_vel_dyn <- cv_vel_dyn[order(MidFile)]

# plot
cv_vel_dyn$Teaching <- rep(rating[Skill == "dynamics"]$Mean_Percent, each = 2)
cv_vel_dyn$TeachingSD <- rep(rating[Skill == "dynamics"]$SD_Percent, each = 2)

ggscatter(cv_vel_dyn, x = "CV", y = "Teaching", color = "Subcomponent", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

### Forte (n.s.)
```{r, echo = FALSE}
# normality check
shapiro.test(cv_vel_dyn[Subcomponent == "Forte"]$Teaching)
shapiro.test(cv_vel_dyn[Subcomponent == "Forte"]$CV)

cor.test(cv_vel_dyn[Subcomponent == "Forte"]$Teaching, cv_vel_dyn[Subcomponent == "Forte"]$CV)
```

### Piano (n.s.)
```{r, echo = FALSE}
# normality check
shapiro.test(cv_vel_dyn[Subcomponent == "Piano"]$Teaching)
shapiro.test(cv_vel_dyn[Subcomponent == "Piano"]$CV)

cor.test(cv_vel_dyn[Subcomponent == "Piano"]$Teaching, cv_vel_dyn[Subcomponent == "Piano"]$CV)

cor.test(cv_vel_dyn[Subcomponent == "Piano"]$Teaching, cv_vel_dyn[Subcomponent == "Piano"]$CV, method = "spearman", exact = FALSE)
```

## Articulation
```{r cv-vel-art, echo = FALSE}
cv_vel_art <- dt_vel[Subcomponent == "Legato" | Subcomponent == "Staccato", .(N = .N, CV = sd(Velocity)/mean(Velocity)), by = .(MidFile, Subcomponent)]
cv_vel_art

# sorted
cv_vel_art <- cv_vel_art[order(MidFile)]

# plot
cv_vel_art$Teaching <- rep(rating[Skill == "articulation"]$Mean_Percent, each = 2)
cv_vel_art$TeachingSD <- rep(rating[Skill == "articulation"]$SD_Percent, each = 2)

ggscatter(cv_vel_art, x = "CV", y = "Teaching", color = "Subcomponent", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

### Legato (**)
```{r, echo = FALSE}
# normality check
shapiro.test(cv_vel_art[Subcomponent == "Legato"]$Teaching)
shapiro.test(cv_vel_art[Subcomponent == "Legato"]$CV)

cor.test(cv_vel_art[Subcomponent == "Legato"]$Teaching, cv_vel_art[Subcomponent == "Legato"]$CV)

cor.test(cv_vel_art[Subcomponent == "Legato"]$Teaching, cv_vel_art[Subcomponent == "Legato"]$CV, method = "spearman", exact = FALSE)
```

### Staccato (*)
```{r, echo = FALSE}
# normality check
shapiro.test(cv_vel_art[Subcomponent == "Staccato"]$Teaching)
shapiro.test(cv_vel_art[Subcomponent == "Staccato"]$CV)

cor.test(cv_vel_art[Subcomponent == "Staccato"]$Teaching, cv_vel_art[Subcomponent == "Staccato"]$CV)
```

### 2021-07-02 analysis/analysis.Rmd
move data folder to the front
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 # read files and combine them
-data_ls <- list.files("data", pattern = "csv")
+data_ls <- list.files("../data", pattern = "csv")
 combined <- lapply(data_ls, function(f){
-  fread(paste("data/", f, sep = ""), sep = ",")
+  fread(paste("../data/", f, sep = ""), sep = ",")
 })

### 2021-07-02 analysis/analysis.R

@@ -12,9 +12,9 @@ if (!require("performance")) {install.packages("performance"); require("performa
 
 ## ----read, include = FALSE----------------------------------
 # read files and combine them
-data_ls <- list.files("data", pattern = "csv")
+data_ls <- list.files("../data", pattern = "csv")
 combined <- lapply(data_ls, function(f){
-  fread(paste("data/", f, sep = ""), sep = ",")
+  fread(paste("../data/", f, sep = ""), sep = ",")
 })
 all_data <- do.call(rbind.data.frame, combined)
 
@@ -208,6 +208,8 @@ shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
 shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)
 
 cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean)
+
+cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
 
 
 ## ----cv, echo = FALSE---------------------------------------

### 2021-07-02 analysis/analysis.Rmd
update data
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-06-11 analysis/analysis.Rmd
@@
 ---
-title: "Music Perception 1: Analysis"
+title: "Music Perception 2: Analysis"
 output: html_notebook
@@
 
-- 21 participants (experimental error = 1) >> 20 participants were included for analysis.
+- 17 participants (experimental error = 1) >> 16 participants were included for analysis.
 
@@
 - linear regression lines and 95% confidence interval (gray)
-- dotted lines indicate an ideal tempo (80bpm for 16th notes - 188ms interval)
 
@@
 dt_ioi <- data_onset[NoteNr != 1]
-dt_ioi$Interval <- rep(1:66, nrow(dt_ioi)/66)
+dt_ioi$Interval <- rep(1:71, nrow(dt_ioi)/71)
 
@@
 
-## All (***)
+## All ()
 ```{r ioi-all, echo = FALSE}
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
-## Articulation (***)
+## Articulation ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(ioi[Skill == "articulation"]$Teaching)
-shapiro.test(ioi[Skill == "articulation"]$Mean)
-
-cor_ioi_art <- cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
-cor_ioi_art
+cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
 ```
 
-## Dynamics (**)
+## Dynamics ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(ioi[Skill == "dynamics"]$Teaching)
-shapiro.test(ioi[Skill == "dynamics"]$Mean)
-
-cor_ioi_dyn <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
-cor_ioi_dyn
-
-cor_ioi_dyn_spearman <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean, method = "spearman")
-cor_ioi_dyn_spearman
+cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
 ```
@@
 
-## All (***)
+## All ()
 ```{r ioi-tra-all, echo = FALSE}
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
 ```
 
-## Articulation (***)
+## Articulation ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
-shapiro.test(ioi_tra[Skill == "articulation"]$Mean)
-
 cor.test(ioi_tra[Skill == "articulation"]$Teaching, ioi_tra[Skill == "articulation"]$Mean)
@@
 
-## Dynamics (**)
+## Dynamics ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
-shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)
-
 cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean)
@@
 ```
-## Articulation (n.s.)
+## Articulation ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(cv[Skill == "articulation"]$Teaching)
-shapiro.test(cv[Skill == "articulation"]$CV)
-
 cor.test(cv[Skill == "articulation"]$Teaching, cv[Skill == "articulation"]$CV)
 ```
-## Dynamics (n.s.)
+
+## Dynamics ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(cv[Skill == "dynamics"]$Teaching)
-shapiro.test(cv[Skill == "dynamics"]$CV)
-
 cor.test(cv[Skill == "dynamics"]$Teaching, cv[Skill == "dynamics"]$CV)
@@
 ```
-## Legato (**)
+## Legato ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
-shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)
-
-cor_kot_leg <- cor.test(kot_all[Subcomponent == "Legato"]$Teaching, kot_all[Subcomponent == "Legato"]$Mean)
-cor_kot_leg
+cor.test(kot_all[Subcomponent == "Legato"]$Teaching, kot_all[Subcomponent == "Legato"]$Mean)
 ```
 
-## Staccato (***)
+## Staccato ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
-shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)
-
-cor_kot_sta <- cor.test(kot_all[Subcomponent == "Staccato"]$Teaching, kot_all[Subcomponent == "Staccato"]$Mean)
-cor_kot_sta
+cor.test(kot_all[Subcomponent == "Staccato"]$Teaching, kot_all[Subcomponent == "Staccato"]$Mean)
 ```
 
-## Forte (n.s.)
+## Forte ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
-shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)
-
-cor_kot_for <- cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean)
-cor_kot_for
-
-cor_kot_for_spearman <- cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean, method = "spearman")
-cor_kot_for_spearman
+cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean)
 ```
 
-## Piano (n.s.)
+## Piano ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
-shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)
-
-cor_kot_pia <- cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean)
-cor_kot_pia
-
-cor_kot_pia_spearman <- cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean, method = "spearman")
-cor_kot_pia_spearman
+cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean)
 ```
@@
 
-## Forte (***)
+## Forte ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
-shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)
-
-cor_vel_for <- cor.test(vel_all[Subcomponent == "Forte"]$Teaching, vel_all[Subcomponent == "Forte"]$Mean)
-cor_vel_for
+cor.test(vel_all[Subcomponent == "Forte"]$Teaching, vel_all[Subcomponent == "Forte"]$Mean)
 ```
 
-## Piano (n.s.)
+## Piano ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
-shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)
-
-cor_vel_pia <- cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean)
-cor_vel_pia
+cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean)
 ```
-## Legato (n.s.)
+## Legato ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
-shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)
-
-cor_vel_leg <- cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean)
-cor_vel_leg
-
-cor_vel_leg_spearman <- cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean, method = "spearman")
-cor_vel_leg_spearman
+cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean)
 ```
 
-## Staccato (n.s.)
+## Staccato ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
-shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)
-
-cor_vel_sta <- cor.test(vel_all[Subcomponent == "Staccato"]$Teaching, vel_all[Subcomponent == "Staccato"]$Mean)
-cor_vel_sta
+cor.test(vel_all[Subcomponent == "Staccato"]$Teaching, vel_all[Subcomponent == "Staccato"]$Mean)
 ```
@@
 
-## Forte to Piano (***)
+## Forte to Piano ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
-shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)
-
-cor_vel_diff_ftop <- cor.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching, vel_diff_all[Subcomponent == "FtoP"]$Mean)
-cor_vel_diff_ftop
+cor.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching, vel_diff_all[Subcomponent == "FtoP"]$Mean)
 ```
 
-## Piano to Forte (***)
+## Piano to Forte ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
-shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)
-
-cor_vel_diff_ptof <- cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean)
-cor_vel_diff_ptof
+cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean)
 ```
-## Legato to Staccato (n.s.)
+## Legato to Staccato ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
-shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)
-
-cor_vel_diff_ltos <- cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean)
-cor_vel_diff_ltos
-
-cor_vel_diff_ltos_spearman <- cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean, method = "spearman")
-cor_vel_diff_ltos_spearman
+cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean)
 ```
 
-## Staccato to Legato (n.s.)
+## Staccato to Legato ()
 ```{r, echo = FALSE}
-# normality check
-shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Teaching)
-shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Mean)
-
-cor_vel_diff_stol <- cor.test(vel_diff_all[Subcomponent == "StoL"]$Teaching, vel_diff_all[Subcomponent == "StoL"]$Mean)
-cor_vel_diff_stol
+cor.test(vel_diff_all[Subcomponent == "StoL"]$Teaching, vel_diff_all[Subcomponent == "StoL"]$Mean)
 ```
@@
 # KOT
-## Legato (**)
+## Legato ()
 ```{r kot-partial-leg, echo = TRUE}
@@
 
-## Staccato (*)
+## Staccato ()
 ```{r kot-partial-sta, echo = TRUE}
@@
 # KV
-## Forte (*)
+## Forte ()
 ```{r vel-partial-for, echo = TRUE}
@@
 # KV-Diff
-## Forte to Piano (n.s.)
+## Forte to Piano ()
 ```{r vel-diff-partial-ftop, echo = TRUE}
@@
 ```
+
 ```{r export, include = FALSE}

### 2021-07-02 analysis/questionnaire.Rmd
export R code
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
export R code / change the title
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
update data
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ---
+
+- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`
 
@@
 # extract the total number of years of training for the longest instrument (input manually based on the original csv file)
-dt$Training <- c(14, 13, 7, 18, 23, 12, 17, 20, 12, 7, 12, 7, 7, 13, 20)
+dt$Training <- c(14, 13, 7, 18, 23, 12, 17, 20, 12, 7, 12, 7, 7, 13, 20, 15, 6)
 
@@
 ```
+
+```{r export, include = FALSE}
+knitr::purl("questionnaire.Rmd")
+```

### 2021-07-02 analysis/analysis.R

@@ -13,7 +13,7 @@ if (!require("performance")) {install.packages("performance"); require("performa
 
 ## ----read, include = FALSE----------------------------------
 # read files and combine them
-data_ls <- list.files("data")
+data_ls <- list.files("data", pattern = "csv")
 combined <- lapply(data_ls, function(f){
   fread(paste("data/", f, sep = ""), sep = ",")
 })

### 2021-07-02 analysis/questionnaire.R

@@ -16,7 +16,7 @@ colnames(dt)[4] <- "Gender"
 colnames(dt)[7] <- "Handedness"
 
 # extract the total number of years of training for the longest instrument (input manually based on the original csv file)
-dt$Training <- c(14, 13, 7, 18, 23, 12, 17, 20, 12, 7, 12, 7, 7, 13, 20)
+dt$Training <- c(14, 13, 7, 18, 23, 12, 17, 20, 12, 7, 12, 7, 7, 13, 20, 15, 6)
 
 # exclude participants
 dt_included <- dt[SubNr != 4]

### 2021-07-02 analysis/variability.Rmd
update variability analysis (look at each recording, which creates a large CV for KOT)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-# Data analysis
+# Variability
 - Pearson's correlation (if normality is violated, Spearman's rank correlation instead) between variability measurements and participants' judgments as "teaching"
@@
 ```
+
+# Appendix
+
+## deviated CVs based on legato
+```{r kot-extra-1, echo = FALSE}
+cv_deviated_legato <- cv_kot_leg[abs(CV) > 10]
+
+# a_p_16
+a_p_16 <- dt_kot[MidFile == cv_deviated_legato[1]$MidFile]
+a_p_16$Interval <- c(1:nrow(a_p_16))
+
+ggline(a_p_16, x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_16") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+ggline(a_p_16[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_16 (Legato)") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+ggline(a_p_16[Subcomponent == "Staccato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_16 (Staccato)") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+# a_p_16
+a_p_6 <- dt_kot[MidFile == cv_deviated_legato[2]$MidFile]
+a_p_6$Interval <- c(1:nrow(a_p_6))
+
+ggline(a_p_6, x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_6") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+ggline(a_p_6[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_6 (Legato)") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+ggline(a_p_6[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_ (Staccato)") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+# a_p_15
+a_p_15 <- dt_kot[MidFile == cv_deviated_legato[3]$MidFile]
+a_p_15$Interval <- c(1:nrow(a_p_15))
+
+ggline(a_p_15, x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_15") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+ggline(a_p_15[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_15 (Legato)") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+ggline(a_p_15[Subcomponent == "Staccato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_15 (Staccato)") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+# a_p_24
+a_p_24 <- dt_kot[MidFile == cv_deviated_legato[4]$MidFile]
+a_p_24$Interval <- c(1:nrow(a_p_24))
+
+ggline(a_p_24, x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_24") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+ggline(a_p_24[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_24 (Legato)") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+ggline(a_p_24[Subcomponent == "Staccato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_24 (Staccato)") +
+  scale_x_continuous(breaks = seq(1,66,1))
+```
+
+## stable CVs based on legato
+```{r kot-extra-2, echo = FALSE}
+cv_stable_legato <- cv_kot_leg[abs(CV) < 0.5]
+
+# a_p_2
+a_p_2 <- dt_kot[MidFile == cv_stable_legato[1]$MidFile]
+a_p_2$Interval <- c(1:nrow(a_p_2))
+
+ggline(a_p_2, x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_2") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+ggline(a_p_2[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_2 (Legato)") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+ggline(a_p_2[Subcomponent == "Staccato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_2 (Staccato)") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+# a_p_4
+a_p_4 <- dt_kot[MidFile == cv_stable_legato[2]$MidFile]
+a_p_4$Interval <- c(1:nrow(a_p_4))
+
+ggline(a_p_4, x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_4") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+ggline(a_p_4[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_4 (Legato)") +
+  scale_x_continuous(breaks = seq(1,66,1))
+
+ggline(a_p_4[Subcomponent == "Staccato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_4 (Staccato)") +
+  scale_x_continuous(breaks = seq(1,66,1))
+```

### 2021-07-05 analysis/analysis.Rmd
add shapiro.wilk() for normality check
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-## All ()
+## All
 ```{r ioi-all, echo = FALSE}
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(ioi[Skill == "articulation"]$Teaching)
+shapiro.test(ioi[Skill == "articulation"]$Mean)
+
 cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(ioi[Skill == "dynamics"]$Teaching)
+shapiro.test(ioi[Skill == "dynamics"]$Mean)
+
 cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
+
+cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
 ```
@@
 
-## All ()
+## All
 ```{r ioi-tra-all, echo = FALSE}
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
+shapiro.test(ioi_tra[Skill == "articulation"]$Mean)
+
 cor.test(ioi_tra[Skill == "articulation"]$Teaching, ioi_tra[Skill == "articulation"]$Mean)
+
+cor.test(ioi_tra[Skill == "articulation"]$Teaching, ioi_tra[Skill == "articulation"]$Mean, method = "spearman", exact = FALSE)
 ```
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
+shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)
+
 cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean)
+
+cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
 ```
@@
 
-## All ()
+## All
 ```{r cv, echo = FALSE}
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(cv[Skill == "articulation"]$Teaching)
+shapiro.test(cv[Skill == "articulation"]$CV)
+
 cor.test(cv[Skill == "articulation"]$Teaching, cv[Skill == "articulation"]$CV)
+
+cor.test(cv[Skill == "articulation"]$Teaching, cv[Skill == "articulation"]$CV, method = "spearman", exact = FALSE)
 ```
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(cv[Skill == "dynamics"]$Teaching)
+shapiro.test(cv[Skill == "dynamics"]$CV)
+
 cor.test(cv[Skill == "dynamics"]$Teaching, cv[Skill == "dynamics"]$CV)
+
+cor.test(cv[Skill == "dynamics"]$Teaching, cv[Skill == "dynamics"]$CV, method = "spearman", exact = FALSE)
 ```
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
+shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)
+
 cor.test(kot_all[Subcomponent == "Legato"]$Teaching, kot_all[Subcomponent == "Legato"]$Mean)
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
+shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)
+
 cor.test(kot_all[Subcomponent == "Staccato"]$Teaching, kot_all[Subcomponent == "Staccato"]$Mean)
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
+shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)
+
 cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean)
+
+cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean, method = "spearman", exact = FALSE)
 ```
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
+shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)
+
 cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean)
+
+cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
 ```
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
+shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)
+
 cor.test(vel_all[Subcomponent == "Forte"]$Teaching, vel_all[Subcomponent == "Forte"]$Mean)
+
+cor.test(vel_all[Subcomponent == "Forte"]$Teaching, vel_all[Subcomponent == "Forte"]$Mean, method = "spearman", exact = FALSE)
 ```
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
+shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)
+
 cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean)
+
+cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
 ```
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
+shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)
+
 cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean)
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
+shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)
+
 cor.test(vel_all[Subcomponent == "Staccato"]$Teaching, vel_all[Subcomponent == "Staccato"]$Mean)
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
+shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)
+
 cor.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching, vel_diff_all[Subcomponent == "FtoP"]$Mean)
+
+cor.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching, vel_diff_all[Subcomponent == "FtoP"]$Mean, method = "spearman", exact = FALSE)
 ```
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
+shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)
+
 cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean)
+
+cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean, method = "spearman", exact = FALSE)
 ```
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
+shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)
+
 cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean)
@@
 ```{r, echo = FALSE}
+# normality check
+shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Teaching)
+shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Mean)
+
 cor.test(vel_diff_all[Subcomponent == "StoL"]$Teaching, vel_diff_all[Subcomponent == "StoL"]$Mean)

### 2021-07-05 analysis/analysis.R

@@ -160,11 +160,21 @@ ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
 
 
 ## ---- echo = FALSE------------------------------------------
+# normality check
+shapiro.test(ioi[Skill == "articulation"]$Teaching)
+shapiro.test(ioi[Skill == "articulation"]$Mean)
+
 cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
 
 
 ## ---- echo = FALSE------------------------------------------
+# normality check
+shapiro.test(ioi[Skill == "dynamics"]$Teaching)
+shapiro.test(ioi[Skill == "dynamics"]$Mean)
+
 cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
+
+cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
 
 
 ## ----ioi-tra-all, echo = FALSE------------------------------
@@ -183,11 +193,23 @@ ggscatter(ioi_tra, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line"
 
 
 ## ---- echo = FALSE------------------------------------------
+# normality check
+shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
+shapiro.test(ioi_tra[Skill == "articulation"]$Mean)
+
 cor.test(ioi_tra[Skill == "articulation"]$Teaching, ioi_tra[Skill == "articulation"]$Mean)
+
+cor.test(ioi_tra[Skill == "articulation"]$Teaching, ioi_tra[Skill == "articulation"]$Mean, method = "spearman", exact = FALSE)
 
 
 ## ---- echo = FALSE------------------------------------------
+# normality check
+shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
+shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)
+
 cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean)
+
+cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
 
 
 ## ----cv, echo = FALSE---------------------------------------
[…]

### 2021-07-05 analysis/analysis.Rmd
remove irrelevant texts
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-07-02 analysis/analysis.Rmd
@@
 
-## All (***)
+## All
 ```{r ioi-all, echo = FALSE}
@@
 
-## All (***)
+## All
 ```{r ioi-tra-all, echo = FALSE}
@@
 
-## All (n.s.)
+## All
 ```{r cv, echo = FALSE}

### 2021-08-26 analysis/analysis.Rmd
update analysis (with the 20th participant)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-07-05 analysis/analysis.Rmd
@@
 
-- 17 participants (experimental error = 1) >> 16 participants were included for analysis.
+- 21 participants (experimental error = 1) >> 20 participants were included for analysis.
 
@@
 ```
-## Articulation ()
+## Articulation (n.s.)
 ```{r, echo = FALSE}
@@
 
-## Dynamics ()
+## Dynamics (n.s.)
 ```{r, echo = FALSE}
@@
 
-## Articulation ()
+## Articulation (n.s.)
 ```{r, echo = FALSE}
@@
 
-## Dynamics ()
+## Dynamics (*)
 ```{r, echo = FALSE}
@@
 ```
-## Legato ()
+## Legato (n.s.)
 ```{r, echo = FALSE}
@@
 
-## Staccato ()
+## Staccato (n.s.)
 ```{r, echo = FALSE}
@@
 
-## Forte ()
+## Forte (n.s.)
 ```{r, echo = FALSE}
@@
 
-## Piano ()
+## Piano (*)
 ```{r, echo = FALSE}
@@
 
-## Forte ()
+## Forte (**)
 ```{r, echo = FALSE}
@@
 
-## Forte to Piano ()
+## Forte to Piano (***)
 ```{r, echo = FALSE}
@@
 
-## Piano to Forte ()
+## Piano to Forte (***)
 ```{r, echo = FALSE}
@@
 ```
-## Legato to Staccato ()
+## Legato to Staccato (n.s.)
 ```{r, echo = FALSE}
@@
 
-## Staccato to Legato ()
+## Staccato to Legato (*)
 ```{r, echo = FALSE}
@@
 # KOT
-## Legato ()
+## Legato (n.s.)
 ```{r kot-partial-leg, echo = TRUE}
@@
 
-## Staccato ()
+## Staccato (n.s.)
 ```{r kot-partial-sta, echo = TRUE}
@@
 # KV
-## Forte ()
+## Forte (n.s.)
 ```{r vel-partial-for, echo = TRUE}
@@
 
-## Piano ()
+## Piano (n.s.)
 ```{r vel-partial-pia, echo = TRUE}
@@
 # KV-Diff
-## Forte to Piano ()
+## Forte to Piano (***)
 ```{r vel-diff-partial-ftop, echo = TRUE}
@@
 
-## Piano to Forte ()
+## Piano to Forte (***)
 ```{r vel-diff-partial-ptof, echo = TRUE}

### 2021-08-26 analysis/questionnaire.R
update analysis (with the 20th participant)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@ -16,7 +16,7 @@ colnames(dt)[4] <- "Gender"
 colnames(dt)[7] <- "Handedness"
 
 # extract the total number of years of training for the longest instrument (input manually based on the original csv file)
-dt$Training <- c(14, 13, 7, 18, 23, 12, 17, 20, 12, 7, 12, 7, 7, 13, 20, 15, 6)
+dt$Training <- c(14, 13, 7, 18, 23, 12, 17, 20, 12, 7, 12, 7, 7, 13, 20, 15, 6, 15, 8, 5, 20)
 
 # exclude participants
 dt_included <- dt[SubNr != 4]

### 2022-01-14 experiment-1/analysis/prereg_analysis/prereg_analysis.Rmd
merge perception-v1.0 / move stuff to experiment-1
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-06-10 analysis/prereg_analysis/prereg_analysis.Rmd
@@
 - 48 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 96 stimuli).
-The half of them was selected from the teaching condition and the other half was from the performing condition.
+Half of them was selected from the teaching condition and the other half was from the performing condition.
   + 24 for teaching-articulation performances
@@
 # read files and combine them
-data_ls <- list.files("../data", pattern = "csv")
+data_ls <- list.files("../../data", pattern = "csv")
 combined <- lapply(data_ls, function(f){
-  fread(paste("../data/", f, sep = ""), sep = ",")
+  fread(paste("../../data/", f, sep = ""), sep = ",")
 })
@@
 
-data_box <- data.table(subjectNumber = ind_data_ad$subjectNumber, articulation = ind_data_ad[Skill == "articulation"]$Percent, dynamics = ind_data_ad[Skill == "dynamics"]$Percent)
+data_box <- data.table(subjectNumber = ind_data_ad[Skill == "articulation"]$subjectNumber, articulation = ind_data_ad[Skill == "articulation"]$Percent, dynamics = ind_data_ad[Skill == "dynamics"]$Percent)
 box <- ggpaired(data_box, cond1 = "articulation", cond2 = "dynamics", line.color = "gray", line.size = 0.4, ylab = "Correct %")

### 2022-01-14 experiment-1/analysis/variability.Rmd
merge perception-v1.0 / move stuff to experiment-1
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-07-02 analysis/variability.Rmd
@@
 
-ggline(a_p_6[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_ (Staccato)") +
+ggline(a_p_6[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_6 (Staccato)") +
   scale_x_continuous(breaks = seq(1,66,1))

### 2022-01-14 analysis/prereg_analysis/prereg_analysis.Rmd

@@
 ---
-title: "Music Perception 1: Preregistered Analysis"
+title: "Music Perception 2: Preregistered Analysis"
 output: html_notebook
@@
 
-- 21 participants (experimental error = 1) >> 20 participants were included for analysis.
+- 21 participants (excluded = 1) >> 20 participants were included for analysis.
 
@@
 # individual
-ind_data <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber)]
+ind_data <- data[subjectNumber != 4, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber)]
 ind_data <- ind_data[order(subjectNumber)]
@@
 # all
-subset <- ind_data[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/96)*100, SD_Percent = (sd(Sum)/96)*100)]
+subset <- ind_data[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/72)*100, SD_Percent = (sd(Sum)/72)*100)]
 subset
@@
 t.test(ind_data$Percent, mu = 50, alternative = "two.sided")
+
+wilcox.test(ind_data$Percent, mu = 50, alternative = "two.sided", exact = FALSE)
 ```
@@
 ```{r plot2, echo = FALSE}
-ind_data_ad <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Skill)]
+ind_data_ad <- data[subjectNumber != 4, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Skill)]
 ind_data_ad <- ind_data_ad[order(subjectNumber, Skill)]
 
-subset_ad <- ind_data_ad[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100), by = .(Skill)]
+subset_ad <- ind_data_ad[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/36)*100, SD_Percent = (sd(Sum)/36)*100), by = .(Skill)]
 subset_ad
 
-data_box <- data.table(subjectNumber = ind_data_ad$subjectNumber, articulation = ind_data_ad[Skill == "articulation"]$Percent, dynamics = ind_data_ad[Skill == "dynamics"]$Percent)
+data_box <- data.table(subjectNumber = ind_data_ad[Skill == "articulation"]$subjectNumber, articulation = ind_data_ad[Skill == "articulation"]$Percent, dynamics = ind_data_ad[Skill == "dynamics"]$Percent)
 box <- ggpaired(data_box, cond1 = "articulation", cond2 = "dynamics", line.color = "gray", line.size = 0.4, ylab = "Correct %")

### 2022-01-14 analysis/questionnaire.Rmd

@@
 # extract the total number of years of training for the longest instrument (input manually based on the original csv file)
-dt$Training <- c(14, 13, 7, 18, 23, 12, 17, 20, 12, 7, 12, 7, 7, 13, 20, 15, 6)
+dt$Training <- c(14, 13, 7, 18, 23, 12, 17, 20, 12, 7, 12, 7, 7, 13, 20, 15, 6, 15, 8, 5, 20)
 

### 2022-01-27 experiment-1/analysis/analysis.Rmd
update analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-07-05 analysis/analysis.Rmd
@@
 ---
-title: "Music Perception 1: Analysis"
-output: html_notebook
+title: 'Music Perception 1: Analysis'
+output:
+  html_document:
+    df_print: paged
 ---
@@
 
-```{r packages, include = FALSE}
+```{r setup, include = FALSE}
 # data manipulation

### 2022-01-27 experiment-1/analysis/analysis.R

@@ -1,4 +1,4 @@
-## ----packages, include = FALSE------------------------------
+## ----setup, include = FALSE---------------------------------
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
 # midi

### 2022-01-27 experiment-1/analysis/questionnaire.R

@@ -1,4 +1,4 @@
-## ----setup, include = FALSE----------------------------------
+## ----setup, include = FALSE---------------------------------------------------
 # packages
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
@@ -6,7 +6,7 @@ if (!require("data.table")) {install.packages("data.table"); require("data.table
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
 
 
-## ----read, echo = FALSE--------------------------------------
+## ----read, echo = FALSE-------------------------------------------------------
 dt <- fread("questionnaire.csv", header = T, sep = ",", dec = ".", na.string = "NA")
 
 # change some colnames
@@ -24,10 +24,10 @@ dt_included <- dt[SubNr != 9]
 print(dt_included)
 
 
-## ----1, echo = FALSE-----------------------------------------
+## ----1, echo = FALSE----------------------------------------------------------
 data.table("Answer" = dt_included$`Have you noticed anything special regarding the tasks in the experiment? If any, please describe below.`)
 
 
-## ----export, include = FALSE---------------------------------
+## ----export, include = FALSE--------------------------------------------------
 knitr::purl("questionnaire.Rmd")
 

### 2022-01-27 paper/manuscript.Rmd
upload manuscript
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title             : "What makes listeners infer teaching intentions?"
shorttitle        : "What makes listeners infer teaching intentions?"

author: 
  - name          : "Atsuko Tominaga"
    affiliation   : "1,*"
    # corresponding : yes    # Define only one corresponding author
    # address       : "Quellenstraße 51, 1100 Vienna, Austria"
    # email         : "Tominaga_Atsuko@phd.ceu.edu"

  - name          : "Günther Knoblich"
    affiliation   : "1"

  - name          : "Natalie Sebanz"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Cognitive Science, Central European University, Quellenstraße 51, 1100 Vienna, Austria"
  - id            : "*"
    institution   : "Corresponding author: Tominaga_Atsuko@phd.ceu.edu"

abstract: |
  Social learning plays an important role in human skill transmission. It has been known that experts tend to change their behaviour particularly for teaching purposes. Our previous research demonstrated that expert pianists systematically modulated their sound so as to teach musical expressive techniques such as articulation and dynamics. For example, pianists played slower and exaggerated each technique when they had an intention to teach. In order to achieve successful skill transmission, it is vital to examine whether such sound modulations are identified and used to infer teaching intentions by novices, who are going to acquire skills. The current experiments investigated which features of piano performance make musicians (in the role of potential learners) infer teaching intentions. Musicians listened to a number of piano recordings where a musical expressive technique of either articulation or dynamics was implemented. Musicians were asked to judge whether each performance was produced in order to teach the designated expressive technique. We quantified recordings with regard to tempo, articulation and dynamics. Overall, slower tempo contributed to musicians’ judgments as teaching. Moreover, performances with exaggeration for each technique (e.g., shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching. These performance features are consistent with expert pianists’ sound modulations for teaching purposes. Therefore, musicians (in the role of potential learners) seem to be able to identify didactic sound modulations, only by listening to recorded performances.

keywords          : "teaching, intention, skill transmission, musical expression"

bibliography      : ["references.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
# packages
if (!require("papaja")) {install.packages("papaja"); require("papaja")}
if (!require("here")) {install.packages("here"); require("here")}
if (!require("magick")) {install.packages("magick"); require("magick")}

# create image folder
if (!file.exists(here("paper/image"))){
  dir.create(here("paper/image"))
}
```

```{r function, include = FALSE}
# function to extract the overall ANOVA p-value out of a linear model object
# https://gettinggeneticsdone.blogspot.com/2011/01/rstats-function-for-extracting-f-test-p.html
lmp <- function (modelobject) {
	if (class(modelobject) != "lm") stop("Not an object of class 'lm' ")
	f <- summary(modelobject)$fstatistic
	p <- pf(f[1], f[2], f[3],lower.tail = F)
	attributes(p) <- NULL
	return(p)
}
```

# Introduction
Learning from others is one of the important elements of skill acquisition. Not only are we able to learn by observing and imitating others, but also we benefit greatly from interacting with others such as teachers and peers [@tomasello_1993]. Adults are often being pedagogical to children in order to explain and transmit cultural conventions [@csibra_2009]. Active teaching seems to play a crucial role not only to transit skills over generations but also to further develop sophisticated cultures, which cannot be achieved by one single individual or generation [@tennie_2009]. From a learner's perspective, it is important to identify informative teachers and infer teachers' expectations so that learners can acquire skills through interacting with teachers [@gweon_2020; @veissiere_2020].

In pedagogical settings where teachers are supposed to convey useful information to learners, it has been found that teachers often modulate their behaviour for teaching purposes. For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills [e.g., @brand_2002; @kuhl_2004]. Also, some studies have revealed that even towards adult learners, people modulated their speech and action in the similar way as they did for infants [@mcellin_2017; @uther_2007]. These findings suggest that there are general pedagogical behaviours such as slow demonstration and exaggeration of speech and action to send teaching intentions to learners.

Tominaga, Knoblich & Sebanz (*in prep*) extended this line of research to expertise transmission where skills to be acquired are much more complicated than general knowledge, which is mostly acquired throughout development [e.g., @csibra_2009]. Expertise usually demands an enormous amount of practice to acquire so that only experts can accomplish a higher level of performance including artistic expression. Based on the assumption that expert pianists are very good at controlling and modulating their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound). The results demonstrated that expert pianists could successfully modulate their performance by playing slower or exaggerating relevant aspects of the performance (e.g., producing shorter staccato or making a larger contrast between forte and piano) to teach musical expressive techniques. Therefore, it seems that even in the domain of expertise, experts exhibit general pedagogical behaviours to communicate with their potential learners.

In order to achieve successful skill transmission, it is necessary to investigate whether novice learners can identify teaching intentions produced by experts. A recent study by @mcellin_2018 demonstrated that people could identify informative intentions such as acting with others or teaching by relying on specific kinematics cues (e.g., velocity profiles of movements). Some research in the field of action expertise suggest that motor simulation (i.e., using one's own motor systems to simulate an action) plays a key role to understand observed actions. For example, expert basketball players were better at predicting the outcome of a free shot compared to expert observers (coaches or sports journalists) and novices [@aglioti_2008]. Also, it was found that deceptive intentions of fake basketball passes were detected from non-verbal bodily cues only by expert basketball players [@sebanz_2009]. Taken together, people seem to be able to infer informative intentions by observing actions and motor expertise may enable accurate action prediction.

In the domain of music, musical emotion is often communicated by sound alone and listeners seem to be able to infer performers' intended emotions only by listening to recorded performances [e.g., @akkermans_2019; @gabrielsson_1996]. It has been known that musicians are generally more accurate to decode emotions from performances [@battcock_2021; @lima_2011]. @repp_2004 also found that expert pianists could distinguish their own performance from others' performances by listening to recordings. These results suggest that musical expertise may be important to accurately identify and infer intentions by listening to recorded performances.

The current experiments investigate which features of piano performance make musicians (in the role of potential learners) infer teaching intentions, only by listening to recorded performances. We collected various piano recordings from our previous experiments (Tominaga et al., *in prep*). The obtained recordings consisted of two pieces (one was used for Experiment 1 and the other was used for Experiment 2 in the current paper). The two pieces were performed by various pianists multiple times, therefore the recordings contained many variations in terms of timing, articulation and dynamics. In the current experiments, we asked musically trained participants to judge which performance was performed for teaching purposes. If teachers' intentions are successfully communicated with learners, pedagogical behavioural features in our previous experiments such as slower demonstration and exaggerated performance should be identified and used to infer teaching intentions. In Experiment 1, we examined which features of piano performance were correlated with participants judgments as "teaching". Experiment 2 was conducted to replicate what we found in Experiment 1 with a more naturalistic piece of music.

```{r questionnaire-1, include = FALSE}
source(here("experiment-1/analysis", "questionnaire.R"), chdir = TRUE)
```

# Experiment 1
# Methods
## Participants
We recruited `r nrow(dt)` participants who had at least six years of training in any musical instrument. They were able to read sheet music and knew two musical expressive techniques of articulation and dynamics. One participant was excluded due to an experimental error. Therefore, `r nrow(dt_included)` participants (Female: `r nrow(dt_included[Gender == "Female"])`) were included for data analysis and had `r round(mean(dt_included$Training), 2)` years of musical training on average (*SD* = `r round(sd(dt_included$Training), 2)`). They were all right-handed with a mean age of `r round(mean(dt_included$Age), 2)` (*SD* = `r round(sd(dt_included$Age), 2)`). All participants were recruited through an online participant platform (SONA system, https://www.sona-systems.com). The study (No. 2020/02) was approved by the Psychological Research Ethics Board (PREBO) CEU PU in Austria.

## Apparatus
The experiment was programmed in Python 3.8.2 using the PsychoPy library (2020.2.4; https://www.psychopy.org/) on a Mac Book Pro with Mac OS X Catalina 10.15.6. Stimuli (MIDI data) were played using the Mido library (1.2.9; https://mido.readthedocs.io/en/latest/) on a Max/MSP patcher (8.1.7; https://cycling74.com/products/max). During the experiment, participants listened to the stimuli via headphones (Audio-Technica ATH-M50X).

## Stimuli
Piano recordings were used as stimuli. The stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files. One piece of music was selected as a base piece and was taken from "A Dozen a Day - Play with Ease in Many Keys" by Edna-Mae Burnam and modified for the experiment. The piece was performed with a musical expressive technique of either articulation (*Figure \ref{fig:stim1}*, A) or dynamics (*Figure \ref{fig:stim1}*, B) by multiple pianists. Therefore, all stimuli had the same musical sequence but had subtle differences in terms of musical expressions (e.g., timing, articulation and dynamics). Articulation refers to the smoothness of sound, which is comprised of legato and staccato. Legato indicates smooth and connected sound whereas staccato indicates sharp and separate sound. Dynamics refers to the loudness of sound, which is comprised of forte and piano. Forte indicates loud sound while piano indicates soft sound. The stimuli were performed around 80 quarter-beats per minute (i.e., around 188 ms for 16th-note IOIs).

Ninety-six stimuli (MIDI recordings) were obtained from our previous experiments (Tominaga et al., *submitted*). In the previous experiments, we asked expert pianists to perform one piece of music with a musical expressive technique of either articulation (*Figure \ref{fig:stim1}*, A) or dynamics (*Figure \ref{fig:stim1}*, B). There were two experimental conditions. In the teaching condition, participants were instructed to perform the piece with the designated expressive technique as if they were teaching it to students (e.g., in a lesson). In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert). There were 453 valid performances (i.e., performances without any pitch error) for the teaching condition and 436 valid performances for the performing conditions. We randomly chose 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition. It is important to note that the recordings from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments since we randomly sampled the recordings.

## Procedure
Upon arrival, participants read information sheet about the experiment and gave informed consent prior to participation. In the experiment, all instructions were displayed on a computer screen and an experimenter also explained the procedure. Participants were instructed that they were going to listen to piano recordings and would be asked if each recording was performed as if a pianist were teaching it to students (e.g., in a lesson / teaching) or as if a pianist were performing it to an audience (e.g., in a concert / performing). They responded by pressing either a yes (teaching / left arrow key) or no (performing / right arrow key) button. While listening to each stimulus, sheet music, which corresponded to the stimulus, was shown on a monitor in front of the participants. After making a judgment, the next recording was played (*Figure \ref{fig:procedure1}*).

There were two blocks and each block only contained recordings with one musical expressive technique of either articulation or dynamics. Each block consisted of 4 practice trials and 48 experimental trials. In each trial, participants listened to one recording only once. After listening the recording, they were asked to judge by pressing either the left arrow key (i.e., teaching) or the right arrow key (i.e., performing). Each recording was evaluated only once in the experiment. The order of the blocks was counterbalanced across the participants. The order of the recordings was randomised within each block.

At the end of the experiment, participants filled in a questionnaire about their demographic information and experience in musical instruments.

## Data analysis{#dataanalysis}
Data processing and statistical analysis were performed in R version 4.0.5. Correlation analysis was performed with the standard *cor* function and regression models for multiple regression were fit with the standard *lm* function from the *stats* R package. Stimuli (MIDI files) were converted to numerical data in terms of time, pitch and velocity for the onset and offset of each note using the *tuneR* R package ([https://cran.r-project.org/web/packages/tuneR/tuneR.pdf](https://cran.r-project.org/web/packages/tuneR/tuneR.pdf)).

Stimuli (performances) were quantified with regard to tempo (interonset intervals; IOIs), articulation (key-overlap time; KOT), dynamics (key velocity; KV) and dynamics contrast (key velocity difference; KV-Diff) only for 16th notes. Interonset intervals are time intervals between onsets of adjacent notes. Larger IOIs indicate slower tempo while smaller IOIs indicate faster tempo. Key-overlap time is the time overlap between two adjacent notes, namely the difference between the offset time of the current note and the onset time of the ensuing note [e.g., @bresin_2000]. Positive KOT values indicate legato styles whereas negative KOT values indicate staccato styles. Key velocity is obtained from MIDI data to describe how fast a performer hit the key. Larger KV values indicate forte styles while smaller KV values indicate piano styles. Additionally, we also measured dynamics contrast where one subcomponent of the technique moves to the other (e.g., from forte to piano) to illustrate how much dynamics contrast a performer made at transition points.

First, we investigated data by looking at correlations between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as "teaching" (i.e., what percentage of participants responded as "yes (teaching)") for each stimulus. Second, we run multiple regression and entered all four performance features to examine which predictor significantly contributed to participants' judgments as teaching. Since articulation and dynamics were comprised of two opposite directional values (i.e., legato vs. staccato, forte vs. piano), we entered each subcomponent (i.e., legato, staccato, forte, piano) separately to represent either an articulation or dynamics feature of the performance for a regression model. For articulation recordings, there were two models. The first model considered only legato parts of the stimuli for KOT and KV, and transition points from legato to staccato for KV-Diff. The second model considered only staccato parts of the stimuli for KOT and KV, and transition points from staccato to legato for KV-Diff. For dynamics recordings, there were two models. The first model considered only forte parts of the stimuli for KV and KOT, and transition points from forte to piano for KV-Diff. The second model considered only piano parts of the stimuli for KV and KOT, and transition points from piano to forte for KV-Diff. With regard to tempo (IOIs), there was only one value for each technique because tempo was consistent across the performance and was not dependent on subcomponents.

<!-- Additionally, we also analysed data in terms of accuracy of their judgments as we originally planned in our Open Science Framework preregistration (available here: [https://osf.io/z3j69/](https://osf.io/z3j69/)). As we sampled data from the two conditions (i.e., teaching and performing) in our previous experiments, we were also interested in whether musicians could accurately judge the stimuli selected from the teaching condition as "teaching (yes)" and the stimuli selected from the performing condition as "performing (no)". However, during a pilot study, we realised that the stimuli in the teaching condition were not sufficiently different from those in the performing condition because of the random sampling. Therefore, we decided to switch to the current analysis and added the planned analysis in *[Supplementary Materials](#supplementary)*.   -->

```{r stim-1, out.width = "100%", fig.cap = "\\label{fig:stim1}Stimuli. (A)Articulation. The curved line (slur) indicates legato and the dots indicate staccato. (B)Dynamics. The symbol `f' denotes forte and the symbol `p' denotes piano. Only the 16th notes were used for data analysis.", echo = FALSE}
stim_a <- image_border(image_read(here("paper/image", "stim_a.png")), "#FFFFFF", "120x120")
stim_d <- image_border(image_read(here("paper/image", "stim_d.png")), "#FFFFFF", "120x120")

# combine
img_stimuli_1 <- image_append(c(stim_a, stim_d), stack = TRUE)
img_stimuli_1 <- image_annotate(img_stimuli_1, "(A)", size = 80, location = "+100+0", color = "black", font = "helvetica")
img_stimuli_1 <- image_annotate(img_stimuli_1, "(B)", size = 80, location = "+100+650", color = "black", font = "helvetica")
img_stimuli_1
```

```{r procedure-1, out.width = "100%", fig.cap = "\\label{fig:procedure1}Procedure. Participants listened to a recording via headphones while corresponding sheet music was displayed on a monitor. They were required to respond by pressing a left-arrow (yes) or right-arrow (no) key for each judgment.", echo = FALSE}
knitr::include_graphics(here("paper/image", "procedure.png"))
```

\clearpage

# Results

```{r results-1, cache = TRUE, include = FALSE}
source(here("experiment-1/analysis", "analysis.R"), chdir = TRUE)
```

All results were reported as significant at *p* < 0.05.

## Correlation
A Pearson product-moment correlation coefficient was computed by default for correlation analysis and a Spearman's rank correlation coefficient was additionally computed if normality assumption was violated based on the Shapiro-Wilk normality test.

### Tempo (IOIs)
Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_art$p.value))}`, Dynamics; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-1}*).  Participants tended to identify slower performances as teaching.

However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed. Therefore, a Spearman's rank correlation coefficient was additionally used to assess the relationship between performance tempi of dynamics recordings and participants' judgments. The result failed to reach significance (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`), suggesting that we need to be careful about the interpretation of the relationship between performance tempi of dynamics recordings and participants' judgments as teaching.

```{r ioi-1, include = FALSE}
cor_ioi_1 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line", palette = "d3",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype = "dotted", color = "gray", size = 1) +
  theme_pubr(base_size = 20, base_family = "Helvetica") +
  labs(color = "")
cor_ioi_1

# save
ggsave(here("paper/image", "cor_ioi_1.png"), plot = cor_ioi_1, dpi = 600, width = 7, height = 5)
img_cor_ioi_1 <- image_read(here("paper/image", "cor_ioi_1.png"))
```

### Articulation (KOT)
For articulation recordings, there was a significant relationship between KOT values and participants' judgments as teaching (*Figure \ref{fig:kot-1}*, left). Specifically, performances with shorter staccato (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`) and longer legato (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_leg$p.value))}`) were more likely to be judged as teaching.

For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`, Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`, *Figure \ref{fig:kot-1}*, right).

```{r kot-1, include = FALSE}
kot_all$Subcomponent <- factor(kot_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_kot_1 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
  theme_pubr(base_size = 20, base_family = "Helvetica") +
  labs(color = "")
cor_kot_1

# save
ggsave(here("paper/image", "cor_kot_1.png"), plot = cor_kot_1, dpi = 600, width = 7, height = 5)
img_cor_kot_1  <- image_read(here("paper/image", "cor_kot_1.png"))
```

### Dynamics (KV)
For dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-1}*, right). Specifically, performances with louder forte were more likely to be judged as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`). However, there was no significant relationship between KV values for piano and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia$p.value))}`).

For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-1}*, left).

```{r vel-1, include = FALSE}
vel_all$Subcomponent <- factor(vel_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_vel_1 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
  theme_pubr(base_size = 20, base_family = "Helvetica") +
  labs(color = "")
cor_vel_1

# save
ggsave(here("paper/image", "cor_vel_1.png"), plot = cor_vel_1, dpi = 600, width = 7, height = 5)
img_cor_vel_1  <- image_read(here("paper/image", "cor_vel_1.png"))
```

### Dynamics contrast (KV-Diff)
For dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (*Figure \ref{fig:vel-diff-1}*, right). Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).

For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ltos$p.value))}`, From Staccato to Legato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_stol$p.value))}`, *Figure \ref{fig:vel-diff-1}*, left).

```{r vel-diff-1, include = FALSE}
vel_diff_all$Subcomponent <- factor(vel_diff_all$Subcomponent, levels = c("LtoS", "StoL", "FtoP", "PtoF"))
cor_vel_diff_1 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
  theme_pubr(base_size = 20, base_family = "Helvetica") +
  labs(color = "")
cor_vel_diff_1

# save
ggsave(here("paper/image", "cor_vel_diff_1.png"), plot = cor_vel_diff_1, dpi = 600, width = 7, height = 5)
img_cor_vel_diff_1  <- image_read(here("paper/image", "cor_vel_diff_1.png"))
```

## Multiple regression

In order to further explore which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted. Statistical model assumptions were tested using the *performance* R package [@ludecke_2021] and all assumptions were met. Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs. staccato, forte vs. piano) and therefore cannot be summed up to represent each technique, we reported four regression models for each subcomponent (see details in *[Data analysis](#dataanalysis)*).

### Legato
A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato). The result of the regression indicated that the model explained `r summary(m1)$adj.r.squared*100` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r round(summary(m1)$fstatistic[1], 1)`, *p* `r if(lmp(m1) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m1)))}`). It was found that tempo (IOIs; *$\beta$* = `r summary(m1)$coefficients[2]`, *p* `r if(summary(m1)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[2, 4]))}`) and articulation for the legato parts (KOT; *$\beta$* = `r summary(m1)$coefficients[3]`, *p* `r if(summary(m1)$coefficients[3, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[3, 4]))}`) were significant predictors of participants' judgments as teaching.

### Staccato
A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato). The result of the regression indicated that the model explained `r summary(m2)$adj.r.squared*100` % of the variance (*F*(`r summary(m2)$fstatistic[2]`, `r summary(m2)$fstatistic[3]`) = `r round(summary(m2)$fstatistic[1], 1)`, *p* `r if(lmp(m2) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m2)))}`). It was found that tempo (IOIs; *$\beta$* = `r summary(m2)$coefficients[2]`, *p* `r if(summary(m2)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m2)$coefficients[2, 4]))}`) and articulation for the staccato parts (KOT; *$\beta$* = `r summary(m2)$coefficients[3]`, *p* `r if(summary(m2)$coefficients[3, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m2)$coefficients[3, 4]))}`) were significant predictors of participants' judgments as teaching.

### Forte
A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano). The result of the regression indicated that the model explained `r summary(m3)$adj.r.squared*100` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r round(summary(m3)$fstatistic[1], 1)`, *p* `r if(lmp(m3) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m3)))}`). It was found that tempo (IOIs; *$\beta$* = `r summary(m3)$coefficients[2]`, *p* `r if(summary(m3)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m3)$coefficients[2, 4]))}`) and dynamics for the forte parts (KV; *$\beta$* = `r summary(m3)$coefficients[4]`, *p* `r if(summary(m3)$coefficients[4, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m3)$coefficients[4, 4]))}`) were significant predictors of participants' judgments as teaching.

### Piano
A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte). The result of the regression indicated that the model explained `r summary(m4)$adj.r.squared*100` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r round(summary(m4)$fstatistic[1], 1)`, *p* `r if(lmp(m4) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m4)))}`). It was found that tempo (IOIs; *$\beta$* = `r summary(m4)$coefficients[2]`, *p* `r if(summary(m4)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[2, 4]))}`) and dynamics contrast from piano to forte (KV-Diff; *$\beta$* = `r summary(m4)$coefficients[5]`, *p* `r if(summary(m4)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[5, 4]))}`) were significant predictors of participants' judgments as teaching.

```{r plot-ioi-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:ioi-1}Experiment 1: Scatter plot showing the correlation between tempo feature (IOIs) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus."}
img_cor_ioi_1
```

```{r plot-kot-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:kot-1}Experiment 1: Scatter plot showing the correlation between articulation feature (KOT) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus."}
img_cor_kot_1
```

```{r plot-vel-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-1}Experiment 1: Scatter plot showing the correlation between dynamics feature (KV) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus."}
img_cor_vel_1
```

```{r plot-vel-diff-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-diff-1}Experiment 1: Scatter plot showing the correlation between dynamics contrast feature (KV-Diff) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus."}
img_cor_vel_diff_1
```

\clearpage

# Discussion

Experiment 1 investigated which features of piano performance made musicians (in the role of potential learners) infer teaching intentions. The results demonstrated that performances with slower tempo were more likely to be judged as teaching by musicians regardless which expressive technique was implemented in the piece. For articulation recordings, performances with longer legato and shorter staccato were tended to be judged as teaching. For dynamics recordings, performances with louder forte were more likely to be judged as teaching whereas there was no relationship between softer sound (i.e., piano) and participants' judgements as teaching. However, performances with larger contrasts between forte and piano for both directions (i.e., from forte to piano, from piano to forte) were more likely to be judged as teaching. This result may suggest that dynamics contrast might be reliably used to infer teaching intentions, rather than absolute dynamics values themselves. Moreover, multiple regression analyses implied that tempo feature is the strongest predictor of participants' judgments as teaching in general whereas there were specific predictors depending on which expressive technique was implemented in the piece. These performance features were overall consistent with what expert pianists did in our previous experiments for teaching purposes. Therefore, our findings suggest that musicians may be able to successfully infer teaching intentions of expert pianists, only by listening to recorded performances.

\clearpage

# Experiment 2

The aim of Experiment 2 was to replicate our previous findings in Experiment 1 with a more naturalistic piece of music. We could not finish data collection, therefore interpreted data by looking at scatter plots without any statistical analysis.

```{r questionnaire-2, include = FALSE}
source(here("experiment-2/analysis", "questionnaire.R"), chdir = TRUE)
```

# Methods
## Participants
We recruited `r nrow(dt)` participants who had at least six years of training in any musical instrument or singing. They were able to read sheet music and know two musical expressive techniques of articulation and dynamics. One participant was excluded because s/he did not understand the instructions. Therefore, `r nrow(dt_included)` participants (Female: `r nrow(dt_included[Gender == "Female"])`) were included for data analysis and had `r round(mean(dt_included$Training), 2)` years of training on average in any musical instrument or singing (*SD* = `r round(sd(dt_included$Training), 2)`). Most people were right-handed (Left; `r nrow(dt_included[Handedness == "Left"])`) with a mean age of `r round(mean(dt_included$Age), 2)` (*SD* = `r round(sd(dt_included$Age), 2)`). As Experiment 1, all participants were recruited through the SONA system and the study (No. 2020/02) was approved by the PREBO CEU PU in Austria.

## Apparatus and procedure
The experimental setting and procedure were identical to Experiment 1 except that each block consisted of 4 practice trials and 36 experimental trials. The number of trials was reduced due to the time constraint of the experiment.

## Stimuli
As Experiment 1, stimuli were produced by actual pianists on a weighed Yamaha MIDI digital piano and recorded as MIDI files. One piece of music was selected as a base piece, which was performed with a musical expressive technique of either articulation (*Figure \ref{fig:stim2}*, A) or dynamics (*Figure \ref{fig:stim2}*, B). The excerpt was taken from ``Sonatina Op.36 (No.3) in C major" by Muzio Clementi and modified for the experiment. The stimuli were performed around 100 - 120 quarter-beats per minute (i.e., around 250 - 300 ms for 8th-note IOIs).

Recorded piano performances for the stimuli were obtained from our previous experiments (Tominaga et al., *in prep*). Half of the stimuli (36 recordings) was randomly chosen from 248 valid performances in the teaching condition whereas the other half (36 recordings) was randomly chosen from 256 valid performances in the performing condition. In total, 72 recordings were selected as stimuli for the current experiment. Again, it is important to note that each recording from the teaching condition did not necessarily exhibit specific features of teaching performances that we found in the previous experiments since we randomly sampled recordings.

## Data analysis{#dataanalysis2}
As Experiment 1, stimuli were quantified with regard to tempo (IOIs), articulation (KOT), dynamics (KV) and dynamics contrast (KV-Diff). Only the 8th notes with expressive notations were included for data analysis. We did not run any statistical analysis for Experiment 2.

```{r stim-2, out.width = "100%", fig.cap = "\\label{fig:stim2}Stimuli. (A)Articulation. The curved line (slur) indicates legato and the dots indicate staccato. (B)Dynamics. The symbol `f' denotes forte and the symbol `p' denotes piano. Only the 8th notes with expressive notations were used for data analysis.", echo = FALSE}
stim_a_2 <- image_border(image_read(here("paper/image", "stim_a_2.png")), "#FFFFFF", "120x120")
stim_d_2 <- image_border(image_read(here("paper/image", "stim_d_2.png")), "#FFFFFF", "120x120")

# combine
img_stimuli_2 <- image_append(c(stim_a_2, stim_d_2), stack = TRUE)
img_stimuli_2 <- image_annotate(img_stimuli_2, "(A)", size = 80, location = "+100+70", color = "black", font = "helvetica")
img_stimuli_2 <- image_annotate(img_stimuli_2, "(B)", size = 80, location = "+100+1125", color = "black", font = "helvetica")
img_stimuli_2
```

# Results

```{r results-2, cache = TRUE, include = FALSE}
source(here("experiment-2/analysis", "analysis.R"), chdir = TRUE)
```

## Scatter plots
### Tempo (IOIs)
As Experiment 1, it seems that performance tempi (IOIs) are correlated with participants' judgments as teaching. Slower performances were more likely to be judged as teaching. However, the slope of articulation seems to be less steep than that of Experiment 1 (*Figure \ref{fig:ioi-2}*).

```{r ioi-2, include = FALSE}
cor_ioi_2 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line", palette = "d3",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
  theme_pubr(base_size = 20, base_family = "Helvetica") +
  labs(color = "")
cor_ioi_2

# save
ggsave(here("paper/image", "cor_ioi_2.png"), plot = cor_ioi_2, dpi = 600, width = 7, height = 5)
img_cor_ioi_2 <- image_read(here("paper/image", "cor_ioi_2.png"))
```

### Articulation (KOT)
Unlike Experiment 1, there seems to be no relationship between KOT values and participants' judgments as teaching. The scatter plot suggests that participants did not use articulation values to infer teaching intentions (*Figure \ref{fig:kot-2}*).

```{r kot-2, include = FALSE}
kot_all$Subcomponent <- factor(kot_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_kot_2 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
  theme_pubr(base_size = 20, base_family = "Helvetica") +
  labs(color = "")
cor_kot_2

# save
ggsave(here("paper/image", "cor_kot_2.png"), plot = cor_kot_2, dpi = 600, width = 7, height = 5)
img_cor_kot_2  <- image_read(here("paper/image", "cor_kot_2.png"))
```

### Dynamics (KV)
As Experiment 1, there seems to be a relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-2}*). Performances with louder forte adn softer piano seem to be judged as teaching.

```{r vel-2, include = FALSE}
vel_all$Subcomponent <- factor(vel_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_vel_2 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
  theme_pubr(base_size = 20, base_family = "Helvetica") +
  labs(color = "")
cor_vel_2

# save
ggsave(here("paper/image", "cor_vel_2.png"), plot = cor_vel_2, dpi = 600, width = 7, height = 5)
img_cor_vel_2  <- image_read(here("paper/image", "cor_vel_2.png"))
```

### Dynamics contrast (KV-Diff)
As Experiment 1, there seems to be a relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-diff-2}*). Performances with larger contrasts between forte and piano seem to be judged as teaching.

```{r vel-diff-2, include = FALSE}
vel_diff_all$Subcomponent <- factor(vel_diff_all$Subcomponent, levels = c("LtoS", "StoL", "FtoP", "PtoF"))
cor_vel_diff_2 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
  theme_pubr(base_size = 20, base_family = "Helvetica") +
  labs(color = "")
cor_vel_diff_2

# save
ggsave(here("paper/image", "cor_vel_diff_2.png"), plot = cor_vel_diff_2, dpi = 600, width = 7, height = 5)
img_cor_vel_diff_2  <- image_read(here("paper/image", "cor_vel_diff_2.png"))
```

```{r plot-ioi-2, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:ioi-2}Experiment 2: Scatter plot showing the correlation between tempo featurea (IOIs) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus."}
img_cor_ioi_2
```

```{r plot-kot-2, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:kot-2}Experiment 2: Scatter plot showing the correlation between articulation features (KOT) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus."}
img_cor_kot_2
```

```{r plot-vel-2, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-2}Experiment 2: Scatter plot showing the correlation between dynamics features (KV) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus."}
img_cor_vel_2
```

```{r plot-vel-diff-2, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-diff-2}Experiment 2: Scatter plot showing the correlation between dynamics contrast features (KV-Diff) and average participants' judgment as teaching for each stimulus."}
img_cor_vel_diff_2
```

# Discussion
Experiment 2 aims to replicate our previous findings in Experiment 1 with a more naturalistic piece of music. The preliminary data suggest that some features of piano performance contributes to participant' judgments as teaching. For instance, performances with slower tempo were likely to be judged as teaching regardless which expressive technique was implemented. Also, performances with louder forte and softer piano were likely to be judged as teaching for dynamics recordings. Moreover, there seems to be a strong relationship between dynamics contrast between forte and piano and participants' judgments as teaching.

However, it seems there was no relationship between articulation values and participants' judgments as teaching. Compared with Experiment 1, the piece used in Experiment 2 was musically much complex. Therefore, articulation features may not be that reliable in order to infer teaching intentions. Unlike tempo and loudness, which are relatively easier to understand, articulation is very particular to music. The reason we could not see a relationship between articulation values and participants' judgments as teaching might be coming from conceptual and perceptual difficulties of articulation, even for musicians.

\newpage

# References

\begingroup
\setlength{\parindent}{-0in}
\setlength{\leftskip}{0in}
<div id="refs" custom-style="Bibliography"></div>

\endgroup

```{r results-prereg, cache = TRUE}
source(here("experiment-1/analysis/prereg_analysis", "prereg_analysis.R"), chdir = TRUE)
```

<!-- # Supplementary Materials{#supplementary} -->

<!-- ## Accuracy for Experiment 1 -->
<!-- We examined whether participants could accurately judge the stimuli chosen from the teaching condition in the previous experiments as teaching (yes response in the current experiment) and the stimuli chosen from the performing condition in the previous experiments as performing (no response in the current experiment). We compared how accurate participants were against the chance level (50%). The results revealed that the accuracy of participants' judgments was above the chance level (*M* = `r round(mean(ind_data_ad[Skill == "articulation"]$Percent), 1)`, *SD* = `r round(sd(ind_data_ad[Skill == "articulation"]$Percent), 2)`; *t*(`r t.test(ind_data$Percent, mu = 50, alternative = "two.sided")$parameter`) = `r t.test(ind_data$Percent, mu = 50, alternative = "two.sided")$statistic`, *p* `r if(t.test(ind_data$Percent, mu = 50, alternative = "two.sided")$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`). However, the 95 confidence intervals for the sample mean contained the sample -->

### 2022-01-27 paper/manuscript.tex
upload manuscript
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={What makes listeners infer teaching intentions?},
  pdfauthor={Atsuko Tominaga1,*, Günther Knoblich1, \& Natalie Sebanz1},
  pdflang={en-EN},
  pdfkeywords={teaching, intention, skill transmission, musical expression},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{teaching, intention, skill transmission, musical expression}
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{What makes listeners infer teaching intentions?}
\author{Atsuko Tominaga\textsuperscript{1,*}, Günther Knoblich\textsuperscript{1}, \& Natalie Sebanz\textsuperscript{1}}
\date{}

\shorttitle{What makes listeners infer teaching intentions?}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Cognitive Science, Central European University, Quellenstraße 51, 1100 Vienna, Austria\\\textsuperscript{*} Corresponding author: \href{mailto:Tominaga_Atsuko@phd.ceu.edu}{\nolinkurl{Tominaga\_Atsuko@phd.ceu.edu}}}

\abstract{
Social learning plays an important role in human skill transmission. It has been known that experts tend to change their behaviour particularly for teaching purposes. Our previous research demonstrated that expert pianists systematically modulated their sound so as to teach musical expressive techniques such as articulation and dynamics. For example, pianists played slower and exaggerated each technique when they had an intention to teach. In order to achieve successful skill transmission, it is vital to examine whether such sound modulations are identified and used to infer teaching intentions by novices, who are going to acquire skills. The current experiments investigated which features of piano performance make musicians (in the role of potential learners) infer teaching intentions. Musicians listened to a number of piano recordings where a musical expressive technique of either articulation or dynamics was implemented. Musicians were asked to judge whether each performance was produced in order to teach the designated expressive technique. We quantified recordings with regard to tempo, articulation and dynamics. Overall, slower tempo contributed to musicians' judgments as teaching. Moreover, performances with exaggeration for each technique (e.g., shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching. These performance features are consistent with expert pianists' sound modulations for teaching purposes. Therefore, musicians (in the role of potential learners) seem to be able to identify didactic sound modulations, only by listening to recorded performances.
}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Learning from others is one of the important elements of skill acquisition. Not only are we able to learn by observing and imitating others, but also we benefit greatly from interacting with others such as teachers and peers (Tomasello, Kruger, \& Ratner, 1993). Adults are often being pedagogical to children in order to explain and transmit cultural conventions (Csibra \& Gergely, 2009). Active teaching seems to play a crucial role not only to transit skills over generations but also to further develop sophisticated cultures, which cannot be achieved by one single individual or generation (Tennie, Call, \& Tomasello, 2009). From a learner's perspective, it is important to identify informative teachers and infer teachers' expectations so that learners can acquire skills through interacting with teachers (Gweon, 2020; Veissière, Constant, Ramstead, Friston, \& Kirmayer, 2020).

In pedagogical settings where teachers are supposed to convey useful information to learners, it has been found that teachers often modulate their behaviour for teaching purposes. For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills (e.g., Brand, Baldwin, \& Ashburn, 2002; Kuhl, 2004). Also, some studies have revealed that even towards adult learners, people modulated their speech and action in the similar way as they did for infants (McEllin, Knoblich, \& Sebanz, 2017; Uther, Knoll, \& Burnham, 2007). These findings suggest that there are general pedagogical behaviours such as slow demonstration and exaggeration of speech and action to send teaching intentions to learners.

Tominaga, Knoblich \& Sebanz (\emph{in prep}) extended this line of research to expertise transmission where skills to be acquired are much more complicated than general knowledge, which is mostly acquired throughout development (e.g., Csibra \& Gergely, 2009). Expertise usually demands an enormous amount of practice to acquire so that only experts can accomplish a higher level of performance including artistic expression. Based on the assumption that expert pianists are very good at controlling and modulating their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound). The results demonstrated that expert pianists could successfully modulate their performance by playing slower or exaggerating relevant aspects of the performance (e.g., producing shorter staccato or making a larger contrast between forte and piano) to teach musical expressive techniques. Therefore, it seems that even in the domain of expertise, experts exhibit general pedagogical behaviours to communicate with their potential learners.

In order to achieve successful skill transmission, it is necessary to investigate whether novice learners can identify teaching intentions produced by experts. A recent study by McEllin, Sebanz, and Knoblich (2018) demonstrated that people could identify informative intentions such as acting with others or teaching by relying on specific kinematics cues (e.g., velocity profiles of movements). Some research in the field of action expertise suggest that motor simulation (i.e., using one's own motor systems to simulate an action) plays a key role to understand observed actions. For example, expert basketball players were better at predicting the outcome of a free shot compared to expert observers (coaches or sports journalists) and novices (Aglioti, Cesari, Romani, \& Urgesi, 2008). Also, it was found that deceptive intentions of fake basketball passes were detected from non-verbal bodily cues only by expert basketball players (Sebanz \& Shiffrar, 2009). Taken together, people seem to be able to infer informative intentions by observing actions and motor expertise may enable accurate action prediction.

In the domain of music, musical emotion is often communicated by sound alone and listeners seem to be able to infer performers' intended emotions only by listening to recorded performances (e.g., Akkermans et al., 2019; Gabrielsson \& Juslin, 1996). It has been known that musicians are generally more accurate to decode emotions from performances (Battcock \& Schutz, 2021; Lima \& Castro, 2011). Repp and Knoblich (2004) also found that expert pianists could distinguish their own performance from others' performances by listening to recordings. These results suggest that musical expertise may be important to accurately identify and infer intentions by listening to recorded performances.

The current experiments investigate which features of piano performance make musicians (in the role of potential learners) infer teaching intentions, only by listening to recorded performances. We collected various piano recordings from our previous experiments (Tominaga et al., \emph{in prep}). The obtained recordings consisted of two pieces (one was used for Experiment 1 and the other was used for Experiment 2 in the current paper). The two pieces were performed by various pianists multiple times, therefore the recordings contained many variations in terms of timing, articulation and dynamics. In the current experiments, we asked musically trained participants to judge which performance was performed for teaching purposes. If teachers' intentions are successfully communicated with learners, pedagogical behavioural features in our previous experiments such as slower demonstration and exaggerated performance should be identified and used to infer teaching intentions. In Experiment 1, we examined which features of piano performance were correlated with participants judgments as ``teaching''. Experiment 2 was conducted to replicate what we found in Experiment 1 with a more naturalistic piece of music.

\hypertarget{experiment-1}{%
\section{Experiment 1}\label{experiment-1}}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

We recruited 21 participants who had at least six years of training in any musical instrument. They were able to read sheet music and knew two musical expressive techniques of articulation and dynamics. One participant was excluded due to an experimental error. Therefore, 20 participants (Female: 13) were included for data analysis and had 11.85 years of musical training on average (\emph{SD} = 5.62). They were all right-handed with a mean age of 28.80 (\emph{SD} = 9.09). All participants were recruited through an online participant platform (SONA system, \url{https://www.sona-systems.com}). The study (No.~2020/02) was approved by the Psychological Research Ethics Board (PREBO) CEU PU in Austria.

\hypertarget{apparatus}{%
\subsection{Apparatus}\label{apparatus}}

The experiment was programmed in Python 3.8.2 using the PsychoPy library (2020.2.4; \url{https://www.psychopy.org/}) on a Mac Book Pro with Mac OS X 10.15.6. Stimuli (MIDI data) were played using the Mido library (1.2.9; \url{https://mido.readthedocs.io/en/latest/}) on a Max/MSP patcher (8.1.7; \url{https://cycling74.com/products/max}). During the experiment, participants listened to the stimuli via headphones (Audio-Technica ATH-M50X).

\hypertarget{stimuli}{%
\subsection{Stimuli}\label{stimuli}}

Piano recordings obtained as MIDI data were used as Stimuli. Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files. One piece of music was selected as a base piece, which was performed with a musical expressive technique of either articulation (\emph{Figure \ref{fig:stim1}}, A) or dynamics (\emph{Figure \ref{fig:stim1}}, B). The piece was taken from ``A Dozen a Day - Play with Ease in Many Keys'' by Edna-Mae Burnam and modified for the experiment. Therefore, all stimuli had the same musical sequence but had subtle differences in terms of musical expressions (e.g., timing, articulation and dynamics). Articulation refers to the smoothness of sound, which is comprised of legato and staccato. Legato indicates smooth and connected sound whereas staccato indicates sharp and separate sound. Dynamics refers to the loudness of sound, which is comprised of forte and piano. Forte indicates loud sound while piano indicates soft sound. The stimuli were performed around 80 quarter-beats per minute (i.e., around 188 ms for 16th-note IOIs).

96 stimuli (MIDI recordings) were obtained from our previous experiments (Tominaga et al., \emph{submitted}). In the previous experiments, we asked expert pianists to perform one piece of music with a musical expressive technique of either articulation (\emph{Figure \ref{fig:stim1}}, A) or dynamics (\emph{Figure \ref{fig:stim1}}, B). There were two experimental conditions. In the teaching condition, participants were instructed to perform the piece with the designated expressive technique as if they were teaching it to students (e.g., in a lesson). In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert). There were 453 valid performances (i.e., performances without any pitch error) for the teaching condition and 436 valid performances for the performing conditions. We randomly chose 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition. It is important to note that the recordings from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments since we randomly sampled the recordings.

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

Upon arrival, participants read information sheet about the experiment and gave informed consent prior to participation. In the experiment, all instructions were displayed on a computer screen and an experimenter also explained the procedure. Participants were instructed that they were going to listen to piano recordings and would be asked if each recording was performed as if a pianist were teaching it to students (e.g., in a lesson / teaching) or as if a pianist were performing it to an audience (e.g., in a concert / performing). They responded by pressing either a yes (teaching / left arrow key) or no (performing / right arrow key) button. While listening to each stimulus, sheet music, which corresponded to the stimulus, was shown on a monitor in front of the participants. After making a judgment, the next recording was played (\emph{Figure \ref{fig:procedure1}}).

There were two blocks and each block only contained recordings with one musical expressive technique of either articulation or dynamics. Each block consisted of 4 practice trials and 48 experimental trials. In each trial, participants listened to one recording only once. After listening the recording, they were asked to judge by pressing either the left arrow key (i.e., teaching) or the right arrow key (i.e., performing). Each recording was evaluated only once in the experiment. The order of the blocks was counterbalanced across the participants. The order of the recordings was randomised within each block.

At the end of the experiment, participants filled in a questionnaire about their demographic information and experience in musical instruments.

\hypertarget{dataanalysis}{%
\subsection{Data analysis}\label{dataanalysis}}

Data processing and statistical analysis were performed in R version 4.0.5. Correlation analysis was performed with the standard \emph{cor} function and regression models for multiple regression were fit with the standard \emph{lm} function from the \emph{stats} R package. Stimuli (MIDI files) were converted to numerical data in terms of time, pitch and velocity for the onset and offset of each note using the \emph{tuneR} R package (\url{https://cran.r-project.org/web/packages/tuneR/tuneR.pdf}).

Stimuli (performances) were quantified with regard to tempo (interonset intervals; IOIs), articulation (key-overlap time; KOT), dynamics (key velocity; KV) and dynamics contrast (key velocity difference; KV-Diff) only for 16th notes. Interonset intervals are time intervals between onsets of adjacent notes. Larger IOIs indicate slower tempo while smaller IOIs indicate faster tempo. Key-overlap time is the time overlap between two adjacent notes, namely the difference between the offset time of the current note and the onset time of the ensuing note (e.g., Bresin \& Battel, 2000). Positive KOT values indicate legato styles whereas negative KOT values indicate staccato styles. Key velocity is obtained from MIDI data to describe how fast a performer hit the key. Larger KV values indicate forte styles while smaller KV values indicate piano styles. Additionally, we also measured dynamics contrast where one subcomponent of the technique moves to the other (e.g., from forte to piano) to illustrate how much dynamics contrast a performer made at transition points.

First, we investigated data by looking at correlations between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as ``teaching'' (i.e., what percentage of participants responded as ``yes (teaching)'') for each stimulus. Second, we run multiple regression and entered all four performance features to examine which predictor significantly contributed to participants' judgments as teaching. Since articulation and dynamics were comprised of two opposite directional values (i.e., legato vs.~staccato, forte vs.~piano), we entered each subcomponent (i.e., legato, staccato, forte, piano) separately to represent either an articulation or dynamics feature of the performance for a regression model. For articulation recordings, there were two models. The first model considered only legato parts of the stimuli for KOT and KV, and transition points from legato to staccato for KV-Diff. The second model considered only staccato parts of the stimuli for KOT and KV, and transition points from staccato to legato for KV-Diff. For dynamics recordings, there were two models. The first model considered only forte parts of the stimuli for KV and KOT, and transition points from forte to piano for KV-Diff. The second model considered only piano parts of the stimuli for KV and KOT, and transition points from piano to forte for KV-Diff. With regard to tempo (IOIs), there was only one value for each technique because tempo was consistent across the performance and was not dependent on subcomponents.

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/stim-1-1} \caption{\label{fig:stim1}Stimuli. (A)Articulation. The curved line (slur) indicates legato and the dots indicate staccato. (B)Dynamics. The symbol `f' denotes forte and the symbol `p' denotes piano. Only the 16th notes were used for data analysis.}\label{fig:stim-1}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/atsukotominaga/Google Drive/Project/music-perception/paper/image/procedure} \caption{\label{fig:procedure1}Procedure. Participants listened to a recording via headphones while corresponding sheet music was displayed on a monitor. They were required to respond by pressing a left-arrow (yes) or right-arrow (no) key for each judgment.}\label{fig:procedure-1}
\end{figure}

\clearpage

\hypertarget{results}{%
\section{Results}\label{results}}

All results were reported as significant at \emph{p} \textless{} 0.05.

\hypertarget{correlation}{%
\subsection{Correlation}\label{correlation}}

A Pearson product-moment correlation coefficient was computed by default for correlation analysis and a Spearman's rank correlation coefficient was additionally computed if normality assumption was violated based on the Shapiro-Wilk normality test.

\hypertarget{tempo-iois}{%
\subsubsection{Tempo (IOIs)}\label{tempo-iois}}

Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; \emph{r} = .77, \emph{p} \textless{} 0.001, Dynamics; \emph{r} = .42, \emph{p} = 0.003, \emph{Figure \ref{fig:ioi-1}}). Participants tended to identify slower performances as teaching.

However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed. Therefore, a Spearman's rank correlation coefficient was additionally used to assess the relationship between performance tempi of dynamics recordings and participants' judgments. The result failed to reach significance (\emph{r} = .27, \emph{p} = 0.066), suggesting that we need to be careful about the interpretation of the relationship between performance tempi of dynamics recordings and participants' judgments as teaching.

\hypertarget{articulation-kot}{%
\subsubsection{Articulation (KOT)}\label{articulation-kot}}

For articulation recordings, there was a significant relationship between KOT values and participants' judgments as teaching (\emph{Figure \ref{fig:kot-1}}, left). Specifically, performances with shorter staccato (\emph{r} = -.73, \emph{p} \textless{} 0.001) and longer legato (\emph{r} = .40, \emph{p} = 0.005) were more likely to be judged as teaching.

For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r} = -.04, \emph{p} = 0.81, Piano; \emph{r} = -.19, \emph{p} = 0.19, \emph{Figure \ref{fig:kot-1}}, right).

\hypertarget{dynamics-kv}{%
\subsubsection{Dynamics (KV)}\label{dynamics-kv}}

For dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-1}}, right). Specifically, performances with louder forte were more likely to be judged as teaching (\emph{r} = .45, \emph{p} = 0.001). However, there was no significant relationship between KV values for piano and participants' judgments as teaching (\emph{r} = -.22, \emph{p} = 0.13).

For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r} = .10, \emph{p} = 0.52, Staccato; \emph{r} = -.02, \emph{p} = 0.87, \emph{Figure \ref{fig:vel-1}}, left).

\hypertarget{dynamics-contrast-kv-diff}{%
\subsubsection{Dynamics contrast (KV-Diff)}\label{dynamics-contrast-kv-diff}}

For dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (\emph{Figure \ref{fig:vel-diff-1}}, right). Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r} = -.50, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r} = .62, \emph{p} \textless{} 0.001).

For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r} = -.26, \emph{p} = 0.071, From Staccato to Legato; \emph{r} = -.19, \emph{p} = 0.21, \emph{Figure \ref{fig:vel-diff-1}}, left).

\hypertarget{multiple-regression}{%
\subsection{Multiple regression}\label{multiple-regression}}

In order to further explore which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted. Statistical model assumptions were tested using the \emph{performance} R package (Lüdecke, Ben-Shachar, Patil, Waggoner, \& Makowski, 2021) and all assumptions were met. Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique, we reported four regression models for each subcomponent (see details in \emph{\protect\hyperlink{dataanalysis}{Data analysis}}).

\hypertarget{legato}{%
\subsubsection{Legato}\label{legato}}

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato). The result of the regression indicated that the model explained 64.63 \% of the variance (\emph{F}(4, 43) = 22.50, \emph{p} \textless{} 0.001). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.78, \emph{p} \textless{} 0.001) and articulation for the legato parts (KOT; \emph{\(\beta\)} = 0.26, \emph{p} = 0.004) were significant predictors of participants' judgments as teaching.

\hypertarget{staccato}{%
\subsubsection{Staccato}\label{staccato}}

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato). The result of the regression indicated that the model explained 63.97 \% of the variance (\emph{F}(4, 43) = 21.90, \emph{p} \textless{} 0.001). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.52, \emph{p} = 0.002) and articulation for the staccato parts (KOT; \emph{\(\beta\)} = -0.28, \emph{p} = 0.020) were significant predictors of participants' judgments as teaching.

\hypertarget{forte}{%
\subsubsection{Forte}\label{forte}}

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano). The result of the regression indicated that the model explained 35.90 \% of the variance (\emph{F}(4, 43) = 7.60, \emph{p} \textless{} 0.001). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.35, \emph{p} = 0.007) and dynamics for the forte parts (KV; \emph{\(\beta\)} = 0.73, \emph{p} = 0.048) were significant predictors of participants' judgments as teaching.

\hypertarget{piano}{%
\subsubsection{Piano}\label{piano}}

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte). The result of the regression indicated that the model explained 51.21 \% of the variance (\emph{F}(4, 43) = 13.30, \emph{p} \textless{} 0.001). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.38, \emph{p} \textless{} 0.001) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 0.99, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.

\begin{figure}

{\centering \includegraphics[width=0.7\linewidth]{manuscript_files/figure-latex/plot-ioi-1-1}

}

\caption{\label{fig:ioi-1}Experiment 1: Scatter plot showing the correlation between tempo feature (IOIs) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus.}\label{fig:plot-ioi-1}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.7\linewidth]{manuscript_files/figure-latex/plot-kot-1-1}

}

\caption{\label{fig:kot-1}Experiment 1: Scatter plot showing the correlation between articulation feature (KOT) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus.}\label{fig:plot-kot-1}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.7\linewidth]{manuscript_files/figure-latex/plot-vel-1-1}

}

\caption{\label{fig:vel-1}Experiment 1: Scatter plot showing the correlation between dynamics feature (KV) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus.}\label{fig:plot-vel-1}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.7\linewidth]{manuscript_files/figure-latex/plot-vel-diff-1-1}

}

\caption{\label{fig:vel-diff-1}Experiment 1: Scatter plot showing the correlation between dynamics contrast feature (KV-Diff) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus.}\label{fig:plot-vel-diff-1}
\end{figure}

\clearpage

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Experiment 1 investigated which features of piano performance made musicians (in the role of potential learners) infer teaching intentions. The results demonstrated that performances with slower tempo were more likely to be judged as teaching by musicians regardless which expressive technique was implemented in the piece. For articulation recordings, performances with longer legato and shorter staccato were tended to be judged as teaching. For dynamics recordings, performances with louder forte were more likely to be judged as teaching whereas there was no relationship between softer sound (i.e., piano) and participants' judgements as teaching. However, performances with larger contrasts between forte and piano for both directions (i.e., from forte to piano, from piano to forte) were more likely to be judged as teaching. This result may suggest that dynamics contrast might be reliably used to infer teaching intentions, rather than absolute dynamics values themselves. Moreover, multiple regression analyses implied that tempo feature is the strongest predictor of participants' judgments as teaching in general whereas there were specific predictors depending on which expressive technique was implemented in the piece. These performance features were overall consistent with what expert pianists did in our previous experiments for teaching purposes. Therefore, our findings suggest that musicians may be able to successfully infer teaching intentions of expert pianists, only by listening to recorded performances.

\clearpage

\hypertarget{experiment-2}{%
\section{Experiment 2}\label{experiment-2}}

The aim of Experiment 2 was to replicate our previous findings in Experiment 1 with a more naturalistic piece of music. We could not finish data collection, therefore interpreted data by looking at scatter plots without any statistical analysis.

\hypertarget{methods-1}{%
\section{Methods}\label{methods-1}}

\hypertarget{participants-1}{%
\subsection{Participants}\label{participants-1}}

We recruited 21 participants who had at least six years of training in any musical instrument or singing. They were able to read sheet music and know two musical expressive techniques of articulation and dynamics. One participant was excluded because s/he did not understand the instructions. Therefore, 20 participants (Female: 10) were included for data analysis and had 12.65 years of training on average in any musical instrument or singing (\emph{SD} = 5.40). Most people were right-handed (Left; 1) with a mean age of 33.55 (\emph{SD} = 12.80). As Experiment 1, all participants were recruited through the SONA system and the study (No.~2020/02) was approved by the PREBO CEU PU in Austria.

\hypertarget{apparatus-and-procedure}{%
\subsection{Apparatus and procedure}\label{apparatus-and-procedure}}

The experimental setting and procedure were identical to Experiment 1 except that each block consisted of 4 practice trials and 36 experimental trials. The number of trials was reduced due to the time constraint of the experiment.

\hypertarget{stimuli-1}{%
\subsection{Stimuli}\label{stimuli-1}}

As Experiment 1, stimuli were produced by actual pianists on a weighed Yamaha MIDI digital piano and recorded as MIDI files. One piece of music was selected as a base piece, which was performed with a musical expressive technique of either articulation (\emph{Figure \ref{fig:stim2}}, A) or dynamics (\emph{Figure \ref{fig:stim2}}, B). The excerpt was taken from ``Sonatina Op.36 (No.3) in C major'' by Muzio Clementi and modified for the experiment. The stimuli were performed around 100 - 120 quarter-beats per minute (i.e., around 250 - 300 ms for 8th-note IOIs).

Recorded piano performances for the stimuli were obtained from our previous experiments (Tominaga et al., \emph{in prep}). Half of the stimuli (36 recordings) was randomly chosen from 248 valid performances in the teaching condition whereas the other half (36 recordings) was randomly chosen from 256 valid performances in the performing condition. In total, 72 recordings were selected as stimuli for the current experiment. Again, it is important to note that each recording from the teaching condition did not necessarily exhibit specific features of teaching performances that we found in the previous experiments since we randomly sampled recordings.

\hypertarget{dataanalysis2}{%
\subsection{Data analysis}\label{dataanalysis2}}

As Experiment 1, stimuli were quantified with regard to tempo (IOIs), articulation (KOT), dynamics (KV) and dynamics contrast (KV-Diff). Only the 8th notes with expressive notations were included for data analysis. We did not run any statistical analysis for Experiment 2.

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/stim-2-1} \caption{\label{fig:stim2}Stimuli. (A)Articulation. The curved line (slur) indicates legato and the dots indicate staccato. (B)Dynamics. The symbol `f' denotes forte and the symbol `p' denotes piano. Only the 8th notes with expressive notations were used for data analysis.}\label{fig:stim-2}
\end{figure}

\hypertarget{results-1}{%
\section{Results}\label{results-1}}

\hypertarget{scatter-plots}{%
\subsection{Scatter plots}\label{scatter-plots}}

\hypertarget{tempo-iois-1}{%
\subsubsection{Tempo (IOIs)}\label{tempo-iois-1}}

As Experiment 1, it seems that performance tempi (IOIs) are correlated with participants' judgments as teaching. Slower performances were more likely to be judged as teaching. However, the slope of articulation seems to be less steep than that of Experiment 1 (\emph{Figure \ref{fig:ioi-2}}).

\hypertarget{articulation-kot-1}{%
\subsubsection{Articulation (KOT)}\label{articulation-kot-1}}

Unlike Experiment 1, there seems to be no relationship between KOT values and participants' judgments as teaching. The scatter plot suggests that participants did not use articulation values to infer teaching intentions (\emph{Figure \ref{fig:kot-2}}).

\hypertarget{dynamics-kv-1}{%
\subsubsection{Dynamics (KV)}\label{dynamics-kv-1}}

As Experiment 1, there seems to be a relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-2}}). Performances with louder forte adn softer piano seem to be judged as teaching.

\hypertarget{dynamics-contrast-kv-diff-1}{%
\subsubsection{Dynamics contrast (KV-Diff)}\label{dynamics-contrast-kv-diff-1}}

As Experiment 1, there seems to be a relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-diff-2}}). Performances with larger contrasts between forte and piano seem to be judged as teaching.

\begin{figure}

{\centering \includegraphics[width=0.7\linewidth]{manuscript_files/figure-latex/plot-ioi-2-1}

}

\caption{\label{fig:ioi-2}Experiment 2: Scatter plot showing the correlation between tempo featurea (IOIs) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus.}\label{fig:plot-ioi-2}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.7\linewidth]{manuscript_files/figure-latex/plot-kot-2-1}

}

\caption{\label{fig:kot-2}Experiment 2: Scatter plot showing the correlation between articulation features (KOT) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus.}\label{fig:plot-kot-2}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.7\linewidth]{manuscript_files/figure-latex/plot-vel-2-1}

}

\caption{\label{fig:vel-2}Experiment 2: Scatter plot showing the correlation between dynamics features (KV) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus.}\label{fig:plot-vel-2}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.7\linewidth]{manuscript_files/figure-latex/plot-vel-diff-2-1}

}

\caption{\label{fig:vel-diff-2}Experiment 2: Scatter plot showing the correlation between dynamics contrast features (KV-Diff) and average participants' judgment as teaching for each stimulus.}\label{fig:plot-vel-diff-2}
\end{figure}

\hypertarget{discussion-1}{%
\section{Discussion}\label{discussion-1}}

Experiment 2 aims to replicate our previous findings in Experiment 1 with a more naturalistic piece of music. The preliminary data suggest that some features of piano performance contributes to participant' judgments as teaching. For instance, performances with slower tempo were likely to be judged as teaching regardless which expressive technique was implemented. Also, performances with louder forte and softer piano were likely to be judged as teaching for dynamics recordings. Moreover, there seems to be a strong relationship between dynamics contrast between forte and piano and participants' judgments as teaching.

However, it seems there was no relationship between articulation values and participants' judgments as teaching. Compared with Experiment 1, the piece used in Experiment 2 was musically much complex. Therefore, articulation features may not be that reliable in order to infer teaching intentions. Unlike tempo and loudness, which are relatively easier to understand, articulation is very particular to music. The reason we could not see a relationship between articulation values and participants' judgments as teaching might be coming from conceptual and perceptual difficulties of articulation, even for musicians.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0in}
\setlength{\leftskip}{0in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-aglioti_2008}{}}%
Aglioti, S. M., Cesari, P., Romani, M., \& Urgesi, C. (2008). Action anticipation and motor resonance in elite basketball players. \emph{Nature Neuroscience}, \emph{11}(9), 1109--1116. \url{https://doi.org/10.1038/nn.2182}

\leavevmode\vadjust pre{\hypertarget{ref-akkermans_2019}{}}%
Akkermans, J., Schapiro, R., Müllensiefen, D., Jakubowski, K., Shanahan, D., Baker, D., \ldots{} Frieler, K. (2019). Decoding emotions in expressive music performances: {A} multi-lab replication and extension study. \emph{Cognition and Emotion}, \emph{33}(6), 1099--1118. \url{https://doi.org/10.1080/02699931.2018.1541312}

\leavevmode\vadjust pre{\hypertarget{ref-battcock_2021}{}}%
Battcock, A., \& Schutz, M. (2021). Emotion and expertise: How listeners with formal music training use cues to perceive emotion. \emph{Psychological Research}. \url{https://doi.org/10.1007/s00426-020-01467-1}

\leavevmode\vadjust pre{\hypertarget{ref-brand_2002}{}}%
Brand, R. J., Baldwin, D. A., \& Ashburn, L. A. (2002). Evidence for {``motionese''}: Modifications in mothers' infant-directed action. \emph{Developmental Science}, \emph{5}(1), 72--83. \url{https://doi.org/10.1111/1467-7687.00211}

\leavevmode\vadjust pre{\hypertarget{ref-bresin_2000}{}}%
Bresin, R., \& Battel, G. U. (2000). Articulation {Strategies} in {Expressive Piano Performance Analysis} of {Legato}, {Staccato}, and {Repeated Notes} in {Performances} of the {Andante Movement} of {Mozart}'s {Sonata} in {G Major} ({K} 545). \emph{Journal of New Music Research}, \emph{29}(3), 211--224. \url{https://doi.org/10.1076/jnmr.29.3.211.3092}

\leavevmode\vadjust pre{\hypertarget{ref-csibra_2009}{}}%
Csibra, G., \& Gergely, G. (2009). Natural pedagogy. \emph{Trends in Cognitive Sciences}, \emph{13}(4), 148--153. \url{https://doi.org/10.1016/j.tics.2009.01.005}

\leavevmode\vadjust pre{\hypertarget{ref-gabrielsson_1996}{}}%
Gabrielsson, A., \& Juslin, P. N. (1996). Emotional {Expression} in {Music Performance}: {Between} the {Performer}'s {Intention} and the {Listener}'s {Experience}. \emph{Psychology of Music}, \emph{24}(1), 68--91. \url{https://doi.org/10.1177/0305735696241007}

\leavevmode\vadjust pre{\hypertarget{ref-gweon_2020}{}}%
Gweon, H. (2020). The role of communication in acquisition, curation, and transmission of culture. \emph{Behavioral and Brain Sciences}, \emph{43}. \url{https://doi.org/10.1017/S0140525X19002863}

\leavevmode\vadjust pre{\hypertarget{ref-kuhl_2004}{}}%
Kuhl, P. K. (2004). Early language acquisition: Cracking the speech code. \emph{Nature Reviews Neuroscience}, \emph{5}(11), 831--843. \url{https://doi.org/10.1038/nrn1533}

\leavevmode\vadjust pre{\hypertarget{ref-lima_2011}{}}%
Lima, C. F., \& Castro, S. L. (2011). Speaking to the trained ear: Musical expertise enhances the recognition of emotions in speech prosody. \emph{Emotion}, \emph{11}(5), 1021--1031. \url{https://doi.org/10.1037/a0024521}

\leavevmode\vadjust pre{\hypertarget{ref-ludecke_2021}{}}%
Lüdecke, D., Ben-Shachar, M. S., Patil, I., Waggoner, P., \& Makowski, D. (2021). Performance: {An R Package} for {Assessment}, {Comparison} and {Testing} of {Statistical Models}. \emph{Journal of Open Source Software}, \emph{6}(60), 3139. \url{https://doi.org/10.21105/joss.03139}

\leavevmode\vadjust pre{\hypertarget{ref-mcellin_2017}{}}%
McEllin, L., Knoblich, G., \& Sebanz, N. (2017). Distinct kinematic markers of demonstration and joint action coordination? {Evidence} from virtual xylophone playing. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{44}(6), 885. \url{https://doi.org/10.1037/xhp0000505}

\leavevmode\vadjust pre{\hypertarget{ref-mcellin_2018}{}}%
McEllin, L., Sebanz, N., \& Knoblich, G. (2018). Identifying others' informative intentions from movement kinematics. \emph{Cognition}, \emph{180}, 246--258. \url{https://doi.org/10.1016/j.cognition.2018.08.001}

\leavevmode\vadjust pre{\hypertarget{ref-repp_2004}{}}%
Repp, B. H., \& Knoblich, G. (2004). Perceiving {Action Identity}: {How Pianists Recognize Their Own Performances}. \emph{Psychol Sci}, \emph{15}(9), 604--609. \url{https://doi.org/10.1111/j.0956-7976.2004.00727.x}

\leavevmode\vadjust pre{\hypertarget{ref-sebanz_2009}{}}%
Sebanz, N., \& Shiffrar, M. (2009). Detecting deception in a bluffing body: {The} role of expertise. \emph{Psychonomic Bulletin and Review}, \emph{16}(1), 170--175. \url{https://doi.org/10.3758/PBR.16.1.170}

\leavevmode\vadjust pre{\hypertarget{ref-tennie_2009}{}}%
Tennie, C., Call, J., \& Tomasello, M. (2009). Ratcheting up the ratchet: On the evolution of cumulative culture. \emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{364}(1528), 2405--2415. \url{https://doi.org/10.1098/rstb.2009.0052}

\leavevmode\vadjust pre{\hypertarget{ref-tomasello_1993}{}}%
Tomasello, M., Kruger, A. C., \& Ratner, H. H. (1993). Cultural learning. \emph{Behavioral and Brain Sciences}, \emph{16}(3), 495--511. \url{https://doi.org/10.1017/S0140525X0003123X}

\leavevmode\vadjust pre{\hypertarget{ref-uther_2007}{}}%
Uther, M., Knoll, M. A., \& Burnham, D. (2007). Do you speak {E-NG-L-I-SH}? {A} comparison of foreigner- and infant-directed speech. \emph{Speech Communication}, \emph{49}(1), 2--7. \url{https://doi.org/10.1016/j.specom.2006.10.003}

\leavevmode\vadjust pre{\hypertarget{ref-veissiere_2020}{}}%
Veissière, S. P. L., Constant, A., Ramstead, M. J. D., Friston, K. J., \& Kirmayer, L. J. (2020). Thinking through other minds: {A} variational approach to cognition and culture. \emph{Behavioral and Brain Sciences}, \emph{43}. \url{https://doi.org/10.1017/S0140525X19001213}

\end{CSLReferences}

\endgroup

\end{document}

### 2022-01-27 experiment-1/analysis/prereg_analysis/prereg_analysis.R

@@ -1,4 +1,4 @@
-## ----packages, include = FALSE------------------------------
+## ----packages, include = FALSE------------------------------------
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
 # midi
@@ -10,7 +10,7 @@ if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
 if (!require("performance")) {install.packages("performance"); require("performance")}
 
 
-## ----read, include = FALSE----------------------------------
+## ----read, include = FALSE----------------------------------------
 # read files and combine them
 data_ls <- list.files("../../data", pattern = "csv")
 combined <- lapply(data_ls, function(f){
@@ -40,7 +40,7 @@ all <- data[expMode == "experiment", .(N = .N, Sum = sum(Correct), Percent = (su
 all[order(subjectNumber, Condition, Skill)]
 
 
-## ----acc, echo = FALSE--------------------------------------
+## ----acc, echo = FALSE--------------------------------------------
 # individual
 ind_data <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber)]
 ind_data <- ind_data[order(subjectNumber)]
@@ -50,18 +50,18 @@ subset <- ind_data[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (m
 subset
 
 
-## ----plot, echo = FALSE-------------------------------------
+## ----plot, echo = FALSE-------------------------------------------
 ggboxplot(ind_data, x = "N", y = "Percent", add = "dotplot", xlab = FALSE) + ylab("Correct %") + theme(axis.text.x = element_blank())
 
 
-## ----t-test, echo = FALSE-----------------------------------
+## ----t-test, echo = FALSE-----------------------------------------
 # normality check
 shapiro.test(ind_data$Percent)
 
 t.test(ind_data$Percent, mu = 50, alternative = "two.sided")
 
 
-## ----plot2, echo = FALSE------------------------------------
+## ----plot2, echo = FALSE------------------------------------------
 ind_data_ad <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Skill)]
 ind_data_ad <- ind_data_ad[order(subjectNumber, Skill)]
 
[…]

### 2022-01-27 experiment-2/analysis/analysis.R

@@ -1,4 +1,4 @@
-## ----setup, include = FALSE---------------------------------
+## ----setup, include = FALSE---------------------------------------
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
 # midi
@@ -11,7 +11,7 @@ if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
 if (!require("performance")) {install.packages("performance"); require("performance")}
 
 
-## ----read, include = FALSE----------------------------------
+## ----read, include = FALSE----------------------------------------
 # read files and combine them
 data_ls <- list.files("../data", pattern = "csv")
 combined <- lapply(data_ls, function(f){
@@ -33,7 +33,7 @@ data[grepl("a_", midFile)]$Skill <- "articulation"
 data[grepl("d_", midFile)]$Skill <- "dynamics"
 
 
-## ----teaching, echo = FALSE---------------------------------
+## ----teaching, echo = FALSE---------------------------------------
 data$Teaching <- 0
 data[rating == "Yes"]$Teaching <- 1
 
@@ -47,7 +47,7 @@ all <- all[order(MidFile)]
 all
 
 
-## ----midi, include = FALSE----------------------------------
+## ----midi, include = FALSE----------------------------------------
 # create a list of data file names
 lf <- list.files("../experiment/mid/", pattern = "mid")
 
@@ -95,7 +95,7 @@ change_1 <- c(5, 17, 47)
 change_2 <- c(8, 20, 39)
 
 
-## ----ioi, include = FALSE-----------------------------------
+## ----ioi, include = FALSE-----------------------------------------
 data_onset <- data[event == "Note On"]
 data_offset <- data[event == "Note Off"]
 
@@ -142,7 +142,7 @@ for (number in change_2){
 }
 
 
-## ----ioi-all, echo = FALSE----------------------------------
+## ----ioi-all, echo = FALSE----------------------------------------
 rating <- all # rating data
 
 ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill)]
[…]

### 2022-01-27 experiment-2/analysis/questionnaire.R

@@ -1,4 +1,4 @@
-## ----setup, include = FALSE----------------------------------
+## ----setup, include = FALSE---------------------------------------
 # packages
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
@@ -6,7 +6,7 @@ if (!require("data.table")) {install.packages("data.table"); require("data.table
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
 
 
-## ----read, echo = FALSE--------------------------------------
+## ----read, echo = FALSE-------------------------------------------
 dt <- fread("questionnaire.csv", header = T, sep = ",", dec = ".", na.string = "NA")
 
 # change some colnames
@@ -24,10 +24,10 @@ dt_included <- dt[SubNr != 4]
 print(dt_included)
 
 
-## ----1, echo = FALSE-----------------------------------------
+## ----1, echo = FALSE----------------------------------------------
 data.table("Answer" = dt_included$`Have you noticed anything special regarding the tasks in the experiment? If any, please describe below.`)
 
 
-## ----export, include = FALSE---------------------------------
+## ----export, include = FALSE--------------------------------------
 knitr::purl("questionnaire.Rmd")
 

### 2022-01-28 paper/manuscript.Rmd
update methods
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 The experiment was programmed in Python 3.8.2 using the PsychoPy library (2020.2.4; https://www.psychopy.org/) on a Mac Book Pro with Mac OS X Catalina 10.15.6.
-Stimuli (MIDI data) were played using the Mido library (1.2.9; https://mido.readthedocs.io/en/latest/) on a Max/MSP patcher (8.1.7; https://cycling74.com/products/max).
+Stimuli were played using the Mido library (1.2.9; https://mido.readthedocs.io/en/latest/) on a Max/MSP patcher (8.1.7; https://cycling74.com/products/max).
 During the experiment, participants listened to the stimuli via headphones (Audio-Technica ATH-M50X).
@@
 ## Stimuli
-Piano recordings were used as stimuli.
-The stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files.
-One piece of music was selected as a base piece and was taken from "A Dozen a Day - Play with Ease in Many Keys" by Edna-Mae Burnam and modified for the experiment.
-The piece was performed with a musical expressive technique of either articulation (*Figure \ref{fig:stim1}*, A) or dynamics (*Figure \ref{fig:stim1}*, B) by multiple pianists.
-Therefore, all stimuli had the same musical sequence but had subtle differences in terms of musical expressions (e.g., timing, articulation and dynamics).
+We selected stimuli from our previous experiments (Tominaga et al., *submitted*; Experiment 1).
+Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files.
+Multiple pianists played one piece of music with a musical expressive techniques of either articulation (*Figure \ref{fig:stim1}*, A) or dynamics (*Figure \ref{fig:stim1}*, B).
 Articulation refers to the smoothness of sound, which is comprised of legato and staccato.
@@
 Forte indicates loud sound while piano indicates soft sound.
-The stimuli were performed around 80 quarter-beats per minute (i.e., around 188 ms for 16th-note IOIs).
+The piece was taken from "A Dozen a Day - Play with Ease in Many Keys" by Edna-Mae Burnam and modified for the experiment.
+The stimuli were performed around 80 quarter-beats per minute.
 
-Ninety-six stimuli (MIDI recordings) were obtained from our previous experiments (Tominaga et al., *submitted*).
-In the previous experiments, we asked expert pianists to perform one piece of music with a musical expressive technique of either articulation (*Figure \ref{fig:stim1}*, A) or dynamics (*Figure \ref{fig:stim1}*, B).
-There were two experimental conditions.
+In Tominaga et al., (*submitted*), participants were asked to perform the piece with either articulation or dynamics in two different conditions.
 In the teaching condition, participants were instructed to perform the piece with the designated expressive technique as if they were teaching it to students (e.g., in a lesson).
 In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert).
-There were 453 valid performances (i.e., performances without any pitch error) for the teaching condition and 436 valid performances for the performing conditions.
-We randomly chose 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition.
-It is important to note that the recordings from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments since we randomly sampled the recordings.
+In total, we obtained 453 valid performances (i.e., performances without any pitch error) from the teaching condition and 436 valid performances from the performing condition.
+
+For the current experiment, 96 performances were chosen from the valid performances in Tominaga et al.
+(*submitted*).
+We randomly sampled 24 articulation performances and 24 dynamics performances from the teaching condition as well as 24 articulation performances and 24 dynamics performances from the performing condition.
+It is important to note that the performances from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments since we randomly sampled the recordings.
 
@@
 Upon arrival, participants read information sheet about the experiment and gave informed consent prior to participation.
-In the experiment, all instructions were displayed on a computer screen and an experimenter also explained the procedure.
-Participants were instructed that they were going to listen to piano recordings and would be asked if each recording was performed as if a pianist were teaching it to students (e.g., in a lesson / teaching) or as if a pianist were performing it to an audience (e.g., in a concert / performing).
-They responded by pressing either a yes (teaching / left arrow key) or no (performing / right arrow key) button.
-While listening to each stimulus, sheet music, which corresponded to the stimulus, was shown on a monitor in front of the participants.
-After making a judgment, the next recording was played (*Figure \ref{fig:procedure1}*).
+In the experiment, all instructions were displayed on a computer screen in front of the participants and an experimenter also explained the procedure.
+Participants were instructed that they were going to listen to piano recordings with musical expression (either articulation or dynamics), which were either produced as if a pianist were teaching the expression to students (e.g., in a lesson; teaching) or as if a pianist were performing it to an audience (e.g., in a concert; performing).
+In each trial, participants listened to one recording and were asked whether the recording was produced for teaching purposes or not.
+Participants responded by pressing either a yes (for teaching; left arrow key) or no (for performing; right arrow key) button.
+While listening to each recording, sheet music, which corresponded to the recording, was shown on the screen in front of the participants (*Figure \ref{fig:procedure1}*).
 
-There were two blocks and each block only contained recordings with one musical expressive technique of either articulation or dynamics.
+There were two blocks and each block only included recordings with one musical expressive technique of either articulation or dynamics.
 Each block consisted of 4 practice trials and 48 experimental trials.
-In each trial, participants listened to one recording only once.
-After listening the recording, they were asked to judge by pressing either the left arrow key (i.e., teaching) or the right arrow key (i.e., performing).
 Each recording was evaluated only once in the experiment.

### 2022-01-28 paper/manuscript.tex
update methods
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-The experiment was programmed in Python 3.8.2 using the PsychoPy library (2020.2.4; \url{https://www.psychopy.org/}) on a Mac Book Pro with Mac OS X 10.15.6.
-Stimuli (MIDI data) were played using the Mido library (1.2.9; \url{https://mido.readthedocs.io/en/latest/}) on a Max/MSP patcher (8.1.7; \url{https://cycling74.com/products/max}).
+The experiment was programmed in Python 3.8.2 using the PsychoPy library (2020.2.4; \url{https://www.psychopy.org/}) on a Mac Book Pro with Mac OS X Catalina 10.15.6.
+Stimuli were played using the Mido library (1.2.9; \url{https://mido.readthedocs.io/en/latest/}) on a Max/MSP patcher (8.1.7; \url{https://cycling74.com/products/max}).
 During the experiment, participants listened to the stimuli via headphones (Audio-Technica ATH-M50X).
@@
 
-Piano recordings obtained as MIDI data were used as Stimuli.
+We selected stimuli from our previous experiments (Tominaga et al., \emph{submitted}; Experiment 1).
 Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files.
-One piece of music was selected as a base piece, which was performed with a musical expressive technique of either articulation (\emph{Figure \ref{fig:stim1}}, A) or dynamics (\emph{Figure \ref{fig:stim1}}, B).
-The piece was taken from ``A Dozen a Day - Play with Ease in Many Keys'' by Edna-Mae Burnam and modified for the experiment.
-Therefore, all stimuli had the same musical sequence but had subtle differences in terms of musical expressions (e.g., timing, articulation and dynamics).
+Multiple pianists played one piece of music with a musical expressive techniques of either articulation (\emph{Figure \ref{fig:stim1}}, A) or dynamics (\emph{Figure \ref{fig:stim1}}, B).
 Articulation refers to the smoothness of sound, which is comprised of legato and staccato.
@@
 Forte indicates loud sound while piano indicates soft sound.
-The stimuli were performed around 80 quarter-beats per minute (i.e., around 188 ms for 16th-note IOIs).
+The piece was taken from ``A Dozen a Day - Play with Ease in Many Keys'' by Edna-Mae Burnam and modified for the experiment.
+The stimuli were performed around 80 quarter-beats per minute.
 
-96 stimuli (MIDI recordings) were obtained from our previous experiments (Tominaga et al., \emph{submitted}).
-In the previous experiments, we asked expert pianists to perform one piece of music with a musical expressive technique of either articulation (\emph{Figure \ref{fig:stim1}}, A) or dynamics (\emph{Figure \ref{fig:stim1}}, B).
-There were two experimental conditions.
+In Tominaga et al., (\emph{submitted}), participants were asked to perform the piece with either articulation or dynamics in two different conditions.
 In the teaching condition, participants were instructed to perform the piece with the designated expressive technique as if they were teaching it to students (e.g., in a lesson).
 In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert).
-There were 453 valid performances (i.e., performances without any pitch error) for the teaching condition and 436 valid performances for the performing conditions.
-We randomly chose 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition.
-It is important to note that the recordings from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments since we randomly sampled the recordings.
+In total, we obtained 453 valid performances (i.e., performances without any pitch error) from the teaching condition and 436 valid performances from the performing condition.
+
+For the current experiment, 96 performances were chosen from the valid performances in Tominaga et al.~(\emph{submitted}).
+We randomly sampled 24 articulation performances and 24 dynamics performances from the teaching condition as well as 24 articulation performances and 24 dynamics performances from the performing condition.
+It is important to note that the performances from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments since we randomly sampled the recordings.
 
@@
 Upon arrival, participants read information sheet about the experiment and gave informed consent prior to participation.
-In the experiment, all instructions were displayed on a computer screen and an experimenter also explained the procedure.
-Participants were instructed that they were going to listen to piano recordings and would be asked if each recording was performed as if a pianist were teaching it to students (e.g., in a lesson / teaching) or as if a pianist were performing it to an audience (e.g., in a concert / performing).
-They responded by pressing either a yes (teaching / left arrow key) or no (performing / right arrow key) button.
-While listening to each stimulus, sheet music, which corresponded to the stimulus, was shown on a monitor in front of the participants.
-After making a judgment, the next recording was played (\emph{Figure \ref{fig:procedure1}}).
+In the experiment, all instructions were displayed on a computer screen in front of the participants and an experimenter also explained the procedure.
+Participants were instructed that they were going to listen to piano recordings with musical expression (either articulation or dynamics), which were either produced as if a pianist were teaching the expression to students (e.g., in a lesson; teaching) or as if a pianist were performing it to an audience (e.g., in a concert; performing).
+In each trial, participants listened to one recording and were asked whether the recording was produced for teaching purposes or not.
+Participants responded by pressing either a yes (for teaching; left arrow key) or no (for performing; right arrow key) button.
+While listening to each recording, sheet music, which corresponded to the recording, was shown on the screen in front of the participants (\emph{Figure \ref{fig:procedure1}}).
 
-There were two blocks and each block only contained recordings with one musical expressive technique of either articulation or dynamics.
+There were two blocks and each block only included recordings with one musical expressive technique of either articulation or dynamics.
 Each block consisted of 4 practice trials and 48 experimental trials.
-In each trial, participants listened to one recording only once.
-After listening the recording, they were asked to judge by pressing either the left arrow key (i.e., teaching) or the right arrow key (i.e., performing).
 Each recording was evaluated only once in the experiment.

### 2022-01-29 experiment-1/analysis/analysis.Rmd
update analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 # read files and combine them
-data_ls <- list.files("../data", pattern = "csv")
-combined <- lapply(data_ls, function(f){
+data_lf <- list.files("../data", pattern = "csv")
+combined <- lapply(data_lf, function(f){
   fread(paste("../data/", f, sep = ""), sep = ",")
@@
 # all
-all <- individual[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
+all <- individual[, .(N = .N, Sum = sum(Sum), Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
 all <- all[order(MidFile)]
@@
 # create a list of data file names
-lf <- list.files("../experiment/mid/", pattern = "mid")
+midi_lf <- list.files("../experiment/mid/", pattern = "mid")
 
 # combine data
-all_data <- data.table()
-for (file in lf){
+all_midi <- data.table()
+for (file in midi_lf){
    current <- readMidi(paste("../experiment/mid/", file, sep = ""))
    current$MidFile <- gsub(".mid", "", file)
-   all_data <- rbind(all_data, current)
+   all_midi <- rbind(all_midi, current)
 }
 
-data <- all_data[event == "Note On" | event == "Note Off"]
-data$NoteNr <- rep(1:134, nrow(data)/134)
-data$channel <- NULL
-data$parameterMetaSystem <- NULL
-data$track <- NULL
-data$type <- NULL
-data$time2 <- (data$time/960)*1000 # deltatime to time (ms)
+midi <- all_midi[event == "Note On" | event == "Note Off"]
+midi$NoteNr <- rep(1:134, nrow(midi)/134)
+midi$channel <- NULL
+midi$parameterMetaSystem <- NULL
+midi$track <- NULL
+midi$type <- NULL
+midi$time2 <- (midi$time/960)*1000 # deltatime to time (ms)
 
 # labelling
-colnames(data)[c(3,4)] <- c("Pitch", "Velocity") # time event also change
-data$Condition <- "NA"
-data$Skill <- "NA"
-data[grepl("_t_", MidFile)]$Condition <- "teaching"
-data[grepl("_p_", MidFile)]$Condition <- "performing"
-data[grepl("a_", MidFile)]$Skill <- "articulation"
-data[grepl("d_", MidFile)]$Skill <- "dynamics"
+colnames(midi)[c(3,4)] <- c("Pitch", "Velocity") # time event also change
+midi$Condition <- "NA"
+midi$Skill <- "NA"
+midi[grepl("_t_", MidFile)]$Condition <- "teaching"
+midi[grepl("_p_", MidFile)]$Condition <- "performing"
+midi[grepl("a_", MidFile)]$Skill <- "articulation"
+midi[grepl("d_", MidFile)]$Skill <- "dynamics"
 
 # define subcomponents
-# For intervals
+# for intervals
 ls_legato <- list(c(1:7), c(17:23), c(42:48), c(58:64))
@@
 
-# For each note (velocity only)
+# for each note (velocity only)
 ls_legato_2 <- list(c(1:8), c(17:24), c(42:49), c(58:65))
@@
 
-# Define Skill Change (LtoS, FtoP)
+# define Skill Change (LtoS, FtoP)
 change_1 <- c(8, 24, 49)
-# Define Skill Change (StoL, PtoF)
+# define Skill Change (StoL, PtoF)
 change_2 <- c(16, 41, 57)
@@
 ```{r ioi, include = FALSE}
-data_onset <- data[event == "Note On"]
-data_offset <- data[event == "Note Off"]
+data_onset <- midi[event == "Note On"]
+data_offset <- midi[event == "Note Off"]
 
@@
 # normality check
-shapiro.test(ioi[Skill == "articulation"]$Teaching)
-shapiro.test(ioi[Skill == "articulation"]$Mean)
+ioi_art_norm_teaching <- shapiro.test(ioi[Skill == "articulation"]$Teaching)
+ioi_art_norm_judge <- shapiro.test(ioi[Skill == "articulation"]$Mean)
+qqnorm(ioi[Skill == "articulation"]$Teaching)
+qqline(ioi[Skill == "articulation"]$Teaching)
+ioi_art_norm_teaching
+
+qqnorm(ioi[Skill == "articulation"]$Mean)
+qqline(ioi[Skill == "articulation"]$Mean)
+ioi_art_norm_judge
 
@@
 # normality check
-shapiro.test(ioi[Skill == "dynamics"]$Teaching)
-shapiro.test(ioi[Skill == "dynamics"]$Mean)
+ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
+ioi_dyn_norm_judge <- shapiro.test(ioi[Skill == "dynamics"]$Mean)
+
+qqnorm(ioi[Skill == "dynamics"]$Teaching)
+qqline(ioi[Skill == "dynamics"]$Teaching)
+ioi_dyn_norm_teaching
+
+qqnorm(ioi[Skill == "dynamics"]$Mean)
+qqline(ioi[Skill == "dynamics"]$Mean)
+ioi_dyn_norm_judge
 
@@
 # normality check
-shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
-shapiro.test(ioi_tra[Skill == "articulation"]$Mean)
+ioi_art_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
+
+ioi_art_tra_norm_judge <- shapiro.test(ioi_tra[Skill == "articulation"]$Mean)
+
+qqnorm(ioi_tra[Skill == "articulation"]$Teaching)
+qqline(ioi_tra[Skill == "articulation"]$Teaching)
+ioi_art_tra_norm_teaching
+
+qqnorm(ioi_tra[Skill == "articulation"]$Mean)
+qqline(ioi_tra[Skill == "articulation"]$Mean)
+ioi_art_tra_norm_judge
 
@@
 # normality check
-shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
-shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)
+ioi_dyn_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
+ioi_dyn_tra_norm_judge <- shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)
+
+qqnorm(ioi_tra[Skill == "dynamics"]$Teaching)
+qqline(ioi_tra[Skill == "dynamics"]$Teaching)
+ioi_dyn_tra_norm_teaching
+
+qqnorm(ioi_tra[Skill == "dynamics"]$Mean)
+qqline(ioi_tra[Skill == "dynamics"]$Mean)
+ioi_dyn_tra_norm_judge
 
@@
 # normality check
-shapiro.test(cv[Skill == "articulation"]$Teaching)
-shapiro.test(cv[Skill == "articulation"]$CV)
+cv_art_norm_teaching <- shapiro.test(cv[Skill == "articulation"]$Teaching)
+cv_art_norm_judge <- shapiro.test(cv[Skill == "articulation"]$CV)
 

### 2022-01-30 experiment-1/analysis/analysis.Rmd
update analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 }
-
 # Forte
@@
 }
-
 # assign Subcomponent Change
@@
 ioi_art_norm_judge <- shapiro.test(ioi[Skill == "articulation"]$Mean)
+
 qqnorm(ioi[Skill == "articulation"]$Teaching)
@@
 ioi_art_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
-
 ioi_art_tra_norm_judge <- shapiro.test(ioi_tra[Skill == "articulation"]$Mean)
@@
 
+qqnorm(cv[Skill == "articulation"]$Teaching)
+qqline(cv[Skill == "articulation"]$Teaching)
+cv_art_norm_teaching
+
+qqnorm(cv[Skill == "articulation"]$CV)
+qqline(cv[Skill == "articulation"]$CV)
+cv_art_norm_judge
+
 cor.test(cv[Skill == "articulation"]$Teaching, cv[Skill == "articulation"]$CV)
+
+cor.test(cv[Skill == "articulation"]$Teaching, cv[Skill == "articulation"]$CV, method = "spearman", exact = FALSE)
 ```
@@
 # normality check
-shapiro.test(cv[Skill == "dynamics"]$Teaching)
-shapiro.test(cv[Skill == "dynamics"]$CV)
+cv_dyn_norm_teaching <- shapiro.test(cv[Skill == "dynamics"]$Teaching)
+cv_dyn_norm_judge <- shapiro.test(cv[Skill == "dynamics"]$CV)
+
+qqnorm(cv[Skill == "dynamics"]$Teaching)
+qqline(cv[Skill == "dynamics"]$Teaching)
+cv_dyn_norm_teaching
+
+qqnorm(cv[Skill == "dynamics"]$CV)
+qqline(cv[Skill == "dynamics"]$CV)
+cv_dyn_norm_judge
 
 cor.test(cv[Skill == "dynamics"]$Teaching, cv[Skill == "dynamics"]$CV)
+
+cor.test(cv[Skill == "dynamics"]$Teaching, cv[Skill == "dynamics"]$CV, method = "spearman", exact = FALSE)
 ```
@@
 # normality check
-shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
-shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)
+kot_leg_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
+kot_leg_norm_judge <- shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)
+
+qqnorm(kot_all[Subcomponent == "Legato"]$Teaching)
+qqline(kot_all[Subcomponent == "Legato"]$Teaching)
+kot_leg_norm_teaching
+
+qqnorm(kot_all[Subcomponent == "Legato"]$Mean)
+qqline(kot_all[Subcomponent == "Legato"]$Mean)
+kot_leg_norm_judge
 
@@
 # normality check
-shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
-shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)
+kot_sta_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
+kot_sta_norm_judge <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)
+
+qqnorm(kot_all[Subcomponent == "Staccato"]$Teaching)
+qqline(kot_all[Subcomponent == "Staccato"]$Teaching)
+kot_sta_norm_teaching
+
+qqnorm(kot_all[Subcomponent == "Staccato"]$Mean)
+qqline(kot_all[Subcomponent == "Staccato"]$Mean)
+kot_sta_norm_judge
 
@@
 # normality check
-shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
-shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)
+kot_for_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
+kot_for_norm_judge <- shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)
+
+qqnorm(kot_all[Subcomponent == "Forte"]$Teaching)
+qqline(kot_all[Subcomponent == "Forte"]$Teaching)
+kot_for_norm_teaching
+
+qqnorm(kot_all[Subcomponent == "Forte"]$Mean)
+qqline(kot_all[Subcomponent == "Forte"]$Mean)
+kot_for_norm_judge
 
@@
 # normality check
-shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
-shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)
+kot_pia_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
+kot_pia_norm_judge <- shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)
+
+qqnorm(kot_all[Subcomponent == "Piano"]$Teaching)
+qqline(kot_all[Subcomponent == "Piano"]$Teaching)
+kot_pia_norm_teaching
+
+qqnorm(kot_all[Subcomponent == "Piano"]$Mean)
+qqline(kot_all[Subcomponent == "Piano"]$Mean)
+kot_pia_norm_judge
 
@@
 dt_vel$Note <- rep(1:67, nrow(dt_vel)/67)
+
 # assign Subcomponents
-# for each note
 dt_vel$Subcomponent <- "NA"
@@
 # normality check
-shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
-shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)
+vel_for_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
+vel_for_norm_judge <- shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)
+
+qqnorm(vel_all[Subcomponent == "Forte"]$Teaching)
+qqline(vel_all[Subcomponent == "Forte"]$Teaching)
+vel_for_norm_teaching
+
+qqnorm(vel_all[Subcomponent == "Forte"]$Mean)
+qqline(vel_all[Subcomponent == "Forte"]$Mean)
+vel_for_norm_judge
 
@@
 # normality check
-shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
-shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)
+vel_pia_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
+vel_pia_norm_judge <- shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)
+
+qqnorm(vel_all[Subcomponent == "Piano"]$Teaching)
+qqline(vel_all[Subcomponent == "Piano"]$Teaching)
+vel_pia_norm_teaching
+
+qqnorm(vel_all[Subcomponent == "Piano"]$Mean)
+qqline(vel_all[Subcomponent == "Piano"]$Mean)
+vel_pia_norm_judge
 
@@
 # normality check
-shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
-shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)
+vel_leg_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
+vel_leg_norm_judge <- shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)
+
+qqnorm(vel_all[Subcomponent == "Legato"]$Teaching)
+qqline(vel_all[Subcomponent == "Legato"]$Teaching)
+vel_leg_norm_teaching
+
+qqnorm(vel_all[Subcomponent == "Legato"]$Mean)
+qqline(vel_all[Subcomponent == "Legato"]$Mean)
+vel_leg_norm_judge
 
@@
 # normality check
-shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
-shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)
+vel_sta_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
+vel_sta_norm_judge <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)
+
+qqnorm(vel_all[Subcomponent == "Staccato"]$Teaching)
+qqline(vel_all[Subcomponent == "Staccato"]$Teaching)
+vel_sta_norm_teaching
+
+qqnorm(vel_all[Subcomponent == "Staccato"]$Mean)
+qqline(vel_all[Subcomponent == "Staccato"]$Mean)
+vel_sta_norm_judge
 
@@
 dt_vel_diff <- data_onset[NoteNr != 1]
-# assign Interval
 dt_vel_diff$Interval <- rep(1:66, nrow(dt_vel_diff)/66)
 
-# for intervals
+# assign Subcomponents
 dt_vel_diff$Subcomponent <- "NA"
@@
 }
-# Assign Skill Change
+
+# assign Subcomponent Change
 for (i in change_1){
@@
 # normality check
-shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
-shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)
+vel_diff_ftop_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
+vel_diff_ftop_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)
+
+qqnorm(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
+qqline(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
+vel_diff_ftop_norm_teaching
+
+qqnorm(vel_diff_all[Subcomponent == "FtoP"]$Mean)
+qqline(vel_diff_all[Subcomponent == "FtoP"]$Mean)
+vel_diff_ftop_norm_judge
 
@@
 # normality check
-shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
-shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)
+vel_diff_ptof_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
+vel_diff_ptof_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)
+
+qqnorm(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
+qqline(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
+vel_diff_ptof_norm_teaching
+
+qqnorm(vel_diff_all[Subcomponent == "PtoF"]$Mean)
+qqline(vel_diff_all[Subcomponent == "PtoF"]$Mean)
+vel_diff_ptof_norm_judge
 
@@
 # normality check
-shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
-shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)
+vel_diff_ltos_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
+vel_diff_ltos_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)
+
+qqnorm(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
+qqline(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
+vel_diff_ltos_norm_teaching
+
+qqnorm(vel_diff_all[Subcomponent == "LtoS"]$Mean)
+qqline(vel_diff_all[Subcomponent == "LtoS"]$Mean)
+vel_diff_ltos_norm_judge
 
@@
 # normality check
-shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Teaching)
-shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Mean)
+vel_diff_stol_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Teaching)
+vel_diff_stol_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Mean)
+
+qqnorm(vel_diff_all[Subcomponent == "StoL"]$Teaching)
+qqline(vel_diff_all[Subcomponent == "StoL"]$Teaching)
+vel_diff_stol_norm_teaching
+
+qqnorm(vel_diff_all[Subcomponent == "StoL"]$Mean)
+qqline(vel_diff_all[Subcomponent == "StoL"]$Mean)
+vel_diff_stol_norm_judge
 

### 2022-01-31 experiment-1/analysis/analysis.Rmd
update analysis (add qqplots, corrplots)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques (expressions) separately. The order of the blocks was counterbalanced across participants.
-- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented across participants.
+- 2 blocks (articulation / dynamics): each block only contained performances with either of articulation or dynamics. The order of the blocks was counterbalanced across participants.
+- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented within the block.
 
@@
 
-3. Correct answers would be 1) participants pressed "YES" when they listened to teaching performances or 2) participants pressed "NO" when they listened to performing performances.
+- For additional analysis
+(3. Correct answers would be 1) participants pressed "YES" when they listened to teaching performances or 2) participants pressed "NO" when they listened to performing performances.)
 
@@
 
-```{r setup, include = FALSE}
+```{r set-up, include = FALSE}
+options(knitr.duplicate.label = "allow")
+
 # data manipulation
@@
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
+if (!require("corrplot")) {install.packages("corrplot"); require("corrplot")}
 # stats
@@
 ```
+
 ## Articulation (***)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ## Dynamics (**)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ## Articulation (***)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ## Articulation (n.s.)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ## Dynamics (n.s.)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ## Legato (**)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ## Staccato (***)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ## Forte (n.s.)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ## Piano (n.s.)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ## Forte (***)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ```
+
 ## Legato (n.s.)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ## Staccato (n.s.)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ## Forte to Piano (***)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ## Piano to Forte (***)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ```
+
 ## Legato to Staccato (n.s.)
-```{r, echo = FALSE}
+```{r, echo = TRUE}
 # normality check
@@
 ## Legato (**)
+### Estimate
+```{r partial-plot-leg, echo = FALSE}
+# plot
+corrplot.mixed(pcor(partial[Subcomponent == "Legato", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
+```
+
 ```{r kot-partial-leg, echo = TRUE}
@@
 ## Staccato (*)
+### Estimate
+```{r partial-plot-sta, echo = FALSE}
+# plot
+corrplot.mixed(pcor(partial[Subcomponent == "Staccato", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
+```
+
 ```{r kot-partial-sta, echo = TRUE}
@@
 ## Forte (*)
+### Estimate
+```{r partial-plot-for, echo = FALSE}
+# plot
+corrplot.mixed(pcor(partial[Subcomponent == "Forte", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
+```
+
 ```{r vel-partial-for, echo = TRUE}
@@
 ## Piano (n.s.)
+### Estimate
+```{r partial-plot-pia, echo = FALSE}
+# plot
+corrplot.mixed(pcor(partial[Subcomponent == "Piano", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
+```
+
 ```{r vel-partial-pia, echo = TRUE}
@@
 ## Forte to Piano (n.s.)
+### Estimate
+```{r partial-plot-ftop, echo = FALSE}
+# plot
+corrplot.mixed(pcor(partial[Subcomponent2 == "FtoP", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
+```
+
 ```{r vel-diff-partial-ftop, echo = TRUE}
@@
 ## Piano to Forte (***)
+### Estimate
+```{r partial-plot-ptof, echo = FALSE}
+# plot
+corrplot.mixed(pcor(partial[Subcomponent2 == "PtoF", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
+```
+
 ```{r vel-diff-partial-ptof, echo = TRUE}

### 2022-01-31 experiment-1/analysis/analysis.R

@@ -1,19 +1,22 @@
-## ----setup, include = FALSE---------------------------------
+## ----set-up, include = FALSE--------------------------------------------------
+options(knitr.duplicate.label = "allow")
+
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
 # midi
 if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
 # plot
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
+if (!require("corrplot")) {install.packages("corrplot"); require("corrplot")}
 # stats
 if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
 if (!require("performance")) {install.packages("performance"); require("performance")}
 
 
-## ----read, include = FALSE----------------------------------
+## ----read, include = FALSE----------------------------------------------------
 # read files and combine them
-data_ls <- list.files("../data", pattern = "csv")
-combined <- lapply(data_ls, function(f){
+data_lf <- list.files("../data", pattern = "csv")
+combined <- lapply(data_lf, function(f){
   fread(paste("../data/", f, sep = ""), sep = ",")
 })
 all_data <- do.call(rbind.data.frame, combined)
@@ -32,7 +35,7 @@ data[grepl("a_", midFile)]$Skill <- "articulation"
 data[grepl("d_", midFile)]$Skill <- "dynamics"
 
 
-## ----teaching, echo = FALSE---------------------------------
+## ----teaching, echo = FALSE---------------------------------------------------
 data$Teaching <- 0
 data[rating == "Yes"]$Teaching <- 1
 
@@ -41,62 +44,62 @@ individual <- data[subjectNumber != 9, .(N = .N, Sum = sum(Teaching)), by = .(su
 individual<- individual[order(subjectNumber)]
 
 # all
-all <- individual[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
[…]

### 2022-01-31 experiment-1/analysis/analysis.Rmd
finalise analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 2. Participants pressed "YES" if they think the recording was produced for teaching (as a teacher) whereas they pressed "NO" if they thought the recording was produced for performing (as a performer).
-
-- For additional analysis
-(3. Correct answers would be 1) participants pressed "YES" when they listened to teaching performances or 2) participants pressed "NO" when they listened to performing performances.)
 
@@
 }
+
 # assign Subcomponent Change
@@
 ```
+
 ## Legato (**)
@@
 ### Estimate
+- partial correlation coefficient between two variables (Teaching vs KOT)
+
 ```{r partial-plot-leg, echo = FALSE}
@@
 ### Estimate
+- partial correlation coefficient between two variables (Teaching vs KOT)
+
 ```{r partial-plot-sta, echo = FALSE}
@@
 ### Estimate
+- partial correlation coefficient between two variables (Teaching vs KV)
+
 ```{r partial-plot-for, echo = FALSE}
@@
 ### Estimate
+- partial correlation coefficient between two variables (Teaching vs KV)
+
 ```{r partial-plot-pia, echo = FALSE}
@@
 ### Estimate
+- partial correlation coefficient between two variables (Teaching vs KVDiff)
+
 ```{r partial-plot-ftop, echo = FALSE}
@@
 ### Estimate
+- partial correlation coefficient between two (Teaching vs KVDiff)
+
 ```{r partial-plot-ptof, echo = FALSE}

### 2022-01-31 experiment-2/analysis/analysis.Rmd
finalise analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2021-08-26 analysis/analysis.Rmd
@@
 title: "Music Perception 2: Analysis"
-output: html_notebook
+output:
+  html_document:
+    df_print: paged
 ---
@@
 
-- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques (expressions) separately. The order of the blocks was counterbalanced across participants.
-- 36 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented across participants.
+- 2 blocks (articulation / dynamics): each block only contained performances with either of articulation or dynamics. The order of the blocks was counterbalanced across participants.
+- 36 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented within the block.
 
@@
 
-3. Correct answers would be 1) participants pressed "YES" when they listened to teaching performances or 2) participants pressed "NO" when they listened to performing performances.
-
 ## Variables
@@
 
-```{r packages, include = FALSE}
+```{r setup, include = FALSE}
+options(knitr.duplicate.label = "allow")
+
 # data manipulation
@@
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
+if (!require("corrplot")) {install.packages("corrplot"); require("corrplot")}
 if (!require("qqplotr")) {install.packages("qqplotr"); require("qqplotr")}
@@
 # read files and combine them
-data_ls <- list.files("data", pattern = "csv")
-combined <- lapply(data_ls, function(f){
-  fread(paste("data/", f, sep = ""), sep = ",")
+data_lf <- list.files("../data", pattern = "csv")
+combined <- lapply(data_lf, function(f){
+  fread(paste("../data/", f, sep = ""), sep = ",")
 })
@@
 # create a list of data file names
-lf <- list.files("../experiment/mid/", pattern = "mid")
+midi_lf <- list.files("../experiment/mid/", pattern = "mid")
 
 # combine data
-all_data <- data.table()
-for (file in lf){
+all_midi <- data.table()
+for (file in midi_lf){
    current <- readMidi(paste("../experiment/mid/", file, sep = ""))
    current$MidFile <- gsub(".mid", "", file)
-   all_data <- rbind(all_data, current)
+   all_midi <- rbind(all_midi, current)
 }
 
-data <- all_data[event == "Note On" | event == "Note Off"]
-data$NoteNr <- rep(1:144, nrow(data)/144)
-data$channel <- NULL
-data$parameterMetaSystem <- NULL
-data$track <- NULL
-data$type <- NULL
-data$time2 <- (data$time/960)*1000 # deltatime to time (ms)
+midi <- all_midi[event == "Note On" | event == "Note Off"]
+midi$NoteNr <- rep(1:144, nrow(midi)/144)
+midi$channel <- NULL
+midi$parameterMetaSystem <- NULL
+midi$track <- NULL
+midi$type <- NULL
+midi$time2 <- (midi$time/960)*1000 # deltatime to time (ms)
 
 # labelling
-colnames(data)[c(3,4)] <- c("Pitch", "Velocity") # time event also change
-data$Condition <- "NA"
-data$Skill <- "NA"
-data[grepl("_t_", MidFile)]$Condition <- "teaching"
-data[grepl("_p_", MidFile)]$Condition <- "performing"
-data[grepl("a_", MidFile)]$Skill <- "articulation"
-data[grepl("d_", MidFile)]$Skill <- "dynamics"
+colnames(midi)[c(3,4)] <- c("Pitch", "Velocity") # time event also change
+midi$Condition <- "NA"
+midi$Skill <- "NA"
+midi[grepl("_t_", MidFile)]$Condition <- "teaching"
+midi[grepl("_p_", MidFile)]$Condition <- "performing"
+midi[grepl("a_", MidFile)]$Skill <- "articulation"
+midi[grepl("d_", MidFile)]$Skill <- "dynamics"
 
@@
 ```
+
 ## Articulation (n.s.)
@@
 # normality check
-shapiro.test(ioi[Skill == "articulation"]$Teaching)
-shapiro.test(ioi[Skill == "articulation"]$Mean)
+ioi_art_norm_teaching <- shapiro.test(ioi[Skill == "articulation"]$Teaching)
+ioi_art_norm_judge <- shapiro.test(ioi[Skill == "articulation"]$Mean)
 
-cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
+qqnorm(ioi[Skill == "articulation"]$Teaching)
+qqline(ioi[Skill == "articulation"]$Teaching)
+ioi_art_norm_teaching
+
+qqnorm(ioi[Skill == "articulation"]$Mean)
+qqline(ioi[Skill == "articulation"]$Mean)
+ioi_art_norm_judge
+
+cor_ioi_art <- cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
+cor_ioi_art
 ```
@@
 # normality check
-shapiro.test(ioi[Skill == "dynamics"]$Teaching)
-shapiro.test(ioi[Skill == "dynamics"]$Mean)
+ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
+ioi_dyn_norm_judge <- shapiro.test(ioi[Skill == "dynamics"]$Mean)
 
-cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
+qqnorm(ioi[Skill == "dynamics"]$Teaching)
+qqline(ioi[Skill == "dynamics"]$Teaching)
+ioi_dyn_norm_teaching
 
-cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
+qqnorm(ioi[Skill == "dynamics"]$Mean)
+qqline(ioi[Skill == "dynamics"]$Mean)
+ioi_dyn_norm_judge
+
+cor_ioi_dyn <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
+cor_ioi_dyn
+
+cor_ioi_dyn_spearman <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
+cor_ioi_dyn_spearman
 ```
@@
 # normality check
-shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
-shapiro.test(ioi_tra[Skill == "articulation"]$Mean)
+ioi_art_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
+ioi_art_tra_norm_judge <- shapiro.test(ioi_tra[Skill == "articulation"]$Mean)
+
+qqnorm(ioi_tra[Skill == "articulation"]$Teaching)
+qqline(ioi_tra[Skill == "articulation"]$Teaching)
+ioi_art_tra_norm_teaching
+
+qqnorm(ioi_tra[Skill == "articulation"]$Mean)
+qqline(ioi_tra[Skill == "articulation"]$Mean)
+ioi_art_tra_norm_judge
 
@@
 # normality check
-shapiro.test(cv[Skill == "articulation"]$Teaching)
-shapiro.test(cv[Skill == "articulation"]$CV)
+cv_art_norm_teaching <- shapiro.test(cv[Skill == "articulation"]$Teaching)
+cv_art_norm_judge <- shapiro.test(cv[Skill == "articulation"]$CV)
+
+qqnorm(cv[Skill == "articulation"]$Teaching)
+qqline(cv[Skill == "articulation"]$Teaching)
+cv_art_norm_teaching
+
+qqnorm(cv[Skill == "articulation"]$CV)
+qqline(cv[Skill == "articulation"]$CV)
+cv_art_norm_judge
 
@@
 # normality check
-shapiro.test(cv[Skill == "dynamics"]$Teaching)
-shapiro.test(cv[Skill == "dynamics"]$CV)
+cv_dyn_norm_teaching <- shapiro.test(cv[Skill == "dynamics"]$Teaching)
+cv_dyn_norm_judge <- shapiro.test(cv[Skill == "dynamics"]$CV)
+
+qqnorm(cv[Skill == "dynamics"]$Teaching)
+qqline(cv[Skill == "dynamics"]$Teaching)
+cv_dyn_norm_teaching
+
+qqnorm(cv[Skill == "dynamics"]$CV)
+qqline(cv[Skill == "dynamics"]$CV)
+cv_dyn_norm_judge
 
@@
 ```
+
 ## Legato (n.s.)
@@
 # normality check
-shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
-shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)
+kot_leg_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
+kot_leg_norm_judge <- shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)
 
-cor.test(kot_all[Subcomponent == "Legato"]$Teaching, kot_all[Subcomponent == "Legato"]$Mean)
+qqnorm(kot_all[Subcomponent == "Legato"]$Teaching)
+qqline(kot_all[Subcomponent == "Legato"]$Teaching)
+kot_leg_norm_teaching
+
+qqnorm(kot_all[Subcomponent == "Legato"]$Mean)
+qqline(kot_all[Subcomponent == "Legato"]$Mean)
+kot_leg_norm_judge
+
+cor_kot_leg <- cor.test(kot_all[Subcomponent == "Legato"]$Teaching, kot_all[Subcomponent == "Legato"]$Mean)
+cor_kot_leg
 ```
@@
 # normality check
-shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
-shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)
+kot_sta_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
+kot_sta_norm_judge <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)
 
-cor.test(kot_all[Subcomponent == "Staccato"]$Teaching, kot_all[Subcomponent == "Staccato"]$Mean)
+qqnorm(kot_all[Subcomponent == "Staccato"]$Teaching)
+qqline(kot_all[Subcomponent == "Staccato"]$Teaching)
+kot_sta_norm_teaching
+
+qqnorm(kot_all[Subcomponent == "Staccato"]$Mean)
+qqline(kot_all[Subcomponent == "Staccato"]$Mean)
+kot_sta_norm_judge
+
+cor_kot_sta <- cor.test(kot_all[Subcomponent == "Staccato"]$Teaching, kot_all[Subcomponent == "Staccato"]$Mean)
+cor_kot_sta
 ```
@@
 # normality check
-shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
-shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)
+kot_for_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
+kot_for_norm_judge <- shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)
 
-cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean)
+qqnorm(kot_all[Subcomponent == "Forte"]$Teaching)
+qqline(kot_all[Subcomponent == "Forte"]$Teaching)
+kot_for_norm_teaching
 
-cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean, method = "spearman", exact = FALSE)
+qqnorm(kot_all[Subcomponent == "Forte"]$Mean)
+qqline(kot_all[Subcomponent == "Forte"]$Mean)
+kot_for_norm_judge
+
+cor_kot_for <- cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean)
+cor_kot_for
+
+cor_kot_for_spearman <- cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean, method = "spearman", exact = FALSE)
+cor_kot_for_spearman
 ```
@@
 # normality check
-shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
-shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)
+kot_pia_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
+kot_pia_norm_judge <- shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)
 
-cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean)
+qqnorm(kot_all[Subcomponent == "Piano"]$Teaching)
+qqline(kot_all[Subcomponent == "Piano"]$Teaching)
+kot_pia_norm_teaching
 
-cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
+qqnorm(kot_all[Subcomponent == "Piano"]$Mean)
+qqline(kot_all[Subcomponent == "Piano"]$Mean)
+kot_pia_norm_judge
+
+cor_kot_pia <- cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean)
+cor_kot_pia
+
+cor_kot_pia_spearman <- cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
+cor_kot_pia_spearman
 ```
@@
 # normality check
-shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
-shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)
+vel_for_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
+vel_for_norm_judge <- shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)
 
-cor.test(vel_all[Subcomponent == "Forte"]$Teaching, vel_all[Subcomponent == "Forte"]$Mean)
+qqnorm(vel_all[Subcomponent == "Forte"]$Teaching)
+qqline(vel_all[Subcomponent == "Forte"]$Teaching)
+vel_for_norm_teaching
 
-cor.test(vel_all[Subcomponent == "Forte"]$Teaching, vel_all[Subcomponent == "Forte"]$Mean, method = "spearman", exact = FALSE)
+qqnorm(vel_all[Subcomponent == "Forte"]$Mean)
+qqline(vel_all[Subcomponent == "Forte"]$Mean)
+vel_for_norm_judge
+
+cor_vel_for <- cor.test(vel_all[Subcomponent == "Forte"]$Teaching, vel_all[Subcomponent == "Forte"]$Mean)
+cor_vel_for
+
+cor_vel_for_spearman <- cor.test(vel_all[Subcomponent == "Forte"]$Teaching, vel_all[Subcomponent == "Forte"]$Mean, method = "spearman", exact = FALSE)
+cor_vel_for_spearman
 ```
@@
 # normality check
-shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
-shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)
+vel_pia_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
+vel_pia_norm_judge <- shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)
 
-cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean)
+qqnorm(vel_all[Subcomponent == "Piano"]$Teaching)
+qqline(vel_all[Subcomponent == "Piano"]$Teaching)
+vel_pia_norm_teaching
 
-cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
+qqnorm(vel_all[Subcomponent == "Piano"]$Mean)
+qqline(vel_all[Subcomponent == "Piano"]$Mean)
+vel_pia_norm_judge
+
+cor_vel_pia <- cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean)
+cor_vel_pia
+
+cor_vel_pia_spearman <- cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
+cor_vel_pia_spearman
 ```
@@
 # normality check
-shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
-shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)
+vel_leg_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
+vel_leg_norm_judge <- shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)
 
-cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean)
+qqnorm(vel_all[Subcomponent == "Legato"]$Teaching)
+qqline(vel_all[Subcomponent == "Legato"]$Teaching)
+vel_leg_norm_teaching
+
+qqnorm(vel_all[Subcomponent == "Legato"]$Mean)
+qqline(vel_all[Subcomponent == "Legato"]$Mean)
+vel_leg_norm_judge
+
+cor_vel_leg <- cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean)
+cor_vel_leg
 ```
@@
 # normality check
-shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
-shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)
+vel_sta_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
+vel_sta_norm_judge <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)
 
-cor.test(vel_all[Subcomponent == "Staccato"]$Teaching, vel_all[Subcomponent == "Staccato"]$Mean)
+qqnorm(vel_all[Subcomponent == "Staccato"]$Teaching)
+qqline(vel_all[Subcomponent == "Staccato"]$Teaching)
+vel_sta_norm_teaching
+
+qqnorm(vel_all[Subcomponent == "Staccato"]$Mean)
+qqline(vel_all[Subcomponent == "Staccato"]$Mean)
+vel_sta_norm_judge
+
+cor_vel_sta <- cor.test(vel_all[Subcomponent == "Staccato"]$Teaching, vel_all[Subcomponent == "Staccato"]$Mean)
+cor_vel_sta
 ```
@@
 dt_vel_diff <- data_onset[NoteNr != 1]
-# assign Interval
 dt_vel_diff$Interval <- rep(1:71, nrow(dt_vel_diff)/71)
 
-# for intervals
+# assign Subcomponents
 dt_vel_diff$Subcomponent <- "NA"
@@
 # normality check
-shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
-shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)
+vel_diff_ftop_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
+vel_diff_ftop_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)
 
-cor.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching, vel_diff_all[Subcomponent == "FtoP"]$Mean)
+qqnorm(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
+qqline(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
+vel_diff_ftop_norm_teaching
 
-cor.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching, vel_diff_all[Subcomponent == "FtoP"]$Mean, method = "spearman", exact = FALSE)
+qqnorm(vel_diff_all[Subcomponent == "FtoP"]$Mean)
+qqline(vel_diff_all[Subcomponent == "FtoP"]$Mean)
+vel_diff_ftop_norm_judge
+
+cor_vel_diff_ftop <- cor.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching, vel_diff_all[Subcomponent == "FtoP"]$Mean)
+cor_vel_diff_ftop
+
+cor_vel_diff_ftop_spearman <- cor.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching, vel_diff_all[Subcomponent == "FtoP"]$Mean, method = "spearman", exact = FALSE)
+cor_vel_diff_ftop_spearman
 ```
@@
 # normality check
-shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
-shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)
+vel_diff_ptof_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
+vel_diff_ptof_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)
 
-cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean)
+qqnorm(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
+qqline(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
+vel_diff_ptof_norm_teaching
 
-cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean, method = "spearman", exact = FALSE)
+qqnorm(vel_diff_all[Subcomponent == "PtoF"]$Mean)
+qqline(vel_diff_all[Subcomponent == "PtoF"]$Mean)
+vel_diff_ptof_norm_judge
+
+cor_vel_diff_ptof <- cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean)
+cor_vel_diff_ptof
+
+cor_vel_diff_ptof_spearman <- cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean, method = "spearman", exact = FALSE)
+cor_vel_diff_ptof_spearman
 ```
@@
 # normality check
-shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
-shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)
+vel_diff_ltos_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
+vel_diff_ltos_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)
 
-cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean)
+qqnorm(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
+qqline(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
+vel_diff_ltos_norm_teaching
+
+qqnorm(vel_diff_all[Subcomponent == "LtoS"]$Mean)
+qqline(vel_diff_all[Subcomponent == "LtoS"]$Mean)
+vel_diff_ltos_norm_judge
+
+cor_vel_diff_ltos <- cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean)
+cor_vel_diff_ltos
 ```
@@
 # normality check
-shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Teaching)
-shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Mean)
+vel_diff_stol_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Teaching)
+vel_diff_stol_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Mean)
 
-cor.test(vel_diff_all[Subcomponent == "StoL"]$Teaching, vel_diff_all[Subcomponent == "StoL"]$Mean)
+qqnorm(vel_diff_all[Subcomponent == "StoL"]$Teaching)
+qqline(vel_diff_all[Subcomponent == "StoL"]$Teaching)
+vel_diff_stol_norm_teaching
+
+qqnorm(vel_diff_all[Subcomponent == "StoL"]$Mean)
+qqline(vel_diff_all[Subcomponent == "StoL"]$Mean)
+vel_diff_stol_norm_judge
+
+cor_vel_diff_stol <- cor.test(vel_diff_all[Subcomponent == "StoL"]$Teaching, vel_diff_all[Subcomponent == "StoL"]$Mean)
+cor_vel_diff_stol
 ```
@@
 ## Legato (n.s.)
+### Estimate
+- partial correlation coefficient between two variables (Teaching vs KOT)
+
+```{r partial-plot-leg, echo = FALSE}
+# plot
+corrplot.mixed(pcor(partial[Subcomponent == "Legato", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
+```
+
 ```{r kot-partial-leg, echo = TRUE}
@@
 ## Staccato (n.s.)
+### Estimate
+- partial correlation coefficient between two variables (Teaching vs KOT)
+
+```{r partial-plot-sta, echo = FALSE}
+# plot
+corrplot.mixed(pcor(partial[Subcomponent == "Staccato", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
+```
+
 ```{r kot-partial-sta, echo = TRUE}
@@
 ## Forte (n.s.)
+### Estimate
+- partial correlation coefficient between two variables (Teaching vs KV)
+
+```{r partial-plot-for, echo = FALSE}
+# plot
+corrplot.mixed(pcor(partial[Subcomponent == "Forte", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
+```
+
 ```{r vel-partial-for, echo = TRUE}
@@
 ## Piano (n.s.)
+### Estimate
+- partial correlation coefficient between two variables (Teaching vs KV)
+
+```{r partial-plot-pia, echo = FALSE}
+# plot
+corrplot.mixed(pcor(partial[Subcomponent == "Piano", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
+```
+
 ```{r vel-partial-pia, echo = TRUE}
@@
 ## Forte to Piano (***)
+### Estimate
+- partial correlation coefficient between two variables (Teaching vs KVDiff)
+
+```{r partial-plot-ftop, echo = FALSE}
+# plot
+corrplot.mixed(pcor(partial[Subcomponent2 == "FtoP", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
+```
+
 ```{r vel-diff-partial-ftop, echo = TRUE}
@@
 ## Piano to Forte (***)
+### Estimate
+- partial correlation coefficient between two variables (Teaching vs KVDiff)
+
+```{r partial-plot-ptof, echo = FALSE}
+# plot
+corrplot.mixed(pcor(partial[Subcomponent2 == "PtoF", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
+```
+
 ```{r vel-diff-partial-ptof, echo = TRUE}

### 2022-01-31 experiment-1/analysis/analysis.R

@@ -131,6 +131,7 @@ for (phrase in 1:length(ls_piano)){
    dt_ioi[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
  }
 }
+
 # assign Subcomponent Change
 for (number in change_1){
  dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
@@ -333,6 +334,7 @@ for (phrase in 1:length(ls_piano)){
      dt_kot[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
    }
 }
+
 # assign Subcomponent Change
 for (number in change_1){
    dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"

### 2022-01-31 experiment-2/analysis/analysis.R

@@ -1,20 +1,23 @@
-## ----setup, include = FALSE---------------------------------------
+## ----setup, include = FALSE---------------------------------------------------
+options(knitr.duplicate.label = "allow")
+
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
 # midi
 if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
 # plot
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
+if (!require("corrplot")) {install.packages("corrplot"); require("corrplot")}
 if (!require("qqplotr")) {install.packages("qqplotr"); require("qqplotr")}
 # stats
 if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
 if (!require("performance")) {install.packages("performance"); require("performance")}
 
 
-## ----read, include = FALSE----------------------------------------
+## ----read, include = FALSE----------------------------------------------------
 # read files and combine them
-data_ls <- list.files("../data", pattern = "csv")
-combined <- lapply(data_ls, function(f){
+data_lf <- list.files("../data", pattern = "csv")
+combined <- lapply(data_lf, function(f){
   fread(paste("../data/", f, sep = ""), sep = ",")
 })
 all_data <- do.call(rbind.data.frame, combined)
@@ -33,7 +36,7 @@ data[grepl("a_", midFile)]$Skill <- "articulation"
 data[grepl("d_", midFile)]$Skill <- "dynamics"
 
 
-## ----teaching, echo = FALSE---------------------------------------
+## ----teaching, echo = FALSE---------------------------------------------------
 data$Teaching <- 0
 data[rating == "Yes"]$Teaching <- 1
 
@@ -47,34 +50,34 @@ all <- all[order(MidFile)]
 all
 
 
-## ----midi, include = FALSE----------------------------------------
+## ----midi, include = FALSE----------------------------------------------------
 # create a list of data file names
[…]

### 2022-01-31 paper/manuscript.Rmd
update methods
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ## Apparatus
-The experiment was programmed in Python 3.8.2 using the PsychoPy library (2020.2.4; https://www.psychopy.org/) on a Mac Book Pro with Mac OS X Catalina 10.15.6.
-Stimuli were played using the Mido library (1.2.9; https://mido.readthedocs.io/en/latest/) on a Max/MSP patcher (8.1.7; https://cycling74.com/products/max).
+The experiment was programmed in Python 3.8.2 using the PsychoPy Python library (2020.2.4; https://www.psychopy.org/) on a Mac Book Pro with Mac OS X Catalina 10.15.6.
+Stimuli were played using the Mido Python library (1.2.9; https://mido.readthedocs.io/en/latest/) on a Max/MSP patcher (8.1.7; https://cycling74.com/products/max).
 During the experiment, participants listened to the stimuli via headphones (Audio-Technica ATH-M50X).
@@
 We randomly sampled 24 articulation performances and 24 dynamics performances from the teaching condition as well as 24 articulation performances and 24 dynamics performances from the performing condition.
-It is important to note that the performances from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments since we randomly sampled the recordings.
+It is important to note that the performances from the teaching condition did not necessarily exhibit specific features of teaching that we found in our previous experiments (e.g., exaggeration) since we randomly sampled the performances.
 
@@
 
-Stimuli (performances) were quantified with regard to tempo (interonset intervals; IOIs), articulation (key-overlap time; KOT), dynamics (key velocity; KV) and dynamics contrast (key velocity difference; KV-Diff) only for 16th notes.
+Stimuli were quantified with regard to tempo (interonset intervals; IOIs), articulation (key-overlap time; KOT), dynamics (key velocity; KV) and dynamics contrast (key velocity difference; KV-Diff) only for 16th notes.
 Interonset intervals are time intervals between onsets of adjacent notes.
@@
 
-First, we investigated data by looking at correlations between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as "teaching" (i.e., what percentage of participants responded as "yes (teaching)") for each stimulus.
+First, we investigated data by looking at correlations between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as "teaching" (i.e., what percentage of participants responded as "yes") for each stimulus.
 Second, we run multiple regression and entered all four performance features to examine which predictor significantly contributed to participants' judgments as teaching.
@@
 piano), we entered each subcomponent (i.e., legato, staccato, forte, piano) separately to represent either an articulation or dynamics feature of the performance for a regression model.
+
 For articulation recordings, there were two models.
@@
 With regard to tempo (IOIs), there was only one value for each technique because tempo was consistent across the performance and was not dependent on subcomponents.
+Therefore, we entered the same tempo value for legato and staccato or forte and piano parts.
 

### 2022-01-31 paper/manuscript.tex
update methods
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 Since articulation and dynamics were comprised of two opposite directional values (i.e., legato vs.~staccato, forte vs.~piano), we entered each subcomponent (i.e., legato, staccato, forte, piano) separately to represent either an articulation or dynamics feature of the performance for a regression model.
+
 For articulation recordings, there were two models.

### 2022-01-31 experiment-1/analysis/analysis.Rmd
update analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ioi_art_norm_teaching <- shapiro.test(ioi[Skill == "articulation"]$Teaching)
-ioi_art_norm_judge <- shapiro.test(ioi[Skill == "articulation"]$Mean)
+ioi_art_norm_performance <- shapiro.test(ioi[Skill == "articulation"]$Mean)
 
@@
 qqline(ioi[Skill == "articulation"]$Mean)
-ioi_art_norm_judge
+ioi_art_norm_performance
 
@@
 ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
-ioi_dyn_norm_judge <- shapiro.test(ioi[Skill == "dynamics"]$Mean)
+ioi_dyn_norm_performance <- shapiro.test(ioi[Skill == "dynamics"]$Mean)
 
@@
 qqline(ioi[Skill == "dynamics"]$Mean)
-ioi_dyn_norm_judge
+ioi_dyn_norm_performance
 
@@
 ioi_art_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
-ioi_art_tra_norm_judge <- shapiro.test(ioi_tra[Skill == "articulation"]$Mean)
+ioi_art_tra_norm_performance <- shapiro.test(ioi_tra[Skill == "articulation"]$Mean)
 
@@
 qqline(ioi_tra[Skill == "articulation"]$Mean)
-ioi_art_tra_norm_judge
+ioi_art_tra_norm_performance
 
@@
 ioi_dyn_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
-ioi_dyn_tra_norm_judge <- shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)
+ioi_dyn_tra_norm_performance <- shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)
 
@@
 qqline(ioi_tra[Skill == "dynamics"]$Mean)
-ioi_dyn_tra_norm_judge
+ioi_dyn_tra_norm_performance
 
@@
 cv_art_norm_teaching <- shapiro.test(cv[Skill == "articulation"]$Teaching)
-cv_art_norm_judge <- shapiro.test(cv[Skill == "articulation"]$CV)
+cv_art_norm_performance <- shapiro.test(cv[Skill == "articulation"]$CV)
 
@@
 qqline(cv[Skill == "articulation"]$CV)
-cv_art_norm_judge
+cv_art_norm_performance
 
@@
 cv_dyn_norm_teaching <- shapiro.test(cv[Skill == "dynamics"]$Teaching)
-cv_dyn_norm_judge <- shapiro.test(cv[Skill == "dynamics"]$CV)
+cv_dyn_norm_performance <- shapiro.test(cv[Skill == "dynamics"]$CV)
 
@@
 qqline(cv[Skill == "dynamics"]$CV)
-cv_dyn_norm_judge
+cv_dyn_norm_performance
 
@@
 kot_leg_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
-kot_leg_norm_judge <- shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)
+kot_leg_norm_performance <- shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)
 
@@
 qqline(kot_all[Subcomponent == "Legato"]$Mean)
-kot_leg_norm_judge
+kot_leg_norm_performance
 
@@
 kot_sta_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
-kot_sta_norm_judge <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)
+kot_sta_norm_performance <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)
 
@@
 qqline(kot_all[Subcomponent == "Staccato"]$Mean)
-kot_sta_norm_judge
+kot_sta_norm_performance
 
@@
 kot_for_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
-kot_for_norm_judge <- shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)
+kot_for_norm_performance <- shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)
 
@@
 qqline(kot_all[Subcomponent == "Forte"]$Mean)
-kot_for_norm_judge
+kot_for_norm_performance
 
@@
 kot_pia_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
-kot_pia_norm_judge <- shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)
+kot_pia_norm_performance <- shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)
 
@@
 qqline(kot_all[Subcomponent == "Piano"]$Mean)
-kot_pia_norm_judge
+kot_pia_norm_performance
 
@@
 vel_for_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
-vel_for_norm_judge <- shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)
+vel_for_norm_performance <- shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)
 
@@
 qqline(vel_all[Subcomponent == "Forte"]$Mean)
-vel_for_norm_judge
+vel_for_norm_performance
 
@@
 vel_pia_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
-vel_pia_norm_judge <- shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)
+vel_pia_norm_performance <- shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)
 
@@
 qqline(vel_all[Subcomponent == "Piano"]$Mean)
-vel_pia_norm_judge
+vel_pia_norm_performance
 
@@
 vel_leg_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
-vel_leg_norm_judge <- shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)
+vel_leg_norm_performance <- shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)
 
@@
 qqline(vel_all[Subcomponent == "Legato"]$Mean)
-vel_leg_norm_judge
+vel_leg_norm_performance
 
@@
 vel_sta_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
-vel_sta_norm_judge <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)
+vel_sta_norm_performance <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)
 
@@
 qqline(vel_all[Subcomponent == "Staccato"]$Mean)
-vel_sta_norm_judge
+vel_sta_norm_performance
 
@@
 vel_diff_ftop_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
-vel_diff_ftop_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)
+vel_diff_ftop_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)
 
@@
 qqline(vel_diff_all[Subcomponent == "FtoP"]$Mean)
-vel_diff_ftop_norm_judge
+vel_diff_ftop_norm_performance
 
@@
 vel_diff_ptof_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
-vel_diff_ptof_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)
+vel_diff_ptof_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)
 
@@
 qqline(vel_diff_all[Subcomponent == "PtoF"]$Mean)
-vel_diff_ptof_norm_judge
+vel_diff_ptof_norm_performance
 
@@
 vel_diff_ltos_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
-vel_diff_ltos_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)
+vel_diff_ltos_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)
 
@@
 qqline(vel_diff_all[Subcomponent == "LtoS"]$Mean)
-vel_diff_ltos_norm_judge
+vel_diff_ltos_norm_performance
 
@@
 vel_diff_stol_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Teaching)
-vel_diff_stol_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Mean)
+vel_diff_stol_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Mean)
 
@@
 qqline(vel_diff_all[Subcomponent == "StoL"]$Mean)
-vel_diff_stol_norm_judge
+vel_diff_stol_norm_performance
 

### 2022-01-31 experiment-1/analysis/analysis.R

@@ -163,7 +163,7 @@ ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
 ## ---- echo = TRUE-------------------------------------------------------------
 # normality check
 ioi_art_norm_teaching <- shapiro.test(ioi[Skill == "articulation"]$Teaching)
-ioi_art_norm_judge <- shapiro.test(ioi[Skill == "articulation"]$Mean)
+ioi_art_norm_performance <- shapiro.test(ioi[Skill == "articulation"]$Mean)
 
 qqnorm(ioi[Skill == "articulation"]$Teaching)
 qqline(ioi[Skill == "articulation"]$Teaching)
@@ -171,7 +171,7 @@ ioi_art_norm_teaching
 
 qqnorm(ioi[Skill == "articulation"]$Mean)
 qqline(ioi[Skill == "articulation"]$Mean)
-ioi_art_norm_judge
+ioi_art_norm_performance
 
 cor_ioi_art <- cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
 cor_ioi_art
@@ -180,7 +180,7 @@ cor_ioi_art
 ## ---- echo = TRUE-------------------------------------------------------------
 # normality check
 ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
-ioi_dyn_norm_judge <- shapiro.test(ioi[Skill == "dynamics"]$Mean)
+ioi_dyn_norm_performance <- shapiro.test(ioi[Skill == "dynamics"]$Mean)
 
 qqnorm(ioi[Skill == "dynamics"]$Teaching)
 qqline(ioi[Skill == "dynamics"]$Teaching)
@@ -188,7 +188,7 @@ ioi_dyn_norm_teaching
 
 qqnorm(ioi[Skill == "dynamics"]$Mean)
 qqline(ioi[Skill == "dynamics"]$Mean)
-ioi_dyn_norm_judge
+ioi_dyn_norm_performance
 
 cor_ioi_dyn <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
 cor_ioi_dyn
@@ -215,7 +215,7 @@ ggscatter(ioi_tra, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line"
[…]

### 2022-01-31 experiment-2/analysis/analysis.R

@@ -164,7 +164,7 @@ ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
 ## ---- echo = FALSE------------------------------------------------------------
 # normality check
 ioi_art_norm_teaching <- shapiro.test(ioi[Skill == "articulation"]$Teaching)
-ioi_art_norm_judge <- shapiro.test(ioi[Skill == "articulation"]$Mean)
+ioi_art_norm_performance <- shapiro.test(ioi[Skill == "articulation"]$Mean)
 
 qqnorm(ioi[Skill == "articulation"]$Teaching)
 qqline(ioi[Skill == "articulation"]$Teaching)
@@ -172,7 +172,7 @@ ioi_art_norm_teaching
 
 qqnorm(ioi[Skill == "articulation"]$Mean)
 qqline(ioi[Skill == "articulation"]$Mean)
-ioi_art_norm_judge
+ioi_art_norm_performance
 
 cor_ioi_art <- cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
 cor_ioi_art
@@ -181,7 +181,7 @@ cor_ioi_art
 ## ---- echo = FALSE------------------------------------------------------------
 # normality check
 ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
-ioi_dyn_norm_judge <- shapiro.test(ioi[Skill == "dynamics"]$Mean)
+ioi_dyn_norm_performance <- shapiro.test(ioi[Skill == "dynamics"]$Mean)
 
 qqnorm(ioi[Skill == "dynamics"]$Teaching)
 qqline(ioi[Skill == "dynamics"]$Teaching)
@@ -189,7 +189,7 @@ ioi_dyn_norm_teaching
 
 qqnorm(ioi[Skill == "dynamics"]$Mean)
 qqline(ioi[Skill == "dynamics"]$Mean)
-ioi_dyn_norm_judge
+ioi_dyn_norm_performance
 
 cor_ioi_dyn <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
 cor_ioi_dyn
@@ -216,7 +216,7 @@ ggscatter(ioi_tra, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line"
[…]

### 2022-02-01 paper/manuscript.Rmd
update results (experiment-1)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed.
+However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (*p* `r if(ioi_dyn_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_dyn_norm_performance$p.value))}`).
 Therefore, a Spearman's rank correlation coefficient was additionally used to assess the relationship between performance tempi of dynamics recordings and participants' judgments.
@@
 
+The Shapiro-Wilk normality test revealed that the distribution of KOT for dynamics recordings was not normally distributed (Forte; *p* `r if(kot_for_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', kot_for_norm_performance$p.value))}`, Piano; *p* `r if(kot_pia_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', kot_pia_norm_performance$p.value))}`).
+Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for_spearman$estimate))`, *p* `r if(cor_kot_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for_spearman$p.value))}`, Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia_spearman$estimate))`, *p* `r if(cor_kot_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia_spearman$p.value))}`).
+
 ```{r kot-1, include = FALSE}
@@
 
+The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings for legato was not normally distributed (;*p* `r if(vel_leg_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_leg_norm_performance$p.value))}`).
+A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg_spearman$estimate))`, *p* `r if(cor_vel_leg_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg_spearman$p.value))}`).
+
 ```{r vel-1, include = FALSE}
@@
 For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ltos$p.value))}`, From Staccato to Legato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_stol$p.value))}`, *Figure \ref{fig:vel-diff-1}*, left).
+
+The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings for transition points from legato to staccato was not normally distributed (;*p* `r if(vel_diff_ltos_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ltos_norm_performance$p.value))}`).
+A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos_spearman$estimate))`, *p* `r if(cor_vel_diff_ltos_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ltos_spearman$p.value))}`).
 
@@
 For articulation recordings, performances with longer legato and shorter staccato were tended to be judged as teaching.
-For dynamics recordings, performances with louder forte were more likely to be judged as teaching whereas there was no relationship between softer sound (i.e., piano) and participants' judgements as teaching.
-However, performances with larger contrasts between forte and piano for both directions (i.e., from forte to piano, from piano to forte) were more likely to be judged as teaching.
+For dynamics recordings, performances with louder forte were more likely to be judged as teaching whereas there was no relationship between softer sound (i.e., piano) and participants' judgments as teaching.
+Importantly, performances with larger contrasts between forte and piano for both directions (i.e., from forte to piano, from piano to forte) were more likely to be judged as teaching.
 This result may suggest that dynamics contrast might be reliably used to infer teaching intentions, rather than absolute dynamics values themselves.
@@
 These performance features were overall consistent with what expert pianists did in our previous experiments for teaching purposes.
-Therefore, our findings suggest that musicians may be able to successfully infer teaching intentions of expert pianists, only by listening to recorded performances.
+Therefore, our findings suggest that musicians may rely on generic pedagogical behaviour (e.g., slower demonstration, exaggeration) to infer teaching intentions of expert pianists, only by listening to recorded performances.
 
@@
 
-```{r results-2, cache = TRUE, include = FALSE}
+```{r results-2, cache = FALSE, include = FALSE}
 source(here("experiment-2/analysis", "analysis.R"), chdir = TRUE)

### 2022-02-01 paper/manuscript.tex
update results (experiment-1)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-The experiment was programmed in Python 3.8.2 using the PsychoPy library (2020.2.4; \url{https://www.psychopy.org/}) on a Mac Book Pro with Mac OS X Catalina 10.15.6.
-Stimuli were played using the Mido library (1.2.9; \url{https://mido.readthedocs.io/en/latest/}) on a Max/MSP patcher (8.1.7; \url{https://cycling74.com/products/max}).
+The experiment was programmed in Python 3.8.2 using the PsychoPy Python library (2020.2.4; \url{https://www.psychopy.org/}) on a Mac Book Pro with Mac OS X Catalina 10.15.6.
+Stimuli were played using the Mido Python library (1.2.9; \url{https://mido.readthedocs.io/en/latest/}) on a Max/MSP patcher (8.1.7; \url{https://cycling74.com/products/max}).
 During the experiment, participants listened to the stimuli via headphones (Audio-Technica ATH-M50X).
@@
 
-First, we investigated data by looking at correlations between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as ``teaching'' (i.e., what percentage of participants responded as ``yes (teaching)'') for each stimulus.
+First, we investigated data by looking at correlations between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as ``teaching'' (i.e., what percentage of participants responded as ``yes'') for each stimulus.
 Second, we run multiple regression and entered all four performance features to examine which predictor significantly contributed to participants' judgments as teaching.
@@
 
-However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed.
+However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (\emph{p} = 0.037).
 Therefore, a Spearman's rank correlation coefficient was additionally used to assess the relationship between performance tempi of dynamics recordings and participants' judgments.
@@
 
+The Shapiro-Wilk normality test revealed that the distribution of KOT for dynamics recordings was not normally distributed (Forte; \emph{p} \textless{} 0.001, Piano; \emph{p} \textless{} 0.001).
+Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r} = .15, \emph{p} = 0.31, Piano; \emph{r} = -.12, \emph{p} = 0.43).
+
 \hypertarget{dynamics-kv}{%
@@
 
+The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings for legato was not normally distributed (;\emph{p} = 0.002).
+A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r} = .03, \emph{p} = 0.84).
+
 \hypertarget{dynamics-contrast-kv-diff}{%
@@
 For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r} = -.26, \emph{p} = 0.071, From Staccato to Legato; \emph{r} = -.19, \emph{p} = 0.21, \emph{Figure \ref{fig:vel-diff-1}}, left).
+
+The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings for transition points from legato to staccato was not normally distributed (;\emph{p} = 0.007).
+A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r} = -.23, \emph{p} = 0.12).
 

### 2022-02-01 paper/manuscript.Rmd
update methods and results (exp2)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ## Stimuli
-We selected stimuli from our previous experiments (Tominaga et al., *submitted*; Experiment 1).
+We selected stimuli from our previous experiments (Tominaga et al., *submitted*).
 Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files.
@@
 For the current experiment, 96 performances were chosen from the valid performances in Tominaga et al.
-(*submitted*).
+(*submitted*; Experiment 1).
 We randomly sampled 24 articulation performances and 24 dynamics performances from the teaching condition as well as 24 articulation performances and 24 dynamics performances from the performing condition.
@@
 
-```{r results-1, cache = TRUE, include = FALSE}
+```{r results-1, cache = FALSE, include = FALSE}
 source(here("experiment-1/analysis", "analysis.R"), chdir = TRUE)
@@
 staccato, forte vs.
-piano) and therefore cannot be summed up to represent each technique, we reported four regression models for each subcomponent (see details in *[Data analysis](#dataanalysis)*).
+piano) and therefore cannot be summed up to represent each technique as one value, we reported four separateregression models for each subcomponent (see details in *Data analysis*).
 
@@
 These performance features were overall consistent with what expert pianists did in our previous experiments for teaching purposes.
-Therefore, our findings suggest that musicians may rely on generic pedagogical behaviour (e.g., slower demonstration, exaggeration) to infer teaching intentions of expert pianists, only by listening to recorded performances.
+Therefore, our findings suggest that musicians may rely on generic pedagogical behaviours (e.g., slower demonstration, exaggeration) to infer teaching intentions of expert pianists, only by listening to recorded performances.
 
@@
 The aim of Experiment 2 was to replicate our previous findings in Experiment 1 with a more naturalistic piece of music.
-We could not finish data collection, therefore interpreted data by looking at scatter plots without any statistical analysis.
+Given the findings on Experiment 1, we predicted that slower performance would be likely to be judged as teaching.
+Also performances with exaggerated articulation and dynamics (in particular, longer legato and shorter staccato, larger contrast between forte and piano) would be likely to be judged as teaching.
 
@@
 ## Apparatus and procedure
-The experimental setting and procedure were identical to Experiment 1 except that each block consisted of 4 practice trials and 36 experimental trials.
+The apparatus and procedure were identical to Experiment 1 except that each block consisted of 4 practice trials and 36 experimental trials.
 The number of trials was reduced due to the time constraint of the experiment.
@@
 ## Stimuli
-As Experiment 1, stimuli were produced by actual pianists on a weighed Yamaha MIDI digital piano and recorded as MIDI files.
-One piece of music was selected as a base piece, which was performed with a musical expressive technique of either articulation (*Figure \ref{fig:stim2}*, A) or dynamics (*Figure \ref{fig:stim2}*, B).
+As Experiment 1, we selected stimuli from our previous experiments (Tominaga et al., *submitted*).
 The excerpt was taken from ``Sonatina Op.36 (No.3) in C major" by Muzio Clementi and modified for the experiment.
+The excerpt was performed with either articulation (*Figure \ref{fig:stim2}*, A) or dynamics (*Figure \ref{fig:stim2}*, B).
 The stimuli were performed around 100 - 120 quarter-beats per minute (i.e., around 250 - 300 ms for 8th-note IOIs).
 
-Recorded piano performances for the stimuli were obtained from our previous experiments (Tominaga et al., *in prep*).
-Half of the stimuli (36 recordings) was randomly chosen from 248 valid performances in the teaching condition whereas the other half (36 recordings) was randomly chosen from 256 valid performances in the performing condition.
+For the current experiment, 96 performances were chosen from the valid performances in Tominaga et al.
+(*submitted*; Experiment 2).
+There were 248 valid performances in the teaching condition and 256 valid performances in the performing condition.
+We randomly sampled 18 articulation performances and 18 dynamics performances from the teaching condition as well as 18 articulation performances and 18 dynamics performances from the performing condition.
 In total, 72 recordings were selected as stimuli for the current experiment.
-Again, it is important to note that each recording from the teaching condition did not necessarily exhibit specific features of teaching performances that we found in the previous experiments since we randomly sampled recordings.
+Again, it is important to note that each performance from the teaching condition did not necessarily exhibit specific features of teaching that we found in the previous experiments (e.g., exaggeration) since we randomly sampled the performances.
 
 ## Data analysis{#dataanalysis2}
-As Experiment 1, stimuli were quantified with regard to tempo (IOIs), articulation (KOT), dynamics (KV) and dynamics contrast (KV-Diff).
+The data analysis was identical to Experiment 1.
 Only the 8th notes with expressive notations were included for data analysis.
-We did not run any statistical analysis for Experiment 2.
+As a result, only one 8th note in the 4th measure without any expression was not included.
 
@@
 
-## Scatter plots
+All results were reported as significant at *p* < 0.05.
+
+## Correlation
+As Experiment 1, a Pearson product-moment correlation coefficient was computed by default for correlation analysis and a Spearman's rank correlation coefficient was additionally computed if normality assumption was violated based on the Shapiro-Wilk normality test.
+
 ### Tempo (IOIs)
-As Experiment 1, it seems that performance tempi (IOIs) are correlated with participants' judgments as teaching.
-Slower performances were more likely to be judged as teaching.
-However, the slope of articulation seems to be less steep than that of Experiment 1 (*Figure \ref{fig:ioi-2}*).
+Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_art$p.value))}`, Dynamics; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-2}*).
+
+The Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (*p* `r if(ioi_dyn_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_dyn_norm_performance$p.value))}`).
+A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`).
 
@@
 ### Articulation (KOT)
-Unlike Experiment 1, there seems to be no relationship between KOT values and participants' judgments as teaching.
-The scatter plot suggests that participants did not use articulation values to infer teaching intentions (*Figure \ref{fig:kot-2}*).
+Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`, Staccato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_leg$p.value))}`, *Figure \ref{fig:kot-2}*, left).
+
+For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`).
+However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`), suggesting that performances with louder staccato were more likely to be considered as teaching performance (*Figure \ref{fig:kot-2}*, right).
 
@@
 ### Dynamics (KV)
-As Experiment 1, there seems to be a relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-2}*).
-Performances with louder forte adn softer piano seem to be judged as teaching.
+As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-2}*, right).
+Specifically, performances with louder forte (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`) and softer piano (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia$p.value))}`) were more likely to be judged as teaching.
+
+The Shapiro-Wilk normality test revealed that the distribution of KV values for dynamics recordings was not normally distributed (Forte; *p* `r if(vel_for_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_for_norm_performance$p.value))}`, Piano' *p* `r if(vel_pia_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_pia_norm_performance$p.value))}`).
+Spearman's rank correlation coefficient also confirmed that performances with louder forte (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for_spearman$estimate))`, *p* `r if(cor_vel_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for_spearman$p.value))}`) and softer piano (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia_spearman$p.value))}`) were more likely to be judged as teaching.
+
+For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-2}*, left).
 
@@
 ### Dynamics contrast (KV-Diff)
-As Experiment 1, there seems to be a relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-diff-2}*).
-Performances with larger contrasts between forte and piano seem to be judged as teaching.
+As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (*Figure \ref{fig:vel-diff-2}*, right).
+Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).
+
+The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; *p* `r if(vel_diff_ftop_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ftop_norm_performance$p.value))}`, Piano to Forte; *p* `r if(vel_diff_ptof_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ptof_norm_performance$p.value))}`).
+Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop_spearman$estimate))`, *p* `r if(cor_vel_diff_ftop_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop_spearman$p.value))}`, Piano to Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ptof_spearman$p.value))}`).
 
@@
 ```
+
+## Multiple regression
+
+As Experiment 1, we performed multiple regression analyses to further explore which feature of performance contributed the most to participants' judgments as teaching.
+Again, since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.
+staccato, forte vs.
+piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in *Data analysis* in Experiment 1).
+
+### Legato
+A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
+The result of the regression indicated that the model explained `r summary(m1)$adj.r.squared*100` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r round(summary(m1)$fstatistic[1], 1)`, *p* `r if(lmp(m1) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m1)))}`).
+It was found that tempo (IOIs; *$\beta$* = `r summary(m1)$coefficients[2]`, *p* `r if(summary(m1)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[2, 4]))}`), dynamics (KV) and dynamics contrast (KV-Diff) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
+However, articulation (KOT; *$\beta$* = `r summary(m1)$coefficients[3]`, *p* `r if(summary(m1)$coefficients[3, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[3, 4]))}`) for the legato parts was not a significant predictor as opposed to Experiment 1.
+
+### Staccato
+A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato).
+The overall was not statistically significant ($R^{2}$ = `r summary(m2)$adj.r.squared*100`, *F*(`r summary(m2)$fstatistic[2]`, `r summary(m2)$fstatistic[3]`) = `r round(summary(m2)$fstatistic[1], 1)`, *p* `r if(lmp(m2) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m2)))}`).
+
+### Forte
+A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano).
+The result of the regression indicated that the model explained `r summary(m3)$adj.r.squared*100` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r round(summary(m3)$fstatistic[1], 1)`, *p* `r if(lmp(m3) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m3)))}`).
+It was found that dynamics contrast from forte to piano (KV-Diff; *$\beta$* = `r summary(m3)$coefficients[5]`, *p* `r if(summary(m3)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m3)$coefficients[5, 4]))}`) were significant predictors of participants' judgments as teaching.
+
+### Piano
+A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte).
+The result of the regression indicated that the model explained `r summary(m4)$adj.r.squared*100` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r round(summary(m4)$fstatistic[1], 1)`, *p* `r if(lmp(m4) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m4)))}`).
+It was found that tempo (IOIs; *$\beta$* = `r summary(m4)$coefficients[2]`, *p* `r if(summary(m4)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[2, 4]))}`) and dynamics contrast from piano to forte (KV-Diff; *$\beta$* = `r summary(m4)$coefficients[5]`, *p* `r if(summary(m4)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[5, 4]))}`) were significant predictors of participants' judgments as teaching.
 
@@
 # Discussion
-Experiment 2 aims to replicate our previous findings in Experiment 1 with a more naturalistic piece of music.
-The preliminary data suggest that some features of piano performance contributes to participant' judgments as teaching.
-For instance, performances with slower tempo were likely to be judged as teaching regardless which expressive technique was implemented.
-Also, performances with louder forte and softer piano were likely to be judged as teaching for dynamics recordings.
+Experiment 2 aimed to replicate our previous findings in Experiment 1 with a more naturalistic piece of music.
+We successfully replicated the findings from Experiment 1 in dynamics features.
+Performances with louder forte and softer piano were likely to be judged as teaching for dynamics recordings.
 Moreover, there seems to be a strong relationship between dynamics contrast between forte and piano and participants' judgments as teaching.
 
-However, it seems there was no relationship between articulation values and participants' judgments as teaching.
+However, we failed to replicate the results in terms of tempo (IOIs) and articulation (KOT).
 Compared with Experiment 1, the piece used in Experiment 2 was musically much complex.
@@
 
-```{r results-prereg, cache = TRUE}
+```{r results-prereg, cache = FALSE}
 source(here("experiment-1/analysis/prereg_analysis", "prereg_analysis.R"), chdir = TRUE)

### 2022-02-01 paper/manuscript.tex
update methods and results (exp2)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-We selected stimuli from our previous experiments (Tominaga et al., \emph{submitted}; Experiment 1).
+We selected stimuli from our previous experiments (Tominaga et al., \emph{submitted}).
 Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files.
@@
 
-For the current experiment, 96 performances were chosen from the valid performances in Tominaga et al.~(\emph{submitted}).
+For the current experiment, 96 performances were chosen from the valid performances in Tominaga et al.~(\emph{submitted}; Experiment 1).
 We randomly sampled 24 articulation performances and 24 dynamics performances from the teaching condition as well as 24 articulation performances and 24 dynamics performances from the performing condition.
@@
 Statistical model assumptions were tested using the \emph{performance} R package (Lüdecke, Ben-Shachar, Patil, Waggoner, \& Makowski, 2021) and all assumptions were met.
-Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique, we reported four regression models for each subcomponent (see details in \emph{\protect\hyperlink{dataanalysis}{Data analysis}}).
+Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separateregression models for each subcomponent (see details in \emph{Data analysis}).
 
@@
 
-The experimental setting and procedure were identical to Experiment 1 except that each block consisted of 4 practice trials and 36 experimental trials.
+The apparatus and procedure were identical to Experiment 1 except that each block consisted of 4 practice trials and 36 experimental trials.
 The number of trials was reduced due to the time constraint of the experiment.
@@
 
-As Experiment 1, stimuli were produced by actual pianists on a weighed Yamaha MIDI digital piano and recorded as MIDI files.
-One piece of music was selected as a base piece, which was performed with a musical expressive technique of either articulation (\emph{Figure \ref{fig:stim2}}, A) or dynamics (\emph{Figure \ref{fig:stim2}}, B).
+As Experiment 1, we selected stimuli from our previous experiments (Tominaga et al., \emph{submitted}).
 The excerpt was taken from ``Sonatina Op.36 (No.3) in C major'' by Muzio Clementi and modified for the experiment.
+The excerpt was performed with either articulation (\emph{Figure \ref{fig:stim2}}, A) or dynamics (\emph{Figure \ref{fig:stim2}}, B).
 The stimuli were performed around 100 - 120 quarter-beats per minute (i.e., around 250 - 300 ms for 8th-note IOIs).
 
-Recorded piano performances for the stimuli were obtained from our previous experiments (Tominaga et al., \emph{in prep}).
-Half of the stimuli (36 recordings) was randomly chosen from 248 valid performances in the teaching condition whereas the other half (36 recordings) was randomly chosen from 256 valid performances in the performing condition.
+For the current experiment, 96 performances were chosen from the valid performances in Tominaga et al.~(\emph{submitted}; Experiment 2).
+There were 248 valid performances in the teaching condition and 256 valid performances in the performing condition.
+We randomly sampled 18 articulation performances and 18 dynamics performances from the teaching condition as well as 18 articulation performances and 18 dynamics performances from the performing condition.
 In total, 72 recordings were selected as stimuli for the current experiment.
-Again, it is important to note that each recording from the teaching condition did not necessarily exhibit specific features of teaching performances that we found in the previous experiments since we randomly sampled recordings.
+Again, it is important to note that each performance from the teaching condition did not necessarily exhibit specific features of teaching that we found in the previous experiments (e.g., exaggeration) since we randomly sampled the performances.
 
@@
 
-As Experiment 1, stimuli were quantified with regard to tempo (IOIs), articulation (KOT), dynamics (KV) and dynamics contrast (KV-Diff).
+The data analysis was identical to Experiment 1.
 Only the 8th notes with expressive notations were included for data analysis.
-We did not run any statistical analysis for Experiment 2.
+As a result, only one 8th note in the 4th measure without any expression was not included.
 
@@
 
-\hypertarget{scatter-plots}{%
-\subsection{Scatter plots}\label{scatter-plots}}
+All results were reported as significant at \emph{p} \textless{} 0.05.
+
+\hypertarget{correlation-1}{%
+\subsection{Correlation}\label{correlation-1}}
+
+As Experiment 1, a Pearson product-moment correlation coefficient was computed by default for correlation analysis and a Spearman's rank correlation coefficient was additionally computed if normality assumption was violated based on the Shapiro-Wilk normality test.
 
@@
 
-As Experiment 1, it seems that performance tempi (IOIs) are correlated with participants' judgments as teaching.
-Slower performances were more likely to be judged as teaching.
-However, the slope of articulation seems to be less steep than that of Experiment 1 (\emph{Figure \ref{fig:ioi-2}}).
+Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; \emph{r} = .25, \emph{p} = 0.147, Dynamics; \emph{r} = .39, \emph{p} = 0.019, \emph{Figure \ref{fig:ioi-2}}).
+
+The Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (\emph{p} = 0.080).
+A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (\emph{r} = .29, \emph{p} = 0.091).
 
@@
 
-Unlike Experiment 1, there seems to be no relationship between KOT values and participants' judgments as teaching.
-The scatter plot suggests that participants did not use articulation values to infer teaching intentions (\emph{Figure \ref{fig:kot-2}}).
+Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; \emph{r} = -.15, \emph{p} = 0.390, Staccato; \emph{r} = -.03, \emph{p} = 0.880, \emph{Figure \ref{fig:kot-2}}, left).
+
+For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (\emph{r} = -.11, \emph{p} = 0.52).
+However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r} = -.35, \emph{p} = 0.03), suggesting that performances with louder staccato were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).
 
@@
 
-As Experiment 1, there seems to be a relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-2}}).
-Performances with louder forte adn softer piano seem to be judged as teaching.
+As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-2}}, right).
+Specifically, performances with louder forte (\emph{r} = .45, \emph{p} = 0.007) and softer piano (\emph{r} = -.45, \emph{p} = 0.01) were more likely to be judged as teaching.
+
+The Shapiro-Wilk normality test revealed that the distribution of KV values for dynamics recordings was not normally distributed (Forte; \emph{p} = 0.048, Piano' \emph{p} = 0.004).
+Spearman's rank correlation coefficient also confirmed that performances with louder forte (\emph{r} = .43, \emph{p} = 0.010) and softer piano (\emph{r} = -.45, \emph{p} = 0.01) were more likely to be judged as teaching.
+
+For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r} = .08, \emph{p} = 0.63, Staccato; \emph{r} = .21, \emph{p} = 0.22, \emph{Figure \ref{fig:vel-2}}, left).
 
@@
 
-As Experiment 1, there seems to be a relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-diff-2}}).
-Performances with larger contrasts between forte and piano seem to be judged as teaching.
+As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (\emph{Figure \ref{fig:vel-diff-2}}, right).
+Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r} = -.75, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r} = .59, \emph{p} \textless{} 0.001).
+
+The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; \emph{p} = 0.850, Piano to Forte; \emph{p} = 0.008).
+Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; \emph{r} = -.73, \emph{p} \textless{} 0.001, Piano to Forte; \emph{r} = .59, \emph{p} \textless{} 0.001).
+
+\hypertarget{multiple-regression-1}{%
+\subsection{Multiple regression}\label{multiple-regression-1}}
+
+As Experiment 1, we performed multiple regression analyses to further explore which feature of performance contributed the most to participants' judgments as teaching.
+Again, since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in \emph{Data analysis} in Experiment 1).
+
+\hypertarget{legato-1}{%
+\subsubsection{Legato}\label{legato-1}}
+
+A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
+The result of the regression indicated that the model explained 19.77 \% of the variance (\emph{F}(4, 31) = 3.20, \emph{p} = 0.03).
+It was found that tempo (IOIs; \emph{\(\beta\)} = 0.58, \emph{p} = 0.011), dynamics (KV) and dynamics contrast (KV-Diff) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
+However, articulation (KOT; \emph{\(\beta\)} = -0.08, \emph{p} = 0.466) for the legato parts was not a significant predictor as opposed to Experiment 1.
+
+\hypertarget{staccato-1}{%
+\subsubsection{Staccato}\label{staccato-1}}
+
+A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato).
+The overall was not statistically significant (\(R^{2}\) = 12.28, \emph{F}(4, 31) = 2.20, \emph{p} = 0.09).
+
+\hypertarget{forte-1}{%
+\subsubsection{Forte}\label{forte-1}}
+
+A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano).
+The result of the regression indicated that the model explained 60.69 \% of the variance (\emph{F}(4, 31) = 14.50, \emph{p} \textless{} 0.001).
+It was found that dynamics contrast from forte to piano (KV-Diff; \emph{\(\beta\)} = -1.64, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.
+
+\hypertarget{piano-1}{%
+\subsubsection{Piano}\label{piano-1}}
+
+A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte).
+The result of the regression indicated that the model explained 49.49 \% of the variance (\emph{F}(4, 31) = 9.60, \emph{p} \textless{} 0.001).
+It was found that tempo (IOIs; \emph{\(\beta\)} = 0.55, \emph{p} = 0.022) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 1.09, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.
 
@@
 
-Experiment 2 aims to replicate our previous findings in Experiment 1 with a more naturalistic piece of music.
-The preliminary data suggest that some features of piano performance contributes to participant' judgments as teaching.
-For instance, performances with slower tempo were likely to be judged as teaching regardless which expressive technique was implemented.
-Also, performances with louder forte and softer piano were likely to be judged as teaching for dynamics recordings.
+Experiment 2 aimed to replicate our previous findings in Experiment 1 with a more naturalistic piece of music.
+We successfully replicated the findings from Experiment 1 in dynamics features.
+Performances with louder forte and softer piano were likely to be judged as teaching for dynamics recordings.
 Moreover, there seems to be a strong relationship between dynamics contrast between forte and piano and participants' judgments as teaching.
 
-However, it seems there was no relationship between articulation values and participants' judgments as teaching.
+However, we failed to replicate the results in terms of tempo (IOIs) and articulation (KOT).
 Compared with Experiment 1, the piece used in Experiment 2 was musically much complex.

### 2022-02-01 paper/manuscript.Rmd
update abstract
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 For example, pianists played slower and exaggerated each technique when they had an intention to teach.
-In order to achieve successful skill transmission, it is vital to examine whether such sound modulations are identified and used to infer teaching intentions by novices, who are going to acquire skills.
-The current experiments investigated which features of piano performance make musicians (in the role of potential learners) infer teaching intentions.
-Musicians listened to a number of piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
-Musicians were asked to judge whether each performance was produced in order to teach the designated expressive technique.
+Here we investigated whether the modulations that expert pianists produce when they intend to teach are also perceived by listeners as conveying pedagogical intentions.
+In the current study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
+They were asked to judge whether each performance was produced to teach the designated expressive technique or not.
 We quantified recordings with regard to tempo, articulation and dynamics.
-Overall, slower tempo contributed to musicians’ judgments as teaching.
-Moreover, performances with exaggeration for each technique (e.g., shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching.
-These performance features are consistent with expert pianists’ sound modulations for teaching purposes.
-Therefore, musicians (in the role of potential learners) seem to be able to identify didactic sound modulations, only by listening to recorded performances.
+We performed correlation and regression analysis to investigate which features of piano performance make musicians infer teaching intention.
+The findings in Experiment 1 with a simple musical scales demonstrated that slower tempo contributed to musicians’ judgments as teaching regardless of the techniques.
+Moreover, performances with exaggeration for each technique (e.g., longer legato, shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching.
+We run Experiment 2 with a more naturalistic piece to replicate the findings of Experiment 1.
+We only replicated the findings related to dynamics (e.g., larger contrast between forte and piano).
+Taken together, dynamics features of piano performance were more reliably perceived by musicians to infer pedagogical intentions.
 
@@
 
-Tominaga, Knoblich & Sebanz (*in prep*) extended this line of research to expertise transmission where skills to be acquired are much more complicated than general knowledge, which is mostly acquired throughout development [e.g., @csibra_2009].
+Tominaga, Knoblich & Sebanz (*submitted*) extended this line of research to expertise transmission where skills to be acquired are much more complicated than general knowledge, which is mostly acquired throughout development [e.g., @csibra_2009].
 Expertise usually demands an enormous amount of practice to acquire so that only experts can accomplish a higher level of performance including artistic expression.

### 2022-02-01 paper/manuscript.tex
update abstract
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 For example, pianists played slower and exaggerated each technique when they had an intention to teach.
-In order to achieve successful skill transmission, it is vital to examine whether such sound modulations are identified and used to infer teaching intentions by novices, who are going to acquire skills.
-The current experiments investigated which features of piano performance make musicians (in the role of potential learners) infer teaching intentions.
-Musicians listened to a number of piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
-Musicians were asked to judge whether each performance was produced in order to teach the designated expressive technique.
+Here we investigated whether the modulations that expert pianists produce when they intend to teach are also perceived by listeners as conveying pedagogical intentions.
+In the current study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
+They were asked to judge whether each performance was produced to teach the designated expressive technique or not.
 We quantified recordings with regard to tempo, articulation and dynamics.
-Overall, slower tempo contributed to musicians' judgments as teaching.
-Moreover, performances with exaggeration for each technique (e.g., shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching.
-These performance features are consistent with expert pianists' sound modulations for teaching purposes.
-Therefore, musicians (in the role of potential learners) seem to be able to identify didactic sound modulations, only by listening to recorded performances.
+We performed correlation and regression analysis to investigate which features of piano performance make musicians infer teaching intention.
+The findings in Experiment 1 with a simple musical scales demonstrated that slower tempo contributed to musicians' judgments as teaching regardless of the techniques.
+Moreover, performances with exaggeration for each technique (e.g., longer legato, shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching.
+We run Experiment 2 with a more naturalistic piece to replicate the findings of Experiment 1.
+We only replicated the findings related to dynamics (e.g., larger contrast between forte and piano).
+Taken together, dynamics features of piano performance were more reliably perceived by musicians to infer pedagogical intentions.
 }
@@
 
-Tominaga, Knoblich \& Sebanz (\emph{in prep}) extended this line of research to expertise transmission where skills to be acquired are much more complicated than general knowledge, which is mostly acquired throughout development (e.g., Csibra \& Gergely, 2009).
+Tominaga, Knoblich \& Sebanz (\emph{submitted}) extended this line of research to expertise transmission where skills to be acquired are much more complicated than general knowledge, which is mostly acquired throughout development (e.g., Csibra \& Gergely, 2009).
 Expertise usually demands an enormous amount of practice to acquire so that only experts can accomplish a higher level of performance including artistic expression.

### 2022-02-02 paper/manuscript.Rmd
added dfs for correlation analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ### Tempo (IOIs)
-Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_art$p.value))}`, Dynamics; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-1}*).
+Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_art$p.value))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-1}*).
 Participants tended to identify slower performances as teaching.
@@
 Therefore, a Spearman's rank correlation coefficient was additionally used to assess the relationship between performance tempi of dynamics recordings and participants' judgments.
-The result failed to reach significance (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`), suggesting that we need to be careful about the interpretation of the relationship between performance tempi of dynamics recordings and participants' judgments as teaching.
+The result failed to reach significance (*r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`), suggesting that we need to be careful about the interpretation of the relationship between performance tempi of dynamics recordings and participants' judgments as teaching.
 
@@
 For articulation recordings, there was a significant relationship between KOT values and participants' judgments as teaching (*Figure \ref{fig:kot-1}*, left).
-Specifically, performances with shorter staccato (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`) and longer legato (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_leg$p.value))}`) were more likely to be judged as teaching.
+Specifically, performances with shorter staccato (*r(`r cor_kot_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`) and longer legato (*r(`r cor_kot_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_leg$p.value))}`) were more likely to be judged as teaching.
 
-For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`, Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`, *Figure \ref{fig:kot-1}*, right).
+For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`, Piano; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`, *Figure \ref{fig:kot-1}*, right).
 
 The Shapiro-Wilk normality test revealed that the distribution of KOT for dynamics recordings was not normally distributed (Forte; *p* `r if(kot_for_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', kot_for_norm_performance$p.value))}`, Piano; *p* `r if(kot_pia_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', kot_pia_norm_performance$p.value))}`).
-Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for_spearman$estimate))`, *p* `r if(cor_kot_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for_spearman$p.value))}`, Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia_spearman$estimate))`, *p* `r if(cor_kot_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia_spearman$p.value))}`).
+Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for_spearman$estimate))`, *p* `r if(cor_kot_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for_spearman$p.value))}`, Piano; *r(`r cor_kot_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia_spearman$estimate))`, *p* `r if(cor_kot_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia_spearman$p.value))}`).
 
@@
 For dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-1}*, right).
-Specifically, performances with louder forte were more likely to be judged as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`).
-However, there was no significant relationship between KV values for piano and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia$p.value))}`).
+Specifically, performances with louder forte were more likely to be judged as teaching (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`).
+However, there was no significant relationship between KV values for piano and participants' judgments as teaching (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia$p.value))}`).
 
-For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-1}*, left).
+For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r(`r cor_vel_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-1}*, left).
 
 The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings for legato was not normally distributed (;*p* `r if(vel_leg_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_leg_norm_performance$p.value))}`).
-A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg_spearman$estimate))`, *p* `r if(cor_vel_leg_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg_spearman$p.value))}`).
+A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg_spearman$estimate))`, *p* `r if(cor_vel_leg_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg_spearman$p.value))}`).
 
@@
 For dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (*Figure \ref{fig:vel-diff-1}*, right).
-Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).
+Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).
 
-For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ltos$p.value))}`, From Staccato to Legato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_stol$p.value))}`, *Figure \ref{fig:vel-diff-1}*, left).
+For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ltos$p.value))}`, From Staccato to Legato; *r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_stol$p.value))}`, *Figure \ref{fig:vel-diff-1}*, left).
 
 The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings for transition points from legato to staccato was not normally distributed (;*p* `r if(vel_diff_ltos_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ltos_norm_performance$p.value))}`).
-A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos_spearman$estimate))`, *p* `r if(cor_vel_diff_ltos_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ltos_spearman$p.value))}`).
+A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos_spearman$estimate))`, *p* `r if(cor_vel_diff_ltos_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ltos_spearman$p.value))}`).
 
@@
 ### Tempo (IOIs)
-Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_art$p.value))}`, Dynamics; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-2}*).
+Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_art$p.value))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-2}*).
 
 The Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (*p* `r if(ioi_dyn_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_dyn_norm_performance$p.value))}`).
-A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`).
+A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (*r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`).
 
@@
 ### Articulation (KOT)
-Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`, Staccato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_leg$p.value))}`, *Figure \ref{fig:kot-2}*, left).
+Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; *r(`r cor_kot_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`, Staccato; *r(`r cor_kot_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`, *Figure \ref{fig:kot-2}*, left).
 
-For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`).
-However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`), suggesting that performances with louder staccato were more likely to be considered as teaching performance (*Figure \ref{fig:kot-2}*, right).
+For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (*r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`).
+However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (*r(`r cor_kot_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`), suggesting that performances with louder staccato were more likely to be considered as teaching performance (*Figure \ref{fig:kot-2}*, right).
 
@@
 As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-2}*, right).
-Specifically, performances with louder forte (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`) and softer piano (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia$p.value))}`) were more likely to be judged as teaching.
+Specifically, performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia$p.value))}`) were more likely to be judged as teaching.
 
 The Shapiro-Wilk normality test revealed that the distribution of KV values for dynamics recordings was not normally distributed (Forte; *p* `r if(vel_for_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_for_norm_performance$p.value))}`, Piano' *p* `r if(vel_pia_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_pia_norm_performance$p.value))}`).
-Spearman's rank correlation coefficient also confirmed that performances with louder forte (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for_spearman$estimate))`, *p* `r if(cor_vel_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for_spearman$p.value))}`) and softer piano (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia_spearman$p.value))}`) were more likely to be judged as teaching.
+Spearman's rank correlation coefficient also confirmed that performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for_spearman$estimate))`, *p* `r if(cor_vel_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for_spearman$p.value))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia_spearman$p.value))}`) were more likely to be judged as teaching.
 
-For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-2}*, left).
+For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r(`r cor_vel_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-2}*, left).
 
@@
 As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (*Figure \ref{fig:vel-diff-2}*, right).
-Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).
+Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).
 
 The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; *p* `r if(vel_diff_ftop_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ftop_norm_performance$p.value))}`, Piano to Forte; *p* `r if(vel_diff_ptof_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ptof_norm_performance$p.value))}`).
-Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop_spearman$estimate))`, *p* `r if(cor_vel_diff_ftop_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop_spearman$p.value))}`, Piano to Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ptof_spearman$p.value))}`).
+Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop_spearman$estimate))`, *p* `r if(cor_vel_diff_ftop_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop_spearman$p.value))}`, Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ptof_spearman$p.value))}`).
 

### 2022-02-02 paper/manuscript.tex
added dfs for correlation analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; \emph{r} = .77, \emph{p} \textless{} 0.001, Dynamics; \emph{r} = .42, \emph{p} = 0.003, \emph{Figure \ref{fig:ioi-1}}).
+Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; \emph{r(46)} = .77, \emph{p} \textless{} 0.001, Dynamics; \emph{r(46)} = .42, \emph{p} = 0.003, \emph{Figure \ref{fig:ioi-1}}).
 Participants tended to identify slower performances as teaching.
@@
 Therefore, a Spearman's rank correlation coefficient was additionally used to assess the relationship between performance tempi of dynamics recordings and participants' judgments.
-The result failed to reach significance (\emph{r} = .27, \emph{p} = 0.066), suggesting that we need to be careful about the interpretation of the relationship between performance tempi of dynamics recordings and participants' judgments as teaching.
+The result failed to reach significance (\emph{r(46)} = .27, \emph{p} = 0.066), suggesting that we need to be careful about the interpretation of the relationship between performance tempi of dynamics recordings and participants' judgments as teaching.
 
@@
 For articulation recordings, there was a significant relationship between KOT values and participants' judgments as teaching (\emph{Figure \ref{fig:kot-1}}, left).
-Specifically, performances with shorter staccato (\emph{r} = -.73, \emph{p} \textless{} 0.001) and longer legato (\emph{r} = .40, \emph{p} = 0.005) were more likely to be judged as teaching.
+Specifically, performances with shorter staccato (\emph{r(46)} = -.73, \emph{p} \textless{} 0.001) and longer legato (\emph{r(46)} = .40, \emph{p} = 0.005) were more likely to be judged as teaching.
 
-For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r} = -.04, \emph{p} = 0.81, Piano; \emph{r} = -.19, \emph{p} = 0.19, \emph{Figure \ref{fig:kot-1}}, right).
+For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r(46)} = -.04, \emph{p} = 0.81, Piano; \emph{r(46)} = -.19, \emph{p} = 0.19, \emph{Figure \ref{fig:kot-1}}, right).
 
 The Shapiro-Wilk normality test revealed that the distribution of KOT for dynamics recordings was not normally distributed (Forte; \emph{p} \textless{} 0.001, Piano; \emph{p} \textless{} 0.001).
-Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r} = .15, \emph{p} = 0.31, Piano; \emph{r} = -.12, \emph{p} = 0.43).
+Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r(46)} = .15, \emph{p} = 0.31, Piano; \emph{r(46)} = -.12, \emph{p} = 0.43).
 
@@
 For dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-1}}, right).
-Specifically, performances with louder forte were more likely to be judged as teaching (\emph{r} = .45, \emph{p} = 0.001).
-However, there was no significant relationship between KV values for piano and participants' judgments as teaching (\emph{r} = -.22, \emph{p} = 0.13).
+Specifically, performances with louder forte were more likely to be judged as teaching (\emph{r(46)} = .45, \emph{p} = 0.001).
+However, there was no significant relationship between KV values for piano and participants' judgments as teaching (\emph{r(46)} = -.22, \emph{p} = 0.13).
 
-For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r} = .10, \emph{p} = 0.52, Staccato; \emph{r} = -.02, \emph{p} = 0.87, \emph{Figure \ref{fig:vel-1}}, left).
+For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r(46)} = .10, \emph{p} = 0.52, Staccato; \emph{r(46)} = -.02, \emph{p} = 0.87, \emph{Figure \ref{fig:vel-1}}, left).
 
 The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings for legato was not normally distributed (;\emph{p} = 0.002).
-A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r} = .03, \emph{p} = 0.84).
+A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r(46)} = .03, \emph{p} = 0.84).
 
@@
 For dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (\emph{Figure \ref{fig:vel-diff-1}}, right).
-Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r} = -.50, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r} = .62, \emph{p} \textless{} 0.001).
+Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r(46)} = -.50, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r(46)} = .62, \emph{p} \textless{} 0.001).
 
-For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r} = -.26, \emph{p} = 0.071, From Staccato to Legato; \emph{r} = -.19, \emph{p} = 0.21, \emph{Figure \ref{fig:vel-diff-1}}, left).
+For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r(46)} = -.26, \emph{p} = 0.071, From Staccato to Legato; \emph{r(46)} = -.19, \emph{p} = 0.21, \emph{Figure \ref{fig:vel-diff-1}}, left).
 
 The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings for transition points from legato to staccato was not normally distributed (;\emph{p} = 0.007).
-A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r} = -.23, \emph{p} = 0.12).
+A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r(46)} = -.23, \emph{p} = 0.12).
 
@@
 
-Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; \emph{r} = .25, \emph{p} = 0.147, Dynamics; \emph{r} = .39, \emph{p} = 0.019, \emph{Figure \ref{fig:ioi-2}}).
+Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; \emph{r(34)} = .25, \emph{p} = 0.147, Dynamics; \emph{r(34)} = .39, \emph{p} = 0.019, \emph{Figure \ref{fig:ioi-2}}).
 
 The Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (\emph{p} = 0.080).
-A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (\emph{r} = .29, \emph{p} = 0.091).
+A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (\emph{r(34)} = .29, \emph{p} = 0.091).
 
@@
 
-Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; \emph{r} = -.15, \emph{p} = 0.390, Staccato; \emph{r} = -.03, \emph{p} = 0.880, \emph{Figure \ref{fig:kot-2}}, left).
+Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; \emph{r(34)} = -.03, \emph{p} = 0.390, Staccato; \emph{r(34)} = -.15, \emph{p} = 0.390, \emph{Figure \ref{fig:kot-2}}, left).
 
-For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (\emph{r} = -.11, \emph{p} = 0.52).
-However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r} = -.35, \emph{p} = 0.03), suggesting that performances with louder staccato were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).
+For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (\emph{r(34)} = -.11, \emph{p} = 0.52).
+However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r(34)} = -.35, \emph{p} = 0.03), suggesting that performances with louder staccato were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).
 
@@
 As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-2}}, right).
-Specifically, performances with louder forte (\emph{r} = .45, \emph{p} = 0.007) and softer piano (\emph{r} = -.45, \emph{p} = 0.01) were more likely to be judged as teaching.
+Specifically, performances with louder forte (\emph{r(34)} = .45, \emph{p} = 0.007) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.01) were more likely to be judged as teaching.
 
 The Shapiro-Wilk normality test revealed that the distribution of KV values for dynamics recordings was not normally distributed (Forte; \emph{p} = 0.048, Piano' \emph{p} = 0.004).
-Spearman's rank correlation coefficient also confirmed that performances with louder forte (\emph{r} = .43, \emph{p} = 0.010) and softer piano (\emph{r} = -.45, \emph{p} = 0.01) were more likely to be judged as teaching.
+Spearman's rank correlation coefficient also confirmed that performances with louder forte (\emph{r(34)} = .43, \emph{p} = 0.010) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.01) were more likely to be judged as teaching.
 
-For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r} = .08, \emph{p} = 0.63, Staccato; \emph{r} = .21, \emph{p} = 0.22, \emph{Figure \ref{fig:vel-2}}, left).
+For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r(34)} = .08, \emph{p} = 0.63, Staccato; \emph{r(34)} = .21, \emph{p} = 0.22, \emph{Figure \ref{fig:vel-2}}, left).
 
@@
 As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (\emph{Figure \ref{fig:vel-diff-2}}, right).
-Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r} = -.75, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r} = .59, \emph{p} \textless{} 0.001).
+Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r(34)} = -.75, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r(34)} = .59, \emph{p} \textless{} 0.001).
 
 The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; \emph{p} = 0.850, Piano to Forte; \emph{p} = 0.008).
-Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; \emph{r} = -.73, \emph{p} \textless{} 0.001, Piano to Forte; \emph{r} = .59, \emph{p} \textless{} 0.001).
+Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; \emph{r(34)} = -.73, \emph{p} \textless{} 0.001, Piano to Forte; \emph{r(34)} = .59, \emph{p} \textless{} 0.001).
 

### 2022-02-02 paper/manuscript.Rmd
update stats values
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`, Piano; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`, *Figure \ref{fig:kot-1}*, right).
-
 The Shapiro-Wilk normality test revealed that the distribution of KOT for dynamics recordings was not normally distributed (Forte; *p* `r if(kot_for_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', kot_for_norm_performance$p.value))}`, Piano; *p* `r if(kot_pia_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', kot_pia_norm_performance$p.value))}`).
@@
 For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r(`r cor_vel_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-1}*, left).
-
-The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings for legato was not normally distributed (;*p* `r if(vel_leg_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_leg_norm_performance$p.value))}`).
+The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings for legato was not normally distributed (*p* `r if(vel_leg_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_leg_norm_performance$p.value))}`).
 A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg_spearman$estimate))`, *p* `r if(cor_vel_leg_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg_spearman$p.value))}`).
@@
 For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ltos$p.value))}`, From Staccato to Legato; *r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_stol$p.value))}`, *Figure \ref{fig:vel-diff-1}*, left).
-
-The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings for transition points from legato to staccato was not normally distributed (;*p* `r if(vel_diff_ltos_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ltos_norm_performance$p.value))}`).
+The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings for transition points from legato to staccato was not normally distributed (*p* `r if(vel_diff_ltos_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ltos_norm_performance$p.value))}`).
 A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos_spearman$estimate))`, *p* `r if(cor_vel_diff_ltos_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ltos_spearman$p.value))}`).
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
-The result of the regression indicated that the model explained `r summary(m1)$adj.r.squared*100` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r round(summary(m1)$fstatistic[1], 1)`, *p* `r if(lmp(m1) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m1)))}`).
+The result of the regression indicated that the model explained `r summary(m1)$adj.r.squared*100` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r sprintf('%.1f', summary(m1)$fstatistic[1])`, *p* `r if(lmp(m1) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m1)))}`).
 It was found that tempo (IOIs; *$\beta$* = `r summary(m1)$coefficients[2]`, *p* `r if(summary(m1)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[2, 4]))}`) and articulation for the legato parts (KOT; *$\beta$* = `r summary(m1)$coefficients[3]`, *p* `r if(summary(m1)$coefficients[3, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[3, 4]))}`) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato).
-The result of the regression indicated that the model explained `r summary(m2)$adj.r.squared*100` % of the variance (*F*(`r summary(m2)$fstatistic[2]`, `r summary(m2)$fstatistic[3]`) = `r round(summary(m2)$fstatistic[1], 1)`, *p* `r if(lmp(m2) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m2)))}`).
+The result of the regression indicated that the model explained `r summary(m2)$adj.r.squared*100` % of the variance (*F*(`r summary(m2)$fstatistic[2]`, `r summary(m2)$fstatistic[3]`) = `r sprintf('%.1f', summary(m2)$fstatistic[1])`, *p* `r if(lmp(m2) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m2)))}`).
 It was found that tempo (IOIs; *$\beta$* = `r summary(m2)$coefficients[2]`, *p* `r if(summary(m2)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m2)$coefficients[2, 4]))}`) and articulation for the staccato parts (KOT; *$\beta$* = `r summary(m2)$coefficients[3]`, *p* `r if(summary(m2)$coefficients[3, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m2)$coefficients[3, 4]))}`) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano).
-The result of the regression indicated that the model explained `r summary(m3)$adj.r.squared*100` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r round(summary(m3)$fstatistic[1], 1)`, *p* `r if(lmp(m3) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m3)))}`).
+The result of the regression indicated that the model explained `r summary(m3)$adj.r.squared*100` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r sprintf('%.2f', summary(m3)$fstatistic[1])`, *p* `r if(lmp(m3) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m3)))}`).
 It was found that tempo (IOIs; *$\beta$* = `r summary(m3)$coefficients[2]`, *p* `r if(summary(m3)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m3)$coefficients[2, 4]))}`) and dynamics for the forte parts (KV; *$\beta$* = `r summary(m3)$coefficients[4]`, *p* `r if(summary(m3)$coefficients[4, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m3)$coefficients[4, 4]))}`) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte).
-The result of the regression indicated that the model explained `r summary(m4)$adj.r.squared*100` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r round(summary(m4)$fstatistic[1], 1)`, *p* `r if(lmp(m4) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m4)))}`).
+The result of the regression indicated that the model explained `r summary(m4)$adj.r.squared*100` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r sprintf('%.1f', summary(m4)$fstatistic[1])`, *p* `r if(lmp(m4) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m4)))}`).
 It was found that tempo (IOIs; *$\beta$* = `r summary(m4)$coefficients[2]`, *p* `r if(summary(m4)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[2, 4]))}`) and dynamics contrast from piano to forte (KV-Diff; *$\beta$* = `r summary(m4)$coefficients[5]`, *p* `r if(summary(m4)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[5, 4]))}`) were significant predictors of participants' judgments as teaching.
@@
 ### Tempo (IOIs)
-Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_art$p.value))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-2}*).
-
+Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_ioi_art$p.value))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-2}*).
 The Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (*p* `r if(ioi_dyn_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_dyn_norm_performance$p.value))}`).
@@
 ### Articulation (KOT)
-Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; *r(`r cor_kot_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`, Staccato; *r(`r cor_kot_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`, *Figure \ref{fig:kot-2}*, left).
+Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; *r(`r cor_kot_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_sta$p.value))}`, Staccato; *r(`r cor_kot_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_sta$p.value))}`, *Figure \ref{fig:kot-2}*, left).
 
 For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (*r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`).
-However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (*r(`r cor_kot_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`), suggesting that performances with louder staccato were more likely to be considered as teaching performance (*Figure \ref{fig:kot-2}*, right).
+However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (*r(`r cor_kot_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_pia$p.value))}`), suggesting that performances with louder staccato were more likely to be considered as teaching performance (*Figure \ref{fig:kot-2}*, right).
 
@@
 As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-2}*, right).
-Specifically, performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia$p.value))}`) were more likely to be judged as teaching.
-
+Specifically, performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_pia$p.value))}`) were more likely to be judged as teaching.
 The Shapiro-Wilk normality test revealed that the distribution of KV values for dynamics recordings was not normally distributed (Forte; *p* `r if(vel_for_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_for_norm_performance$p.value))}`, Piano' *p* `r if(vel_pia_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_pia_norm_performance$p.value))}`).
-Spearman's rank correlation coefficient also confirmed that performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for_spearman$estimate))`, *p* `r if(cor_vel_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for_spearman$p.value))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia_spearman$p.value))}`) were more likely to be judged as teaching.
+Spearman's rank correlation coefficient also confirmed that performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for_spearman$estimate))`, *p* `r if(cor_vel_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for_spearman$p.value))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_pia_spearman$p.value))}`) were more likely to be judged as teaching.
 
@@
 The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; *p* `r if(vel_diff_ftop_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ftop_norm_performance$p.value))}`, Piano to Forte; *p* `r if(vel_diff_ptof_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ptof_norm_performance$p.value))}`).
-Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop_spearman$estimate))`, *p* `r if(cor_vel_diff_ftop_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop_spearman$p.value))}`, Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ptof_spearman$p.value))}`).
+Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop_spearman$estimate))`, *p* `r if(cor_vel_diff_ftop_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop_spearman$p.value))}`, Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof_spearman$estimate))`, *p* `r if(cor_vel_diff_ptof_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ptof_spearman$p.value))}`).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
-The result of the regression indicated that the model explained `r summary(m1)$adj.r.squared*100` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r round(summary(m1)$fstatistic[1], 1)`, *p* `r if(lmp(m1) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m1)))}`).
-It was found that tempo (IOIs; *$\beta$* = `r summary(m1)$coefficients[2]`, *p* `r if(summary(m1)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[2, 4]))}`), dynamics (KV) and dynamics contrast (KV-Diff) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
-However, articulation (KOT; *$\beta$* = `r summary(m1)$coefficients[3]`, *p* `r if(summary(m1)$coefficients[3, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[3, 4]))}`) for the legato parts was not a significant predictor as opposed to Experiment 1.
+The result of the regression indicated that the model explained `r summary(m1)$adj.r.squared*100` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r sprintf('%.2f', summary(m1)$fstatistic[1])`, *p* `r if(lmp(m1) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', lmp(m1)))}`).
+It was found that tempo (IOIs; *$\beta$* = `r summary(m1)$coefficients[2]`, *p* `r if(summary(m1)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[2, 4]))}`), dynamics (KV; *$\beta$* = `r summary(m1)$coefficients[4]`, *p* `r if(summary(m1)$coefficients[4, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[4, 4]))}`) and dynamics contrast (KV-Diff; *$\beta$* = `r summary(m1)$coefficients[5]`, *p* `r if(summary(m1)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[5, 4]))}`) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
+However, articulation (KOT; *$\beta$* = `r summary(m1)$coefficients[3]`, *p* `r if(summary(m1)$coefficients[3, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', summary(m1)$coefficients[3, 4]))}`) for the legato parts was not a significant predictor as opposed to Experiment 1.
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato).
-The overall was not statistically significant ($R^{2}$ = `r summary(m2)$adj.r.squared*100`, *F*(`r summary(m2)$fstatistic[2]`, `r summary(m2)$fstatistic[3]`) = `r round(summary(m2)$fstatistic[1], 1)`, *p* `r if(lmp(m2) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m2)))}`).
+The overall model was not statistically significant ($R^{2}$ = `r sprintf('%.1f', summary(m2)$adj.r.squared*100)`, *F*(`r summary(m2)$fstatistic[2]`, `r summary(m2)$fstatistic[3]`) = `r sprintf('%.2f', summary(m2)$fstatistic[1])`, *p* `r if(lmp(m2) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m2)))}`).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano).
-The result of the regression indicated that the model explained `r summary(m3)$adj.r.squared*100` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r round(summary(m3)$fstatistic[1], 1)`, *p* `r if(lmp(m3) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m3)))}`).
+The result of the regression indicated that the model explained `r summary(m3)$adj.r.squared*100` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r sprintf('%.1f', summary(m3)$fstatistic[1])`, *p* `r if(lmp(m3) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m3)))}`).
 It was found that dynamics contrast from forte to piano (KV-Diff; *$\beta$* = `r summary(m3)$coefficients[5]`, *p* `r if(summary(m3)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m3)$coefficients[5, 4]))}`) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte).
-The result of the regression indicated that the model explained `r summary(m4)$adj.r.squared*100` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r round(summary(m4)$fstatistic[1], 1)`, *p* `r if(lmp(m4) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m4)))}`).
+The result of the regression indicated that the model explained `r summary(m4)$adj.r.squared*100` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r sprintf('%.2f', summary(m4)$fstatistic[1])`, *p* `r if(lmp(m4) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m4)))}`).
 It was found that tempo (IOIs; *$\beta$* = `r summary(m4)$coefficients[2]`, *p* `r if(summary(m4)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[2, 4]))}`) and dynamics contrast from piano to forte (KV-Diff; *$\beta$* = `r summary(m4)$coefficients[5]`, *p* `r if(summary(m4)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[5, 4]))}`) were significant predictors of participants' judgments as teaching.

### 2022-02-02 paper/manuscript.tex
update stats values
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r(46)} = -.04, \emph{p} = 0.81, Piano; \emph{r(46)} = -.19, \emph{p} = 0.19, \emph{Figure \ref{fig:kot-1}}, right).
-
 The Shapiro-Wilk normality test revealed that the distribution of KOT for dynamics recordings was not normally distributed (Forte; \emph{p} \textless{} 0.001, Piano; \emph{p} \textless{} 0.001).
@@
 For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r(46)} = .10, \emph{p} = 0.52, Staccato; \emph{r(46)} = -.02, \emph{p} = 0.87, \emph{Figure \ref{fig:vel-1}}, left).
-
-The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings for legato was not normally distributed (;\emph{p} = 0.002).
+The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings for legato was not normally distributed (\emph{p} = 0.002).
 A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r(46)} = .03, \emph{p} = 0.84).
@@
 For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r(46)} = -.26, \emph{p} = 0.071, From Staccato to Legato; \emph{r(46)} = -.19, \emph{p} = 0.21, \emph{Figure \ref{fig:vel-diff-1}}, left).
-
-The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings for transition points from legato to staccato was not normally distributed (;\emph{p} = 0.007).
+The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings for transition points from legato to staccato was not normally distributed (\emph{p} = 0.007).
 A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r(46)} = -.23, \emph{p} = 0.12).
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
-The result of the regression indicated that the model explained 64.63 \% of the variance (\emph{F}(4, 43) = 22.50, \emph{p} \textless{} 0.001).
+The result of the regression indicated that the model explained 64.63 \% of the variance (\emph{F}(4, 43) = 22.5, \emph{p} \textless{} 0.001).
 It was found that tempo (IOIs; \emph{\(\beta\)} = 0.78, \emph{p} \textless{} 0.001) and articulation for the legato parts (KOT; \emph{\(\beta\)} = 0.26, \emph{p} = 0.004) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato).
-The result of the regression indicated that the model explained 63.97 \% of the variance (\emph{F}(4, 43) = 21.90, \emph{p} \textless{} 0.001).
+The result of the regression indicated that the model explained 63.97 \% of the variance (\emph{F}(4, 43) = 21.9, \emph{p} \textless{} 0.001).
 It was found that tempo (IOIs; \emph{\(\beta\)} = 0.52, \emph{p} = 0.002) and articulation for the staccato parts (KOT; \emph{\(\beta\)} = -0.28, \emph{p} = 0.020) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano).
-The result of the regression indicated that the model explained 35.90 \% of the variance (\emph{F}(4, 43) = 7.60, \emph{p} \textless{} 0.001).
+The result of the regression indicated that the model explained 35.90 \% of the variance (\emph{F}(4, 43) = 7.58, \emph{p} \textless{} 0.001).
 It was found that tempo (IOIs; \emph{\(\beta\)} = 0.35, \emph{p} = 0.007) and dynamics for the forte parts (KV; \emph{\(\beta\)} = 0.73, \emph{p} = 0.048) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte).
-The result of the regression indicated that the model explained 51.21 \% of the variance (\emph{F}(4, 43) = 13.30, \emph{p} \textless{} 0.001).
+The result of the regression indicated that the model explained 51.21 \% of the variance (\emph{F}(4, 43) = 13.3, \emph{p} \textless{} 0.001).
 It was found that tempo (IOIs; \emph{\(\beta\)} = 0.38, \emph{p} \textless{} 0.001) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 0.99, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.
@@
 
-Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; \emph{r(34)} = .25, \emph{p} = 0.147, Dynamics; \emph{r(34)} = .39, \emph{p} = 0.019, \emph{Figure \ref{fig:ioi-2}}).
-
+Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; \emph{r(34)} = .25, \emph{p} = 0.15, Dynamics; \emph{r(34)} = .39, \emph{p} = 0.02, \emph{Figure \ref{fig:ioi-2}}).
 The Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (\emph{p} = 0.080).
@@
 
-Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; \emph{r(34)} = -.03, \emph{p} = 0.390, Staccato; \emph{r(34)} = -.15, \emph{p} = 0.390, \emph{Figure \ref{fig:kot-2}}, left).
+Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; \emph{r(34)} = -.03, \emph{p} = 0.39, Staccato; \emph{r(34)} = -.15, \emph{p} = 0.39, \emph{Figure \ref{fig:kot-2}}, left).
 
 For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (\emph{r(34)} = -.11, \emph{p} = 0.52).
-However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r(34)} = -.35, \emph{p} = 0.03), suggesting that performances with louder staccato were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).
+However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r(34)} = -.35, \emph{p} = 0.034), suggesting that performances with louder staccato were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).
 
@@
 As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-2}}, right).
-Specifically, performances with louder forte (\emph{r(34)} = .45, \emph{p} = 0.007) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.01) were more likely to be judged as teaching.
-
+Specifically, performances with louder forte (\emph{r(34)} = .45, \emph{p} = 0.007) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.006) were more likely to be judged as teaching.
 The Shapiro-Wilk normality test revealed that the distribution of KV values for dynamics recordings was not normally distributed (Forte; \emph{p} = 0.048, Piano' \emph{p} = 0.004).
-Spearman's rank correlation coefficient also confirmed that performances with louder forte (\emph{r(34)} = .43, \emph{p} = 0.010) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.01) were more likely to be judged as teaching.
+Spearman's rank correlation coefficient also confirmed that performances with louder forte (\emph{r(34)} = .43, \emph{p} = 0.010) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.013) were more likely to be judged as teaching.
 
@@
 The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; \emph{p} = 0.850, Piano to Forte; \emph{p} = 0.008).
-Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; \emph{r(34)} = -.73, \emph{p} \textless{} 0.001, Piano to Forte; \emph{r(34)} = .59, \emph{p} \textless{} 0.001).
+Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; \emph{r(34)} = -.73, \emph{p} \textless{} 0.001, Piano to Forte; \emph{r(34)} = .57, \emph{p} \textless{} 0.001).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
-The result of the regression indicated that the model explained 19.77 \% of the variance (\emph{F}(4, 31) = 3.20, \emph{p} = 0.03).
-It was found that tempo (IOIs; \emph{\(\beta\)} = 0.58, \emph{p} = 0.011), dynamics (KV) and dynamics contrast (KV-Diff) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
-However, articulation (KOT; \emph{\(\beta\)} = -0.08, \emph{p} = 0.466) for the legato parts was not a significant predictor as opposed to Experiment 1.
+The result of the regression indicated that the model explained 19.77 \% of the variance (\emph{F}(4, 31) = 3.16, \emph{p} = 0.028).
+It was found that tempo (IOIs; \emph{\(\beta\)} = 0.58, \emph{p} = 0.011), dynamics (KV; \emph{\(\beta\)} = 1.10, \emph{p} = 0.018) and dynamics contrast (KV-Diff; \emph{\(\beta\)} = 1.90, \emph{p} = 0.006) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
+However, articulation (KOT; \emph{\(\beta\)} = -0.08, \emph{p} = 0.47) for the legato parts was not a significant predictor as opposed to Experiment 1.
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato).
-The overall was not statistically significant (\(R^{2}\) = 12.28, \emph{F}(4, 31) = 2.20, \emph{p} = 0.09).
+The overall model was not statistically significant (\(R^{2}\) = 12.3, \emph{F}(4, 31) = 2.22, \emph{p} = 0.09).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano).
-The result of the regression indicated that the model explained 60.69 \% of the variance (\emph{F}(4, 31) = 14.50, \emph{p} \textless{} 0.001).
+The result of the regression indicated that the model explained 60.69 \% of the variance (\emph{F}(4, 31) = 14.5, \emph{p} \textless{} 0.001).
 It was found that dynamics contrast from forte to piano (KV-Diff; \emph{\(\beta\)} = -1.64, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte).
-The result of the regression indicated that the model explained 49.49 \% of the variance (\emph{F}(4, 31) = 9.60, \emph{p} \textless{} 0.001).
+The result of the regression indicated that the model explained 49.49 \% of the variance (\emph{F}(4, 31) = 9.57, \emph{p} \textless{} 0.001).
 It was found that tempo (IOIs; \emph{\(\beta\)} = 0.55, \emph{p} = 0.022) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 1.09, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.

### 2022-02-02 experiment-1/analysis/analysis.Rmd
add some diagnosis for multi regression
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ## Articulation (***)
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 # normality check
@@
 ## Dynamics (**)
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 # normality check
@@
 ## Articulation (n.s.)
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 # normality check
@@
 ## Dynamics (n.s.)
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 # normality check
@@
 ## Legato (**)
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 # normality check
@@
 ## Staccato (***)
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 # normality check
@@
 ## Forte (n.s.)
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 # normality check
@@
 ## Piano (n.s.)
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 # normality check
@@
 ## Forte (***)
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 # normality check
@@
 ## Legato (n.s.)
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 # normality check
@@
 ## Staccato (n.s.)
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 # normality check
@@
 ## Forte to Piano (***)
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 # normality check
@@
 ## Piano to Forte (***)
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 # normality check
@@
 ## Legato to Staccato (n.s.)
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 # normality check
@@
 
-```{r kot-partial-leg, echo = TRUE}
+```{r kot-partial-leg, echo = FALSE}
 pcor.test(partial[Subcomponent == "Legato"]$KOT, partial[Subcomponent == "Legato"]$Teaching, partial[Subcomponent == "Legato", c("IOI", "KV", "KVDiff")])
@@
 
-```{r kot-partial-sta, echo = TRUE}
+```{r kot-partial-sta, echo = FALSE}
 pcor.test(partial[Subcomponent == "Staccato"]$KOT, partial[Subcomponent == "Staccato"]$Teaching, partial[Subcomponent == "Staccato", c("IOI", "KV", "KVDiff")])
@@
 
-```{r vel-partial-for, echo = TRUE}
+```{r vel-partial-for, echo = FALSE}
 pcor.test(partial[Subcomponent == "Forte"]$KV, partial[Subcomponent == "Forte"]$Teaching, partial[Subcomponent == "Forte", c("IOI", "KOT", "KVDiff")])
@@
 
-```{r vel-partial-pia, echo = TRUE}
+```{r vel-partial-pia, echo = FALSE}
 pcor.test(partial[Subcomponent == "Piano"]$KV, partial[Subcomponent == "Piano"]$Teaching, partial[Subcomponent == "Piano", c("IOI", "KOT", "KVDiff")])
@@
 
-```{r vel-diff-partial-ftop, echo = TRUE}
+```{r vel-diff-partial-ftop, echo = FALSE}
 pcor.test(partial[Subcomponent2 == "FtoP"]$KVDiff, partial[Subcomponent2 == "FtoP"]$Teaching, partial[Subcomponent2 == "FtoP", c("IOI", "KOT", "KV")])
@@
 
-```{r vel-diff-partial-ptof, echo = TRUE}
+```{r vel-diff-partial-ptof, echo = FALSE}
 pcor.test(partial[Subcomponent2 == "PtoF"]$KVDiff, partial[Subcomponent2 == "PtoF"]$Teaching, partial[Subcomponent2 == "PtoF", c("IOI", "KOT", "KV")])
@@
 ## Legato
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 m1 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Legato"])
@@
 
+### Collinearity
+```{r, echo = FALSE}
+check_collinearity(m1)
+```
+
+### Heteroscedacity
+```{r, echo = FALSE}
+check_heteroscedasticity(m1)
+```
+
+### Normality
+```{r, echo = FALSE}
+check_normality(m1)
+```
+
 ## Staccato
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 m2 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Staccato"])
@@
 
+### Collinearity
+```{r, echo = FALSE}
+check_collinearity(m2)
+```
+
+### Heteroscedacity
+```{r, echo = FALSE}
+check_heteroscedasticity(m2)
+```
+
+### Normality
+```{r, echo = FALSE}
+check_normality(m2)
+```
+
 ## Forte
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 m3 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Forte"])
@@
 
+### Collinearity
+```{r, echo = FALSE}
+check_collinearity(m3)
+```
+
+### Heteroscedacity
+```{r, echo = FALSE}
+check_heteroscedasticity(m3)
+```
+
+### Normality
+```{r, echo = FALSE}
+check_normality(m3)
+```
+
 ## Piano
-```{r, echo = TRUE}
+```{r, echo = FALSE}
 m4 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Piano"])
@@
 
+### Collinearity
+```{r, echo = FALSE}
+check_collinearity(m4)
+```
+
+### Heteroscedacity
+```{r, echo = FALSE}
+check_heteroscedasticity(m4)
+```
+
+### Normality
+```{r, echo = FALSE}
+check_normality(m4)
+```
+
 ```{r export, include = FALSE}

### 2022-02-02 experiment-2/analysis/analysis.Rmd
add some diagnosis for multi regression
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 if (!require("corrplot")) {install.packages("corrplot"); require("corrplot")}
-if (!require("qqplotr")) {install.packages("qqplotr"); require("qqplotr")}
 # stats

### 2022-02-02 experiment-1/analysis/analysis.R

@@ -160,7 +160,7 @@ ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
           xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
 
 
-## ---- echo = TRUE-------------------------------------------------------------
+## ---- echo = FALSE------------------------------------------------------------
 # normality check
 ioi_art_norm_teaching <- shapiro.test(ioi[Skill == "articulation"]$Teaching)
 ioi_art_norm_performance <- shapiro.test(ioi[Skill == "articulation"]$Mean)
@@ -177,7 +177,7 @@ cor_ioi_art <- cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "art
 cor_ioi_art
 
 
-## ---- echo = TRUE-------------------------------------------------------------
+## ---- echo = FALSE------------------------------------------------------------
 # normality check
 ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
 ioi_dyn_norm_performance <- shapiro.test(ioi[Skill == "dynamics"]$Mean)
@@ -212,7 +212,7 @@ ggscatter(ioi_tra, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line"
           xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
 
 
-## ---- echo = TRUE-------------------------------------------------------------
+## ---- echo = FALSE------------------------------------------------------------
 # normality check
 ioi_art_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
 ioi_art_tra_norm_performance <- shapiro.test(ioi_tra[Skill == "articulation"]$Mean)
@@ -228,7 +228,7 @@ ioi_art_tra_norm_performance
 cor.test(ioi_tra[Skill == "articulation"]$Teaching, ioi_tra[Skill == "articulation"]$Mean)
 
 
-## ---- echo = TRUE-------------------------------------------------------------
+## ---- echo = FALSE------------------------------------------------------------
 # normality check
[…]

### 2022-02-02 experiment-2/analysis/analysis.R

@@ -8,7 +8,6 @@ if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
 # plot
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
 if (!require("corrplot")) {install.packages("corrplot"); require("corrplot")}
-if (!require("qqplotr")) {install.packages("qqplotr"); require("qqplotr")}
 # stats
 if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
 if (!require("performance")) {install.packages("performance"); require("performance")}
@@ -763,28 +762,76 @@ corrplot.mixed(pcor(partial[Subcomponent2 == "PtoF", c("Teaching", "IOI", "KOT",
 pcor.test(partial[Subcomponent2 == "PtoF"]$KVDiff, partial[Subcomponent2 == "PtoF"]$Teaching, partial[Subcomponent2 == "PtoF", c("IOI", "KOT", "KV")])
 
 
-## ---- echo = TRUE-------------------------------------------------------------
+## ---- echo = FALSE------------------------------------------------------------
 m1 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Legato"])
 summary(m1)
 check_model(m1)
 
 
-## ---- echo = TRUE-------------------------------------------------------------
+## ---- echo = FALSE------------------------------------------------------------
+check_collinearity(m1)
+
+
+## ---- echo = FALSE------------------------------------------------------------
+check_heteroscedasticity(m1)
+
+
+## ---- echo = FALSE------------------------------------------------------------
+check_normality(m1)
+
+
+## ---- echo = FALSE------------------------------------------------------------
 m2 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Staccato"])
 summary(m2)
 check_model(m2)
 
 
-## ---- echo = TRUE-------------------------------------------------------------
+## ---- echo = FALSE------------------------------------------------------------
+check_collinearity(m2)
+
+
+## ---- echo = FALSE------------------------------------------------------------
+check_heteroscedasticity(m2)
+
+
+## ---- echo = FALSE------------------------------------------------------------
+check_normality(m2)
+
+
+## ---- echo = FALSE------------------------------------------------------------
 m3 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Forte"])
 summary(m3)
 check_model(m3)
 
 
[…]

### 2022-02-02 paper/manuscript.Rmd
first draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ---
-title             : "What makes listeners infer teaching intentions?"
-shorttitle        : "What makes listeners infer teaching intentions?"
+title             : "What makes musicians infer teaching intentions?"
+shorttitle        : "What makes musicians infer teaching intentions?"
 
@@
 abstract: |
-  Social learning plays an important role in human skill transmission.
-It has been known that experts tend to change their behaviour particularly for teaching purposes.
+  Perceiving pedagogical intentions is vital when learning skills from others.
 Our previous research demonstrated that expert pianists systematically modulated their sound so as to teach musical expressive techniques such as articulation and dynamics.
@@
 In the current study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
-They were asked to judge whether each performance was produced to teach the designated expressive technique or not.
+They were asked to judge whether each recording was produced to teach the designated expressive technique or not.
 We quantified recordings with regard to tempo, articulation and dynamics.
-We performed correlation and regression analysis to investigate which features of piano performance make musicians infer teaching intention.
-The findings in Experiment 1 with a simple musical scales demonstrated that slower tempo contributed to musicians’ judgments as teaching regardless of the techniques.
+We performed correlation and multiple regression analysis to investigate which features of piano performance made musicians infer teaching intention.
+The findings in Experiment 1 with a simple musical scale demonstrated that slower tempo contributed to musicians’ judgments as teaching regardless of the techniques.
 Moreover, performances with exaggeration for each technique (e.g., longer legato, shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching.
-We run Experiment 2 with a more naturalistic piece to replicate the findings of Experiment 1.
-We only replicated the findings related to dynamics (e.g., larger contrast between forte and piano).
-Taken together, dynamics features of piano performance were more reliably perceived by musicians to infer pedagogical intentions.
+Experiment 2 aimed to replicate the findings of Experiment 1 with a more naturalistic piece.
+We only replicated the findings related to dynamics (in particular, larger contrast between forte and piano).
+Taken together, loudness (dynamics) seems to be reliably used to infer teaching intentions regardless of the complexity of a musical piece.
+Also, typical pedagogical behaviour such as slowing down may not be necessarily perceived as teaching performance when learning complex skills such as artistic expression.
 
@@
 Also, some studies have revealed that even towards adult learners, people modulated their speech and action in the similar way as they did for infants [@mcellin_2017; @uther_2007].
-These findings suggest that there are general pedagogical behaviours such as slow demonstration and exaggeration of speech and action to send teaching intentions to learners.
+Moreover, @mcellin_2018 demonstrated that people could identify informative intentions such as acting with others or teaching by relying on specific kinematics cues (e.g., velocity profiles of movements).
+These findings suggest that experts modified their speech and action to send teaching intentions and that novices could successfully perceive the intentions.
 
-Tominaga, Knoblich & Sebanz (*submitted*) extended this line of research to expertise transmission where skills to be acquired are much more complicated than general knowledge, which is mostly acquired throughout development [e.g., @csibra_2009].
-Expertise usually demands an enormous amount of practice to acquire so that only experts can accomplish a higher level of performance including artistic expression.
+Tominaga, Knoblich & Sebanz (*submitted*) extended this line of research to expertise transmission where skills to be acquired are complex such as artistic expression.
 Based on the assumption that expert pianists are very good at controlling and modulating their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
@@
 
-In order to achieve successful skill transmission, it is necessary to investigate whether novice learners can identify teaching intentions produced by experts.
-A recent study by @mcellin_2018 demonstrated that people could identify informative intentions such as acting with others or teaching by relying on specific kinematics cues (e.g., velocity profiles of movements).
-Some research in the field of action expertise suggest that motor simulation (i.e., using one's own motor systems to simulate an action) plays a key role to understand observed actions.
+Furthermore, some research in the field of action expertise suggest that motor simulation (i.e., using one's own motor systems to simulate an action) plays a key role to understand observed actions.
 For example, expert basketball players were better at predicting the outcome of a free shot compared to expert observers (coaches or sports journalists) and novices [@aglioti_2008].
 Also, it was found that deceptive intentions of fake basketball passes were detected from non-verbal bodily cues only by expert basketball players [@sebanz_2009].
-Taken together, people seem to be able to infer informative intentions by observing actions and motor expertise may enable accurate action prediction.
+Taken together, people seem to be able to infer informative intentions by observing actions accurately if they have enough expertise to simulate the actions.
 
@@
 @repp_2004 also found that expert pianists could distinguish their own performance from others' performances by listening to recordings.
-These results suggest that musical expertise may be important to accurately identify and infer intentions by listening to recorded performances.
+These results suggest that musical expertise may enable people identify and infer intentions accurately by using their own motor resources.
 
-The current experiments investigate which features of piano performance make musicians (in the role of potential learners) infer teaching intentions, only by listening to recorded performances.
-We collected various piano recordings from our previous experiments (Tominaga et al., *in prep*).
-The obtained recordings consisted of two pieces (one was used for Experiment 1 and the other was used for Experiment 2 in the current paper).
-The two pieces were performed by various pianists multiple times, therefore the recordings contained many variations in terms of timing, articulation and dynamics.
-In the current experiments, we asked musically trained participants to judge which performance was performed for teaching purposes.
-If teachers' intentions are successfully communicated with learners, pedagogical behavioural features in our previous experiments such as slower demonstration and exaggerated performance should be identified and used to infer teaching intentions.
-In Experiment 1, we examined which features of piano performance were correlated with participants judgments as "teaching".
-Experiment 2 was conducted to replicate what we found in Experiment 1 with a more naturalistic piece of music.
+Here we investigated whether the modulations that expert pianists made when they intended to teach were also perceived by listeners as conveying pedagogical intentions.
+We quantified recordings with regard to tempo, articulation and dynamics and examined which features of piano performance made musicians infer teaching intentions.
+We performed correlation and multiple regression analysis to investigate relationships between performance features of a recording and how likely people think the recording was produced for teaching purposes.
+Various piano recordings were collected from our previous experiments (Tominaga et al., *submitted*).
+The recordings were performed by various pianists multiple times, therefore the recordings contained many variations in terms of timing, articulation and dynamics.
+In the current study, we asked musically trained participants to judge which each recording was performed for teaching purposes.
+If performers' intentions are successfully communicated with learners, pedagogical behavioural features in our previous experiments such as slower demonstration and exaggerated performance should be identified and used to infer teaching intentions.
+We examined which features of piano performance were correlated with participants judgments as "teaching".
+We conducted Experiment 1 with a simple musical scale and Experiment 2 with a more naturalistic piece of music to replicate the findings from Experiment 1.
 
@@
 One participant was excluded due to an experimental error.
-Therefore, `r nrow(dt_included)` participants (Female: `r nrow(dt_included[Gender == "Female"])`) were included for data analysis and had `r round(mean(dt_included$Training), 2)` years of musical training on average (*SD* = `r round(sd(dt_included$Training), 2)`).
-They were all right-handed with a mean age of `r round(mean(dt_included$Age), 2)` (*SD* = `r round(sd(dt_included$Age), 2)`).
+Therefore, `r nrow(dt_included)` participants (Female: `r nrow(dt_included[Gender == "Female"])`) were included for data analysis and had `r sprintf('%.1f', mean(dt_included$Training))` years of musical training on average (*SD* = `r round(sd(dt_included$Training), 2)`).
+They were all right-handed with a mean age of `r sprintf('%.1f', mean(dt_included$Age))` (*SD* = `r round(sd(dt_included$Age), 2)`).
 All participants were recruited through an online participant platform (SONA system, https://www.sona-systems.com).
@@
 In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert).
-In total, we obtained 453 valid performances (i.e., performances without any pitch error) from the teaching condition and 436 valid performances from the performing condition.
+In total, we obtained 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition.
 
-For the current experiment, 96 performances were chosen from the valid performances in Tominaga et al.
+For the current experiment, 96 recordings were chosen from the valid performances in Tominaga et al.
 (*submitted*; Experiment 1).
-We randomly sampled 24 articulation performances and 24 dynamics performances from the teaching condition as well as 24 articulation performances and 24 dynamics performances from the performing condition.
-It is important to note that the performances from the teaching condition did not necessarily exhibit specific features of teaching that we found in our previous experiments (e.g., exaggeration) since we randomly sampled the performances.
+We randomly sampled 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition.
+It is important to note that the recordings from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments (e.g., exaggeration) since we randomly sampled the performances.
 
@@
 In the experiment, all instructions were displayed on a computer screen in front of the participants and an experimenter also explained the procedure.
-Participants were instructed that they were going to listen to piano recordings with musical expression (either articulation or dynamics), which were either produced as if a pianist were teaching the expression to students (e.g., in a lesson; teaching) or as if a pianist were performing it to an audience (e.g., in a concert; performing).
+Participants were instructed that they were going to listen to piano recordings with one musical expressive technique of either articulation or dynamics, which were either produced as if a pianist were teaching the designated expressive technique to students (e.g., in a lesson) or as if a pianist were performing it to an audience (e.g., in a concert).
 In each trial, participants listened to one recording and were asked whether the recording was produced for teaching purposes or not.
-Participants responded by pressing either a yes (for teaching; left arrow key) or no (for performing; right arrow key) button.
+Participants responded by pressing either a yes (left arrow key) or no (right arrow key) button.
 While listening to each recording, sheet music, which corresponded to the recording, was shown on the screen in front of the participants (*Figure \ref{fig:procedure1}*).
 
-There were two blocks and each block only included recordings with one musical expressive technique of either articulation or dynamics.
-Each block consisted of 4 practice trials and 48 experimental trials.
+There were two blocks and each block only included the recordings with one musical expressive technique of either articulation or dynamics.
+Each block consisted of four practice trials and 48 experimental trials.
 Each recording was evaluated only once in the experiment.
-The order of the blocks was counterbalanced across the participants.
+All participants completed both blocks and the order of the blocks was counterbalanced across the participants.
 The order of the recordings was randomised within each block.
@@
 
-## Data analysis{#dataanalysis}
+## Data analysis
 Data processing and statistical analysis were performed in R version 4.0.5.
@@
 Larger KV values indicate forte styles while smaller KV values indicate piano styles.
-Additionally, we also measured dynamics contrast where one subcomponent of the technique moves to the other (e.g., from forte to piano) to illustrate how much dynamics contrast a performer made at transition points.
+Additionally, we also measured dynamics contrast where one subcomponent of the technique moves to the other (e.g., from forte to piano, from staccato to legato) to illustrate how much dynamics contrast a performer made at transition points.
 
-First, we investigated data by looking at correlations between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as "teaching" (i.e., what percentage of participants responded as "yes") for each stimulus.
+First, in order to investigate relationships between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as teaching (i.e., what percentage of participants responded as "yes"), we performed correlation analysis.
 Second, we run multiple regression and entered all four performance features to examine which predictor significantly contributed to participants' judgments as teaching.
@@
 staccato, forte vs.
-piano), we entered each subcomponent (i.e., legato, staccato, forte, piano) separately to represent either an articulation or dynamics feature of the performance for a regression model.
+piano), we created four separate models, which considered only one subcomponent of either legato, staccato, forte or piano.
 
 For articulation recordings, there were two models.
-The first model considered only legato parts of the stimuli for KOT and KV, and transition points from legato to staccato for KV-Diff.
-The second model considered only staccato parts of the stimuli for KOT and KV, and transition points from staccato to legato for KV-Diff.
-For dynamics recordings, there were two models.
-The first model considered only forte parts of the stimuli for KV and KOT, and transition points from forte to piano for KV-Diff.
-The second model considered only piano parts of the stimuli for KV and KOT, and transition points from piano to forte for KV-Diff.
-With regard to tempo (IOIs), there was only one value for each technique because tempo was consistent across the performance and was not dependent on subcomponents.
-Therefore, we entered the same tempo value for legato and staccato or forte and piano parts.
+The Legato model considered only legato parts of the stimuli.
+We entered the legato parts of KOT and KV and KV-Diff or transition points from legato to staccato.
+The Staccato model considered only staccato parts of the stimuli.
+We entered the staccato parts of KOT and KV and KV-Diff of transition points from staccato to legato.
+Similarly, there were two models for dynamics recordings.
+The Forte model considered only forte parts of the stimuli for KV and KOT, and transition points from forte to piano for KV-Diff.
+The Piano model considered only piano parts of the stimuli for KV and KOT, and transition points from piano to forte for KV-Diff.
+With regard to tempo (IOIs), there was only one value for each recording regardless of the subcomponents because tempo was consistent across the performance.
+Therefore, we entered the same tempo value for the Legato and Staccato models or the Forte and Piano models.
 
@@
 Therefore, a Spearman's rank correlation coefficient was additionally used to assess the relationship between performance tempi of dynamics recordings and participants' judgments.
-The result failed to reach significance (*r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`), suggesting that we need to be careful about the interpretation of the relationship between performance tempi of dynamics recordings and participants' judgments as teaching.
+The result failed to reach significance (*r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`), suggesting that we need to be careful about the interpretation of the relationship between the performance tempi of dynamics recordings and participants' judgments as teaching.
 
@@
 For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r(`r cor_vel_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-1}*, left).
-The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings for legato was not normally distributed (*p* `r if(vel_leg_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_leg_norm_performance$p.value))}`).
+The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings (legato parts) was not normally distributed (*p* `r if(vel_leg_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_leg_norm_performance$p.value))}`).
 A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg_spearman$estimate))`, *p* `r if(cor_vel_leg_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg_spearman$p.value))}`).
@@
 For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ltos$p.value))}`, From Staccato to Legato; *r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_stol$p.value))}`, *Figure \ref{fig:vel-diff-1}*, left).
-The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings for transition points from legato to staccato was not normally distributed (*p* `r if(vel_diff_ltos_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ltos_norm_performance$p.value))}`).
-A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos_spearman$estimate))`, *p* `r if(cor_vel_diff_ltos_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ltos_spearman$p.value))}`).
+The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings (transition points from legato to staccato) was not normally distributed (*p* `r if(vel_diff_ltos_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ltos_norm_performance$p.value))}`).
+A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for the transition points from legato to staccato and participants' judgments as teaching (*r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos_spearman$estimate))`, *p* `r if(cor_vel_diff_ltos_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ltos_spearman$p.value))}`).
 
@@
 staccato, forte vs.
-piano) and therefore cannot be summed up to represent each technique as one value, we reported four separateregression models for each subcomponent (see details in *Data analysis*).
+piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in *Data analysis*).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
-The result of the regression indicated that the model explained `r summary(m1)$adj.r.squared*100` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r sprintf('%.1f', summary(m1)$fstatistic[1])`, *p* `r if(lmp(m1) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m1)))}`).
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m1)$adj.r.squared*100)` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r sprintf('%.1f', summary(m1)$fstatistic[1])`, *p* `r if(lmp(m1) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m1)))}`).
 It was found that tempo (IOIs; *$\beta$* = `r summary(m1)$coefficients[2]`, *p* `r if(summary(m1)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[2, 4]))}`) and articulation for the legato parts (KOT; *$\beta$* = `r summary(m1)$coefficients[3]`, *p* `r if(summary(m1)$coefficients[3, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[3, 4]))}`) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato).
-The result of the regression indicated that the model explained `r summary(m2)$adj.r.squared*100` % of the variance (*F*(`r summary(m2)$fstatistic[2]`, `r summary(m2)$fstatistic[3]`) = `r sprintf('%.1f', summary(m2)$fstatistic[1])`, *p* `r if(lmp(m2) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m2)))}`).
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m2)$adj.r.squared*100)` % of the variance (*F*(`r summary(m2)$fstatistic[2]`, `r summary(m2)$fstatistic[3]`) = `r sprintf('%.1f', summary(m2)$fstatistic[1])`, *p* `r if(lmp(m2) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m2)))}`).
 It was found that tempo (IOIs; *$\beta$* = `r summary(m2)$coefficients[2]`, *p* `r if(summary(m2)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m2)$coefficients[2, 4]))}`) and articulation for the staccato parts (KOT; *$\beta$* = `r summary(m2)$coefficients[3]`, *p* `r if(summary(m2)$coefficients[3, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m2)$coefficients[3, 4]))}`) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano).
-The result of the regression indicated that the model explained `r summary(m3)$adj.r.squared*100` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r sprintf('%.2f', summary(m3)$fstatistic[1])`, *p* `r if(lmp(m3) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m3)))}`).
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m3)$adj.r.squared*100)` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r sprintf('%.2f', summary(m3)$fstatistic[1])`, *p* `r if(lmp(m3) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m3)))}`).
 It was found that tempo (IOIs; *$\beta$* = `r summary(m3)$coefficients[2]`, *p* `r if(summary(m3)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m3)$coefficients[2, 4]))}`) and dynamics for the forte parts (KV; *$\beta$* = `r summary(m3)$coefficients[4]`, *p* `r if(summary(m3)$coefficients[4, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m3)$coefficients[4, 4]))}`) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte).
-The result of the regression indicated that the model explained `r summary(m4)$adj.r.squared*100` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r sprintf('%.1f', summary(m4)$fstatistic[1])`, *p* `r if(lmp(m4) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m4)))}`).
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m4)$adj.r.squared*100)` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r sprintf('%.1f', summary(m4)$fstatistic[1])`, *p* `r if(lmp(m4) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m4)))}`).
 It was found that tempo (IOIs; *$\beta$* = `r summary(m4)$coefficients[2]`, *p* `r if(summary(m4)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[2, 4]))}`) and dynamics contrast from piano to forte (KV-Diff; *$\beta$* = `r summary(m4)$coefficients[5]`, *p* `r if(summary(m4)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[5, 4]))}`) were significant predictors of participants' judgments as teaching.
@@
 
-Experiment 1 investigated which features of piano performance made musicians (in the role of potential learners) infer teaching intentions.
-The results demonstrated that performances with slower tempo were more likely to be judged as teaching by musicians regardless which expressive technique was implemented in the piece.
+Experiment 1 investigated which features of piano performance made musicians infer teaching intentions.
+The results demonstrated that performances with slower tempo were more likely to be judged as teaching by musicians regardless of which expressive technique was implemented in the piece.
 For articulation recordings, performances with longer legato and shorter staccato were tended to be judged as teaching.
@@
 This result may suggest that dynamics contrast might be reliably used to infer teaching intentions, rather than absolute dynamics values themselves.
-Moreover, multiple regression analyses implied that tempo feature is the strongest predictor of participants' judgments as teaching in general whereas there were specific predictors depending on which expressive technique was implemented in the piece.
+Moreover, multiple regression analyses implied that tempo feature was the strongest predictor of participants' judgments as teaching in general whereas there were specific predictors depending on which expressive technique was implemented in the piece.
 These performance features were overall consistent with what expert pianists did in our previous experiments for teaching purposes.
@@
 
-The aim of Experiment 2 was to replicate our previous findings in Experiment 1 with a more naturalistic piece of music.
-Given the findings on Experiment 1, we predicted that slower performance would be likely to be judged as teaching.
+The aim of Experiment 2 was to replicate the findings in Experiment 1 with a more naturalistic piece of music.
+Given the findings in Experiment 1, we predicted that slower performance would be likely to be judged as teaching regardless of which expressive technique (articulation or dynamics) was implemented.
 Also performances with exaggerated articulation and dynamics (in particular, longer legato and shorter staccato, larger contrast between forte and piano) would be likely to be judged as teaching.
@@
 One participant was excluded because s/he did not understand the instructions.
-Therefore, `r nrow(dt_included)` participants (Female: `r nrow(dt_included[Gender == "Female"])`) were included for data analysis and had `r round(mean(dt_included$Training), 2)` years of training on average in any musical instrument or singing (*SD* = `r round(sd(dt_included$Training), 2)`).
-Most people were right-handed (Left; `r nrow(dt_included[Handedness == "Left"])`) with a mean age of `r round(mean(dt_included$Age), 2)` (*SD* = `r round(sd(dt_included$Age), 2)`).
+Therefore, `r nrow(dt_included)` participants (Female: `r nrow(dt_included[Gender == "Female"])`) were included for data analysis and had `r sprintf('%.2f', mean(dt_included$Training))` years of training on average in any musical instrument or singing (*SD* = `r round(sd(dt_included$Training), 2)`).
+Most people were right-handed (Left; `r nrow(dt_included[Handedness == "Left"])`) with a mean age of `r sprintf('%.2f', mean(dt_included$Age))` (*SD* = `r round(sd(dt_included$Age), 2)`).
 As Experiment 1, all participants were recruited through the SONA system and the study (No.
@@
 ## Apparatus and procedure
-The apparatus and procedure were identical to Experiment 1 except that each block consisted of 4 practice trials and 36 experimental trials.
+The apparatus and procedure were identical to Experiment 1 except that each block consisted of four practice trials and 36 experimental trials.
 The number of trials was reduced due to the time constraint of the experiment.
@@
 ## Stimuli
-As Experiment 1, we selected stimuli from our previous experiments (Tominaga et al., *submitted*).
+As Experiment 1, we selected stimuli from our previous experiments (Tominaga et al., *submitted*; Experiment 2).
 The excerpt was taken from ``Sonatina Op.36 (No.3) in C major" by Muzio Clementi and modified for the experiment.
 The excerpt was performed with either articulation (*Figure \ref{fig:stim2}*, A) or dynamics (*Figure \ref{fig:stim2}*, B).
-The stimuli were performed around 100 - 120 quarter-beats per minute (i.e., around 250 - 300 ms for 8th-note IOIs).
+The stimuli were performed around 100 - 120 quarter-beats per minute.
 
-For the current experiment, 96 performances were chosen from the valid performances in Tominaga et al.
+For the current experiment, 72 performances were chosen from the valid performances in Tominaga et al.
 (*submitted*; Experiment 2).
@@
 We randomly sampled 18 articulation performances and 18 dynamics performances from the teaching condition as well as 18 articulation performances and 18 dynamics performances from the performing condition.
-In total, 72 recordings were selected as stimuli for the current experiment.
 Again, it is important to note that each performance from the teaching condition did not necessarily exhibit specific features of teaching that we found in the previous experiments (e.g., exaggeration) since we randomly sampled the performances.
 
-## Data analysis{#dataanalysis2}
+## Data analysis
 The data analysis was identical to Experiment 1.
@@
 Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).
-
 The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; *p* `r if(vel_diff_ftop_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ftop_norm_performance$p.value))}`, Piano to Forte; *p* `r if(vel_diff_ptof_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ptof_norm_performance$p.value))}`).
 Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop_spearman$estimate))`, *p* `r if(cor_vel_diff_ftop_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop_spearman$p.value))}`, Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof_spearman$estimate))`, *p* `r if(cor_vel_diff_ptof_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ptof_spearman$p.value))}`).
+
+For articulation recordings, there was no significant relationship between KV difference between transition points from legato to staccato and participants' judgments as teaching (*r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ltos$p.value))}`).
+However, there was a significant relationship between the transition points from staccato to legato and participants' judgments as teaching (*r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_stol$p.value))}`), suggesting that performances with larger contrast from staccato to legato were more likely to be considered as teaching performance (*Figure \ref{fig:vel-diff-2}*, left).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
-The result of the regression indicated that the model explained `r summary(m1)$adj.r.squared*100` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r sprintf('%.2f', summary(m1)$fstatistic[1])`, *p* `r if(lmp(m1) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', lmp(m1)))}`).
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m1)$adj.r.squared*100)` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r sprintf('%.2f', summary(m1)$fstatistic[1])`, *p* `r if(lmp(m1) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', lmp(m1)))}`).
 It was found that tempo (IOIs; *$\beta$* = `r summary(m1)$coefficients[2]`, *p* `r if(summary(m1)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[2, 4]))}`), dynamics (KV; *$\beta$* = `r summary(m1)$coefficients[4]`, *p* `r if(summary(m1)$coefficients[4, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[4, 4]))}`) and dynamics contrast (KV-Diff; *$\beta$* = `r summary(m1)$coefficients[5]`, *p* `r if(summary(m1)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[5, 4]))}`) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano).
-The result of the regression indicated that the model explained `r summary(m3)$adj.r.squared*100` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r sprintf('%.1f', summary(m3)$fstatistic[1])`, *p* `r if(lmp(m3) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m3)))}`).
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m3)$adj.r.squared*100)` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r sprintf('%.1f', summary(m3)$fstatistic[1])`, *p* `r if(lmp(m3) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m3)))}`).
 It was found that dynamics contrast from forte to piano (KV-Diff; *$\beta$* = `r summary(m3)$coefficients[5]`, *p* `r if(summary(m3)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m3)$coefficients[5, 4]))}`) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte).
-The result of the regression indicated that the model explained `r summary(m4)$adj.r.squared*100` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r sprintf('%.2f', summary(m4)$fstatistic[1])`, *p* `r if(lmp(m4) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m4)))}`).
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m4)$adj.r.squared*100)` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r sprintf('%.2f', summary(m4)$fstatistic[1])`, *p* `r if(lmp(m4) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m4)))}`).
 It was found that tempo (IOIs; *$\beta$* = `r summary(m4)$coefficients[2]`, *p* `r if(summary(m4)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[2, 4]))}`) and dynamics contrast from piano to forte (KV-Diff; *$\beta$* = `r summary(m4)$coefficients[5]`, *p* `r if(summary(m4)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[5, 4]))}`) were significant predictors of participants' judgments as teaching.
@@
 # Discussion
-Experiment 2 aimed to replicate our previous findings in Experiment 1 with a more naturalistic piece of music.
-We successfully replicated the findings from Experiment 1 in dynamics features.
-Performances with louder forte and softer piano were likely to be judged as teaching for dynamics recordings.
-Moreover, there seems to be a strong relationship between dynamics contrast between forte and piano and participants' judgments as teaching.
 
-However, we failed to replicate the results in terms of tempo (IOIs) and articulation (KOT).
-Compared with Experiment 1, the piece used in Experiment 2 was musically much complex.
-Therefore, articulation features may not be that reliable in order to infer teaching intentions.
-Unlike tempo and loudness, which are relatively easier to understand, articulation is very particular to music.
-The reason we could not see a relationship between articulation values and participants' judgments as teaching might be coming from conceptual and perceptual difficulties of articulation, even for musicians.
+# General discussion
 

### 2022-02-02 paper/manuscript.tex
first draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 \hypersetup{
-  pdftitle={What makes listeners infer teaching intentions?},
+  pdftitle={What makes musicians infer teaching intentions?},
   pdfauthor={Atsuko Tominaga1,*, Günther Knoblich1, \& Natalie Sebanz1},
@@
 
-\title{What makes listeners infer teaching intentions?}
+\title{What makes musicians infer teaching intentions?}
 \author{Atsuko Tominaga\textsuperscript{1,*}, Günther Knoblich\textsuperscript{1}, \& Natalie Sebanz\textsuperscript{1}}
@@
 
-\shorttitle{What makes listeners infer teaching intentions?}
+\shorttitle{What makes musicians infer teaching intentions?}
 
@@
 \abstract{
-Social learning plays an important role in human skill transmission.
-It has been known that experts tend to change their behaviour particularly for teaching purposes.
+Perceiving pedagogical intentions is vital when learning skills from others.
 Our previous research demonstrated that expert pianists systematically modulated their sound so as to teach musical expressive techniques such as articulation and dynamics.
@@
 In the current study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
-They were asked to judge whether each performance was produced to teach the designated expressive technique or not.
+They were asked to judge whether each recording was produced to teach the designated expressive technique or not.
 We quantified recordings with regard to tempo, articulation and dynamics.
-We performed correlation and regression analysis to investigate which features of piano performance make musicians infer teaching intention.
-The findings in Experiment 1 with a simple musical scales demonstrated that slower tempo contributed to musicians' judgments as teaching regardless of the techniques.
+We performed correlation and multiple regression analysis to investigate which features of piano performance made musicians infer teaching intention.
+The findings in Experiment 1 with a simple musical scale demonstrated that slower tempo contributed to musicians' judgments as teaching regardless of the techniques.
 Moreover, performances with exaggeration for each technique (e.g., longer legato, shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching.
-We run Experiment 2 with a more naturalistic piece to replicate the findings of Experiment 1.
-We only replicated the findings related to dynamics (e.g., larger contrast between forte and piano).
-Taken together, dynamics features of piano performance were more reliably perceived by musicians to infer pedagogical intentions.
+Experiment 2 aimed to replicate the findings of Experiment 1 with a more naturalistic piece.
+We only replicated the findings related to dynamics (in particular, larger contrast between forte and piano).
+Taken together, loudness (dynamics) seems to be reliably used to infer teaching intentions regardless of the complexity of a musical piece.
+Also, typical pedagogical behaviour such as slowing down may not be necessarily perceived as teaching performance when learning complex skills such as artistic expression.
 }
@@
 Also, some studies have revealed that even towards adult learners, people modulated their speech and action in the similar way as they did for infants (McEllin, Knoblich, \& Sebanz, 2017; Uther, Knoll, \& Burnham, 2007).
-These findings suggest that there are general pedagogical behaviours such as slow demonstration and exaggeration of speech and action to send teaching intentions to learners.
+Moreover, McEllin, Sebanz, and Knoblich (2018) demonstrated that people could identify informative intentions such as acting with others or teaching by relying on specific kinematics cues (e.g., velocity profiles of movements).
+These findings suggest that experts modified their speech and action to send teaching intentions and that novices could successfully perceive the intentions.
 
-Tominaga, Knoblich \& Sebanz (\emph{submitted}) extended this line of research to expertise transmission where skills to be acquired are much more complicated than general knowledge, which is mostly acquired throughout development (e.g., Csibra \& Gergely, 2009).
-Expertise usually demands an enormous amount of practice to acquire so that only experts can accomplish a higher level of performance including artistic expression.
+Tominaga, Knoblich \& Sebanz (\emph{submitted}) extended this line of research to expertise transmission where skills to be acquired are complex such as artistic expression.
 Based on the assumption that expert pianists are very good at controlling and modulating their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
@@
 
-In order to achieve successful skill transmission, it is necessary to investigate whether novice learners can identify teaching intentions produced by experts.
-A recent study by McEllin, Sebanz, and Knoblich (2018) demonstrated that people could identify informative intentions such as acting with others or teaching by relying on specific kinematics cues (e.g., velocity profiles of movements).
-Some research in the field of action expertise suggest that motor simulation (i.e., using one's own motor systems to simulate an action) plays a key role to understand observed actions.
+Furthermore, some research in the field of action expertise suggest that motor simulation (i.e., using one's own motor systems to simulate an action) plays a key role to understand observed actions.
 For example, expert basketball players were better at predicting the outcome of a free shot compared to expert observers (coaches or sports journalists) and novices (Aglioti, Cesari, Romani, \& Urgesi, 2008).
 Also, it was found that deceptive intentions of fake basketball passes were detected from non-verbal bodily cues only by expert basketball players (Sebanz \& Shiffrar, 2009).
-Taken together, people seem to be able to infer informative intentions by observing actions and motor expertise may enable accurate action prediction.
+Taken together, people seem to be able to infer informative intentions by observing actions accurately if they have enough expertise to simulate the actions.
 
@@
 Repp and Knoblich (2004) also found that expert pianists could distinguish their own performance from others' performances by listening to recordings.
-These results suggest that musical expertise may be important to accurately identify and infer intentions by listening to recorded performances.
+These results suggest that musical expertise may enable people identify and infer intentions accurately by using their own motor resources.
 
-The current experiments investigate which features of piano performance make musicians (in the role of potential learners) infer teaching intentions, only by listening to recorded performances.
-We collected various piano recordings from our previous experiments (Tominaga et al., \emph{in prep}).
-The obtained recordings consisted of two pieces (one was used for Experiment 1 and the other was used for Experiment 2 in the current paper).
-The two pieces were performed by various pianists multiple times, therefore the recordings contained many variations in terms of timing, articulation and dynamics.
-In the current experiments, we asked musically trained participants to judge which performance was performed for teaching purposes.
-If teachers' intentions are successfully communicated with learners, pedagogical behavioural features in our previous experiments such as slower demonstration and exaggerated performance should be identified and used to infer teaching intentions.
-In Experiment 1, we examined which features of piano performance were correlated with participants judgments as ``teaching''.
-Experiment 2 was conducted to replicate what we found in Experiment 1 with a more naturalistic piece of music.
+Here we investigated whether the modulations that expert pianists made when they intended to teach were also perceived by listeners as conveying pedagogical intentions.
+We quantified recordings with regard to tempo, articulation and dynamics and examined which features of piano performance made musicians infer teaching intentions.
+We performed correlation and multiple regression analysis to investigate relationships between performance features of a recording and how likely people think the recording was produced for teaching purposes.
+Various piano recordings were collected from our previous experiments (Tominaga et al., \emph{submitted}).
+The recordings were performed by various pianists multiple times, therefore the recordings contained many variations in terms of timing, articulation and dynamics.
+In the current study, we asked musically trained participants to judge which each recording was performed for teaching purposes.
+If performers' intentions are successfully communicated with learners, pedagogical behavioural features in our previous experiments such as slower demonstration and exaggerated performance should be identified and used to infer teaching intentions.
+We examined which features of piano performance were correlated with participants judgments as ``teaching''.
+We conducted Experiment 1 with a simple musical scale and Experiment 2 with a more naturalistic piece of music to replicate the findings from Experiment 1.
 
@@
 One participant was excluded due to an experimental error.
-Therefore, 20 participants (Female: 13) were included for data analysis and had 11.85 years of musical training on average (\emph{SD} = 5.62).
-They were all right-handed with a mean age of 28.80 (\emph{SD} = 9.09).
+Therefore, 20 participants (Female: 13) were included for data analysis and had 11.8 years of musical training on average (\emph{SD} = 5.62).
+They were all right-handed with a mean age of 28.8 (\emph{SD} = 9.09).
 All participants were recruited through an online participant platform (SONA system, \url{https://www.sona-systems.com}).
@@
 In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert).
-In total, we obtained 453 valid performances (i.e., performances without any pitch error) from the teaching condition and 436 valid performances from the performing condition.
+In total, we obtained 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition.
 
-For the current experiment, 96 performances were chosen from the valid performances in Tominaga et al.~(\emph{submitted}; Experiment 1).
-We randomly sampled 24 articulation performances and 24 dynamics performances from the teaching condition as well as 24 articulation performances and 24 dynamics performances from the performing condition.
-It is important to note that the performances from the teaching condition did not necessarily exhibit specific features of teaching that we found in our previous experiments (e.g., exaggeration) since we randomly sampled the performances.
+For the current experiment, 96 recordings were chosen from the valid performances in Tominaga et al.~(\emph{submitted}; Experiment 1).
+We randomly sampled 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition.
+It is important to note that the recordings from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments (e.g., exaggeration) since we randomly sampled the performances.
 
@@
 In the experiment, all instructions were displayed on a computer screen in front of the participants and an experimenter also explained the procedure.
-Participants were instructed that they were going to listen to piano recordings with musical expression (either articulation or dynamics), which were either produced as if a pianist were teaching the expression to students (e.g., in a lesson; teaching) or as if a pianist were performing it to an audience (e.g., in a concert; performing).
+Participants were instructed that they were going to listen to piano recordings with one musical expressive technique of either articulation or dynamics, which were either produced as if a pianist were teaching the designated expressive technique to students (e.g., in a lesson) or as if a pianist were performing it to an audience (e.g., in a concert).
 In each trial, participants listened to one recording and were asked whether the recording was produced for teaching purposes or not.
-Participants responded by pressing either a yes (for teaching; left arrow key) or no (for performing; right arrow key) button.
+Participants responded by pressing either a yes (left arrow key) or no (right arrow key) button.
 While listening to each recording, sheet music, which corresponded to the recording, was shown on the screen in front of the participants (\emph{Figure \ref{fig:procedure1}}).
 
-There were two blocks and each block only included recordings with one musical expressive technique of either articulation or dynamics.
-Each block consisted of 4 practice trials and 48 experimental trials.
+There were two blocks and each block only included the recordings with one musical expressive technique of either articulation or dynamics.
+Each block consisted of four practice trials and 48 experimental trials.
 Each recording was evaluated only once in the experiment.
-The order of the blocks was counterbalanced across the participants.
+All participants completed both blocks and the order of the blocks was counterbalanced across the participants.
 The order of the recordings was randomised within each block.
@@
 
-\hypertarget{dataanalysis}{%
-\subsection{Data analysis}\label{dataanalysis}}
+\hypertarget{data-analysis}{%
+\subsection{Data analysis}\label{data-analysis}}
 
@@
 Larger KV values indicate forte styles while smaller KV values indicate piano styles.
-Additionally, we also measured dynamics contrast where one subcomponent of the technique moves to the other (e.g., from forte to piano) to illustrate how much dynamics contrast a performer made at transition points.
+Additionally, we also measured dynamics contrast where one subcomponent of the technique moves to the other (e.g., from forte to piano, from staccato to legato) to illustrate how much dynamics contrast a performer made at transition points.
 
-First, we investigated data by looking at correlations between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as ``teaching'' (i.e., what percentage of participants responded as ``yes'') for each stimulus.
+First, in order to investigate relationships between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as teaching (i.e., what percentage of participants responded as ``yes''), we performed correlation analysis.
 Second, we run multiple regression and entered all four performance features to examine which predictor significantly contributed to participants' judgments as teaching.
-Since articulation and dynamics were comprised of two opposite directional values (i.e., legato vs.~staccato, forte vs.~piano), we entered each subcomponent (i.e., legato, staccato, forte, piano) separately to represent either an articulation or dynamics feature of the performance for a regression model.
+Since articulation and dynamics were comprised of two opposite directional values (i.e., legato vs.~staccato, forte vs.~piano), we created four separate models, which considered only one subcomponent of either legato, staccato, forte or piano.
 
 For articulation recordings, there were two models.
-The first model considered only legato parts of the stimuli for KOT and KV, and transition points from legato to staccato for KV-Diff.
-The second model considered only staccato parts of the stimuli for KOT and KV, and transition points from staccato to legato for KV-Diff.
-For dynamics recordings, there were two models.
-The first model considered only forte parts of the stimuli for KV and KOT, and transition points from forte to piano for KV-Diff.
-The second model considered only piano parts of the stimuli for KV and KOT, and transition points from piano to forte for KV-Diff.
-With regard to tempo (IOIs), there was only one value for each technique because tempo was consistent across the performance and was not dependent on subcomponents.
-Therefore, we entered the same tempo value for legato and staccato or forte and piano parts.
+The Legato model considered only legato parts of the stimuli.
+We entered the legato parts of KOT and KV and KV-Diff or transition points from legato to staccato.
+The Staccato model considered only staccato parts of the stimuli.
+We entered the staccato parts of KOT and KV and KV-Diff of transition points from staccato to legato.
+Similarly, there were two models for dynamics recordings.
+The Forte model considered only forte parts of the stimuli for KV and KOT, and transition points from forte to piano for KV-Diff.
+The Piano model considered only piano parts of the stimuli for KV and KOT, and transition points from piano to forte for KV-Diff.
+With regard to tempo (IOIs), there was only one value for each recording regardless of the subcomponents because tempo was consistent across the performance.
+Therefore, we entered the same tempo value for the Legato and Staccato models or the Forte and Piano models.
 
@@
 Therefore, a Spearman's rank correlation coefficient was additionally used to assess the relationship between performance tempi of dynamics recordings and participants' judgments.
-The result failed to reach significance (\emph{r(46)} = .27, \emph{p} = 0.066), suggesting that we need to be careful about the interpretation of the relationship between performance tempi of dynamics recordings and participants' judgments as teaching.
+The result failed to reach significance (\emph{r(46)} = .27, \emph{p} = 0.066), suggesting that we need to be careful about the interpretation of the relationship between the performance tempi of dynamics recordings and participants' judgments as teaching.
 
@@
 For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r(46)} = .10, \emph{p} = 0.52, Staccato; \emph{r(46)} = -.02, \emph{p} = 0.87, \emph{Figure \ref{fig:vel-1}}, left).
-The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings for legato was not normally distributed (\emph{p} = 0.002).
+The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings (legato parts) was not normally distributed (\emph{p} = 0.002).
 A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r(46)} = .03, \emph{p} = 0.84).
@@
 For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r(46)} = -.26, \emph{p} = 0.071, From Staccato to Legato; \emph{r(46)} = -.19, \emph{p} = 0.21, \emph{Figure \ref{fig:vel-diff-1}}, left).
-The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings for transition points from legato to staccato was not normally distributed (\emph{p} = 0.007).
-A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r(46)} = -.23, \emph{p} = 0.12).
+The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings (transition points from legato to staccato) was not normally distributed (\emph{p} = 0.007).
+A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for the transition points from legato to staccato and participants' judgments as teaching (\emph{r(46)} = -.23, \emph{p} = 0.12).
 
@@
 Statistical model assumptions were tested using the \emph{performance} R package (Lüdecke, Ben-Shachar, Patil, Waggoner, \& Makowski, 2021) and all assumptions were met.
-Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separateregression models for each subcomponent (see details in \emph{Data analysis}).
+Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in \emph{Data analysis}).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
-The result of the regression indicated that the model explained 64.63 \% of the variance (\emph{F}(4, 43) = 22.5, \emph{p} \textless{} 0.001).
+The result of the regression indicated that the model explained 64.6 \% of the variance (\emph{F}(4, 43) = 22.5, \emph{p} \textless{} 0.001).
 It was found that tempo (IOIs; \emph{\(\beta\)} = 0.78, \emph{p} \textless{} 0.001) and articulation for the legato parts (KOT; \emph{\(\beta\)} = 0.26, \emph{p} = 0.004) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato).
-The result of the regression indicated that the model explained 63.97 \% of the variance (\emph{F}(4, 43) = 21.9, \emph{p} \textless{} 0.001).
+The result of the regression indicated that the model explained 64.0 \% of the variance (\emph{F}(4, 43) = 21.9, \emph{p} \textless{} 0.001).
 It was found that tempo (IOIs; \emph{\(\beta\)} = 0.52, \emph{p} = 0.002) and articulation for the staccato parts (KOT; \emph{\(\beta\)} = -0.28, \emph{p} = 0.020) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano).
-The result of the regression indicated that the model explained 35.90 \% of the variance (\emph{F}(4, 43) = 7.58, \emph{p} \textless{} 0.001).
+The result of the regression indicated that the model explained 35.9 \% of the variance (\emph{F}(4, 43) = 7.58, \emph{p} \textless{} 0.001).
 It was found that tempo (IOIs; \emph{\(\beta\)} = 0.35, \emph{p} = 0.007) and dynamics for the forte parts (KV; \emph{\(\beta\)} = 0.73, \emph{p} = 0.048) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte).
-The result of the regression indicated that the model explained 51.21 \% of the variance (\emph{F}(4, 43) = 13.3, \emph{p} \textless{} 0.001).
+The result of the regression indicated that the model explained 51.2 \% of the variance (\emph{F}(4, 43) = 13.3, \emph{p} \textless{} 0.001).
 It was found that tempo (IOIs; \emph{\(\beta\)} = 0.38, \emph{p} \textless{} 0.001) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 0.99, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.
@@
 
-The apparatus and procedure were identical to Experiment 1 except that each block consisted of 4 practice trials and 36 experimental trials.
+The apparatus and procedure were identical to Experiment 1 except that each block consisted of four practice trials and 36 experimental trials.
 The number of trials was reduced due to the time constraint of the experiment.
@@
 
-As Experiment 1, we selected stimuli from our previous experiments (Tominaga et al., \emph{submitted}).
+As Experiment 1, we selected stimuli from our previous experiments (Tominaga et al., \emph{submitted}; Experiment 2).
 The excerpt was taken from ``Sonatina Op.36 (No.3) in C major'' by Muzio Clementi and modified for the experiment.
 The excerpt was performed with either articulation (\emph{Figure \ref{fig:stim2}}, A) or dynamics (\emph{Figure \ref{fig:stim2}}, B).
-The stimuli were performed around 100 - 120 quarter-beats per minute (i.e., around 250 - 300 ms for 8th-note IOIs).
+The stimuli were performed around 100 - 120 quarter-beats per minute.
 
-For the current experiment, 96 performances were chosen from the valid performances in Tominaga et al.~(\emph{submitted}; Experiment 2).
+For the current experiment, 72 performances were chosen from the valid performances in Tominaga et al.~(\emph{submitted}; Experiment 2).
 There were 248 valid performances in the teaching condition and 256 valid performances in the performing condition.
 We randomly sampled 18 articulation performances and 18 dynamics performances from the teaching condition as well as 18 articulation performances and 18 dynamics performances from the performing condition.
-In total, 72 recordings were selected as stimuli for the current experiment.
 Again, it is important to note that each performance from the teaching condition did not necessarily exhibit specific features of teaching that we found in the previous experiments (e.g., exaggeration) since we randomly sampled the performances.
 
-\hypertarget{dataanalysis2}{%
-\subsection{Data analysis}\label{dataanalysis2}}
+\hypertarget{data-analysis-1}{%
+\subsection{Data analysis}\label{data-analysis-1}}
 
@@
 Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r(34)} = -.75, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r(34)} = .59, \emph{p} \textless{} 0.001).
-
 The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; \emph{p} = 0.850, Piano to Forte; \emph{p} = 0.008).
 Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; \emph{r(34)} = -.73, \emph{p} \textless{} 0.001, Piano to Forte; \emph{r(34)} = .57, \emph{p} \textless{} 0.001).
+
+For articulation recordings, there was no significant relationship between KV difference between transition points from legato to staccato and participants' judgments as teaching (\emph{r(34)} = .23, \emph{p} = 0.176).
+However, there was a significant relationship between the transition points from staccato to legato and participants' judgments as teaching (\emph{r(34)} = .36, \emph{p} = 0.03), suggesting that performances with larger contrast from staccato to legato were more likely to be considered as teaching performance (\emph{Figure \ref{fig:vel-diff-2}}, left).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
-The result of the regression indicated that the model explained 19.77 \% of the variance (\emph{F}(4, 31) = 3.16, \emph{p} = 0.028).
+The result of the regression indicated that the model explained 19.8 \% of the variance (\emph{F}(4, 31) = 3.16, \emph{p} = 0.028).
 It was found that tempo (IOIs; \emph{\(\beta\)} = 0.58, \emph{p} = 0.011), dynamics (KV; \emph{\(\beta\)} = 1.10, \emph{p} = 0.018) and dynamics contrast (KV-Diff; \emph{\(\beta\)} = 1.90, \emph{p} = 0.006) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano).
-The result of the regression indicated that the model explained 60.69 \% of the variance (\emph{F}(4, 31) = 14.5, \emph{p} \textless{} 0.001).
+The result of the regression indicated that the model explained 60.7 \% of the variance (\emph{F}(4, 31) = 14.5, \emph{p} \textless{} 0.001).
 It was found that dynamics contrast from forte to piano (KV-Diff; \emph{\(\beta\)} = -1.64, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte).
-The result of the regression indicated that the model explained 49.49 \% of the variance (\emph{F}(4, 31) = 9.57, \emph{p} \textless{} 0.001).
+The result of the regression indicated that the model explained 49.5 \% of the variance (\emph{F}(4, 31) = 9.57, \emph{p} \textless{} 0.001).
 It was found that tempo (IOIs; \emph{\(\beta\)} = 0.55, \emph{p} = 0.022) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 1.09, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.
@@
 
-Experiment 2 aimed to replicate our previous findings in Experiment 1 with a more naturalistic piece of music.
-We successfully replicated the findings from Experiment 1 in dynamics features.
-Performances with louder forte and softer piano were likely to be judged as teaching for dynamics recordings.
-Moreover, there seems to be a strong relationship between dynamics contrast between forte and piano and participants' judgments as teaching.
-
-However, we failed to replicate the results in terms of tempo (IOIs) and articulation (KOT).
-Compared with Experiment 1, the piece used in Experiment 2 was musically much complex.
-Therefore, articulation features may not be that reliable in order to infer teaching intentions.
-Unlike tempo and loudness, which are relatively easier to understand, articulation is very particular to music.
-The reason we could not see a relationship between articulation values and participants' judgments as teaching might be coming from conceptual and perceptual difficulties of articulation, even for musicians.
+\hypertarget{general-discussion}{%
+\section{General discussion}\label{general-discussion}}
 

### 2022-03-08 experiment-1/analysis/prereg_analysis/prereg_analysis.Rmd
update prereg analysis (add two-way anova / jittered plot
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ## Preregistered Analysis
-We originally had a analysis plan to look at the accuracy of participants' judgements whether participants would be able to judge stimuli from the teaching condition as "teaching".
+The preregistered analysis aims to investigate whether participants could distinguish performances produced for teaching purposes from those produced for performing purposes.
 For more detailed explanations, please see [the OSF preregistration](https://osf.io/z3j69).
@@
 
-- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques (expressions) separately. The order of the blocks was counterbalanced across participants.
-- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented across participants.
+- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques separately. The order of the blocks was counterbalanced across participants.
+- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented within a block.
 
@@
 # stats
-if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
-if (!require("performance")) {install.packages("performance"); require("performance")}
+if (!require("afex")) {install.packages("afex"); require("afex")}
 ```
@@
 ## 1. Statistics
-### All
+## All
 ```{r acc, echo = FALSE}
@@
 # all
-subset <- ind_data[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/96)*100, SD_Percent = (sd(Sum)/96)*100)]
+subset <- ind_data[, .(N = .N, Mean_Percent = mean(Percent), SD_Percent = sd(Percent))]
 subset
@@
 ```{r plot, echo = FALSE}
-ggboxplot(ind_data, x = "N", y = "Percent", add = "dotplot", xlab = FALSE) + ylab("Correct %") + theme(axis.text.x = element_blank())
+ggboxplot(ind_data, x = "N", y = "Percent", add = "dotplot", xlab = FALSE) + ylab("Correct %") + theme(axis.text.x = element_blank()) + geom_hline(yintercept = 50, linetype = "dashed")
 ```
@@
 
-### Articulation vs. Dynamics
+## Articulation vs. Dynamics
+Reference for a paired plot with jitter: [https://stackoverflow.com/questions/48042810/add-jitter-to-ggpaired#48044022](https://stackoverflow.com/questions/48042810/add-jitter-to-ggpaired#48044022)
 
 ```{r plot2, echo = FALSE}
-ind_data_ad <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Skill)]
+ind_data_ad <- data[subjectNumber != 4, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Skill)]
 ind_data_ad <- ind_data_ad[order(subjectNumber, Skill)]
 
-subset_ad <- ind_data_ad[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100), by = .(Skill)]
+subset_ad <- ind_data_ad[, .(N = .N, Mean_Percent = mean(Percent), SD_Percent = sd(Percent)), by = .(Skill)]
 subset_ad
@@
 data_box <- data.table(subjectNumber = ind_data_ad[Skill == "articulation"]$subjectNumber, articulation = ind_data_ad[Skill == "articulation"]$Percent, dynamics = ind_data_ad[Skill == "dynamics"]$Percent)
-box <- ggpaired(data_box, cond1 = "articulation", cond2 = "dynamics", line.color = "gray", line.size = 0.4, ylab = "Correct %")
-box
+
+# plot with jitter
+n <- length(data_box$articulation)
+d <- data.frame(y = c(data_box$articulation, data_box$dynamics), 
+                x = rep(c(1, 2), each = n),
+                id = factor(rep(1:n, 2)))
+
+set.seed(321)    
+d$xj <- jitter(d$x, amount = .05)
+ggplot(data = d, aes(y=y)) +
+  geom_boxplot(aes(x = x, group = x), width = 0.5, outlier.shape = NA) +
+  geom_point(aes(x = xj)) +
+  geom_line(aes(x = xj, group = id), color = "gray", size = .4) + labs(x = "Skill", y = "Correct %") +
+  scale_x_continuous(breaks = c(1, 2), labels = c("articulation", "dynamics"), limits = c(0.5, 2.5)) + geom_hline(yintercept = 50, linetype = "dashed") + theme_pubr()
+
+# plot without jitter
+# ggpaired(data_box, cond1 = "articulation", cond2 = "dynamics", line.color = "gray", line.size = 0.4, xlab = "Skill", ylab = "Correct %") + geom_hline(yintercept = 50, linetype = "dashed")
 ```
 
-## One-sample *t*-test
+### One-sample *t*-test
 ### Articulation
@@
 
-## Paired *t*-test between articulation and dynamics
+### Paired *t*-test between articulation and dynamics
 ```{r p-t-test, echo = FALSE}
@@
 
+## Two-way ANOVA (Condition * Skill)
+```{r plot3, echo = FALSE}
+ind_data_tp_ad <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill)]
+ind_data_tp_ad <- ind_data_tp_ad[order(subjectNumber, Condition, Skill)]
+
+ggboxplot(ind_data_tp_ad, "Skill", "Percent", color = "Condition") + geom_hline(yintercept = 50, linetype = "dashed")
+```
+
+```{r, echo = FALSE}
+anova <- aov_ez("subjectNumber", "Percent",
+                data = ind_data_tp_ad, within = c("Condition", "Skill"))
+anova
+```
+
 ```{r export, include = FALSE}

### 2022-03-08 experiment-2/analysis/prereg_analysis/prereg_analysis.Rmd
update prereg analysis (add two-way anova / jittered plot
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2022-03-08 experiment-1/analysis/prereg_analysis/prereg_analysis.Rmd
@@
 ## Preregistered Analysis
-The preregistered analysis aims to investigate whether participants could distinguish performances produced for teaching purposes from those produced for performing purposes.
+We originally had a analysis plan to look at the accuracy of participants' judgements whether participants would be able to judge stimuli from the teaching condition as "teaching".
 For more detailed explanations, please see [the OSF preregistration](https://osf.io/z3j69).
@@
 ## Stimuli
-- Stimuli were selected from the previous study ([the sound of teaching music/experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1)).
-- 48 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 96 stimuli).
-Half of them was selected from the teaching condition and the other half was from the performing condition.
-  + 24 for teaching-articulation performances
-  + 24 for performing-articulation performances
-  + 24 for teaching-dynamics performances
-  + 24 for performing-dynamics performances
+- Stimuli were selected from the previous study ([the sound of teaching music/experiment-2](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2)).
+- 36 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 72 stimuli).
+The half of them was selected from the teaching condition and the other half was from the performing condition.
+  + 18 for teaching-articulation performances
+  + 18 for performing-articulation performances
+  + 18 for teaching-dynamics performances
+  + 18 for performing-dynamics performances
 
@@
 
-- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques separately. The order of the blocks was counterbalanced across participants.
-- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented within a block.
+- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques (expressions) separately. The order of the blocks was counterbalanced across participants.
+- 36 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented across participants.
 
@@
 ```{r plot3, echo = FALSE}
-ind_data_tp_ad <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill)]
+ind_data_tp_ad <- data[subjectNumber != 4, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill)]
 ind_data_tp_ad <- ind_data_tp_ad[order(subjectNumber, Condition, Skill)]

### 2022-03-08 experiment-1/analysis/prereg_analysis/prereg_analysis.R

@@ -1,4 +1,4 @@
-## ----packages, include = FALSE------------------------------------
+## ----packages, include = FALSE-----------------------------
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
 # midi
@@ -6,11 +6,10 @@ if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
 # plot
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
 # stats
-if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
-if (!require("performance")) {install.packages("performance"); require("performance")}
+if (!require("afex")) {install.packages("afex"); require("afex")}
 
 
-## ----read, include = FALSE----------------------------------------
+## ----read, include = FALSE---------------------------------
 # read files and combine them
 data_ls <- list.files("../../data", pattern = "csv")
 combined <- lapply(data_ls, function(f){
@@ -40,60 +39,88 @@ all <- data[expMode == "experiment", .(N = .N, Sum = sum(Correct), Percent = (su
 all[order(subjectNumber, Condition, Skill)]
 
 
-## ----acc, echo = FALSE--------------------------------------------
+## ----acc, echo = FALSE-------------------------------------
 # individual
 ind_data <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber)]
 ind_data <- ind_data[order(subjectNumber)]
 
 # all
-subset <- ind_data[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/96)*100, SD_Percent = (sd(Sum)/96)*100)]
+subset <- ind_data[, .(N = .N, Mean_Percent = mean(Percent), SD_Percent = sd(Percent))]
 subset
 
 
-## ----plot, echo = FALSE-------------------------------------------
-ggboxplot(ind_data, x = "N", y = "Percent", add = "dotplot", xlab = FALSE) + ylab("Correct %") + theme(axis.text.x = element_blank())
+## ----plot, echo = FALSE------------------------------------
[…]

### 2022-03-08 experiment-2/analysis/prereg_analysis/prereg_analysis.R

@@ -1,4 +1,4 @@
-## ----packages, include = FALSE------------------------------
+## ----packages, include = FALSE-----------------------------
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
 # midi
@@ -6,11 +6,10 @@ if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
 # plot
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
 # stats
-if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
-if (!require("performance")) {install.packages("performance"); require("performance")}
+if (!require("afex")) {install.packages("afex"); require("afex")}
 
 
-## ----read, include = FALSE----------------------------------
+## ----read, include = FALSE---------------------------------
 # read files and combine them
 data_ls <- list.files("../../data", pattern = "csv")
 combined <- lapply(data_ls, function(f){
@@ -40,60 +39,88 @@ all <- data[expMode == "experiment", .(N = .N, Sum = sum(Correct), Percent = (su
 all[order(subjectNumber, Condition, Skill)]
 
 
-## ----acc, echo = FALSE--------------------------------------
+## ----acc, echo = FALSE-------------------------------------
 # individual
 ind_data <- data[subjectNumber != 4, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber)]
 ind_data <- ind_data[order(subjectNumber)]
 
 # all
-subset <- ind_data[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/72)*100, SD_Percent = (sd(Sum)/72)*100)]
+subset <- ind_data[, .(N = .N, Mean_Percent = mean(Percent), SD_Percent = sd(Percent))]
 subset
 
 
-## ----plot, echo = FALSE-------------------------------------
-ggboxplot(ind_data, x = "N", y = "Percent", add = "dotplot", xlab = FALSE) + ylab("Correct %") + theme(axis.text.x = element_blank())
+## ----plot, echo = FALSE------------------------------------
[…]

### 2022-03-14 paper/manuscript.Rmd
first draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 In the current study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
-They were asked to judge whether each recording was produced to teach the designated expressive technique or not.
-We quantified recordings with regard to tempo, articulation and dynamics.
-We performed correlation and multiple regression analysis to investigate which features of piano performance made musicians infer teaching intention.
-The findings in Experiment 1 with a simple musical scale demonstrated that slower tempo contributed to musicians’ judgments as teaching regardless of the techniques.
+Half of the recordings was produced when pianists were instructed to play as if they were teaching the designated musical technique in a lesson (i.e., teaching recordings) whereas the other half was produced when pianists were instructed to play as if they were performing it in a concert (i.e., performing recordings).
+Participants were asked to judge whether each recording was produced for teaching purposes or not.
+We calculated the accuracy of participants' judgments to investigate whether they could distinguish teaching recordings from performing recordings.
+Also, recordings were quantified with regard to tempo, articulation and dynamic so that we could perform correlation and multiple regression analysis to investigate which features of piano performance made musicians infer teaching intentions.
+The findings in Experiment 1 with a simple musical scale demonstrated that the accuracy of musicians' judgments was significantly above chance.
+Also, it was found that slower tempo contributed to musicians’ judgments as teaching regardless of the techniques.
 Moreover, performances with exaggeration for each technique (e.g., longer legato, shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching.
 Experiment 2 aimed to replicate the findings of Experiment 1 with a more naturalistic piece.
-We only replicated the findings related to dynamics (in particular, larger contrast between forte and piano).
+As Experiment 1, the accuracy of musicians' judgments was significantly above chance.
+However, we only replicated that performances with exaggerated dynamics (in particular, larger contrast between forte and piano) were more likely to be judged as teaching.
 Taken together, loudness (dynamics) seems to be reliably used to infer teaching intentions regardless of the complexity of a musical piece.
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_word
 ---
@@
 In pedagogical settings where teachers are supposed to convey useful information to learners, it has been found that teachers often modulate their behaviour for teaching purposes.
-For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills [e.g., @brand_2002; @kuhl_2004].
+For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills [e.g., @brand_2002; @saint-georges_2013].
 Also, some studies have revealed that even towards adult learners, people modulated their speech and action in the similar way as they did for infants [@mcellin_2017; @uther_2007].
@@
 Tominaga, Knoblich & Sebanz (*submitted*) extended this line of research to expertise transmission where skills to be acquired are complex such as artistic expression.
-Based on the assumption that expert pianists are very good at controlling and modulating their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
+Based on the assumption that expert pianists are skilled at controlling their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
 The results demonstrated that expert pianists could successfully modulate their performance by playing slower or exaggerating relevant aspects of the performance (e.g., producing shorter staccato or making a larger contrast between forte and piano) to teach musical expressive techniques.
@@
 
-Furthermore, some research in the field of action expertise suggest that motor simulation (i.e., using one's own motor systems to simulate an action) plays a key role to understand observed actions.
-For example, expert basketball players were better at predicting the outcome of a free shot compared to expert observers (coaches or sports journalists) and novices [@aglioti_2008].
-Also, it was found that deceptive intentions of fake basketball passes were detected from non-verbal bodily cues only by expert basketball players [@sebanz_2009].
-Taken together, people seem to be able to infer informative intentions by observing actions accurately if they have enough expertise to simulate the actions.
-
-In the domain of music, musical emotion is often communicated by sound alone and listeners seem to be able to infer performers' intended emotions only by listening to recorded performances [e.g., @akkermans_2019; @gabrielsson_1996].
-It has been known that musicians are generally more accurate to decode emotions from performances [@battcock_2021; @lima_2011].
-@repp_2004 also found that expert pianists could distinguish their own performance from others' performances by listening to recordings.
-These results suggest that musical expertise may enable people identify and infer intentions accurately by using their own motor resources.
-
 Here we investigated whether the modulations that expert pianists made when they intended to teach were also perceived by listeners as conveying pedagogical intentions.
-We quantified recordings with regard to tempo, articulation and dynamics and examined which features of piano performance made musicians infer teaching intentions.
-We performed correlation and multiple regression analysis to investigate relationships between performance features of a recording and how likely people think the recording was produced for teaching purposes.
+We assumed that listeners would be able to infer intentions only by listening to recordings because some research revealed that musical emotion is often communicated by sound alone and that listeners seem to be able to infer performers' intended emotions only by listening to recorded performances [e.g., @akkermans_2019; @gabrielsson_1996].
+In the present study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
+They were asked to judge whether each recording was produced for teaching purposes or not.
+Half of the recordings was produced when pianists were instructed to play as if they were teaching the designated musical technique in a lesson (i.e., teaching recordings) whereas the other half was produced when pianists were instructed to play as if they were performing it in a concert (i.e., performing recordings).
+First, we calculated the accuracy of participants’ judgments to examine whether they could distinguish teaching recordings from performing recordings.
+Furthermore, recordings were quantified with regard to tempo, articulation and dynamic.
+We performed correlation and multiple regression analysis to examine relationships between performance features of the recordings and how likely people think the recordings were produced for teaching purposes.
 Various piano recordings were collected from our previous experiments (Tominaga et al., *submitted*).
 The recordings were performed by various pianists multiple times, therefore the recordings contained many variations in terms of timing, articulation and dynamics.
-In the current study, we asked musically trained participants to judge which each recording was performed for teaching purposes.
-If performers' intentions are successfully communicated with learners, pedagogical behavioural features in our previous experiments such as slower demonstration and exaggerated performance should be identified and used to infer teaching intentions.
-We examined which features of piano performance were correlated with participants judgments as "teaching".
+
+If performers' intentions are successfully communicated with learners, musicians would be able to distinguish teaching recordings from performing recordings.
+Moreover, pedagogical behavioural features in our previous experiments such as slower demonstration and exaggerated performance should be identified and used to infer teaching intentions.
+We examined which features of piano performance were correlated with participants judgments as teaching.
 We conducted Experiment 1 with a simple musical scale and Experiment 2 with a more naturalistic piece of music to replicate the findings from Experiment 1.
@@
 Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files.
-Multiple pianists played one piece of music with a musical expressive techniques of either articulation (*Figure \ref{fig:stim1}*, A) or dynamics (*Figure \ref{fig:stim1}*, B).
+Multiple pianists played one piece of music with a musical expressive technique of either articulation (*Figure \ref{fig:stim1}*, A) or dynamics (*Figure \ref{fig:stim1}*, B).
 Articulation refers to the smoothness of sound, which is comprised of legato and staccato.
@@
 In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert).
-In total, we obtained 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition.
-
-For the current experiment, 96 recordings were chosen from the valid performances in Tominaga et al.
-(*submitted*; Experiment 1).
+In Tominaga et al.
+(*submitted*; Experiment 1), there were 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition.
+For the current experiment, 96 recordings were chosen from the valid performances.
 We randomly sampled 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition.
@@
 
+### Accuracy
+First, we examined whether participants could accurately distinguish the stimuli chosen from the teaching condition in Tominaga et al., (*submitted*; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (*submitted*; Experiment 1) as performing.
+We compared how accurate participants were against the chance level (50%).
+The correct responses were either pressing the yes button when listening to the teaching recordings or pressing the no button when listening to the performing recordings.
+The incorrect responses were either pressing the yes button when listening to the performing recordings or pressing the no button when listening to the teaching recordings.
+
+### Correlation and multiple regression
 Stimuli were quantified with regard to tempo (interonset intervals; IOIs), articulation (key-overlap time; KOT), dynamics (key velocity; KV) and dynamics contrast (key velocity difference; KV-Diff) only for 16th notes.
@@
 Therefore, we entered the same tempo value for the Legato and Staccato models or the Forte and Piano models.
-
-<!-- Additionally, we also analysed data in terms of accuracy of their judgments as we originally planned in our Open Science Framework preregistration (available here: [https://osf.io/z3j69/](https://osf.io/z3j69/)).
-As we sampled data from the two conditions (i.e., teaching and performing) in our previous experiments, we were also interested in whether musicians could accurately judge the stimuli selected from the teaching condition as "teaching (yes)" and the stimuli selected from the performing condition as "performing (no)".
-However, during a pilot study, we realised that the stimuli in the teaching condition were not sufficiently different from those in the performing condition because of the random sampling.
-Therefore, we decided to switch to the current analysis and added the planned analysis in *[Supplementary Materials](#supplementary)*.
--->
 
@@
 source(here("experiment-1/analysis", "analysis.R"), chdir = TRUE)
+source(here("experiment-1/analysis/prereg_analysis", "prereg_analysis.R"), chdir = TRUE)
 ```
@@
 All results were reported as significant at *p* < 0.05.
+
+## Accuracy
+A one sample *t*-test was performed to compare the accuracy of participants' judgments against the chance level (50%).
+The mean percentage of correct answers [*M* = `r sprintf('%.1f', subset$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset$SD_Percent)`] was significantly higher than chance (*t*(`r ttest_all$parameter`) = `r sprintf('%.2f', ttest_all$statistic)`, *p* `r if(ttest_all$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_all$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_all$effsize)`).
+
+We also performed a one sample *t*-test for each technique separately.
+For articulation, the mean percentage of correct answers [*M* = `r sprintf('%.1f', subset_ad[Skill == "articulation"]$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset_ad[Skill == "articulation"]$SD_Percent)`] was not significantly different from chance (*t*(`r ttest_art$parameter`) = `r sprintf('%.2f', ttest_art$statistic)`, *p* `r if(ttest_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_art$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_art$effsize)`).
+For dynamics, the mean percentage of correct answers [*M* = `r sprintf('%.1f', subset_ad[Skill == "dynamics"]$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset_ad[Skill == "dynamics"]$SD_Percent)`] was significantly higher than chance (*t*(`r ttest_dyn$parameter`) = `r sprintf('%.2f', ttest_dyn$statistic)`, *p* `r if(ttest_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_dyn$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_dyn$effsize)`).
+A paired *t*-test revealed that there was a significant difference between the two techniques in terms of the accuracy (*t*(`r ttest_paired$parameter`) = `r sprintf('%.2f', ttest_paired$statistic)`, *p* `r if(ttest_paired$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_paired$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_paired$effsize)`), suggesting participants chose correct answers more for dynamics recordings than articulation recordings.
 
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype = "dotted", color = "gray", size = 1) +
-  theme_pubr(base_size = 20, base_family = "Helvetica") +
-  labs(color = "")
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + theme_pubr(base_size = 20, base_family = "Helvetica")
 cor_ioi_1
@@
           xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
-  theme_pubr(base_size = 20, base_family = "Helvetica") +
-  labs(color = "")
+  theme_pubr(base_size = 20, base_family = "Helvetica")
 cor_kot_1
@@
           xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
-  theme_pubr(base_size = 20, base_family = "Helvetica") +
-  labs(color = "")
+  theme_pubr(base_size = 20, base_family = "Helvetica")
 cor_vel_1
@@
           xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
-  theme_pubr(base_size = 20, base_family = "Helvetica") +
-  labs(color = "")
+  theme_pubr(base_size = 20, base_family = "Helvetica")
 cor_vel_diff_1
@@
 In order to further explore which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted.
-Statistical model assumptions were tested using the *performance* R package [@ludecke_2021] and all assumptions were met.
+Statistical model assumptions were tested using the *performance* R package [@ludecke_2021] and most of the assumptions (see *Supplementary Material* for details) were met.
 Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.
@@
 
-Experiment 1 investigated which features of piano performance made musicians infer teaching intentions.
-The results demonstrated that performances with slower tempo were more likely to be judged as teaching by musicians regardless of which expressive technique was implemented in the piece.
+Experiment 1 investigated whether musicians could distinguish teaching recordings from performing recordings accurately and which features of piano performance made them infer teaching intentions.
+The results demonstrated that musicians could choose correct answers above chance.
+Also, it was found that the accuracy of participants' judgments was better for dynamics recordings than for articulation recordings.
+When it comes to how performance features contributed to participants' judments, performances with slower tempo were more likely to be judged as teaching by musicians regardless of which expressive technique was implemented in the piece.
 For articulation recordings, performances with longer legato and shorter staccato were tended to be judged as teaching.
 For dynamics recordings, performances with louder forte were more likely to be judged as teaching whereas there was no relationship between softer sound (i.e., piano) and participants' judgments as teaching.
-Importantly, performances with larger contrasts between forte and piano for both directions (i.e., from forte to piano, from piano to forte) were more likely to be judged as teaching.
+Importantly, performances with larger contrast between forte and piano for both directions (i.e., from forte to piano, from piano to forte) were more likely to be judged as teaching.
 This result may suggest that dynamics contrast might be reliably used to infer teaching intentions, rather than absolute dynamics values themselves.
@@
 ## Data analysis
-The data analysis was identical to Experiment 1.
+The data analysis was almost identical to Experiment 1.
 Only the 8th notes with expressive notations were included for data analysis.
@@
 source(here("experiment-2/analysis", "analysis.R"), chdir = TRUE)
+source(here("experiment-2/analysis/prereg_analysis", "prereg_analysis.R"), chdir = TRUE)
 ```
@@
 All results were reported as significant at *p* < 0.05.
+
+## Accuracy
+A one sample *t*-test was performed to compare the accuracy of participants' judgments against the chance level (50%).
+The mean percentage of correct answers [*M* = `r sprintf('%.1f', subset$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset$SD_Percent)`] was significantly higher than chance (*t*(`r ttest_all$parameter`) = `r sprintf('%.2f', ttest_all$statistic)`, *p* `r if(ttest_all$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_all$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_all$effsize)`).
+
+We also performed a one sample *t*-test for each technique separately.
+For articulation, the mean percentage of correct answers [*M* = `r sprintf('%.1f', subset_ad[Skill == "articulation"]$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset_ad[Skill == "articulation"]$SD_Percent)`] was not significantly different from chance (*t*(`r ttest_art$parameter`) = `r sprintf('%.2f', ttest_art$statistic)`, *p* `r if(ttest_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_art$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_art$effsize)`).
+Also for dynamics, the mean percentage of correct answers [*M* = `r sprintf('%.1f', subset_ad[Skill == "dynamics"]$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset_ad[Skill == "dynamics"]$SD_Percent)`] was not significantly different from chance (*t*(`r ttest_dyn$parameter`) = `r sprintf('%.2f', ttest_dyn$statistic)`, *p* `r if(ttest_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_dyn$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_dyn$effsize)`).
+A paired *t*-test revealed that there was no significant difference between the two techniques in terms of the accuracy (*t*(`r ttest_paired$parameter`) = `r sprintf('%.2f', ttest_paired$statistic)`, *p* `r if(ttest_paired$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_paired$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_paired$effsize)`).
 
@@
 ### Tempo (IOIs)
-Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_ioi_art$p.value))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-2}*).
-The Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (*p* `r if(ioi_dyn_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_dyn_norm_performance$p.value))}`).
-A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (*r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`).
+Unlike Experiment 1, there was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_ioi_art$p.value))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-2}*).
+Participants tended to identify slower performances as teaching for dynamics recordings.
+
+However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (*p* `r if(ioi_dyn_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_dyn_norm_performance$p.value))}`).
+A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (*r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`), suggesting that we need to be careful about the interpretation of the relationship between the performance tempi of dynamics recordings and participants' judgments as teaching.
 
@@
           xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
-  theme_pubr(base_size = 20, base_family = "Helvetica") +
-  labs(color = "")
+  theme_pubr(base_size = 20, base_family = "Helvetica")
 cor_ioi_2
@@
 For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (*r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`).
-However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (*r(`r cor_kot_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_pia$p.value))}`), suggesting that performances with louder staccato were more likely to be considered as teaching performance (*Figure \ref{fig:kot-2}*, right).
+However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (*r(`r cor_kot_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_pia$p.value))}`), suggesting that performances with staccato-style piano were more likely to be considered as teaching performance (*Figure \ref{fig:kot-2}*, right).
 
@@
           xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
-  theme_pubr(base_size = 20, base_family = "Helvetica") +
-  labs(color = "")
+  theme_pubr(base_size = 20, base_family = "Helvetica")
 cor_kot_2
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
-  theme_pubr(base_size = 20, base_family = "Helvetica") +
-  labs(color = "")
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + xlim(50, 102) + ylim(0, 100) +
+  theme_pubr(base_size = 20, base_family = "Helvetica")
 cor_vel_2
@@
 Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).
-The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; *p* `r if(vel_diff_ftop_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ftop_norm_performance$p.value))}`, Piano to Forte; *p* `r if(vel_diff_ptof_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ptof_norm_performance$p.value))}`).
+The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; *p* `r if(vel_diff_ftop_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', vel_diff_ftop_norm_performance$p.value))}`, Piano to Forte; *p* `r if(vel_diff_ptof_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ptof_norm_performance$p.value))}`).
 Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop_spearman$estimate))`, *p* `r if(cor_vel_diff_ftop_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop_spearman$p.value))}`, Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof_spearman$estimate))`, *p* `r if(cor_vel_diff_ptof_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ptof_spearman$p.value))}`).
@@
           xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
-  theme_pubr(base_size = 20, base_family = "Helvetica") +
-  labs(color = "")
+  theme_pubr(base_size = 20, base_family = "Helvetica")
 cor_vel_diff_2
@@
 As Experiment 1, we performed multiple regression analyses to further explore which feature of performance contributed the most to participants' judgments as teaching.
+Statistical model assumptions were tested and most of the assumptions (see *Supplementary Material* for details) were met.
 Again, since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.
@@
 # Discussion
+The aim of Experiment 2 was to replicate the results of Experiment 1 with a more naturalistic piece of music.
+However, unlike Experiment 1, tempo (IOIs) does not seem to contribute to participants' judgments as teaching.
+This could be that in a musically complex piece, tempo might have been considered to be one of the interpretations of music and was not used as a reliable cue to infer teaching intentions.
+Also, articulation (KOT) does not seem to contribute to participants' judgments as teaching.
+As Experiment 1, dynamics (KV) seems to be used as a reliable cue to detect the characteristic of teaching performance.
+We could successfully replicate that performances with larger contrast between forte and piano seem to be considered as teaching.
+Moreover, performances with both exaggerated forte and piano were considered to be for teaching.
+These consistent results suggest that loudness (dynamics) might be used as a reliable cue to infer teaching intentions regardless of the complexity of a musical piece.
+
+Multiple regression analyses also implied that tempo feature was not a strong predictor of participants' judgments as teaching when listening to a musically complex piece.
+However, dynamics contrast seems to be a strong predictor of participants' judgments as teaching, especially for dynamics recordings.
+This finding also suggests that loudness might be a strong cue to infer pedagogical intentions even in a naturalistic piece of music.
 
 # General discussion
+
+The present study investigated whether and how musician infer pedagogical intentions by listening to piano recordings.
+In both Experiment 1 and 2, participants were able to choose correct answers accurately more than chance (50%).
+However, the results showed that the accuracy was relatively low (52.7 % in Experiment 1; 52.8 % in Experiment 2).
+This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al.
+(*submitted*) and all the selected recordings did not exhibit the characteristics of teaching performance (e.g., slow performance, exaggeration).
+The reason why we randomly selected the stimuli from each condition (i.e., teaching or performing) was because all the characteristics of teaching performance (e.g., IOIs, KOT, KV) were intercorrelated and it was difficult to choose stimuli based on one single criterion.
+Future research should examine if musicians answer more accurately with more experimentally controlled stimuli.
+
+In order to examine which features of piano performance make musicians infer pedagogical intentions, we performed correlation and multiple regression analysis.
+Across the two experiments, it was found that loudness, particularly larger contrast between forte and piano, strongly contributed to participants' judgments when listening to dynamics recordings.
+On the other hand, unlike what we predicted, slower performance was only considered to be for teaching in Experiment 1 where the stimuli consisted of a simple musical scale.
+Also, we could not find that performances with exaggerated articulation (e.g., longer legato and shorter staccato) were more likely to be judged as teaching in Experiment 2.
+This might suggest that some characteristics of performance are not necessarily used or reliable to infer performers' intentions when listening to musically complex pieces.
+It can be speculated that certain modulations are too subtle so that participants could not perceive them.
+Another possibility is that modulations can also be considered as one of the expressions or interpretations.
+
+In the current study, we exclusively recruited musicians to explore our research questions.
+The reason why we recruited musicians only was because the concepts of articulation and dynamics seem to be difficult for those who don't play an instrument to understand in the current settings.
+It would be important to investigate how novices perceive and infer pedagogical intentions differently from musicians, who already have some experience in playing music.
 

### 2022-03-14 paper/manuscript.tex
first draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 In the current study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
-They were asked to judge whether each recording was produced to teach the designated expressive technique or not.
-We quantified recordings with regard to tempo, articulation and dynamics.
-We performed correlation and multiple regression analysis to investigate which features of piano performance made musicians infer teaching intention.
-The findings in Experiment 1 with a simple musical scale demonstrated that slower tempo contributed to musicians' judgments as teaching regardless of the techniques.
+Half of the recordings was produced when pianists were instructed to play as if they were teaching the designated musical technique in a lesson (i.e., teaching recordings) whereas the other half was produced when pianists were instructed to play as if they were performing it in a concert (i.e., performing recordings).
+Participants were asked to judge whether each recording was produced for teaching purposes or not.
+We calculated the accuracy of participants' judgments to investigate whether they could distinguish teaching recordings from performing recordings.
+Also, recordings were quantified with regard to tempo, articulation and dynamic so that we could perform correlation and multiple regression analysis to investigate which features of piano performance made musicians infer teaching intentions.
+The findings in Experiment 1 with a simple musical scale demonstrated that the accuracy of musicians' judgments was significantly above chance.
+Also, it was found that slower tempo contributed to musicians' judgments as teaching regardless of the techniques.
 Moreover, performances with exaggeration for each technique (e.g., longer legato, shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching.
 Experiment 2 aimed to replicate the findings of Experiment 1 with a more naturalistic piece.
-We only replicated the findings related to dynamics (in particular, larger contrast between forte and piano).
+As Experiment 1, the accuracy of musicians' judgments was significantly above chance.
+However, we only replicated that performances with exaggerated dynamics (in particular, larger contrast between forte and piano) were more likely to be judged as teaching.
 Taken together, loudness (dynamics) seems to be reliably used to infer teaching intentions regardless of the complexity of a musical piece.
@@
 In pedagogical settings where teachers are supposed to convey useful information to learners, it has been found that teachers often modulate their behaviour for teaching purposes.
-For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills (e.g., Brand, Baldwin, \& Ashburn, 2002; Kuhl, 2004).
+For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills (e.g., Brand, Baldwin, \& Ashburn, 2002; Saint-Georges et al., 2013).
 Also, some studies have revealed that even towards adult learners, people modulated their speech and action in the similar way as they did for infants (McEllin, Knoblich, \& Sebanz, 2017; Uther, Knoll, \& Burnham, 2007).
@@
 Tominaga, Knoblich \& Sebanz (\emph{submitted}) extended this line of research to expertise transmission where skills to be acquired are complex such as artistic expression.
-Based on the assumption that expert pianists are very good at controlling and modulating their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
+Based on the assumption that expert pianists are skilled at controlling their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
 The results demonstrated that expert pianists could successfully modulate their performance by playing slower or exaggerating relevant aspects of the performance (e.g., producing shorter staccato or making a larger contrast between forte and piano) to teach musical expressive techniques.
@@
 
-Furthermore, some research in the field of action expertise suggest that motor simulation (i.e., using one's own motor systems to simulate an action) plays a key role to understand observed actions.
-For example, expert basketball players were better at predicting the outcome of a free shot compared to expert observers (coaches or sports journalists) and novices (Aglioti, Cesari, Romani, \& Urgesi, 2008).
-Also, it was found that deceptive intentions of fake basketball passes were detected from non-verbal bodily cues only by expert basketball players (Sebanz \& Shiffrar, 2009).
-Taken together, people seem to be able to infer informative intentions by observing actions accurately if they have enough expertise to simulate the actions.
-
-In the domain of music, musical emotion is often communicated by sound alone and listeners seem to be able to infer performers' intended emotions only by listening to recorded performances (e.g., Akkermans et al., 2019; Gabrielsson \& Juslin, 1996).
-It has been known that musicians are generally more accurate to decode emotions from performances (Battcock \& Schutz, 2021; Lima \& Castro, 2011).
-Repp and Knoblich (2004) also found that expert pianists could distinguish their own performance from others' performances by listening to recordings.
-These results suggest that musical expertise may enable people identify and infer intentions accurately by using their own motor resources.
-
 Here we investigated whether the modulations that expert pianists made when they intended to teach were also perceived by listeners as conveying pedagogical intentions.
-We quantified recordings with regard to tempo, articulation and dynamics and examined which features of piano performance made musicians infer teaching intentions.
-We performed correlation and multiple regression analysis to investigate relationships between performance features of a recording and how likely people think the recording was produced for teaching purposes.
+We assumed that listeners would be able to infer intentions only by listening to recordings because some research revealed that musical emotion is often communicated by sound alone and that listeners seem to be able to infer performers' intended emotions only by listening to recorded performances (e.g., Akkermans et al., 2019; Gabrielsson \& Juslin, 1996).
+In the present study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
+They were asked to judge whether each recording was produced for teaching purposes or not.
+Half of the recordings was produced when pianists were instructed to play as if they were teaching the designated musical technique in a lesson (i.e., teaching recordings) whereas the other half was produced when pianists were instructed to play as if they were performing it in a concert (i.e., performing recordings).
+First, we calculated the accuracy of participants' judgments to examine whether they could distinguish teaching recordings from performing recordings.
+Furthermore, recordings were quantified with regard to tempo, articulation and dynamic.
+We performed correlation and multiple regression analysis to examine relationships between performance features of the recordings and how likely people think the recordings were produced for teaching purposes.
 Various piano recordings were collected from our previous experiments (Tominaga et al., \emph{submitted}).
 The recordings were performed by various pianists multiple times, therefore the recordings contained many variations in terms of timing, articulation and dynamics.
-In the current study, we asked musically trained participants to judge which each recording was performed for teaching purposes.
-If performers' intentions are successfully communicated with learners, pedagogical behavioural features in our previous experiments such as slower demonstration and exaggerated performance should be identified and used to infer teaching intentions.
-We examined which features of piano performance were correlated with participants judgments as ``teaching''.
+
+If performers' intentions are successfully communicated with learners, musicians would be able to distinguish teaching recordings from performing recordings.
+Moreover, pedagogical behavioural features in our previous experiments such as slower demonstration and exaggerated performance should be identified and used to infer teaching intentions.
+We examined which features of piano performance were correlated with participants judgments as teaching.
 We conducted Experiment 1 with a simple musical scale and Experiment 2 with a more naturalistic piece of music to replicate the findings from Experiment 1.
@@
 Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files.
-Multiple pianists played one piece of music with a musical expressive techniques of either articulation (\emph{Figure \ref{fig:stim1}}, A) or dynamics (\emph{Figure \ref{fig:stim1}}, B).
+Multiple pianists played one piece of music with a musical expressive technique of either articulation (\emph{Figure \ref{fig:stim1}}, A) or dynamics (\emph{Figure \ref{fig:stim1}}, B).
 Articulation refers to the smoothness of sound, which is comprised of legato and staccato.
@@
 In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert).
-In total, we obtained 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition.
-
-For the current experiment, 96 recordings were chosen from the valid performances in Tominaga et al.~(\emph{submitted}; Experiment 1).
+In Tominaga et al.~(\emph{submitted}; Experiment 1), there were 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition.
+For the current experiment, 96 recordings were chosen from the valid performances.
 We randomly sampled 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition.
@@
 Stimuli (MIDI files) were converted to numerical data in terms of time, pitch and velocity for the onset and offset of each note using the \emph{tuneR} R package (\url{https://cran.r-project.org/web/packages/tuneR/tuneR.pdf}).
+
+\hypertarget{accuracy}{%
+\subsubsection{Accuracy}\label{accuracy}}
+
+First, we examined whether participants could accurately distinguish the stimuli chosen from the teaching condition in Tominaga et al., (\emph{submitted}; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (\emph{submitted}; Experiment 1) as performing.
+We compared how accurate participants were against the chance level (50\%).
+The correct responses were either pressing the yes button when listening to the teaching recordings or pressing the no button when listening to the performing recordings.
+The incorrect responses were either pressing the yes button when listening to the performing recordings or pressing the no button when listening to the teaching recordings.
+
+\hypertarget{correlation-and-multiple-regression}{%
+\subsubsection{Correlation and multiple regression}\label{correlation-and-multiple-regression}}
 
@@
 All results were reported as significant at \emph{p} \textless{} 0.05.
+
+\hypertarget{accuracy-1}{%
+\subsection{Accuracy}\label{accuracy-1}}
+
+A one sample \emph{t}-test was performed to compare the accuracy of participants' judgments against the chance level (50\%).
+The mean percentage of correct answers {[}\emph{M} = 52.7, \emph{SD} = 4.90{]} was significantly higher than chance (\emph{t}(19) = 2.47, \emph{p} = 0.02, cohen's \emph{d} = 0.55).
+
+We also performed a one sample \emph{t}-test for each technique separately.
+For articulation, the mean percentage of correct answers {[}\emph{M} = 50.2, \emph{SD} = 6.55{]} was not significantly different from chance (\emph{t}(19) = 0.14, \emph{p} = 0.89, cohen's \emph{d} = 0.03).
+For dynamics, the mean percentage of correct answers {[}\emph{M} = 55.2, \emph{SD} = 7.81{]} was significantly higher than chance (\emph{t}(19) = 2.98, \emph{p} = 0.01, cohen's \emph{d} = 0.67).
+A paired \emph{t}-test revealed that there was a significant difference between the two techniques in terms of the accuracy (\emph{t}(19) = -2.12, \emph{p} = 0.05, cohen's \emph{d} = -0.69), suggesting participants chose correct answers more for dynamics recordings than articulation recordings.
 
@@
 In order to further explore which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted.
-Statistical model assumptions were tested using the \emph{performance} R package (Lüdecke, Ben-Shachar, Patil, Waggoner, \& Makowski, 2021) and all assumptions were met.
+Statistical model assumptions were tested using the \emph{performance} R package (Lüdecke, Ben-Shachar, Patil, Waggoner, \& Makowski, 2021) and most of the assumptions (see \emph{Supplementary Material} for details) were met.
 Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in \emph{Data analysis}).
@@
 
-The data analysis was identical to Experiment 1.
+The data analysis was almost identical to Experiment 1.
 Only the 8th notes with expressive notations were included for data analysis.
@@
 
+\hypertarget{accuracy-2}{%
+\subsection{Accuracy}\label{accuracy-2}}
+
+A one sample \emph{t}-test was performed to compare the accuracy of participants' judgments against the chance level (50\%).
+The mean percentage of correct answers {[}\emph{M} = 52.8, \emph{SD} = 4.78{]} was significantly higher than chance (\emph{t}(19) = 2.66, \emph{p} = 0.02, cohen's \emph{d} = 0.60).
+
+We also performed a one sample \emph{t}-test for each technique separately.
+For articulation, the mean percentage of correct answers {[}\emph{M} = 52.4, \emph{SD} = 6.94{]} was not significantly different from chance (\emph{t}(19) = 1.52, \emph{p} = 0.14, cohen's \emph{d} = 0.34).
+Also for dynamics, the mean percentage of correct answers {[}\emph{M} = 53.3, \emph{SD} = 8.53{]} was not significantly different from chance (\emph{t}(19) = 1.75, \emph{p} = 0.10, cohen's \emph{d} = 0.39).
+A paired \emph{t}-test revealed that there was no significant difference between the two techniques in terms of the accuracy (\emph{t}(19) = -0.35, \emph{p} = 0.73, cohen's \emph{d} = -0.13).
+
 \hypertarget{correlation-1}{%
@@
 
-Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; \emph{r(34)} = .25, \emph{p} = 0.15, Dynamics; \emph{r(34)} = .39, \emph{p} = 0.02, \emph{Figure \ref{fig:ioi-2}}).
-The Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (\emph{p} = 0.080).
-A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (\emph{r(34)} = .29, \emph{p} = 0.091).
+Unlike Experiment 1, there was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; \emph{r(34)} = .25, \emph{p} = 0.15, Dynamics; \emph{r(34)} = .39, \emph{p} = 0.02, \emph{Figure \ref{fig:ioi-2}}).
+Participants tended to identify slower performances as teaching for dynamics recordings.
+
+However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (\emph{p} = 0.080).
+A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (\emph{r(34)} = .29, \emph{p} = 0.091), suggesting that we need to be careful about the interpretation of the relationship between the performance tempi of dynamics recordings and participants' judgments as teaching.
 
@@
 For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (\emph{r(34)} = -.11, \emph{p} = 0.52).
-However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r(34)} = -.35, \emph{p} = 0.034), suggesting that performances with louder staccato were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).
+However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r(34)} = -.35, \emph{p} = 0.034), suggesting that performances with staccato-style piano were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).
 
@@
 Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r(34)} = -.75, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r(34)} = .59, \emph{p} \textless{} 0.001).
-The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; \emph{p} = 0.850, Piano to Forte; \emph{p} = 0.008).
+The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; \emph{p} = 0.85, Piano to Forte; \emph{p} = 0.008).
 Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; \emph{r(34)} = -.73, \emph{p} \textless{} 0.001, Piano to Forte; \emph{r(34)} = .57, \emph{p} \textless{} 0.001).
@@
 As Experiment 1, we performed multiple regression analyses to further explore which feature of performance contributed the most to participants' judgments as teaching.
+Statistical model assumptions were tested and most of the assumptions (see \emph{Supplementary Material} for details) were met.
 Again, since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in \emph{Data analysis} in Experiment 1).
@@
 
+The aim of Experiment 2 was to replicate the results of Experiment 1 with a more naturalistic piece of music.
+However, unlike Experiment 1, tempo (IOIs) does not seem to contribute to participants' judgments as teaching.
+This could be that in a musically complex piece, tempo might have been considered to be one of the interpretations of music and was not used as a reliable cue to infer teaching intentions.
+Also, articulation (KOT) does not seem to contribute to participants' judgments as teaching.
+As Experiment 1, dynamics (KV) seems to be used as a reliable cue to detect the characteristic of teaching performance.
+We could successfully replicate that performances with larger contrast between forte and piano seem to be considered as teaching.
+Moreover, performances with both exaggerated forte and piano were considered to be for teaching.
+These consistent results suggest that loudness (dynamics) might be used as a reliable cue to infer teaching intentions regardless of the complexity of a musical piece.
+
+Multiple regression analyses also implied that tempo feature was not a strong predictor of participants' judgments as teaching when listening to a musically complex piece.
+However, dynamics contrast seems to be a strong predictor of participants' judgments as teaching, especially for dynamics recordings.
+This finding also suggests that loudness might be a strong cue to infer pedagogical intentions even in a naturalistic piece of music.
+
 \hypertarget{general-discussion}{%
 \section{General discussion}\label{general-discussion}}
+
+The present study investigated whether and how musician infer pedagogical intentions by listening to piano recordings.
+In both Experiment 1 and 2, participants were able to choose correct answers accurately more than chance (50\%).
+However, the results showed that the accuracy was relatively low (52.7 \% in Experiment 1; 52.8 \% in Experiment 2).
+This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al.~(\emph{submitted}) and all the selected recordings did not exhibit the characteristics of teaching performance (e.g., slow performance, exaggeration).
+The reason why we randomly selected the stimuli from each condition (i.e., teaching or performing) was because all the characteristics of teaching performance (e.g., IOIs, KOT, KV) were intercorrelated and it was difficult to choose stimuli based on one single criterion.
+Future research should examine if musicians answer more accurately with more experimentally controlled stimuli.
+
+In order to examine which features of piano performance make musicians infer pedagogical intentions, we performed correlation and multiple regression analysis.
+Across the two experiments, it was found that loudness, particularly larger contrast between forte and piano, strongly contributed to participants' judgments when listening to dynamics recordings.
+On the other hand, unlike what we predicted, slower performance was only considered to be for teaching in Experiment 1 where the stimuli consisted of a simple musical scale.
+Also, we could not find that performances with exaggerated articulation (e.g., longer legato and shorter staccato) were more likely to be judged as teaching in Experiment 2.
+This might suggest that some characteristics of performance are not necessarily used or reliable to infer performers' intentions when listening to musically complex pieces.
+It can be speculated that certain modulations are too subtle so that participants could not perceive them.
+Another possibility is that modulations can also be considered as one of the expressions or interpretations.
+
+In the current study, we exclusively recruited musicians to explore our research questions.
+The reason why we recruited musicians only was because the concepts of articulation and dynamics seem to be difficult for those who don't play an instrument to understand in the current settings.
+It would be important to investigate how novices perceive and infer pedagogical intentions differently from musicians, who already have some experience in playing music.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-aglioti_2008}{}}%
-Aglioti, S.
-M., Cesari, P., Romani, M., \& Urgesi, C.
-(2008).
-Action anticipation and motor resonance in elite basketball players.
-\emph{Nature Neuroscience}, \emph{11}(9), 1109--1116.
-\url{https://doi.org/10.1038/nn.2182}
-
 \leavevmode\vadjust pre{\hypertarget{ref-akkermans_2019}{}}%
@@
 \url{https://doi.org/10.1080/02699931.2018.1541312}
-
-\leavevmode\vadjust pre{\hypertarget{ref-battcock_2021}{}}%
-Battcock, A., \& Schutz, M.
-(2021).
-Emotion and expertise: How listeners with formal music training use cues to perceive emotion.
-\emph{Psychological Research}.
-\url{https://doi.org/10.1007/s00426-020-01467-1}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kuhl_2004}{}}%
-Kuhl, P. K. (2004). Early language acquisition: Cracking the speech code. \emph{Nature Reviews Neuroscience}, \emph{5}(11), 831--843. \url{https://doi.org/10.1038/nrn1533}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lima_2011}{}}%
-Lima, C.
-F., \& Castro, S.
-L.
-(2011).
-Speaking to the trained ear: Musical expertise enhances the recognition of emotions in speech prosody.
-\emph{Emotion}, \emph{11}(5), 1021--1031.
-\url{https://doi.org/10.1037/a0024521}
-
 \leavevmode\vadjust pre{\hypertarget{ref-ludecke_2021}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-repp_2004}{}}%
-Repp, B.
-H., \& Knoblich, G.
-(2004).
-Perceiving {Action Identity}: {How Pianists Recognize Their Own Performances}.
-\emph{Psychol Sci}, \emph{15}(9), 604--609.
-\url{https://doi.org/10.1111/j.0956-7976.2004.00727.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sebanz_2009}{}}%
-Sebanz, N., \& Shiffrar, M.
-(2009).
-Detecting deception in a bluffing body: {The} role of expertise.
-\emph{Psychonomic Bulletin and Review}, \emph{16}(1), 170--175.
-\url{https://doi.org/10.3758/PBR.16.1.170}
+\leavevmode\vadjust pre{\hypertarget{ref-saint-georges_2013}{}}%
+Saint-Georges, C., Chetouani, M., Cassel, R., Apicella, F., Mahdhaoui, A., Muratori, F., \ldots{} Cohen, D.
+(2013).
+Motherese in {Interaction}: {At} the {Cross-Road} of {Emotion} and {Cognition}?
+({A Systematic Review}).
+\emph{PLOS ONE}, \emph{8}(10), e78103.
+\url{https://doi.org/10.1371/journal.pone.0078103}
 

### 2022-03-14 experiment-1/analysis/analysis.Rmd
update analysis for first draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
+### Remove outliers for dynamics (outside 2SD)
+```{r, echo = FALSE}
+mean = mean(ioi[Skill == "dynamics"]$Mean)
+sd = sd(ioi[Skill == "dynamics"]$Mean)
+
+# normality check
+shapiro.test(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+shapiro.test(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+
+qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+cor.test(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+```
+
 # Tempo at transition points
@@
 
+### Remove outliers for dynamics (outside 2SD)
+```{r, echo = FALSE}
+mean = mean(ioi_tra[Skill == "dynamics"]$Mean)
+sd = sd(ioi_tra[Skill == "dynamics"]$Mean)
+
+# normality check
+shapiro.test(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+shapiro.test(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+qqnorm(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+qqline(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+
+qqnorm(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+qqline(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+cor.test(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+```
+
 # CV (tempo variability)
@@
 
+### Remove outliers for articulation (outside 2SD)
+```{r, echo = FALSE}
+mean = mean(cv[Skill == "articulation"]$CV)
+sd = sd(cv[Skill == "articulation"]$CV)
+
+# normality check
+shapiro.test(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
+shapiro.test(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+
+qqnorm(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
+qqline(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
+
+qqnorm(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+qqline(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+
+cor.test(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching, cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+```
+
 ## Dynamics (n.s.)
@@
 
+### Remove outliers for dynamics (outside 2SD)
+```{r, echo = FALSE}
+mean = mean(cv[Skill == "dynamics"]$CV)
+sd = sd(cv[Skill == "dynamics"]$CV)
+
+# normality check
+shapiro.test(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
+shapiro.test(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+
+qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
+qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
+
+qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+
+cor.test(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching, cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+```
 # KOT
@@
 
+### Remove outliers for forte (outside 2SD)
+```{r, echo = FALSE}
+mean = mean(kot_all[Subcomponent == "Forte"]$Mean)
+sd = sd(kot_all[Subcomponent == "Forte"]$Mean)
+
+# normality check
+shapiro.test(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+shapiro.test(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+qqnorm(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+qqline(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+
+qqnorm(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+qqline(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+cor.test(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+```
+
 ## Piano (n.s.)
@@
 cor_kot_pia_spearman
+```
+
+### Remove outliers for piano (outside 2SD)
+```{r, echo = FALSE}
+mean = mean(kot_all[Subcomponent == "Piano"]$Mean)
+sd = sd(kot_all[Subcomponent == "Piano"]$Mean)
+
+# normality check
+shapiro.test(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+shapiro.test(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+qqnorm(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+qqline(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+
+qqnorm(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+qqline(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+cor.test(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
 ```
@@
 
-## Forte (***)
+## Forte (**)
 ```{r, echo = FALSE}
@@
 cor_vel_leg_spearman
+```
+
+### Remove outliers for legato (outside 2SD)
+```{r, echo = FALSE}
+mean = mean(vel_all[Subcomponent == "Legato"]$Mean)
+sd = sd(vel_all[Subcomponent == "Legato"]$Mean)
+
+# normality check
+shapiro.test(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+shapiro.test(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+qqnorm(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+qqline(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+
+qqnorm(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+qqline(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+cor.test(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
 ```
@@
 cor_vel_diff_ltos_spearman
+```
+
+### Remove outliers for ltos (outside 2SD)
+```{r, echo = FALSE}
+mean = mean(vel_diff_all[Subcomponent == "LtoS"]$Mean)
+sd = sd(vel_diff_all[Subcomponent == "LtoS"]$Mean)
+
+# normality check
+shapiro.test(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+shapiro.test(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+qqnorm(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+qqline(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+
+qqnorm(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+qqline(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+cor.test(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
 ```

### 2022-03-14 experiment-1/analysis/prereg_analysis/prereg_analysis.Rmd
update analysis for first draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ## Design
-
 - 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques separately. The order of the blocks was counterbalanced across participants.
@@
 if (!require("afex")) {install.packages("afex"); require("afex")}
+if (!require("rstatix")) {install.packages("rstatix"); require("rstatix")}
 ```
@@
 
-t.test(ind_data$Percent, mu = 50, alternative = "two.sided")
+ttest_all <- t.test(ind_data$Percent, mu = 50, alternative = "two.sided")
+ttest_all
+```
+
+### Effect size
+```{r, echo = FALSE}
+coheneff_all <- ind_data %>% cohens_d(Percent ~ 1, mu = 50)
+coheneff_all
 ```
@@
 ```{r plot2, echo = FALSE}
-ind_data_ad <- data[subjectNumber != 4, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Skill)]
+ind_data_ad <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Skill)]
 ind_data_ad <- ind_data_ad[order(subjectNumber, Skill)]
@@
 
-t.test(ind_data_ad[Skill == "articulation"]$Percent, mu = 50, alternative = "two.sided")
+ttest_art <- t.test(ind_data_ad[Skill == "articulation"]$Percent, mu = 50, alternative = "two.sided")
+ttest_art
+```
+
+### Effect size
+```{r, echo = FALSE}
+coheneff_art <- ind_data_ad[Skill == "articulation"] %>% cohens_d(Percent ~ 1, mu = 50)
+coheneff_art
 ```
@@
 
-t.test(ind_data_ad[Skill == "dynamics"]$Percent, mu = 50, alternative = "two.sided")
+ttest_dyn <- t.test(ind_data_ad[Skill == "dynamics"]$Percent, mu = 50, alternative = "two.sided")
+ttest_dyn
+```
+
+### Effect size
+```{r, echo = FALSE}
+coheneff_dyn <- ind_data_ad[Skill == "dynamics"] %>% cohens_d(Percent ~ 1, mu = 50)
+coheneff_dyn
 ```
@@
 
-t.test(ind_data_ad[Skill == "articulation"]$Percent, ind_data_ad[Skill == "dynamics"]$Percent, paired = TRUE)
+ttest_paired <- t.test(ind_data_ad[Skill == "articulation"]$Percent, ind_data_ad[Skill == "dynamics"]$Percent, paired = TRUE)
+ttest_paired
+```
+### Effect size
+```{r, echo = FALSE}
+coheneff_paired <- ind_data_ad %>% cohens_d(Percent ~ Skill, mu = 50)
+coheneff_paired
 ```

### 2022-03-14 experiment-2/analysis/analysis.Rmd
update analysis for first draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-## Dynamics (n.s.)
+## Dynamics (*)
 ```{r, echo = FALSE}
@@
 
-## Dynamics (*)
+## Dynamics (**)
 ```{r, echo = FALSE}
@@
 cor.test(cv[Skill == "dynamics"]$Teaching, cv[Skill == "dynamics"]$CV, method = "spearman", exact = FALSE)
+```
+
+### Remove outliers for dynamics (outside 2SD)
+```{r, echo = FALSE}
+mean = mean(cv[Skill == "dynamics"]$CV)
+sd = sd(cv[Skill == "dynamics"]$CV)
+
+# normality check
+shapiro.test(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
+shapiro.test(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+
+qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
+qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
+
+qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+
+cor.test(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching, cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
 ```
@@
 
+### Remove outliers for forte (outside 2SD)
+```{r, echo = FALSE}
+mean = mean(kot_all[Subcomponent == "Forte"]$Mean)
+sd = sd(kot_all[Subcomponent == "Forte"]$Mean)
+
+# normality check
+shapiro.test(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+shapiro.test(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+qqnorm(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+qqline(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+
+qqnorm(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+qqline(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+cor.test(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+```
+
 ## Piano (*)
@@
 
-## Piano (*)
+### Remove outliers for forte (outside 2SD)
+```{r, echo = FALSE}
+mean = mean(vel_all[Subcomponent == "Forte"]$Mean)
+sd = sd(vel_all[Subcomponent == "Forte"]$Mean)
+
+# normality check
+shapiro.test(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+shapiro.test(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+qqnorm(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+qqline(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+
+qqnorm(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+qqline(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+cor.test(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+```
+
+## Piano (**)
 ```{r, echo = FALSE}
@@
 ```
+
+### Remove outliers for forte (outside 2SD)
+```{r, echo = FALSE}
+mean = mean(vel_all[Subcomponent == "Piano"]$Mean)
+sd = sd(vel_all[Subcomponent == "Piano"]$Mean)
+
+# normality check
+shapiro.test(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+shapiro.test(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+qqnorm(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+qqline(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+
+qqnorm(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+qqline(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+cor.test(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+```
+
 ## Legato (n.s.)
@@
 
+### Remove outliers for ftop (outside 2SD)
+```{r, echo = FALSE}
+mean = mean(vel_diff_all[Subcomponent == "FtoP"]$Mean)
+sd = sd(vel_diff_all[Subcomponent == "FtoP"]$Mean)
+
+# normality check
+shapiro.test(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+shapiro.test(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+qqnorm(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+qqline(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+
+qqnorm(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+qqline(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+cor.test(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+```
+
 ## Piano to Forte (***)
@@
 ```
+
+### Remove outliers for ltop (outside 2SD)
+```{r, echo = FALSE}
+mean = mean(vel_diff_all[Subcomponent == "PtoF"]$Mean)
+sd = sd(vel_diff_all[Subcomponent == "PtoF"]$Mean)
+
+# normality check
+shapiro.test(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+shapiro.test(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+qqnorm(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+qqline(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+
+qqnorm(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+qqline(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+cor.test(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+```
+
 ## Legato to Staccato (n.s.)

### 2022-03-14 experiment-2/analysis/prereg_analysis/prereg_analysis.Rmd
update analysis for first draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 - 36 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 72 stimuli).
-The half of them was selected from the teaching condition and the other half was from the performing condition.
+Half of them was selected from the teaching condition and the other half was from the performing condition.
   + 18 for teaching-articulation performances
@@
 ## Design
-
-- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques (expressions) separately. The order of the blocks was counterbalanced across participants.
-- 36 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented across participants.
+- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques separately. The order of the blocks was counterbalanced across participants.
+- 36 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented within a block.
 

### 2022-03-14 experiment-1/analysis/analysis.R

@@ -197,6 +197,23 @@ cor_ioi_dyn_spearman <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill ==
 cor_ioi_dyn_spearman
 
 
+## ---- echo = FALSE------------------------------------------------------------
+mean = mean(ioi[Skill == "dynamics"]$Mean)
+sd = sd(ioi[Skill == "dynamics"]$Mean)
+
+# normality check
+shapiro.test(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+shapiro.test(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+
+qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+cor.test(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+
 ## ----ioi-tra-all, echo = FALSE------------------------------------------------
 ioi_tra <- dt_ioi[Subcomponent == "LtoS" | Subcomponent == "StoL" | Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill)]
 
@@ -246,6 +263,23 @@ cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mea
 cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
 
 
+## ---- echo = FALSE------------------------------------------------------------
+mean = mean(ioi_tra[Skill == "dynamics"]$Mean)
+sd = sd(ioi_tra[Skill == "dynamics"]$Mean)
+
+# normality check
[…]

### 2022-03-14 experiment-1/analysis/prereg_analysis/prereg_analysis.R

@@ -1,4 +1,4 @@
-## ----packages, include = FALSE-----------------------------
+## ----packages, include = FALSE------------------------------------------------
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
 # midi
@@ -7,9 +7,10 @@ if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
 # stats
 if (!require("afex")) {install.packages("afex"); require("afex")}
+if (!require("rstatix")) {install.packages("rstatix"); require("rstatix")}
 
 
-## ----read, include = FALSE---------------------------------
+## ----read, include = FALSE----------------------------------------------------
 # read files and combine them
 data_ls <- list.files("../../data", pattern = "csv")
 combined <- lapply(data_ls, function(f){
@@ -39,7 +40,7 @@ all <- data[expMode == "experiment", .(N = .N, Sum = sum(Correct), Percent = (su
 all[order(subjectNumber, Condition, Skill)]
 
 
-## ----acc, echo = FALSE-------------------------------------
+## ----acc, echo = FALSE--------------------------------------------------------
 # individual
 ind_data <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber)]
 ind_data <- ind_data[order(subjectNumber)]
@@ -49,19 +50,25 @@ subset <- ind_data[, .(N = .N, Mean_Percent = mean(Percent), SD_Percent = sd(Per
 subset
 
 
-## ----plot, echo = FALSE------------------------------------
+## ----plot, echo = FALSE-------------------------------------------------------
 ggboxplot(ind_data, x = "N", y = "Percent", add = "dotplot", xlab = FALSE) + ylab("Correct %") + theme(axis.text.x = element_blank()) + geom_hline(yintercept = 50, linetype = "dashed")
 
 
-## ----t-test, echo = FALSE----------------------------------
+## ----t-test, echo = FALSE-----------------------------------------------------
 # normality check
 shapiro.test(ind_data$Percent)
 
-t.test(ind_data$Percent, mu = 50, alternative = "two.sided")
[…]

### 2022-03-14 experiment-2/analysis/analysis.R

@@ -197,6 +197,23 @@ cor_ioi_dyn_spearman <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill ==
 cor_ioi_dyn_spearman
 
 
+## ---- echo = FALSE------------------------------------------------------------
+mean = mean(ioi[Skill == "dynamics"]$Mean)
+sd = sd(ioi[Skill == "dynamics"]$Mean)
+
+# normality check
+shapiro.test(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+shapiro.test(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+
+qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+cor.test(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+
+
 ## ----ioi-tra-all, echo = FALSE------------------------------------------------
 ioi_tra <- dt_ioi[Subcomponent == "LtoS" | Subcomponent == "StoL" | Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill)]
 
@@ -248,6 +265,23 @@ cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mea
 cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
 
 
+## ---- echo = FALSE------------------------------------------------------------
+mean = mean(ioi_tra[Skill == "dynamics"]$Mean)
+sd = sd(ioi_tra[Skill == "dynamics"]$Mean)
+
+# normality check
[…]

### 2022-03-14 experiment-2/analysis/prereg_analysis/prereg_analysis.R

@@ -1,4 +1,4 @@
-## ----packages, include = FALSE-----------------------------
+## ----packages, include = FALSE-------------------------------------------------
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
 # midi
@@ -7,9 +7,10 @@ if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
 # stats
 if (!require("afex")) {install.packages("afex"); require("afex")}
+if (!require("rstatix")) {install.packages("rstatix"); require("rstatix")}
 
 
-## ----read, include = FALSE---------------------------------
+## ----read, include = FALSE-----------------------------------------------------
 # read files and combine them
 data_ls <- list.files("../../data", pattern = "csv")
 combined <- lapply(data_ls, function(f){
@@ -39,7 +40,7 @@ all <- data[expMode == "experiment", .(N = .N, Sum = sum(Correct), Percent = (su
 all[order(subjectNumber, Condition, Skill)]
 
 
-## ----acc, echo = FALSE-------------------------------------
+## ----acc, echo = FALSE---------------------------------------------------------
 # individual
 ind_data <- data[subjectNumber != 4, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber)]
 ind_data <- ind_data[order(subjectNumber)]
@@ -49,18 +50,24 @@ subset <- ind_data[, .(N = .N, Mean_Percent = mean(Percent), SD_Percent = sd(Per
 subset
 
 
-## ----plot, echo = FALSE------------------------------------
+## ----plot, echo = FALSE--------------------------------------------------------
 ggboxplot(ind_data, x = "N", y = "Percent", add = "dotplot", xlab = FALSE) + ylab("Correct %") + theme(axis.text.x = element_blank()) + geom_hline(yintercept = 50, linetype = "dashed")
 
 
-## ----t-test, echo = FALSE----------------------------------
+## ----t-test, echo = FALSE------------------------------------------------------
 # normality check
 shapiro.test(ind_data$Percent)
 
-t.test(ind_data$Percent, mu = 50, alternative = "two.sided")
[…]

### 2022-03-30 paper/manuscript.Rmd
remove spearman's tests
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 classoption       : "man"
-output            : papaja::apa6_word
+output            : papaja::apa6_pdf
 ---
@@
 ## Correlation
-A Pearson product-moment correlation coefficient was computed by default for correlation analysis and a Spearman's rank correlation coefficient was additionally computed if normality assumption was violated based on the Shapiro-Wilk normality test.
-
 ### Tempo (IOIs)
@@
 Participants tended to identify slower performances as teaching.
-
-However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (*p* `r if(ioi_dyn_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_dyn_norm_performance$p.value))}`).
-Therefore, a Spearman's rank correlation coefficient was additionally used to assess the relationship between performance tempi of dynamics recordings and participants' judgments.
-The result failed to reach significance (*r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`), suggesting that we need to be careful about the interpretation of the relationship between the performance tempi of dynamics recordings and participants' judgments as teaching.
 
@@
 For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`, Piano; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`, *Figure \ref{fig:kot-1}*, right).
-The Shapiro-Wilk normality test revealed that the distribution of KOT for dynamics recordings was not normally distributed (Forte; *p* `r if(kot_for_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', kot_for_norm_performance$p.value))}`, Piano; *p* `r if(kot_pia_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', kot_pia_norm_performance$p.value))}`).
-Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for_spearman$estimate))`, *p* `r if(cor_kot_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for_spearman$p.value))}`, Piano; *r(`r cor_kot_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia_spearman$estimate))`, *p* `r if(cor_kot_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia_spearman$p.value))}`).
 
@@
 For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r(`r cor_vel_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-1}*, left).
-The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings (legato parts) was not normally distributed (*p* `r if(vel_leg_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_leg_norm_performance$p.value))}`).
-A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg_spearman$estimate))`, *p* `r if(cor_vel_leg_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg_spearman$p.value))}`).
 
@@
 For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ltos$p.value))}`, From Staccato to Legato; *r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_stol$p.value))}`, *Figure \ref{fig:vel-diff-1}*, left).
-The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings (transition points from legato to staccato) was not normally distributed (*p* `r if(vel_diff_ltos_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ltos_norm_performance$p.value))}`).
-A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for the transition points from legato to staccato and participants' judgments as teaching (*r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos_spearman$estimate))`, *p* `r if(cor_vel_diff_ltos_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ltos_spearman$p.value))}`).
 
@@
 ## Multiple regression
-
 In order to further explore which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted.
@@
 ## Correlation
-As Experiment 1, a Pearson product-moment correlation coefficient was computed by default for correlation analysis and a Spearman's rank correlation coefficient was additionally computed if normality assumption was violated based on the Shapiro-Wilk normality test.
-
 ### Tempo (IOIs)
@@
 Participants tended to identify slower performances as teaching for dynamics recordings.
-
-However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (*p* `r if(ioi_dyn_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_dyn_norm_performance$p.value))}`).
-A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (*r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`), suggesting that we need to be careful about the interpretation of the relationship between the performance tempi of dynamics recordings and participants' judgments as teaching.
 
@@
 Specifically, performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_pia$p.value))}`) were more likely to be judged as teaching.
-The Shapiro-Wilk normality test revealed that the distribution of KV values for dynamics recordings was not normally distributed (Forte; *p* `r if(vel_for_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_for_norm_performance$p.value))}`, Piano' *p* `r if(vel_pia_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_pia_norm_performance$p.value))}`).
-Spearman's rank correlation coefficient also confirmed that performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for_spearman$estimate))`, *p* `r if(cor_vel_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for_spearman$p.value))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_pia_spearman$p.value))}`) were more likely to be judged as teaching.
 
@@
 Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).
-The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; *p* `r if(vel_diff_ftop_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', vel_diff_ftop_norm_performance$p.value))}`, Piano to Forte; *p* `r if(vel_diff_ptof_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ptof_norm_performance$p.value))}`).
-Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop_spearman$estimate))`, *p* `r if(cor_vel_diff_ftop_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop_spearman$p.value))}`, Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof_spearman$estimate))`, *p* `r if(cor_vel_diff_ptof_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ptof_spearman$p.value))}`).
 
@@
 ## Multiple regression
-
 As Experiment 1, we performed multiple regression analyses to further explore which feature of performance contributed the most to participants' judgments as teaching.

### 2022-03-30 paper/manuscript.tex
remove spearman's tests
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-A Pearson product-moment correlation coefficient was computed by default for correlation analysis and a Spearman's rank correlation coefficient was additionally computed if normality assumption was violated based on the Shapiro-Wilk normality test.
-
 \hypertarget{tempo-iois}{%
@@
 Participants tended to identify slower performances as teaching.
-
-However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (\emph{p} = 0.037).
-Therefore, a Spearman's rank correlation coefficient was additionally used to assess the relationship between performance tempi of dynamics recordings and participants' judgments.
-The result failed to reach significance (\emph{r(46)} = .27, \emph{p} = 0.066), suggesting that we need to be careful about the interpretation of the relationship between the performance tempi of dynamics recordings and participants' judgments as teaching.
 
@@
 For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r(46)} = -.04, \emph{p} = 0.81, Piano; \emph{r(46)} = -.19, \emph{p} = 0.19, \emph{Figure \ref{fig:kot-1}}, right).
-The Shapiro-Wilk normality test revealed that the distribution of KOT for dynamics recordings was not normally distributed (Forte; \emph{p} \textless{} 0.001, Piano; \emph{p} \textless{} 0.001).
-Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r(46)} = .15, \emph{p} = 0.31, Piano; \emph{r(46)} = -.12, \emph{p} = 0.43).
 
@@
 For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r(46)} = .10, \emph{p} = 0.52, Staccato; \emph{r(46)} = -.02, \emph{p} = 0.87, \emph{Figure \ref{fig:vel-1}}, left).
-The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings (legato parts) was not normally distributed (\emph{p} = 0.002).
-A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r(46)} = .03, \emph{p} = 0.84).
 
@@
 For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r(46)} = -.26, \emph{p} = 0.071, From Staccato to Legato; \emph{r(46)} = -.19, \emph{p} = 0.21, \emph{Figure \ref{fig:vel-diff-1}}, left).
-The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings (transition points from legato to staccato) was not normally distributed (\emph{p} = 0.007).
-A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for the transition points from legato to staccato and participants' judgments as teaching (\emph{r(46)} = -.23, \emph{p} = 0.12).
 
@@
 
-As Experiment 1, a Pearson product-moment correlation coefficient was computed by default for correlation analysis and a Spearman's rank correlation coefficient was additionally computed if normality assumption was violated based on the Shapiro-Wilk normality test.
-
 \hypertarget{tempo-iois-1}{%
@@
 Participants tended to identify slower performances as teaching for dynamics recordings.
-
-However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (\emph{p} = 0.080).
-A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (\emph{r(34)} = .29, \emph{p} = 0.091), suggesting that we need to be careful about the interpretation of the relationship between the performance tempi of dynamics recordings and participants' judgments as teaching.
 
@@
 Specifically, performances with louder forte (\emph{r(34)} = .45, \emph{p} = 0.007) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.006) were more likely to be judged as teaching.
-The Shapiro-Wilk normality test revealed that the distribution of KV values for dynamics recordings was not normally distributed (Forte; \emph{p} = 0.048, Piano' \emph{p} = 0.004).
-Spearman's rank correlation coefficient also confirmed that performances with louder forte (\emph{r(34)} = .43, \emph{p} = 0.010) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.013) were more likely to be judged as teaching.
 
@@
 Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r(34)} = -.75, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r(34)} = .59, \emph{p} \textless{} 0.001).
-The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; \emph{p} = 0.85, Piano to Forte; \emph{p} = 0.008).
-Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; \emph{r(34)} = -.73, \emph{p} \textless{} 0.001, Piano to Forte; \emph{r(34)} = .57, \emph{p} \textless{} 0.001).
 

### 2022-04-08 experiment-1/analysis/analysis.Rmd
adjust range for figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ## All
-```{r ioi-all, echo = FALSE}
+```{r ioi-all, echo = FALSE, fig.width = 6, fig.height = 6}
 rating <- all # rating data
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 10)) + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
 ```
@@
 ## All
-```{r kot-all, echo = FALSE}
+```{r kot-all, echo = FALSE, fig.width = 7, fig.height = 4.5}
 kot_all <- dt_kot[Subcomponent == "Legato" | Subcomponent == "Staccato" | Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile, Skill, Subcomponent)]
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-240, 130, 50)) + coord_cartesian(xlim = c(-240, 130), ylim = c(0, 100))
 ```
@@
 ## All
-```{r vel-all, echo = FALSE}
+```{r vel-all, echo = FALSE, fig.width = 7, fig.height = 4.5}
 vel_all <- dt_vel[Subcomponent == "Legato" | Subcomponent == "Staccato" | Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(MidFile, Skill, Subcomponent)]
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(45, 95, 10)) + coord_cartesian(xlim = c(45, 95), ylim = c(0, 100))
 ```
@@
 
-```{r vel-diff, include = FALSE}
+```{r vel-diff, include = FALSE, fig.width = 7, fig.height = 4.5}
 data_onset$Diff <- diff(c(0, data_onset$Velocity))
@@
 ## All
-```{r vel-diff-all, echo = FALSE}
+```{r vel-diff-all, echo = FALSE, fig.width = 7, fig.height = 4.5}
 vel_diff_all <- dt_vel_diff[Subcomponent == "FtoP" | Subcomponent == "PtoF" | Subcomponent == "LtoS" | Subcomponent == "StoL", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(MidFile, Skill, Subcomponent)]
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-35, 52, 10)) + coord_cartesian(xlim = c(-35, 52), ylim = c(0, 100))
 ```

### 2022-04-08 experiment-2/analysis/analysis.Rmd
adjust range for figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 10)) + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100))
 ```
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + 
+scale_x_continuous(breaks = seq(-260, 110, 50)) + coord_cartesian(xlim = c(-260, 110), ylim = c(0, 100))
 ```
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(50, 100, 10)) + coord_cartesian(xlim = c(50, 100), ylim = c(0, 100))
 ```

### 2022-04-08 experiment-1/analysis/analysis.R

@@ -143,7 +143,7 @@ for (number in change_2){
 }
 
 
-## ----ioi-all, echo = FALSE----------------------------------------------------
+## ----ioi-all, echo = FALSE, fig.width = 6, fig.height = 6---------------------
 rating <- all # rating data
 
 ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill)]
@@ -157,7 +157,7 @@ ioi$TeachingSD <- rating$SD_Percent
 
 ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 10)) + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
 
 
 ## ---- echo = FALSE------------------------------------------------------------
@@ -414,7 +414,7 @@ for (number in change_2){
 }
 
 
-## ----kot-all, echo = FALSE----------------------------------------------------
+## ----kot-all, echo = FALSE, fig.width = 7, fig.height = 4.5-------------------
 kot_all <- dt_kot[Subcomponent == "Legato" | Subcomponent == "Staccato" | Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile, Skill, Subcomponent)]
 
 # sorted
@@ -426,7 +426,7 @@ kot_all$TeachingSD <- rep(rating$SD_Percent, each = 2)
 
 ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
[…]

### 2022-04-08 experiment-2/analysis/analysis.R

@@ -143,7 +143,7 @@ for (number in change_2){
 }
 
 
-## ----ioi-all, echo = FALSE----------------------------------------------------
+## ----ioi-all, echo = FALSE, fig.width = 6, fig.height = 6---------------------
 rating <- all # rating data
 
 ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill)]
@@ -157,7 +157,7 @@ ioi$TeachingSD <- rating$SD_Percent
 
 ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 10)) + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100))
 
 
 ## ---- echo = FALSE------------------------------------------------------------
@@ -416,7 +416,7 @@ for (number in change_2){
 }
 
 
-## ----kot-all, echo = FALSE----------------------------------------------------
+## ----kot-all, echo = FALSE, fig.width = 7, fig.height = 4.5-------------------
 kot_all <- dt_kot[Subcomponent == "Legato" | Subcomponent == "Staccato" | Subcomponent == "Forte" | Subcomponent == "Piano", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile, Skill, Subcomponent)]
 
 # sorted
@@ -428,7 +428,8 @@ kot_all$TeachingSD <- rep(rating$SD_Percent, each = 2)
 
 ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + 
+scale_x_continuous(breaks = seq(-260, 110, 50)) + coord_cartesian(xlim = c(-260, 110), ylim = c(0, 100))
 
 
[…]

### 2022-04-08 experiment-1/analysis/analysis.Rmd
update figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2022-03-14 experiment-1/analysis/analysis.Rmd
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1)
 ```
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + theme(aspect.ratio = 1)
 ```
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100) + theme(aspect.ratio = 1)
 ```
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-250, 200, 100)) + coord_cartesian(xlim = c(-250, 200), ylim = c(0, 100)) + theme(aspect.ratio = 1)
 ```
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1)
 ```
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1)
 ```

### 2022-04-08 experiment-2/analysis/analysis.Rmd
update figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

--- 2022-03-14 experiment-2/analysis/analysis.Rmd
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1)
 ```
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + theme(aspect.ratio = 1)
 ```
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + 
+scale_x_continuous(breaks = seq(-300, 150, 100)) + coord_cartesian(xlim = c(-300, 150), ylim = c(0, 100)) + theme(aspect.ratio = 1)
 ```

### 2022-04-08 paper/manuscript.Rmd
update figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + theme_pubr(base_size = 20, base_family = "Helvetica")
-cor_ioi_1
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
 # save
-ggsave(here("paper/image", "cor_ioi_1.png"), plot = cor_ioi_1, dpi = 600, width = 7, height = 5)
+ggsave(here("paper/image", "cor_ioi_1.png"), plot = cor_ioi_1, dpi = 300, width = 6, height = 6)
 img_cor_ioi_1 <- image_read(here("paper/image", "cor_ioi_1.png"))
@@
 cor_kot_1 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
-          add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
-  theme_pubr(base_size = 20, base_family = "Helvetica")
-cor_kot_1
+          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-250, 200, 100)) + coord_cartesian(xlim = c(-250, 200), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 20, base_family = "Helvetica")
 
 # save
-ggsave(here("paper/image", "cor_kot_1.png"), plot = cor_kot_1, dpi = 600, width = 7, height = 5)
+ggsave(here("paper/image", "cor_kot_1.png"), plot = cor_kot_1, dpi = 300, width = 7, height = 5)
 img_cor_kot_1  <- image_read(here("paper/image", "cor_kot_1.png"))
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
-  theme_pubr(base_size = 20, base_family = "Helvetica")
-cor_vel_1
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 20, base_family = "Helvetica")
 
 # save
-ggsave(here("paper/image", "cor_vel_1.png"), plot = cor_vel_1, dpi = 600, width = 7, height = 5)
+ggsave(here("paper/image", "cor_vel_1.png"), plot = cor_vel_1, dpi = 300, width = 7, height = 5)
 img_cor_vel_1  <- image_read(here("paper/image", "cor_vel_1.png"))
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
-  theme_pubr(base_size = 20, base_family = "Helvetica")
-cor_vel_diff_1
+          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-35, 55, 20)) + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
 # save
-ggsave(here("paper/image", "cor_vel_diff_1.png"), plot = cor_vel_diff_1, dpi = 600, width = 7, height = 5)
+ggsave(here("paper/image", "cor_vel_diff_1.png"), plot = cor_vel_diff_1, dpi = 300, width = 7, height = 5)
 img_cor_vel_diff_1  <- image_read(here("paper/image", "cor_vel_diff_1.png"))
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
-  theme_pubr(base_size = 20, base_family = "Helvetica")
-cor_ioi_2
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
 # save
-ggsave(here("paper/image", "cor_ioi_2.png"), plot = cor_ioi_2, dpi = 600, width = 7, height = 5)
+ggsave(here("paper/image", "cor_ioi_2.png"), plot = cor_ioi_2, dpi = 300, width = 6, height = 6)
 img_cor_ioi_2 <- image_read(here("paper/image", "cor_ioi_2.png"))
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
-  theme_pubr(base_size = 20, base_family = "Helvetica")
-cor_kot_2
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-300, 150, 100)) + coord_cartesian(xlim = c(-300, 150), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
 # save
-ggsave(here("paper/image", "cor_kot_2.png"), plot = cor_kot_2, dpi = 600, width = 7, height = 5)
+ggsave(here("paper/image", "cor_kot_2.png"), plot = cor_kot_2, dpi = 300, width = 7, height = 5)
 img_cor_kot_2  <- image_read(here("paper/image", "cor_kot_2.png"))
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + xlim(50, 102) + ylim(0, 100) +
-  theme_pubr(base_size = 20, base_family = "Helvetica")
-cor_vel_2
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
 # save
-ggsave(here("paper/image", "cor_vel_2.png"), plot = cor_vel_2, dpi = 600, width = 7, height = 5)
+ggsave(here("paper/image", "cor_vel_2.png"), plot = cor_vel_2, dpi = 300, width = 7, height = 5)
 img_cor_vel_2  <- image_read(here("paper/image", "cor_vel_2.png"))
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
-  theme_pubr(base_size = 20, base_family = "Helvetica")
-cor_vel_diff_2
+          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
 # save
-ggsave(here("paper/image", "cor_vel_diff_2.png"), plot = cor_vel_diff_2, dpi = 600, width = 7, height = 5)
+ggsave(here("paper/image", "cor_vel_diff_2.png"), plot = cor_vel_diff_2, dpi = 300, width = 7, height = 5)
 img_cor_vel_diff_2  <- image_read(here("paper/image", "cor_vel_diff_2.png"))

### 2022-04-08 experiment-1/analysis/analysis.R

@@ -143,7 +143,7 @@ for (number in change_2){
 }
 
 
-## ----ioi-all, echo = FALSE, fig.width = 6, fig.height = 6---------------------
+## ----ioi-all, echo = FALSE----------------------------------------------------
 rating <- all # rating data
 
 ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill)]
@@ -157,7 +157,7 @@ ioi$TeachingSD <- rating$SD_Percent
 
 ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 10)) + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1)
 
 
 ## ---- echo = FALSE------------------------------------------------------------
@@ -226,7 +226,7 @@ ioi_tra$TeachingSD <- rating$SD_Percent
 
 ggscatter(ioi_tra, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + theme(aspect.ratio = 1)
 
 
 ## ---- echo = FALSE------------------------------------------------------------
@@ -292,7 +292,7 @@ cv$TeachingSD <- rating$SD_Percent
 
 ggscatter(cv, x = "CV", y = "Teaching", color = "Skill", add = "reg.line",
           add.params = list(fill = "lightgray"), conf.int = TRUE,
[…]

### 2022-04-08 experiment-2/analysis/analysis.R

@@ -143,7 +143,7 @@ for (number in change_2){
 }
 
 
-## ----ioi-all, echo = FALSE, fig.width = 6, fig.height = 6---------------------
+## ----ioi-all, echo = FALSE----------------------------------------------------
 rating <- all # rating data
 
 ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill)]
@@ -157,7 +157,7 @@ ioi$TeachingSD <- rating$SD_Percent
 
 ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 10)) + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100))
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1)
 
 
 ## ---- echo = FALSE------------------------------------------------------------
@@ -226,7 +226,7 @@ ioi_tra$TeachingSD <- rating$SD_Percent
 
 ggscatter(ioi_tra, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + theme(aspect.ratio = 1)
 
 
 ## ---- echo = FALSE------------------------------------------------------------
@@ -294,7 +294,7 @@ cv$TeachingSD <- rating$SD_Percent
 
 ggscatter(cv, x = "CV", y = "Teaching", color = "Skill", add = "reg.line",
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
+          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100) + theme(aspect.ratio = 1)
 
 
[…]

### 2022-04-13 paper/manuscript.Rmd
update figures for methods and for ioi
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills [e.g., @brand_2002; @saint-georges_2013].
-Also, some studies have revealed that even towards adult learners, people modulated their speech and action in the similar way as they did for infants [@mcellin_2017; @uther_2007].
+Further studies have revealed that even towards adult learners, people modulated their speech and action in a similar way as they did for infants [@mcellin_2017; @uther_2007].
 Moreover, @mcellin_2018 demonstrated that people could identify informative intentions such as acting with others or teaching by relying on specific kinematics cues (e.g., velocity profiles of movements).
@@
 
-Tominaga, Knoblich & Sebanz (*submitted*) extended this line of research to expertise transmission where skills to be acquired are complex such as artistic expression.
-Based on the assumption that expert pianists are skilled at controlling their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
-The results demonstrated that expert pianists could successfully modulate their performance by playing slower or exaggerating relevant aspects of the performance (e.g., producing shorter staccato or making a larger contrast between forte and piano) to teach musical expressive techniques.
-Therefore, it seems that even in the domain of expertise, experts exhibit general pedagogical behaviours to communicate with their potential learners.
+Tominaga, Knoblich & Sebanz (*submitted*) extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression.
+We investigated whether and how expert pianists are able to communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
+The results demonstrated that expert pianists systematically modulated their performance by playing slower or by exaggerating relevant aspects of the performance (e.g., producing shorter staccato or producing a larger contrast between forte and piano) when intending to teach the musical expressive techniques.
+Therefore, it seems that even in the domain of expertise, experts exhibit pedagogical behaviours to highlight crucial performance aspects for potential learners.
 
-Here we investigated whether the modulations that expert pianists made when they intended to teach were also perceived by listeners as conveying pedagogical intentions.
-We assumed that listeners would be able to infer intentions only by listening to recordings because some research revealed that musical emotion is often communicated by sound alone and that listeners seem to be able to infer performers' intended emotions only by listening to recorded performances [e.g., @akkermans_2019; @gabrielsson_1996].
+Here we investigated whether the modulations that expert pianists make when they intended to teach are also perceived by listeners as conveying teaching intentions.
+We started from the assumption that listeners would be able to infer intentions from listening to recordings because previous research revealed that sound alone is sufficient to communicate different aspects of a musical performance.
+For instance, listeners are well able to infer performers' intended emotions when listening to recorded performances [e.g., @akkermans_2019; @gabrielsson_1996].
+
 In the present study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
@@
 Furthermore, recordings were quantified with regard to tempo, articulation and dynamic.
-We performed correlation and multiple regression analysis to examine relationships between performance features of the recordings and how likely people think the recordings were produced for teaching purposes.
-Various piano recordings were collected from our previous experiments (Tominaga et al., *submitted*).
-The recordings were performed by various pianists multiple times, therefore the recordings contained many variations in terms of timing, articulation and dynamics.
+Using correlations and multiple regression analysis, we examined which modulations of performance were used to infer teaching intentions.
 
-If performers' intentions are successfully communicated with learners, musicians would be able to distinguish teaching recordings from performing recordings.
-Moreover, pedagogical behavioural features in our previous experiments such as slower demonstration and exaggerated performance should be identified and used to infer teaching intentions.
-We examined which features of piano performance were correlated with participants judgments as teaching.
-We conducted Experiment 1 with a simple musical scale and Experiment 2 with a more naturalistic piece of music to replicate the findings from Experiment 1.
+If performers' intentions are understood by learners with basic musical skills, listeners should be able to distinguish teaching recordings from performing recordings.
+Moreover, the same modulations of pedagogical performance parameters observed in our previous experiments such as slower demonstration and exaggerated performance, should be used to infer teaching intentions by the earners.
+In Experiment 1 learners listened to performances with that followed simple musical scales.
+In Experiment 2 learners listen to performances of a more naturalistic piece of music in aan attempt to replicate the findings from Experiment 1.
 
@@
 ## Procedure
-Upon arrival, participants read information sheet about the experiment and gave informed consent prior to participation.
+Upon arrival, participants read the information sheet about the experiment and gave informed consent prior to participation.
 In the experiment, all instructions were displayed on a computer screen in front of the participants and an experimenter also explained the procedure.
@@
 While listening to each recording, sheet music, which corresponded to the recording, was shown on the screen in front of the participants (*Figure \ref{fig:procedure1}*).
+Participants were allowed to listen to each recording only once.
 
@@
 
-### Correlation and multiple regression
-Stimuli were quantified with regard to tempo (interonset intervals; IOIs), articulation (key-overlap time; KOT), dynamics (key velocity; KV) and dynamics contrast (key velocity difference; KV-Diff) only for 16th notes.
+### Correlations and multiple regression
+Stimuli were quantified regarding tempo (interonset intervals; IOIs), articulation (key-overlap time; KOT), dynamics (key velocity; KV) and dynamics contrast (key velocity difference; KV-Diff) only for 16th notes.
 Interonset intervals are time intervals between onsets of adjacent notes.
@@
 
-First, in order to investigate relationships between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as teaching (i.e., what percentage of participants responded as "yes"), we performed correlation analysis.
-Second, we run multiple regression and entered all four performance features to examine which predictor significantly contributed to participants' judgments as teaching.
+To investigate relationships between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as teaching (i.e., what percentage of participants responded as "yes"), we first performed separate correlation analyses for each performance feature.
+Second, we run multiple regression that included all four performance features to examine which predictor significantly contributed to participants' judgments as teaching.
 Since articulation and dynamics were comprised of two opposite directional values (i.e., legato vs.
 staccato, forte vs.
-piano), we created four separate models, which considered only one subcomponent of either legato, staccato, forte or piano.
-
+piano), we created four separate models that included different parts of the piece (see ).
+Each model considered only parts of the piece that comprised either legato, staccato, forte or piano.
 For articulation recordings, there were two models.
-The Legato model considered only legato parts of the stimuli.
+The Legato model considered only legato parts of the performances.
 We entered the legato parts of KOT and KV and KV-Diff or transition points from legato to staccato.
-The Staccato model considered only staccato parts of the stimuli.
+The Staccato model considered only staccato parts of the performances.
 We entered the staccato parts of KOT and KV and KV-Diff of transition points from staccato to legato.
@@
 The symbol `f' denotes forte and the symbol `p' denotes piano.
-Only the 16th notes were used for data analysis.", echo = FALSE}
-stim_a <- image_border(image_read(here("paper/image", "stim_a.png")), "#FFFFFF", "120x120")
-stim_d <- image_border(image_read(here("paper/image", "stim_d.png")), "#FFFFFF", "120x120")
+Only the parts composed of 16th notes were used for data analysis.", echo = FALSE}
+stim_a <- image_border(image_read(here("paper/image", "stim_a.jpg")), "#FFFFFF", "120x120")
+stim_d <- image_border(image_read(here("paper/image", "stim_d.jpg")), "#FFFFFF", "120x120")
 
@@
 img_stimuli_1 <- image_append(c(stim_a, stim_d), stack = TRUE)
-img_stimuli_1 <- image_annotate(img_stimuli_1, "(A)", size = 80, location = "+100+0", color = "black", font = "helvetica")
-img_stimuli_1 <- image_annotate(img_stimuli_1, "(B)", size = 80, location = "+100+650", color = "black", font = "helvetica")
 img_stimuli_1
@@
 
-```{r procedure-1, out.width = "100%", fig.cap = "\\label{fig:procedure1}Procedure.
+```{r procedure-1, fig.align="center", out.width = "50%", fig.cap = "\\label{fig:procedure1}Procedure.
 Participants listened to a recording via headphones while corresponding sheet music was displayed on a monitor.
-They were required to respond by pressing a left-arrow (yes) or right-arrow (no) key for each judgment.", echo = FALSE}
-knitr::include_graphics(here("paper/image", "procedure.png"))
+They were required to respond by pressing a left-arrow (yes) or right-arrow (no) key for each judgment.
+Headphone image from Flaticon.com", echo = FALSE}
+knitr::include_graphics("image/procedure.jpg")
 ```
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + labs(color = "Technique") + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-250, 200, 100)) + coord_cartesian(xlim = c(-250, 200), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 20, base_family = "Helvetica")
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-250, 200, 100)) + coord_cartesian(xlim = c(-250, 200), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 20, base_family = "Helvetica")
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
@@
 Only the 8th notes with expressive notations were used for data analysis.", echo = FALSE}
-stim_a_2 <- image_border(image_read(here("paper/image", "stim_a_2.png")), "#FFFFFF", "120x120")
-stim_d_2 <- image_border(image_read(here("paper/image", "stim_d_2.png")), "#FFFFFF", "120x120")
+stim_a_2 <- image_border(image_read(here("paper/image", "stim_a_2.jpg")), "#FFFFFF", "120x120")
+stim_d_2 <- image_border(image_read(here("paper/image", "stim_d_2.jpg")), "#FFFFFF", "120x120")
 
@@
 img_stimuli_2 <- image_append(c(stim_a_2, stim_d_2), stack = TRUE)
-img_stimuli_2 <- image_annotate(img_stimuli_2, "(A)", size = 80, location = "+100+70", color = "black", font = "helvetica")
-img_stimuli_2 <- image_annotate(img_stimuli_2, "(B)", size = 80, location = "+100+1125", color = "black", font = "helvetica")
 img_stimuli_2
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + labs(color = "Technique") + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 

### 2022-04-13 paper/manuscript.tex
update figures for methods and for ioi
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={What makes musicians infer teaching intentions?},
-  pdfauthor={Atsuko Tominaga1,*, Günther Knoblich1, \& Natalie Sebanz1},
-  pdflang={en-EN},
-  pdfkeywords={teaching, intention, skill transmission, musical expression},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={What makes musicians infer teaching intentions?},
+  pdfauthor={Atsuko Tominaga1,*, Günther Knoblich1, \& Natalie Sebanz1},
+  pdflang={en-EN},
+  pdfkeywords={teaching, intention, skill transmission, musical expression},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills (e.g., Brand, Baldwin, \& Ashburn, 2002; Saint-Georges et al., 2013).
-Also, some studies have revealed that even towards adult learners, people modulated their speech and action in the similar way as they did for infants (McEllin, Knoblich, \& Sebanz, 2017; Uther, Knoll, \& Burnham, 2007).
+Further studies have revealed that even towards adult learners, people modulated their speech and action in a similar way as they did for infants (McEllin, Knoblich, \& Sebanz, 2017; Uther, Knoll, \& Burnham, 2007).
 Moreover, McEllin, Sebanz, and Knoblich (2018) demonstrated that people could identify informative intentions such as acting with others or teaching by relying on specific kinematics cues (e.g., velocity profiles of movements).
@@
 
-Tominaga, Knoblich \& Sebanz (\emph{submitted}) extended this line of research to expertise transmission where skills to be acquired are complex such as artistic expression.
-Based on the assumption that expert pianists are skilled at controlling their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
-The results demonstrated that expert pianists could successfully modulate their performance by playing slower or exaggerating relevant aspects of the performance (e.g., producing shorter staccato or making a larger contrast between forte and piano) to teach musical expressive techniques.
-Therefore, it seems that even in the domain of expertise, experts exhibit general pedagogical behaviours to communicate with their potential learners.
+Tominaga, Knoblich \& Sebanz (\emph{submitted}) extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression.
+We investigated whether and how expert pianists are able to communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
+The results demonstrated that expert pianists systematically modulated their performance by playing slower or by exaggerating relevant aspects of the performance (e.g., producing shorter staccato or producing a larger contrast between forte and piano) when intending to teach the musical expressive techniques.
+Therefore, it seems that even in the domain of expertise, experts exhibit pedagogical behaviours to highlight crucial performance aspects for potential learners.
 
-Here we investigated whether the modulations that expert pianists made when they intended to teach were also perceived by listeners as conveying pedagogical intentions.
-We assumed that listeners would be able to infer intentions only by listening to recordings because some research revealed that musical emotion is often communicated by sound alone and that listeners seem to be able to infer performers' intended emotions only by listening to recorded performances (e.g., Akkermans et al., 2019; Gabrielsson \& Juslin, 1996).
+Here we investigated whether the modulations that expert pianists make when they intended to teach are also perceived by listeners as conveying teaching intentions.
+We started from the assumption that listeners would be able to infer intentions from listening to recordings because previous research revealed that sound alone is sufficient to communicate different aspects of a musical performance.
+For instance, listeners are well able to infer performers' intended emotions when listening to recorded performances (e.g., Akkermans et al., 2019; Gabrielsson \& Juslin, 1996).
+
 In the present study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
@@
 Furthermore, recordings were quantified with regard to tempo, articulation and dynamic.
-We performed correlation and multiple regression analysis to examine relationships between performance features of the recordings and how likely people think the recordings were produced for teaching purposes.
-Various piano recordings were collected from our previous experiments (Tominaga et al., \emph{submitted}).
-The recordings were performed by various pianists multiple times, therefore the recordings contained many variations in terms of timing, articulation and dynamics.
+Using correlations and multiple regression analysis, we examined which modulations of performance were used to infer teaching intentions.
 
-If performers' intentions are successfully communicated with learners, musicians would be able to distinguish teaching recordings from performing recordings.
-Moreover, pedagogical behavioural features in our previous experiments such as slower demonstration and exaggerated performance should be identified and used to infer teaching intentions.
-We examined which features of piano performance were correlated with participants judgments as teaching.
-We conducted Experiment 1 with a simple musical scale and Experiment 2 with a more naturalistic piece of music to replicate the findings from Experiment 1.
+If performers' intentions are understood by learners with basic musical skills, listeners should be able to distinguish teaching recordings from performing recordings.
+Moreover, the same modulations of pedagogical performance parameters observed in our previous experiments such as slower demonstration and exaggerated performance, should be used to infer teaching intentions by the earners.
+In Experiment 1 learners listened to performances with that followed simple musical scales.
+In Experiment 2 learners listen to performances of a more naturalistic piece of music in aan attempt to replicate the findings from Experiment 1.
 
@@
 
-Upon arrival, participants read information sheet about the experiment and gave informed consent prior to participation.
+Upon arrival, participants read the information sheet about the experiment and gave informed consent prior to participation.
 In the experiment, all instructions were displayed on a computer screen in front of the participants and an experimenter also explained the procedure.
@@
 While listening to each recording, sheet music, which corresponded to the recording, was shown on the screen in front of the participants (\emph{Figure \ref{fig:procedure1}}).
+Participants were allowed to listen to each recording only once.
 
@@
 
-\hypertarget{correlation-and-multiple-regression}{%
-\subsubsection{Correlation and multiple regression}\label{correlation-and-multiple-regression}}
+\hypertarget{correlations-and-multiple-regression}{%
+\subsubsection{Correlations and multiple regression}\label{correlations-and-multiple-regression}}
 
-Stimuli were quantified with regard to tempo (interonset intervals; IOIs), articulation (key-overlap time; KOT), dynamics (key velocity; KV) and dynamics contrast (key velocity difference; KV-Diff) only for 16th notes.
+Stimuli were quantified regarding tempo (interonset intervals; IOIs), articulation (key-overlap time; KOT), dynamics (key velocity; KV) and dynamics contrast (key velocity difference; KV-Diff) only for 16th notes.
 Interonset intervals are time intervals between onsets of adjacent notes.
@@
 
-First, in order to investigate relationships between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as teaching (i.e., what percentage of participants responded as ``yes''), we performed correlation analysis.
-Second, we run multiple regression and entered all four performance features to examine which predictor significantly contributed to participants' judgments as teaching.
-Since articulation and dynamics were comprised of two opposite directional values (i.e., legato vs.~staccato, forte vs.~piano), we created four separate models, which considered only one subcomponent of either legato, staccato, forte or piano.
-
+To investigate relationships between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as teaching (i.e., what percentage of participants responded as ``yes''), we first performed separate correlation analyses for each performance feature.
+Second, we run multiple regression that included all four performance features to examine which predictor significantly contributed to participants' judgments as teaching.
+Since articulation and dynamics were comprised of two opposite directional values (i.e., legato vs.~staccato, forte vs.~piano), we created four separate models that included different parts of the piece (see ).
+Each model considered only parts of the piece that comprised either legato, staccato, forte or piano.
 For articulation recordings, there were two models.
-The Legato model considered only legato parts of the stimuli.
+The Legato model considered only legato parts of the performances.
 We entered the legato parts of KOT and KV and KV-Diff or transition points from legato to staccato.
-The Staccato model considered only staccato parts of the stimuli.
+The Staccato model considered only staccato parts of the performances.
 We entered the staccato parts of KOT and KV and KV-Diff of transition points from staccato to legato.
@@
 The symbol `f' denotes forte and the symbol `p' denotes piano.
-Only the 16th notes were used for data analysis.}\label{fig:stim-1}
+Only the parts composed of 16th notes were used for data analysis.}\label{fig:stim-1}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/atsukotominaga/Google Drive/Project/music-perception/paper/image/procedure} \caption{\label{fig:procedure1}Procedure.
+
+{\centering \includegraphics[width=0.5\linewidth]{image/procedure}
+
+}
+
+\caption{\label{fig:procedure1}Procedure.
 Participants listened to a recording via headphones while corresponding sheet music was displayed on a monitor.
-They were required to respond by pressing a left-arrow (yes) or right-arrow (no) key for each judgment.}\label{fig:procedure-1}
+They were required to respond by pressing a left-arrow (yes) or right-arrow (no) key for each judgment.
+Headphone image from Flaticon.com}\label{fig:procedure-1}
 \end{figure}

### 2022-04-13 paper/manuscript.Rmd
update figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + labs(color = "Technique") + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + labs(color = "Technique") + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
 
@@
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + labs(color = "Technique") + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + labs(color = "Technique") + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
 
@@
 
-```{r results-prereg, cache = FALSE}
-source(here("experiment-1/analysis/prereg_analysis", "prereg_analysis.R"), chdir = TRUE)
-```
+# Supplementary Materials
+All data is available at .
 
-<!-- # Supplementary Materials{#supplementary} -->
+# Acknowledgement
 
-<!-- ## Accuracy for Experiment 1 -->
-<!-- We examined whether participants could accurately judge the stimuli chosen from the teaching condition in the previous experiments as teaching (yes response in the current experiment) and the stimuli chosen from the performing condition in the previous experiments as performing (no response in the current experiment).
-We compared how accurate participants were against the chance level (50%).
-The results revealed that the accuracy of participants' judgments was above the chance level (*M* = `r round(mean(ind_data_ad[Skill == "articulation"]$Percent), 1)`, *SD* = `r round(sd(ind_data_ad[Skill == "articulation"]$Percent), 2)`; *t*(`r t.test(ind_data$Percent, mu = 50, alternative = "two.sided")$parameter`) = `r t.test(ind_data$Percent, mu = 50, alternative = "two.sided")$statistic`, *p* `r if(t.test(ind_data$Percent, mu = 50, alternative = "two.sided")$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).
-However, the 95 confidence intervals for the sample mean contained the sample -->
+This research was supported by the European Research Council under the European Union’s Seventh Framework Program (FP7/2007–2013)/ERC Grant agreement no.
+609819, SOMICS, and by ERC Grant agreement no.
+616072, JAXPERTISE.
+We thank Fanni Takátsy for her help with data collection.

### 2022-04-14 paper/manuscript.Rmd
update figures (grey scale)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills [e.g., @brand_2002; @saint-georges_2013].
-Further studies have revealed that even towards adult learners, people modulated their speech and action in a similar way as they did for infants [@mcellin_2017; @uther_2007].
+Further studies have revealed that even towards adult learners, people modulate their speech and action in a similar way as they did for infants [@mcellin_2017; @uther_2007].
 Moreover, @mcellin_2018 demonstrated that people could identify informative intentions such as acting with others or teaching by relying on specific kinematics cues (e.g., velocity profiles of movements).
@@
 ```{r ioi-1, include = FALSE}
-cor_ioi_1 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line", palette = "d3",
-          add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + labs(color = "Technique") + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
+cor_ioi_1 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", shape = "Skill", add = "reg.line", palette = "d3", add.params = list(fill = "lightgray"), conf.int = TRUE, xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + labs(color = "Technique", shape = "Technique") + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
 
@@
 kot_all$Subcomponent <- factor(kot_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
-cor_kot_1 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
+cor_kot_1 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-250, 200, 100)) + coord_cartesian(xlim = c(-250, 200), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-250, 200, 100)) + coord_cartesian(xlim = c(-250, 200), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
 
@@
 vel_all$Subcomponent <- factor(vel_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
-cor_vel_1 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
+cor_vel_1 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
 
@@
 vel_diff_all$Subcomponent <- factor(vel_diff_all$Subcomponent, levels = c("LtoS", "StoL", "FtoP", "PtoF"))
-cor_vel_diff_1 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
+cor_vel_diff_1 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-35, 55, 20)) + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
+          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-35, 55, 20)) + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
 
@@
 ```{r ioi-2, include = FALSE}
-cor_ioi_2 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line", palette = "d3",
+cor_ioi_2 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", shape = "Skill", add = "reg.line", palette = "d3",
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + labs(color = "Technique") + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + labs(color = "Technique", shape = "Technique") + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
 
@@
 kot_all$Subcomponent <- factor(kot_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
-cor_kot_2 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
+cor_kot_2 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-300, 150, 100)) + coord_cartesian(xlim = c(-300, 150), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-300, 150, 100)) + coord_cartesian(xlim = c(-300, 150), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
 
@@
 vel_all$Subcomponent <- factor(vel_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
-cor_vel_2 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
+cor_vel_2 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
 
@@
 vel_diff_all$Subcomponent <- factor(vel_diff_all$Subcomponent, levels = c("LtoS", "StoL", "FtoP", "PtoF"))
-cor_vel_diff_2 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
+cor_vel_diff_2 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
+          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
 
@@
 # Supplementary Materials
-All data is available at .
+All data is available at https://osf.io/f6nr2/.
 
@@
 This research was supported by the European Research Council under the European Union’s Seventh Framework Program (FP7/2007–2013)/ERC Grant agreement no.
-609819, SOMICS, and by ERC Grant agreement no.
-616072, JAXPERTISE.
+609819, SOMICS.
 We thank Fanni Takátsy for her help with data collection.

### 2022-04-15 paper/manuscript.Rmd
second draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
   Perceiving pedagogical intentions is vital when learning skills from others.
-Our previous research demonstrated that expert pianists systematically modulated their sound so as to teach musical expressive techniques such as articulation and dynamics.
-For example, pianists played slower and exaggerated each technique when they had an intention to teach.
 Here we investigated whether the modulations that expert pianists produce when they intend to teach are also perceived by listeners as conveying pedagogical intentions.
-In the current study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
-Half of the recordings was produced when pianists were instructed to play as if they were teaching the designated musical technique in a lesson (i.e., teaching recordings) whereas the other half was produced when pianists were instructed to play as if they were performing it in a concert (i.e., performing recordings).
-Participants were asked to judge whether each recording was produced for teaching purposes or not.
-We calculated the accuracy of participants' judgments to investigate whether they could distinguish teaching recordings from performing recordings.
-Also, recordings were quantified with regard to tempo, articulation and dynamic so that we could perform correlation and multiple regression analysis to investigate which features of piano performance made musicians infer teaching intentions.
+Musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
+They were asked to judge whether each recording was produced for teaching purposes or not.
 The findings in Experiment 1 with a simple musical scale demonstrated that the accuracy of musicians' judgments was significantly above chance.
-Also, it was found that slower tempo contributed to musicians’ judgments as teaching regardless of the techniques.
-Moreover, performances with exaggeration for each technique (e.g., longer legato, shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching.
+Also, slower tempo contributed to musicians’ judgments as teaching regardless of the techniques.
+Moreover, performances with exaggeration for each technique were more likely to be judged as teaching.
 Experiment 2 aimed to replicate the findings of Experiment 1 with a more naturalistic piece.
-As Experiment 1, the accuracy of musicians' judgments was significantly above chance.
-However, we only replicated that performances with exaggerated dynamics (in particular, larger contrast between forte and piano) were more likely to be judged as teaching.
-Taken together, loudness (dynamics) seems to be reliably used to infer teaching intentions regardless of the complexity of a musical piece.
+The accuracy of musicians' judgments was significantly above chance.
+However, we only replicated that performances with exaggerated dynamics were more likely to be judged as teaching.
+Taken together, loudness seems to be reliably used to infer teaching intentions regardless of the complexity of a musical piece.
 Also, typical pedagogical behaviour such as slowing down may not be necessarily perceived as teaching performance when learning complex skills such as artistic expression.
 
-keywords          : "teaching, intention, skill transmission, musical expression"
+keywords          : "perception, expression, learning, expertise, music education"
 
@@
 
-floatsintext      : yes
-figurelist        : no
+floatsintext      : no
+figurelist        : yes
 tablelist         : no
@@
 
-Here we investigated whether the modulations that expert pianists make when they intended to teach are also perceived by listeners as conveying teaching intentions.
+Here we investigated whether the modulations that expert pianists make when they intend to teach are perceived by listeners as conveying teaching intentions.
 We started from the assumption that listeners would be able to infer intentions from listening to recordings because previous research revealed that sound alone is sufficient to communicate different aspects of a musical performance.
-For instance, listeners are well able to infer performers' intended emotions when listening to recorded performances [e.g., @akkermans_2019; @gabrielsson_1996].
+For instance, listeners are generally able to infer performers' intended emotions when listening to recorded performances and musically skilled listeners are even better at decoding emotions from performances [e.g., @akkermans_2019; @gabrielsson_1996].
 
@@
 First, we calculated the accuracy of participants’ judgments to examine whether they could distinguish teaching recordings from performing recordings.
-Furthermore, recordings were quantified with regard to tempo, articulation and dynamic.
+Furthermore, recordings were quantified with regard to tempo, articulation and dynamics.
 Using correlations and multiple regression analysis, we examined which modulations of performance were used to infer teaching intentions.
 
-If performers' intentions are understood by learners with basic musical skills, listeners should be able to distinguish teaching recordings from performing recordings.
-Moreover, the same modulations of pedagogical performance parameters observed in our previous experiments such as slower demonstration and exaggerated performance, should be used to infer teaching intentions by the earners.
-In Experiment 1 learners listened to performances with that followed simple musical scales.
-In Experiment 2 learners listen to performances of a more naturalistic piece of music in aan attempt to replicate the findings from Experiment 1.
+If performers' intentions are understood by learners with basic musical skills, they should be able to distinguish teaching recordings from performing recordings.
+Moreover, the same modulations of pedagogical performance parameters observed in our previous experiments such as slower demonstration and exaggerated performance, should be used to infer teaching intentions by the learners.
+In Experiment 1 learners listened to performances that followed simple musical scales.
+In Experiment 2 learners listened to performances of a more naturalistic piece of music in an attempt to replicate the findings from Experiment 1.
 
@@
 ## Stimuli
-We selected stimuli from our previous experiments (Tominaga et al., *submitted*).
+We selected stimuli from the performances obtained in our previous experiments (Tominaga et al., *submitted*).
 Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files.
@@
 staccato, forte vs.
-piano), we created four separate models that included different parts of the piece (see ).
+piano), we created four separate models that included different parts of the piece.
 Each model considered only parts of the piece that comprised either legato, staccato, forte or piano.
 For articulation recordings, there were two models.
-The Legato model considered only legato parts of the performances.
+The Legato model (*Figure \ref{fig:stim1}*, 1) considered only legato parts of the performances.
 We entered the legato parts of KOT and KV and KV-Diff or transition points from legato to staccato.
-The Staccato model considered only staccato parts of the performances.
+The Staccato model (*Figure \ref{fig:stim1}*, 2) considered only staccato parts of the performances.
 We entered the staccato parts of KOT and KV and KV-Diff of transition points from staccato to legato.
 Similarly, there were two models for dynamics recordings.
-The Forte model considered only forte parts of the stimuli for KV and KOT, and transition points from forte to piano for KV-Diff.
-The Piano model considered only piano parts of the stimuli for KV and KOT, and transition points from piano to forte for KV-Diff.
+The Forte model (*Figure \ref{fig:stim1}*, 3) considered only forte parts of the performances for KV and KOT, and transition points from forte to piano for KV-Diff.
+The Piano model (*Figure \ref{fig:stim1}*, 4) considered only piano parts of the performances for KV and KOT, and transition points from piano to forte for KV-Diff.
 With regard to tempo (IOIs), there was only one value for each recording regardless of the subcomponents because tempo was consistent across the performance.
@@
 The curved line (slur) indicates legato and the dots indicate staccato.
+In multiple regression analysis, (1) corresponds to Legato model and (2) corresponds to Staccato model.
 (B)Dynamics.
 The symbol `f' denotes forte and the symbol `p' denotes piano.
-Only the parts composed of 16th notes were used for data analysis.", echo = FALSE}
+In multiple regression analysis, (3) corresponds to Forte model and (2) corresponds to Piano model.
+Only the parts composed of 16th notes (i.e., (1), (2), (3), (4)) were used for data analysis.", echo = FALSE}
 stim_a <- image_border(image_read(here("paper/image", "stim_a.jpg")), "#FFFFFF", "120x120")
@@
 They were required to respond by pressing a left-arrow (yes) or right-arrow (no) key for each judgment.
-Headphone image from Flaticon.com", echo = FALSE}
+Headphone image from Flaticon.com.", echo = FALSE}
 knitr::include_graphics("image/procedure.jpg")
@@
 A one sample *t*-test was performed to compare the accuracy of participants' judgments against the chance level (50%).
-The mean percentage of correct answers [*M* = `r sprintf('%.1f', subset$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset$SD_Percent)`] was significantly higher than chance (*t*(`r ttest_all$parameter`) = `r sprintf('%.2f', ttest_all$statistic)`, *p* `r if(ttest_all$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_all$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_all$effsize)`).
+The mean percentage of correct answers [*M* = `r sprintf('%.1f', subset$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset$SD_Percent)`] was significantly higher than chance (*t*(`r ttest_all$parameter`) = `r sprintf('%.2f', ttest_all$statistic)`, *p* `r if(ttest_all$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', ttest_all$p.value)))}`, cohen's *d* = `r sprintf('%.2f', coheneff_all$effsize)`).
 
 We also performed a one sample *t*-test for each technique separately.
-For articulation, the mean percentage of correct answers [*M* = `r sprintf('%.1f', subset_ad[Skill == "articulation"]$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset_ad[Skill == "articulation"]$SD_Percent)`] was not significantly different from chance (*t*(`r ttest_art$parameter`) = `r sprintf('%.2f', ttest_art$statistic)`, *p* `r if(ttest_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_art$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_art$effsize)`).
-For dynamics, the mean percentage of correct answers [*M* = `r sprintf('%.1f', subset_ad[Skill == "dynamics"]$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset_ad[Skill == "dynamics"]$SD_Percent)`] was significantly higher than chance (*t*(`r ttest_dyn$parameter`) = `r sprintf('%.2f', ttest_dyn$statistic)`, *p* `r if(ttest_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_dyn$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_dyn$effsize)`).
-A paired *t*-test revealed that there was a significant difference between the two techniques in terms of the accuracy (*t*(`r ttest_paired$parameter`) = `r sprintf('%.2f', ttest_paired$statistic)`, *p* `r if(ttest_paired$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_paired$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_paired$effsize)`), suggesting participants chose correct answers more for dynamics recordings than articulation recordings.
+For articulation, the mean percentage of correct answers [*M* = `r sprintf('%.1f', subset_ad[Skill == "articulation"]$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset_ad[Skill == "articulation"]$SD_Percent)`] was not significantly different from chance (*t*(`r ttest_art$parameter`) = `r sprintf('%.2f', ttest_art$statistic)`, *p* `r if(ttest_art$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', ttest_art$p.value)))}`, cohen's *d* = `r sprintf('%.2f', coheneff_art$effsize)`).
+For dynamics, the mean percentage of correct answers [*M* = `r sprintf('%.1f', subset_ad[Skill == "dynamics"]$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset_ad[Skill == "dynamics"]$SD_Percent)`] was significantly higher than chance (*t*(`r ttest_dyn$parameter`) = `r sprintf('%.2f', ttest_dyn$statistic)`, *p* `r if(ttest_dyn$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', ttest_dyn$p.value)))}`, cohen's *d* = `r sprintf('%.2f', coheneff_dyn$effsize)`).
+A paired *t*-test revealed that there was a significant difference between the two techniques in terms of the accuracy (*t*(`r ttest_paired$parameter`) = `r sprintf('%.2f', ttest_paired$statistic)`, *p* `r if(ttest_paired$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', ttest_paired$p.value)))}`, cohen's *d* = `r sprintf('%.2f', coheneff_paired$effsize)`), suggesting participants chose correct answers more for dynamics recordings than articulation recordings.
 
-## Correlation
+## Correlations
 ### Tempo (IOIs)
-Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_art$p.value))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-1}*).
+Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_ioi_art$p.value)))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_ioi_dyn$p.value)))}`, *Figure \ref{fig:ioi-1}*).
 Participants tended to identify slower performances as teaching.
@@
 For articulation recordings, there was a significant relationship between KOT values and participants' judgments as teaching (*Figure \ref{fig:kot-1}*, left).
-Specifically, performances with shorter staccato (*r(`r cor_kot_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`) and longer legato (*r(`r cor_kot_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_leg$p.value))}`) were more likely to be judged as teaching.
+Specifically, performances with shorter staccato (*r(`r cor_kot_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< .001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`) and longer legato (*r(`r cor_kot_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_kot_leg$p.value)))}`) were more likely to be judged as teaching.
 
-For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`, Piano; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`, *Figure \ref{fig:kot-1}*, right).
+For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$p.value)))}`, Piano; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$p.value)))}`, *Figure \ref{fig:kot-1}*, right).
 
@@
 For dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-1}*, right).
-Specifically, performances with louder forte were more likely to be judged as teaching (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`).
-However, there was no significant relationship between KV values for piano and participants' judgments as teaching (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia$p.value))}`).
+Specifically, performances with louder forte were more likely to be judged as teaching (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_for$p.value)))}`).
+However, there was no significant relationship between KV values for piano and participants' judgments as teaching (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$p.value)))}`).
 
-For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r(`r cor_vel_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-1}*, left).
+For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$p.value)))}`, Staccato; *r(`r cor_vel_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$p.value)))}`, *Figure \ref{fig:vel-1}*, left).
 
@@
 For dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (*Figure \ref{fig:vel-diff-1}*, right).
-Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).
+Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_diff_ftop$p.value)))}`, From Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_diff_ptof$p.value)))}`).
 
-For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ltos$p.value))}`, From Staccato to Legato; *r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_stol$p.value))}`, *Figure \ref{fig:vel-diff-1}*, left).
+For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_diff_ltos$p.value)))}`, From Staccato to Legato; *r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$p.value)))}`, *Figure \ref{fig:vel-diff-1}*, left).
 
@@
 In order to further explore which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted.
-Statistical model assumptions were tested using the *performance* R package [@ludecke_2021] and most of the assumptions (see *Supplementary Material* for details) were met.
+Statistical model assumptions were tested using the *performance* R package [@ludecke_2021].
 Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.
 staccato, forte vs.
-piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in *Data analysis*).
+piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in *Data analysis* and *Figure \ref{fig:stim1}*).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
-The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m1)$adj.r.squared*100)` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r sprintf('%.1f', summary(m1)$fstatistic[1])`, *p* `r if(lmp(m1) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m1)))}`).
-It was found that tempo (IOIs; *$\beta$* = `r summary(m1)$coefficients[2]`, *p* `r if(summary(m1)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[2, 4]))}`) and articulation for the legato parts (KOT; *$\beta$* = `r summary(m1)$coefficients[3]`, *p* `r if(summary(m1)$coefficients[3, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[3, 4]))}`) were significant predictors of participants' judgments as teaching.
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m1)$adj.r.squared*100)` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r sprintf('%.1f', summary(m1)$fstatistic[1])`, *p* `r if(lmp(m1) < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', lmp(m1))))}`).
+It was found that tempo (IOIs; *$\beta$* = `r summary(m1)$coefficients[2]`, *p* `r if(summary(m1)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[2, 4]))}`) and articulation for the legato parts (KOT; *$\beta$* = `r summary(m1)$coefficients[3]`, *p* `r if(summary(m1)$coefficients[3, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m1)$coefficients[3, 4])))}`) were significant predictors of participants' judgments as teaching.
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato).
-The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m2)$adj.r.squared*100)` % of the variance (*F*(`r summary(m2)$fstatistic[2]`, `r summary(m2)$fstatistic[3]`) = `r sprintf('%.1f', summary(m2)$fstatistic[1])`, *p* `r if(lmp(m2) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m2)))}`).
-It was found that tempo (IOIs; *$\beta$* = `r summary(m2)$coefficients[2]`, *p* `r if(summary(m2)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m2)$coefficients[2, 4]))}`) and articulation for the staccato parts (KOT; *$\beta$* = `r summary(m2)$coefficients[3]`, *p* `r if(summary(m2)$coefficients[3, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m2)$coefficients[3, 4]))}`) were significant predictors of participants' judgments as teaching.
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m2)$adj.r.squared*100)` % of the variance (*F*(`r summary(m2)$fstatistic[2]`, `r summary(m2)$fstatistic[3]`) = `r sprintf('%.1f', summary(m2)$fstatistic[1])`, *p* `r if(lmp(m2) < 0.001){"< .001"} else {paste("= ", sprintf('%.2f', lmp(m2)))}`).
+It was found that tempo (IOIs; *$\beta$* = `r summary(m2)$coefficients[2]`, *p* `r if(summary(m2)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m2)$coefficients[2, 4])))}`) and articulation for the staccato parts (KOT; *$\beta$* = `r summary(m2)$coefficients[3]`, *p* `r if(summary(m2)$coefficients[3, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m2)$coefficients[3, 4])))}`) were significant predictors of participants' judgments as teaching.
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano).
-The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m3)$adj.r.squared*100)` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r sprintf('%.2f', summary(m3)$fstatistic[1])`, *p* `r if(lmp(m3) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m3)))}`).
-It was found that tempo (IOIs; *$\beta$* = `r summary(m3)$coefficients[2]`, *p* `r if(summary(m3)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m3)$coefficients[2, 4]))}`) and dynamics for the forte parts (KV; *$\beta$* = `r summary(m3)$coefficients[4]`, *p* `r if(summary(m3)$coefficients[4, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m3)$coefficients[4, 4]))}`) were significant predictors of participants' judgments as teaching.
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m3)$adj.r.squared*100)` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r sprintf('%.2f', summary(m3)$fstatistic[1])`, *p* `r if(lmp(m3) < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', lmp(m3))))}`).
+It was found that tempo (IOIs; *$\beta$* = `r summary(m3)$coefficients[2]`, *p* `r if(summary(m3)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m3)$coefficients[2, 4])))}`) and dynamics for the forte parts (KV; *$\beta$* = `r summary(m3)$coefficients[4]`, *p* `r if(summary(m3)$coefficients[4, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m3)$coefficients[4, 4])))}`) were significant predictors of participants' judgments as teaching.
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte).
-The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m4)$adj.r.squared*100)` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r sprintf('%.1f', summary(m4)$fstatistic[1])`, *p* `r if(lmp(m4) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m4)))}`).
-It was found that tempo (IOIs; *$\beta$* = `r summary(m4)$coefficients[2]`, *p* `r if(summary(m4)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[2, 4]))}`) and dynamics contrast from piano to forte (KV-Diff; *$\beta$* = `r summary(m4)$coefficients[5]`, *p* `r if(summary(m4)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[5, 4]))}`) were significant predictors of participants' judgments as teaching.
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m4)$adj.r.squared*100)` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r sprintf('%.1f', summary(m4)$fstatistic[1])`, *p* `r if(lmp(m4) < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', lmp(m4))))}`).
+It was found that tempo (IOIs; *$\beta$* = `r summary(m4)$coefficients[2]`, *p* `r if(summary(m4)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m4)$coefficients[2, 4])))}`) and dynamics contrast from piano to forte (KV-Diff; *$\beta$* = `r summary(m4)$coefficients[5]`, *p* `r if(summary(m4)$coefficients[5, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m4)$coefficients[5, 4])))}`) were significant predictors of participants' judgments as teaching.
 
 ```{r plot-ioi-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:ioi-1}Experiment 1: Scatter plot showing the correlation between tempo feature (IOIs) and average participants' judgments as teaching for each recording.
-Therefore, each dot represents each stimulus."}
+Therefore, each dot represents each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
 img_cor_ioi_1
@@
 ```{r plot-kot-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:kot-1}Experiment 1: Scatter plot showing the correlation between articulation feature (KOT) and average participants' judgments as teaching for each recording.
-Therefore, each dot represents each stimulus."}
+Therefore, each dot represents each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
 img_cor_kot_1
@@
 ```{r plot-vel-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-1}Experiment 1: Scatter plot showing the correlation between dynamics feature (KV) and average participants' judgments as teaching for each recording.
-Therefore, each dot represents each stimulus."}
+Therefore, each dot represents each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
 img_cor_vel_1
@@
 ```{r plot-vel-diff-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-diff-1}Experiment 1: Scatter plot showing the correlation between dynamics contrast feature (KV-Diff) and average participants' judgments as teaching for each recording.
-Therefore, each dot represents each stimulus."}
+Therefore, each dot represents each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
 img_cor_vel_diff_1
@@
 These performance features were overall consistent with what expert pianists did in our previous experiments for teaching purposes.
-Therefore, our findings suggest that musicians may rely on generic pedagogical behaviours (e.g., slower demonstration, exaggeration) to infer teaching intentions of expert pianists, only by listening to recorded performances.
+Therefore, our findings suggest that musicians may rely on generic pedagogical behaviours (e.g., slower demonstration, exaggeration) to infer teaching intentions of expert pianists when listening to recorded performances.
 
@@
 The aim of Experiment 2 was to replicate the findings in Experiment 1 with a more naturalistic piece of music.
-Given the findings in Experiment 1, we predicted that slower performance would be likely to be judged as teaching regardless of which expressive technique (articulation or dynamics) was implemented.
+Given the findings in Experiment 1, we predicted that slower performance would be likely to be judged as teaching regardless of which expressive technique (i.e., articulation or dynamics) was implemented.
 Also performances with exaggerated articulation and dynamics (in particular, longer legato and shorter staccato, larger contrast between forte and piano) would be likely to be judged as teaching.
@@
 Only the 8th notes with expressive notations were included for data analysis.
-As a result, only one 8th note in the 4th measure without any expression was not included.
+As a result, only one 8th note in the 4th measure without any expression was not included (see *Figure \ref{fig:stim2}*).
 
@@
 The curved line (slur) indicates legato and the dots indicate staccato.
+In multiple regression analysis, (1) corresponds to Legato model and (2) corresponds to Staccato model.
 (B)Dynamics.
 The symbol `f' denotes forte and the symbol `p' denotes piano.
-Only the 8th notes with expressive notations were used for data analysis.", echo = FALSE}
+In multiple regression analysis, (3) corresponds to Forte model and (2) corresponds to Piano model.
+Only the 8th notes with expressive notations (i.e., (1), (2), (3), (4)) were used for data analysis.", echo = FALSE}
 stim_a_2 <- image_border(image_read(here("paper/image", "stim_a_2.jpg")), "#FFFFFF", "120x120")
@@
 A one sample *t*-test was performed to compare the accuracy of participants' judgments against the chance level (50%).
-The mean percentage of correct answers [*M* = `r sprintf('%.1f', subset$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset$SD_Percent)`] was significantly higher than chance (*t*(`r ttest_all$parameter`) = `r sprintf('%.2f', ttest_all$statistic)`, *p* `r if(ttest_all$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_all$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_all$effsize)`).
+The mean percentage of correct answers [*M* = `r sprintf('%.1f', subset$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset$SD_Percent)`] was significantly higher than chance (*t*(`r ttest_all$parameter`) = `r sprintf('%.2f', ttest_all$statistic)`, *p* `r if(ttest_all$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', ttest_all$p.value)))}`, cohen's *d* = `r sprintf('%.2f', coheneff_all$effsize)`).
 
 We also performed a one sample *t*-test for each technique separately.
-For articulation, the mean percentage of correct answers [*M* = `r sprintf('%.1f', subset_ad[Skill == "articulation"]$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset_ad[Skill == "articulation"]$SD_Percent)`] was not significantly different from chance (*t*(`r ttest_art$parameter`) = `r sprintf('%.2f', ttest_art$statistic)`, *p* `r if(ttest_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_art$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_art$effsize)`).
-Also for dynamics, the mean percentage of correct answers [*M* = `r sprintf('%.1f', subset_ad[Skill == "dynamics"]$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset_ad[Skill == "dynamics"]$SD_Percent)`] was not significantly different from chance (*t*(`r ttest_dyn$parameter`) = `r sprintf('%.2f', ttest_dyn$statistic)`, *p* `r if(ttest_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_dyn$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_dyn$effsize)`).
-A paired *t*-test revealed that there was no significant difference between the two techniques in terms of the accuracy (*t*(`r ttest_paired$parameter`) = `r sprintf('%.2f', ttest_paired$statistic)`, *p* `r if(ttest_paired$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ttest_paired$p.value))}`, cohen's *d* = `r sprintf('%.2f', coheneff_paired$effsize)`).
+For articulation, the mean percentage of correct answers [*M* = `r sprintf('%.1f', subset_ad[Skill == "articulation"]$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset_ad[Skill == "articulation"]$SD_Percent)`] was not significantly different from chance (*t*(`r ttest_art$parameter`) = `r sprintf('%.2f', ttest_art$statistic)`, *p* `r if(ttest_art$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', ttest_art$p.value)))}`, cohen's *d* = `r sprintf('%.2f', coheneff_art$effsize)`).
+Also for dynamics, the mean percentage of correct answers [*M* = `r sprintf('%.1f', subset_ad[Skill == "dynamics"]$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset_ad[Skill == "dynamics"]$SD_Percent)`] was not significantly different from chance (*t*(`r ttest_dyn$parameter`) = `r sprintf('%.2f', ttest_dyn$statistic)`, *p* `r if(ttest_dyn$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', ttest_dyn$p.value)))}`, cohen's *d* = `r sprintf('%.2f', coheneff_dyn$effsize)`).
+A paired *t*-test revealed that there was no significant difference between the two techniques in terms of the accuracy (*t*(`r ttest_paired$parameter`) = `r sprintf('%.2f', ttest_paired$statistic)`, *p* `r if(ttest_paired$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', ttest_paired$p.value)))}`, cohen's *d* = `r sprintf('%.2f', coheneff_paired$effsize)`).
 
-## Correlation
+## Correlations
 ### Tempo (IOIs)
-Unlike Experiment 1, there was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_ioi_art$p.value))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-2}*).
+Unlike Experiment 1, there was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$p.value)))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$p.value)))}`, *Figure \ref{fig:ioi-2}*).
 Participants tended to identify slower performances as teaching for dynamics recordings.
@@
 ### Articulation (KOT)
-Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; *r(`r cor_kot_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_sta$p.value))}`, Staccato; *r(`r cor_kot_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_sta$p.value))}`, *Figure \ref{fig:kot-2}*, left).
+Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; *r(`r cor_kot_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$p.value)))}`, Staccato; *r(`r cor_kot_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$p.value)))}`, *Figure \ref{fig:kot-2}*, left).
 
-For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (*r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`).
-However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (*r(`r cor_kot_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_pia$p.value))}`), suggesting that performances with staccato-style piano were more likely to be considered as teaching performance (*Figure \ref{fig:kot-2}*, right).
+For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (*r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$p.value)))}`).
+However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (*r(`r cor_kot_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_kot_pia$p.value)))}`), suggesting that performances with staccato-style piano were more likely to be considered as teaching performance (*Figure \ref{fig:kot-2}*, right).
+However, this significance disappeared after removing one outlier outside of 2 standard deviations in terms of KOT values for piano.
 
@@
 As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-2}*, right).
-Specifically, performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_pia$p.value))}`) were more likely to be judged as teaching.
+Specifically, performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_for$p.value)))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_pia$p.value)))}`) were more likely to be judged as teaching.
 
-For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r(`r cor_vel_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-2}*, left).
+For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$p.value)))}`, Staccato; *r(`r cor_vel_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$p.value)))}`, *Figure \ref{fig:vel-2}*, left).
 
@@
 As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (*Figure \ref{fig:vel-diff-2}*, right).
-Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).
+Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_diff_ftop$p.value)))}`, From Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_diff_ptof$p.value)))}`).
 
-For articulation recordings, there was no significant relationship between KV difference between transition points from legato to staccato and participants' judgments as teaching (*r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ltos$p.value))}`).
-However, there was a significant relationship between the transition points from staccato to legato and participants' judgments as teaching (*r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_stol$p.value))}`), suggesting that performances with larger contrast from staccato to legato were more likely to be considered as teaching performance (*Figure \ref{fig:vel-diff-2}*, left).
+For articulation recordings, there was no significant relationship between KV difference between transition points from legato to staccato and participants' judgments as teaching (*r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_diff_ltos$p.value)))}`).
+However, there was a significant relationship between the transition points from staccato to legato and participants' judgments as teaching (*r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$p.value)))}`), suggesting that performances with larger contrast from staccato to legato were more likely to be considered as teaching performance (*Figure \ref{fig:vel-diff-2}*, left).
 
@@
 As Experiment 1, we performed multiple regression analyses to further explore which feature of performance contributed the most to participants' judgments as teaching.
-Statistical model assumptions were tested and most of the assumptions (see *Supplementary Material* for details) were met.
 Again, since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.
 staccato, forte vs.
-piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in *Data analysis* in Experiment 1).
+piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in *Data analysis* in Experiment 1 and *Figure \ref{fig:stim2}*).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
-The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m1)$adj.r.squared*100)` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r sprintf('%.2f', summary(m1)$fstatistic[1])`, *p* `r if(lmp(m1) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', lmp(m1)))}`).
-It was found that tempo (IOIs; *$\beta$* = `r summary(m1)$coefficients[2]`, *p* `r if(summary(m1)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[2, 4]))}`), dynamics (KV; *$\beta$* = `r summary(m1)$coefficients[4]`, *p* `r if(summary(m1)$coefficients[4, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[4, 4]))}`) and dynamics contrast (KV-Diff; *$\beta$* = `r summary(m1)$coefficients[5]`, *p* `r if(summary(m1)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m1)$coefficients[5, 4]))}`) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
-However, articulation (KOT; *$\beta$* = `r summary(m1)$coefficients[3]`, *p* `r if(summary(m1)$coefficients[3, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', summary(m1)$coefficients[3, 4]))}`) for the legato parts was not a significant predictor as opposed to Experiment 1.
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m1)$adj.r.squared*100)` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r sprintf('%.2f', summary(m1)$fstatistic[1])`, *p* `r if(lmp(m1) < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', lmp(m1))))}`).
+It was found that tempo (IOIs; *$\beta$* = `r summary(m1)$coefficients[2]`, *p* `r if(summary(m1)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m1)$coefficients[2, 4])))}`), dynamics (KV; *$\beta$* = `r summary(m1)$coefficients[4]`, *p* `r if(summary(m1)$coefficients[4, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m1)$coefficients[4, 4])))}`) and dynamics contrast (KV-Diff; *$\beta$* = `r summary(m1)$coefficients[5]`, *p* `r if(summary(m1)$coefficients[5, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m1)$coefficients[5, 4])))}`) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
+However, articulation (KOT; *$\beta$* = `r summary(m1)$coefficients[3]`, *p* `r if(summary(m1)$coefficients[3, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', summary(m1)$coefficients[3, 4])))}`) for the legato parts was not a significant predictor as opposed to Experiment 1.
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato).
-The overall model was not statistically significant ($R^{2}$ = `r sprintf('%.1f', summary(m2)$adj.r.squared*100)`, *F*(`r summary(m2)$fstatistic[2]`, `r summary(m2)$fstatistic[3]`) = `r sprintf('%.2f', summary(m2)$fstatistic[1])`, *p* `r if(lmp(m2) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m2)))}`).
+The overall model was not statistically significant ($R^{2}$ = `r sprintf('%.1f', summary(m2)$adj.r.squared*100)`, *F*(`r summary(m2)$fstatistic[2]`, `r summary(m2)$fstatistic[3]`) = `r sprintf('%.2f', summary(m2)$fstatistic[1])`, *p* `r if(lmp(m2) < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', lmp(m2))))}`).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano).
-The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m3)$adj.r.squared*100)` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r sprintf('%.1f', summary(m3)$fstatistic[1])`, *p* `r if(lmp(m3) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m3)))}`).
-It was found that dynamics contrast from forte to piano (KV-Diff; *$\beta$* = `r summary(m3)$coefficients[5]`, *p* `r if(summary(m3)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m3)$coefficients[5, 4]))}`) were significant predictors of participants' judgments as teaching.
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m3)$adj.r.squared*100)` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r sprintf('%.1f', summary(m3)$fstatistic[1])`, *p* `r if(lmp(m3) < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', lmp(m3))))}`).
+It was found that dynamics contrast from forte to piano (KV-Diff; *$\beta$* = `r summary(m3)$coefficients[5]`, *p* `r if(summary(m3)$coefficients[5, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m3)$coefficients[5, 4])))}`) were significant predictors of participants' judgments as teaching.
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte).
-The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m4)$adj.r.squared*100)` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r sprintf('%.2f', summary(m4)$fstatistic[1])`, *p* `r if(lmp(m4) < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', lmp(m4)))}`).
-It was found that tempo (IOIs; *$\beta$* = `r summary(m4)$coefficients[2]`, *p* `r if(summary(m4)$coefficients[2, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[2, 4]))}`) and dynamics contrast from piano to forte (KV-Diff; *$\beta$* = `r summary(m4)$coefficients[5]`, *p* `r if(summary(m4)$coefficients[5, 4] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', summary(m4)$coefficients[5, 4]))}`) were significant predictors of participants' judgments as teaching.
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m4)$adj.r.squared*100)` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r sprintf('%.2f', summary(m4)$fstatistic[1])`, *p* `r if(lmp(m4) < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', lmp(m4))))}`).
+It was found that tempo (IOIs; *$\beta$* = `r summary(m4)$coefficients[2]`, *p* `r if(summary(m4)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m4)$coefficients[2, 4])))}`) and dynamics contrast from piano to forte (KV-Diff; *$\beta$* = `r summary(m4)$coefficients[5]`, *p* `r if(summary(m4)$coefficients[5, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m4)$coefficients[5, 4])))}`) were significant predictors of participants' judgments as teaching.
 
 ```{r plot-ioi-2, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:ioi-2}Experiment 2: Scatter plot showing the correlation between tempo featurea (IOIs) and average participants' judgments as teaching for each recording.
-Therefore, each dot represents each stimulus."}
+Therefore, each dot represents each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
 img_cor_ioi_2
@@
 ```{r plot-kot-2, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:kot-2}Experiment 2: Scatter plot showing the correlation between articulation features (KOT) and average participants' judgments as teaching for each recording.
-Therefore, each dot represents each stimulus."}
+Therefore, each dot represents each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
 img_cor_kot_2
@@
 ```{r plot-vel-2, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-2}Experiment 2: Scatter plot showing the correlation between dynamics features (KV) and average participants' judgments as teaching for each recording.
-Therefore, each dot represents each stimulus."}
+Therefore, each dot represents each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
 img_cor_vel_2
@@
 
-```{r plot-vel-diff-2, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-diff-2}Experiment 2: Scatter plot showing the correlation between dynamics contrast features (KV-Diff) and average participants' judgment as teaching for each stimulus."}
+```{r plot-vel-diff-2, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-diff-2}Experiment 2: Scatter plot showing the correlation between dynamics contrast features (KV-Diff) and average participants' judgment as teaching for each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
 img_cor_vel_diff_2
@@
 # Discussion
-The aim of Experiment 2 was to replicate the results of Experiment 1 with a more naturalistic piece of music.
+The aim of Experiment 2 was to replicate the results of Experiment 1 and examine how musicians would infer teaching intentions when listening to a more naturalistic piece of music.
 However, unlike Experiment 1, tempo (IOIs) does not seem to contribute to participants' judgments as teaching.
@@
 We could successfully replicate that performances with larger contrast between forte and piano seem to be considered as teaching.
-Moreover, performances with both exaggerated forte and piano were considered to be for teaching.
+Moreover, performances with both exaggerated forte and piano were considered to be for teaching whereas performances with only exaggerated forte were judged as teaching in Experiment 1.
 These consistent results suggest that loudness (dynamics) might be used as a reliable cue to infer teaching intentions regardless of the complexity of a musical piece.
@@
 Multiple regression analyses also implied that tempo feature was not a strong predictor of participants' judgments as teaching when listening to a musically complex piece.
-However, dynamics contrast seems to be a strong predictor of participants' judgments as teaching, especially for dynamics recordings.
+As Experiment 1, dynamics contrast seems to be a strong predictor of participants' judgments as teaching, especially for dynamics recordings.
 This finding also suggests that loudness might be a strong cue to infer pedagogical intentions even in a naturalistic piece of music.
@@
 
-The present study investigated whether and how musician infer pedagogical intentions by listening to piano recordings.
+The present study investigated whether and how musicians infer pedagogical intentions by listening to piano recordings.
 In both Experiment 1 and 2, participants were able to choose correct answers accurately more than chance (50%).
@@
 This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al.
-(*submitted*) and all the selected recordings did not exhibit the characteristics of teaching performance (e.g., slow performance, exaggeration).
+(*submitted*) and all the selected recordings did not exhibit the characteristics of teaching performance (e.g., slower demonstration, exaggeration).
 The reason why we randomly selected the stimuli from each condition (i.e., teaching or performing) was because all the characteristics of teaching performance (e.g., IOIs, KOT, KV) were intercorrelated and it was difficult to choose stimuli based on one single criterion.
 Future research should examine if musicians answer more accurately with more experimentally controlled stimuli.
+Another possibility for the low accuracy could be that it was difficult even for musicians to find which cues were produced for teaching when listening to one piece of music with several phrases.
+Future research should examine whether accuracy would be improved when listening to phrases compared to pieces.
 
@@
 Across the two experiments, it was found that loudness, particularly larger contrast between forte and piano, strongly contributed to participants' judgments when listening to dynamics recordings.
-On the other hand, unlike what we predicted, slower performance was only considered to be for teaching in Experiment 1 where the stimuli consisted of a simple musical scale.
-Also, we could not find that performances with exaggerated articulation (e.g., longer legato and shorter staccato) were more likely to be judged as teaching in Experiment 2.
+On the other hand, unlike what we predicted, slower performance was only considered to be for teaching in Experiment 1 where the stimuli consisted of simple musical scales.
+Also, we could not find that performances with exaggerated articulation (i.e., longer legato and shorter staccato) were more likely to be judged as teaching in Experiment 2.
 This might suggest that some characteristics of performance are not necessarily used or reliable to infer performers' intentions when listening to musically complex pieces.
@@
 Another possibility is that modulations can also be considered as one of the expressions or interpretations.
+These findings may suggest that it is easier for novices to learn musical expressive techniques in musical scales rather than in a piece.
 
 In the current study, we exclusively recruited musicians to explore our research questions.
-The reason why we recruited musicians only was because the concepts of articulation and dynamics seem to be difficult for those who don't play an instrument to understand in the current settings.
-It would be important to investigate how novices perceive and infer pedagogical intentions differently from musicians, who already have some experience in playing music.
+The reason why we recruited musicians only was because the concepts of articulation and dynamics seem to be difficult for those who don't play an instrument to understand in the current experimental settings.
+It would be important to investigate how complete novices perceive and infer pedagogical intentions differently from musicians, who already have some experience in playing music.
 

### 2022-04-15 paper/manuscript.tex
update figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
update figures (grey scale)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
second draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 \documentclass[
-  man,floatsintext]{apa6}
+  man]{apa6}
 \usepackage{amsmath,amssymb}
@@
 {}{\PatchFailed}
-\keywords{teaching, intention, skill transmission, musical expression}
+\keywords{perception, expression, learning, expertise, music education}
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
 \usepackage{csquotes}
+\usepackage[titles]{tocloft}
+\cftpagenumbersoff{figure}
+\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
+\renewcommand{\cftfigaftersnum}{.\space}
+\setlength{\cftfigindent}{0pt}
+\setlength{\cftafterloftitleskip}{0pt}
+\settowidth{\cftfignumwidth}{Figure 10.\qquad}
 \ifLuaTeX
@@
   pdflang={en-EN},
-  pdfkeywords={teaching, intention, skill transmission, musical expression},
+  pdfkeywords={perception, expression, learning, expertise, music education},
   hidelinks,
@@
 Perceiving pedagogical intentions is vital when learning skills from others.
-Our previous research demonstrated that expert pianists systematically modulated their sound so as to teach musical expressive techniques such as articulation and dynamics.
-For example, pianists played slower and exaggerated each technique when they had an intention to teach.
 Here we investigated whether the modulations that expert pianists produce when they intend to teach are also perceived by listeners as conveying pedagogical intentions.
-In the current study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
-Half of the recordings was produced when pianists were instructed to play as if they were teaching the designated musical technique in a lesson (i.e., teaching recordings) whereas the other half was produced when pianists were instructed to play as if they were performing it in a concert (i.e., performing recordings).
-Participants were asked to judge whether each recording was produced for teaching purposes or not.
-We calculated the accuracy of participants' judgments to investigate whether they could distinguish teaching recordings from performing recordings.
-Also, recordings were quantified with regard to tempo, articulation and dynamic so that we could perform correlation and multiple regression analysis to investigate which features of piano performance made musicians infer teaching intentions.
+Musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented.
+They were asked to judge whether each recording was produced for teaching purposes or not.
 The findings in Experiment 1 with a simple musical scale demonstrated that the accuracy of musicians' judgments was significantly above chance.
-Also, it was found that slower tempo contributed to musicians' judgments as teaching regardless of the techniques.
-Moreover, performances with exaggeration for each technique (e.g., longer legato, shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching.
+Also, slower tempo contributed to musicians' judgments as teaching regardless of the techniques.
+Moreover, performances with exaggeration for each technique were more likely to be judged as teaching.
 Experiment 2 aimed to replicate the findings of Experiment 1 with a more naturalistic piece.
-As Experiment 1, the accuracy of musicians' judgments was significantly above chance.
-However, we only replicated that performances with exaggerated dynamics (in particular, larger contrast between forte and piano) were more likely to be judged as teaching.
-Taken together, loudness (dynamics) seems to be reliably used to infer teaching intentions regardless of the complexity of a musical piece.
+The accuracy of musicians' judgments was significantly above chance.
+However, we only replicated that performances with exaggerated dynamics were more likely to be judged as teaching.
+Taken together, loudness seems to be reliably used to infer teaching intentions regardless of the complexity of a musical piece.
 Also, typical pedagogical behaviour such as slowing down may not be necessarily perceived as teaching performance when learning complex skills such as artistic expression.
@@
 For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills (e.g., Brand, Baldwin, \& Ashburn, 2002; Saint-Georges et al., 2013).
-Further studies have revealed that even towards adult learners, people modulated their speech and action in a similar way as they did for infants (McEllin, Knoblich, \& Sebanz, 2017; Uther, Knoll, \& Burnham, 2007).
+Further studies have revealed that even towards adult learners, people modulate their speech and action in a similar way as they did for infants (McEllin, Knoblich, \& Sebanz, 2017; Uther, Knoll, \& Burnham, 2007).
 Moreover, McEllin, Sebanz, and Knoblich (2018) demonstrated that people could identify informative intentions such as acting with others or teaching by relying on specific kinematics cues (e.g., velocity profiles of movements).
@@
 
-Here we investigated whether the modulations that expert pianists make when they intended to teach are also perceived by listeners as conveying teaching intentions.
+Here we investigated whether the modulations that expert pianists make when they intend to teach are perceived by listeners as conveying teaching intentions.
 We started from the assumption that listeners would be able to infer intentions from listening to recordings because previous research revealed that sound alone is sufficient to communicate different aspects of a musical performance.
-For instance, listeners are well able to infer performers' intended emotions when listening to recorded performances (e.g., Akkermans et al., 2019; Gabrielsson \& Juslin, 1996).
+For instance, listeners are generally able to infer performers' intended emotions when listening to recorded performances and musically skilled listeners are even better at decoding emotions from performances (e.g., Akkermans et al., 2019; Gabrielsson \& Juslin, 1996).
 
@@
 First, we calculated the accuracy of participants' judgments to examine whether they could distinguish teaching recordings from performing recordings.
-Furthermore, recordings were quantified with regard to tempo, articulation and dynamic.
+Furthermore, recordings were quantified with regard to tempo, articulation and dynamics.
 Using correlations and multiple regression analysis, we examined which modulations of performance were used to infer teaching intentions.
 
-If performers' intentions are understood by learners with basic musical skills, listeners should be able to distinguish teaching recordings from performing recordings.
-Moreover, the same modulations of pedagogical performance parameters observed in our previous experiments such as slower demonstration and exaggerated performance, should be used to infer teaching intentions by the earners.
-In Experiment 1 learners listened to performances with that followed simple musical scales.
-In Experiment 2 learners listen to performances of a more naturalistic piece of music in aan attempt to replicate the findings from Experiment 1.
+If performers' intentions are understood by learners with basic musical skills, they should be able to distinguish teaching recordings from performing recordings.
+Moreover, the same modulations of pedagogical performance parameters observed in our previous experiments such as slower demonstration and exaggerated performance, should be used to infer teaching intentions by the learners.
+In Experiment 1 learners listened to performances that followed simple musical scales.
+In Experiment 2 learners listened to performances of a more naturalistic piece of music in an attempt to replicate the findings from Experiment 1.
 
@@
 
-We selected stimuli from our previous experiments (Tominaga et al., \emph{submitted}).
+We selected stimuli from the performances obtained in our previous experiments (Tominaga et al., \emph{submitted}).
 Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files.
@@
 Second, we run multiple regression that included all four performance features to examine which predictor significantly contributed to participants' judgments as teaching.
-Since articulation and dynamics were comprised of two opposite directional values (i.e., legato vs.~staccato, forte vs.~piano), we created four separate models that included different parts of the piece (see ).
+Since articulation and dynamics were comprised of two opposite directional values (i.e., legato vs.~staccato, forte vs.~piano), we created four separate models that included different parts of the piece.
 Each model considered only parts of the piece that comprised either legato, staccato, forte or piano.
 For articulation recordings, there were two models.
-The Legato model considered only legato parts of the performances.
+The Legato model (\emph{Figure \ref{fig:stim1}}, 1) considered only legato parts of the performances.
 We entered the legato parts of KOT and KV and KV-Diff or transition points from legato to staccato.
-The Staccato model considered only staccato parts of the performances.
+The Staccato model (\emph{Figure \ref{fig:stim1}}, 2) considered only staccato parts of the performances.
 We entered the staccato parts of KOT and KV and KV-Diff of transition points from staccato to legato.
 Similarly, there were two models for dynamics recordings.
-The Forte model considered only forte parts of the stimuli for KV and KOT, and transition points from forte to piano for KV-Diff.
-The Piano model considered only piano parts of the stimuli for KV and KOT, and transition points from piano to forte for KV-Diff.
+The Forte model (\emph{Figure \ref{fig:stim1}}, 3) considered only forte parts of the performances for KV and KOT, and transition points from forte to piano for KV-Diff.
+The Piano model (\emph{Figure \ref{fig:stim1}}, 4) considered only piano parts of the performances for KV and KOT, and transition points from piano to forte for KV-Diff.
 With regard to tempo (IOIs), there was only one value for each recording regardless of the subcomponents because tempo was consistent across the performance.
@@
 The curved line (slur) indicates legato and the dots indicate staccato.
+In multiple regression analysis, (1) corresponds to Legato model and (2) corresponds to Staccato model.
 (B)Dynamics.
 The symbol `f' denotes forte and the symbol `p' denotes piano.
-Only the parts composed of 16th notes were used for data analysis.}\label{fig:stim-1}
+In multiple regression analysis, (3) corresponds to Forte model and (2) corresponds to Piano model.
+Only the parts composed of 16th notes (i.e., (1), (2), (3), (4)) were used for data analysis.}\label{fig:stim-1}
 \end{figure}
@@
 They were required to respond by pressing a left-arrow (yes) or right-arrow (no) key for each judgment.
-Headphone image from Flaticon.com}\label{fig:procedure-1}
+Headphone image from Flaticon.com.}\label{fig:procedure-1}
 \end{figure}
@@
 A one sample \emph{t}-test was performed to compare the accuracy of participants' judgments against the chance level (50\%).
-The mean percentage of correct answers {[}\emph{M} = 52.7, \emph{SD} = 4.90{]} was significantly higher than chance (\emph{t}(19) = 2.47, \emph{p} = 0.02, cohen's \emph{d} = 0.55).
+The mean percentage of correct answers {[}\emph{M} = 52.7, \emph{SD} = 4.90{]} was significantly higher than chance (\emph{t}(19) = 2.47, \emph{p} = .02, cohen's \emph{d} = 0.55).
 
 We also performed a one sample \emph{t}-test for each technique separately.
-For articulation, the mean percentage of correct answers {[}\emph{M} = 50.2, \emph{SD} = 6.55{]} was not significantly different from chance (\emph{t}(19) = 0.14, \emph{p} = 0.89, cohen's \emph{d} = 0.03).
-For dynamics, the mean percentage of correct answers {[}\emph{M} = 55.2, \emph{SD} = 7.81{]} was significantly higher than chance (\emph{t}(19) = 2.98, \emph{p} = 0.01, cohen's \emph{d} = 0.67).
-A paired \emph{t}-test revealed that there was a significant difference between the two techniques in terms of the accuracy (\emph{t}(19) = -2.12, \emph{p} = 0.05, cohen's \emph{d} = -0.69), suggesting participants chose correct answers more for dynamics recordings than articulation recordings.
+For articulation, the mean percentage of correct answers {[}\emph{M} = 50.2, \emph{SD} = 6.55{]} was not significantly different from chance (\emph{t}(19) = 0.14, \emph{p} = .89, cohen's \emph{d} = 0.03).
+For dynamics, the mean percentage of correct answers {[}\emph{M} = 55.2, \emph{SD} = 7.81{]} was significantly higher than chance (\emph{t}(19) = 2.98, \emph{p} = .01, cohen's \emph{d} = 0.67).
+A paired \emph{t}-test revealed that there was a significant difference between the two techniques in terms of the accuracy (\emph{t}(19) = -2.12, \emph{p} = .05, cohen's \emph{d} = -0.69), suggesting participants chose correct answers more for dynamics recordings than articulation recordings.
 
-\hypertarget{correlation}{%
-\subsection{Correlation}\label{correlation}}
+\hypertarget{correlations}{%
+\subsection{Correlations}\label{correlations}}
 
@@
 
-Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; \emph{r(46)} = .77, \emph{p} \textless{} 0.001, Dynamics; \emph{r(46)} = .42, \emph{p} = 0.003, \emph{Figure \ref{fig:ioi-1}}).
+Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; \emph{r(46)} = .77, \emph{p} \textless{} .001, Dynamics; \emph{r(46)} = .42, \emph{p} = .003, \emph{Figure \ref{fig:ioi-1}}).
 Participants tended to identify slower performances as teaching.
@@
 For articulation recordings, there was a significant relationship between KOT values and participants' judgments as teaching (\emph{Figure \ref{fig:kot-1}}, left).
-Specifically, performances with shorter staccato (\emph{r(46)} = -.73, \emph{p} \textless{} 0.001) and longer legato (\emph{r(46)} = .40, \emph{p} = 0.005) were more likely to be judged as teaching.
+Specifically, performances with shorter staccato (\emph{r(46)} = -.73, \emph{p} \textless{} .001) and longer legato (\emph{r(46)} = .40, \emph{p} = .005) were more likely to be judged as teaching.
 
-For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r(46)} = -.04, \emph{p} = 0.81, Piano; \emph{r(46)} = -.19, \emph{p} = 0.19, \emph{Figure \ref{fig:kot-1}}, right).
+For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r(46)} = -.04, \emph{p} = .81, Piano; \emph{r(46)} = -.19, \emph{p} = .19, \emph{Figure \ref{fig:kot-1}}, right).
 
@@
 For dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-1}}, right).
-Specifically, performances with louder forte were more likely to be judged as teaching (\emph{r(46)} = .45, \emph{p} = 0.001).
-However, there was no significant relationship between KV values for piano and participants' judgments as teaching (\emph{r(46)} = -.22, \emph{p} = 0.13).
+Specifically, performances with louder forte were more likely to be judged as teaching (\emph{r(46)} = .45, \emph{p} = .001).
+However, there was no significant relationship between KV values for piano and participants' judgments as teaching (\emph{r(46)} = -.22, \emph{p} = .13).
 
-For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r(46)} = .10, \emph{p} = 0.52, Staccato; \emph{r(46)} = -.02, \emph{p} = 0.87, \emph{Figure \ref{fig:vel-1}}, left).
+For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r(46)} = .10, \emph{p} = .52, Staccato; \emph{r(46)} = -.02, \emph{p} = .87, \emph{Figure \ref{fig:vel-1}}, left).
 
@@
 For dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (\emph{Figure \ref{fig:vel-diff-1}}, right).
-Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r(46)} = -.50, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r(46)} = .62, \emph{p} \textless{} 0.001).
+Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r(46)} = -.50, \emph{p} \textless{} .001, From Piano to Forte; \emph{r(46)} = .62, \emph{p} \textless{} .001).
 
-For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r(46)} = -.26, \emph{p} = 0.071, From Staccato to Legato; \emph{r(46)} = -.19, \emph{p} = 0.21, \emph{Figure \ref{fig:vel-diff-1}}, left).
+For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r(46)} = -.26, \emph{p} = .071, From Staccato to Legato; \emph{r(46)} = -.19, \emph{p} = .21, \emph{Figure \ref{fig:vel-diff-1}}, left).
 
@@
 In order to further explore which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted.
-Statistical model assumptions were tested using the \emph{performance} R package (Lüdecke, Ben-Shachar, Patil, Waggoner, \& Makowski, 2021) and most of the assumptions (see \emph{Supplementary Material} for details) were met.
-Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in \emph{Data analysis}).
+Statistical model assumptions were tested using the \emph{performance} R package (Lüdecke, Ben-Shachar, Patil, Waggoner, \& Makowski, 2021).
+Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in \emph{Data analysis} and \emph{Figure \ref{fig:stim1}}).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
-The result of the regression indicated that the model explained 64.6 \% of the variance (\emph{F}(4, 43) = 22.5, \emph{p} \textless{} 0.001).
-It was found that tempo (IOIs; \emph{\(\beta\)} = 0.78, \emph{p} \textless{} 0.001) and articulation for the legato parts (KOT; \emph{\(\beta\)} = 0.26, \emph{p} = 0.004) were significant predictors of participants' judgments as teaching.
+The result of the regression indicated that the model explained 64.6 \% of the variance (\emph{F}(4, 43) = 22.5, \emph{p} \textless{} .001).
+It was found that tempo (IOIs; \emph{\(\beta\)} = 0.78, \emph{p} \textless{} .001) and articulation for the legato parts (KOT; \emph{\(\beta\)} = 0.26, \emph{p} = .004) were significant predictors of participants' judgments as teaching.
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato).
-The result of the regression indicated that the model explained 64.0 \% of the variance (\emph{F}(4, 43) = 21.9, \emph{p} \textless{} 0.001).
-It was found that tempo (IOIs; \emph{\(\beta\)} = 0.52, \emph{p} = 0.002) and articulation for the staccato parts (KOT; \emph{\(\beta\)} = -0.28, \emph{p} = 0.020) were significant predictors of participants' judgments as teaching.
+The result of the regression indicated that the model explained 64.0 \% of the variance (\emph{F}(4, 43) = 21.9, \emph{p} \textless{} .001).
+It was found that tempo (IOIs; \emph{\(\beta\)} = 0.52, \emph{p} = .002) and articulation for the staccato parts (KOT; \emph{\(\beta\)} = -0.28, \emph{p} = .020) were significant predictors of participants' judgments as teaching.
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano).
-The result of the regression indicated that the model explained 35.9 \% of the variance (\emph{F}(4, 43) = 7.58, \emph{p} \textless{} 0.001).
-It was found that tempo (IOIs; \emph{\(\beta\)} = 0.35, \emph{p} = 0.007) and dynamics for the forte parts (KV; \emph{\(\beta\)} = 0.73, \emph{p} = 0.048) were significant predictors of participants' judgments as teaching.
+The result of the regression indicated that the model explained 35.9 \% of the variance (\emph{F}(4, 43) = 7.58, \emph{p} \textless{} .001).
+It was found that tempo (IOIs; \emph{\(\beta\)} = 0.35, \emph{p} = .007) and dynamics for the forte parts (KV; \emph{\(\beta\)} = 0.73, \emph{p} = .048) were significant predictors of participants' judgments as teaching.
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte).
-The result of the regression indicated that the model explained 51.2 \% of the variance (\emph{F}(4, 43) = 13.3, \emph{p} \textless{} 0.001).
-It was found that tempo (IOIs; \emph{\(\beta\)} = 0.38, \emph{p} \textless{} 0.001) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 0.99, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.
+The result of the regression indicated that the model explained 51.2 \% of the variance (\emph{F}(4, 43) = 13.3, \emph{p} \textless{} .001).
+It was found that tempo (IOIs; \emph{\(\beta\)} = 0.38, \emph{p} \textless{} .001) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 0.99, \emph{p} \textless{} .001) were significant predictors of participants' judgments as teaching.
 
@@
 \caption{\label{fig:ioi-1}Experiment 1: Scatter plot showing the correlation between tempo feature (IOIs) and average participants' judgments as teaching for each recording.
-Therefore, each dot represents each stimulus.}\label{fig:plot-ioi-1}
+Therefore, each dot represents each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-ioi-1}
 \end{figure}
@@
 \caption{\label{fig:kot-1}Experiment 1: Scatter plot showing the correlation between articulation feature (KOT) and average participants' judgments as teaching for each recording.
-Therefore, each dot represents each stimulus.}\label{fig:plot-kot-1}
+Therefore, each dot represents each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-kot-1}
 \end{figure}
@@
 \caption{\label{fig:vel-1}Experiment 1: Scatter plot showing the correlation between dynamics feature (KV) and average participants' judgments as teaching for each recording.
-Therefore, each dot represents each stimulus.}\label{fig:plot-vel-1}
+Therefore, each dot represents each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-vel-1}
 \end{figure}
@@
 \caption{\label{fig:vel-diff-1}Experiment 1: Scatter plot showing the correlation between dynamics contrast feature (KV-Diff) and average participants' judgments as teaching for each recording.
-Therefore, each dot represents each stimulus.}\label{fig:plot-vel-diff-1}
+Therefore, each dot represents each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-vel-diff-1}
 \end{figure}
@@
 Only the 8th notes with expressive notations were included for data analysis.
-As a result, only one 8th note in the 4th measure without any expression was not included.
+As a result, only one 8th note in the 4th measure without any expression was not included (see \emph{Figure \ref{fig:stim2}}).
 
@@
 The curved line (slur) indicates legato and the dots indicate staccato.
+In multiple regression analysis, (1) corresponds to Legato model and (2) corresponds to Staccato model.
 (B)Dynamics.
 The symbol `f' denotes forte and the symbol `p' denotes piano.
-Only the 8th notes with expressive notations were used for data analysis.}\label{fig:stim-2}
+In multiple regression analysis, (3) corresponds to Forte model and (2) corresponds to Piano model.
+Only the 8th notes with expressive notations (i.e., (1), (2), (3), (4)) were used for data analysis.}\label{fig:stim-2}
 \end{figure}
@@
 A one sample \emph{t}-test was performed to compare the accuracy of participants' judgments against the chance level (50\%).
-The mean percentage of correct answers {[}\emph{M} = 52.8, \emph{SD} = 4.78{]} was significantly higher than chance (\emph{t}(19) = 2.66, \emph{p} = 0.02, cohen's \emph{d} = 0.60).
+The mean percentage of correct answers {[}\emph{M} = 52.8, \emph{SD} = 4.78{]} was significantly higher than chance (\emph{t}(19) = 2.66, \emph{p} = .02, cohen's \emph{d} = 0.60).
 
 We also performed a one sample \emph{t}-test for each technique separately.
-For articulation, the mean percentage of correct answers {[}\emph{M} = 52.4, \emph{SD} = 6.94{]} was not significantly different from chance (\emph{t}(19) = 1.52, \emph{p} = 0.14, cohen's \emph{d} = 0.34).
-Also for dynamics, the mean percentage of correct answers {[}\emph{M} = 53.3, \emph{SD} = 8.53{]} was not significantly different from chance (\emph{t}(19) = 1.75, \emph{p} = 0.10, cohen's \emph{d} = 0.39).
-A paired \emph{t}-test revealed that there was no significant difference between the two techniques in terms of the accuracy (\emph{t}(19) = -0.35, \emph{p} = 0.73, cohen's \emph{d} = -0.13).
+For articulation, the mean percentage of correct answers {[}\emph{M} = 52.4, \emph{SD} = 6.94{]} was not significantly different from chance (\emph{t}(19) = 1.52, \emph{p} = .14, cohen's \emph{d} = 0.34).
+Also for dynamics, the mean percentage of correct answers {[}\emph{M} = 53.3, \emph{SD} = 8.53{]} was not significantly different from chance (\emph{t}(19) = 1.75, \emph{p} = .10, cohen's \emph{d} = 0.39).
+A paired \emph{t}-test revealed that there was no significant difference between the two techniques in terms of the accuracy (\emph{t}(19) = -0.35, \emph{p} = .73, cohen's \emph{d} = -0.13).
 
-\hypertarget{correlation-1}{%
-\subsection{Correlation}\label{correlation-1}}
+\hypertarget{correlations-1}{%
+\subsection{Correlations}\label{correlations-1}}
 
@@
 
-Unlike Experiment 1, there was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; \emph{r(34)} = .25, \emph{p} = 0.15, Dynamics; \emph{r(34)} = .39, \emph{p} = 0.02, \emph{Figure \ref{fig:ioi-2}}).
+Unlike Experiment 1, there was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; \emph{r(34)} = .25, \emph{p} = .15, Dynamics; \emph{r(34)} = .39, \emph{p} = .02, \emph{Figure \ref{fig:ioi-2}}).
 Participants tended to identify slower performances as teaching for dynamics recordings.
@@
 
-Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; \emph{r(34)} = -.03, \emph{p} = 0.39, Staccato; \emph{r(34)} = -.15, \emph{p} = 0.39, \emph{Figure \ref{fig:kot-2}}, left).
+Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; \emph{r(34)} = -.03, \emph{p} = .88, Staccato; \emph{r(34)} = -.15, \emph{p} = .39, \emph{Figure \ref{fig:kot-2}}, left).
 
-For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (\emph{r(34)} = -.11, \emph{p} = 0.52).
-However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r(34)} = -.35, \emph{p} = 0.034), suggesting that performances with staccato-style piano were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).
+For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (\emph{r(34)} = -.11, \emph{p} = .52).
+However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r(34)} = -.35, \emph{p} = .034), suggesting that performances with staccato-style piano were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).
+However, this significance disappeared after removing one outlier outside of 2 standard deviations in terms of KOT values for piano.
 
@@
 As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-2}}, right).
-Specifically, performances with louder forte (\emph{r(34)} = .45, \emph{p} = 0.007) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.006) were more likely to be judged as teaching.
+Specifically, performances with louder forte (\emph{r(34)} = .45, \emph{p} = .007) and softer piano (\emph{r(34)} = -.45, \emph{p} = .006) were more likely to be judged as teaching.
 
-For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r(34)} = .08, \emph{p} = 0.63, Staccato; \emph{r(34)} = .21, \emph{p} = 0.22, \emph{Figure \ref{fig:vel-2}}, left).
+For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r(34)} = .08, \emph{p} = .63, Staccato; \emph{r(34)} = .21, \emph{p} = .22, \emph{Figure \ref{fig:vel-2}}, left).
 
@@
 As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (\emph{Figure \ref{fig:vel-diff-2}}, right).
-Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r(34)} = -.75, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r(34)} = .59, \emph{p} \textless{} 0.001).
+Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r(34)} = -.75, \emph{p} \textless{} .001, From Piano to Forte; \emph{r(34)} = .59, \emph{p} \textless{} .001).
 
-For articulation recordings, there was no significant relationship between KV difference between transition points from legato to staccato and participants' judgments as teaching (\emph{r(34)} = .23, \emph{p} = 0.176).
-However, there was a significant relationship between the transition points from staccato to legato and participants' judgments as teaching (\emph{r(34)} = .36, \emph{p} = 0.03), suggesting that performances with larger contrast from staccato to legato were more likely to be considered as teaching performance (\emph{Figure \ref{fig:vel-diff-2}}, left).
+For articulation recordings, there was no significant relationship between KV difference between transition points from legato to staccato and participants' judgments as teaching (\emph{r(34)} = .23, \emph{p} = .176).
+However, there was a significant relationship between the transition points from staccato to legato and participants' judgments as teaching (\emph{r(34)} = .36, \emph{p} = .03), suggesting that performances with larger contrast from staccato to legato were more likely to be considered as teaching performance (\emph{Figure \ref{fig:vel-diff-2}}, left).
 
@@
 As Experiment 1, we performed multiple regression analyses to further explore which feature of performance contributed the most to participants' judgments as teaching.
-Statistical model assumptions were tested and most of the assumptions (see \emph{Supplementary Material} for details) were met.
-Again, since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in \emph{Data analysis} in Experiment 1).
+Again, since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in \emph{Data analysis} in Experiment 1 and \emph{Figure \ref{fig:stim2}}).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
-The result of the regression indicated that the model explained 19.8 \% of the variance (\emph{F}(4, 31) = 3.16, \emph{p} = 0.028).
-It was found that tempo (IOIs; \emph{\(\beta\)} = 0.58, \emph{p} = 0.011), dynamics (KV; \emph{\(\beta\)} = 1.10, \emph{p} = 0.018) and dynamics contrast (KV-Diff; \emph{\(\beta\)} = 1.90, \emph{p} = 0.006) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
-However, articulation (KOT; \emph{\(\beta\)} = -0.08, \emph{p} = 0.47) for the legato parts was not a significant predictor as opposed to Experiment 1.
+The result of the regression indicated that the model explained 19.8 \% of the variance (\emph{F}(4, 31) = 3.16, \emph{p} = .028).
+It was found that tempo (IOIs; \emph{\(\beta\)} = 0.58, \emph{p} = .011), dynamics (KV; \emph{\(\beta\)} = 1.10, \emph{p} = .018) and dynamics contrast (KV-Diff; \emph{\(\beta\)} = 1.90, \emph{p} = .006) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
+However, articulation (KOT; \emph{\(\beta\)} = -0.08, \emph{p} = .47) for the legato parts was not a significant predictor as opposed to Experiment 1.
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato).
-The overall model was not statistically significant (\(R^{2}\) = 12.3, \emph{F}(4, 31) = 2.22, \emph{p} = 0.09).
+The overall model was not statistically significant (\(R^{2}\) = 12.3, \emph{F}(4, 31) = 2.22, \emph{p} = .09).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano).
-The result of the regression indicated that the model explained 60.7 \% of the variance (\emph{F}(4, 31) = 14.5, \emph{p} \textless{} 0.001).
-It was found that dynamics contrast from forte to piano (KV-Diff; \emph{\(\beta\)} = -1.64, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.
+The result of the regression indicated that the model explained 60.7 \% of the variance (\emph{F}(4, 31) = 14.5, \emph{p} \textless{} .001).
+It was found that dynamics contrast from forte to piano (KV-Diff; \emph{\(\beta\)} = -1.64, \emph{p} \textless{} .001) were significant predictors of participants' judgments as teaching.
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte).
-The result of the regression indicated that the model explained 49.5 \% of the variance (\emph{F}(4, 31) = 9.57, \emph{p} \textless{} 0.001).
-It was found that tempo (IOIs; \emph{\(\beta\)} = 0.55, \emph{p} = 0.022) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 1.09, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.
+The result of the regression indicated that the model explained 49.5 \% of the variance (\emph{F}(4, 31) = 9.57, \emph{p} \textless{} .001).
+It was found that tempo (IOIs; \emph{\(\beta\)} = 0.55, \emph{p} = .022) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 1.09, \emph{p} \textless{} .001) were significant predictors of participants' judgments as teaching.
 
@@
 \caption{\label{fig:ioi-2}Experiment 2: Scatter plot showing the correlation between tempo featurea (IOIs) and average participants' judgments as teaching for each recording.
-Therefore, each dot represents each stimulus.}\label{fig:plot-ioi-2}
+Therefore, each dot represents each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-ioi-2}
 \end{figure}
@@
 \caption{\label{fig:kot-2}Experiment 2: Scatter plot showing the correlation between articulation features (KOT) and average participants' judgments as teaching for each recording.
-Therefore, each dot represents each stimulus.}\label{fig:plot-kot-2}
+Therefore, each dot represents each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-kot-2}
 \end{figure}
@@
 \caption{\label{fig:vel-2}Experiment 2: Scatter plot showing the correlation between dynamics features (KV) and average participants' judgments as teaching for each recording.
-Therefore, each dot represents each stimulus.}\label{fig:plot-vel-2}
+Therefore, each dot represents each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-vel-2}
 \end{figure}
@@
 
-\caption{\label{fig:vel-diff-2}Experiment 2: Scatter plot showing the correlation between dynamics contrast features (KV-Diff) and average participants' judgment as teaching for each stimulus.}\label{fig:plot-vel-diff-2}
+\caption{\label{fig:vel-diff-2}Experiment 2: Scatter plot showing the correlation between dynamics contrast features (KV-Diff) and average participants' judgment as teaching for each stimulus.
+Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-vel-diff-2}
 \end{figure}
@@
 
-The aim of Experiment 2 was to replicate the results of Experiment 1 with a more naturalistic piece of music.
+The aim of Experiment 2 was to replicate the results of Experiment 1 and examine how musicians would infer teaching intentions when listening to a more naturalistic piece of music.
 However, unlike Experiment 1, tempo (IOIs) does not seem to contribute to participants' judgments as teaching.
@@
 
-The present study investigated whether and how musician infer pedagogical intentions by listening to piano recordings.
+The present study investigated whether and how musicians infer pedagogical intentions by listening to piano recordings.
 In both Experiment 1 and 2, participants were able to choose correct answers accurately more than chance (50\%).
 However, the results showed that the accuracy was relatively low (52.7 \% in Experiment 1; 52.8 \% in Experiment 2).
-This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al.~(\emph{submitted}) and all the selected recordings did not exhibit the characteristics of teaching performance (e.g., slow performance, exaggeration).
+This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al.~(\emph{submitted}) and all the selected recordings did not exhibit the characteristics of teaching performance (e.g., slower demonstration, exaggeration).
 The reason why we randomly selected the stimuli from each condition (i.e., teaching or performing) was because all the characteristics of teaching performance (e.g., IOIs, KOT, KV) were intercorrelated and it was difficult to choose stimuli based on one single criterion.
 Future research should examine if musicians answer more accurately with more experimentally controlled stimuli.
+Another possibility for the low accuracy could be that it was difficult even for musicians to find which cues were produced for teaching when listening to one piece of music with several phrases.
+Future research should examine whether accuracy would be improved when listening to phrases compared to pieces.
 
@@
 
+\hypertarget{supplementary-materials}{%
+\section{Supplementary Materials}\label{supplementary-materials}}
+
+All data is available at \url{https://osf.io/f6nr2/}.
+
+\hypertarget{acknowledgement}{%
+\section{Acknowledgement}\label{acknowledgement}}
+
+This research was supported by the European Research Council under the European Union's Seventh Framework Program (FP7/2007--2013)/ERC Grant agreement no.
+609819, SOMICS.
+We thank Fanni Takátsy for her help with data collection.
+
+\clearpage
+\renewcommand{\listfigurename}{Figure captions}
+
 \end{document}

### 2022-04-26 paper/manuscript.Rmd
update figures / manuscript except for general discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 The accuracy of musicians' judgments was significantly above chance.
-However, we only replicated that performances with exaggerated dynamics were more likely to be judged as teaching.
-Taken together, loudness seems to be reliably used to infer teaching intentions regardless of the complexity of a musical piece.
-Also, typical pedagogical behaviour such as slowing down may not be necessarily perceived as teaching performance when learning complex skills such as artistic expression.
+In contrast to Experiment 1, only exaggerated dynamics were more likely to be judged as teaching.
+Taken together, the results indicate that recognition of some teaching intentions may be facilitated by low musical complexity.
 
-keywords          : "perception, expression, learning, expertise, music education"
+keywords          : "perception, expression, pedagogy, expertise, music education"
 
@@
 Not only are we able to learn by observing and imitating others, but also we benefit greatly from interacting with others such as teachers and peers [@tomasello_1993].
-Adults are often being pedagogical to children in order to explain and transmit cultural conventions [@csibra_2009].
+Adults are often being pedagogical to children to explain and transmit cultural conventions [@csibra_2009].
 Active teaching seems to play a crucial role not only to transit skills over generations but also to further develop sophisticated cultures, which cannot be achieved by one single individual or generation [@tennie_2009].
@@
 In pedagogical settings where teachers are supposed to convey useful information to learners, it has been found that teachers often modulate their behaviour for teaching purposes.
-For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills [e.g., @brand_2002; @saint-georges_2013].
+For example, adults are likely to modulate their speech and action for infants to help them acquire skills [e.g., @brand_2002; @saint-georges_2013].
 Further studies have revealed that even towards adult learners, people modulate their speech and action in a similar way as they did for infants [@mcellin_2017; @uther_2007].
@@
 Tominaga, Knoblich & Sebanz (*submitted*) extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression.
-We investigated whether and how expert pianists are able to communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
-The results demonstrated that expert pianists systematically modulated their performance by playing slower or by exaggerating relevant aspects of the performance (e.g., producing shorter staccato or producing a larger contrast between forte and piano) when intending to teach the musical expressive techniques.
-Therefore, it seems that even in the domain of expertise, experts exhibit pedagogical behaviours to highlight crucial performance aspects for potential learners.
+We investigated whether and how expert pianists communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
+The results demonstrated that expert pianists systematically modulated their performance by playing slower or by exaggerating relevant aspects of the performance (e.g., producing shorter staccato or producing a larger contrast between forte and piano) when intending to teach musical expressive techniques.
+Therefore, it seems that experts exhibit pedagogical behaviours to highlight crucial performance aspects for potential learners.
 
@@
 They were asked to judge whether each recording was produced for teaching purposes or not.
-Half of the recordings was produced when pianists were instructed to play as if they were teaching the designated musical technique in a lesson (i.e., teaching recordings) whereas the other half was produced when pianists were instructed to play as if they were performing it in a concert (i.e., performing recordings).
+Half of the recordings was produced when pianists were instructed to play as if they were teaching the designated musical technique in a lesson (i.e., teaching recordings).
+The other half was produced when pianists were instructed to play as if they were performing it in a concert (i.e., performing recordings).
 First, we calculated the accuracy of participants’ judgments to examine whether they could distinguish teaching recordings from performing recordings.
@@
 In Experiment 1 learners listened to performances that followed simple musical scales.
-In Experiment 2 learners listened to performances of a more naturalistic piece of music in an attempt to replicate the findings from Experiment 1.
+In Experiment 2 learners listened to performances of a more complex piece.
 
@@
 Each recording was evaluated only once in the experiment.
-All participants completed both blocks and the order of the blocks was counterbalanced across the participants.
+All participants completed both blocks.
+The order of the blocks was counterbalanced across participants.
 The order of the recordings was randomised within each block.
 
-At the end of the experiment, participants filled in a questionnaire about their demographic information and experience in musical instruments.
+At the end of the experiment, participants filled in a questionnaire about their demographic information and thier prior experience with playing musical instruments.
 
@@
 We compared how accurate participants were against the chance level (50%).
-The correct responses were either pressing the yes button when listening to the teaching recordings or pressing the no button when listening to the performing recordings.
-The incorrect responses were either pressing the yes button when listening to the performing recordings or pressing the no button when listening to the teaching recordings.
+Correct responses were either pressing the yes button when listening to teaching recordings or pressing the no button when listening to performing recordings.
+Incorrect responses were either pressing the yes button when listening to performing recordings or pressing the no button when listening to teaching recordings.
 
@@
 Key-overlap time is the time overlap between two adjacent notes, namely the difference between the offset time of the current note and the onset time of the ensuing note [e.g., @bresin_2000].
-Positive KOT values indicate legato styles whereas negative KOT values indicate staccato styles.
+Positive KOT values indicate a legato style whereas negative KOT values indicate a staccato style.
 Key velocity is obtained from MIDI data to describe how fast a performer hit the key.
-Larger KV values indicate forte styles while smaller KV values indicate piano styles.
+Larger KV values indicate a forte style while smaller KV values indicate a piano style.
 Additionally, we also measured dynamics contrast where one subcomponent of the technique moves to the other (e.g., from forte to piano, from staccato to legato) to illustrate how much dynamics contrast a performer made at transition points.
 
-To investigate relationships between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as teaching (i.e., what percentage of participants responded as "yes"), we first performed separate correlation analyses for each performance feature.
-Second, we run multiple regression that included all four performance features to examine which predictor significantly contributed to participants' judgments as teaching.
+To investigate the relationships between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as teaching (i.e., what percentage of participants responded as "yes"), we first performed separate correlation analyses for each performance feature.
+Second, we run multiple regression that included all four performance features to examine the strongest predictor of participants' judgments as teaching.
 Since articulation and dynamics were comprised of two opposite directional values (i.e., legato vs.
@@
 ## Accuracy
-A one sample *t*-test was performed to compare the accuracy of participants' judgments against the chance level (50%).
+A one sample *t*-test was performed to compare the accuracy of participants' judgments against chance level (50%).
 The mean percentage of correct answers [*M* = `r sprintf('%.1f', subset$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset$SD_Percent)`] was significantly higher than chance (*t*(`r ttest_all$parameter`) = `r sprintf('%.2f', ttest_all$statistic)`, *p* `r if(ttest_all$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', ttest_all$p.value)))}`, cohen's *d* = `r sprintf('%.2f', coheneff_all$effsize)`).
@@
 Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_ioi_art$p.value)))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_ioi_dyn$p.value)))}`, *Figure \ref{fig:ioi-1}*).
-Participants tended to identify slower performances as teaching.
+Participants identified slower performances as teaching.
 
 ```{r ioi-1, include = FALSE}
-cor_ioi_1 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", shape = "Skill", add = "reg.line", palette = "d3", add.params = list(fill = "lightgray"), conf.int = TRUE, xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + labs(color = "Technique", shape = "Technique") + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
+cor_ioi_1 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line", palette = "d3", add.params = list(fill = "lightgray"), conf.int = TRUE, xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + labs(color = "Technique", shape = "Technique") + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
@@
 kot_all$Subcomponent <- factor(kot_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
-cor_kot_1 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
+cor_kot_1 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-250, 200, 100)) + coord_cartesian(xlim = c(-250, 200), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-250, 200, 100)) + coord_cartesian(xlim = c(-250, 200), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
@@
 vel_all$Subcomponent <- factor(vel_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
-cor_vel_1 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
+cor_vel_1 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
@@
 vel_diff_all$Subcomponent <- factor(vel_diff_all$Subcomponent, levels = c("LtoS", "StoL", "FtoP", "PtoF"))
-cor_vel_diff_1 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
+cor_vel_diff_1 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-35, 55, 20)) + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
+          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-35, 55, 20)) + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
@@
 ## Multiple regression
-In order to further explore which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted.
+In order to further investigate which feature of performance contributed most to participants' judgments as teaching, multiple regression analyses were conducted.
 Statistical model assumptions were tested using the *performance* R package [@ludecke_2021].
@@
 Therefore, each dot represents each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
+The gray bands display the 95 percent confidence intervals."}
 img_cor_ioi_1
@@
 Therefore, each dot represents each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
+The gray bands display the 95 percent confidence intervals."}
 img_cor_kot_1
@@
 Therefore, each dot represents each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
+The gray bands display the 95 percent confidence intervals."}
 img_cor_vel_1
@@
 Therefore, each dot represents each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
+The gray bands display the 95 percent confidence intervals."}
 img_cor_vel_diff_1
@@
 
-Experiment 1 investigated whether musicians could distinguish teaching recordings from performing recordings accurately and which features of piano performance made them infer teaching intentions.
+Experiment 1 investigated whether musicians could distinguish teaching recordings from performing recordings and which features of piano performance made them infer teaching intentions.
 The results demonstrated that musicians could choose correct answers above chance.
 Also, it was found that the accuracy of participants' judgments was better for dynamics recordings than for articulation recordings.
-When it comes to how performance features contributed to participants' judments, performances with slower tempo were more likely to be judged as teaching by musicians regardless of which expressive technique was implemented in the piece.
+
+Performances with slower tempo were more likely to be judged as teaching by musicians regardless of which expressive technique was implemented in the piece.
 For articulation recordings, performances with longer legato and shorter staccato were tended to be judged as teaching.
-For dynamics recordings, performances with louder forte were more likely to be judged as teaching whereas there was no relationship between softer sound (i.e., piano) and participants' judgments as teaching.
+For dynamics recordings, louder performances were more likely to be judged as teaching whereas there was no relationship between softer sound and participants' judgments as teaching.
 Importantly, performances with larger contrast between forte and piano for both directions (i.e., from forte to piano, from piano to forte) were more likely to be judged as teaching.
@@
 
-The aim of Experiment 2 was to replicate the findings in Experiment 1 with a more naturalistic piece of music.
+The aim of Experiment 2 was to replicate the findings in Experiment 1 with a more complex piece of music.
 Given the findings in Experiment 1, we predicted that slower performance would be likely to be judged as teaching regardless of which expressive technique (i.e., articulation or dynamics) was implemented.
@@
 ### Tempo (IOIs)
-Unlike Experiment 1, there was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$p.value)))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$p.value)))}`, *Figure \ref{fig:ioi-2}*).
+There was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$p.value)))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$p.value)))}`, *Figure \ref{fig:ioi-2}*).
 Participants tended to identify slower performances as teaching for dynamics recordings.
@@
 ```{r ioi-2, include = FALSE}
-cor_ioi_2 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", shape = "Skill", add = "reg.line", palette = "d3",
+cor_ioi_2 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line", palette = "d3",
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + labs(color = "Technique", shape = "Technique") + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
+          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + labs(color = "Technique", shape = "Technique") + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
@@
 ### Articulation (KOT)
-Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; *r(`r cor_kot_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$p.value)))}`, Staccato; *r(`r cor_kot_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$p.value)))}`, *Figure \ref{fig:kot-2}*, left).
+For articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; *r(`r cor_kot_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$p.value)))}`, Staccato; *r(`r cor_kot_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$p.value)))}`, *Figure \ref{fig:kot-2}*, left).
 
@@
 kot_all$Subcomponent <- factor(kot_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
-cor_kot_2 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
+cor_kot_2 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE,
-          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-300, 150, 100)) + coord_cartesian(xlim = c(-300, 150), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
+          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-300, 150, 100)) + coord_cartesian(xlim = c(-300, 150), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
@@
 ### Dynamics (KV)
-As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-2}*, right).
+For dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-2}*, right).
 Specifically, performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_for$p.value)))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_pia$p.value)))}`) were more likely to be judged as teaching.
@@
 vel_all$Subcomponent <- factor(vel_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
-cor_vel_2 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
+cor_vel_2 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
+          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
@@
 ### Dynamics contrast (KV-Diff)
-As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (*Figure \ref{fig:vel-diff-2}*, right).
+For dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (*Figure \ref{fig:vel-diff-2}*, right).
 Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_diff_ftop$p.value)))}`, From Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_diff_ptof$p.value)))}`).
@@
 vel_diff_all$Subcomponent <- factor(vel_diff_all$Subcomponent, levels = c("LtoS", "StoL", "FtoP", "PtoF"))
-cor_vel_diff_2 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
+cor_vel_diff_2 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
           add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
-          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()
+          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
 
@@
 ## Multiple regression
-As Experiment 1, we performed multiple regression analyses to further explore which feature of performance contributed the most to participants' judgments as teaching.
+As Experiment 1, we performed multiple regression analyses to further investigate which feature of performance contributed the most to participants' judgments as teaching.
 Again, since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.
@@
 It was found that tempo (IOIs; *$\beta$* = `r summary(m1)$coefficients[2]`, *p* `r if(summary(m1)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m1)$coefficients[2, 4])))}`), dynamics (KV; *$\beta$* = `r summary(m1)$coefficients[4]`, *p* `r if(summary(m1)$coefficients[4, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m1)$coefficients[4, 4])))}`) and dynamics contrast (KV-Diff; *$\beta$* = `r summary(m1)$coefficients[5]`, *p* `r if(summary(m1)$coefficients[5, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m1)$coefficients[5, 4])))}`) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
-However, articulation (KOT; *$\beta$* = `r summary(m1)$coefficients[3]`, *p* `r if(summary(m1)$coefficients[3, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', summary(m1)$coefficients[3, 4])))}`) for the legato parts was not a significant predictor as opposed to Experiment 1.
+However, articulation (KOT; *$\beta$* = `r summary(m1)$coefficients[3]`, *p* `r if(summary(m1)$coefficients[3, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', summary(m1)$coefficients[3, 4])))}`) for the legato parts was not a significant predictor.
 
@@
 The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m3)$adj.r.squared*100)` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r sprintf('%.1f', summary(m3)$fstatistic[1])`, *p* `r if(lmp(m3) < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', lmp(m3))))}`).
-It was found that dynamics contrast from forte to piano (KV-Diff; *$\beta$* = `r summary(m3)$coefficients[5]`, *p* `r if(summary(m3)$coefficients[5, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m3)$coefficients[5, 4])))}`) were significant predictors of participants' judgments as teaching.
+It was found that the dynamics contrast from forte to piano (KV-Diff; *$\beta$* = `r summary(m3)$coefficients[5]`, *p* `r if(summary(m3)$coefficients[5, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m3)$coefficients[5, 4])))}`) was the only significant predictor of participants' judgments as teaching.
 
@@
 Therefore, each dot represents each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
+The gray bands display the 95 percent confidence intervals."}
 img_cor_ioi_2
@@
 Therefore, each dot represents each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
+The gray bands display the 95 percent confidence intervals."}
 img_cor_kot_2
@@
 Therefore, each dot represents each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
+The gray bands display the 95 percent confidence intervals."}
 img_cor_vel_2
@@
 ```{r plot-vel-diff-2, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-diff-2}Experiment 2: Scatter plot showing the correlation between dynamics contrast features (KV-Diff) and average participants' judgment as teaching for each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
+The gray bands display the 95 percent confidence intervals."}
 img_cor_vel_diff_2
@@
 # Discussion
-The aim of Experiment 2 was to replicate the results of Experiment 1 and examine how musicians would infer teaching intentions when listening to a more naturalistic piece of music.
-However, unlike Experiment 1, tempo (IOIs) does not seem to contribute to participants' judgments as teaching.
-This could be that in a musically complex piece, tempo might have been considered to be one of the interpretations of music and was not used as a reliable cue to infer teaching intentions.
-Also, articulation (KOT) does not seem to contribute to participants' judgments as teaching.
-As Experiment 1, dynamics (KV) seems to be used as a reliable cue to detect the characteristic of teaching performance.
-We could successfully replicate that performances with larger contrast between forte and piano seem to be considered as teaching.
-Moreover, performances with both exaggerated forte and piano were considered to be for teaching whereas performances with only exaggerated forte were judged as teaching in Experiment 1.
-These consistent results suggest that loudness (dynamics) might be used as a reliable cue to infer teaching intentions regardless of the complexity of a musical piece.
-
-Multiple regression analyses also implied that tempo feature was not a strong predictor of participants' judgments as teaching when listening to a musically complex piece.
-As Experiment 1, dynamics contrast seems to be a strong predictor of participants' judgments as teaching, especially for dynamics recordings.
-This finding also suggests that loudness might be a strong cue to infer pedagogical intentions even in a naturalistic piece of music.
+The aim of Experiment 2 was to replicate the results of Experiment 1 and examine how musicians would infer teaching intentions when listening to a more complex piece of music.
+We found that tempo (IOIs) and articulation (KOT) did not seem to contribute to participants' judgments as teaching.
+It seems that variations in these two parameters were considered to be in the space of possible interpretations of the music and were not used as general cues to infer teaching intentions.
 

### 2022-04-26 paper/manuscript.tex
update figures / manuscript except for general discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 {}{\PatchFailed}
-\keywords{perception, expression, learning, expertise, music education}
+\keywords{perception, expression, pedagogy, expertise, music education}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
   pdflang={en-EN},
-  pdfkeywords={perception, expression, learning, expertise, music education},
+  pdfkeywords={perception, expression, pedagogy, expertise, music education},
   hidelinks,
@@
 The accuracy of musicians' judgments was significantly above chance.
-However, we only replicated that performances with exaggerated dynamics were more likely to be judged as teaching.
-Taken together, loudness seems to be reliably used to infer teaching intentions regardless of the complexity of a musical piece.
-Also, typical pedagogical behaviour such as slowing down may not be necessarily perceived as teaching performance when learning complex skills such as artistic expression.
+In contrast to Experiment 1, only exaggerated dynamics were more likely to be judged as teaching.
+Taken together, the results indicate that recognition of some teaching intentions may be facilitated by low musical complexity.
 }
@@
 Not only are we able to learn by observing and imitating others, but also we benefit greatly from interacting with others such as teachers and peers (Tomasello, Kruger, \& Ratner, 1993).
-Adults are often being pedagogical to children in order to explain and transmit cultural conventions (Csibra \& Gergely, 2009).
+Adults are often being pedagogical to children to explain and transmit cultural conventions (Csibra \& Gergely, 2009).
 Active teaching seems to play a crucial role not only to transit skills over generations but also to further develop sophisticated cultures, which cannot be achieved by one single individual or generation (Tennie, Call, \& Tomasello, 2009).
@@
 In pedagogical settings where teachers are supposed to convey useful information to learners, it has been found that teachers often modulate their behaviour for teaching purposes.
-For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills (e.g., Brand, Baldwin, \& Ashburn, 2002; Saint-Georges et al., 2013).
+For example, adults are likely to modulate their speech and action for infants to help them acquire skills (e.g., Brand, Baldwin, \& Ashburn, 2002; Saint-Georges et al., 2013).
 Further studies have revealed that even towards adult learners, people modulate their speech and action in a similar way as they did for infants (McEllin, Knoblich, \& Sebanz, 2017; Uther, Knoll, \& Burnham, 2007).
@@
 Tominaga, Knoblich \& Sebanz (\emph{submitted}) extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression.
-We investigated whether and how expert pianists are able to communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
-The results demonstrated that expert pianists systematically modulated their performance by playing slower or by exaggerating relevant aspects of the performance (e.g., producing shorter staccato or producing a larger contrast between forte and piano) when intending to teach the musical expressive techniques.
-Therefore, it seems that even in the domain of expertise, experts exhibit pedagogical behaviours to highlight crucial performance aspects for potential learners.
+We investigated whether and how expert pianists communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
+The results demonstrated that expert pianists systematically modulated their performance by playing slower or by exaggerating relevant aspects of the performance (e.g., producing shorter staccato or producing a larger contrast between forte and piano) when intending to teach musical expressive techniques.
+Therefore, it seems that experts exhibit pedagogical behaviours to highlight crucial performance aspects for potential learners.
 
@@
 They were asked to judge whether each recording was produced for teaching purposes or not.
-Half of the recordings was produced when pianists were instructed to play as if they were teaching the designated musical technique in a lesson (i.e., teaching recordings) whereas the other half was produced when pianists were instructed to play as if they were performing it in a concert (i.e., performing recordings).
+Half of the recordings was produced when pianists were instructed to play as if they were teaching the designated musical technique in a lesson (i.e., teaching recordings).
+The other half was produced when pianists were instructed to play as if they were performing it in a concert (i.e., performing recordings).
 First, we calculated the accuracy of participants' judgments to examine whether they could distinguish teaching recordings from performing recordings.
@@
 We compared how accurate participants were against the chance level (50\%).
-The correct responses were either pressing the yes button when listening to the teaching recordings or pressing the no button when listening to the performing recordings.
-The incorrect responses were either pressing the yes button when listening to the performing recordings or pressing the no button when listening to the teaching recordings.
+Correct responses were either pressing the yes button when listening to teaching recordings or pressing the no button when listening to performing recordings.
+Incorrect responses were either pressing the yes button when listening to performing recordings or pressing the no button when listening to teaching recordings.
 
@@
 Key-overlap time is the time overlap between two adjacent notes, namely the difference between the offset time of the current note and the onset time of the ensuing note (e.g., Bresin \& Battel, 2000).
-Positive KOT values indicate legato styles whereas negative KOT values indicate staccato styles.
+Positive KOT values indicate a legato style whereas negative KOT values indicate a staccato style.
 Key velocity is obtained from MIDI data to describe how fast a performer hit the key.
-Larger KV values indicate forte styles while smaller KV values indicate piano styles.
+Larger KV values indicate a forte style while smaller KV values indicate a piano style.
 Additionally, we also measured dynamics contrast where one subcomponent of the technique moves to the other (e.g., from forte to piano, from staccato to legato) to illustrate how much dynamics contrast a performer made at transition points.
 
-To investigate relationships between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as teaching (i.e., what percentage of participants responded as ``yes''), we first performed separate correlation analyses for each performance feature.
-Second, we run multiple regression that included all four performance features to examine which predictor significantly contributed to participants' judgments as teaching.
+To investigate the relationships between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as teaching (i.e., what percentage of participants responded as ``yes''), we first performed separate correlation analyses for each performance feature.
+Second, we run multiple regression that included all four performance features to examine the strongest predictor of participants' judgments as teaching.
 Since articulation and dynamics were comprised of two opposite directional values (i.e., legato vs.~staccato, forte vs.~piano), we created four separate models that included different parts of the piece.
@@
 
-A one sample \emph{t}-test was performed to compare the accuracy of participants' judgments against the chance level (50\%).
+A one sample \emph{t}-test was performed to compare the accuracy of participants' judgments against chance level (50\%).
 The mean percentage of correct answers {[}\emph{M} = 52.7, \emph{SD} = 4.90{]} was significantly higher than chance (\emph{t}(19) = 2.47, \emph{p} = .02, cohen's \emph{d} = 0.55).
@@
 Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; \emph{r(46)} = .77, \emph{p} \textless{} .001, Dynamics; \emph{r(46)} = .42, \emph{p} = .003, \emph{Figure \ref{fig:ioi-1}}).
-Participants tended to identify slower performances as teaching.
+Participants identified slower performances as teaching.
 
@@
 
-In order to further explore which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted.
+In order to further investigate which feature of performance contributed most to participants' judgments as teaching, multiple regression analyses were conducted.
 Statistical model assumptions were tested using the \emph{performance} R package (Lüdecke, Ben-Shachar, Patil, Waggoner, \& Makowski, 2021).
@@
 Therefore, each dot represents each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-ioi-1}
+The gray bands display the 95 percent confidence intervals.}\label{fig:plot-ioi-1}
 \end{figure}
@@
 Therefore, each dot represents each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-kot-1}
+The gray bands display the 95 percent confidence intervals.}\label{fig:plot-kot-1}
 \end{figure}
@@
 Therefore, each dot represents each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-vel-1}
+The gray bands display the 95 percent confidence intervals.}\label{fig:plot-vel-1}
 \end{figure}
@@
 Therefore, each dot represents each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-vel-diff-1}
+The gray bands display the 95 percent confidence intervals.}\label{fig:plot-vel-diff-1}
 \end{figure}
@@
 
-A one sample \emph{t}-test was performed to compare the accuracy of participants' judgments against the chance level (50\%).
+A one sample \emph{t}-test was performed to compare the accuracy of participants' judgments against chance level (50\%).
 The mean percentage of correct answers {[}\emph{M} = 52.8, \emph{SD} = 4.78{]} was significantly higher than chance (\emph{t}(19) = 2.66, \emph{p} = .02, cohen's \emph{d} = 0.60).
@@
 
-Unlike Experiment 1, there was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; \emph{r(34)} = .25, \emph{p} = .15, Dynamics; \emph{r(34)} = .39, \emph{p} = .02, \emph{Figure \ref{fig:ioi-2}}).
+There was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; \emph{r(34)} = .25, \emph{p} = .15, Dynamics; \emph{r(34)} = .39, \emph{p} = .02, \emph{Figure \ref{fig:ioi-2}}).
 Participants tended to identify slower performances as teaching for dynamics recordings.
@@
 
-Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; \emph{r(34)} = -.03, \emph{p} = .88, Staccato; \emph{r(34)} = -.15, \emph{p} = .39, \emph{Figure \ref{fig:kot-2}}, left).
+For articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; \emph{r(34)} = -.03, \emph{p} = .88, Staccato; \emph{r(34)} = -.15, \emph{p} = .39, \emph{Figure \ref{fig:kot-2}}, left).
 
@@
 
-As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-2}}, right).
+For dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-2}}, right).
 Specifically, performances with louder forte (\emph{r(34)} = .45, \emph{p} = .007) and softer piano (\emph{r(34)} = -.45, \emph{p} = .006) were more likely to be judged as teaching.
@@
 
-As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (\emph{Figure \ref{fig:vel-diff-2}}, right).
+For dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (\emph{Figure \ref{fig:vel-diff-2}}, right).
 Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r(34)} = -.75, \emph{p} \textless{} .001, From Piano to Forte; \emph{r(34)} = .59, \emph{p} \textless{} .001).
@@
 
-As Experiment 1, we performed multiple regression analyses to further explore which feature of performance contributed the most to participants' judgments as teaching.
+As Experiment 1, we performed multiple regression analyses to further investigate which feature of performance contributed the most to participants' judgments as teaching.
 Again, since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in \emph{Data analysis} in Experiment 1 and \emph{Figure \ref{fig:stim2}}).
@@
 It was found that tempo (IOIs; \emph{\(\beta\)} = 0.58, \emph{p} = .011), dynamics (KV; \emph{\(\beta\)} = 1.10, \emph{p} = .018) and dynamics contrast (KV-Diff; \emph{\(\beta\)} = 1.90, \emph{p} = .006) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
-However, articulation (KOT; \emph{\(\beta\)} = -0.08, \emph{p} = .47) for the legato parts was not a significant predictor as opposed to Experiment 1.
+However, articulation (KOT; \emph{\(\beta\)} = -0.08, \emph{p} = .47) for the legato parts was not a significant predictor.
 
@@
 The result of the regression indicated that the model explained 60.7 \% of the variance (\emph{F}(4, 31) = 14.5, \emph{p} \textless{} .001).
-It was found that dynamics contrast from forte to piano (KV-Diff; \emph{\(\beta\)} = -1.64, \emph{p} \textless{} .001) were significant predictors of participants' judgments as teaching.
+It was found that the dynamics contrast from forte to piano (KV-Diff; \emph{\(\beta\)} = -1.64, \emph{p} \textless{} .001) was the only significant predictor of participants' judgments as teaching.
 
@@
 Therefore, each dot represents each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-ioi-2}
+The gray bands display the 95 percent confidence intervals.}\label{fig:plot-ioi-2}
 \end{figure}
@@
 Therefore, each dot represents each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-kot-2}
+The gray bands display the 95 percent confidence intervals.}\label{fig:plot-kot-2}
 \end{figure}
@@
 Therefore, each dot represents each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-vel-2}
+The gray bands display the 95 percent confidence intervals.}\label{fig:plot-vel-2}
 \end{figure}
@@
 \caption{\label{fig:vel-diff-2}Experiment 2: Scatter plot showing the correlation between dynamics contrast features (KV-Diff) and average participants' judgment as teaching for each stimulus.
-Each line indicates a regression line and the gray bands display the 95 percent confidence intervals.}\label{fig:plot-vel-diff-2}
+The gray bands display the 95 percent confidence intervals.}\label{fig:plot-vel-diff-2}
 \end{figure}
@@
 
-The aim of Experiment 2 was to replicate the results of Experiment 1 and examine how musicians would infer teaching intentions when listening to a more naturalistic piece of music.
-However, unlike Experiment 1, tempo (IOIs) does not seem to contribute to participants' judgments as teaching.
-This could be that in a musically complex piece, tempo might have been considered to be one of the interpretations of music and was not used as a reliable cue to infer teaching intentions.
-Also, articulation (KOT) does not seem to contribute to participants' judgments as teaching.
-As Experiment 1, dynamics (KV) seems to be used as a reliable cue to detect the characteristic of teaching performance.
-We could successfully replicate that performances with larger contrast between forte and piano seem to be considered as teaching.
-Moreover, performances with both exaggerated forte and piano were considered to be for teaching whereas performances with only exaggerated forte were judged as teaching in Experiment 1.
-These consistent results suggest that loudness (dynamics) might be used as a reliable cue to infer teaching intentions regardless of the complexity of a musical piece.
-
-Multiple regression analyses also implied that tempo feature was not a strong predictor of participants' judgments as teaching when listening to a musically complex piece.
-As Experiment 1, dynamics contrast seems to be a strong predictor of participants' judgments as teaching, especially for dynamics recordings.
-This finding also suggests that loudness might be a strong cue to infer pedagogical intentions even in a naturalistic piece of music.
+The aim of Experiment 2 was to replicate the results of Experiment 1 and examine how musicians would infer teaching intentions when listening to a more complex piece of music.
+We found that tempo (IOIs) and articulation (KOT) did not seem to contribute to participants' judgments as teaching.
+It seems that variations in these two parameters were considered to be in the space of possible interpretations of the music and were not used as general cues to infer teaching intentions.
 

### 2022-04-28 paper/manuscript.Rmd
first submission
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
   - name          : "Atsuko Tominaga"
-    affiliation   : "1,*"
-    # corresponding : yes    # Define only one corresponding author
-    # address       : "Quellenstraße 51, 1100 Vienna, Austria"
-    # email         : "Tominaga_Atsuko@phd.ceu.edu"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Quellenstraße 51, 1100 Vienna, Austria"
+    email         : "Tominaga_Atsuko@phd.ceu.edu"
 
@@
     institution   : "Department of Cognitive Science, Central European University, Quellenstraße 51, 1100 Vienna, Austria"
-  - id            : "*"
-    institution   : "Corresponding author: Tominaga_Atsuko@phd.ceu.edu"
 
@@
 Moreover, performances with exaggeration for each technique were more likely to be judged as teaching.
-Experiment 2 aimed to replicate the findings of Experiment 1 with a more naturalistic piece.
+Experiment 2 aimed to replicate the findings of Experiment 1 with a more complex piece of music.
 The accuracy of musicians' judgments was significantly above chance.
@@
 
-keywords          : "perception, expression, pedagogy, expertise, music education"
+keywords          : "perception, expression, expertise, music education, pedagogy"
 
@@
 
-floatsintext      : no
+floatsintext      : yes
 figurelist        : yes
@@
 We investigated whether and how expert pianists communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
-The results demonstrated that expert pianists systematically modulated their performance by playing slower or by exaggerating relevant aspects of the performance (e.g., producing shorter staccato or producing a larger contrast between forte and piano) when intending to teach musical expressive techniques.
+The results demonstrated that expert pianists systematically modulated their performance by playing slower or by exaggerating relevant aspects of the performance (e.g., producing shorter staccato or producing larger contrast between forte and piano) when intending to teach musical expressive techniques.
 Therefore, it seems that experts exhibit pedagogical behaviours to highlight crucial performance aspects for potential learners.
@@
 Moreover, the same modulations of pedagogical performance parameters observed in our previous experiments such as slower demonstration and exaggerated performance, should be used to infer teaching intentions by the learners.
-In Experiment 1 learners listened to performances that followed simple musical scales.
-In Experiment 2 learners listened to performances of a more complex piece.
+In Experiment 1 participants listened to performances that followed simple musical scales.
+In Experiment 2 participants listened to performances of a more complex piece.
 
@@
 We randomly sampled 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition.
-It is important to note that the recordings from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments (e.g., exaggeration) since we randomly sampled the performances.
+It is important to note that the recordings from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments (e.g., exaggeration) since we randomly sampled the performances from multiple pianists.
 
@@
 
-At the end of the experiment, participants filled in a questionnaire about their demographic information and thier prior experience with playing musical instruments.
+At the end of the experiment, participants filled in a questionnaire about their demographic information and their prior experience with playing musical instruments.
 
@@
 ### Accuracy
-First, we examined whether participants could accurately distinguish the stimuli chosen from the teaching condition in Tominaga et al., (*submitted*; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (*submitted*; Experiment 1) as performing.
+First, we examined whether participants could accurately recognise the stimuli chosen from the teaching condition in Tominaga et al., (*submitted*; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (*submitted*; Experiment 1) as performing.
 We compared how accurate participants were against the chance level (50%).
@@
 For articulation recordings, there were two models.
-The Legato model (*Figure \ref{fig:stim1}*, 1) considered only legato parts of the performances.
+The Legato model (*Figure \ref{fig:stim1}*, (1)) considered only legato parts of the performances.
 We entered the legato parts of KOT and KV and KV-Diff or transition points from legato to staccato.
-The Staccato model (*Figure \ref{fig:stim1}*, 2) considered only staccato parts of the performances.
+The Staccato model (*Figure \ref{fig:stim1}*, (2)) considered only staccato parts of the performances.
 We entered the staccato parts of KOT and KV and KV-Diff of transition points from staccato to legato.
 Similarly, there were two models for dynamics recordings.
-The Forte model (*Figure \ref{fig:stim1}*, 3) considered only forte parts of the performances for KV and KOT, and transition points from forte to piano for KV-Diff.
-The Piano model (*Figure \ref{fig:stim1}*, 4) considered only piano parts of the performances for KV and KOT, and transition points from piano to forte for KV-Diff.
+The Forte model (*Figure \ref{fig:stim1}*, (3)) considered only forte parts of the performances for KV and KOT, and transition points from forte to piano for KV-Diff.
+The Piano model (*Figure \ref{fig:stim1}*, (4)) considered only piano parts of the performances for KV and KOT, and transition points from piano to forte for KV-Diff.
 With regard to tempo (IOIs), there was only one value for each recording regardless of the subcomponents because tempo was consistent across the performance.
@@
 Participants listened to a recording via headphones while corresponding sheet music was displayed on a monitor.
-They were required to respond by pressing a left-arrow (yes) or right-arrow (no) key for each judgment.
+They were required to respond by pressing the left-arrow (yes) or right-arrow (no) key for each judgment.
 Headphone image from Flaticon.com.", echo = FALSE}
@@
 
-For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_diff_ltos$p.value)))}`, From Staccato to Legato; *r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$p.value)))}`, *Figure \ref{fig:vel-diff-1}*, left).
+For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$p.value)))}`, From Staccato to Legato; *r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$p.value)))}`, *Figure \ref{fig:vel-diff-1}*, left).
 
@@
 ## Multiple regression
-In order to further investigate which feature of performance contributed most to participants' judgments as teaching, multiple regression analyses were conducted.
+In order to further investigate which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted.
 Statistical model assumptions were tested using the *performance* R package [@ludecke_2021].
@@
 The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m2)$adj.r.squared*100)` % of the variance (*F*(`r summary(m2)$fstatistic[2]`, `r summary(m2)$fstatistic[3]`) = `r sprintf('%.1f', summary(m2)$fstatistic[1])`, *p* `r if(lmp(m2) < 0.001){"< .001"} else {paste("= ", sprintf('%.2f', lmp(m2)))}`).
-It was found that tempo (IOIs; *$\beta$* = `r summary(m2)$coefficients[2]`, *p* `r if(summary(m2)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m2)$coefficients[2, 4])))}`) and articulation for the staccato parts (KOT; *$\beta$* = `r summary(m2)$coefficients[3]`, *p* `r if(summary(m2)$coefficients[3, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m2)$coefficients[3, 4])))}`) were significant predictors of participants' judgments as teaching.
+It was found that tempo (IOIs; *$\beta$* = `r summary(m2)$coefficients[2]`, *p* `r if(summary(m2)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m2)$coefficients[2, 4])))}`) and articulation for the staccato parts (KOT; *$\beta$* = `r summary(m2)$coefficients[3]`, *p* `r if(summary(m2)$coefficients[3, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', summary(m2)$coefficients[3, 4])))}`) were significant predictors of participants' judgments as teaching.
 
@@
 The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m3)$adj.r.squared*100)` % of the variance (*F*(`r summary(m3)$fstatistic[2]`, `r summary(m3)$fstatistic[3]`) = `r sprintf('%.2f', summary(m3)$fstatistic[1])`, *p* `r if(lmp(m3) < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', lmp(m3))))}`).
-It was found that tempo (IOIs; *$\beta$* = `r summary(m3)$coefficients[2]`, *p* `r if(summary(m3)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m3)$coefficients[2, 4])))}`) and dynamics for the forte parts (KV; *$\beta$* = `r summary(m3)$coefficients[4]`, *p* `r if(summary(m3)$coefficients[4, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m3)$coefficients[4, 4])))}`) were significant predictors of participants' judgments as teaching.
+It was found that tempo (IOIs; *$\beta$* = `r summary(m3)$coefficients[2]`, *p* `r if(summary(m3)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m3)$coefficients[2, 4])))}`) and dynamics for the forte parts (KV; *$\beta$* = `r summary(m3)$coefficients[4]`, *p* `r if(summary(m3)$coefficients[4, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', summary(m3)$coefficients[4, 4])))}`) were significant predictors of participants' judgments as teaching.
 
@@
 Therefore, each dot represents each stimulus.
-The gray bands display the 95 percent confidence intervals."}
+The gray bands display the 95 percent confidence intervals.
+LtoS; Legato to Staccato, StoL; Staccato to Legato, FtoP; Forte to Piano, PtoF; Piano to Forte."}
 img_cor_vel_diff_1
@@
 For dynamics recordings, louder performances were more likely to be judged as teaching whereas there was no relationship between softer sound and participants' judgments as teaching.
-Importantly, performances with larger contrast between forte and piano for both directions (i.e., from forte to piano, from piano to forte) were more likely to be judged as teaching.
+Importantly, performances with larger contrasts between forte and piano for both directions (i.e., from forte to piano, from piano to forte) were more likely to be judged as teaching.
 This result may suggest that dynamics contrast might be reliably used to infer teaching intentions, rather than absolute dynamics values themselves.
@@
 Given the findings in Experiment 1, we predicted that slower performance would be likely to be judged as teaching regardless of which expressive technique (i.e., articulation or dynamics) was implemented.
-Also performances with exaggerated articulation and dynamics (in particular, longer legato and shorter staccato, larger contrast between forte and piano) would be likely to be judged as teaching.
+Also performances with exaggerated articulation and dynamics (in particular, longer legato and shorter staccato, larger contrasts between forte and piano) would be likely to be judged as teaching.
 
@@
 We recruited `r nrow(dt)` participants who had at least six years of training in any musical instrument or singing.
-They were able to read sheet music and know two musical expressive techniques of articulation and dynamics.
+They were able to read sheet music and knew two musical expressive techniques of articulation and dynamics.
 One participant was excluded because s/he did not understand the instructions.
@@
 For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (*r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$p.value)))}`).
-However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (*r(`r cor_kot_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_kot_pia$p.value)))}`), suggesting that performances with staccato-style piano were more likely to be considered as teaching performance (*Figure \ref{fig:kot-2}*, right).
+However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (*r(`r cor_kot_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$p.value)))}`), suggesting that performances with staccato-style piano were more likely to be considered as teaching performance (*Figure \ref{fig:kot-2}*, right).
 However, this significance disappeared after removing one outlier outside of 2 standard deviations in terms of KOT values for piano.
@@
 
-For articulation recordings, there was no significant relationship between KV difference between transition points from legato to staccato and participants' judgments as teaching (*r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_vel_diff_ltos$p.value)))}`).
-However, there was a significant relationship between the transition points from staccato to legato and participants' judgments as teaching (*r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$p.value)))}`), suggesting that performances with larger contrast from staccato to legato were more likely to be considered as teaching performance (*Figure \ref{fig:vel-diff-2}*, left).
+For articulation recordings, there was no significant relationship between KV difference between transition points from legato to staccato and participants' judgments as teaching (*r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$p.value)))}`).
+However, there was a significant relationship between the transition points from staccato to legato and participants' judgments as teaching (*r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$p.value)))}`), suggesting that performances with larger contrasts from staccato to legato were more likely to be considered as teaching performance (*Figure \ref{fig:vel-diff-2}*, left).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
-The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m1)$adj.r.squared*100)` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r sprintf('%.2f', summary(m1)$fstatistic[1])`, *p* `r if(lmp(m1) < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', lmp(m1))))}`).
-It was found that tempo (IOIs; *$\beta$* = `r summary(m1)$coefficients[2]`, *p* `r if(summary(m1)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m1)$coefficients[2, 4])))}`), dynamics (KV; *$\beta$* = `r summary(m1)$coefficients[4]`, *p* `r if(summary(m1)$coefficients[4, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m1)$coefficients[4, 4])))}`) and dynamics contrast (KV-Diff; *$\beta$* = `r summary(m1)$coefficients[5]`, *p* `r if(summary(m1)$coefficients[5, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m1)$coefficients[5, 4])))}`) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
+The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m1)$adj.r.squared*100)` % of the variance (*F*(`r summary(m1)$fstatistic[2]`, `r summary(m1)$fstatistic[3]`) = `r sprintf('%.2f', summary(m1)$fstatistic[1])`, *p* `r if(lmp(m1) < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', lmp(m1))))}`).
+It was found that tempo (IOIs; *$\beta$* = `r summary(m1)$coefficients[2]`, *p* `r if(summary(m1)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', summary(m1)$coefficients[2, 4])))}`), dynamics (KV; *$\beta$* = `r summary(m1)$coefficients[4]`, *p* `r if(summary(m1)$coefficients[4, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', summary(m1)$coefficients[4, 4])))}`) and dynamics contrast (KV-Diff; *$\beta$* = `r summary(m1)$coefficients[5]`, *p* `r if(summary(m1)$coefficients[5, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m1)$coefficients[5, 4])))}`) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
 However, articulation (KOT; *$\beta$* = `r summary(m1)$coefficients[3]`, *p* `r if(summary(m1)$coefficients[3, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', summary(m1)$coefficients[3, 4])))}`) for the legato parts was not a significant predictor.
@@
 The result of the regression indicated that the model explained `r sprintf('%.1f', summary(m4)$adj.r.squared*100)` % of the variance (*F*(`r summary(m4)$fstatistic[2]`, `r summary(m4)$fstatistic[3]`) = `r sprintf('%.2f', summary(m4)$fstatistic[1])`, *p* `r if(lmp(m4) < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', lmp(m4))))}`).
-It was found that tempo (IOIs; *$\beta$* = `r summary(m4)$coefficients[2]`, *p* `r if(summary(m4)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m4)$coefficients[2, 4])))}`) and dynamics contrast from piano to forte (KV-Diff; *$\beta$* = `r summary(m4)$coefficients[5]`, *p* `r if(summary(m4)$coefficients[5, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m4)$coefficients[5, 4])))}`) were significant predictors of participants' judgments as teaching.
+It was found that tempo (IOIs; *$\beta$* = `r summary(m4)$coefficients[2]`, *p* `r if(summary(m4)$coefficients[2, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', summary(m4)$coefficients[2, 4])))}`) and dynamics contrast from piano to forte (KV-Diff; *$\beta$* = `r summary(m4)$coefficients[5]`, *p* `r if(summary(m4)$coefficients[5, 4] < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', summary(m4)$coefficients[5, 4])))}`) were significant predictors of participants' judgments as teaching.
 
-```{r plot-ioi-2, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:ioi-2}Experiment 2: Scatter plot showing the correlation between tempo featurea (IOIs) and average participants' judgments as teaching for each recording.
+```{r plot-ioi-2, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:ioi-2}Experiment 2: Scatter plot showing the correlation between tempo feature (IOIs) and average participants' judgments as teaching for each recording.
 Therefore, each dot represents each stimulus.
@@
 ```{r plot-vel-diff-2, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-diff-2}Experiment 2: Scatter plot showing the correlation between dynamics contrast features (KV-Diff) and average participants' judgment as teaching for each stimulus.
-The gray bands display the 95 percent confidence intervals."}
+The gray bands display the 95 percent confidence intervals.
+LtoS; Legato to Staccato, StoL; Staccato to Legato, FtoP; Forte to Piano, PtoF; Piano to Forte."}
 img_cor_vel_diff_2
@@
 The aim of Experiment 2 was to replicate the results of Experiment 1 and examine how musicians would infer teaching intentions when listening to a more complex piece of music.
-We found that tempo (IOIs) and articulation (KOT) did not seem to contribute to participants' judgments as teaching.
+We found that articulation (KOT) did not seem to contribute to participants’ judgments as teaching.
+Also, tempo (IOIs) was related to participants’ judgments as teaching for dynamics recordings only.
 It seems that variations in these two parameters were considered to be in the space of possible interpretations of the music and were not used as general cues to infer teaching intentions.
+
+However, dynamics (KV) seems continued to be used as cue to teaching intentions despite the increased musical complexity.
+Particularly performances with larger contrasts between forte and piano seem to be considered as teaching.
+Moreover, performances with both exaggerated forte and piano were considered to be for teaching.
+Thus, loudness (dynamics) might be used as a reliable cue to infer teaching intentions regardless of the complexity of a musical piece.
 
@@
 This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al.
-(*submitted*) and all the selected recordings did not exhibit the characteristics of teaching performance (e.g., slower demonstration, exaggeration).
+(*submitted*).
+There was great variability in the selected recordings from multiple pianists and some of them do not seem to have exhibited the characteristics of teaching performance (e.g., slower demonstration, exaggeration).
+A possible reason is that some participants had difficulties in situating themselves in a teaching context and therefore did not produce cues.
+
 The reason why we randomly selected the stimuli from each condition (i.e., teaching or performing) was because all the characteristics of teaching performance (e.g., IOIs, KOT, KV) were intercorrelated and it was difficult to choose stimuli based on one single criterion.
@@
 Another possibility for the low accuracy could be that it was difficult even for musicians to find which cues were produced for teaching when listening to one piece of music with several phrases.
-Future research should examine whether accuracy would be improved when listening to phrases compared to pieces.
+Future research should examine whether accuracy would be improved when listening to phrases compared to whole pieces.
 
-In order to examine which features of piano performance make musicians infer pedagogical intentions, we performed correlation and multiple regression analysis.
-Across the two experiments, it was found that loudness, particularly larger contrast between forte and piano, strongly contributed to participants' judgments when listening to dynamics recordings.
-On the other hand, unlike what we predicted, slower performance was only considered to be for teaching in Experiment 1 where the stimuli consisted of simple musical scales.
+To examine which features of piano performance make musicians infer pedagogical intentions, we performed correlation and multiple regression analysis.
+Across the two experiments, it was found that loudness, particularly larger contrast between forte and piano, strongly contributed to participants’ judgments when listening to dynamics recordings.
+On the other hand, unlike what we predicted, slower performance was only considered to be for teaching for both techniques in Experiment 1 where the stimuli consisted of simple musical scales.
 Also, we could not find that performances with exaggerated articulation (i.e., longer legato and shorter staccato) were more likely to be judged as teaching in Experiment 2.
-This might suggest that some characteristics of performance are not necessarily used or reliable to infer performers' intentions when listening to musically complex pieces.
-It can be speculated that certain modulations are too subtle so that participants could not perceive them.
-Another possibility is that modulations can also be considered as one of the expressions or interpretations.
-These findings may suggest that it is easier for novices to learn musical expressive techniques in musical scales rather than in a piece.
+This indicates that some characteristics of performance are not necessarily used or reliable to infer performers’ intentions when listening to musically complex pieces.
+Certain modulations may have been too subtle to be noticed by the participants.
+This would be in line with @gabrielsson_2010 who reported that tempo and loudness reign over other musical factors and seem to be easier for listeners to judge.
+Another possibility is that a wide range of modulations is considered as expressive in more complex pieces.
+This raises the possibility that it is easier to learn and teach musical expressive techniques when musical complexity is low.
+
+The piece used in Experiment 2 was from actual sonatinas.
+Although sonatina pieces are generally aimed to be simple and easy for beginner pianists to play, they add a multitude of musical properties to a performance that is not present in musical scales.
+Not only do performers produce their communicative intentions such as emotion, but composers can express their feelings by handling various musical notations such as melody, rhythm and harmony [@gabrielsson_2010].
+In our study, most of the staccato parts of the piece used in Experiment 2 (Figure, 7 (2)) were comprised of the same repetitive notes.
+This implied that they could be only played in staccato style.
+Dynamics may be more independent of the structure of the piece compared to articulation.
+Therefore, participants might have had difficulties in recognising teaching intentions from articulation in Experiment 2.
+This would imply that the ease of difficulty with which teaching intentions can be derived vary across different pieces depend on a variety of musical properties.
 
@@
 
+\newpage
+
 # Supplementary Materials

### 2022-04-28 paper/manuscript.tex
first submission
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 \documentclass[
-  man]{apa6}
+  man,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
@@
 {}{\PatchFailed}
-\keywords{perception, expression, pedagogy, expertise, music education}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
+\keywords{perception, expression, expertise, music education, pedagogy}
 \usepackage{csquotes}
@@
   pdftitle={What makes musicians infer teaching intentions?},
-  pdfauthor={Atsuko Tominaga1,*, Günther Knoblich1, \& Natalie Sebanz1},
+  pdfauthor={Atsuko Tominaga1, Günther Knoblich1, \& Natalie Sebanz1},
   pdflang={en-EN},
-  pdfkeywords={perception, expression, pedagogy, expertise, music education},
+  pdfkeywords={perception, expression, expertise, music education, pedagogy},
   hidelinks,
@@
 \title{What makes musicians infer teaching intentions?}
-\author{Atsuko Tominaga\textsuperscript{1,*}, Günther Knoblich\textsuperscript{1}, \& Natalie Sebanz\textsuperscript{1}}
+\author{Atsuko Tominaga\textsuperscript{1}, Günther Knoblich\textsuperscript{1}, \& Natalie Sebanz\textsuperscript{1}}
 \date{}
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Cognitive Science, Central European University, Quellenstraße 51, 1100 Vienna, Austria\\\textsuperscript{*} Corresponding author: \href{mailto:Tominaga_Atsuko@phd.ceu.edu}{\nolinkurl{Tominaga\_Atsuko@phd.ceu.edu}}}
+\authornote{
+
+Correspondence concerning this article should be addressed to Atsuko Tominaga, Quellenstraße 51, 1100 Vienna, Austria.
+E-mail: \href{mailto:Tominaga_Atsuko@phd.ceu.edu}{\nolinkurl{Tominaga\_Atsuko@phd.ceu.edu}}
+
+}
+
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Cognitive Science, Central European University, Quellenstraße 51, 1100 Vienna, Austria}
 
@@
 
-First, we examined whether participants could accurately distinguish the stimuli chosen from the teaching condition in Tominaga et al., (\emph{submitted}; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (\emph{submitted}; Experiment 1) as performing.
+First, we examined whether participants could accurately recognise the stimuli chosen from the teaching condition in Tominaga et al., (\emph{submitted}; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (\emph{submitted}; Experiment 1) as performing.
 We compared how accurate participants were against the chance level (50\%).
@@
 For articulation recordings, there were two models.
-The Legato model (\emph{Figure \ref{fig:stim1}}, 1) considered only legato parts of the performances.
+The Legato model (\emph{Figure \ref{fig:stim1}}, (1)) considered only legato parts of the performances.
 We entered the legato parts of KOT and KV and KV-Diff or transition points from legato to staccato.
-The Staccato model (\emph{Figure \ref{fig:stim1}}, 2) considered only staccato parts of the performances.
+The Staccato model (\emph{Figure \ref{fig:stim1}}, (2)) considered only staccato parts of the performances.
 We entered the staccato parts of KOT and KV and KV-Diff of transition points from staccato to legato.
 Similarly, there were two models for dynamics recordings.
-The Forte model (\emph{Figure \ref{fig:stim1}}, 3) considered only forte parts of the performances for KV and KOT, and transition points from forte to piano for KV-Diff.
-The Piano model (\emph{Figure \ref{fig:stim1}}, 4) considered only piano parts of the performances for KV and KOT, and transition points from piano to forte for KV-Diff.
+The Forte model (\emph{Figure \ref{fig:stim1}}, (3)) considered only forte parts of the performances for KV and KOT, and transition points from forte to piano for KV-Diff.
+The Piano model (\emph{Figure \ref{fig:stim1}}, (4)) considered only piano parts of the performances for KV and KOT, and transition points from piano to forte for KV-Diff.
 With regard to tempo (IOIs), there was only one value for each recording regardless of the subcomponents because tempo was consistent across the performance.
@@
 Participants listened to a recording via headphones while corresponding sheet music was displayed on a monitor.
-They were required to respond by pressing a left-arrow (yes) or right-arrow (no) key for each judgment.
+They were required to respond by pressing the left-arrow (yes) or right-arrow (no) key for each judgment.
 Headphone image from Flaticon.com.}\label{fig:procedure-1}
@@
 For dynamics, the mean percentage of correct answers {[}\emph{M} = 55.2, \emph{SD} = 7.81{]} was significantly higher than chance (\emph{t}(19) = 2.98, \emph{p} = .01, cohen's \emph{d} = 0.67).
-A paired \emph{t}-test revealed that there was a significant difference between the two techniques in terms of the accuracy (\emph{t}(19) = -2.12, \emph{p} = .05, cohen's \emph{d} = -0.69), suggesting participants chose correct answers more for dynamics recordings than articulation recordings.
+A paired \emph{t}-test revealed that there was a significant difference between the two techniques in terms of the accuracy (\emph{t}(19) = -2.12, \emph{p} = .048, cohen's \emph{d} = -0.69), suggesting participants chose correct answers more for dynamics recordings than articulation recordings.
 
@@
 
-For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r(46)} = -.26, \emph{p} = .071, From Staccato to Legato; \emph{r(46)} = -.19, \emph{p} = .21, \emph{Figure \ref{fig:vel-diff-1}}, left).
+For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r(46)} = -.26, \emph{p} = .07, From Staccato to Legato; \emph{r(46)} = -.19, \emph{p} = .21, \emph{Figure \ref{fig:vel-diff-1}}, left).
 
@@
 
-In order to further investigate which feature of performance contributed most to participants' judgments as teaching, multiple regression analyses were conducted.
+In order to further investigate which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted.
 Statistical model assumptions were tested using the \emph{performance} R package (Lüdecke, Ben-Shachar, Patil, Waggoner, \& Makowski, 2021).
@@
 The result of the regression indicated that the model explained 64.0 \% of the variance (\emph{F}(4, 43) = 21.9, \emph{p} \textless{} .001).
-It was found that tempo (IOIs; \emph{\(\beta\)} = 0.52, \emph{p} = .002) and articulation for the staccato parts (KOT; \emph{\(\beta\)} = -0.28, \emph{p} = .020) were significant predictors of participants' judgments as teaching.
+It was found that tempo (IOIs; \emph{\(\beta\)} = 0.52, \emph{p} = .002) and articulation for the staccato parts (KOT; \emph{\(\beta\)} = -0.28, \emph{p} = .02) were significant predictors of participants' judgments as teaching.
 
@@
 The result of the regression indicated that the model explained 35.9 \% of the variance (\emph{F}(4, 43) = 7.58, \emph{p} \textless{} .001).
-It was found that tempo (IOIs; \emph{\(\beta\)} = 0.35, \emph{p} = .007) and dynamics for the forte parts (KV; \emph{\(\beta\)} = 0.73, \emph{p} = .048) were significant predictors of participants' judgments as teaching.
+It was found that tempo (IOIs; \emph{\(\beta\)} = 0.35, \emph{p} = .007) and dynamics for the forte parts (KV; \emph{\(\beta\)} = 0.73, \emph{p} = .05) were significant predictors of participants' judgments as teaching.
 
@@
 Therefore, each dot represents each stimulus.
-The gray bands display the 95 percent confidence intervals.}\label{fig:plot-vel-diff-1}
+The gray bands display the 95 percent confidence intervals.
+LtoS; Legato to Staccato, StoL; Staccato to Legato, FtoP; Forte to Piano, PtoF; Piano to Forte.}\label{fig:plot-vel-diff-1}
 \end{figure}
@@
 We recruited 21 participants who had at least six years of training in any musical instrument or singing.
-They were able to read sheet music and know two musical expressive techniques of articulation and dynamics.
+They were able to read sheet music and knew two musical expressive techniques of articulation and dynamics.
 One participant was excluded because s/he did not understand the instructions.
@@
 For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (\emph{r(34)} = -.11, \emph{p} = .52).
-However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r(34)} = -.35, \emph{p} = .034), suggesting that performances with staccato-style piano were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).
+However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r(34)} = -.35, \emph{p} = .03), suggesting that performances with staccato-style piano were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).
 However, this significance disappeared after removing one outlier outside of 2 standard deviations in terms of KOT values for piano.
@@
 
-For articulation recordings, there was no significant relationship between KV difference between transition points from legato to staccato and participants' judgments as teaching (\emph{r(34)} = .23, \emph{p} = .176).
-However, there was a significant relationship between the transition points from staccato to legato and participants' judgments as teaching (\emph{r(34)} = .36, \emph{p} = .03), suggesting that performances with larger contrast from staccato to legato were more likely to be considered as teaching performance (\emph{Figure \ref{fig:vel-diff-2}}, left).
+For articulation recordings, there was no significant relationship between KV difference between transition points from legato to staccato and participants' judgments as teaching (\emph{r(34)} = .23, \emph{p} = .18).
+However, there was a significant relationship between the transition points from staccato to legato and participants' judgments as teaching (\emph{r(34)} = .36, \emph{p} = .03), suggesting that performances with larger contrasts from staccato to legato were more likely to be considered as teaching performance (\emph{Figure \ref{fig:vel-diff-2}}, left).
 
@@
 A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato).
-The result of the regression indicated that the model explained 19.8 \% of the variance (\emph{F}(4, 31) = 3.16, \emph{p} = .028).
-It was found that tempo (IOIs; \emph{\(\beta\)} = 0.58, \emph{p} = .011), dynamics (KV; \emph{\(\beta\)} = 1.10, \emph{p} = .018) and dynamics contrast (KV-Diff; \emph{\(\beta\)} = 1.90, \emph{p} = .006) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
+The result of the regression indicated that the model explained 19.8 \% of the variance (\emph{F}(4, 31) = 3.16, \emph{p} = .03).
+It was found that tempo (IOIs; \emph{\(\beta\)} = 0.58, \emph{p} = .01), dynamics (KV; \emph{\(\beta\)} = 1.10, \emph{p} = .02) and dynamics contrast (KV-Diff; \emph{\(\beta\)} = 1.90, \emph{p} = .006) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching.
 However, articulation (KOT; \emph{\(\beta\)} = -0.08, \emph{p} = .47) for the legato parts was not a significant predictor.
@@
 The result of the regression indicated that the model explained 49.5 \% of the variance (\emph{F}(4, 31) = 9.57, \emph{p} \textless{} .001).
-It was found that tempo (IOIs; \emph{\(\beta\)} = 0.55, \emph{p} = .022) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 1.09, \emph{p} \textless{} .001) were significant predictors of participants' judgments as teaching.
+It was found that tempo (IOIs; \emph{\(\beta\)} = 0.55, \emph{p} = .02) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 1.09, \emph{p} \textless{} .001) were significant predictors of participants' judgments as teaching.
 
@@
 
-\caption{\label{fig:ioi-2}Experiment 2: Scatter plot showing the correlation between tempo featurea (IOIs) and average participants' judgments as teaching for each recording.
+\caption{\label{fig:ioi-2}Experiment 2: Scatter plot showing the correlation between tempo feature (IOIs) and average participants' judgments as teaching for each recording.
 Therefore, each dot represents each stimulus.
@@
 \caption{\label{fig:vel-diff-2}Experiment 2: Scatter plot showing the correlation between dynamics contrast features (KV-Diff) and average participants' judgment as teaching for each stimulus.
-The gray bands display the 95 percent confidence intervals.}\label{fig:plot-vel-diff-2}
+The gray bands display the 95 percent confidence intervals.
+LtoS; Legato to Staccato, StoL; Staccato to Legato, FtoP; Forte to Piano, PtoF; Piano to Forte.}\label{fig:plot-vel-diff-2}
 \end{figure}
@@
 The aim of Experiment 2 was to replicate the results of Experiment 1 and examine how musicians would infer teaching intentions when listening to a more complex piece of music.
-We found that tempo (IOIs) and articulation (KOT) did not seem to contribute to participants' judgments as teaching.
+We found that articulation (KOT) did not seem to contribute to participants' judgments as teaching.
+Also, tempo (IOIs) was related to participants' judgments as teaching for dynamics recordings only.
 It seems that variations in these two parameters were considered to be in the space of possible interpretations of the music and were not used as general cues to infer teaching intentions.
+
+However, dynamics (KV) seems continued to be used as cue to teaching intentions despite the increased musical complexity.
+Particularly performances with larger contrasts between forte and piano seem to be considered as teaching.
+Moreover, performances with both exaggerated forte and piano were considered to be for teaching.
+Thus, loudness (dynamics) might be used as a reliable cue to infer teaching intentions regardless of the complexity of a musical piece.
 
@@
 However, the results showed that the accuracy was relatively low (52.7 \% in Experiment 1; 52.8 \% in Experiment 2).
-This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al.~(\emph{submitted}) and all the selected recordings did not exhibit the characteristics of teaching performance (e.g., slower demonstration, exaggeration).
+This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al.~(\emph{submitted}).
+There was great variability in the selected recordings from multiple pianists and some of them do not seem to have exhibited the characteristics of teaching performance (e.g., slower demonstration, exaggeration).
+A possible reason is that some participants had difficulties in situating themselves in a teaching context and therefore did not produce cues.
+
 The reason why we randomly selected the stimuli from each condition (i.e., teaching or performing) was because all the characteristics of teaching performance (e.g., IOIs, KOT, KV) were intercorrelated and it was difficult to choose stimuli based on one single criterion.
@@
 Another possibility for the low accuracy could be that it was difficult even for musicians to find which cues were produced for teaching when listening to one piece of music with several phrases.
-Future research should examine whether accuracy would be improved when listening to phrases compared to pieces.
+Future research should examine whether accuracy would be improved when listening to phrases compared to whole pieces.
 
-In order to examine which features of piano performance make musicians infer pedagogical intentions, we performed correlation and multiple regression analysis.
+To examine which features of piano performance make musicians infer pedagogical intentions, we performed correlation and multiple regression analysis.
 Across the two experiments, it was found that loudness, particularly larger contrast between forte and piano, strongly contributed to participants' judgments when listening to dynamics recordings.
-On the other hand, unlike what we predicted, slower performance was only considered to be for teaching in Experiment 1 where the stimuli consisted of simple musical scales.
+On the other hand, unlike what we predicted, slower performance was only considered to be for teaching for both techniques in Experiment 1 where the stimuli consisted of simple musical scales.
 Also, we could not find that performances with exaggerated articulation (i.e., longer legato and shorter staccato) were more likely to be judged as teaching in Experiment 2.
-This might suggest that some characteristics of performance are not necessarily used or reliable to infer performers' intentions when listening to musically complex pieces.
-It can be speculated that certain modulations are too subtle so that participants could not perceive them.
-Another possibility is that modulations can also be considered as one of the expressions or interpretations.
-These findings may suggest that it is easier for novices to learn musical expressive techniques in musical scales rather than in a piece.
+This indicates that some characteristics of performance are not necessarily used or reliable to infer performers' intentions when listening to musically complex pieces.
+Certain modulations may have been too subtle to be noticed by the participants.
+This would be in line with Gabrielsson and Lindström (2010) who reported that tempo and loudness reign over other musical factors and seem to be easier for listeners to judge.
+Another possibility is that a wide range of modulations is considered as expressive in more complex pieces.
+This raises the possibility that it is easier to learn and teach musical expressive techniques when musical complexity is low.
+
+The piece used in Experiment 2 was from actual sonatinas.
+Although sonatina pieces are generally aimed to be simple and easy for beginner pianists to play, they add a multitude of musical properties to a performance that is not present in musical scales.
+Not only do performers produce their communicative intentions such as emotion, but composers can express their feelings by handling various musical notations such as melody, rhythm and harmony (Gabrielsson \& Lindström, 2010).
+In our study, most of the staccato parts of the piece used in Experiment 2 (Figure, 7 (2)) were comprised of the same repetitive notes.
+This implied that they could be only played in staccato style.
+Dynamics may be more independent of the structure of the piece compared to articulation.
+Therefore, participants might have had difficulties in recognising teaching intentions from articulation in Experiment 2.
+This would imply that the ease of difficulty with which teaching intentions can be derived vary across different pieces depend on a variety of musical properties.
 
@@
 \url{https://doi.org/10.1177/0305735696241007}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gabrielsson_2010}{}}%
+Gabrielsson, A., \& Lindström, E.
+(2010).
+The role of structure in the musical expression of emotions.
+In \emph{Series in Affective Science}.
+\emph{Handbook of music and emotion: {Theory}, research, applications} (pp.
+367--400).
+{New York, NY, US}: {Oxford University Press}.
 
@@
 
+\newpage
+
 \hypertarget{supplementary-materials}{%

### 2022-04-28 paper/manuscript.Rmd
submitted documents
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-Tominaga, Knoblich & Sebanz (*submitted*) extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression.
+@tominaga_2022a extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression.
 We investigated whether and how expert pianists communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
@@
 ## Stimuli
-We selected stimuli from the performances obtained in our previous experiments (Tominaga et al., *submitted*).
+We selected stimuli from the performances obtained in our previous experiments [@tominaga_2022a].
 Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files.
@@
 
-In Tominaga et al., (*submitted*), participants were asked to perform the piece with either articulation or dynamics in two different conditions.
+In @tominaga_2022a, participants were asked to perform the piece with either articulation or dynamics in two different conditions.
 In the teaching condition, participants were instructed to perform the piece with the designated expressive technique as if they were teaching it to students (e.g., in a lesson).
@@
 In Tominaga et al.
-(*submitted*; Experiment 1), there were 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition.
+(2022; Experiment 1), there were 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition.
 For the current experiment, 96 recordings were chosen from the valid performances.
@@
 ### Accuracy
-First, we examined whether participants could accurately recognise the stimuli chosen from the teaching condition in Tominaga et al., (*submitted*; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (*submitted*; Experiment 1) as performing.
+First, we examined whether participants could accurately recognise the stimuli chosen from the teaching condition in Tominaga et al., (2022; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (2022; Experiment 1) as performing.
 We compared how accurate participants were against the chance level (50%).
@@
 The symbol `f' denotes forte and the symbol `p' denotes piano.
-In multiple regression analysis, (3) corresponds to Forte model and (2) corresponds to Piano model.
+In multiple regression analysis, (3) corresponds to Forte model and (4) corresponds to Piano model.
 Only the parts composed of 16th notes (i.e., (1), (2), (3), (4)) were used for data analysis.", echo = FALSE}
@@
 ## Stimuli
-As Experiment 1, we selected stimuli from our previous experiments (Tominaga et al., *submitted*; Experiment 2).
+As Experiment 1, we selected stimuli from our previous experiments (Tominaga et al., 2022; Experiment 2).
 The excerpt was taken from ``Sonatina Op.36 (No.3) in C major" by Muzio Clementi and modified for the experiment.
@@
 For the current experiment, 72 performances were chosen from the valid performances in Tominaga et al.
-(*submitted*; Experiment 2).
+(2022; Experiment 2).
 There were 248 valid performances in the teaching condition and 256 valid performances in the performing condition.
@@
 The symbol `f' denotes forte and the symbol `p' denotes piano.
-In multiple regression analysis, (3) corresponds to Forte model and (2) corresponds to Piano model.
+In multiple regression analysis, (3) corresponds to Forte model and (4) corresponds to Piano model.
 Only the 8th notes with expressive notations (i.e., (1), (2), (3), (4)) were used for data analysis.", echo = FALSE}
@@
 However, the results showed that the accuracy was relatively low (52.7 % in Experiment 1; 52.8 % in Experiment 2).
-This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al.
-(*submitted*).
+This might be because the stimuli were randomly sampled from the teaching and performing condition in @tominaga_2022a.
 There was great variability in the selected recordings from multiple pianists and some of them do not seem to have exhibited the characteristics of teaching performance (e.g., slower demonstration, exaggeration).
@@
 Not only do performers produce their communicative intentions such as emotion, but composers can express their feelings by handling various musical notations such as melody, rhythm and harmony [@gabrielsson_2010].
-In our study, most of the staccato parts of the piece used in Experiment 2 (Figure, 7 (2)) were comprised of the same repetitive notes.
-This implied that they could be only played in staccato style.
+In our study, most of the staccato parts of the piece used in Experiment 2 (*Figure \ref{fig:stim2}*, (2)) were comprised of the same repetitive notes.
+This implied that they could be only played in a staccato style.
 Dynamics may be more independent of the structure of the piece compared to articulation.

### 2022-04-28 paper/manuscript.tex
submitted documents
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-Tominaga, Knoblich \& Sebanz (\emph{submitted}) extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression.
+Tominaga, Knoblich, and Sebanz (2022) extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression.
 We investigated whether and how expert pianists communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
@@
 
-We selected stimuli from the performances obtained in our previous experiments (Tominaga et al., \emph{submitted}).
+We selected stimuli from the performances obtained in our previous experiments (Tominaga et al., 2022).
 Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files.
@@
 
-In Tominaga et al., (\emph{submitted}), participants were asked to perform the piece with either articulation or dynamics in two different conditions.
+In Tominaga et al.
+(2022), participants were asked to perform the piece with either articulation or dynamics in two different conditions.
 In the teaching condition, participants were instructed to perform the piece with the designated expressive technique as if they were teaching it to students (e.g., in a lesson).
 In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert).
-In Tominaga et al.~(\emph{submitted}; Experiment 1), there were 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition.
+In Tominaga et al.~(2022; Experiment 1), there were 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition.
 For the current experiment, 96 recordings were chosen from the valid performances.
@@
 
-First, we examined whether participants could accurately recognise the stimuli chosen from the teaching condition in Tominaga et al., (\emph{submitted}; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (\emph{submitted}; Experiment 1) as performing.
+First, we examined whether participants could accurately recognise the stimuli chosen from the teaching condition in Tominaga et al., (2022; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (2022; Experiment 1) as performing.
 We compared how accurate participants were against the chance level (50\%).
@@
 The symbol `f' denotes forte and the symbol `p' denotes piano.
-In multiple regression analysis, (3) corresponds to Forte model and (2) corresponds to Piano model.
+In multiple regression analysis, (3) corresponds to Forte model and (4) corresponds to Piano model.
 Only the parts composed of 16th notes (i.e., (1), (2), (3), (4)) were used for data analysis.}\label{fig:stim-1}
@@
 For dynamics, the mean percentage of correct answers {[}\emph{M} = 55.2, \emph{SD} = 7.81{]} was significantly higher than chance (\emph{t}(19) = 2.98, \emph{p} = .01, cohen's \emph{d} = 0.67).
-A paired \emph{t}-test revealed that there was a significant difference between the two techniques in terms of the accuracy (\emph{t}(19) = -2.12, \emph{p} = .048, cohen's \emph{d} = -0.69), suggesting participants chose correct answers more for dynamics recordings than articulation recordings.
+A paired \emph{t}-test revealed that there was a significant difference between the two techniques in terms of the accuracy (\emph{t}(19) = -2.12, \emph{p} = .05, cohen's \emph{d} = -0.69), suggesting participants chose correct answers more for dynamics recordings than articulation recordings.
 
@@
 
-As Experiment 1, we selected stimuli from our previous experiments (Tominaga et al., \emph{submitted}; Experiment 2).
+As Experiment 1, we selected stimuli from our previous experiments (Tominaga et al., 2022; Experiment 2).
 The excerpt was taken from ``Sonatina Op.36 (No.3) in C major'' by Muzio Clementi and modified for the experiment.
@@
 
-For the current experiment, 72 performances were chosen from the valid performances in Tominaga et al.~(\emph{submitted}; Experiment 2).
+For the current experiment, 72 performances were chosen from the valid performances in Tominaga et al.~(2022; Experiment 2).
 There were 248 valid performances in the teaching condition and 256 valid performances in the performing condition.
@@
 The symbol `f' denotes forte and the symbol `p' denotes piano.
-In multiple regression analysis, (3) corresponds to Forte model and (2) corresponds to Piano model.
+In multiple regression analysis, (3) corresponds to Forte model and (4) corresponds to Piano model.
 Only the 8th notes with expressive notations (i.e., (1), (2), (3), (4)) were used for data analysis.}\label{fig:stim-2}
@@
 However, the results showed that the accuracy was relatively low (52.7 \% in Experiment 1; 52.8 \% in Experiment 2).
-This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al.~(\emph{submitted}).
+This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al.
+(2022).
 There was great variability in the selected recordings from multiple pianists and some of them do not seem to have exhibited the characteristics of teaching performance (e.g., slower demonstration, exaggeration).
@@
 Not only do performers produce their communicative intentions such as emotion, but composers can express their feelings by handling various musical notations such as melody, rhythm and harmony (Gabrielsson \& Lindström, 2010).
-In our study, most of the staccato parts of the piece used in Experiment 2 (Figure, 7 (2)) were comprised of the same repetitive notes.
-This implied that they could be only played in staccato style.
+In our study, most of the staccato parts of the piece used in Experiment 2 (\emph{Figure \ref{fig:stim2}}, (2)) were comprised of the same repetitive notes.
+This implied that they could be only played in a staccato style.
 Dynamics may be more independent of the structure of the piece compared to articulation.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-tominaga_2022a}{}}%
+Tominaga, A., Knoblich, G., \& Sebanz, N. (2022). \emph{The sound of teaching music: {Expert} pianists' performance modulations for novices}. {PsyArXiv}. \url{https://doi.org/10.31234/osf.io/wzuyj}
+
 \leavevmode\vadjust pre{\hypertarget{ref-uther_2007}{}}%

### 2022-10-14 experiment-1/analysis/analysis.Rmd
upload analysis summary to RPubs
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ---
-title: 'Music Perception 1: Analysis'
+title: 'Music Perception: Analysis (Experiment 1)'
 output:
-  html_document:
-    df_print: paged
+  html_notebook: default
+editor_options: 
+  chunk_output_type: inline
 ---
@@
 
-qqnorm(ioi[Skill == "articulation"]$Teaching)
-qqline(ioi[Skill == "articulation"]$Teaching)
-ioi_art_norm_teaching
-
-qqnorm(ioi[Skill == "articulation"]$Mean)
-qqline(ioi[Skill == "articulation"]$Mean)
-ioi_art_norm_performance
+# qqnorm(ioi[Skill == "articulation"]$Teaching)
+# qqline(ioi[Skill == "articulation"]$Teaching)
+# ioi_art_norm_teaching
+# 
+# qqnorm(ioi[Skill == "articulation"]$Mean)
+# qqline(ioi[Skill == "articulation"]$Mean)
+# ioi_art_norm_performance
 
@@
 
-qqnorm(ioi[Skill == "dynamics"]$Teaching)
-qqline(ioi[Skill == "dynamics"]$Teaching)
-ioi_dyn_norm_teaching
-
-qqnorm(ioi[Skill == "dynamics"]$Mean)
-qqline(ioi[Skill == "dynamics"]$Mean)
-ioi_dyn_norm_performance
+# qqnorm(ioi[Skill == "dynamics"]$Teaching)
+# qqline(ioi[Skill == "dynamics"]$Teaching)
+# ioi_dyn_norm_teaching
+# 
+# qqnorm(ioi[Skill == "dynamics"]$Mean)
+# qqline(ioi[Skill == "dynamics"]$Mean)
+# ioi_dyn_norm_performance
 
@@
 
-qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-
-qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
-qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# 
+# qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
 
@@
 
-qqnorm(ioi_tra[Skill == "articulation"]$Teaching)
-qqline(ioi_tra[Skill == "articulation"]$Teaching)
-ioi_art_tra_norm_teaching
-
-qqnorm(ioi_tra[Skill == "articulation"]$Mean)
-qqline(ioi_tra[Skill == "articulation"]$Mean)
-ioi_art_tra_norm_performance
+# qqnorm(ioi_tra[Skill == "articulation"]$Teaching)
+# qqline(ioi_tra[Skill == "articulation"]$Teaching)
+# ioi_art_tra_norm_teaching
+# 
+# qqnorm(ioi_tra[Skill == "articulation"]$Mean)
+# qqline(ioi_tra[Skill == "articulation"]$Mean)
+# ioi_art_tra_norm_performance
 
@@
 
-qqnorm(ioi_tra[Skill == "dynamics"]$Teaching)
-qqline(ioi_tra[Skill == "dynamics"]$Teaching)
-ioi_dyn_tra_norm_teaching
-
-qqnorm(ioi_tra[Skill == "dynamics"]$Mean)
-qqline(ioi_tra[Skill == "dynamics"]$Mean)
-ioi_dyn_tra_norm_performance
+# qqnorm(ioi_tra[Skill == "dynamics"]$Teaching)
+# qqline(ioi_tra[Skill == "dynamics"]$Teaching)
+# ioi_dyn_tra_norm_teaching
+# 
+# qqnorm(ioi_tra[Skill == "dynamics"]$Mean)
+# qqline(ioi_tra[Skill == "dynamics"]$Mean)
+# ioi_dyn_tra_norm_performance
 
@@
 
-qqnorm(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-qqline(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-
-qqnorm(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
-qqline(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqnorm(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# qqline(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# 
+# qqnorm(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqline(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
 
@@
 
-qqnorm(cv[Skill == "articulation"]$Teaching)
-qqline(cv[Skill == "articulation"]$Teaching)
-cv_art_norm_teaching
-
-qqnorm(cv[Skill == "articulation"]$CV)
-qqline(cv[Skill == "articulation"]$CV)
-cv_art_norm_performance
+# qqnorm(cv[Skill == "articulation"]$Teaching)
+# qqline(cv[Skill == "articulation"]$Teaching)
+# cv_art_norm_teaching
+# 
+# qqnorm(cv[Skill == "articulation"]$CV)
+# qqline(cv[Skill == "articulation"]$CV)
+# cv_art_norm_performance
 
@@
 
-qqnorm(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
-qqline(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
-
-qqnorm(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)
-qqline(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+# qqnorm(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
+# qqline(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
+# 
+# qqnorm(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+# qqline(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)
 
@@
 
-qqnorm(cv[Skill == "dynamics"]$Teaching)
-qqline(cv[Skill == "dynamics"]$Teaching)
-cv_dyn_norm_teaching
-
-qqnorm(cv[Skill == "dynamics"]$CV)
-qqline(cv[Skill == "dynamics"]$CV)
-cv_dyn_norm_performance
+# qqnorm(cv[Skill == "dynamics"]$Teaching)
+# qqline(cv[Skill == "dynamics"]$Teaching)
+# cv_dyn_norm_teaching
+# 
+# qqnorm(cv[Skill == "dynamics"]$CV)
+# qqline(cv[Skill == "dynamics"]$CV)
+# cv_dyn_norm_performance
 
@@
 
-qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
-qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
-
-qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
-qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+# qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
+# qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
+# 
+# qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
+# qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
 
@@
 
-qqnorm(kot_all[Subcomponent == "Legato"]$Teaching)
-qqline(kot_all[Subcomponent == "Legato"]$Teaching)
-kot_leg_norm_teaching
-
-qqnorm(kot_all[Subcomponent == "Legato"]$Mean)
-qqline(kot_all[Subcomponent == "Legato"]$Mean)
-kot_leg_norm_performance
+# qqnorm(kot_all[Subcomponent == "Legato"]$Teaching)
+# qqline(kot_all[Subcomponent == "Legato"]$Teaching)
+# kot_leg_norm_teaching
+# 
+# qqnorm(kot_all[Subcomponent == "Legato"]$Mean)
+# qqline(kot_all[Subcomponent == "Legato"]$Mean)
+# kot_leg_norm_performance
 
@@
 
-qqnorm(kot_all[Subcomponent == "Staccato"]$Teaching)
-qqline(kot_all[Subcomponent == "Staccato"]$Teaching)
-kot_sta_norm_teaching
-
-qqnorm(kot_all[Subcomponent == "Staccato"]$Mean)
-qqline(kot_all[Subcomponent == "Staccato"]$Mean)
-kot_sta_norm_performance
+# qqnorm(kot_all[Subcomponent == "Staccato"]$Teaching)
+# qqline(kot_all[Subcomponent == "Staccato"]$Teaching)
+# kot_sta_norm_teaching
+# 
+# qqnorm(kot_all[Subcomponent == "Staccato"]$Mean)
+# qqline(kot_all[Subcomponent == "Staccato"]$Mean)
+# kot_sta_norm_performance
 
@@
 
-qqnorm(kot_all[Subcomponent == "Forte"]$Teaching)
-qqline(kot_all[Subcomponent == "Forte"]$Teaching)
-kot_for_norm_teaching
-
-qqnorm(kot_all[Subcomponent == "Forte"]$Mean)
-qqline(kot_all[Subcomponent == "Forte"]$Mean)
-kot_for_norm_performance
+# qqnorm(kot_all[Subcomponent == "Forte"]$Teaching)
+# qqline(kot_all[Subcomponent == "Forte"]$Teaching)
+# kot_for_norm_teaching
+# 
+# qqnorm(kot_all[Subcomponent == "Forte"]$Mean)
+# qqline(kot_all[Subcomponent == "Forte"]$Mean)
+# kot_for_norm_performance
 
@@
 
-qqnorm(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-qqline(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-
-qqnorm(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
-qqline(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqnorm(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# qqline(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# 
+# qqnorm(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqline(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
 
@@
 
-qqnorm(kot_all[Subcomponent == "Piano"]$Teaching)
-qqline(kot_all[Subcomponent == "Piano"]$Teaching)
-kot_pia_norm_teaching
-
-qqnorm(kot_all[Subcomponent == "Piano"]$Mean)
-qqline(kot_all[Subcomponent == "Piano"]$Mean)
-kot_pia_norm_performance
+# qqnorm(kot_all[Subcomponent == "Piano"]$Teaching)
+# qqline(kot_all[Subcomponent == "Piano"]$Teaching)
+# kot_pia_norm_teaching
+# 
+# qqnorm(kot_all[Subcomponent == "Piano"]$Mean)
+# qqline(kot_all[Subcomponent == "Piano"]$Mean)
+# kot_pia_norm_performance
 
@@
 
-qqnorm(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-qqline(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-
-qqnorm(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
-qqline(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqnorm(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# qqline(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# 
+# qqnorm(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqline(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
 
@@
 
-qqnorm(vel_all[Subcomponent == "Forte"]$Teaching)
-qqline(vel_all[Subcomponent == "Forte"]$Teaching)
-vel_for_norm_teaching
-
-qqnorm(vel_all[Subcomponent == "Forte"]$Mean)
-qqline(vel_all[Subcomponent == "Forte"]$Mean)
-vel_for_norm_performance
+# qqnorm(vel_all[Subcomponent == "Forte"]$Teaching)
+# qqline(vel_all[Subcomponent == "Forte"]$Teaching)
+# vel_for_norm_teaching
+# 
+# qqnorm(vel_all[Subcomponent == "Forte"]$Mean)
+# qqline(vel_all[Subcomponent == "Forte"]$Mean)
+# vel_for_norm_performance
 
@@
 
-qqnorm(vel_all[Subcomponent == "Piano"]$Teaching)
-qqline(vel_all[Subcomponent == "Piano"]$Teaching)
-vel_pia_norm_teaching
-
-qqnorm(vel_all[Subcomponent == "Piano"]$Mean)
-qqline(vel_all[Subcomponent == "Piano"]$Mean)
-vel_pia_norm_performance
+# qqnorm(vel_all[Subcomponent == "Piano"]$Teaching)
+# qqline(vel_all[Subcomponent == "Piano"]$Teaching)
+# vel_pia_norm_teaching
+# 
+# qqnorm(vel_all[Subcomponent == "Piano"]$Mean)
+# qqline(vel_all[Subcomponent == "Piano"]$Mean)
+# vel_pia_norm_performance
 
@@
 
-qqnorm(vel_all[Subcomponent == "Legato"]$Teaching)
-qqline(vel_all[Subcomponent == "Legato"]$Teaching)
-vel_leg_norm_teaching
-
-qqnorm(vel_all[Subcomponent == "Legato"]$Mean)
-qqline(vel_all[Subcomponent == "Legato"]$Mean)
-vel_leg_norm_performance
+# qqnorm(vel_all[Subcomponent == "Legato"]$Teaching)
+# qqline(vel_all[Subcomponent == "Legato"]$Teaching)
+# vel_leg_norm_teaching
+# 
+# qqnorm(vel_all[Subcomponent == "Legato"]$Mean)
+# qqline(vel_all[Subcomponent == "Legato"]$Mean)
+# vel_leg_norm_performance
 
@@
 
-qqnorm(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-qqline(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-
-qqnorm(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
-qqline(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqnorm(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# qqline(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# 
+# qqnorm(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqline(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
 
@@
 
-qqnorm(vel_all[Subcomponent == "Staccato"]$Teaching)
-qqline(vel_all[Subcomponent == "Staccato"]$Teaching)
-vel_sta_norm_teaching
-
-qqnorm(vel_all[Subcomponent == "Staccato"]$Mean)
-qqline(vel_all[Subcomponent == "Staccato"]$Mean)
-vel_sta_norm_performance
+# qqnorm(vel_all[Subcomponent == "Staccato"]$Teaching)
+# qqline(vel_all[Subcomponent == "Staccato"]$Teaching)
+# vel_sta_norm_teaching
+# 
+# qqnorm(vel_all[Subcomponent == "Staccato"]$Mean)
+# qqline(vel_all[Subcomponent == "Staccato"]$Mean)
+# vel_sta_norm_performance
 
@@
 
-qqnorm(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
-qqline(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
-vel_diff_ftop_norm_teaching
-
-qqnorm(vel_diff_all[Subcomponent == "FtoP"]$Mean)
-qqline(vel_diff_all[Subcomponent == "FtoP"]$Mean)
-vel_diff_ftop_norm_performance
+# qqnorm(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
+# qqline(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
+# vel_diff_ftop_norm_teaching
+# 
+# qqnorm(vel_diff_all[Subcomponent == "FtoP"]$Mean)
+# qqline(vel_diff_all[Subcomponent == "FtoP"]$Mean)
+# vel_diff_ftop_norm_performance
 
@@
 
-qqnorm(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
-qqline(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
-vel_diff_ptof_norm_teaching
-
-qqnorm(vel_diff_all[Subcomponent == "PtoF"]$Mean)
-qqline(vel_diff_all[Subcomponent == "PtoF"]$Mean)
-vel_diff_ptof_norm_performance
+# qqnorm(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
+# qqline(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
+# vel_diff_ptof_norm_teaching
+# 
+# qqnorm(vel_diff_all[Subcomponent == "PtoF"]$Mean)
+# qqline(vel_diff_all[Subcomponent == "PtoF"]$Mean)
+# vel_diff_ptof_norm_performance
 
@@
 
-qqnorm(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
-qqline(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
-vel_diff_ltos_norm_teaching
-
-qqnorm(vel_diff_all[Subcomponent == "LtoS"]$Mean)
-qqline(vel_diff_all[Subcomponent == "LtoS"]$Mean)
-vel_diff_ltos_norm_performance
+# qqnorm(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
+# qqline(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
+# vel_diff_ltos_norm_teaching
+# 
+# qqnorm(vel_diff_all[Subcomponent == "LtoS"]$Mean)
+# qqline(vel_diff_all[Subcomponent == "LtoS"]$Mean)
+# vel_diff_ltos_norm_performance
 
@@
 
-qqnorm(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-qqline(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-
-qqnorm(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
-qqline(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqnorm(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# qqline(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# 
+# qqnorm(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqline(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
 
@@
 
-qqnorm(vel_diff_all[Subcomponent == "StoL"]$Teaching)
-qqline(vel_diff_all[Subcomponent == "StoL"]$Teaching)
-vel_diff_stol_norm_teaching
-
-qqnorm(vel_diff_all[Subcomponent == "StoL"]$Mean)
-qqline(vel_diff_all[Subcomponent == "StoL"]$Mean)
-vel_diff_stol_norm_performance
+# qqnorm(vel_diff_all[Subcomponent == "StoL"]$Teaching)
+# qqline(vel_diff_all[Subcomponent == "StoL"]$Teaching)
+# vel_diff_stol_norm_teaching
+# 
+# qqnorm(vel_diff_all[Subcomponent == "StoL"]$Mean)
+# qqline(vel_diff_all[Subcomponent == "StoL"]$Mean)
+# vel_diff_stol_norm_performance
 
@@
 ## Legato
-```{r, echo = FALSE}
+```{r, echo = FALSE, fig.height = 4}
 m1 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Legato"])
@@
 ## Staccato
-```{r, echo = FALSE}
+```{r, echo = FALSE, fig.height = 4}
 m2 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Staccato"])
@@
 ## Forte
-```{r, echo = FALSE}
+```{r, echo = FALSE, fig.height = 4}
 m3 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Forte"])
@@
 ## Piano
-```{r, echo = FALSE}
+```{r, echo = FALSE, fig.height = 4}
 m4 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Piano"])

### 2022-10-14 experiment-2/analysis/analysis.Rmd
upload analysis summary to RPubs
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 output:
-  html_document:
-    df_print: paged
+  html_notebook: default
+editor_options: 
+  chunk_output_type: inline
 ---
@@
 
-qqnorm(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-qqline(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-
-qqnorm(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
-qqline(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqnorm(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# qqline(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# 
+# qqnorm(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqline(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
 
@@
 
-qqnorm(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-qqline(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-
-qqnorm(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
-qqline(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqnorm(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# qqline(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# 
+# qqnorm(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqline(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
 
@@
 
-qqnorm(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-qqline(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-
-qqnorm(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
-qqline(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqnorm(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# qqline(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# 
+# qqnorm(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqline(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
 
@@
 
-qqnorm(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-qqline(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
-
-qqnorm(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
-qqline(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqnorm(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# qqline(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
+# 
+# qqnorm(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
+# qqline(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
 

### 2022-10-14 experiment-1/analysis/analysis.R

@@ -1,4 +1,4 @@
-## ----set-up, include = FALSE--------------------------------------------------
+## ----set-up, include = FALSE------------------------------
 options(knitr.duplicate.label = "allow")
 
 # data manipulation
@@ -13,7 +13,7 @@ if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
 if (!require("performance")) {install.packages("performance"); require("performance")}
 
 
-## ----read, include = FALSE----------------------------------------------------
+## ----read, include = FALSE--------------------------------
 # read files and combine them
 data_lf <- list.files("../data", pattern = "csv")
 combined <- lapply(data_lf, function(f){
@@ -35,7 +35,7 @@ data[grepl("a_", midFile)]$Skill <- "articulation"
 data[grepl("d_", midFile)]$Skill <- "dynamics"
 
 
-## ----teaching, echo = FALSE---------------------------------------------------
+## ----teaching, echo = FALSE-------------------------------
 data$Teaching <- 0
 data[rating == "Yes"]$Teaching <- 1
 
@@ -49,7 +49,7 @@ all <- all[order(MidFile)]
 all
 
 
-## ----midi, include = FALSE----------------------------------------------------
+## ----midi, include = FALSE--------------------------------
 # create a list of data file names
 midi_lf <- list.files("../experiment/mid/", pattern = "mid")
 
@@ -97,7 +97,7 @@ change_1 <- c(8, 24, 49)
 change_2 <- c(16, 41, 57)
 
 
-## ----ioi, include = FALSE-----------------------------------------------------
+## ----ioi, include = FALSE---------------------------------
 data_onset <- midi[event == "Note On"]
 data_offset <- midi[event == "Note Off"]
 
@@ -143,7 +143,7 @@ for (number in change_2){
 }
 
 
-## ----ioi-all, echo = FALSE----------------------------------------------------
[…]

### 2022-10-14 experiment-1/analysis/questionnaire.R

@@ -1,4 +1,4 @@
-## ----setup, include = FALSE---------------------------------------------------
+## ----setup, include = FALSE---------------------------------
 # packages
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
@@ -6,7 +6,7 @@ if (!require("data.table")) {install.packages("data.table"); require("data.table
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
 
 
-## ----read, echo = FALSE-------------------------------------------------------
+## ----read, echo = FALSE-------------------------------------
 dt <- fread("questionnaire.csv", header = T, sep = ",", dec = ".", na.string = "NA")
 
 # change some colnames
@@ -24,10 +24,10 @@ dt_included <- dt[SubNr != 9]
 print(dt_included)
 
 
-## ----1, echo = FALSE----------------------------------------------------------
+## ----1, echo = FALSE----------------------------------------
 data.table("Answer" = dt_included$`Have you noticed anything special regarding the tasks in the experiment? If any, please describe below.`)
 
 
-## ----export, include = FALSE--------------------------------------------------
+## ----export, include = FALSE--------------------------------
 knitr::purl("questionnaire.Rmd")
 

### 2022-10-14 experiment-2/analysis/questionnaire.R

@@ -1,4 +1,4 @@
-## ----setup, include = FALSE---------------------------------------
+## ----setup, include = FALSE---------------------------------
 # packages
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
@@ -6,7 +6,7 @@ if (!require("data.table")) {install.packages("data.table"); require("data.table
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
 
 
-## ----read, echo = FALSE-------------------------------------------
+## ----read, echo = FALSE-------------------------------------
 dt <- fread("questionnaire.csv", header = T, sep = ",", dec = ".", na.string = "NA")
 
 # change some colnames
@@ -24,10 +24,10 @@ dt_included <- dt[SubNr != 4]
 print(dt_included)
 
 
-## ----1, echo = FALSE----------------------------------------------
+## ----1, echo = FALSE----------------------------------------
 data.table("Answer" = dt_included$`Have you noticed anything special regarding the tasks in the experiment? If any, please describe below.`)
 
 
-## ----export, include = FALSE--------------------------------------
+## ----export, include = FALSE--------------------------------
 knitr::purl("questionnaire.Rmd")
 

### 2023-01-06 paper/manuscript.Rmd
update docx file
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_word
 ---
 
-```{r setup, include = FALSE}
+```{r set-up, include = FALSE}
 # packages

### 2023-01-06 paper/manuscript.Rmd
fix citation
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-@tominaga_2022a extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression.
+@tominaga_2022 extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression.
 We investigated whether and how expert pianists communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound).
@@
 ## Stimuli
-We selected stimuli from the performances obtained in our previous experiments [@tominaga_2022a].
+We selected stimuli from the performances obtained in our previous experiments [@tominaga_2022].
 Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files.
@@
 
-In @tominaga_2022a, participants were asked to perform the piece with either articulation or dynamics in two different conditions.
+In @tominaga_2022, participants were asked to perform the piece with either articulation or dynamics in two different conditions.
 In the teaching condition, participants were instructed to perform the piece with the designated expressive technique as if they were teaching it to students (e.g., in a lesson).
@@
 However, the results showed that the accuracy was relatively low (52.7 % in Experiment 1; 52.8 % in Experiment 2).
-This might be because the stimuli were randomly sampled from the teaching and performing condition in @tominaga_2022a.
+This might be because the stimuli were randomly sampled from the teaching and performing condition in @tominaga_2022.
 There was great variability in the selected recordings from multiple pianists and some of them do not seem to have exhibited the characteristics of teaching performance (e.g., slower demonstration, exaggeration).

### 2023-01-06 experiment-1/analysis/analysis.R

@@ -1,4 +1,4 @@
-## ----set-up, include = FALSE------------------------------
+## ----set-up, include = FALSE--------------------------------------------------
 options(knitr.duplicate.label = "allow")
 
 # data manipulation
@@ -13,7 +13,7 @@ if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
 if (!require("performance")) {install.packages("performance"); require("performance")}
 
 
-## ----read, include = FALSE--------------------------------
+## ----read, include = FALSE----------------------------------------------------
 # read files and combine them
 data_lf <- list.files("../data", pattern = "csv")
 combined <- lapply(data_lf, function(f){
@@ -35,7 +35,7 @@ data[grepl("a_", midFile)]$Skill <- "articulation"
 data[grepl("d_", midFile)]$Skill <- "dynamics"
 
 
-## ----teaching, echo = FALSE-------------------------------
+## ----teaching, echo = FALSE---------------------------------------------------
 data$Teaching <- 0
 data[rating == "Yes"]$Teaching <- 1
 
@@ -49,7 +49,7 @@ all <- all[order(MidFile)]
 all
 
 
-## ----midi, include = FALSE--------------------------------
+## ----midi, include = FALSE----------------------------------------------------
 # create a list of data file names
 midi_lf <- list.files("../experiment/mid/", pattern = "mid")
 
@@ -97,7 +97,7 @@ change_1 <- c(8, 24, 49)
 change_2 <- c(16, 41, 57)
 
 
-## ----ioi, include = FALSE---------------------------------
+## ----ioi, include = FALSE-----------------------------------------------------
 data_onset <- midi[event == "Note On"]
 data_offset <- midi[event == "Note Off"]
 
@@ -143,7 +143,7 @@ for (number in change_2){
 }
 
 
-## ----ioi-all, echo = FALSE--------------------------------
+## ----ioi-all, echo = FALSE----------------------------------------------------
 rating <- all # rating data
 
 ioi <- dt_ioi[Subcomponent != "NA", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill)]
[…]

### 2023-01-06 experiment-1/analysis/questionnaire.R

@@ -1,4 +1,4 @@
-## ----setup, include = FALSE---------------------------------
+## ----setup, include = FALSE---------------------------------------------------
 # packages
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
@@ -6,7 +6,7 @@ if (!require("data.table")) {install.packages("data.table"); require("data.table
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
 
 
-## ----read, echo = FALSE-------------------------------------
+## ----read, echo = FALSE-------------------------------------------------------
 dt <- fread("questionnaire.csv", header = T, sep = ",", dec = ".", na.string = "NA")
 
 # change some colnames
@@ -24,10 +24,10 @@ dt_included <- dt[SubNr != 9]
 print(dt_included)
 
 
-## ----1, echo = FALSE----------------------------------------
+## ----1, echo = FALSE----------------------------------------------------------
 data.table("Answer" = dt_included$`Have you noticed anything special regarding the tasks in the experiment? If any, please describe below.`)
 
 
-## ----export, include = FALSE--------------------------------
+## ----export, include = FALSE--------------------------------------------------
 knitr::purl("questionnaire.Rmd")
 

### 2023-01-06 experiment-2/analysis/analysis.R

@@ -165,13 +165,13 @@ ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
 ioi_art_norm_teaching <- shapiro.test(ioi[Skill == "articulation"]$Teaching)
 ioi_art_norm_performance <- shapiro.test(ioi[Skill == "articulation"]$Mean)
 
-qqnorm(ioi[Skill == "articulation"]$Teaching)
-qqline(ioi[Skill == "articulation"]$Teaching)
-ioi_art_norm_teaching
-
-qqnorm(ioi[Skill == "articulation"]$Mean)
-qqline(ioi[Skill == "articulation"]$Mean)
-ioi_art_norm_performance
+# qqnorm(ioi[Skill == "articulation"]$Teaching)
+# qqline(ioi[Skill == "articulation"]$Teaching)
+# ioi_art_norm_teaching
+# 
+# qqnorm(ioi[Skill == "articulation"]$Mean)
+# qqline(ioi[Skill == "articulation"]$Mean)
+# ioi_art_norm_performance
 
 cor_ioi_art <- cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
 cor_ioi_art
@@ -182,13 +182,13 @@ cor_ioi_art
 ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
 ioi_dyn_norm_performance <- shapiro.test(ioi[Skill == "dynamics"]$Mean)
 
-qqnorm(ioi[Skill == "dynamics"]$Teaching)
-qqline(ioi[Skill == "dynamics"]$Teaching)
-ioi_dyn_norm_teaching
-
-qqnorm(ioi[Skill == "dynamics"]$Mean)
-qqline(ioi[Skill == "dynamics"]$Mean)
-ioi_dyn_norm_performance
+# qqnorm(ioi[Skill == "dynamics"]$Teaching)
+# qqline(ioi[Skill == "dynamics"]$Teaching)
+# ioi_dyn_norm_teaching
+# 
+# qqnorm(ioi[Skill == "dynamics"]$Mean)
+# qqline(ioi[Skill == "dynamics"]$Mean)
+# ioi_dyn_norm_performance
 
[…]

### 2023-01-06 experiment-2/analysis/questionnaire.R

@@ -1,4 +1,4 @@
-## ----setup, include = FALSE---------------------------------
+## ----setup, include = FALSE---------------------------------------------------
 # packages
 # data manipulation
 if (!require("data.table")) {install.packages("data.table"); require("data.table")}
@@ -6,7 +6,7 @@ if (!require("data.table")) {install.packages("data.table"); require("data.table
 if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
 
 
-## ----read, echo = FALSE-------------------------------------
+## ----read, echo = FALSE-------------------------------------------------------
 dt <- fread("questionnaire.csv", header = T, sep = ",", dec = ".", na.string = "NA")
 
 # change some colnames
@@ -24,10 +24,10 @@ dt_included <- dt[SubNr != 4]
 print(dt_included)
 
 
-## ----1, echo = FALSE----------------------------------------
+## ----1, echo = FALSE----------------------------------------------------------
 data.table("Answer" = dt_included$`Have you noticed anything special regarding the tasks in the experiment? If any, please describe below.`)
 
 
-## ----export, include = FALSE--------------------------------
+## ----export, include = FALSE--------------------------------------------------
 knitr::purl("questionnaire.Rmd")
 

### 2023-01-07 paper/manuscript.Rmd
correct some grammatical errors
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 Moreover, the same modulations of pedagogical performance parameters observed in our previous experiments such as slower demonstration and exaggerated performance, should be used to infer teaching intentions by the learners.
-In Experiment 1 participants listened to performances that followed simple musical scales.
-In Experiment 2 participants listened to performances of a more complex piece.
+In Experiment 1, participants listened to performances that followed simple musical scales.
+In Experiment 2, participants listened to performances of a more complex piece.
 
@@
 The piece was taken from "A Dozen a Day - Play with Ease in Many Keys" by Edna-Mae Burnam and modified for the experiment.
-The stimuli were performed around 80 quarter-beats per minute.
+The stimuli were performed at around 80 quarter-beats per minute.
 
@@
 
-However, dynamics (KV) seems continued to be used as cue to teaching intentions despite the increased musical complexity.
+However, dynamics (KV) seems to continue to be used as a cue to teaching intentions despite the increased musical complexity.
 Particularly performances with larger contrasts between forte and piano seem to be considered as teaching.
@@
 
-# General discussion
+# General Discussion
 
@@
 To examine which features of piano performance make musicians infer pedagogical intentions, we performed correlation and multiple regression analysis.
-Across the two experiments, it was found that loudness, particularly larger contrast between forte and piano, strongly contributed to participants’ judgments when listening to dynamics recordings.
+Across the two experiments, it was found that loudness, particularly larger contrasts between forte and piano, strongly contributed to participants’ judgments when listening to dynamics recordings.
 On the other hand, unlike what we predicted, slower performance was only considered to be for teaching for both techniques in Experiment 1 where the stimuli consisted of simple musical scales.
@@
 Therefore, participants might have had difficulties in recognising teaching intentions from articulation in Experiment 2.
-This would imply that the ease of difficulty with which teaching intentions can be derived vary across different pieces depend on a variety of musical properties.
+This would imply that the ease or difficulty with which teaching intentions can be derived varies across different pieces depending on a variety of musical properties.
 

### 2023-01-07 paper/manuscript.tex
correct some grammatical errors
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
@@
 
-\abstract{
+\abstract{%
 Perceiving pedagogical intentions is vital when learning skills from others.
@@
 The piece was taken from ``A Dozen a Day - Play with Ease in Many Keys'' by Edna-Mae Burnam and modified for the experiment.
-The stimuli were performed around 80 quarter-beats per minute.
+The stimuli were performed at around 80 quarter-beats per minute.
 
@@
 \hypertarget{general-discussion}{%
-\section{General discussion}\label{general-discussion}}
+\section{General Discussion}\label{general-discussion}}
 
@@
 To examine which features of piano performance make musicians infer pedagogical intentions, we performed correlation and multiple regression analysis.
-Across the two experiments, it was found that loudness, particularly larger contrast between forte and piano, strongly contributed to participants' judgments when listening to dynamics recordings.
+Across the two experiments, it was found that loudness, particularly larger contrasts between forte and piano, strongly contributed to participants' judgments when listening to dynamics recordings.
 On the other hand, unlike what we predicted, slower performance was only considered to be for teaching for both techniques in Experiment 1 where the stimuli consisted of simple musical scales.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-tominaga_2022a}{}}%
-Tominaga, A., Knoblich, G., \& Sebanz, N. (2022). \emph{The sound of teaching music: {Expert} pianists' performance modulations for novices}. {PsyArXiv}. \url{https://doi.org/10.31234/osf.io/wzuyj}
+\leavevmode\vadjust pre{\hypertarget{ref-tominaga_2022}{}}%
+Tominaga, A., Knoblich, G., \& Sebanz, N.
+(2022).
+Expert pianists make specific exaggerations for teaching.
+\emph{Scientific Reports}, \emph{12}(1), 21296.
+\url{https://doi.org/10.1038/s41598-022-25711-3}
 

### 2023-01-17 paper/manuscript.Rmd
correct typo
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 ## Apparatus
-The experiment was programmed in Python 3.8.2 using the PsychoPy Python library (2020.2.4; https://www.psychopy.org/) on a Mac Book Pro with Mac OS X Catalina 10.15.6.
+The experiment was programmed in Python 3.8.2 using the PsychoPy Python library (2020.2.4; https://www.psychopy.org/) on a MacBook Pro with Mac OS X Catalina 10.15.6.
 Stimuli were played using the Mido Python library (1.2.9; https://mido.readthedocs.io/en/latest/) on a Max/MSP patcher (8.1.7; https://cycling74.com/products/max).

### 2023-01-17 paper/manuscript.tex
correct typo
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@
 
-The experiment was programmed in Python 3.8.2 using the PsychoPy Python library (2020.2.4; \url{https://www.psychopy.org/}) on a Mac Book Pro with Mac OS X Catalina 10.15.6.
+The experiment was programmed in Python 3.8.2 using the PsychoPy Python library (2020.2.4; \url{https://www.psychopy.org/}) on a MacBook Pro with Mac OS X Catalina 10.15.6.
 Stimuli were played using the Mido Python library (1.2.9; \url{https://mido.readthedocs.io/en/latest/}) on a Max/MSP patcher (8.1.7; \url{https://cycling74.com/products/max}).
